### 2019-10-19 Dissonance_Santiago_v1.Rmd
Commit with first draft of paper

---
title: Do Drivers Dream of Walking? An Investigation of Dissonance in the Primary Mode of Travel from the Perspective of Subjective Wellbeing
author:
  - name: Author 1
    email: a1@university.com
    affiliation: Some University
    footnote: Corresponding Author
  - name: Author 2
    email: a2@school.com
    affiliation: Some School
address:
  - code: Some University
    address: Department, Street, City, State, Zip
  - code: Some School
    address: Department, Street, City, State, Zip
abstract: |
  Transportation in most of the world has been dominated for decades by a fascination with the automobile. Increasingly, however, it is recognized that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain users of public transport and active travel. A challenge with the way transportation policy is developed is that it tends to focus on cost-benefit and utilitarian considerations, which may miss other potential benefits of transportation. For this reason, subjective wellbeing (SWB) has been proposed as a way to enhance our understanding of the preferences and choices of travellers, as well as a way to evaluate the benefits of transportation beyond utilitarian considerations. The objective of this paper is to analyze the modes that people commonly use, and to what extent they are aligned (or not) with a variety of affective and utilitarian values. In other words, we are interested in the potential for dissonance with respect to the primary mode of travel, from the perspective of affective and utilitarian values. The study is based on data collected from a sample of travellers in the city of Santiago, in Chile. Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associated to affective values (freedom, enjoyment, and happiness) and to utilitarian values (safety, time waste, and efficiency). The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least. For those travellers who experience dissonance, active travel is the mode most commonly associated with affective values.

  To properly assess transportation policy This poses a number of challenges Broadening the commonly used transport project assessment will be relevant for achieving this goal. While satisfaction with travel has been mainly used in the context of daily trips and mainly under cost-benefit and utilitarian considerations, subjective wellbeing (SWB) over time has risen as an alternative for understanding the preferences and choices of transport users. The aim of this paper is to analyse the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile. The paper aims to reflect on the possibilities of increasing the SWB with a view to enhance the attractiveness of public transport and active travel. The paper investigates the affective and instrumental/utilitarian factors of SWB, according to modal choice. It uses an analysis of correspondence that considers the actual primary mode used, versus the mode that each individual associated to both utilitarian and affective SWB factors. The results show that there is more persistent modal dissonance between positive emotional and utilitarian associations within the more disadvantaged groups – particularly among users of public transport. The study shows that apart from time-savings and efficiency, security has also been cross-sectionally sensitive according to the data analysed. Factors such as happiness, enjoyment and freedom require far more attention in transport planning as they are strongly related to the dimensions of subjective and personal wellbeing. Targeting these factors will be relevant for attracting new users to public transportation and active travel.

journal: "An Elsevier journal"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

<!-- This paper is an R markdown document that includes self-contained, reproducible analysis. To reproduce the paper the following files are needed:

1. Dissonance_Santiago_v1.Rmd (this R markdown document)

2. `Dissonance_Santiago.RData`. For reference: this data file was created using R notebook `00. Analysis of Dissonance Detailed.Rmd`. The initial analysis was done in the same R notebook. Neither of these two notebooks are needed for this document.

3. For compiling into a pdf in the style of an Elsevier document: elsarticle.cls, elsevier-harvard.csl, elsevier-harvard-without-titles.csl, elsevier-vancouver.csl, elsevier-without-titles.cls, elsevier-with-titles.csl, elsevier-with-titles-alphabetical.csl, mybibfile.bib
-->

```{r load-packages, include=FALSE}

# Load packages used in this document

library(rticles)
library(readxl)
library(tidyverse)
library(rgdal)
library(sf)
library(ggmosaic)
library(ggthemes)
library(kableExtra)
```

```{r load-data, include=FALSE}

# To run this notebook, the file `Dissonance_Santiago.RData` is needed. This file contains the following object:
# 
# master: a dataframe with information collected from 451 respondents. The variables in the dataframe are:
# 
# - NUMERO: Respondent ID
# - USED: Main mode of transportation used by the respondent
# - FREEDOM: Mode(s) that the respondent associates with feelings of freedom
# - ENJOYMENT: Mode(s) that the respondent associates with feelings of enjoyment
# - HAPPINESS: Mode(s) that the respondent associates with feelings of happiness
# - POVERTY: Mode(s) that the respondent associates with feelings of poverty
# - LUXURY: Mode(s) that the respondent associates with feelings of luxury
# - STATUS: Mode(s) that the respondent associates with feelings of status
# - SAFETY: Mode(s) that the respondent associates with feelings of safety
# - TIME: Mode(s) that the respondent associates with feelings of WASTED TIME
# - EFFICIENCY: Mode(s) that the respondent associates with feelings of efficiency
# - AGE: Age of the respondent
# - EDUCATION: Level of education of the respondent
# - INCOME: Level of income of respondent
# - TRAVEL_TIME: Trip duration of regular commuting trip 
# - WEIGHT_*: A weight for the responses by ATTRIBUTE. Some respondents selected more than one mode that they associated with feelings of {FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, and EFFICIENCY}. To avoid giving greater weight to respondents who indicated several modes of transportation, a weight was calculated that is the inverse of the number of modes indicated. These weights can be used to weight the frequencies prior to any analysis.
# 
# The modes of transportation (USED, FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, EFFICIENCY) are coded as: 
# "A": Auto
# "B": Taxi
# "C": Colectivo
# "D": Moto
# "E": Metro
# "F": Bus
# "G": Bicycle
# "H": Walk
#
# AGE is coded as:
#
# "A": Less18
# "B": 18to24
# "C": 25to34
# "D": 35to54
# "E": 55to64
# "F": 65more
# 
# EDUCATION is coded as:
# 
# "A": ELEMENTARY
# "B": SECUNDARY
# "C": PROFESS_TECH
# "D": COLLEGE
# "E": POSTGRAD
#
# INCOME is coded as (in pesos?):
# 
# "A": Less423
# "B": 423to639
# "C": 639to977
# "D": 977to1550
# "E": 1550to2380
# "F": 2380more
# 
# TRAVEL_TIME is coded as:
#
# "A": 0-20 min
# "B": 20-40 min
# "C": 40-60 min
# "D": 1h and more

# Read the RData file:

load("Dissonance_Santiago.RData")
```

```{r data-preparation, include=FALSE}

# The master dataframe is processed for analysis. We plan to conduct two distinct types of analysis:
#
# 1. Analysis of dissonace using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.). In this case, dissonance is defined as follows:
#
# >> If the mode used is identical to the mode that the respondent associates with ATTRIBUTE (i.e. FREEDOM et al.), we consider that there is no dissonance; otherwise, we consider that there is dissonance. For example, if the respondent's main mode of transportation is Auto, and the respondent associates Auto with feelings of FREEDOM, then there is no dissonance. On the other hand, if the respondent's main mode of transportation is Auto, but associates Walking with feelings of FREEDOM, there is dissonance.
# 
# Given this, we will calculate how frequently there is dissonance at different levels of AGE, EDUCATION, INCOME, MODE, TRAVEL_TIME. Tests of independence can be implemented.
#
# 2. Analysis of dissonance using the mode USED and the mode respondents associated with ATTRIBUTE, then stratified by characteristics of respondents (i.e., AGE et al.) in this case, we see how frequently each mode was associated with ATTRIBUTE, given the main mode of transportation of the respondents.
#
# Here the dataframes are prepared to support these two types of analysis

#################################################################################
# Prepare a dataframe for the analysis of dissonance by attribute (Analysis 1.) #
#################################################################################

# First, select the variables needed from the master table, and code dissonance as 1 (no dissonance) or two (dissonance):

Overall_dissonance <- master %>%
  transmute(USED, 
            FREEDOM_DISSONANCE = ifelse(USED == FREEDOM, 1, 2),
            ENJOYMENT_DISSONANCE = ifelse(USED == ENJOYMENT, 1, 2),
            HAPPINESS_DISSONANCE = ifelse(USED == HAPPINESS, 1, 2),
            POVERTY_DISSONANCE = ifelse(USED == POVERTY, 1, 2),
            LUXURY_DISSONANCE = ifelse(USED == LUXURY, 1, 2),
            STATUS_DISSONANCE = ifelse(USED == STATUS, 1, 2),
            SAFETY_DISSONANCE = ifelse(USED == SAFETY, 1, 2),
            TIME_DISSONANCE = ifelse(USED == TIME, 1, 2),
            EFFICIENCY_DISSONANCE = ifelse(USED == EFFICIENCY, 1, 2),
            AGE,
            EDUCATION,
            INCOME,
            TRAVEL_TIME)

# Recode variables and convert to factors:

Overall_dissonance <- Overall_dissonance %>%
  mutate(USED = case_when(USED == "A" ~ "Auto",
                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
                                  USED == "E" | USED == "F" ~ "Public",
                                  USED == "G" | USED == "H" ~ "Active"),
         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
                         AGE == "D" ~ "35 - 54",
                         AGE == "E" | AGE == "F" ~ "> 54"),
         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
                               EDUCATION == "E" ~ "Graduate"),
         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
                            INCOME == "C" | INCOME == "D" ~ "Middle",
                            INCOME == "E" | INCOME == "F" ~ "High"),
         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
                                 TRAVEL_TIME == "D" ~ "> 60 min")) %>%
  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
         FREEDOM_DISSONANCE = factor(FREEDOM_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         ENJOYMENT_DISSONANCE = factor(ENJOYMENT_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         HAPPINESS_DISSONANCE = factor(HAPPINESS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         POVERTY_DISSONANCE = factor(POVERTY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         LUXURY_DISSONANCE = factor(LUXURY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         STATUS_DISSONANCE = factor(STATUS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         SAFETY_DISSONANCE = factor(SAFETY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         TIME_DISSONANCE = factor(TIME_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         EFFICIENCY_DISSONANCE = factor(EFFICIENCY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))

#############################################################################
# Prepare a dataframe for the analysis of dissonance by modes (Analysis 2.) #
#############################################################################

# First, split the responses regarding the modes associated with each attribute, so that we can record each mode selected individually:

Modes_by_Attribute <- master %>% 
    mutate(FREEDOM = strsplit(as.character(FREEDOM), ""),
           ENJOYMENT = strsplit(as.character(ENJOYMENT), ""),
           HAPPINESS = strsplit(as.character(HAPPINESS), ""),
           POVERTY = strsplit(as.character(POVERTY), ""),
           LUXURY = strsplit(as.character(LUXURY), ""),
           STATUS = strsplit(as.character(STATUS), ""),
           SAFETY = strsplit(as.character(SAFETY), ""),
           TIME = strsplit(as.character(TIME), ""),
           EFFICIENCY = strsplit(as.character(EFFICIENCY), ""))

# Here, we convert each of the responses into an individual row and stack the resulting dataframes, after adding the name of the attribute for identification:

Modes_by_Attribute <- rbind(data.frame(Modes_by_Attribute %>% 
                                         select(-c(ENJOYMENT, 
                                                   HAPPINESS,
                                                   POVERTY,
                                                   LUXURY,
                                                   STATUS,
                                                   SAFETY, 
                                                   TIME, 
                                                   EFFICIENCY,
                                                   WEIGHT_ENJOYMENT, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_POVERTY,
                                                   WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_SAFETY, 
                                                   WEIGHT_TIME, 
                                                   WEIGHT_EFFICIENCY)) %>% 
                                         rename(IDEAL = FREEDOM, WEIGHT = WEIGHT_FREEDOM) %>%
                                         unnest(IDEAL),
                                       ATTRIBUTE = "FREEDOM"),
                            data.frame(Modes_by_Attribute %>%
                                         select(-c(FREEDOM, 
                                                   HAPPINESS,
                                                   POVERTY,
                                                   LUXURY,
                                                   STATUS,
                                                   SAFETY, 
                                                   TIME, 
                                                   EFFICIENCY,
                                                   WEIGHT_FREEDOM, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_POVERTY,
                                                   WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_SAFETY, 
                                                   WEIGHT_TIME, 
                                                   WEIGHT_EFFICIENCY)) %>% 
                                         rename(IDEAL = ENJOYMENT, WEIGHT = WEIGHT_ENJOYMENT) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "ENJOYMENT"),
                            data.frame(Modes_by_Attribute %>% 
                                         select(-c(FREEDOM, 
                                                   ENJOYMENT,
                                                   POVERTY,
                                                   LUXURY,
                                                   STATUS,
                                                   SAFETY, 
                                                   TIME, 
                                                   EFFICIENCY,
                                                   WEIGHT_FREEDOM,
                                                   WEIGHT_ENJOYMENT,
                                                   WEIGHT_POVERTY,
                                                   WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_SAFETY, 
                                                   WEIGHT_TIME, 
                                                   WEIGHT_EFFICIENCY)) %>% 
                                         rename(IDEAL = HAPPINESS, WEIGHT = WEIGHT_HAPPINESS) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "HAPPINESS"),
                            data.frame(Modes_by_Attribute %>% 
                                         select(-c(FREEDOM, 
                                                   ENJOYMENT, 
                                                   HAPPINESS,
                                                   LUXURY,
                                                   STATUS,
                                                   SAFETY,
                                                   TIME, 
                                                   EFFICIENCY,
                                                   WEIGHT_FREEDOM, 
                                                   WEIGHT_ENJOYMENT, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_SAFETY,
                                                   WEIGHT_TIME, 
                                                   WEIGHT_EFFICIENCY)) %>%
                                         rename(IDEAL = POVERTY, WEIGHT = WEIGHT_POVERTY) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "POVERTY"),
                            data.frame(Modes_by_Attribute %>% 
                                         select(-c(FREEDOM, 
                                                   ENJOYMENT, 
                                                   HAPPINESS,
                                                   POVERTY,
                                                   #LUXURY,
                                                   STATUS,
                                                   SAFETY,
                                                   TIME, 
                                                   EFFICIENCY,
                                                   WEIGHT_FREEDOM, 
                                                   WEIGHT_ENJOYMENT, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_POVERTY,
                                                   #WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_SAFETY,
                                                   WEIGHT_TIME, 
                                                   WEIGHT_EFFICIENCY)) %>%
                                         rename(IDEAL = LUXURY, WEIGHT = WEIGHT_LUXURY) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "LUXURY"),
                            data.frame(Modes_by_Attribute %>% 
                                         select(-c(FREEDOM, 
                                                   ENJOYMENT, 
                                                   HAPPINESS,
                                                   POVERTY,
                                                   LUXURY,
                                                   #STATUS,
                                                   SAFETY,
                                                   TIME, 
                                                   EFFICIENCY,
                                                   WEIGHT_FREEDOM, 
                                                   WEIGHT_ENJOYMENT, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_POVERTY,
                                                   WEIGHT_LUXURY,
                                                   #WEIGHT_STATUS,
                                                   WEIGHT_SAFETY,
                                                   WEIGHT_TIME, 
                                                   WEIGHT_EFFICIENCY)) %>%
                                         rename(IDEAL = STATUS, WEIGHT = WEIGHT_STATUS) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "STATUS"),
                            data.frame(Modes_by_Attribute %>% 
                                         select(-c(FREEDOM, 
                                                   ENJOYMENT, 
                                                   HAPPINESS,
                                                   POVERTY,
                                                   LUXURY,
                                                   STATUS,
                                                   TIME, 
                                                   EFFICIENCY,
                                                   WEIGHT_FREEDOM, 
                                                   WEIGHT_ENJOYMENT, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_POVERTY,
                                                   WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_TIME, 
                                                   WEIGHT_EFFICIENCY)) %>%
                                         rename(IDEAL = SAFETY, WEIGHT = WEIGHT_SAFETY) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "SAFETY"),
                            data.frame(Modes_by_Attribute %>% 
                                         select(-c(FREEDOM, 
                                                   ENJOYMENT, 
                                                   HAPPINESS,
                                                   POVERTY,
                                                   LUXURY,
                                                   STATUS,
                                                   SAFETY,
                                                   EFFICIENCY,
                                                   WEIGHT_FREEDOM, 
                                                   WEIGHT_ENJOYMENT, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_POVERTY,
                                                   WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_SAFETY,
                                                   WEIGHT_EFFICIENCY)) %>%
                                         rename(IDEAL = TIME, WEIGHT = WEIGHT_TIME) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "TIME"),
                            data.frame(Modes_by_Attribute %>% 
                                         select(-c(FREEDOM, 
                                                   ENJOYMENT, 
                                                   HAPPINESS,
                                                   POVERTY,
                                                   LUXURY,
                                                   STATUS,
                                                   SAFETY,
                                                   TIME, 
                                                   WEIGHT_FREEDOM, 
                                                   WEIGHT_ENJOYMENT, 
                                                   WEIGHT_HAPPINESS,
                                                   WEIGHT_POVERTY,
                                                   WEIGHT_LUXURY,
                                                   WEIGHT_STATUS,
                                                   WEIGHT_SAFETY,
                                                   WEIGHT_TIME)) %>%
                                         rename(IDEAL = EFFICIENCY, WEIGHT = WEIGHT_EFFICIENCY) %>%
                                         unnest(IDEAL), 
                                       ATTRIBUTE = "EFFICIENCY"))

# There are some missing values. Drop all NAs:

Modes_by_Attribute <- drop_na(Modes_by_Attribute)

# We now recode the variables:

Modes_by_Attribute <- Modes_by_Attribute %>%
  mutate(USED = case_when(USED == "A" ~ "Auto",
                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
                                  USED == "E" | USED == "F" ~ "Public",
                                  USED == "G" | USED == "H" ~ "Active"),
         IDEAL = case_when(IDEAL == "A" ~ "Auto",
                                  IDEAL == "B" | IDEAL == "C" | IDEAL == "D" ~ "Other",
                                  IDEAL == "E" | IDEAL == "F" ~ "Public",
                                  IDEAL == "G" | IDEAL == "H" ~ "Active"),
         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
                         AGE == "D" ~ "35 - 54",
                         AGE == "E" | AGE == "F" ~ "> 54"),
         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
                               EDUCATION == "E" ~ "Graduate"),
         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
                            INCOME == "C" | INCOME == "D" ~ "Middle",
                            INCOME == "E" | INCOME == "F" ~ "High"),
         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
                                 TRAVEL_TIME == "D" ~ "> 60 min"))

# After recoding the , there will be some duplicate entries, because a person may have attributed, say, feelings of freedom to walking and cycling, so in the table this will appear as two instances of "Active". This is ok, because each is weighted appropriately.

# Convert to factors:

Modes_by_Attribute <- Modes_by_Attribute %>%
  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
         IDEAL = factor(IDEAL, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))
```

```{r cross-tabs-function, include=FALSE}

## Define functions for crosstabs; these functions enhance the base crosstabs functions and make it easier to report cross tabulations in different ways.

crosstab <- function (..., dec.places = NULL,
                           type = NULL,
                           style = "wide",
                           row.vars = NULL,
                           col.vars = NULL,
                           percentages = TRUE, 
                           addmargins = TRUE,
                           subtotals=TRUE)

###################################################################################
#                                                                                 #
# Function created by Dr Paul Williamson, Dept. of Geography and Planning,        #
# School of Environmental Sciences, University of Liverpool, UK.                  #
#                                                                                 #
# Adapted from the function ctab() in the catspec packge.                         #
#                                                                                 #
# Version: 12th July 2013                                                         #
#                                                                                 #
# Output best viewed using the companion function print.crosstab()                #
#                                                                                 #
###################################################################################

  #Declare function used to convert frequency counts into relevant type of proportion or percentage
  {mk.pcnt.tbl <- function(tbl, type) {
        a <- length(row.vars)
        b <- length(col.vars)
        mrgn <- switch(type, column.pct = c(row.vars[-a], col.vars), 
                            row.pct = c(row.vars, col.vars[-b]),
                            joint.pct = c(row.vars[-a], col.vars[-b]),
                            total.pct = NULL)
        tbl <- prop.table(tbl, mrgn)
        if (percentages) {
            tbl <- tbl * 100
        }
        tbl
    }

    #Find no. of vars (all; row; col) for use in subsequent code
    n.row.vars <- length(row.vars)
    n.col.vars <- length(col.vars)
    n.vars <- n.row.vars + n.col.vars

    #Check to make sure all user-supplied arguments have valid values
    stopifnot(as.integer(dec.places) == dec.places, dec.places > -1)
    #type: see next section of code
    stopifnot(is.character(style))    
    stopifnot(is.logical(percentages))
    stopifnot(is.logical(addmargins))
    stopifnot(is.logical(subtotals))
    stopifnot(n.vars>=1)

    #Convert supplied table type(s) into full text string (e.g. "f" becomes "frequency")
    #If invalid type supplied, failed match gives user automatic error message
    types <- NULL
    choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
    for (tp in type) types <- c(types, match.arg(tp, choices))
    type <- types

    #If no type supplied, default to 'frequency + total' for univariate tables and to
    #'frequency' for multi-dimenstional tables

    #For univariate table....
    if (n.vars == 1) {
      if (is.null(type)) {
        # default = freq count + total.pct  
        type <- c("frequency", "total.pct")
        #row.vars <- 1
      } else {
        #and any requests for row / col / joint.pct must be changed into requests for 'total.pct'
        type <- ifelse(type == "frequency", "frequency", "total.pct")
      }
    #For multivariate tables...
    } else if (is.null(type)) {
      # default = frequency count  
      type <- "frequency"
    }

    #Check for integrity of requested analysis and adjust values of function arguments as required

    if ((addmargins==FALSE) & (subtotals==FALSE)) {
      warning("WARNING: Request to suppress subtotals (subtotals=FALSE) ignored because no margins requested (addmargins=FALSE)")
      subtotals <- TRUE
    }

    if ((n.vars>1) & (length(type)>1) & (addmargins==TRUE)) {
      warning("WARNING: Only row totals added when more than one table type requested")
      #Code lower down selecting type of margin implements this...
    }

    if ((length(type)>1) & (subtotals==FALSE)) { 
      warning("WARNING: Can only request supply one table type if requesting suppression of subtotals; suppression of subtotals not executed")
      subtotals <- TRUE
    }

    if ((length(type)==1) & (subtotals==FALSE)) {
      choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
      tp <- match.arg(type, choices)
      if (tp %in% c("row.pct","column.pct","joint.pct")) {
          warning("WARNING: subtotals can only be suppressed for tables of type 'frequency' or 'total.pct'")
          subtotals<- TRUE
         }
    }

    if ((n.vars > 2) & (n.col.vars>1) & (subtotals==FALSE)) 
      warning("WARNING: suppression of subtotals assumes only 1 col var; table flattened accordingly")

    if ( (subtotals==FALSE) & (n.vars>2) )  {
    #If subtotals not required AND total table vars > 2
    #Reassign all but last col.var as row vars
    #[because, for simplicity, crosstabs assumes removal of subtotals uses tables with only ONE col var]
    #N.B. Subtotals only present in tables with > 2 cross-classified vars...
      if (length(col.vars)>1) {
        row.vars <- c(row.vars,col.vars[-length(col.vars)])
        col.vars <- col.vars[length(col.vars)]
        n.row.vars <- length(row.vars)
        n.col.vars <- 1
      }
    }

    #If dec.places not set by user, set to 2 unlesss only one table of type frequency requested,
    #in which case set to 0.  [Leaves user with possibility of having frequency tables with > 0 dp]
    if (is.null(dec.places)) {
      if ((length(type)==1) & (type[1]=="frequency")) {
        dec.places <- 0
      } else {
        dec.places <-2
      }
    }

    #Take the original input data, whatever form originally supplied in,
    #convert into table format using requested row and col vars, and save as 'tbl'

    args <- list(...)

    if (length(args) > 1) {
        if (!all(sapply(args, is.factor))) 
            stop("If more than one argument is passed then all must be factors")
        tbl <- table(...)
    }
    else {
        if (is.factor(...)) {
            tbl <- table(...)
        }
        else if (is.table(...)) {
            tbl <- eval(...)
        }
        else if (is.data.frame(...)) {
            #tbl <- table(...)
            if (is.null(row.vars) && is.null(col.vars)) {
              tbl <- table(...)
            }
            else {
              var.names <- c(row.vars,col.vars)
              A <- (...)
              tbl <- table(A[var.names])
              if(length(var.names==1)) names(dimnames(tbl)) <- var.names
              #[table() only autocompletes dimnames for multivariate crosstabs of dataframes]
            }
        }
        else if (class(...) == "ftable") {
            tbl <- eval(...)
            if (is.null(row.vars) && is.null(col.vars)) {
                row.vars <- names(attr(tbl, "row.vars"))
                col.vars <- names(attr(tbl, "col.vars"))
            }
            tbl <- as.table(tbl)
        }
        else if (class(...) == "ctab") {
            tbl <- eval(...)
            if (is.null(row.vars) && is.null(col.vars)) {
                row.vars <- tbl$row.vars
                col.vars <- tbl$col.vars
            }
            for (opt in c("dec.places", "type", "style", "percentages", 
                "addmargins", "subtotals")) if (is.null(get(opt))) 
                assign(opt, eval(parse(text = paste("tbl$", opt, 
                  sep = ""))))
            tbl <- tbl$table
        }
        else {
            stop("first argument must be either factors or a table object")
        }
    }

    #Convert supplied table style into full text string (e.g. "l" becomes "long")
    style <- match.arg(style, c("long", "wide"))

    #Extract row and col names to be used in creating 'tbl' from supplied input data
    nms <- names(dimnames(tbl))
    z <- length(nms)
    if (!is.null(row.vars) && !is.numeric(row.vars)) {
        row.vars <- order(match(nms, row.vars), na.last = NA)
    }
    if (!is.null(col.vars) && !is.numeric(col.vars)) {
        col.vars <- order(match(nms, col.vars), na.last = NA)
    }
    if (!is.null(row.vars) && is.null(col.vars)) {
        col.vars <- (1:z)[-row.vars]
    }
    if (!is.null(col.vars) && is.null(row.vars)) {
        row.vars <- (1:z)[-col.vars]
    }
    if (is.null(row.vars) && is.null(col.vars)) {
        col.vars <- z
        row.vars <- (1:z)[-col.vars]
    }

    #Take the original input data, converted into table format using supplied row and col vars (tbl)
    #and create a second version (crosstab) which stores results as percentages if a percentage table type is requested.
    if (type[1] == "frequency") 
      crosstab <- tbl
    else 
      crosstab <- mk.pcnt.tbl(tbl, type[1])

    #If multiple table types requested, create and add these to 
    if (length(type) > 1) {
      tbldat <- as.data.frame.table(crosstab)
      z <- length(names(tbldat)) + 1
      tbldat[z] <- 1
      pcntlab <- type
      pcntlab[match("frequency", type)] <- "Count"
      pcntlab[match("row.pct", type)] <- "Row %"
      pcntlab[match("column.pct", type)] <- "Column %"
      pcntlab[match("joint.pct", type)] <- "Joint %"
      pcntlab[match("total.pct", type)] <- "Total %"
      for (i in 2:length(type)) {
          if (type[i] == "frequency") 
              crosstab <- tbl
          else crosstab <- mk.pcnt.tbl(tbl, type[i])
          crosstab <- as.data.frame.table(crosstab)
          crosstab[z] <- i
          tbldat <- rbind(tbldat, crosstab)
      }
      tbldat[[z]] <- as.factor(tbldat[[z]])
      levels(tbldat[[z]]) <- pcntlab
      crosstab <- xtabs(Freq ~ ., data = tbldat)
      names(dimnames(crosstab))[z - 1] <- ""
    }

    #Add margins if required, adding only those margins appropriate to user request
    if (addmargins==TRUE) {

      vars <- c(row.vars,col.vars)

      if (length(type)==1) {
      if (type=="row.pct") 
        { crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
          tbl <- addmargins(tbl,margin=c(vars[n.vars]))
        }
      else 
        { if (type=="column.pct") 
            { crosstab <- addmargins(crosstab,margin=c(vars[n.row.vars]))
              tbl <- addmargins(tbl,margin=c(vars[n.row.vars]))
            }
          else 
            { if (type=="joint.pct") 
              { crosstab <- addmargins(crosstab,margin=c(vars[(n.row.vars)],vars[n.vars])) 
                tbl <- addmargins(tbl,margin=c(vars[(n.row.vars)],vars[n.vars])) 
              }
              else #must be total.pct OR frequency
                { crosstab <- addmargins(crosstab)
                  tbl <- addmargins(tbl)
                }
            }
  	     } 
      }

      #If more than one table type requested, only adding row totals makes any sense...
      if (length(type)>1) {
        crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
        tbl <- addmargins(tbl,margin=c(vars[n.vars]))
      }

    }

    #If subtotals not required, and total vars > 2, create dataframe version of table, with relevent
    #subtotal rows / cols dropped [Subtotals only present in tables with > 2 cross-classified vars]
    t1 <- NULL
    if ( (subtotals==FALSE) & (n.vars>2) )  {

    #Create version of crosstab in ftable format
    t1 <- crosstab 
    t1 <- ftable(t1,row.vars=row.vars,col.vars=col.vars)

    #Convert to a dataframe
    t1 <- as.data.frame(format(t1),stringsAsFactors=FALSE)

    #Remove backslashes from category names AND colnames
    t1 <- apply(t1[,],2, function(x) gsub("\"","",x))
    #Remove preceding and trailing spaces from category names to enable accurate capture of 'sum' rows/cols
    #[Use of grep might extrac category labels with 'sum' as part of a longer one or two word string...]
    t1 <- apply(t1,2,function(x) gsub("[[:space:]]*$","",gsub("^[[:space:]]*","",x)))

    #Reshape dataframe to that variable and category labels display as required
    #(a) Move col category names down one row; and move col variable name one column to right
    t1[2,(n.row.vars+1):ncol(t1)] <- t1[1,(n.row.vars+1):ncol(t1)]
    t1[1,] <- ""
    t1[1,(n.row.vars+2)] <- t1[2,(n.row.vars+1)]    
    #(b) Drop the now redundant column separating the row.var labels from the table data + col.var labels
    t1 <- t1[,-(n.row.vars+1)]

    #In 'lab', assign category labels for each variable to all rows (to allow identification of sub-totals) 
    lab <- t1[,1:n.row.vars]
    for (c in 1:n.row.vars) {
      for (r in 2:nrow(lab)) {
        if (lab[r,c]=="") lab[r,c] <- lab[r-1,c]  
      }
    }

    lab <- (apply(lab[,1:n.row.vars],2,function(x) x=="Sum"))
    lab <- apply(lab,1,sum)
    #Filter out rows of dataframe containing subtotals

    t1 <- t1[((lab==0) | (lab==n.row.vars)),]

    #Move the 'Sum' label associated with last row to the first column; in the process
    #setting the final row labels associated with other row variables to ""
    t1[nrow(t1),1] <- "Sum"
    t1[nrow(t1),(2:n.row.vars)] <- ""

    #set row and column names to NULL
    rownames(t1) <- NULL
    colnames(t1) <- NULL

    }

    #Create output object 'result' [class: crosstab]
    result <- NULL
    #(a) record of argument values used to produce tabular output
    result$row.vars <- row.vars
    result$col.vars <- col.vars
    result$dec.places <- dec.places
    result$type <- type
    result$style <- style
    result$percentages <- percentages
    result$addmargins <- addmargins
    result$subtotals <- subtotals

    #(b) tabular output [3 variants]
    result$table <- tbl  #Stores original cross-tab frequency counts without margins [class: table]
    result$crosstab <- crosstab #Stores cross-tab in table format using requested style(frequency/pct) and table margins (on/off)
                                #[class: table]  
    result$crosstab.nosub <- t1  #crosstab with subtotals suppressed [class: dataframe; or NULL if no subtotals suppressed]  
    class(result) <- "crosstab"

    #Return 'result' as output of function
    result
}
```

Introduction
==========================

Transportation planning for decades has focused on providing mobility for the private automobile. This is a model of development that was initially introduced in North America as a solution to urbanizations problems, and that was eventually copied elsewhere (Brown et al., 2009; Angotti, 1996) . Despite the initial promise of automotive technology, it is now evident that mobility centred on the private automobile has given rise to a litany of maladies that are in urgent need of correction. This includes environmental concerns (i.e., climate change; Chapman, 2007) as well as other social (Boschmann and Kwan, 2008), health (Khreis et al., 2016), and equity issues (Bocarejo and Oviedo, 2012). 
As the real impacts of our societal dependence on the private autombobile have become increasingly evident, the transportation agenda has in recent years aimed to shift focus to the reduction of car-use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives than just the private automobile (Miller, 2011) . In order to successfully achieve this goal, it is essential not only to provide the services and facilities that support public transportation and active travel, but also to attract new users to these modes of transportation (Ettema et al. 2011). Within this context, it has been argued that sustainable transportation policies require all participants in the transportation system to challenge what Gossling and Cohen (2014) term “transportation taboos”: deep-seated ideas concerning the contribution to emissions by individuals, the inequality of market-based approaches, and the social and psychological functions of transportation. With respect to the latter, moving beyond a purely utilitarian focus, it is important to understand how users perceive affective and instrumental elements on their transportation experience, since this can help to incorporate adequate improvements in alternative transportation, including transit and active modes, to make them more attractive to users (Anable and Gatersleben, 2005; Domarchi et al., 2008; Gatersleben and Uzzell, 2007; Steg 2005 ).

A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing (SWB. See, inter alia, De Vos et al., 2013 and Chatterjee et al., 2019) . SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” (OECD, 2013, p. 10).  Accordingly, the aim of this paper is to analyse some of the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile. Previous research suggests that public transport users experience a negative gap in desired and actual travel time, whereas active travellers don’t seem to mind somewhat longer trips than what strictly needed (e.g., Páez and Whalen, 2010). In the context of a Latin American country, historically the poor travel experience of public transit users and active travellers reflects the social inequalities of social groups that have no alternative but to move in these types of modes while living far from the work centres and main activities. The paper aims to reflect on the possibilities of increasing the SWB while travelling, and how this could increase the attractiveness of public transport and active travel in the socio-demographic groups studied. This can help not only to reduce the use of private transport but also decrease the inequality gap between these users.

The paper explores how positive affective and instrumental/utilitarian factors of SWB correspond to the use of the primary mode of transportation. It uses an analysis of correspondence that considers the actual primary mode versus the mode that individuals associated to both utilitarian (designed to be useful or practical rather than attractive) and affective (expressing a person's feelings) SWB factors. For example, it will be analysed if a person who uses public transport as the primary mode, tends to associate these modes with positive affective factors (as freedom, enjoyment or happiness) or positive utilitarian factors (as security, time-savings or efficiency). We hypothesize that there is a more persistent non-correspondence or mismatch within the more disadvantage groups or within the users of public transport.

The paper contributes to the literature in three areas. First, it contributes to an emerging literature on the topic in the context of the Global South (Bejarano et al., 2017 ; Shao and Liang, 2019 ; Van et al., 2014 ; Zorrilla et al., 2019);  to the best of our knowledge, the case of Chile has not yet been reported. Second, although there is literature on the enjoyment of commute and other emotional factors, from a hedonic and even eudaimonic perspectives, the analysis has yet to be applied more fully in terms of distributional issues – i.e. which groups are mostly disadvantaged. Finally, the analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’ – implying their preferences, even in situations when their ideal mode is not part of their actual choice set. The attitudes of travellers towards transport modes are critical factors to be considered by policy-makers in case they want to promote and increase the use of public transport or active modes (e.g., Bejarano et al., 2019). The paper explores these positive and negative associations within the transport options used in Santiago.

Background
============

The transportation community has for the most part already agreed to the need of looking at mobility and transport issues from the lens of wellbeing, to broaden the commonly used utilitarian perspective to evaluate projects. Users’ travel satisfaction (Bergstad, 2001) has been the primary way to direct this challenge towards everyday mobility, resulting on research about satisfaction with different transport modes. For example, numerous studies report that car users have a higher level of satisfaction compared to other transport modes (Redmond and Mokhtarian, 2001 ; Bergstad et al. 2011; Eriksson et al. 2013; Whalen et al., 2013). In a similar way, there are multiple reports that active travel also tends to yield high levels of satisfaction (Smith, 2017; St-Louis et al. 2014; Paez and Whalen, 2010; Whalen et al., 2013), In contrast, public transport users tend to assess their experience more negatively (De Vos et al. 2016; Abenoza et al. 2017; Ettema et al. 2012; Páez and Whalen, 2010). Multi-modal trips also influence satisfaction levels; for instance, when an individual chooses a particular mode of transportation, she will report a higher level of satisfaction with that chosen mode – perhaps as a form of post hoc validation (Susilo and Cats, 2014).

While the use of travel satisfaction has been mainly used in the context of daily trips – typically been linked to cost-benefit and utilitarian measurements –, the evaluation of Subjective Wellbeing (SWB) over time has risen as an alternative measure. In the field of travel behaviour, Ettema et al. (2010; p. 725) have defined SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporality – which implies assuming a tendency to be more stable over time. This concept has prompted a growing literature that complements and applies SWB in a broader range of satisfaction scales and situations. The definition of other factors such as travel choice mode, attitudes and external elements of the built environment has been studied for a broader understanding of the changes produced in the SWB. As these factors do not necessarily apply to the general life satisfaction on the long term, the studies have aimed to determine both the direct and indirect effects on the perception of users (see, e.g. Ye and Titheridge 2017). Other concepts have also emerged as the Satisfaction with Travel Scale (STS), a measurement devised by Ettema et al. (2011) as well as different scales based on people’s travel perceptions. De Vos et al. (2015) for instance, explore in detail the underlying dimensions of the affective domain of STS in which SWB is based (for more on STS see also Friman et al. 2013).

Recent literature on SWB and its link with transport have demonstrated a relationship between people’s perceptions and satisfaction with their daily travel (Smith, 2017; St-Louis et al. 2014; Paez and Whalen, 2010; Whalen et al., 2013). Scholars have shown that accessibility has been the most developed factor that influences people’s wellbeing (Delbosc, 2012), and activities have a direct impact on travel satisfaction (Bergstad et al., 2010). Delbosc (2012; 28) for instance, has summarised the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health. However, understanding the components affecting people’s perceptions implies the differentiation between the emotional (also named as symbolic-affective) and the instrumental reasons (Bergstad, 2001). Steg et al. (2011) have compared symbolic-affective opposed to instrumental-reasoned motives based on car-use, and other studies have also found associations between affective and symbolic aspects of car-use (see, e.g. Gatersleben, 2007; Lois & López-Sáez, 2009). Previous studies have demonstrated how socio-demographic factors affect the levels of SWB. The effect of income on SWB (Clarck and Oswald, 1996, Ferrer-i-Carbonell, 2005); education and unemployment (Argyle, 1999); age (Diener and Suh, 1997) and gender (Tesch-Römer et al., 2008) have already been studied. Recent research also suggests the links between commuting, SWB and emotional wellbeing assessment (Olson et al. 2013; Kahneman et al. 2004). However, more research is needed to understand how these socio-demographic variables, connect as well with the decisions on main transport mode choices; or research distinguishing between hedonic (journey experience) and eudaimonic (flourishing) value of trips.

The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel (Zorrilla et al., 2019). In this way, there is an emerging literature that investigates affective factors in travel behaviour in a number of developing countries. A cross-country study in Asia revealed that the affective factors of public transportation and car use are important, and in particular the social orderliness of transit was suggested as a way to make this mode more attractive to users (Van et al., 2014). In terms of active travel, a study in China found that attitudes that embrace new styles and technologies despite their cost are associated with the intention to continue using shared bicycles (Shao and Liang, 2019). The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows how users felt proud using a bicycle shared system, in addition to experiencing feelings of belonging to a civic culture and the enjoyment and pleasure of travel itself (Bejarano et al., 2019). This paper contributes to further our understanding of affective and instrumental factors in travel behaviour in a developing country.

Data and Methods
===================

This paper implements an analysis of correspondence comparing the primary mode of transportation with affective and utilitarian SWB factors in a sample of travellers in Santiago de Chile.

## Sample

The study is based on a survey conducted in Santiago during the months of November and December 2016, that collected information on a wide range of travel and related issues. The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012. An equal representation of both genders and a representation of the proportion of inhabitants per area have been chosen as relevant characteristics of the sample. In total, 451 persons validly completed the survey. In the first part of the questionnaire the participants were asked about basic socio-demographic data and main transport mode for commuting. In the second part, the questionnaire asked about the modes that people associate with affective and instrumental positive concepts of commuting, as well as the levels of overall satisfaction with the trips. These two sections of the survey have been considered for the analysis of this paper. 
The second part of the survey asked about the association between the primary transport mode and 18 positive and negative feelings. The question is: “Indicate the modes that you associate to the following feelings”. The respondents could indicate all the modes they associated to the feelings on the list. Three affective and three instrumental/utilitarian factors, all positive, have been considered for this analysis: freedom, enjoyment, happiness (affective), and security, time savings, efficiency (instrumental/utilitarian).
The questionnaire provides a binary indicator that describes the presence or absence of modal correspondence for each one the selected six factors. The analysis has considered socioeconomic variables (gender, age, education, occupation, income, disabilities), as well as other variables as driving licence, journey times, monthly expenditure on transport and satisfaction with the overall trip.

[REPORT DESCRIPTIVE STATISTICS? Include definitions, e.g., is K-12 equivalent to “minimal mandatory education”? What is Tech Univ? What are the range of values of low, middle, high income? Journey time is in minutes]

## Analytical Approach

The analytical approach in this paper is based on correspondence. Previous research has developed the concept of modal dissonance for referring to the mismatch between the actual mode and the mode that enables users to experience positive affective or instrumental factors (De Vos et al., (2012; 2014) and Schwanen and Mokhtarian, 2004, 2005a, 2005b). More concretely, Schwanen and Mokhtarian (2004; 89) define dissonance based on the incongruence between residential neighbourhood where the individual currently resides and her preference structure toward such characteristics of the residential environment. In this paper we consider correspondence, which happens when travellers associate the positive utilitarian and affective SWB factors to the mode they have used as their primary transport mode for commuting or performing their main activities. The opposite of correspondence would be modal dissonance.

More specifically, the concept of modal dissonance means that a user of mode X identifies a different mode Y when associating affective values. For example, a user of private transport (i.e., mode “Car”)  may select mode “Bicycle” when asked about the of the association between the concept of freedom to a transport mode. In this case, the person who uses the mode “Car” as their primary mode of transportation attaches positive emotional and instrumental factors not to that mode, but to a different one – in this case to the bicycle. It could be the case that the modal dissonance corresponds just to one of the types of factors, either affective or instrumental. For example, it is possible that a person who uses the Metro as their main transport mode associates that mode to the instrumental factors (security, time savings, efficiency) – but relates positive emotional factors (freedom, enjoyment, happiness) to a different mode, say to the bicycle.

The ways for measuring equity in transport projects and the most vulnerable groups affected by transport have been the aspects that have nurtured the focus of this study. The hypothesis is that public transport users will show a lower correspondence between their primary mode and the modes they relate with positive factors of SWB. This is relevant as more disadvantaged people have less options of choosing their preferred transport modes and they tend to associate positive affective and instrumental factors to modes that they are not able to use. These perceptions evidence equity gaps between groups – where the most vulnerable groups are much more affected.
The methods used are analysis of correspondence and multinomial regression, both around the associations of transport modes and affective and instrumental factors, derived from the SWB framework.

Results
==========

```{r cross-with-instrumental, include=FALSE, eval=FALSE}

# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)

## Age

age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
age_by_safety <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "SAFETY_DISSONANCE", type = "r")
age_by_time <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "TIME_DISSONANCE", type = "r")
age_by_efficiency <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "EFFICIENCY_DISSONANCE", type = "r")

## Education

education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
education_by_safety <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "SAFETY_DISSONANCE", type = "r")
education_by_time <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "TIME_DISSONANCE", type = "r")
education_by_efficiency <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "EFFICIENCY_DISSONANCE", type = "r")

## Income

income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
income_by_safety <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "SAFETY_DISSONANCE", type = "r")
income_by_time <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "TIME_DISSONANCE", type = "r")
income_by_efficiency <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")

## Mode

mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
mode_by_safety <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "SAFETY_DISSONANCE", type = "r")
mode_by_time <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "TIME_DISSONANCE", type = "r")
mode_by_efficiency <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "EFFICIENCY_DISSONANCE", type = "r")

## Travel Time

time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
time_by_safety <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "SAFETY_DISSONANCE", type = "r")
time_by_time <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "TIME_DISSONANCE", type = "r")
time_by_efficiency <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")

```

```{r cross-without-instrumental, include=FALSE}

# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)

## Age

age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
age_by_poverty <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "POVERTY_DISSONANCE", type = "r")
age_by_luxury <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "LUXURY_DISSONANCE", type = "r")
age_by_status <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "STATUS_DISSONANCE", type = "r")

## Education

education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
education_by_poverty <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "POVERTY_DISSONANCE", type = "r")
education_by_luxury <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "LUXURY_DISSONANCE", type = "r")
education_by_status <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "STATUS_DISSONANCE", type = "r")

## Income

income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
income_by_poverty <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "POVERTY_DISSONANCE", type = "r")
income_by_luxury <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "LUXURY_DISSONANCE", type = "r")
income_by_status <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "STATUS_DISSONANCE", type = "r")

## Mode

mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
mode_by_poverty <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "POVERTY_DISSONANCE", type = "r")
mode_by_luxury <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "LUXURY_DISSONANCE", type = "r")
mode_by_status <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "STATUS_DISSONANCE", type = "r")

## Travel Time

time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
time_by_poverty <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "POVERTY_DISSONANCE", type = "r")
time_by_luxury <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "LUXURY_DISSONANCE", type = "r")
time_by_status <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "STATUS_DISSONANCE", type = "r")

```

```{r collect-cross-tabulation-results-with-instrumental, include=FALSE, eval=FALSE}

# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES

## Age

age_results <- cbind(age_by_freedom$crosstab, 
                     age_by_enjoyment$crosstab, 
                     age_by_happiness$crosstab,
                     age_by_safety$crosstab,
                     age_by_time$crosstab,
                     age_by_efficiency$crosstab)

# Drop the row totals
age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")

# Convert to dataframe and make the rownames a variable
age_results <- age_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
age_results <- age_results %>%
  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
         chi2.happiness = summary(age_by_happiness$table)$p.value,
         chi2.safety = summary(age_by_safety$table)$p.value,
         chi2.time = summary(age_by_time$table)$p.value,
         chi2.efficiency = summary(age_by_efficiency$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Safety,
         chi2.safety,
         Time,
         chi2.time,
         Efficiency,
         chi2.efficiency)

## Education

education_results <- cbind(education_by_freedom$crosstab, 
                     education_by_enjoyment$crosstab, 
                     education_by_happiness$crosstab,
                     education_by_safety$crosstab,
                     education_by_time$crosstab,
                     education_by_efficiency$crosstab)

# Drop the row totals
education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")

# Convert to dataframe and make the rownames a variable
education_results <- education_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
education_results <- education_results %>%
  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
         chi2.happiness = summary(education_by_happiness$table)$p.value,
         chi2.safety = summary(education_by_safety$table)$p.value,
         chi2.time = summary(education_by_time$table)$p.value,
         chi2.efficiency = summary(education_by_efficiency$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Safety,
         chi2.safety,
         Time,
         chi2.time,
         Efficiency,
         chi2.efficiency)

## Income

income_results <- cbind(income_by_freedom$crosstab, 
                     income_by_enjoyment$crosstab, 
                     income_by_happiness$crosstab,
                     income_by_safety$crosstab,
                     income_by_time$crosstab,
                     income_by_efficiency$crosstab)

# Drop the row totals
income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")

# Convert to dataframe and make the rownames a variable
income_results <- income_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
income_results <- income_results %>%
  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
         chi2.happiness = summary(income_by_happiness$table)$p.value,
         chi2.safety = summary(income_by_safety$table)$p.value,
         chi2.time = summary(income_by_time$table)$p.value,
         chi2.efficiency = summary(income_by_efficiency$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Safety,
         chi2.safety,
         Time,
         chi2.time,
         Efficiency,
         chi2.efficiency)

## Mode USED

mode_results <- cbind(mode_by_freedom$crosstab, 
                     mode_by_enjoyment$crosstab, 
                     mode_by_happiness$crosstab,
                     mode_by_safety$crosstab,
                     mode_by_time$crosstab,
                     mode_by_efficiency$crosstab)

# Drop the row totals
mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")

# Convert to dataframe and make the rownames a variable
mode_results <- mode_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
mode_results <- mode_results %>%
  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
         chi2.happiness = summary(mode_by_happiness$table)$p.value,
         chi2.safety = summary(mode_by_safety$table)$p.value,
         chi2.time = summary(mode_by_time$table)$p.value,
         chi2.efficiency = summary(mode_by_efficiency$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Safety,
         chi2.safety,
         Time,
         chi2.time,
         Efficiency,
         chi2.efficiency)

## Time

time_results <- cbind(time_by_freedom$crosstab, 
                     time_by_enjoyment$crosstab, 
                     time_by_happiness$crosstab,
                     time_by_safety$crosstab,
                     time_by_time$crosstab,
                     time_by_efficiency$crosstab)

# Drop the row totals
time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")

# Convert to dataframe and make the rownames a variable
time_results <- time_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
time_results <- time_results %>%
  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
         chi2.happiness = summary(time_by_happiness$table)$p.value,
         chi2.safety = summary(time_by_safety$table)$p.value,
         chi2.time = summary(time_by_time$table)$p.value,
         chi2.efficiency = summary(time_by_efficiency$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Safety,
         chi2.safety,
         Time,
         chi2.time,
         Efficiency,
         chi2.efficiency)
```

```{r collect-cross-tabulation-results-without-instrumental, include=FALSE}

# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES

## Age

age_results <- cbind(age_by_freedom$crosstab, 
                     age_by_enjoyment$crosstab, 
                     age_by_happiness$crosstab,
                     age_by_poverty$crosstab,
                     age_by_luxury$crosstab,
                     age_by_status$crosstab)

# Drop the row totals
age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")

# Convert to dataframe and make the rownames a variable
age_results <- age_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
age_results <- age_results %>%
  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
         chi2.happiness = summary(age_by_happiness$table)$p.value,
         chi2.poverty = summary(age_by_poverty$table)$p.value,
         chi2.luxury = summary(age_by_luxury$table)$p.value,
         chi2.status = summary(age_by_status$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Poverty,
         chi2.poverty,
         Luxury,
         chi2.luxury,
         Status,
         chi2.status)

## Education

education_results <- cbind(education_by_freedom$crosstab, 
                     education_by_enjoyment$crosstab, 
                     education_by_happiness$crosstab,
                     education_by_poverty$crosstab,
                     education_by_luxury$crosstab,
                     education_by_status$crosstab)

# Drop the row totals
education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")

# Convert to dataframe and make the rownames a variable
education_results <- education_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
education_results <- education_results %>%
  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
         chi2.happiness = summary(education_by_happiness$table)$p.value,
         chi2.poverty = summary(education_by_poverty$table)$p.value,
         chi2.luxury = summary(education_by_luxury$table)$p.value,
         chi2.status = summary(education_by_status$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Poverty,
         chi2.poverty,
         Luxury,
         chi2.luxury,
         Status,
         chi2.status)

## Income

income_results <- cbind(income_by_freedom$crosstab, 
                     income_by_enjoyment$crosstab, 
                     income_by_happiness$crosstab,
                     income_by_poverty$crosstab,
                     income_by_luxury$crosstab,
                     income_by_status$crosstab)

# Drop the row totals
income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")

# Convert to dataframe and make the rownames a variable
income_results <- income_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
income_results <- income_results %>%
  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
         chi2.happiness = summary(income_by_happiness$table)$p.value,
         chi2.poverty = summary(income_by_poverty$table)$p.value,
         chi2.luxury = summary(income_by_luxury$table)$p.value,
         chi2.status = summary(income_by_status$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Poverty,
         chi2.poverty,
         Luxury,
         chi2.luxury,
         Status,
         chi2.status)

## Mode USED

mode_results <- cbind(mode_by_freedom$crosstab, 
                     mode_by_enjoyment$crosstab, 
                     mode_by_happiness$crosstab,
                     mode_by_poverty$crosstab,
                     mode_by_luxury$crosstab,
                     mode_by_status$crosstab)

# Drop the row totals
mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")

# Convert to dataframe and make the rownames a variable
mode_results <- mode_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
mode_results <- mode_results %>%
  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
         chi2.happiness = summary(mode_by_happiness$table)$p.value,
         chi2.poverty = summary(mode_by_poverty$table)$p.value,
         chi2.luxury = summary(mode_by_luxury$table)$p.value,
         chi2.status = summary(mode_by_status$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Poverty,
         chi2.poverty,
         Luxury,
         chi2.luxury,
         Status,
         chi2.status)

## Time

time_results <- cbind(time_by_freedom$crosstab, 
                     time_by_enjoyment$crosstab, 
                     time_by_happiness$crosstab,
                     time_by_poverty$crosstab,
                     time_by_luxury$crosstab,
                     time_by_status$crosstab)

# Drop the row totals
time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]

# Change column names
colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")

# Convert to dataframe and make the rownames a variable
time_results <- time_results %>%
  as.data.frame() %>%
  rownames_to_column()

# Add significance of chi2 tests
time_results <- time_results %>%
  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
         chi2.happiness = summary(time_by_happiness$table)$p.value,
         chi2.poverty = summary(time_by_poverty$table)$p.value,
         chi2.luxury = summary(time_by_luxury$table)$p.value,
         chi2.status = summary(time_by_status$table)$p.value) %>%
  dplyr::select(rowname, 
         Freedom, 
         chi2.freedom,
         Enjoyment,
         chi2.enjoyment,
         Happiness,
         chi2.happiness,
         Poverty,
         chi2.poverty,
         Luxury,
         chi2.luxury,
         Status,
         chi2.status)
```

```{r crosstab-all-results-with-instrumental, include=FALSE, eval=FALSE}

# Here we bind all the results into a single dataframe for printing

xtab_results <- rbind(age_results,
                      education_results,
                      income_results,
                      mode_results,
                      time_results) %>%
  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
         chi2.safety = ifelse(chi2.safety >= 0.001, paste0(round(chi2.safety, 4)), "$<0.001$"),
         chi2.time = ifelse(chi2.time >= 0.001, paste0(round(chi2.time, 4)), "$<0.001$"),
         chi2.efficiency = ifelse(chi2.efficiency >= 0.001, paste0(round(chi2.efficiency, 4)), "$<0.001$"))

xtab_results[10:13, 3] <- "$< 0.001$"
```

```{r crosstab-all-results-without-instrumental, echo=FALSE}

# Here we bind all the results into a single dataframe for printing

xtab_results <- rbind(age_results,
                      education_results,
                      income_results,
                      mode_results,
                      time_results) %>%
  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
         chi2.poverty = ifelse(chi2.poverty >= 0.001, paste0(round(chi2.poverty, 4)), "$<0.001$"),
         chi2.luxury = ifelse(chi2.luxury >= 0.001, paste0(round(chi2.luxury, 4)), "$<0.001$"),
         chi2.status = ifelse(chi2.status >= 0.001, paste0(round(chi2.status, 4)), "$<0.001$"))

xtab_results[10:13, 3] <- "$< 0.001$"
```

## Who experiences dissonance?

The first step of the analysis seeks to understand whether there are statistical associations between the variables of interest. The analysis considers the cases where there is a lack of correspondence between the primary mode choice and the 6 SWB/instrumental factors previously described  – or in other words, where there is modal dissonance.

Table 1 shows the results of the analysis of correspondence and the dissonances between the primary mode of travel on the one hand, and SWB and instrumental factors on the other. As seen in the table, there are five categories that we use for the analysis. Three of these categories are socio-economic and demographic, namely age, level of education, income. The other two categories are transportation related, namely primary mode of travel and journey time. Correspondence is tested in every case by means of the $\chi^2$ statistic. It is interesting to note that the only category for which all affective/instrumental factors are significant at better than 5% level of confidence is mode of travel.

With respect to age, we observe that levels of dissonance tend to be high in general, and the results indicate that when it comes to affective factors, dissonance levels tend to be significantly higher for younger travellers, in particular Enjoyment. In terms of instrumental factors, dissonance also tends to significantly decline with age when considering Security. On the other hand, the levels of dissonance in terms of Time Savings and Efficiency, while high, do not show significant differences by age group. Overall, the findings suggest that dissonance tends to decline with age.

The results indicate that the category of Education is less useful to discriminate between different levels of dissonance. Two affective factors are significant at 10% or better (Freedom and Happiness) and show that dissonance tends to decline at higher levels of education. One instrumental factor is significant at 10% or better (Time Savings) and we see there that the level of dissonance tends to grow with higher levels of education. Another instrumental factor (Security) is significant at 5% or better and shows that dissonance in this factor declines with higher education. The picture that emerges is of highly educated people who are relatively less dissatisfied with their primary mode of transportation when it comes to Freedom, Happiness, and Security, but more dissatisfied with their Time Savings than people who are less highly educated.

In general, dissonance tends to be higher for lower income individuals. Table 1 shows that the low-income segment has a significantly higher percentage of cases of dissonance for two affective factors. In the case of Freedom, for example, the lack of correspondence for low-income is 83.9% compared to 60% for the high-income segment. The levels of dissonance are higher for Enjoyment and follow the same decreasing trend for higher levels of income. Dissonance is marginally lower for instrumental factors, and significant for Security and Time Savings.

As noted above, there are significant differences in dissonance by primary mode of travel, both for affective and instrumental factors. For affective factors, the highest levels of dissonance tend to be for users of public transportation, and the lowest for car users and active travellers. For instance, feelings of Freedom, Enjoyment, and Happiness are more frequently expressed by users of car and active travellers than users of public transportation. Indeed, people who travel by Metro or Bus almost never associate any of these positive affective attributes to these modes (dissonance is consistently greater than 90%). In contrast, active travellers have some of the lowest levels of dissonance in all three affective factors, in particular Freedom and Happiness. This analysis is in line with previous research regarding car, active travel, and public transportation (e.g., Steg et al., 2001; Páez and Whalen, 2010; Whalen et al., 2013), which tend to agree on the negative associations in the perception of affective factors when the primary mode is Metro or bus.

Figure 4 shows the percentage of dissonance by primary transport mode, for both affective and instrumental factors. For instance, the graph at the top shows that the highest percentages of dissonances come from users of Metro and bus , compared to other modes as the car or active transport. This is consistent with previous studies that have separately demonstrated that public transport users tend to assess more negatively subjective factors (explored e.g. in Stradling et al., 1999; Gatersleben and Uzzell, 2007). For example, although car users have higher dissonance values than active transport, comparatively this segment has much lower percentages of dissonances than public transport, idea also supported by research that has shown that car users tend to attribute importance to symbolic aspects that positively contribute to their perception on driving (Steg et al., 2001; Mokhtarian and Salomon, 2001).

Freedom and happiness tend to have a lower percentage of dissonances in the case of active transport, which means that cyclists and individuals who mainly walk for their commutes, tend to associate positive subjective values while using these modes. This is also consistent with other studies that have shown positive affective associations with the use of cycling and walking (Anable and Gatersleben, 2005; Gatersleben and Uzzell, 2007). The question at the survey has not specify the dimensions of freedom, thus has open the door for different interpretations as the freedom to choose certain mode or route, freedom while using the mode, or the freedom to access to certain places while travelling.
Journey time: As shown in Figure 3, the analysis carried out by journey time also reveals coincidences with previous research in this area, since for shorter trips (up to 20 minutes) the analysis shows less dissonance between the primary mode and positive subjective associations mainly for affective factors. On the contrary, as journey time increases, higher is the dissonance. Strangely, the feelings of Security and Efficiency have not been statistically representative for the Journey Time analysis.

In terms of instrumental factors, interestingly Figure 4 shows that bus users have the lowest percentage of dissonance regarding time savings (29%). However, considering the other instrumental factors, bus users have a high percentage of dissonance for security and efficiency. In the case of security, this means that most bus users (71%) have considered the bus as a mode that they associate to time-savings, although it is the mode that has more dissonant evaluations in all other SWB factors. This also seems difficult to explain considering the negative evaluation that the Transantiago system has consistently had. Some data provided by the Survey of Satisfaction with Transantiago Operators (DTPM, 2017) is about users' perception of journey time from origin to destination. In this question, and after 10 years of implementation of the system, users diagnose an average journey of 47 minutes, a value that tends to increase with respect to the data delivered by the same survey 5 years before (43.5 minutes on average). Worryingly, long trips of more than 30 minutes have had inconsistent variability over the years, reaching an average of more than 37 minutes in 2016. Short trips, however, remain roughly equal to previous years, and do not show significant changes in the average of 6-7 minutes per trip . This survey has the peculiarity  of being developed by the Metropolitan Public Transport Board (DTPM), whose mission is to articulate the functions of the different modes of public transport with a specific interest in buses Transantiago and Metro de Santiago.

Another big gap on these instrumental factors relates to the perception of security that is especially significant for car users. This means that a 75% of car users have chosen as primary mode the same one as they relate to the feeling of security, which is completely opposite to other transport modes, specially bus users. Bus users have the highest dissonance (98%), which means that practically all this group of users have chosen another mode for referring to the feelings of security. The recently referred DTPM survey does not have any particular question that addresses the issue of safety – mostly related in this context as security.

```{r table-cross-tabulation-results-with-instrumental, echo = FALSE, eval=FALSE}
kable(xtab_results,
      "latex",
      digits = 2,
      booktabs = TRUE,
      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
      escape = FALSE,
      align = c("l", rep("c", 12)),
      col.names = c("Variable", 
                    "Freedom", "$\\chi^2$ p-val", 
                    "Enjoyment", "$\\chi^2$ p-val",
                    "Happiness", "$\\chi^2$ p-val",
                    "Safety", "$\\chi^2$ p-val",
                    "Time", "$\\chi^2$ p-val",
                    "Efficiency", "$\\chi^2$ p-val")) %>%
  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
  pack_rows("Age", 1, 3) %>%
  pack_rows("Education", 4, 6) %>%
  pack_rows("Income", 7, 9) %>%
  pack_rows("Mode", 10, 13) %>%
  pack_rows("Journey Time", 14, 17)  %>%
  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
  landscape()
```

```{r table-cross-tabulation-results-without-instrumental, echo = FALSE}
kable(xtab_results,
      "latex",
      digits = 2,
      booktabs = TRUE,
      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
      escape = FALSE,
      align = c("l", rep("c", 12)),
      col.names = c("Variable", 
                    "Freedom", "$\\chi^2$ p-val", 
                    "Enjoyment", "$\\chi^2$ p-val",
                    "Happiness", "$\\chi^2$ p-val",
                    "Poverty", "$\\chi^2$ p-val",
                    "Luxury", "$\\chi^2$ p-val",
                    "Status", "$\\chi^2$ p-val")) %>%
  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
  pack_rows("Age", 1, 3) %>%
  pack_rows("Education", 4, 6) %>%
  pack_rows("Income", 7, 9) %>%
  pack_rows("Mode", 10, 13) %>%
  pack_rows("Journey Time", 14, 17)  %>%
  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
  landscape()
```

Figure 5 shows the points of origin of the survey for the case of public transport users. Metro users as primary mode are shown, bus users are shown in cyan. The size of the points represents the number of dissonances. The higher the point, the greater the number of SWB factors that do not coincide with the primary transport mode. The image shows that the intensity or size of the circles is homogeneously distributed in the territory, even though the blue circles (metro) tend to show slightly less dissonance. The visualisation of this map is more dramatic when it is compared to the following Figure 6.

Figure 6 shows the points of origin for the case of private transport (cars) and active transport (walking and cycling). Again, the size of the circles represents intensity levels of dissonance. The number of dissonances is lower than in the case of Figure 5, which indicates that users of private and active transport tend to use a mode of transport that they relate to one of the positive factors derived from subjective wellbeing. In this sense, it could be said that this type of user tends to be more advantaged than the public transport user, in a dimension not only utilitarian but also emotional and attitudinal.

## Which modes do travelers associate with affective and instrumental values?

Here we can visualize the modes that travellers associate with different affective and instrumental values. The tool we use for this is a mosaic plot. See the mosaic plots in Figure \ref{fig:mosaic-plots-by-attribute}.

```{r figure-mosaic-plots-by-attribute-with-instrumental, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}

ggplot(data = Modes_by_Attribute) + 
  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
              divider = mosaic("vertical")) + 
  xlab("Mode selected for the value of {Freedom, Enjoyment, Happiness, Safety, Time, Efficiency}") +
  ylab("Main mode of transportation") +
  scale_fill_viridis_d(direction = -1) +
  facet_wrap(~ ATTRIBUTE) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r figure-mosaic-plots-by-attribute-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}

ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"))) + 
  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
              divider = mosaic("vertical")) + 
  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Poverty, Luxury, Status}") +
  ylab("Primary mode of travel") +
  scale_fill_viridis_d(direction = -1) +
  facet_wrap(~ ATTRIBUTE) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r figure-mosaic-plots-by-attribute-and-age-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}

# Select only values that were significant in the tests of independence

ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS"))) + 
  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
              divider = mosaic("vertical")) + 
  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Luxury, Status}") +
  ylab("Primary mode of travel") +
  scale_fill_viridis_d(direction = -1) +
  facet_grid(AGE ~ ATTRIBUTE) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r figure-mosaic-plots-by-attribute-and-education-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}

# Select only values that were significant in the tests of independence

ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("LUXURY", "STATUS"))) + 
  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
              divider = mosaic("vertical")) + 
  xlab("Mode associated with {Luxury, Status}") +
  ylab("Primary mode of travel") +
  scale_fill_viridis_d(direction = -1) +
  facet_grid(EDUCATION ~ ATTRIBUTE) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r figure-mosaic-plots-by-attribute-and-income-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}

# Select only values that were significant in the tests of independence

ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("POVERTY", "LUXURY", "STATUS"))) + 
  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
              divider = mosaic("vertical")) + 
  xlab("Mode associated with {Poverty, Luxury, Status}") +
  ylab("Primary mode of travel") +
  scale_fill_viridis_d(direction = -1) +
  facet_grid(INCOME ~ ATTRIBUTE) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r figure-mosaic-plots-by-attribute-and-time-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by travel time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}

# Select only affective values that were significant in the tests of independence

ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS")) %>% drop_na(TRAVEL_TIME)) + 
  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
              divider = mosaic("vertical")) + 
  xlab("Mode associated with {Freedom, Happiness, Luxury, Status}") +
  ylab("Primary mode of travel") +
  scale_fill_viridis_d(direction = -1) +
  facet_grid(TRAVEL_TIME ~ ATTRIBUTE) +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))
```

Conclusions
==========

Words go here.

References {#references .unnumbered}
==========

### 2019-10-19 Dissonance_Santiago_v1.tex
Commit with first draft of paper

--- 2019-10-19 Dissonance_Santiago_v1.Rmd
@@
----
-title: Do Drivers Dream of Walking? An Investigation of Dissonance in the Primary Mode of Travel from the Perspective of Subjective Wellbeing
-author:
-  - name: Author 1
-    email: a1@university.com
-    affiliation: Some University
-    footnote: Corresponding Author
-  - name: Author 2
-    email: a2@school.com
-    affiliation: Some School
-address:
-  - code: Some University
-    address: Department, Street, City, State, Zip
-  - code: Some School
-    address: Department, Street, City, State, Zip
-abstract: |
-  Transportation in most of the world has been dominated for decades by a fascination with the automobile.
-Increasingly, however, it is recognized that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain users of public transport and active travel.
-A challenge with the way transportation policy is developed is that it tends to focus on cost-benefit and utilitarian considerations, which may miss other potential benefits of transportation.
-For this reason, subjective wellbeing (SWB) has been proposed as a way to enhance our understanding of the preferences and choices of travellers, as well as a way to evaluate the benefits of transportation beyond utilitarian considerations.
-The objective of this paper is to analyze the modes that people commonly use, and to what extent they are aligned (or not) with a variety of affective and utilitarian values.
-In other words, we are interested in the potential for dissonance with respect to the primary mode of travel, from the perspective of affective and utilitarian values.
-The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
-Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associated to affective values (freedom, enjoyment, and happiness) and to utilitarian values (safety, time waste, and efficiency).
-The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with affective values.
-
-  To properly assess transportation policy This poses a number of challenges Broadening the commonly used transport project assessment will be relevant for achieving this goal.
-While satisfaction with travel has been mainly used in the context of daily trips and mainly under cost-benefit and utilitarian considerations, subjective wellbeing (SWB) over time has risen as an alternative for understanding the preferences and choices of transport users.
-The aim of this paper is to analyse the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
-The paper aims to reflect on the possibilities of increasing the SWB with a view to enhance the attractiveness of public transport and active travel.
-The paper investigates the affective and instrumental/utilitarian factors of SWB, according to modal choice.
-It uses an analysis of correspondence that considers the actual primary mode used, versus the mode that each individual associated to both utilitarian and affective SWB factors.
-The results show that there is more persistent modal dissonance between positive emotional and utilitarian associations within the more disadvantaged groups – particularly among users of public transport.
-The study shows that apart from time-savings and efficiency, security has also been cross-sectionally sensitive according to the data analysed.
-Factors such as happiness, enjoyment and freedom require far more attention in transport planning as they are strongly related to the dimensions of subjective and personal wellbeing.
-Targeting these factors will be relevant for attracting new users to public transportation and active travel.
-
-journal: "An Elsevier journal"
-date: "`r Sys.Date()`"
-bibliography: mybibfile.bib
-#linenumbers: true
-#numbersections: true
-csl: elsevier-harvard.csl
-output: rticles::elsevier_article
----
-
-<!-- This paper is an R markdown document that includes self-contained, reproducible analysis. To reproduce the paper the following files are needed:
-
-1. Dissonance_Santiago_v1.Rmd (this R markdown document)
-
-2.
-`Dissonance_Santiago.RData`.
-For reference: this data file was created using R notebook `00.
-Analysis of Dissonance Detailed.Rmd`.
-The initial analysis was done in the same R notebook.
-Neither of these two notebooks are needed for this document.
-
-3.
-For compiling into a pdf in the style of an Elsevier document: elsarticle.cls, elsevier-harvard.csl, elsevier-harvard-without-titles.csl, elsevier-vancouver.csl, elsevier-without-titles.cls, elsevier-with-titles.csl, elsevier-with-titles-alphabetical.csl, mybibfile.bib
--->
-
-```{r load-packages, include=FALSE}
-
-# Load packages used in this document
-
-library(rticles)
-library(readxl)
-library(tidyverse)
-library(rgdal)
-library(sf)
-library(ggmosaic)
-library(ggthemes)
-library(kableExtra)
-```
-
-```{r load-data, include=FALSE}
-
-# To run this notebook, the file `Dissonance_Santiago.RData` is needed. This file contains the following object:
-# 
-# master: a dataframe with information collected from 451 respondents. The variables in the dataframe are:
-# 
-# - NUMERO: Respondent ID
-# - USED: Main mode of transportation used by the respondent
-# - FREEDOM: Mode(s) that the respondent associates with feelings of freedom
-# - ENJOYMENT: Mode(s) that the respondent associates with feelings of enjoyment
-# - HAPPINESS: Mode(s) that the respondent associates with feelings of happiness
-# - POVERTY: Mode(s) that the respondent associates with feelings of poverty
-# - LUXURY: Mode(s) that the respondent associates with feelings of luxury
-# - STATUS: Mode(s) that the respondent associates with feelings of status
-# - SAFETY: Mode(s) that the respondent associates with feelings of safety
-# - TIME: Mode(s) that the respondent associates with feelings of WASTED TIME
-# - EFFICIENCY: Mode(s) that the respondent associates with feelings of efficiency
-# - AGE: Age of the respondent
-# - EDUCATION: Level of education of the respondent
-# - INCOME: Level of income of respondent
-# - TRAVEL_TIME: Trip duration of regular commuting trip 
-# - WEIGHT_*: A weight for the responses by ATTRIBUTE.
-Some respondents selected more than one mode that they associated with feelings of {FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, and EFFICIENCY}.
-To avoid giving greater weight to respondents who indicated several modes of transportation, a weight was calculated that is the inverse of the number of modes indicated.
-These weights can be used to weight the frequencies prior to any analysis.
-# 
-# The modes of transportation (USED, FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, EFFICIENCY) are coded as: 
-# "A": Auto
-# "B": Taxi
-# "C": Colectivo
-# "D": Moto
-# "E": Metro
-# "F": Bus
-# "G": Bicycle
-# "H": Walk
-#
-# AGE is coded as:
-#
-# "A": Less18
-# "B": 18to24
-# "C": 25to34
-# "D": 35to54
-# "E": 55to64
-# "F": 65more
-# 
-# EDUCATION is coded as:
-# 
-# "A": ELEMENTARY
-# "B": SECUNDARY
-# "C": PROFESS_TECH
-# "D": COLLEGE
-# "E": POSTGRAD
-#
-# INCOME is coded as (in pesos?):
-# 
-# "A": Less423
-# "B": 423to639
-# "C": 639to977
-# "D": 977to1550
-# "E": 1550to2380
-# "F": 2380more
-# 
-# TRAVEL_TIME is coded as:
-#
-# "A": 0-20 min
-# "B": 20-40 min
-# "C": 40-60 min
-# "D": 1h and more
-
-# Read the RData file:
-
-load("Dissonance_Santiago.RData")
-```
-
-```{r data-preparation, include=FALSE}
-
-# The master dataframe is processed for analysis. We plan to conduct two distinct types of analysis:
-#
-# 1.
-Analysis of dissonace using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.).
-In this case, dissonance is defined as follows:
-#
-# >> If the mode used is identical to the mode that the respondent associates with ATTRIBUTE (i.e.
-FREEDOM et al.), we consider that there is no dissonance; otherwise, we consider that there is dissonance.
-For example, if the respondent's main mode of transportation is Auto, and the respondent associates Auto with feelings of FREEDOM, then there is no dissonance.
-On the other hand, if the respondent's main mode of transportation is Auto, but associates Walking with feelings of FREEDOM, there is dissonance.
-# 
-# Given this, we will calculate how frequently there is dissonance at different levels of AGE, EDUCATION, INCOME, MODE, TRAVEL_TIME. Tests of independence can be implemented.
-#
-# 2.
-Analysis of dissonance using the mode USED and the mode respondents associated with ATTRIBUTE, then stratified by characteristics of respondents (i.e., AGE et al.) in this case, we see how frequently each mode was associated with ATTRIBUTE, given the main mode of transportation of the respondents.
-#
-# Here the dataframes are prepared to support these two types of analysis
-
-#################################################################################
-# Prepare a dataframe for the analysis of dissonance by attribute (Analysis 1.) #
-#################################################################################
-
-# First, select the variables needed from the master table, and code dissonance as 1 (no dissonance) or two (dissonance):
-
-Overall_dissonance <- master %>%
-  transmute(USED, 
-            FREEDOM_DISSONANCE = ifelse(USED == FREEDOM, 1, 2),
-            ENJOYMENT_DISSONANCE = ifelse(USED == ENJOYMENT, 1, 2),
-            HAPPINESS_DISSONANCE = ifelse(USED == HAPPINESS, 1, 2),
-            POVERTY_DISSONANCE = ifelse(USED == POVERTY, 1, 2),
-            LUXURY_DISSONANCE = ifelse(USED == LUXURY, 1, 2),
-            STATUS_DISSONANCE = ifelse(USED == STATUS, 1, 2),
-            SAFETY_DISSONANCE = ifelse(USED == SAFETY, 1, 2),
-            TIME_DISSONANCE = ifelse(USED == TIME, 1, 2),
-            EFFICIENCY_DISSONANCE = ifelse(USED == EFFICIENCY, 1, 2),
-            AGE,
-            EDUCATION,
-            INCOME,
-            TRAVEL_TIME)
-
-# Recode variables and convert to factors:
-
-Overall_dissonance <- Overall_dissonance %>%
-  mutate(USED = case_when(USED == "A" ~ "Auto",
-                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
-                                  USED == "E" | USED == "F" ~ "Public",
-                                  USED == "G" | USED == "H" ~ "Active"),
-         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
-                         AGE == "D" ~ "35 - 54",
-                         AGE == "E" | AGE == "F" ~ "> 54"),
-         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
-                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
-                               EDUCATION == "E" ~ "Graduate"),
-         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
-                            INCOME == "C" | INCOME == "D" ~ "Middle",
-                            INCOME == "E" | INCOME == "F" ~ "High"),
-         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
-                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
-                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
-                                 TRAVEL_TIME == "D" ~ "> 60 min")) %>%
-  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
-         FREEDOM_DISSONANCE = factor(FREEDOM_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         ENJOYMENT_DISSONANCE = factor(ENJOYMENT_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         HAPPINESS_DISSONANCE = factor(HAPPINESS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         POVERTY_DISSONANCE = factor(POVERTY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         LUXURY_DISSONANCE = factor(LUXURY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         STATUS_DISSONANCE = factor(STATUS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         SAFETY_DISSONANCE = factor(SAFETY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         TIME_DISSONANCE = factor(TIME_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         EFFICIENCY_DISSONANCE = factor(EFFICIENCY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
-         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
-         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
-         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))
-
-#############################################################################
-# Prepare a dataframe for the analysis of dissonance by modes (Analysis 2.) #
-#############################################################################
-
-# First, split the responses regarding the modes associated with each attribute, so that we can record each mode selected individually:
-
-Modes_by_Attribute <- master %>% 
-    mutate(FREEDOM = strsplit(as.character(FREEDOM), ""),
-           ENJOYMENT = strsplit(as.character(ENJOYMENT), ""),
-           HAPPINESS = strsplit(as.character(HAPPINESS), ""),
-           POVERTY = strsplit(as.character(POVERTY), ""),
-           LUXURY = strsplit(as.character(LUXURY), ""),
-           STATUS = strsplit(as.character(STATUS), ""),
-           SAFETY = strsplit(as.character(SAFETY), ""),
-           TIME = strsplit(as.character(TIME), ""),
-           EFFICIENCY = strsplit(as.character(EFFICIENCY), ""))
-
-# Here, we convert each of the responses into an individual row and stack the resulting dataframes, after adding the name of the attribute for identification:
-
-Modes_by_Attribute <- rbind(data.frame(Modes_by_Attribute %>% 
-                                         select(-c(ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = FREEDOM, WEIGHT = WEIGHT_FREEDOM) %>%
-                                         unnest(IDEAL),
-                                       ATTRIBUTE = "FREEDOM"),
-                            data.frame(Modes_by_Attribute %>%
-                                         select(-c(FREEDOM, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = ENJOYMENT, WEIGHT = WEIGHT_ENJOYMENT) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "ENJOYMENT"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM,
-                                                   WEIGHT_ENJOYMENT,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = HAPPINESS, WEIGHT = WEIGHT_HAPPINESS) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "HAPPINESS"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = POVERTY, WEIGHT = WEIGHT_POVERTY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "POVERTY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   #LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   #WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = LUXURY, WEIGHT = WEIGHT_LUXURY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "LUXURY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   #STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   #WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = STATUS, WEIGHT = WEIGHT_STATUS) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "STATUS"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = SAFETY, WEIGHT = WEIGHT_SAFETY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "SAFETY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = TIME, WEIGHT = WEIGHT_TIME) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "TIME"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME)) %>%
-                                         rename(IDEAL = EFFICIENCY, WEIGHT = WEIGHT_EFFICIENCY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "EFFICIENCY"))
-
-# There are some missing values. Drop all NAs:
-
-Modes_by_Attribute <- drop_na(Modes_by_Attribute)
-
-# We now recode the variables:
-
-Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = case_when(USED == "A" ~ "Auto",
-                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
-                                  USED == "E" | USED == "F" ~ "Public",
-                                  USED == "G" | USED == "H" ~ "Active"),
-         IDEAL = case_when(IDEAL == "A" ~ "Auto",
-                                  IDEAL == "B" | IDEAL == "C" | IDEAL == "D" ~ "Other",
-                                  IDEAL == "E" | IDEAL == "F" ~ "Public",
-                                  IDEAL == "G" | IDEAL == "H" ~ "Active"),
-         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
-                         AGE == "D" ~ "35 - 54",
-                         AGE == "E" | AGE == "F" ~ "> 54"),
-         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
-                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
-                               EDUCATION == "E" ~ "Graduate"),
-         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
-                            INCOME == "C" | INCOME == "D" ~ "Middle",
-                            INCOME == "E" | INCOME == "F" ~ "High"),
-         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
-                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
-                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
-                                 TRAVEL_TIME == "D" ~ "> 60 min"))
-
-# After recoding the , there will be some duplicate entries, because a person may have attributed, say, feelings of freedom to walking and cycling, so in the table this will appear as two instances of "Active".
-This is ok, because each is weighted appropriately.
-
-# Convert to factors:
-
-Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
-         IDEAL = factor(IDEAL, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
-         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
-         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
-         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
-         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))
-```
-
-```{r cross-tabs-function, include=FALSE}
-
-## Define functions for crosstabs; these functions enhance the base crosstabs functions and make it easier to report cross tabulations in different ways.
-
-crosstab <- function (..., dec.places = NULL,
-                           type = NULL,
-                           style = "wide",
-                           row.vars = NULL,
-                           col.vars = NULL,
-                           percentages = TRUE, 
-                           addmargins = TRUE,
-                           subtotals=TRUE)
-
-###################################################################################
-#                                                                                 #
-# Function created by Dr Paul Williamson, Dept. of Geography and Planning,        #
-# School of Environmental Sciences, University of Liverpool, UK.                  #
-#                                                                                 #
-# Adapted from the function ctab() in the catspec packge.                         #
-#                                                                                 #
-# Version: 12th July 2013                                                         #
-#                                                                                 #
-# Output best viewed using the companion function print.crosstab()                #
-#                                                                                 #
-###################################################################################
-
-  #Declare function used to convert frequency counts into relevant type of proportion or percentage
-  {mk.pcnt.tbl <- function(tbl, type) {
-        a <- length(row.vars)
-        b <- length(col.vars)
-        mrgn <- switch(type, column.pct = c(row.vars[-a], col.vars), 
-                            row.pct = c(row.vars, col.vars[-b]),
-                            joint.pct = c(row.vars[-a], col.vars[-b]),
-                            total.pct = NULL)
-        tbl <- prop.table(tbl, mrgn)
-        if (percentages) {
-            tbl <- tbl * 100
-        }
-        tbl
-    }
-
-    #Find no. of vars (all; row; col) for use in subsequent code
-    n.row.vars <- length(row.vars)
-    n.col.vars <- length(col.vars)
-    n.vars <- n.row.vars + n.col.vars
-
-    #Check to make sure all user-supplied arguments have valid values
-    stopifnot(as.integer(dec.places) == dec.places, dec.places > -1)
-    #type: see next section of code
-    stopifnot(is.character(style))    
-    stopifnot(is.logical(percentages))
-    stopifnot(is.logical(addmargins))
-    stopifnot(is.logical(subtotals))
-    stopifnot(n.vars>=1)
-
-    #Convert supplied table type(s) into full text string (e.g. "f" becomes "frequency")
-    #If invalid type supplied, failed match gives user automatic error message
-    types <- NULL
-    choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
-    for (tp in type) types <- c(types, match.arg(tp, choices))
-    type <- types
-
-    #If no type supplied, default to 'frequency + total' for univariate tables and to
-    #'frequency' for multi-dimenstional tables
-
-    #For univariate table....
-    if (n.vars == 1) {
-      if (is.null(type)) {
-        # default = freq count + total.pct  
-        type <- c("frequency", "total.pct")
-        #row.vars <- 1
-      } else {
-        #and any requests for row / col / joint.pct must be changed into requests for 'total.pct'
-        type <- ifelse(type == "frequency", "frequency", "total.pct")
-      }
-    #For multivariate tables...
-    } else if (is.null(type)) {
-      # default = frequency count  
-      type <- "frequency"
-    }
-
-    #Check for integrity of requested analysis and adjust values of function arguments as required
-
-    if ((addmargins==FALSE) & (subtotals==FALSE)) {
-      warning("WARNING: Request to suppress subtotals (subtotals=FALSE) ignored because no margins requested (addmargins=FALSE)")
-      subtotals <- TRUE
-    }
-
-    if ((n.vars>1) & (length(type)>1) & (addmargins==TRUE)) {
-      warning("WARNING: Only row totals added when more than one table type requested")
-      #Code lower down selecting type of margin implements this...
-    }
-
-    if ((length(type)>1) & (subtotals==FALSE)) { 
-      warning("WARNING: Can only request supply one table type if requesting suppression of subtotals; suppression of subtotals not executed")
-      subtotals <- TRUE
-    }
-
-    if ((length(type)==1) & (subtotals==FALSE)) {
-      choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
-      tp <- match.arg(type, choices)
-      if (tp %in% c("row.pct","column.pct","joint.pct")) {
-          warning("WARNING: subtotals can only be suppressed for tables of type 'frequency' or 'total.pct'")
-          subtotals<- TRUE
-         }
-    }
-
-    if ((n.vars > 2) & (n.col.vars>1) & (subtotals==FALSE)) 
-      warning("WARNING: suppression of subtotals assumes only 1 col var; table flattened accordingly")
-
-    if ( (subtotals==FALSE) & (n.vars>2) )  {
-    #If subtotals not required AND total table vars > 2
-    #Reassign all but last col.var as row vars
-    #[because, for simplicity, crosstabs assumes removal of subtotals uses tables with only ONE col var]
-    #N.B. Subtotals only present in tables with > 2 cross-classified vars...
-      if (length(col.vars)>1) {
-        row.vars <- c(row.vars,col.vars[-length(col.vars)])
-        col.vars <- col.vars[length(col.vars)]
-        n.row.vars <- length(row.vars)
-        n.col.vars <- 1
-      }
-    }
-
-    #If dec.places not set by user, set to 2 unlesss only one table of type frequency requested,
-    #in which case set to 0.  [Leaves user with possibility of having frequency tables with > 0 dp]
-    if (is.null(dec.places)) {
-      if ((length(type)==1) & (type[1]=="frequency")) {
-        dec.places <- 0
-      } else {
-        dec.places <-2
-      }
-    }
-
-    #Take the original input data, whatever form originally supplied in,
-    #convert into table format using requested row and col vars, and save as 'tbl'
-
-    args <- list(...)
-
-    if (length(args) > 1) {
-        if (!all(sapply(args, is.factor))) 
-            stop("If more than one argument is passed then all must be factors")
-        tbl <- table(...)
-    }
-    else {
-        if (is.factor(...)) {
-            tbl <- table(...)
-        }
-        else if (is.table(...)) {
-            tbl <- eval(...)
-        }
-        else if (is.data.frame(...)) {
-            #tbl <- table(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-              tbl <- table(...)
-            }
-            else {
-              var.names <- c(row.vars,col.vars)
-              A <- (...)
-              tbl <- table(A[var.names])
-              if(length(var.names==1)) names(dimnames(tbl)) <- var.names
-              #[table() only autocompletes dimnames for multivariate crosstabs of dataframes]
-            }
-        }
-        else if (class(...) == "ftable") {
-            tbl <- eval(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-                row.vars <- names(attr(tbl, "row.vars"))
-                col.vars <- names(attr(tbl, "col.vars"))
-            }
-            tbl <- as.table(tbl)
-        }
-        else if (class(...) == "ctab") {
-            tbl <- eval(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-                row.vars <- tbl$row.vars
-                col.vars <- tbl$col.vars
-            }
-            for (opt in c("dec.places", "type", "style", "percentages", 
-                "addmargins", "subtotals")) if (is.null(get(opt))) 
-                assign(opt, eval(parse(text = paste("tbl$", opt, 
-                  sep = ""))))
-            tbl <- tbl$table
-        }
-        else {
-            stop("first argument must be either factors or a table object")
-        }
-    }
-
-    #Convert supplied table style into full text string (e.g. "l" becomes "long")
-    style <- match.arg(style, c("long", "wide"))
-
-    #Extract row and col names to be used in creating 'tbl' from supplied input data
-    nms <- names(dimnames(tbl))
-    z <- length(nms)
-    if (!is.null(row.vars) && !is.numeric(row.vars)) {
-        row.vars <- order(match(nms, row.vars), na.last = NA)
-    }
-    if (!is.null(col.vars) && !is.numeric(col.vars)) {
-        col.vars <- order(match(nms, col.vars), na.last = NA)
-    }
-    if (!is.null(row.vars) && is.null(col.vars)) {
-        col.vars <- (1:z)[-row.vars]
-    }
-    if (!is.null(col.vars) && is.null(row.vars)) {
-        row.vars <- (1:z)[-col.vars]
-    }
-    if (is.null(row.vars) && is.null(col.vars)) {
-        col.vars <- z
-        row.vars <- (1:z)[-col.vars]
-    }
-
-    #Take the original input data, converted into table format using supplied row and col vars (tbl)
-    #and create a second version (crosstab) which stores results as percentages if a percentage table type is requested.
-    if (type[1] == "frequency") 
-      crosstab <- tbl
-    else 
-      crosstab <- mk.pcnt.tbl(tbl, type[1])
-
-    #If multiple table types requested, create and add these to 
-    if (length(type) > 1) {
-      tbldat <- as.data.frame.table(crosstab)
-      z <- length(names(tbldat)) + 1
-      tbldat[z] <- 1
-      pcntlab <- type
-      pcntlab[match("frequency", type)] <- "Count"
-      pcntlab[match("row.pct", type)] <- "Row %"
-      pcntlab[match("column.pct", type)] <- "Column %"
-      pcntlab[match("joint.pct", type)] <- "Joint %"
-      pcntlab[match("total.pct", type)] <- "Total %"
-      for (i in 2:length(type)) {
-          if (type[i] == "frequency") 
-              crosstab <- tbl
-          else crosstab <- mk.pcnt.tbl(tbl, type[i])
-          crosstab <- as.data.frame.table(crosstab)
-          crosstab[z] <- i
-          tbldat <- rbind(tbldat, crosstab)
-      }
-      tbldat[[z]] <- as.factor(tbldat[[z]])
-      levels(tbldat[[z]]) <- pcntlab
-      crosstab <- xtabs(Freq ~ ., data = tbldat)
-      names(dimnames(crosstab))[z - 1] <- ""
-    }
-
-    #Add margins if required, adding only those margins appropriate to user request
-    if (addmargins==TRUE) {
-
-      vars <- c(row.vars,col.vars)
-
-      if (length(type)==1) {
-      if (type=="row.pct") 
-        { crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
-          tbl <- addmargins(tbl,margin=c(vars[n.vars]))
-        }
-      else 
-        { if (type=="column.pct") 
-            { crosstab <- addmargins(crosstab,margin=c(vars[n.row.vars]))
-              tbl <- addmargins(tbl,margin=c(vars[n.row.vars]))
-            }
-          else 
-            { if (type=="joint.pct") 
-              { crosstab <- addmargins(crosstab,margin=c(vars[(n.row.vars)],vars[n.vars])) 
-                tbl <- addmargins(tbl,margin=c(vars[(n.row.vars)],vars[n.vars])) 
-              }
-              else #must be total.pct OR frequency
-                { crosstab <- addmargins(crosstab)
-                  tbl <- addmargins(tbl)
-                }
-            }
-  	     } 
-      }
-
-      #If more than one table type requested, only adding row totals makes any sense...
-      if (length(type)>1) {
-        crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
-        tbl <- addmargins(tbl,margin=c(vars[n.vars]))
-      }
-
-    }
-
-    #If subtotals not required, and total vars > 2, create dataframe version of table, with relevent
-    #subtotal rows / cols dropped [Subtotals only present in tables with > 2 cross-classified vars]
-    t1 <- NULL
-    if ( (subtotals==FALSE) & (n.vars>2) )  {
-
-    #Create version of crosstab in ftable format
-    t1 <- crosstab 
-    t1 <- ftable(t1,row.vars=row.vars,col.vars=col.vars)
-
-    #Convert to a dataframe
-    t1 <- as.data.frame(format(t1),stringsAsFactors=FALSE)
-
-    #Remove backslashes from category names AND colnames
-    t1 <- apply(t1[,],2, function(x) gsub("\"","",x))
-    #Remove preceding and trailing spaces from category names to enable accurate capture of 'sum' rows/cols
-    #[Use of grep might extrac category labels with 'sum' as part of a longer one or two word string...]
-    t1 <- apply(t1,2,function(x) gsub("[[:space:]]*$","",gsub("^[[:space:]]*","",x)))
-
-    #Reshape dataframe to that variable and category labels display as required
-    #(a) Move col category names down one row; and move col variable name one column to right
-    t1[2,(n.row.vars+1):ncol(t1)] <- t1[1,(n.row.vars+1):ncol(t1)]
-    t1[1,] <- ""
-    t1[1,(n.row.vars+2)] <- t1[2,(n.row.vars+1)]    
-    #(b) Drop the now redundant column separating the row.var labels from the table data + col.var labels
-    t1 <- t1[,-(n.row.vars+1)]
-
-    #In 'lab', assign category labels for each variable to all rows (to allow identification of sub-totals) 
-    lab <- t1[,1:n.row.vars]
-    for (c in 1:n.row.vars) {
-      for (r in 2:nrow(lab)) {
-        if (lab[r,c]=="") lab[r,c] <- lab[r-1,c]  
-      }
-    }
-
-    lab <- (apply(lab[,1:n.row.vars],2,function(x) x=="Sum"))
-    lab <- apply(lab,1,sum)
-    #Filter out rows of dataframe containing subtotals
-
-    t1 <- t1[((lab==0) | (lab==n.row.vars)),]
-
-    #Move the 'Sum' label associated with last row to the first column; in the process
-    #setting the final row labels associated with other row variables to ""
-    t1[nrow(t1),1] <- "Sum"
-    t1[nrow(t1),(2:n.row.vars)] <- ""
-
-    #set row and column names to NULL
-    rownames(t1) <- NULL
-    colnames(t1) <- NULL
-
-    }
-
-    #Create output object 'result' [class: crosstab]
-    result <- NULL
-    #(a) record of argument values used to produce tabular output
-    result$row.vars <- row.vars
-    result$col.vars <- col.vars
-    result$dec.places <- dec.places
-    result$type <- type
-    result$style <- style
-    result$percentages <- percentages
-    result$addmargins <- addmargins
-    result$subtotals <- subtotals
-
-    #(b) tabular output [3 variants]
-    result$table <- tbl  #Stores original cross-tab frequency counts without margins [class: table]
-    result$crosstab <- crosstab #Stores cross-tab in table format using requested style(frequency/pct) and table margins (on/off)
-                                #[class: table]  
-    result$crosstab.nosub <- t1  #crosstab with subtotals suppressed [class: dataframe; or NULL if no subtotals suppressed]  
-    class(result) <- "crosstab"
-
-    #Return 'result' as output of function
-    result
-}
-```
-
-Introduction
-==========================
-
-Transportation planning for decades has focused on providing mobility for the private automobile.
-This is a model of development that was initially introduced in North America as a solution to urbanizations problems, and that was eventually copied elsewhere (Brown et al., 2009; Angotti, 1996) .
-Despite the initial promise of automotive technology, it is now evident that mobility centred on the private automobile has given rise to a litany of maladies that are in urgent need of correction.
-This includes environmental concerns (i.e., climate change; Chapman, 2007) as well as other social (Boschmann and Kwan, 2008), health (Khreis et al., 2016), and equity issues (Bocarejo and Oviedo, 2012).
-As the real impacts of our societal dependence on the private autombobile have become increasingly evident, the transportation agenda has in recent years aimed to shift focus to the reduction of car-use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives than just the private automobile (Miller, 2011) .
-In order to successfully achieve this goal, it is essential not only to provide the services and facilities that support public transportation and active travel, but also to attract new users to these modes of transportation (Ettema et al.
-2011).
-Within this context, it has been argued that sustainable transportation policies require all participants in the transportation system to challenge what Gossling and Cohen (2014) term “transportation taboos”: deep-seated ideas concerning the contribution to emissions by individuals, the inequality of market-based approaches, and the social and psychological functions of transportation.
-With respect to the latter, moving beyond a purely utilitarian focus, it is important to understand how users perceive affective and instrumental elements on their transportation experience, since this can help to incorporate adequate improvements in alternative transportation, including transit and active modes, to make them more attractive to users (Anable and Gatersleben, 2005; Domarchi et al., 2008; Gatersleben and Uzzell, 2007; Steg 2005 ).
-
-A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing (SWB.
-See, inter alia, De Vos et al., 2013 and Chatterjee et al., 2019) .
-SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” (OECD, 2013, p.
-10).
-Accordingly, the aim of this paper is to analyse some of the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
-Previous research suggests that public transport users experience a negative gap in desired and actual travel time, whereas active travellers don’t seem to mind somewhat longer trips than what strictly needed (e.g., Páez and Whalen, 2010).
-In the context of a Latin American country, historically the poor travel experience of public transit users and active travellers reflects the social inequalities of social groups that have no alternative but to move in these types of modes while living far from the work centres and main activities.
-The paper aims to reflect on the possibilities of increasing the SWB while travelling, and how this could increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
-This can help not only to reduce the use of private transport but also decrease the inequality gap between these users.
-
-The paper explores how positive affective and instrumental/utilitarian factors of SWB correspond to the use of the primary mode of transportation.
-It uses an analysis of correspondence that considers the actual primary mode versus the mode that individuals associated to both utilitarian (designed to be useful or practical rather than attractive) and affective (expressing a person's feelings) SWB factors.
-For example, it will be analysed if a person who uses public transport as the primary mode, tends to associate these modes with positive affective factors (as freedom, enjoyment or happiness) or positive utilitarian factors (as security, time-savings or efficiency).
-We hypothesize that there is a more persistent non-correspondence or mismatch within the more disadvantage groups or within the users of public transport.
-
-The paper contributes to the literature in three areas.
-First, it contributes to an emerging literature on the topic in the context of the Global South (Bejarano et al., 2017 ; Shao and Liang, 2019 ; Van et al., 2014 ; Zorrilla et al., 2019);  to the best of our knowledge, the case of Chile has not yet been reported.
-Second, although there is literature on the enjoyment of commute and other emotional factors, from a hedonic and even eudaimonic perspectives, the analysis has yet to be applied more fully in terms of distributional issues – i.e.
-which groups are mostly disadvantaged.
-Finally, the analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’ – implying their preferences, even in situations when their ideal mode is not part of their actual choice set.
-The attitudes of travellers towards transport modes are critical factors to be considered by policy-makers in case they want to promote and increase the use of public transport or active modes (e.g., Bejarano et al., 2019).
-The paper explores these positive and negative associations within the transport options used in Santiago.
-
-Background
-============
-
-The transportation community has for the most part already agreed to the need of looking at mobility and transport issues from the lens of wellbeing, to broaden the commonly used utilitarian perspective to evaluate projects.
-Users’ travel satisfaction (Bergstad, 2001) has been the primary way to direct this challenge towards everyday mobility, resulting on research about satisfaction with different transport modes.
-For example, numerous studies report that car users have a higher level of satisfaction compared to other transport modes (Redmond and Mokhtarian, 2001 ; Bergstad et al.
-2011; Eriksson et al.
-2013; Whalen et al., 2013).
-In a similar way, there are multiple reports that active travel also tends to yield high levels of satisfaction (Smith, 2017; St-Louis et al.
-2014; Paez and Whalen, 2010; Whalen et al., 2013), In contrast, public transport users tend to assess their experience more negatively (De Vos et al.
-2016; Abenoza et al.
-2017; Ettema et al.
-2012; Páez and Whalen, 2010).
-Multi-modal trips also influence satisfaction levels; for instance, when an individual chooses a particular mode of transportation, she will report a higher level of satisfaction with that chosen mode – perhaps as a form of post hoc validation (Susilo and Cats, 2014).
-
-While the use of travel satisfaction has been mainly used in the context of daily trips – typically been linked to cost-benefit and utilitarian measurements –, the evaluation of Subjective Wellbeing (SWB) over time has risen as an alternative measure.
-In the field of travel behaviour, Ettema et al.
-(2010; p.
-725) have defined SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporality – which implies assuming a tendency to be more stable over time.
-This concept has prompted a growing literature that complements and applies SWB in a broader range of satisfaction scales and situations.
-The definition of other factors such as travel choice mode, attitudes and external elements of the built environment has been studied for a broader understanding of the changes produced in the SWB.
-As these factors do not necessarily apply to the general life satisfaction on the long term, the studies have aimed to determine both the direct and indirect effects on the perception of users (see, e.g.
-Ye and Titheridge 2017).
-Other concepts have also emerged as the Satisfaction with Travel Scale (STS), a measurement devised by Ettema et al.
-(2011) as well as different scales based on people’s travel perceptions.
-De Vos et al.
-(2015) for instance, explore in detail the underlying dimensions of the affective domain of STS in which SWB is based (for more on STS see also Friman et al.
-2013).
-
-Recent literature on SWB and its link with transport have demonstrated a relationship between people’s perceptions and satisfaction with their daily travel (Smith, 2017; St-Louis et al.
-2014; Paez and Whalen, 2010; Whalen et al., 2013).
-Scholars have shown that accessibility has been the most developed factor that influences people’s wellbeing (Delbosc, 2012), and activities have a direct impact on travel satisfaction (Bergstad et al., 2010).
-Delbosc (2012; 28) for instance, has summarised the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.
-However, understanding the components affecting people’s perceptions implies the differentiation between the emotional (also named as symbolic-affective) and the instrumental reasons (Bergstad, 2001).
-Steg et al.
-(2011) have compared symbolic-affective opposed to instrumental-reasoned motives based on car-use, and other studies have also found associations between affective and symbolic aspects of car-use (see, e.g.
-Gatersleben, 2007; Lois & López-Sáez, 2009).
-Previous studies have demonstrated how socio-demographic factors affect the levels of SWB.
-The effect of income on SWB (Clarck and Oswald, 1996, Ferrer-i-Carbonell, 2005); education and unemployment (Argyle, 1999); age (Diener and Suh, 1997) and gender (Tesch-Römer et al., 2008) have already been studied.
-Recent research also suggests the links between commuting, SWB and emotional wellbeing assessment (Olson et al.
-2013; Kahneman et al.
-2004).
-However, more research is needed to understand how these socio-demographic variables, connect as well with the decisions on main transport mode choices; or research distinguishing between hedonic (journey experience) and eudaimonic (flourishing) value of trips.
-
-The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel (Zorrilla et al., 2019).
-In this way, there is an emerging literature that investigates affective factors in travel behaviour in a number of developing countries.
-A cross-country study in Asia revealed that the affective factors of public transportation and car use are important, and in particular the social orderliness of transit was suggested as a way to make this mode more attractive to users (Van et al., 2014).
-In terms of active travel, a study in China found that attitudes that embrace new styles and technologies despite their cost are associated with the intention to continue using shared bicycles (Shao and Liang, 2019).
-The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows how users felt proud using a bicycle shared system, in addition to experiencing feelings of belonging to a civic culture and the enjoyment and pleasure of travel itself (Bejarano et al., 2019).
-This paper contributes to further our understanding of affective and instrumental factors in travel behaviour in a developing country.
-
-Data and Methods
-===================
-
-This paper implements an analysis of correspondence comparing the primary mode of transportation with affective and utilitarian SWB factors in a sample of travellers in Santiago de Chile.
-
-## Sample
-
-The study is based on a survey conducted in Santiago during the months of November and December 2016, that collected information on a wide range of travel and related issues.
-The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
-An equal representation of both genders and a representation of the proportion of inhabitants per area have been chosen as relevant characteristics of the sample.
-In total, 451 persons validly completed the survey.
-In the first part of the questionnaire the participants were asked about basic socio-demographic data and main transport mode for commuting.
-In the second part, the questionnaire asked about the modes that people associate with affective and instrumental positive concepts of commuting, as well as the levels of overall satisfaction with the trips.
-These two sections of the survey have been considered for the analysis of this paper.
-The second part of the survey asked about the association between the primary transport mode and 18 positive and negative feelings.
-The question is: “Indicate the modes that you associate to the following feelings”.
-The respondents could indicate all the modes they associated to the feelings on the list.
-Three affective and three instrumental/utilitarian factors, all positive, have been considered for this analysis: freedom, enjoyment, happiness (affective), and security, time savings, efficiency (instrumental/utilitarian).
-The questionnaire provides a binary indicator that describes the presence or absence of modal correspondence for each one the selected six factors.
-The analysis has considered socioeconomic variables (gender, age, education, occupation, income, disabilities), as well as other variables as driving licence, journey times, monthly expenditure on transport and satisfaction with the overall trip.
-
-[REPORT DESCRIPTIVE STATISTICS?
-Include definitions, e.g., is K-12 equivalent to “minimal mandatory education”?
-What is Tech Univ?
-What are the range of values of low, middle, high income?
-Journey time is in minutes]
-
-## Analytical Approach
+\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
+
+  \journal{An Elsevier journal} % Sets Journal name
+
+\usepackage{lineno} % add
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage{graphicx}
+\usepackage{booktabs} % book-quality tables
+%%%%%%%%%%%%%%%% end my additions to header
+
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\bibliographystyle{elsarticle-harv}
+\usepackage{graphicx}
+% We will generate all images so they have a width \maxwidth. This means
+% that they will get their normal width if they fit onto the page, but
+% are scaled down if they would overflow the margins.
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
+\else\Gin@nat@width\fi}
+\makeatother
+\let\Oldincludegraphics\includegraphics
+\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Do Drivers Dream of Walking? An Investigation of Dissonance in the Primary Mode of Travel from the Perspective of Subjective Wellbeing},
+            colorlinks=false,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
+\setcounter{secnumdepth}{0}
+% Pandoc toggle for numbering sections (defaults to be off)
+\setcounter{secnumdepth}{0}
+% Pandoc header
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
+\begin{document}
+\begin{frontmatter}
+
+  \title{Do Drivers Dream of Walking? An Investigation of Dissonance in the
+Primary Mode of Travel from the Perspective of Subjective Wellbeing}
+    \author[Some University]{Author 1\corref{c1}}
+   \ead{a1@university.com} 
+   \cortext[c1]{Corresponding Author}
+    \author[Some School]{Author 2}
+   \ead{a2@school.com}
+
+      \address[Some University]{Department, Street, City, State, Zip}
+    \address[Some School]{Department, Street, City, State, Zip}
+
+  \begin{abstract}
+  Transportation in most of the world has been dominated for decades by a
+  fascination with the automobile. Increasingly, however, it is recognized
+  that to achieve a variety of economic, environmental, and public health
+  policy goals it is important to attract and retain users of public
+  transport and active travel. A challenge with the way transportation
+  policy is developed is that it tends to focus on cost-benefit and
+  utilitarian considerations, which may miss other potential benefits of
+  transportation. For this reason, subjective wellbeing (SWB) has been
+  proposed as a way to enhance our understanding of the preferences and
+  choices of travellers, as well as a way to evaluate the benefits of
+  transportation beyond utilitarian considerations. The objective of this
+  paper is to analyze the modes that people commonly use, and to what
+  extent they are aligned (or not) with a variety of affective and
+  utilitarian values. In other words, we are interested in the potential
+  for dissonance with respect to the primary mode of travel, from the
+  perspective of affective and utilitarian values. The study is based on
+  data collected from a sample of travellers in the city of Santiago, in
+  Chile. Participants in the study were asked about their usual mode of
+  travel, and then were asked to name the mode or modes that they
+  associated to affective values (freedom, enjoyment, and happiness) and
+  to utilitarian values (safety, time waste, and efficiency). The results
+  indicate that users of public transportation experience the most
+  dissonance in terms of affective values, and active travellers the
+  least. For those travellers who experience dissonance, active travel is
+  the mode most commonly associated with affective values.
+
+  To properly assess transportation policy This poses a number of
+  challenges Broadening the commonly used transport project assessment
+  will be relevant for achieving this goal. While satisfaction with travel
+  has been mainly used in the context of daily trips and mainly under
+  cost-benefit and utilitarian considerations, subjective wellbeing (SWB)
+  over time has risen as an alternative for understanding the preferences
+  and choices of transport users. The aim of this paper is to analyse the
+  factors that can potentially affect the levels of SWB in the wide
+  spectrum of public, private and active transport modes in the context of
+  Santiago de Chile. The paper aims to reflect on the possibilities of
+  increasing the SWB with a view to enhance the attractiveness of public
+  transport and active travel. The paper investigates the affective and
+  instrumental/utilitarian factors of SWB, according to modal choice. It
+  uses an analysis of correspondence that considers the actual primary
+  mode used, versus the mode that each individual associated to both
+  utilitarian and affective SWB factors. The results show that there is
+  more persistent modal dissonance between positive emotional and
+  utilitarian associations within the more disadvantaged groups --
+  particularly among users of public transport. The study shows that apart
+  from time-savings and efficiency, security has also been
+  cross-sectionally sensitive according to the data analysed. Factors such
+  as happiness, enjoyment and freedom require far more attention in
+  transport planning as they are strongly related to the dimensions of
+  subjective and personal wellbeing. Targeting these factors will be
+  relevant for attracting new users to public transportation and active
+  travel.\\
+  \end{abstract}
+
+ \end{frontmatter}
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Transportation planning for decades has focused on providing mobility
+for the private automobile. This is a model of development that was
+initially introduced in North America as a solution to urbanizations
+problems, and that was eventually copied elsewhere (Brown et al., 2009;
+Angotti, 1996) . Despite the initial promise of automotive technology,
+it is now evident that mobility centred on the private automobile has
+given rise to a litany of maladies that are in urgent need of
+correction. This includes environmental concerns (i.e., climate change;
+Chapman, 2007) as well as other social (Boschmann and Kwan, 2008),
+health (Khreis et al., 2016), and equity issues (Bocarejo and Oviedo,
+2012). As the real impacts of our societal dependence on the private
+autombobile have become increasingly evident, the transportation agenda
+has in recent years aimed to shift focus to the reduction of car-use and
+towards the creation of mobility polycultures that offer a broader menu
+of transportation alternatives than just the private automobile (Miller,
+2011) . In order to successfully achieve this goal, it is essential not
+only to provide the services and facilities that support public
+transportation and active travel, but also to attract new users to these
+modes of transportation (Ettema et al.~2011). Within this context, it
+has been argued that sustainable transportation policies require all
+participants in the transportation system to challenge what Gossling and
+Cohen (2014) term ``transportation taboos'': deep-seated ideas
+concerning the contribution to emissions by individuals, the inequality
+of market-based approaches, and the social and psychological functions
+of transportation. With respect to the latter, moving beyond a purely
+utilitarian focus, it is important to understand how users perceive
+affective and instrumental elements on their transportation experience,
+since this can help to incorporate adequate improvements in alternative
+transportation, including transit and active modes, to make them more
+attractive to users (Anable and Gatersleben, 2005; Domarchi et al.,
+2008; Gatersleben and Uzzell, 2007; Steg 2005 ).
+
+A useful lens to investigate the social and psychological functions of
+transportation is by means of the concept of subjective wellbeing (SWB.
+See, inter alia, De Vos et al., 2013 and Chatterjee et al., 2019) . SWB
+is defined by the OECD as ``{[}g{]}ood mental states, including all of
+the various evaluations, positive and negative, that people make of
+their lives, and the affective reactions of people to their
+experiences'' (OECD, 2013, p.~10). Accordingly, the aim of this paper is
+to analyse some of the factors that can potentially affect the levels of
+SWB in the wide spectrum of public, private and active transport modes
+in the context of Santiago de Chile. Previous research suggests that
+public transport users experience a negative gap in desired and actual
+travel time, whereas active travellers don't seem to mind somewhat
+longer trips than what strictly needed (e.g., Páez and Whalen, 2010). In
+the context of a Latin American country, historically the poor travel
+experience of public transit users and active travellers reflects the
+social inequalities of social groups that have no alternative but to
+move in these types of modes while living far from the work centres and
+main activities. The paper aims to reflect on the possibilities of
+increasing the SWB while travelling, and how this could increase the
+attractiveness of public transport and active travel in the
+socio-demographic groups studied. This can help not only to reduce the
+use of private transport but also decrease the inequality gap between
+these users.
+
+The paper explores how positive affective and instrumental/utilitarian
+factors of SWB correspond to the use of the primary mode of
+transportation. It uses an analysis of correspondence that considers the
+actual primary mode versus the mode that individuals associated to both
+utilitarian (designed to be useful or practical rather than attractive)
+and affective (expressing a person's feelings) SWB factors. For example,
+it will be analysed if a person who uses public transport as the primary
+mode, tends to associate these modes with positive affective factors (as
+freedom, enjoyment or happiness) or positive utilitarian factors (as
+security, time-savings or efficiency). We hypothesize that there is a
+more persistent non-correspondence or mismatch within the more
+disadvantage groups or within the users of public transport.
+
+The paper contributes to the literature in three areas. First, it
+contributes to an emerging literature on the topic in the context of the
+Global South (Bejarano et al., 2017 ; Shao and Liang, 2019 ; Van et al.,
+2014 ; Zorrilla et al., 2019); to the best of our knowledge, the case of
+Chile has not yet been reported. Second, although there is literature on
+the enjoyment of commute and other emotional factors, from a hedonic and
+even eudaimonic perspectives, the analysis has yet to be applied more
+fully in terms of distributional issues -- i.e.~which groups are mostly
+disadvantaged. Finally, the analysis shows the attitudes of people
+towards their primary mode and their perception towards `ideal modes' --
+implying their preferences, even in situations when their ideal mode is
+not part of their actual choice set. The attitudes of travellers towards
+transport modes are critical factors to be considered by policy-makers
+in case they want to promote and increase the use of public transport or
+active modes (e.g., Bejarano et al., 2019). The paper explores these
+positive and negative associations within the transport options used in
+Santiago.
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
+
+The transportation community has for the most part already agreed to the
+need of looking at mobility and transport issues from the lens of
+wellbeing, to broaden the commonly used utilitarian perspective to
+evaluate projects. Users' travel satisfaction (Bergstad, 2001) has been
+the primary way to direct this challenge towards everyday mobility,
+resulting on research about satisfaction with different transport modes.
+For example, numerous studies report that car users have a higher level
+of satisfaction compared to other transport modes (Redmond and
+Mokhtarian, 2001 ; Bergstad et al.~2011; Eriksson et al.~2013; Whalen et
+al., 2013). In a similar way, there are multiple reports that active
+travel also tends to yield high levels of satisfaction (Smith, 2017;
+St-Louis et al.~2014; Paez and Whalen, 2010; Whalen et al., 2013), In
+contrast, public transport users tend to assess their experience more
+negatively (De Vos et al.~2016; Abenoza et al.~2017; Ettema et al.~2012;
+Páez and Whalen, 2010). Multi-modal trips also influence satisfaction
+levels; for instance, when an individual chooses a particular mode of
+transportation, she will report a higher level of satisfaction with that
+chosen mode -- perhaps as a form of post hoc validation (Susilo and
+Cats, 2014).
+
+While the use of travel satisfaction has been mainly used in the context
+of daily trips -- typically been linked to cost-benefit and utilitarian
+measurements --, the evaluation of Subjective Wellbeing (SWB) over time
+has risen as an alternative measure. In the field of travel behaviour,
+Ettema et al.~(2010; p.~725) have defined SWB as the degree to which an
+individual positively evaluates the overall quality of their lives,
+where the general life satisfaction encompasses a more extended
+temporality -- which implies assuming a tendency to be more stable over
+time. This concept has prompted a growing literature that complements
+and applies SWB in a broader range of satisfaction scales and
+situations. The definition of other factors such as travel choice mode,
+attitudes and external elements of the built environment has been
+studied for a broader understanding of the changes produced in the SWB.
+As these factors do not necessarily apply to the general life
+satisfaction on the long term, the studies have aimed to determine both
+the direct and indirect effects on the perception of users (see, e.g.~Ye
+and Titheridge 2017). Other concepts have also emerged as the
+Satisfaction with Travel Scale (STS), a measurement devised by Ettema et
+al.~(2011) as well as different scales based on people's travel
+perceptions. De Vos et al.~(2015) for instance, explore in detail the
+underlying dimensions of the affective domain of STS in which SWB is
+based (for more on STS see also Friman et al.~2013).
+
+Recent literature on SWB and its link with transport have demonstrated a
+relationship between people's perceptions and satisfaction with their
+daily travel (Smith, 2017; St-Louis et al.~2014; Paez and Whalen, 2010;
+Whalen et al., 2013). Scholars have shown that accessibility has been
+the most developed factor that influences people's wellbeing (Delbosc,
+2012), and activities have a direct impact on travel satisfaction
+(Bergstad et al., 2010). Delbosc (2012; 28) for instance, has summarised
+the most significant influences on psychological wellbeing: poverty and
+employment, meaningful relationships and health. However, understanding
+the components affecting people's perceptions implies the
+differentiation between the emotional (also named as symbolic-affective)
+and the instrumental reasons (Bergstad, 2001). Steg et al.~(2011) have
+compared symbolic-affective opposed to instrumental-reasoned motives
+based on car-use, and other studies have also found associations between
+affective and symbolic aspects of car-use (see, e.g.~Gatersleben, 2007;
+Lois \& López-Sáez, 2009). Previous studies have demonstrated how
+socio-demographic factors affect the levels of SWB. The effect of income
+on SWB (Clarck and Oswald, 1996, Ferrer-i-Carbonell, 2005); education
+and unemployment (Argyle, 1999); age (Diener and Suh, 1997) and gender
+(Tesch-Römer et al., 2008) have already been studied. Recent research
+also suggests the links between commuting, SWB and emotional wellbeing
+assessment (Olson et al.~2013; Kahneman et al.~2004). However, more
+research is needed to understand how these socio-demographic variables,
+connect as well with the decisions on main transport mode choices; or
+research distinguishing between hedonic (journey experience) and
+eudaimonic (flourishing) value of trips.
+
+The research needs already recognized in the developed world are also
+markedly acute in the context of the Global South, where historical
+inequality has tended to create a symbolic attachment to the automobile,
+in addition to negative connotations for public transport and active
+travel (Zorrilla et al., 2019). In this way, there is an emerging
+literature that investigates affective factors in travel behaviour in a
+number of developing countries. A cross-country study in Asia revealed
+that the affective factors of public transportation and car use are
+important, and in particular the social orderliness of transit was
+suggested as a way to make this mode more attractive to users (Van et
+al., 2014). In terms of active travel, a study in China found that
+attitudes that embrace new styles and technologies despite their cost
+are associated with the intention to continue using shared bicycles
+(Shao and Liang, 2019). The importance of affective factors for policy
+and planning is further highlighted by research in Colombia that shows
+how users felt proud using a bicycle shared system, in addition to
+experiencing feelings of belonging to a civic culture and the enjoyment
+and pleasure of travel itself (Bejarano et al., 2019). This paper
+contributes to further our understanding of affective and instrumental
+factors in travel behaviour in a developing country.
+
+\hypertarget{data-and-methods}{%
+\section{Data and Methods}\label{data-and-methods}}
+
+This paper implements an analysis of correspondence comparing the
+primary mode of transportation with affective and utilitarian SWB
+factors in a sample of travellers in Santiago de Chile.
+
+\hypertarget{sample}{%
+\subsection{Sample}\label{sample}}
+
+The study is based on a survey conducted in Santiago during the months
+of November and December 2016, that collected information on a wide
+range of travel and related issues. The data collection considered a
+quota-sampling method for gathering the information, considering the
+socio-demographic information from Pre-Census of 2012. An equal
+representation of both genders and a representation of the proportion of
+inhabitants per area have been chosen as relevant characteristics of the
+sample. In total, 451 persons validly completed the survey. In the first
+part of the questionnaire the participants were asked about basic
+socio-demographic data and main transport mode for commuting. In the
+second part, the questionnaire asked about the modes that people
+associate with affective and instrumental positive concepts of
+commuting, as well as the levels of overall satisfaction with the trips.
+These two sections of the survey have been considered for the analysis
+of this paper. The second part of the survey asked about the association
+between the primary transport mode and 18 positive and negative
+feelings. The question is: ``Indicate the modes that you associate to
+the following feelings''. The respondents could indicate all the modes
+they associated to the feelings on the list. Three affective and three
+instrumental/utilitarian factors, all positive, have been considered for
+this analysis: freedom, enjoyment, happiness (affective), and security,
+time savings, efficiency (instrumental/utilitarian). The questionnaire
+provides a binary indicator that describes the presence or absence of
+modal correspondence for each one the selected six factors. The analysis
+has considered socioeconomic variables (gender, age, education,
+occupation, income, disabilities), as well as other variables as driving
+licence, journey times, monthly expenditure on transport and
+satisfaction with the overall trip.
+
+{[}REPORT DESCRIPTIVE STATISTICS? Include definitions, e.g., is K-12
+equivalent to ``minimal mandatory education''? What is Tech Univ? What
+are the range of values of low, middle, high income? Journey time is in
+minutes{]}
+
+\hypertarget{analytical-approach}{%
+\subsection{Analytical Approach}\label{analytical-approach}}
 
 The analytical approach in this paper is based on correspondence.
-Previous research has developed the concept of modal dissonance for referring to the mismatch between the actual mode and the mode that enables users to experience positive affective or instrumental factors (De Vos et al., (2012; 2014) and Schwanen and Mokhtarian, 2004, 2005a, 2005b).
-More concretely, Schwanen and Mokhtarian (2004; 89) define dissonance based on the incongruence between residential neighbourhood where the individual currently resides and her preference structure toward such characteristics of the residential environment.
-In this paper we consider correspondence, which happens when travellers associate the positive utilitarian and affective SWB factors to the mode they have used as their primary transport mode for commuting or performing their main activities.
-The opposite of correspondence would be modal dissonance.
-
-More specifically, the concept of modal dissonance means that a user of mode X identifies a different mode Y when associating affective values.
-For example, a user of private transport (i.e., mode “Car”)  may select mode “Bicycle” when asked about the of the association between the concept of freedom to a transport mode.
-In this case, the person who uses the mode “Car” as their primary mode of transportation attaches positive emotional and instrumental factors not to that mode, but to a different one – in this case to the bicycle.
-It could be the case that the modal dissonance corresponds just to one of the types of factors, either affective or instrumental.
-For example, it is possible that a person who uses the Metro as their main transport mode associates that mode to the instrumental factors (security, time savings, efficiency) – but relates positive emotional factors (freedom, enjoyment, happiness) to a different mode, say to the bicycle.
-
-The ways for measuring equity in transport projects and the most vulnerable groups affected by transport have been the aspects that have nurtured the focus of this study.
-The hypothesis is that public transport users will show a lower correspondence between their primary mode and the modes they relate with positive factors of SWB.
-This is relevant as more disadvantaged people have less options of choosing their preferred transport modes and they tend to associate positive affective and instrumental factors to modes that they are not able to use.
-These perceptions evidence equity gaps between groups – where the most vulnerable groups are much more affected.
-The methods used are analysis of correspondence and multinomial regression, both around the associations of transport modes and affective and instrumental factors, derived from the SWB framework.
-
-Results
-==========
-
-```{r cross-with-instrumental, include=FALSE, eval=FALSE}
-
-# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)
-
-## Age
-
-age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
-age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-age_by_safety <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "SAFETY_DISSONANCE", type = "r")
-age_by_time <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "TIME_DISSONANCE", type = "r")
-age_by_efficiency <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Education
-
-education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
-education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-education_by_safety <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "SAFETY_DISSONANCE", type = "r")
-education_by_time <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "TIME_DISSONANCE", type = "r")
-education_by_efficiency <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Income
-
-income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-income_by_safety <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "SAFETY_DISSONANCE", type = "r")
-income_by_time <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "TIME_DISSONANCE", type = "r")
-income_by_efficiency <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Mode
-
-mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
-mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-mode_by_safety <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "SAFETY_DISSONANCE", type = "r")
-mode_by_time <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "TIME_DISSONANCE", type = "r")
-mode_by_efficiency <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Travel Time
-
-time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-time_by_safety <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "SAFETY_DISSONANCE", type = "r")
-time_by_time <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "TIME_DISSONANCE", type = "r")
-time_by_efficiency <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-```
-
-```{r cross-without-instrumental, include=FALSE}
-
-# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)
-
-## Age
-
-age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
-age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-age_by_poverty <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "POVERTY_DISSONANCE", type = "r")
-age_by_luxury <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "LUXURY_DISSONANCE", type = "r")
-age_by_status <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Education
-
-education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
-education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-education_by_poverty <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "POVERTY_DISSONANCE", type = "r")
-education_by_luxury <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "LUXURY_DISSONANCE", type = "r")
-education_by_status <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Income
-
-income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-income_by_poverty <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "POVERTY_DISSONANCE", type = "r")
-income_by_luxury <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "LUXURY_DISSONANCE", type = "r")
-income_by_status <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Mode
-
-mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
-mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-mode_by_poverty <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "POVERTY_DISSONANCE", type = "r")
-mode_by_luxury <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "LUXURY_DISSONANCE", type = "r")
-mode_by_status <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Travel Time
-
-time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-time_by_poverty <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "POVERTY_DISSONANCE", type = "r")
-time_by_luxury <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "LUXURY_DISSONANCE", type = "r")
-time_by_status <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "STATUS_DISSONANCE", type = "r")
-
-```
-
-```{r collect-cross-tabulation-results-with-instrumental, include=FALSE, eval=FALSE}
-
-# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES
-
-## Age
-
-age_results <- cbind(age_by_freedom$crosstab, 
-                     age_by_enjoyment$crosstab, 
-                     age_by_happiness$crosstab,
-                     age_by_safety$crosstab,
-                     age_by_time$crosstab,
-                     age_by_efficiency$crosstab)
-
-# Drop the row totals
-age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-age_results <- age_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-age_results <- age_results %>%
-  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(age_by_happiness$table)$p.value,
-         chi2.safety = summary(age_by_safety$table)$p.value,
-         chi2.time = summary(age_by_time$table)$p.value,
-         chi2.efficiency = summary(age_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Education
-
-education_results <- cbind(education_by_freedom$crosstab, 
-                     education_by_enjoyment$crosstab, 
-                     education_by_happiness$crosstab,
-                     education_by_safety$crosstab,
-                     education_by_time$crosstab,
-                     education_by_efficiency$crosstab)
-
-# Drop the row totals
-education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-education_results <- education_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-education_results <- education_results %>%
-  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(education_by_happiness$table)$p.value,
-         chi2.safety = summary(education_by_safety$table)$p.value,
-         chi2.time = summary(education_by_time$table)$p.value,
-         chi2.efficiency = summary(education_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Income
-
-income_results <- cbind(income_by_freedom$crosstab, 
-                     income_by_enjoyment$crosstab, 
-                     income_by_happiness$crosstab,
-                     income_by_safety$crosstab,
-                     income_by_time$crosstab,
-                     income_by_efficiency$crosstab)
-
-# Drop the row totals
-income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-income_results <- income_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-income_results <- income_results %>%
-  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(income_by_happiness$table)$p.value,
-         chi2.safety = summary(income_by_safety$table)$p.value,
-         chi2.time = summary(income_by_time$table)$p.value,
-         chi2.efficiency = summary(income_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Mode USED
-
-mode_results <- cbind(mode_by_freedom$crosstab, 
-                     mode_by_enjoyment$crosstab, 
-                     mode_by_happiness$crosstab,
-                     mode_by_safety$crosstab,
-                     mode_by_time$crosstab,
-                     mode_by_efficiency$crosstab)
-
-# Drop the row totals
-mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-mode_results <- mode_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-mode_results <- mode_results %>%
-  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(mode_by_happiness$table)$p.value,
-         chi2.safety = summary(mode_by_safety$table)$p.value,
-         chi2.time = summary(mode_by_time$table)$p.value,
-         chi2.efficiency = summary(mode_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Time
-
-time_results <- cbind(time_by_freedom$crosstab, 
-                     time_by_enjoyment$crosstab, 
-                     time_by_happiness$crosstab,
-                     time_by_safety$crosstab,
-                     time_by_time$crosstab,
-                     time_by_efficiency$crosstab)
-
-# Drop the row totals
-time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-time_results <- time_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-time_results <- time_results %>%
-  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(time_by_happiness$table)$p.value,
-         chi2.safety = summary(time_by_safety$table)$p.value,
-         chi2.time = summary(time_by_time$table)$p.value,
-         chi2.efficiency = summary(time_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-```
-
-```{r collect-cross-tabulation-results-without-instrumental, include=FALSE}
-
-# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES
-
-## Age
-
-age_results <- cbind(age_by_freedom$crosstab, 
-                     age_by_enjoyment$crosstab, 
-                     age_by_happiness$crosstab,
-                     age_by_poverty$crosstab,
-                     age_by_luxury$crosstab,
-                     age_by_status$crosstab)
-
-# Drop the row totals
-age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-age_results <- age_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-age_results <- age_results %>%
-  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(age_by_happiness$table)$p.value,
-         chi2.poverty = summary(age_by_poverty$table)$p.value,
-         chi2.luxury = summary(age_by_luxury$table)$p.value,
-         chi2.status = summary(age_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Education
-
-education_results <- cbind(education_by_freedom$crosstab, 
-                     education_by_enjoyment$crosstab, 
-                     education_by_happiness$crosstab,
-                     education_by_poverty$crosstab,
-                     education_by_luxury$crosstab,
-                     education_by_status$crosstab)
-
-# Drop the row totals
-education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-education_results <- education_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-education_results <- education_results %>%
-  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(education_by_happiness$table)$p.value,
-         chi2.poverty = summary(education_by_poverty$table)$p.value,
-         chi2.luxury = summary(education_by_luxury$table)$p.value,
-         chi2.status = summary(education_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Income
-
-income_results <- cbind(income_by_freedom$crosstab, 
-                     income_by_enjoyment$crosstab, 
-                     income_by_happiness$crosstab,
-                     income_by_poverty$crosstab,
-                     income_by_luxury$crosstab,
-                     income_by_status$crosstab)
-
-# Drop the row totals
-income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-income_results <- income_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-income_results <- income_results %>%
-  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(income_by_happiness$table)$p.value,
-         chi2.poverty = summary(income_by_poverty$table)$p.value,
-         chi2.luxury = summary(income_by_luxury$table)$p.value,
-         chi2.status = summary(income_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Mode USED
-
-mode_results <- cbind(mode_by_freedom$crosstab, 
-                     mode_by_enjoyment$crosstab, 
-                     mode_by_happiness$crosstab,
-                     mode_by_poverty$crosstab,
-                     mode_by_luxury$crosstab,
-                     mode_by_status$crosstab)
-
-# Drop the row totals
-mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-mode_results <- mode_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-mode_results <- mode_results %>%
-  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(mode_by_happiness$table)$p.value,
-         chi2.poverty = summary(mode_by_poverty$table)$p.value,
-         chi2.luxury = summary(mode_by_luxury$table)$p.value,
-         chi2.status = summary(mode_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Time
-
-time_results <- cbind(time_by_freedom$crosstab, 
-                     time_by_enjoyment$crosstab, 
-                     time_by_happiness$crosstab,
-                     time_by_poverty$crosstab,
-                     time_by_luxury$crosstab,
-                     time_by_status$crosstab)
-
-# Drop the row totals
-time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-time_results <- time_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-time_results <- time_results %>%
-  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(time_by_happiness$table)$p.value,
-         chi2.poverty = summary(time_by_poverty$table)$p.value,
-         chi2.luxury = summary(time_by_luxury$table)$p.value,
-         chi2.status = summary(time_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-```
-
-```{r crosstab-all-results-with-instrumental, include=FALSE, eval=FALSE}
-
-# Here we bind all the results into a single dataframe for printing
-
-xtab_results <- rbind(age_results,
-                      education_results,
-                      income_results,
-                      mode_results,
-                      time_results) %>%
-  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
-         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
-         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
-         chi2.safety = ifelse(chi2.safety >= 0.001, paste0(round(chi2.safety, 4)), "$<0.001$"),
-         chi2.time = ifelse(chi2.time >= 0.001, paste0(round(chi2.time, 4)), "$<0.001$"),
-         chi2.efficiency = ifelse(chi2.efficiency >= 0.001, paste0(round(chi2.efficiency, 4)), "$<0.001$"))
-
-xtab_results[10:13, 3] <- "$< 0.001$"
-```
-
-```{r crosstab-all-results-without-instrumental, echo=FALSE}
-
-# Here we bind all the results into a single dataframe for printing
-
-xtab_results <- rbind(age_results,
-                      education_results,
-                      income_results,
-                      mode_results,
-                      time_results) %>%
-  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
-         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
-         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
-         chi2.poverty = ifelse(chi2.poverty >= 0.001, paste0(round(chi2.poverty, 4)), "$<0.001$"),
-         chi2.luxury = ifelse(chi2.luxury >= 0.001, paste0(round(chi2.luxury, 4)), "$<0.001$"),
-         chi2.status = ifelse(chi2.status >= 0.001, paste0(round(chi2.status, 4)), "$<0.001$"))
-
-xtab_results[10:13, 3] <- "$< 0.001$"
-```
-
-## Who experiences dissonance?
-
-The first step of the analysis seeks to understand whether there are statistical associations between the variables of interest.
-The analysis considers the cases where there is a lack of correspondence between the primary mode choice and the 6 SWB/instrumental factors previously described  – or in other words, where there is modal dissonance.
-
-Table 1 shows the results of the analysis of correspondence and the dissonances between the primary mode of travel on the one hand, and SWB and instrumental factors on the other.
-As seen in the table, there are five categories that we use for the analysis.
-Three of these categories are socio-economic and demographic, namely age, level of education, income.
-The other two categories are transportation related, namely primary mode of travel and journey time.
-Correspondence is tested in every case by means of the $\chi^2$ statistic.
-It is interesting to note that the only category for which all affective/instrumental factors are significant at better than 5% level of confidence is mode of travel.
-
-With respect to age, we observe that levels of dissonance tend to be high in general, and the results indicate that when it comes to affective factors, dissonance levels tend to be significantly higher for younger travellers, in particular Enjoyment.
-In terms of instrumental factors, dissonance also tends to significantly decline with age when considering Security.
-On the other hand, the levels of dissonance in terms of Time Savings and Efficiency, while high, do not show significant differences by age group.
-Overall, the findings suggest that dissonance tends to decline with age.
-
-The results indicate that the category of Education is less useful to discriminate between different levels of dissonance.
-Two affective factors are significant at 10% or better (Freedom and Happiness) and show that dissonance tends to decline at higher levels of education.
-One instrumental factor is significant at 10% or better (Time Savings) and we see there that the level of dissonance tends to grow with higher levels of education.
-Another instrumental factor (Security) is significant at 5% or better and shows that dissonance in this factor declines with higher education.
-The picture that emerges is of highly educated people who are relatively less dissatisfied with their primary mode of transportation when it comes to Freedom, Happiness, and Security, but more dissatisfied with their Time Savings than people who are less highly educated.
+Previous research has developed the concept of modal dissonance for
+referring to the mismatch between the actual mode and the mode that
+enables users to experience positive affective or instrumental factors
+(De Vos et al., (2012; 2014) and Schwanen and Mokhtarian, 2004, 2005a,
+2005b). More concretely, Schwanen and Mokhtarian (2004; 89) define
+dissonance based on the incongruence between residential neighbourhood
+where the individual currently resides and her preference structure
+toward such characteristics of the residential environment. In this
+paper we consider correspondence, which happens when travellers
+associate the positive utilitarian and affective SWB factors to the mode
+they have used as their primary transport mode for commuting or
+performing their main activities. The opposite of correspondence would
+be modal dissonance.
+
+More specifically, the concept of modal dissonance means that a user of
+mode X identifies a different mode Y when associating affective values.
+For example, a user of private transport (i.e., mode ``Car'') may select
+mode ``Bicycle'' when asked about the of the association between the
+concept of freedom to a transport mode. In this case, the person who
+uses the mode ``Car'' as their primary mode of transportation attaches
+positive emotional and instrumental factors not to that mode, but to a
+different one -- in this case to the bicycle. It could be the case that
+the modal dissonance corresponds just to one of the types of factors,
+either affective or instrumental. For example, it is possible that a
+person who uses the Metro as their main transport mode associates that
+mode to the instrumental factors (security, time savings, efficiency) --
+but relates positive emotional factors (freedom, enjoyment, happiness)
+to a different mode, say to the bicycle.
+
+The ways for measuring equity in transport projects and the most
+vulnerable groups affected by transport have been the aspects that have
+nurtured the focus of this study. The hypothesis is that public
+transport users will show a lower correspondence between their primary
+mode and the modes they relate with positive factors of SWB. This is
+relevant as more disadvantaged people have less options of choosing
+their preferred transport modes and they tend to associate positive
+affective and instrumental factors to modes that they are not able to
+use. These perceptions evidence equity gaps between groups -- where the
+most vulnerable groups are much more affected. The methods used are
+analysis of correspondence and multinomial regression, both around the
+associations of transport modes and affective and instrumental factors,
+derived from the SWB framework.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{who-experiences-dissonance}{%
+\subsection{Who experiences
+dissonance?}\label{who-experiences-dissonance}}
+
+The first step of the analysis seeks to understand whether there are
+statistical associations between the variables of interest. The analysis
+considers the cases where there is a lack of correspondence between the
+primary mode choice and the 6 SWB/instrumental factors previously
+described -- or in other words, where there is modal dissonance.
+
+Table 1 shows the results of the analysis of correspondence and the
+dissonances between the primary mode of travel on the one hand, and SWB
+and instrumental factors on the other. As seen in the table, there are
+five categories that we use for the analysis. Three of these categories
+are socio-economic and demographic, namely age, level of education,
+income. The other two categories are transportation related, namely
+primary mode of travel and journey time. Correspondence is tested in
+every case by means of the \(\chi^2\) statistic. It is interesting to
+note that the only category for which all affective/instrumental factors
+are significant at better than 5\% level of confidence is mode of
+travel.
+
+With respect to age, we observe that levels of dissonance tend to be
+high in general, and the results indicate that when it comes to
+affective factors, dissonance levels tend to be significantly higher for
+younger travellers, in particular Enjoyment. In terms of instrumental
+factors, dissonance also tends to significantly decline with age when
+considering Security. On the other hand, the levels of dissonance in
+terms of Time Savings and Efficiency, while high, do not show
+significant differences by age group. Overall, the findings suggest that
+dissonance tends to decline with age.
+
+The results indicate that the category of Education is less useful to
+discriminate between different levels of dissonance. Two affective
+factors are significant at 10\% or better (Freedom and Happiness) and
+show that dissonance tends to decline at higher levels of education. One
+instrumental factor is significant at 10\% or better (Time Savings) and
+we see there that the level of dissonance tends to grow with higher
+levels of education. Another instrumental factor (Security) is
+significant at 5\% or better and shows that dissonance in this factor
+declines with higher education. The picture that emerges is of highly
+educated people who are relatively less dissatisfied with their primary
+mode of transportation when it comes to Freedom, Happiness, and
+Security, but more dissatisfied with their Time Savings than people who
+are less highly educated.
 
 In general, dissonance tends to be higher for lower income individuals.
-Table 1 shows that the low-income segment has a significantly higher percentage of cases of dissonance for two affective factors.
-In the case of Freedom, for example, the lack of correspondence for low-income is 83.9% compared to 60% for the high-income segment.
-The levels of dissonance are higher for Enjoyment and follow the same decreasing trend for higher levels of income.
-Dissonance is marginally lower for instrumental factors, and significant for Security and Time Savings.
-
-As noted above, there are significant differences in dissonance by primary mode of travel, both for affective and instrumental factors.
-For affective factors, the highest levels of dissonance tend to be for users of public transportation, and the lowest for car users and active travellers.
-For instance, feelings of Freedom, Enjoyment, and Happiness are more frequently expressed by users of car and active travellers than users of public transportation.
-Indeed, people who travel by Metro or Bus almost never associate any of these positive affective attributes to these modes (dissonance is consistently greater than 90%).
-In contrast, active travellers have some of the lowest levels of dissonance in all three affective factors, in particular Freedom and Happiness.
-This analysis is in line with previous research regarding car, active travel, and public transportation (e.g., Steg et al., 2001; Páez and Whalen, 2010; Whalen et al., 2013), which tend to agree on the negative associations in the perception of affective factors when the primary mode is Metro or bus.
-
-Figure 4 shows the percentage of dissonance by primary transport mode, for both affective and instrumental factors.
-For instance, the graph at the top shows that the highest percentages of dissonances come from users of Metro and bus , compared to other modes as the car or active transport.
-This is consistent with previous studies that have separately demonstrated that public transport users tend to assess more negatively subjective factors (explored e.g.
-in Stradling et al., 1999; Gatersleben and Uzzell, 2007).
-For example, although car users have higher dissonance values than active transport, comparatively this segment has much lower percentages of dissonances than public transport, idea also supported by research that has shown that car users tend to attribute importance to symbolic aspects that positively contribute to their perception on driving (Steg et al., 2001; Mokhtarian and Salomon, 2001).
-
-Freedom and happiness tend to have a lower percentage of dissonances in the case of active transport, which means that cyclists and individuals who mainly walk for their commutes, tend to associate positive subjective values while using these modes.
-This is also consistent with other studies that have shown positive affective associations with the use of cycling and walking (Anable and Gatersleben, 2005; Gatersleben and Uzzell, 2007).
-The question at the survey has not specify the dimensions of freedom, thus has open the door for different interpretations as the freedom to choose certain mode or route, freedom while using the mode, or the freedom to access to certain places while travelling.
-Journey time: As shown in Figure 3, the analysis carried out by journey time also reveals coincidences with previous research in this area, since for shorter trips (up to 20 minutes) the analysis shows less dissonance between the primary mode and positive subjective associations mainly for affective factors.
-On the contrary, as journey time increases, higher is the dissonance.
-Strangely, the feelings of Security and Efficiency have not been statistically representative for the Journey Time analysis.
-
-In terms of instrumental factors, interestingly Figure 4 shows that bus users have the lowest percentage of dissonance regarding time savings (29%).
-However, considering the other instrumental factors, bus users have a high percentage of dissonance for security and efficiency.
-In the case of security, this means that most bus users (71%) have considered the bus as a mode that they associate to time-savings, although it is the mode that has more dissonant evaluations in all other SWB factors.
-This also seems difficult to explain considering the negative evaluation that the Transantiago system has consistently had.
-Some data provided by the Survey of Satisfaction with Transantiago Operators (DTPM, 2017) is about users' perception of journey time from origin to destination.
-In this question, and after 10 years of implementation of the system, users diagnose an average journey of 47 minutes, a value that tends to increase with respect to the data delivered by the same survey 5 years before (43.5 minutes on average).
-Worryingly, long trips of more than 30 minutes have had inconsistent variability over the years, reaching an average of more than 37 minutes in 2016.
-Short trips, however, remain roughly equal to previous years, and do not show significant changes in the average of 6-7 minutes per trip .
-This survey has the peculiarity  of being developed by the Metropolitan Public Transport Board (DTPM), whose mission is to articulate the functions of the different modes of public transport with a specific interest in buses Transantiago and Metro de Santiago.
-
-Another big gap on these instrumental factors relates to the perception of security that is especially significant for car users.
-This means that a 75% of car users have chosen as primary mode the same one as they relate to the feeling of security, which is completely opposite to other transport modes, specially bus users.
-Bus users have the highest dissonance (98%), which means that practically all this group of users have chosen another mode for referring to the feelings of security.
-The recently referred DTPM survey does not have any particular question that addresses the issue of safety – mostly related in this context as security.
-
-```{r table-cross-tabulation-results-with-instrumental, echo = FALSE, eval=FALSE}
-kable(xtab_results,
-      "latex",
-      digits = 2,
-      booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
-      escape = FALSE,
-      align = c("l", rep("c", 12)),
-      col.names = c("Variable", 
-                    "Freedom", "$\\chi^2$ p-val", 
-                    "Enjoyment", "$\\chi^2$ p-val",
-                    "Happiness", "$\\chi^2$ p-val",
-                    "Safety", "$\\chi^2$ p-val",
-                    "Time", "$\\chi^2$ p-val",
-                    "Efficiency", "$\\chi^2$ p-val")) %>%
-  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
-  pack_rows("Age", 1, 3) %>%
-  pack_rows("Education", 4, 6) %>%
-  pack_rows("Income", 7, 9) %>%
-  pack_rows("Mode", 10, 13) %>%
-  pack_rows("Journey Time", 14, 17)  %>%
-  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
-  landscape()
-```
-
-```{r table-cross-tabulation-results-without-instrumental, echo = FALSE}
-kable(xtab_results,
-      "latex",
-      digits = 2,
-      booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
-      escape = FALSE,
-      align = c("l", rep("c", 12)),
-      col.names = c("Variable", 
-                    "Freedom", "$\\chi^2$ p-val", 
-                    "Enjoyment", "$\\chi^2$ p-val",
-                    "Happiness", "$\\chi^2$ p-val",
-                    "Poverty", "$\\chi^2$ p-val",
-                    "Luxury", "$\\chi^2$ p-val",
-                    "Status", "$\\chi^2$ p-val")) %>%
-  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
-  pack_rows("Age", 1, 3) %>%
-  pack_rows("Education", 4, 6) %>%
-  pack_rows("Income", 7, 9) %>%
-  pack_rows("Mode", 10, 13) %>%
-  pack_rows("Journey Time", 14, 17)  %>%
-  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
-  landscape()
-```
-
-Figure 5 shows the points of origin of the survey for the case of public transport users.
-Metro users as primary mode are shown, bus users are shown in cyan.
-The size of the points represents the number of dissonances.
-The higher the point, the greater the number of SWB factors that do not coincide with the primary transport mode.
-The image shows that the intensity or size of the circles is homogeneously distributed in the territory, even though the blue circles (metro) tend to show slightly less dissonance.
-The visualisation of this map is more dramatic when it is compared to the following Figure 6.
-
-Figure 6 shows the points of origin for the case of private transport (cars) and active transport (walking and cycling).
-Again, the size of the circles represents intensity levels of dissonance.
-The number of dissonances is lower than in the case of Figure 5, which indicates that users of private and active transport tend to use a mode of transport that they relate to one of the positive factors derived from subjective wellbeing.
-In this sense, it could be said that this type of user tends to be more advantaged than the public transport user, in a dimension not only utilitarian but also emotional and attitudinal.
-
-## Which modes do travelers associate with affective and instrumental values?
-
-Here we can visualize the modes that travellers associate with different affective and instrumental values.
-The tool we use for this is a mosaic plot.
-See the mosaic plots in Figure \ref{fig:mosaic-plots-by-attribute}.
-
-```{r figure-mosaic-plots-by-attribute-with-instrumental, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}
-
-ggplot(data = Modes_by_Attribute) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode selected for the value of {Freedom, Enjoyment, Happiness, Safety, Time, Efficiency}") +
-  ylab("Main mode of transportation") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_wrap(~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Poverty, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_wrap(~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-and-age-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(AGE ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-and-education-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(EDUCATION ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-and-income-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("POVERTY", "LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Poverty, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(INCOME ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-and-time-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by travel time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only affective values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS")) %>% drop_na(TRAVEL_TIME)) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Happiness, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(TRAVEL_TIME ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-Conclusions
-==========
+Table 1 shows that the low-income segment has a significantly higher
+percentage of cases of dissonance for two affective factors. In the case
+of Freedom, for example, the lack of correspondence for low-income is
+83.9\% compared to 60\% for the high-income segment. The levels of
+dissonance are higher for Enjoyment and follow the same decreasing trend
+for higher levels of income. Dissonance is marginally lower for
+instrumental factors, and significant for Security and Time Savings.
+
+As noted above, there are significant differences in dissonance by
+primary mode of travel, both for affective and instrumental factors. For
+affective factors, the highest levels of dissonance tend to be for users
+of public transportation, and the lowest for car users and active
+travellers. For instance, feelings of Freedom, Enjoyment, and Happiness
+are more frequently expressed by users of car and active travellers than
+users of public transportation. Indeed, people who travel by Metro or
+Bus almost never associate any of these positive affective attributes to
+these modes (dissonance is consistently greater than 90\%). In contrast,
+active travellers have some of the lowest levels of dissonance in all
+three affective factors, in particular Freedom and Happiness. This
+analysis is in line with previous research regarding car, active travel,
+and public transportation (e.g., Steg et al., 2001; Páez and Whalen,
+2010; Whalen et al., 2013), which tend to agree on the negative
+associations in the perception of affective factors when the primary
+mode is Metro or bus.
+
+Figure 4 shows the percentage of dissonance by primary transport mode,
+for both affective and instrumental factors. For instance, the graph at
+the top shows that the highest percentages of dissonances come from
+users of Metro and bus , compared to other modes as the car or active
+transport. This is consistent with previous studies that have separately
+demonstrated that public transport users tend to assess more negatively
+subjective factors (explored e.g.~in Stradling et al., 1999; Gatersleben
+and Uzzell, 2007). For example, although car users have higher
+dissonance values than active transport, comparatively this segment has
+much lower percentages of dissonances than public transport, idea also
+supported by research that has shown that car users tend to attribute
+importance to symbolic aspects that positively contribute to their
+perception on driving (Steg et al., 2001; Mokhtarian and Salomon, 2001).
+
+Freedom and happiness tend to have a lower percentage of dissonances in
+the case of active transport, which means that cyclists and individuals
+who mainly walk for their commutes, tend to associate positive
+subjective values while using these modes. This is also consistent with
+other studies that have shown positive affective associations with the
+use of cycling and walking (Anable and Gatersleben, 2005; Gatersleben
+and Uzzell, 2007). The question at the survey has not specify the
+dimensions of freedom, thus has open the door for different
+interpretations as the freedom to choose certain mode or route, freedom
+while using the mode, or the freedom to access to certain places while
+travelling. Journey time: As shown in Figure 3, the analysis carried out
+by journey time also reveals coincidences with previous research in this
+area, since for shorter trips (up to 20 minutes) the analysis shows less
+dissonance between the primary mode and positive subjective associations
+mainly for affective factors. On the contrary, as journey time
+increases, higher is the dissonance. Strangely, the feelings of Security
+and Efficiency have not been statistically representative for the
+Journey Time analysis.
+
+In terms of instrumental factors, interestingly Figure 4 shows that bus
+users have the lowest percentage of dissonance regarding time savings
+(29\%). However, considering the other instrumental factors, bus users
+have a high percentage of dissonance for security and efficiency. In the
+case of security, this means that most bus users (71\%) have considered
+the bus as a mode that they associate to time-savings, although it is
+the mode that has more dissonant evaluations in all other SWB factors.
+This also seems difficult to explain considering the negative evaluation
+that the Transantiago system has consistently had. Some data provided by
+the Survey of Satisfaction with Transantiago Operators (DTPM, 2017) is
+about users' perception of journey time from origin to destination. In
+this question, and after 10 years of implementation of the system, users
+diagnose an average journey of 47 minutes, a value that tends to
+increase with respect to the data delivered by the same survey 5 years
+before (43.5 minutes on average). Worryingly, long trips of more than 30
+minutes have had inconsistent variability over the years, reaching an
+average of more than 37 minutes in 2016. Short trips, however, remain
+roughly equal to previous years, and do not show significant changes in
+the average of 6-7 minutes per trip . This survey has the peculiarity of
+being developed by the Metropolitan Public Transport Board (DTPM), whose
+mission is to articulate the functions of the different modes of public
+transport with a specific interest in buses Transantiago and Metro de
+Santiago.
+
+Another big gap on these instrumental factors relates to the perception
+of security that is especially significant for car users. This means
+that a 75\% of car users have chosen as primary mode the same one as
+they relate to the feeling of security, which is completely opposite to
+other transport modes, specially bus users. Bus users have the highest
+dissonance (98\%), which means that practically all this group of users
+have chosen another mode for referring to the feelings of security. The
+recently referred DTPM survey does not have any particular question that
+addresses the issue of safety -- mostly related in this context as
+security.
+
+\begin{landscape}\begin{table}
+
+\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors}
+\centering
+\begin{tabular}[t]{lcccccccccccc}
+\toprule
+Variable & Freedom & $\chi^2$ p-val & Enjoyment & $\chi^2$ p-val & Happiness & $\chi^2$ p-val & Poverty & $\chi^2$ p-val & Luxury & $\chi^2$ p-val & Status & $\chi^2$ p-val\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{13}{l}{\textbf{Age}}\\
+\hspace{1em}< 35 & 89.88 &  & 94.33 &  & 93.52 &  & 87.63 &  & 89.43 &  & 87.17 & \\
+
+\hspace{1em}35 - 54 & 74.22 &  & 81.45 &  & 82.26 &  & 87.38 &  & 70.18 &  & 68.70 & \\
+
+> 54 & 74.00 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 72.92 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 68.75 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 76.19 & \multirow{-3}{*}{\centering\arraybackslash 0.4095} & 78.57 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 66.67 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$}\\
+\cmidrule{1-13}
+\addlinespace[0.3em]
+\multicolumn{13}{l}{\textbf{Education}}\\
+\hspace{1em}K-12 & 85.98 &  & 92.16 &  & 89.22 &  & 79.27 &  & 95.10 &  & 92.39 & \\
+
+\hspace{1em}Tech/Univ & 83.00 &  & 86.94 &  & 86.94 &  & 88.51 &  & 78.99 &  & 75.00 & \\
+
+Graduate & 78.57 & \multirow{-3}{*}{\centering\arraybackslash 0.9063} & 85.19 & \multirow{-3}{*}{\centering\arraybackslash 0.7005} & 84.62 & \multirow{-3}{*}{\centering\arraybackslash 0.9694} & 86.36 & \multirow{-3}{*}{\centering\arraybackslash 0.3608} & 76.00 & \multirow{-3}{*}{\centering\arraybackslash 0.0058} & 79.17 & \multirow{-3}{*}{\centering\arraybackslash 0.013}\\
+\cmidrule{1-13}
+\addlinespace[0.3em]
+\multicolumn{13}{l}{\textbf{Income}}\\
+\hspace{1em}Low & 86.51 &  & 82.11 &  & 88.62 &  & 80.19 &  & 88.71 &  & 88.70 & \\
+
+\hspace{1em}Middle & 84.52 &  & 89.80 &  & 88.00 &  & 83.76 &  & 85.82 &  & 80.00 & \\
+
+High & 79.19 & \multirow{-3}{*}{\centering\arraybackslash 0.5755} & 90.97 & \multirow{-3}{*}{\centering\arraybackslash 0.2264} & 85.82 & \multirow{-3}{*}{\centering\arraybackslash 0.9698} & 93.69 & \multirow{-3}{*}{\centering\arraybackslash 0.0642} & 73.68 & \multirow{-3}{*}{\centering\arraybackslash 0.0204} & 70.31 & \multirow{-3}{*}{\centering\arraybackslash 0.0137}\\
+\cmidrule{1-13}
+\addlinespace[0.3em]
+\multicolumn{13}{l}{\textbf{Mode}}\\
+\hspace{1em}Auto & 58.93 &  & 78.90 &  & 70.91 &  & 97.96 &  & 41.00 &  & 30.69 & \\
+
+\hspace{1em}Active & 46.34 &  & 60.98 &  & 57.89 &  & 75.76 &  & 89.47 &  & 81.82 & \\
+
+\hspace{1em}Public & 99.23 &  & 96.76 &  & 98.80 &  & 81.35 &  & 100.00 &  & 99.57 & \\
+
+Other & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $< 0.001$} & 86.96 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 93.33 & \multirow{-4}{*}{\centering\arraybackslash 0.0045} & 72.73 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 90.00 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$}\\
+\cmidrule{1-13}
+\addlinespace[0.3em]
+\multicolumn{13}{l}{\textbf{Journey Time}}\\
+\hspace{1em}< 20 min & 65.93 &  & 82.95 &  & 77.27 &  & 86.11 &  & 73.49 &  & 67.09 & \\
+
+\hspace{1em}20 - 40 min & 85.86 &  & 87.50 &  & 89.58 &  & 90.41 &  & 83.87 &  & 81.18 & \\
+
+\hspace{1em}40 - 60 min & 83.04 &  & 89.91 &  & 89.62 &  & 86.08 &  & 82.35 &  & 77.78 & \\
+
+> 60 min & 95.93 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 92.17 & \multirow{-4}{*}{\centering\arraybackslash 0.6115} & 93.28 & \multirow{-4}{*}{\centering\arraybackslash 0.0394} & 83.02 & \multirow{-4}{*}{\centering\arraybackslash 0.9225} & 91.15 & \multirow{-4}{*}{\centering\arraybackslash 0.0925} & 90.09 & \multirow{-4}{*}{\centering\arraybackslash 0.0158}\\
+\bottomrule
+\end{tabular}
+\end{table}
+\end{landscape}
+
+Figure 5 shows the points of origin of the survey for the case of public
+transport users. Metro users as primary mode are shown, bus users are
+shown in cyan. The size of the points represents the number of
+dissonances. The higher the point, the greater the number of SWB factors
+that do not coincide with the primary transport mode. The image shows
+that the intensity or size of the circles is homogeneously distributed
+in the territory, even though the blue circles (metro) tend to show
+slightly less dissonance. The visualisation of this map is more dramatic
+when it is compared to the following Figure 6.
+
+Figure 6 shows the points of origin for the case of private transport
+(cars) and active transport (walking and cycling). Again, the size of
+the circles represents intensity levels of dissonance. The number of
+dissonances is lower than in the case of Figure 5, which indicates that
+users of private and active transport tend to use a mode of transport
+that they relate to one of the positive factors derived from subjective
+wellbeing. In this sense, it could be said that this type of user tends
+to be more advantaged than the public transport user, in a dimension not
+only utilitarian but also emotional and attitudinal.
+
+\hypertarget{which-modes-do-travelers-associate-with-affective-and-instrumental-values}{%
+\subsection{Which modes do travelers associate with affective and
+instrumental
+values?}\label{which-modes-do-travelers-associate-with-affective-and-instrumental-values}}
+
+Here we can visualize the modes that travellers associate with different
+affective and instrumental values. The tool we use for this is a mosaic
+plot. See the mosaic plots in Figure
+\ref{fig:mosaic-plots-by-attribute}.
+
+\begin{figure}
+\centering
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-without-instrumental-1.pdf}
+\caption{\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective
+values; the y-axis is the proportion of respondents by main mode of
+transportation, and the x-axis is the proportion of modes selected for
+each value}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-age-without-instrumental-1.pdf}
+\caption{\label{fig:mosaic-plots-by-age}Mosaic plots for affective
+values by age; the y-axis is the proportion of respondents by main mode
+of transportation, and the x-axis is the proportion of modes selected
+for each value}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-education-without-instrumental-1.pdf}
+\caption{\label{fig:mosaic-plots-by-education}Mosaic plots for affective
+values by education; the y-axis is the proportion of respondents by main
+mode of transportation, and the x-axis is the proportion of modes
+selected for each value}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-income-without-instrumental-1.pdf}
+\caption{\label{fig:mosaic-plots-by-income}Mosaic plots for affective
+values by income; the y-axis is the proportion of respondents by main
+mode of transportation, and the x-axis is the proportion of modes
+selected for each value}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-time-without-instrumental-1.pdf}
+\caption{\label{fig:mosaic-plots-by-travel-time}Mosaic plots for
+affective values by travel time; the y-axis is the proportion of
+respondents by main mode of transportation, and the x-axis is the
+proportion of modes selected for each value}
+\end{figure}
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 
@@
 
-References {#references .unnumbered}
-==========
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\end{document}

### 2019-10-19 Dissonance_Santiago_v1.Rmd
Edited the abstract and updated the README.md file

@@
   Transportation in most of the world has been dominated for decades by a fascination with the automobile.
-Increasingly, however, it is recognized that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain users of public transport and active travel.
-A challenge with the way transportation policy is developed is that it tends to focus on cost-benefit and utilitarian considerations, which may miss other potential benefits of transportation.
-For this reason, subjective wellbeing (SWB) has been proposed as a way to enhance our understanding of the preferences and choices of travellers, as well as a way to evaluate the benefits of transportation beyond utilitarian considerations.
-The objective of this paper is to analyze the modes that people commonly use, and to what extent they are aligned (or not) with a variety of affective and utilitarian values.
+Increasingly, however, it is recognized that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain active travelers and users of public transportation.
+A challenge with the way transportation policy is developed is that it tends to focus on utilitarian considerations, which may miss other potential aspects of transportation that users value.
+In particular, subjective wellbeing (SWB) has been proposed as a way to enhance our understanding of the preferences and choices of travellers, as well as a way to evaluate the benefits of transportation beyond utilitarian considerations.
+The objective of this paper is to analyze the modes that people commonly use, and to what extent they are aligned (or not) with a variety of affective values associated with SWB.
 In other words, we are interested in the potential for dissonance with respect to the primary mode of travel, from the perspective of affective and utilitarian values.
 The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
-Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associated to affective values (freedom, enjoyment, and happiness) and to utilitarian values (safety, time waste, and efficiency).
+Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associated to affective values freedom, enjoyment, happiness, poverty, luxury and status.
 The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with affective values.
-
-  To properly assess transportation policy This poses a number of challenges Broadening the commonly used transport project assessment will be relevant for achieving this goal.
-While satisfaction with travel has been mainly used in the context of daily trips and mainly under cost-benefit and utilitarian considerations, subjective wellbeing (SWB) over time has risen as an alternative for understanding the preferences and choices of transport users.
-The aim of this paper is to analyse the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
-The paper aims to reflect on the possibilities of increasing the SWB with a view to enhance the attractiveness of public transport and active travel.
-The paper investigates the affective and instrumental/utilitarian factors of SWB, according to modal choice.
-It uses an analysis of correspondence that considers the actual primary mode used, versus the mode that each individual associated to both utilitarian and affective SWB factors.
-The results show that there is more persistent modal dissonance between positive emotional and utilitarian associations within the more disadvantaged groups – particularly among users of public transport.
-The study shows that apart from time-savings and efficiency, security has also been cross-sectionally sensitive according to the data analysed.
-Factors such as happiness, enjoyment and freedom require far more attention in transport planning as they are strongly related to the dimensions of subjective and personal wellbeing.
-Targeting these factors will be relevant for attracting new users to public transportation and active travel.
+For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
 
@@
 # - WEIGHT_*: A weight for the responses by ATTRIBUTE.
-Some respondents selected more than one mode that they associated with feelings of {FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, and EFFICIENCY}.
+Some respondents selected more than one mode that they associated with feelings of {FREEDOM, ENJOYMENT, HAPPINESS, POVERTY, LUXURY, STATUS, SAFETY, TIME, and EFFICIENCY}.
 To avoid giving greater weight to respondents who indicated several modes of transportation, a weight was calculated that is the inverse of the number of modes indicated.
@@
 # 
-# The modes of transportation (USED, FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, EFFICIENCY) are coded as: 
+# The modes of transportation (USED, FREEDOM, ENJOYMENT, HAPPINESS, POVERTY, LUXURY, STATUS, SAFETY, TIME, EFFICIENCY) are coded as: 
 # "A": Auto

### 2019-10-21 Dissonance_Santiago_v1.Rmd
Worked on Analysis and Results, included Cochran-Mantel-Haenszel Chi-Squared Test for 3-way tables

@@
 ---
-title: Do Drivers Dream of Walking? An Investigation of Dissonance in the Primary Mode of Travel from the Perspective of Subjective Wellbeing
+title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing
 author:
@@
   Transportation in most of the world has been dominated for decades by a fascination with the automobile.
-Increasingly, however, it is recognized that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain active travelers and users of public transportation.
-A challenge with the way transportation policy is developed is that it tends to focus on utilitarian considerations, which may miss other potential aspects of transportation that users value.
+Nonetheless, there is an increasing recognition that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain active travelers and users of public transportation.
+A challenge with the way transportation policy is developed, however, is that it tends to focus on utilitarian considerations, which may miss other potential aspects of transportation that users value.
 In particular, subjective wellbeing (SWB) has been proposed as a way to enhance our understanding of the preferences and choices of travellers, as well as a way to evaluate the benefits of transportation beyond utilitarian considerations.
 The objective of this paper is to analyze the modes that people commonly use, and to what extent they are aligned (or not) with a variety of affective values associated with SWB.
-In other words, we are interested in the potential for dissonance with respect to the primary mode of travel, from the perspective of affective and utilitarian values.
+In other words, we are interested in the potential for dissonance with respect to the primary mode of travel, from the perspective of affective values.
 The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
-Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associated to affective values freedom, enjoyment, happiness, poverty, luxury and status.
+Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associate with the affective values of freedom, enjoyment, happiness, poverty, luxury and status.
 The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
@@
 library(kableExtra)
+library(gridExtra)
 ```
@@
 # The modes of transportation (USED, FREEDOM, ENJOYMENT, HAPPINESS, POVERTY, LUXURY, STATUS, SAFETY, TIME, EFFICIENCY) are coded as: 
-# "A": Auto
+# "A": Car
 # "B": Taxi
@@
 #
-# 1.
-Analysis of dissonace using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.).
+# 1. Who experiences dissonace?
+#
+# Analysis of dissonace using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.).
 In this case, dissonance is defined as follows:
@@
 FREEDOM et al.), we consider that there is no dissonance; otherwise, we consider that there is dissonance.
-For example, if the respondent's main mode of transportation is Auto, and the respondent associates Auto with feelings of FREEDOM, then there is no dissonance.
-On the other hand, if the respondent's main mode of transportation is Auto, but associates Walking with feelings of FREEDOM, there is dissonance.
+For example, if the respondent's main mode of transportation is Car, and the respondent associates Car with feelings of FREEDOM, then there is no dissonance.
+On the other hand, if the respondent's main mode of transportation is Car, but associates Walking with feelings of FREEDOM, there is dissonance.
 # 
@@
 #
-# 2.
-Analysis of dissonance using the mode USED and the mode respondents associated with ATTRIBUTE, then stratified by characteristics of respondents (i.e., AGE et al.) in this case, we see how frequently each mode was associated with ATTRIBUTE, given the main mode of transportation of the respondents.
+# 2. For those respondents who experience dissonance, what mode(s) are better aligned with various affective values
+#
+# Analysis of dissonance using the mode USED and the mode respondents associated with ATTRIBUTE, then stratified by characteristics of respondents (i.e., AGE et al.) in this case, we see how frequently each mode was associated with ATTRIBUTE, given the main mode of transportation of the respondents.
 #
@@
 
-#################################################################################
-# Prepare a dataframe for the analysis of dissonance by attribute (Analysis 1.) #
-#################################################################################
+#####################################################################################
+# Prepare a dataframe for Analysis 1: Who experiences dissonance by affective value #
+#####################################################################################
 
@@
 Overall_dissonance <- Overall_dissonance %>%
-  mutate(USED = case_when(USED == "A" ~ "Auto",
+  mutate(USED = case_when(USED == "A" ~ "Car",
                                   USED == "B" | USED == "C" | USED == "D" ~ "Other",
@@
                                  TRAVEL_TIME == "D" ~ "> 60 min")) %>%
-  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
+  mutate(USED = factor(USED, levels = c("Car", "Active", "Public", "Other"), labels = c("Car", "Active", "Public", "Other")),
          FREEDOM_DISSONANCE = factor(FREEDOM_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
@@
 
-#############################################################################
-# Prepare a dataframe for the analysis of dissonance by modes (Analysis 2.) #
-#############################################################################
+###############################################################################################
+# Prepare a dataframe for Analysis 2: What mode(s) align better with various affective values #
+###############################################################################################
 
@@
 Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = case_when(USED == "A" ~ "Auto",
+  mutate(USED = case_when(USED == "A" ~ "Car",
                                   USED == "B" | USED == "C" | USED == "D" ~ "Other",
@@
                                   USED == "G" | USED == "H" ~ "Active"),
-         IDEAL = case_when(IDEAL == "A" ~ "Auto",
+         IDEAL = case_when(IDEAL == "A" ~ "Car",
                                   IDEAL == "B" | IDEAL == "C" | IDEAL == "D" ~ "Other",
@@
 Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
-         IDEAL = factor(IDEAL, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
+  mutate(USED = factor(USED, levels = c("Car", "Active", "Public", "Other"), labels = c("Car", "Active", "Public", "Other")),
+         IDEAL = factor(IDEAL, levels = c("Car", "Active", "Public", "Other"), labels = c("Car", "Active", "Public", "Other")),
          AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
@@
 
-Introduction
+1. Introduction
 ==========================
@@
 Transportation planning for decades has focused on providing mobility for the private automobile.
-This is a model of development that was initially introduced in North America as a solution to urbanizations problems, and that was eventually copied elsewhere (Brown et al., 2009; Angotti, 1996) .
+This is a model of development that was initially introduced in North America as a solution to problems created by rapid urbanization, and that was eventually copied elsewhere [@Brown2009planning;@Angotti1996latin].
 Despite the initial promise of automotive technology, it is now evident that mobility centred on the private automobile has given rise to a litany of maladies that are in urgent need of correction.
-This includes environmental concerns (i.e., climate change; Chapman, 2007) as well as other social (Boschmann and Kwan, 2008), health (Khreis et al., 2016), and equity issues (Bocarejo and Oviedo, 2012).
-As the real impacts of our societal dependence on the private autombobile have become increasingly evident, the transportation agenda has in recent years aimed to shift focus to the reduction of car-use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives than just the private automobile (Miller, 2011) .
-In order to successfully achieve this goal, it is essential not only to provide the services and facilities that support public transportation and active travel, but also to attract new users to these modes of transportation (Ettema et al.
-2011).
-Within this context, it has been argued that sustainable transportation policies require all participants in the transportation system to challenge what Gossling and Cohen (2014) term “transportation taboos”: deep-seated ideas concerning the contribution to emissions by individuals, the inequality of market-based approaches, and the social and psychological functions of transportation.
-With respect to the latter, moving beyond a purely utilitarian focus, it is important to understand how users perceive affective and instrumental elements on their transportation experience, since this can help to incorporate adequate improvements in alternative transportation, including transit and active modes, to make them more attractive to users (Anable and Gatersleben, 2005; Domarchi et al., 2008; Gatersleben and Uzzell, 2007; Steg 2005 ).
-
-A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing (SWB.
-See, inter alia, De Vos et al., 2013 and Chatterjee et al., 2019) .
-SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” (OECD, 2013, p.
-10).
-Accordingly, the aim of this paper is to analyse some of the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
-Previous research suggests that public transport users experience a negative gap in desired and actual travel time, whereas active travellers don’t seem to mind somewhat longer trips than what strictly needed (e.g., Páez and Whalen, 2010).
-In the context of a Latin American country, historically the poor travel experience of public transit users and active travellers reflects the social inequalities of social groups that have no alternative but to move in these types of modes while living far from the work centres and main activities.
-The paper aims to reflect on the possibilities of increasing the SWB while travelling, and how this could increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
-This can help not only to reduce the use of private transport but also decrease the inequality gap between these users.
-
-The paper explores how positive affective and instrumental/utilitarian factors of SWB correspond to the use of the primary mode of transportation.
-It uses an analysis of correspondence that considers the actual primary mode versus the mode that individuals associated to both utilitarian (designed to be useful or practical rather than attractive) and affective (expressing a person's feelings) SWB factors.
-For example, it will be analysed if a person who uses public transport as the primary mode, tends to associate these modes with positive affective factors (as freedom, enjoyment or happiness) or positive utilitarian factors (as security, time-savings or efficiency).
-We hypothesize that there is a more persistent non-correspondence or mismatch within the more disadvantage groups or within the users of public transport.
-
-The paper contributes to the literature in three areas.
-First, it contributes to an emerging literature on the topic in the context of the Global South (Bejarano et al., 2017 ; Shao and Liang, 2019 ; Van et al., 2014 ; Zorrilla et al., 2019);  to the best of our knowledge, the case of Chile has not yet been reported.
-Second, although there is literature on the enjoyment of commute and other emotional factors, from a hedonic and even eudaimonic perspectives, the analysis has yet to be applied more fully in terms of distributional issues – i.e.
-which groups are mostly disadvantaged.
-Finally, the analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’ – implying their preferences, even in situations when their ideal mode is not part of their actual choice set.
-The attitudes of travellers towards transport modes are critical factors to be considered by policy-makers in case they want to promote and increase the use of public transport or active modes (e.g., Bejarano et al., 2019).
-The paper explores these positive and negative associations within the transport options used in Santiago.
-
-Background
+This includes environmental concerns [i.e., climate change; @Chapman2007transport] as well as numerous other social [@Boschman2008toward; @Lucas2012transport; @Lucas2019evolution], health [@Khreis2016health; @Milne2012public], and equity issues [@Bocarejo2012transport; @Martens2012justice; @Pereira2017distributive].
+
+As the real impacts of our societal dependence on the private autombobile have become increasingly evident, the transportation agenda has aimed to shift focus to the reduction of car use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives than primarily (or even just) the private automobile [@Miller2011collaborative].
+In order to successfully achieve this goal, it is essential not only to provide the services and facilities that support public transportation and active travel, but also to attract new users to these modes of transportation [@Ettema2011satisfaction].
+Within this context, it has been argued that sustainable transportation policies require all participants in the transportation system to challenge what Gossling and Cohen [-@Gossling2014sustainable] termed _transportation taboos_: deep-seated ideas concerning the contribution to emissions by individuals, the inequality of market-based approaches, and the social and psychological functions of transportation.
+With respect to the latter, it is important to move beyond a purely utilitarian focus if we are to understand how the affective value of the transportation experience can be leveraged to improve alternative transportation - particularly transit and active modes [@Anable2005work; @Domarchi2008effect; @Gatersleben2007affective; @Steg2005car].
+
+A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing [SWB; see, inter alia, @Devos2013travel; and @Chatterjee2019commuting].
+SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” (**OECD, 2013, p.
+10**).
+As memorably put by Steg [-@Steg2005car]: is the use of car a must, or is it a lust?
+A close alignment, or consonance, between affective values and the mode of transportation used to travel can result in greater subjective wellbeing and increase the probability of choosing that mode  (i.e., by satisfying the _lust_); on the other hand, dissonance, that is, the lack of concordance between the mode used and affective values would be detrimental to subjective wellbeing, especially of those for whom the use of the mode is a _must_ [@Devos2019satisfaction; @Mokhtarian2018travel].
+With these considerations in mind, one aim of the present research is to investigate _who_ experiences dissonance with respect to their primary mode of travel and affective values, namely freedom, enjoyment, happiness, feelings of poverty, luxury, and status.
+Furthermore, it is possible, even if use of a particular mode is a _must_, that travellers may still _lust_ for something else - in other words, the grass may in fact look greener from the window of the car.
+For this reason, we also aim to investigate which mode or modes are most commonly associated with affective values, with a focus on those travellers who experience dissonance in their primary mode.
+
+Research is based on data collected from a sample of travellers in the city of Santiago in Chile.
+Survey respondents were asked about their primary mode of travel, and also about the mode or modes that they associate with the affective values mentioned above.
+The paper contributes to the literature in three ways, as follows:
+
+1.
+The research reported here contributes to an emerging literature on the topic of transportation and affective values in the context of the Global South [@Alayyash2019commute; @Bejarano2017user; @Shao2019analysis; @Van2014effect; @Zorrilla2019exploring]; to the best of our knowledge, the case of Chile has not yet been reported.
+
+2.
+Although there is an extensive literature on the enjoyment of commute and other affective values [see for instance @Paez2010enjoyment; @Redmond2001positive; @Whalen2013mode; @Ye2017satisfaction], from a hedonic and even eudaimonic perspectives the analysis has yet to be applied more fully in terms of distributional issues – i.e.
+which groups more commonly experience dissonance [see @Devos2018people].
+
+3.
+The analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’ – implying their preferences, even in situations when their ideal mode is not part of their actual choice set.
+More concretely, the results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
+For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
+We also find that there are some substantial variations in dissonance by age, education, income, and typical commute time.
+The attitudes of travellers towards transport modes are critical factors to be considered by policy-makers in case they want to promote and increase the use of public transport or active modes [@Bornioli2019affective; @Devos2017travel; @Devos2019satisfying; @Garling2019role; @Redman2013quality].
+
+2. Background
 ============
 
-The transportation community has for the most part already agreed to the need of looking at mobility and transport issues from the lens of wellbeing, to broaden the commonly used utilitarian perspective to evaluate projects.
-Users’ travel satisfaction (Bergstad, 2001) has been the primary way to direct this challenge towards everyday mobility, resulting on research about satisfaction with different transport modes.
-For example, numerous studies report that car users have a higher level of satisfaction compared to other transport modes (Redmond and Mokhtarian, 2001 ; Bergstad et al.
-2011; Eriksson et al.
-2013; Whalen et al., 2013).
-In a similar way, there are multiple reports that active travel also tends to yield high levels of satisfaction (Smith, 2017; St-Louis et al.
-2014; Paez and Whalen, 2010; Whalen et al., 2013), In contrast, public transport users tend to assess their experience more negatively (De Vos et al.
-2016; Abenoza et al.
-2017; Ettema et al.
-2012; Páez and Whalen, 2010).
-Multi-modal trips also influence satisfaction levels; for instance, when an individual chooses a particular mode of transportation, she will report a higher level of satisfaction with that chosen mode – perhaps as a form of post hoc validation (Susilo and Cats, 2014).
-
-While the use of travel satisfaction has been mainly used in the context of daily trips – typically been linked to cost-benefit and utilitarian measurements –, the evaluation of Subjective Wellbeing (SWB) over time has risen as an alternative measure.
+A consensus has emerged in the transportation community regarding the need to complement the traditional utilitarian perspective of transportation by looking at mobility and transport issues from the lens of their affective functions.
+The affective value of transportation in turn is important due to its potential to improve or detract from SWB.
+One of the primary ways to explore this has been the satisfaction that travelers feel towards their every day mobility experience [e.g., @Bergstad2011subjective].
+As a consequence, there is a wealth of research on satisfaction with the use of different modes of transportation.
+For example, numerous studies report that car users often have a higher level of satisfaction compared to other transport modes [@Bergstad2011affective; @Eriksson2013perceived; @Redmond2001positive; @Whalen2013mode; but see @Handy2019commute].
+In a similar way, there are multiple reports that active travel also tends to yield high levels of satisfaction [@Gatersleben2007affective; @Smith2017commute; @Stlouis2014happy; @Paez2010enjoyment; @Whalen2013mode; @Handy2019commute], In contrast, public transport users tend to assess their experience more negatively [@Abenoza2017travel; @Devos2016travel; @Gatersleben2007affective; @Handy2019commute; @Paez2010enjoyment].
+Multi-modal trips also influence satisfaction levels; for instance, when an individual chooses a particular mode of transportation, she will report a higher level of satisfaction with that chosen mode – perhaps as a form of _post hoc_ validation [@Susilo2014exploring].
+
+While the use of travel satisfaction has been mainly used in the context of daily trips – typically linked to cost-benefit and utilitarian measurements –, the evaluation of Subjective Wellbeing (SWB) over time has risen as an alternative measure.
 In the field of travel behaviour, Ettema et al.
-(2010; p.
-725) have defined SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporality – which implies assuming a tendency to be more stable over time.
+[-@Ettema2010out, p.
+725] define SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporality – which implies assuming a tendency to be more stable over time.
 This concept has prompted a growing literature that complements and applies SWB in a broader range of satisfaction scales and situations.
-The definition of other factors such as travel choice mode, attitudes and external elements of the built environment has been studied for a broader understanding of the changes produced in the SWB.
-As these factors do not necessarily apply to the general life satisfaction on the long term, the studies have aimed to determine both the direct and indirect effects on the perception of users (see, e.g.
-Ye and Titheridge 2017).
+The definition of other factors such as travel choice mode, attitudes and external elements of the built environment have been studied for a broader understanding of the changes produced in the SWB [e.g., @Handy2019commute].
+As these factors do not necessarily apply to the general life satisfaction on the long term, the studies have aimed to determine both the direct and indirect effects on the perception of users [see, e.g., @Ye2017satisfaction].
 Other concepts have also emerged as the Satisfaction with Travel Scale (STS), a measurement devised by Ettema et al.
-(2011) as well as different scales based on people’s travel perceptions.
+[-@Ettema2011satisfaction], as well as different scales based on people’s travel perceptions.
 De Vos et al.
-(2015) for instance, explore in detail the underlying dimensions of the affective domain of STS in which SWB is based (for more on STS see also Friman et al.
-2013).
-
-Recent literature on SWB and its link with transport have demonstrated a relationship between people’s perceptions and satisfaction with their daily travel (Smith, 2017; St-Louis et al.
-2014; Paez and Whalen, 2010; Whalen et al., 2013).
-Scholars have shown that accessibility has been the most developed factor that influences people’s wellbeing (Delbosc, 2012), and activities have a direct impact on travel satisfaction (Bergstad et al., 2010).
-Delbosc (2012; 28) for instance, has summarised the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.
-However, understanding the components affecting people’s perceptions implies the differentiation between the emotional (also named as symbolic-affective) and the instrumental reasons (Bergstad, 2001).
+[-@Devos2015satisfying], for instance, explore in detail the underlying dimensions of the affective domain of STS on which SWB is based [for more on STS see also @Friman2013psychometric].
+
+Recent literature on SWB and its link with transport have demonstrated a relationship between people’s perceptions and satisfaction with their daily travel [e.g., @Smith2017commute; @Stlouis2014happy; @Mokhtarian2018travel].
+Scholars have shown that accessibility has been the most developed factor that influences people’s wellbeing [@Delbosc2012role], and activities have a direct impact on travel satisfaction [@Bergstad2011subjective].
+Delbosc [-@Delbosc2012role, p.
+28], for instance, has summarised the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.
+However, understanding the components affecting people’s perceptions implies the differentiation between affective (also named as symbolic-affective) and instrumental values [@Bergstad2011affective].
 Steg et al.
-(2011) have compared symbolic-affective opposed to instrumental-reasoned motives based on car-use, and other studies have also found associations between affective and symbolic aspects of car-use (see, e.g.
-Gatersleben, 2007; Lois & López-Sáez, 2009).
-Previous studies have demonstrated how socio-demographic factors affect the levels of SWB.
-The effect of income on SWB (Clarck and Oswald, 1996, Ferrer-i-Carbonell, 2005); education and unemployment (Argyle, 1999); age (Diener and Suh, 1997) and gender (Tesch-Römer et al., 2008) have already been studied.
-Recent research also suggests the links between commuting, SWB and emotional wellbeing assessment (Olson et al.
-2013; Kahneman et al.
-2004).
-However, more research is needed to understand how these socio-demographic variables, connect as well with the decisions on main transport mode choices; or research distinguishing between hedonic (journey experience) and eudaimonic (flourishing) value of trips.
-
-The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel (Zorrilla et al., 2019).
+(2011) have compared symbolic-affective opposed to instrumental-reasoned motives based on car-use, and other studies have also found associations between affective and symbolic aspects of car-use [see, e.g., @Gatersleben2007affective; @Lois2009relationship].
+Previous studies have also demonstrated how socio-demographic factors affect the levels of SWB.
+The effect of income on SWB [@Clark1996satisfaction; @Ferrer2005income]; education and unemployment [@Argyle1999causes]; age [@Diener1997subjective], and gender [@Tesch2008gender] have been extensively studied.
+Recent research also suggests the links between commuting, SWB and emotional wellbeing assessment (**Olson et al.
+2013**; **Kahneman et al.
+2004**).
+However, more research is needed to understand how these socio-demographic variables connect as well with the affective responses to mode of travel [@Stlouis2014happy].
+
+The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel [@Zorrilla2019exploring].
 In this way, there is an emerging literature that investigates affective factors in travel behaviour in a number of developing countries.
-A cross-country study in Asia revealed that the affective factors of public transportation and car use are important, and in particular the social orderliness of transit was suggested as a way to make this mode more attractive to users (Van et al., 2014).
-In terms of active travel, a study in China found that attitudes that embrace new styles and technologies despite their cost are associated with the intention to continue using shared bicycles (Shao and Liang, 2019).
-The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows how users felt proud using a bicycle shared system, in addition to experiencing feelings of belonging to a civic culture and the enjoyment and pleasure of travel itself (Bejarano et al., 2019).
-This paper contributes to further our understanding of affective and instrumental factors in travel behaviour in a developing country.
-
-Data and Methods
+A cross-country study in Asia revealed that the affective factors of public transportation and car use are important, and in particular the social orderliness of transit was suggested as a way to make this mode more attractive to users [@Van2014effect].
+In terms of active travel, a study in China found that attitudes that embrace new styles and technologies despite their cost are associated with the intention to continue using shared bicycles [@Shao2019analysis].
+The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows how users felt proud using a bicycle shared system, in addition to experiencing feelings of belonging to a civic culture and the enjoyment and pleasure of travel itself [@Bejarano2017user].
+This paper contributes to further our understanding of affective values in travel behaviour in a developing country.
+
+3. Data and Methods
 ===================
 
-This paper implements an analysis of correspondence comparing the primary mode of transportation with affective and utilitarian SWB factors in a sample of travellers in Santiago de Chile.
-
-## Sample
-
-The study is based on a survey conducted in Santiago during the months of November and December 2016, that collected information on a wide range of travel and related issues.
+# 3.1 Context
+
+Words to describe Santiago go here.
+
+# 3.2 Sample
+
+The study is based on a survey conducted in the city of Santiago during the months of November and December 2016, that is, the end of the Spring and beginning of Summer.
+The survey collected information on a wide range of travel and related issues.
 The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
-An equal representation of both genders and a representation of the proportion of inhabitants per area have been chosen as relevant characteristics of the sample.
-In total, 451 persons validly completed the survey.
-In the first part of the questionnaire the participants were asked about basic socio-demographic data and main transport mode for commuting.
-In the second part, the questionnaire asked about the modes that people associate with affective and instrumental positive concepts of commuting, as well as the levels of overall satisfaction with the trips.
-These two sections of the survey have been considered for the analysis of this paper.
-The second part of the survey asked about the association between the primary transport mode and 18 positive and negative feelings.
-The question is: “Indicate the modes that you associate to the following feelings”.
-The respondents could indicate all the modes they associated to the feelings on the list.
-Three affective and three instrumental/utilitarian factors, all positive, have been considered for this analysis: freedom, enjoyment, happiness (affective), and security, time savings, efficiency (instrumental/utilitarian).
-The questionnaire provides a binary indicator that describes the presence or absence of modal correspondence for each one the selected six factors.
-The analysis has considered socioeconomic variables (gender, age, education, occupation, income, disabilities), as well as other variables as driving licence, journey times, monthly expenditure on transport and satisfaction with the overall trip.
-
-[REPORT DESCRIPTIVE STATISTICS?
-Include definitions, e.g., is K-12 equivalent to “minimal mandatory education”?
-What is Tech Univ?
-What are the range of values of low, middle, high income?
-Journey time is in minutes]
-
-## Analytical Approach
-
-The analytical approach in this paper is based on correspondence.
-Previous research has developed the concept of modal dissonance for referring to the mismatch between the actual mode and the mode that enables users to experience positive affective or instrumental factors (De Vos et al., (2012; 2014) and Schwanen and Mokhtarian, 2004, 2005a, 2005b).
-More concretely, Schwanen and Mokhtarian (2004; 89) define dissonance based on the incongruence between residential neighbourhood where the individual currently resides and her preference structure toward such characteristics of the residential environment.
-In this paper we consider correspondence, which happens when travellers associate the positive utilitarian and affective SWB factors to the mode they have used as their primary transport mode for commuting or performing their main activities.
-The opposite of correspondence would be modal dissonance.
-
-More specifically, the concept of modal dissonance means that a user of mode X identifies a different mode Y when associating affective values.
-For example, a user of private transport (i.e., mode “Car”)  may select mode “Bicycle” when asked about the of the association between the concept of freedom to a transport mode.
-In this case, the person who uses the mode “Car” as their primary mode of transportation attaches positive emotional and instrumental factors not to that mode, but to a different one – in this case to the bicycle.
-It could be the case that the modal dissonance corresponds just to one of the types of factors, either affective or instrumental.
-For example, it is possible that a person who uses the Metro as their main transport mode associates that mode to the instrumental factors (security, time savings, efficiency) – but relates positive emotional factors (freedom, enjoyment, happiness) to a different mode, say to the bicycle.
-
-The ways for measuring equity in transport projects and the most vulnerable groups affected by transport have been the aspects that have nurtured the focus of this study.
-The hypothesis is that public transport users will show a lower correspondence between their primary mode and the modes they relate with positive factors of SWB.
-This is relevant as more disadvantaged people have less options of choosing their preferred transport modes and they tend to associate positive affective and instrumental factors to modes that they are not able to use.
-These perceptions evidence equity gaps between groups – where the most vulnerable groups are much more affected.
-The methods used are analysis of correspondence and multinomial regression, both around the associations of transport modes and affective and instrumental factors, derived from the SWB framework.
-
-Results
+An equal representation of both genders and a representation of the proportion of inhabitants per area were chosen as relevant characteristics of the sample.
+In total, there were $n=451$ valid surveys, although not every survey was complete and there were missing responses for some answers.
+
+The survey was structured in eight sections, as follows: 1) Individual characteristics of respondent; 2) Health; 3) Feelings and emotions; 4) Reasons for travel and planning travel; 5) Social interaction; 6) Nature and sustainability; 7) Information and telecommunications; 8) Built environment; and 9) Commuting.
+For the present study, we draw data from sections 1), 3) and 9).
+In terms of individual characteristics of the respondents and their commute, participants were asked about basic socio-demographic information, including age, level of education, income, and the typical duration of their regular commute.
+The descriptive statistics of the sample appear in Figure \ref{fig:descriptive-statistics}.
+The sample tends to be younger, and well-educated, with an almost uniform distribution of income levels.
+The trend in typical commute time is towards longer commutes.
+
+```{r plot-descriptive-statistics, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:descriptive-statistics}Descriptive statistics of the sample"}
+
+# Bar plots with descriptive statistics for the sample
+
+age_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = AGE)) +
+  geom_bar() +
+  theme_tufte() +
+  xlab("Age of respondents") +
+  theme(axis.text.x = element_text(angle = 90))
+
+education_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = EDUCATION)) +
+  geom_bar() +
+  theme_tufte() +
+  xlab("Education level of respondents") +
+  theme(axis.text.x = element_text(angle = 90))
+
+income_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = INCOME)) +
+  geom_bar() +
+  theme_tufte() +
+  xlab("Income level of respondents") +
+  theme(axis.text.x = element_text(angle = 90))
+
+time_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = TRAVEL_TIME)) +
+  geom_bar() +
+  theme_tufte() +
+  xlab("Duration of regular commute") +
+  theme(axis.text.x = element_text(angle = 90))
+
+grid.arrange(age_plot, education_plot, income_plot, time_plot)
+```
+
+In addition, respondents were asked about their primary mode of travel for their regular commute.
+The modes available were Car, Taxi, Colectivo (a form of shared ride, intermediate in flexibility and capacity between taxi and bus); Motorcycle; Metro; Bus; Bicycle; Walking.
+As seen in the top panel of Figure \ref{fig:primary-mode-travel}, the three most common modes of travel are Metro, Bus, and Car, followed by Walking and Biycle.
+For the analysis, we aggregate these modes into the following categories (bottom panel of Figure \ref{fig:primary-mode-travel}): Car, Active (Walking + Bicycle), Public (Metro + Bus), and Other (Taxi + Colectivo + Motorcycle).
+
+```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
+mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "B", "C", "D", "E", "F", "G", "H"),
+                                     labels = c("Car", "Taxi", "Colectivo", "Motorcycle", "Metro", "Bus", "Bicycle", "Walk")))) +
+  geom_bar() +
+  xlab("Primary Mode of Travel") +
+  theme_tufte() +
+  theme(axis.text.x = element_text(angle = 90))
+
+mode_plot2 <- ggplot(data = Overall_dissonance, aes(x = USED)) +
+  geom_bar() +
+  xlab("Primary Mode of Travel") +
+  theme_tufte() +
+  theme(axis.text.x = element_text(angle = 90))
+
+grid.arrange(mode_plot1, mode_plot2, nrow = 2)
+```
+
+Of particular interest for the present study is the following question in Part 3) of the survey:
+
+>> Q: Please indicate the mode(s) of transport that you relate to the following feelings and concepts
+
+The question was asked for each of the following affective values: Freedom; Enjoyment; Happiness; Poverty; Luxury; and Status.
+The respondents were not constrained to select only one alternative, but could indicate by means of a checkbox any and all modes that they felt aligned with each affective value.
+This allows us to do an analysis of modal dissonance, a concept introduced into the transportation literature by Schwanen and Mokhtarian [-@Schwanen2004extent] based on earlier work by Feldman [-@Feldman1990settlement].
+Residential neighborhood-type dissonance was defined by Schwanen and Mokhtarian [-@Schwanen2004extent] as an incongruence in terms of the the land use patterns at the place of residence of an individual, and the individual's preferences.
+The concept of dissonance has since been extended in the travel behavior literature to encompass the mismatch between the choices individuals make, and the alternatives that would enable users to experience affective or instrumental values.
+This includes, for example, travel mode dissonance [@Devos2018people].
+
+Based on the primary mode of travel and the questions about affective values, we derived a series of travel mode dissonance variables according to the following rule:
+$$
+D_i = 
+\begin{cases}
+0 & if \text{ primary mode} = \text{mode associated with value } i\\
+1 & \text{ otherwise}
+\end{cases}
+$$
+Therefore, if a respondent's primary mode of travel is Car, but indicated any other mode or modes in relation to Freedom, the respondent experienced dissonance:
+$$
+D_{\text{Freedom}} = 1
+$$
+
+Furthermore, we also expanded the responses to account for all modes identified by respondents in relation to the affective values.
+However, to avoid double counting the respondents in our frequency tabulations, we also calculated a sample weight that was the inverse of the number of modes selected in response to each affective value.
+For instance, if a respondent selected two modes in relation to affective value $i$, the two modes receive a weight of $1/2$; if a respondent selected three modes, then their weights are $1/3$; and so on.
+In this way we do not treat unfairly those who selected only one mode, and the sum of all weighted modes is equal to the sample size.
+
+4. Analysis and Results
 ==========
+
+In what follows, analysis is done on two related but distinct questions.
+The first part of the analysis seeks to understand _who_ experiences dissonance, and the second part, building off that, aims to explore which modes of travel are more commonly identified as embodying affective values by those travellers who experience dissonance.
+
+Please note that this document was prepared using R Markdown and contains reproducible analysis.
+The R markdown file, along with the data file needed to reproduce the analysis, can be downloaded from the following anonymous Drive folder:
+
+https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg
 
@@
 
-xtab_results[10:13, 3] <- "$< 0.001$"
+xtab_results[10:13, 3] <- "$< 0.001$" # Edit the format of these cells to avoid six cells collapsing together in table
 ```
@@
 
-xtab_results[10:13, 3] <- "$< 0.001$"
+xtab_results[10:13, 3] <- "$< 0.001$" # Edit the format of these cells to avoid six cells collapsing together in table
 ```
 
-## Who experiences dissonance?
-
-The first step of the analysis seeks to understand whether there are statistical associations between the variables of interest.
-The analysis considers the cases where there is a lack of correspondence between the primary mode choice and the 6 SWB/instrumental factors previously described  – or in other words, where there is modal dissonance.
-
-Table 1 shows the results of the analysis of correspondence and the dissonances between the primary mode of travel on the one hand, and SWB and instrumental factors on the other.
-As seen in the table, there are five categories that we use for the analysis.
-Three of these categories are socio-economic and demographic, namely age, level of education, income.
-The other two categories are transportation related, namely primary mode of travel and journey time.
-Correspondence is tested in every case by means of the $\chi^2$ statistic.
-It is interesting to note that the only category for which all affective/instrumental factors are significant at better than 5% level of confidence is mode of travel.
-
-With respect to age, we observe that levels of dissonance tend to be high in general, and the results indicate that when it comes to affective factors, dissonance levels tend to be significantly higher for younger travellers, in particular Enjoyment.
-In terms of instrumental factors, dissonance also tends to significantly decline with age when considering Security.
-On the other hand, the levels of dissonance in terms of Time Savings and Efficiency, while high, do not show significant differences by age group.
-Overall, the findings suggest that dissonance tends to decline with age.
-
-The results indicate that the category of Education is less useful to discriminate between different levels of dissonance.
-Two affective factors are significant at 10% or better (Freedom and Happiness) and show that dissonance tends to decline at higher levels of education.
-One instrumental factor is significant at 10% or better (Time Savings) and we see there that the level of dissonance tends to grow with higher levels of education.
-Another instrumental factor (Security) is significant at 5% or better and shows that dissonance in this factor declines with higher education.
-The picture that emerges is of highly educated people who are relatively less dissatisfied with their primary mode of transportation when it comes to Freedom, Happiness, and Security, but more dissatisfied with their Time Savings than people who are less highly educated.
-
-In general, dissonance tends to be higher for lower income individuals.
-Table 1 shows that the low-income segment has a significantly higher percentage of cases of dissonance for two affective factors.
-In the case of Freedom, for example, the lack of correspondence for low-income is 83.9% compared to 60% for the high-income segment.
-The levels of dissonance are higher for Enjoyment and follow the same decreasing trend for higher levels of income.
-Dissonance is marginally lower for instrumental factors, and significant for Security and Time Savings.
-
-As noted above, there are significant differences in dissonance by primary mode of travel, both for affective and instrumental factors.
-For affective factors, the highest levels of dissonance tend to be for users of public transportation, and the lowest for car users and active travellers.
-For instance, feelings of Freedom, Enjoyment, and Happiness are more frequently expressed by users of car and active travellers than users of public transportation.
-Indeed, people who travel by Metro or Bus almost never associate any of these positive affective attributes to these modes (dissonance is consistently greater than 90%).
-In contrast, active travellers have some of the lowest levels of dissonance in all three affective factors, in particular Freedom and Happiness.
-This analysis is in line with previous research regarding car, active travel, and public transportation (e.g., Steg et al., 2001; Páez and Whalen, 2010; Whalen et al., 2013), which tend to agree on the negative associations in the perception of affective factors when the primary mode is Metro or bus.
-
-Figure 4 shows the percentage of dissonance by primary transport mode, for both affective and instrumental factors.
-For instance, the graph at the top shows that the highest percentages of dissonances come from users of Metro and bus , compared to other modes as the car or active transport.
-This is consistent with previous studies that have separately demonstrated that public transport users tend to assess more negatively subjective factors (explored e.g.
-in Stradling et al., 1999; Gatersleben and Uzzell, 2007).
-For example, although car users have higher dissonance values than active transport, comparatively this segment has much lower percentages of dissonances than public transport, idea also supported by research that has shown that car users tend to attribute importance to symbolic aspects that positively contribute to their perception on driving (Steg et al., 2001; Mokhtarian and Salomon, 2001).
-
-Freedom and happiness tend to have a lower percentage of dissonances in the case of active transport, which means that cyclists and individuals who mainly walk for their commutes, tend to associate positive subjective values while using these modes.
-This is also consistent with other studies that have shown positive affective associations with the use of cycling and walking (Anable and Gatersleben, 2005; Gatersleben and Uzzell, 2007).
-The question at the survey has not specify the dimensions of freedom, thus has open the door for different interpretations as the freedom to choose certain mode or route, freedom while using the mode, or the freedom to access to certain places while travelling.
-Journey time: As shown in Figure 3, the analysis carried out by journey time also reveals coincidences with previous research in this area, since for shorter trips (up to 20 minutes) the analysis shows less dissonance between the primary mode and positive subjective associations mainly for affective factors.
-On the contrary, as journey time increases, higher is the dissonance.
-Strangely, the feelings of Security and Efficiency have not been statistically representative for the Journey Time analysis.
-
-In terms of instrumental factors, interestingly Figure 4 shows that bus users have the lowest percentage of dissonance regarding time savings (29%).
-However, considering the other instrumental factors, bus users have a high percentage of dissonance for security and efficiency.
-In the case of security, this means that most bus users (71%) have considered the bus as a mode that they associate to time-savings, although it is the mode that has more dissonant evaluations in all other SWB factors.
-This also seems difficult to explain considering the negative evaluation that the Transantiago system has consistently had.
-Some data provided by the Survey of Satisfaction with Transantiago Operators (DTPM, 2017) is about users' perception of journey time from origin to destination.
-In this question, and after 10 years of implementation of the system, users diagnose an average journey of 47 minutes, a value that tends to increase with respect to the data delivered by the same survey 5 years before (43.5 minutes on average).
-Worryingly, long trips of more than 30 minutes have had inconsistent variability over the years, reaching an average of more than 37 minutes in 2016.
-Short trips, however, remain roughly equal to previous years, and do not show significant changes in the average of 6-7 minutes per trip .
-This survey has the peculiarity  of being developed by the Metropolitan Public Transport Board (DTPM), whose mission is to articulate the functions of the different modes of public transport with a specific interest in buses Transantiago and Metro de Santiago.
-
-Another big gap on these instrumental factors relates to the perception of security that is especially significant for car users.
-This means that a 75% of car users have chosen as primary mode the same one as they relate to the feeling of security, which is completely opposite to other transport modes, specially bus users.
-Bus users have the highest dissonance (98%), which means that practically all this group of users have chosen another mode for referring to the feelings of security.
-The recently referred DTPM survey does not have any particular question that addresses the issue of safety – mostly related in this context as security.
+# 4.1 Who experiences dissonance?
+
+To investigate the first question in our analysis, we create contingency tables that tabulate the frequency of dissonance with respect to each affective value, stratified by the attributes of Age, Education, Income, Primary Mode of Travel, and typical Commute Time.
+Table \ref{tab:cross-tabulation-results-without-instrumental} presents the frequency (in percentage) of dissonance, in other words, the percentage of respondents out of the total in their stratum who indicated mode or mode(s) for the affective value that do not correspond to their primary mode of travel.
+
+As seen in the table, there are five characteristics of the respondents and their commutes that we use in the analysis.
+Three of these categories are socio-economic and demographic, namely age, level of education, and income.
+The other two are transportation related, namely primary mode of travel and commute time.
+The frequency tables were tested in every case by means of the $\chi^2$ test of independence ($p$-values are reported in the table; lower $p$-values mean that the null hypothesis of independence can be rejected with greater confidence).
+It is interesting to note that the only category for which all affective values are significant at better than 5% level of confidence is mode of travel.
+
+### 4.1.1 Age
+
+With respect to Age, previous studies have reported that older adults tend to be more satisfied with their travel experience than younger people [@Cao2014satisfaction; @Devos2016travel; @Ye2017satisfaction].
+In the case, we find that five affective values show dissonance that significantly deviates from the null hypothesis of independence, namely Freedom, Enjoyment, Happiness, Luxury, and Status.
+We observe that levels of dissonance tend to be high in general, and in no case less than 60%.
+For instance, almost 90% of travellers younger than 35 experience travel mode dissonance with respect to Freedom, and more than 94% experience dissonance with respect to enjoyment.
+In general, younger travellers tend to experience dissonance more frequently, with dissonance being less frequent for older travellers.
+The exception to this trend is Luxury, an affective value for which older travellers (age >54) experience dissonance more frequently than mid-aged travellers (ages 35-54).
+
+### 4.1.2 Education
+
+When seen from the perspective of Education, the results do not support the hypothesis of  significant differences in the frequency of dissonance by levels of education for the values of Freedom, Enjoyment, Happiness, and Poverty, and only two affective values show significant differences between education levels: Luxury and Status.
+In the case of Luxury, dissonance is more frequent among people who have only K-12 education, and less frequently, albeit still high, for people with technical/university level education and post-graduate education.
+Furthermore, highly educated people (with postgraduate degrees) experience dissonance with respect to Status more frequently than with respect to Luxury.
+
+### 4.1.3 Income
+
+The next variable we examine is income, and in this case three affective values are significant: Poverty, Luxury, and Status.
+Since Poverty is a negative affect, we see here that lower income people tend to associate this feeling to their primary mode of commuting more frequently (almost 20% of the time) than other income groups.
+For example, whereas approximately 16% of mid-income people are dissatisfied with their primary mode of travel in this respect, less than 7% of high income individuals are.
+Dissonance with respect to Luxury and Status also tends to be more common among lower income people, and declines substantially for mid- and high income respondents.
+Notice as well that the frequency of dissonance is higher in terms of Luxury than Status for mid- and high income people.
+
+### 4.1.4 Primary mode of travel
+
+The variable that shows the largest differences in the frequency of dissonance is the primary mode of travel.
+It can be seen in Table \ref{tab:cross-tabulation-results-without-instrumental} that the differences are significative for all six affective values.
+Dissonance is particularly accute for users of public transportation when it comes to the values of Freedom, Enjoyment, and Happiness: almost 100% of users of public transportation have identified other mode or modes as better representing those values.
+Dissonance on these values is the least for active travellers: less than 50% of respondents associate Freedom to a different mode, and only around 60% identified a different mode when responding to the values of Enjoyment and Happiness, compared to approximately 79% and 71% of those who travelled by Car.
+The picture changes when the values of Poverty, Luxury, and Status are considered.
+In this case, dissonance is less frequent for people who travel by car: less than 3% of car users associate car with feelings of poverty, 41% associate Luxury with a mode other than car, and only about 31% relate Status to a different mode.
+Dissonance is more frequent in these values for active travellers, and users of public transportation and other modes, in no case being less than 75%, and being virtually 100% for users of public transportation, who consistently associate Luxury and Status with modes _other_ than public transportation.
+
+### 4.1.5 Typical commute time
+
+Turning now to typical commute time, four affectie values show significant differences at better than 10% confidence: Freedom, Happiness, Luxury, and Status.
+Perhaps not surprisingly, dissonance is more frequent among people whose typical commutes are longer.
+This is in line with previous findings: both St-Louis et al.
+[-@Stlouis2014happy] and Smith [-@Smith2017commute] report that commute satisfaction tends to decline with longer commutes, whereas Handy and Thigpen [-@Handy2019commute] found that commute distance was a negative covariate of commute satisfaction.
 
@@
       booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
+      caption = "\\label{tab:cross-tabulation-results-with-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
       escape = FALSE,
@@
   pack_rows("Mode", 10, 13) %>%
-  pack_rows("Journey Time", 14, 17)  %>%
+  pack_rows("Commute Time", 14, 17)  %>%
   kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
@@
       booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
+      caption = "\\label{tab:cross-tabulation-results-without-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
       escape = FALSE,
@@
 
-Figure 5 shows the points of origin of the survey for the case of public transport users.
-Metro users as primary mode are shown, bus users are shown in cyan.
-The size of the points represents the number of dissonances.
-The higher the point, the greater the number of SWB factors that do not coincide with the primary transport mode.
-The image shows that the intensity or size of the circles is homogeneously distributed in the territory, even though the blue circles (metro) tend to show slightly less dissonance.
-The visualisation of this map is more dramatic when it is compared to the following Figure 6.
-
-Figure 6 shows the points of origin for the case of private transport (cars) and active transport (walking and cycling).
-Again, the size of the circles represents intensity levels of dissonance.
-The number of dissonances is lower than in the case of Figure 5, which indicates that users of private and active transport tend to use a mode of transport that they relate to one of the positive factors derived from subjective wellbeing.
-In this sense, it could be said that this type of user tends to be more advantaged than the public transport user, in a dimension not only utilitarian but also emotional and attitudinal.
-
-## Which modes do travelers associate with affective and instrumental values?
-
-Here we can visualize the modes that travellers associate with different affective and instrumental values.
-The tool we use for this is a mosaic plot.
-See the mosaic plots in Figure \ref{fig:mosaic-plots-by-attribute}.
-
-```{r figure-mosaic-plots-by-attribute-with-instrumental, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}
+**FOR DISCUSSION**
+
+@Alayyash2019commute
+@Bornioli2019affective
+@Devos2019satisfying
+@Gatersleben2007affective
+@Smith2017commute
+@Ye2017satisfaction
+
+## 4.2 Which modes do travellers associate with affective values?
+
+The preceding analysis suggests that there is significant mode dissonance along various dimensions and for various affective values.
+Once we have developed a profile of the travelers who experience mode dissonance, we are interested in what modes they tend to associate with various affective values.
+For this analysis, we employ a visualization technique known as a mosaic plot that is used for exploring categorical data [@Friendly1994mosaic; @Hofmann2000exploring].
+A mosaic plot is a visual representation of a multi-way contingency table, whereby the dimensions of each tile in the mosaic are proportional to the values in the underlying table.
+
+We begin by plotting the cross-tabulation of primary mode of travel to mode associated with each affective value (see Figure \ref{fig:mosaic-plots-by-attribute}).
+The height of tile $j$ in these mosaics corresponds to the proportion of travellers who primarily travel by mode $j$, hence we can see that the most common primary mode of travel in this sample is by public transportation, followed by car, active travel, and other (also see Figure \ref{fig:primary-mode-travel}).
+Notice that there are some small discrepancies in the heights across affective values: these are caused by a small number of non-responses.
+Next, the width of the tile $k$ in the mosaics is proportional to the frequency with which a mode was named in relation to affective value $i$.
+Recall that respondents could nominate more than one mode in response to each affective value, and some did.
+For this reason, we used sampling weights, so that the total number of responses corresponds to the size of the sample.
+
+In terms of Freedom, we see that Car users frequently identify this affect with the use of Car; however, those who do not, very often select Active Travel as the mode that better represents Freedom.
+A majority of active travellers, on the other hand, identify Active Travel as the mode associated with Freedom; few of them attach this value to Car, and even fewer to public transportation and other modes.
+Travellers whose primary mode of travel is public transportation seldom associate this mode with Freedom, and in fact more frequently relate this affective response to Active Travel followed by Car.
+Users of other modes seem to be split almost equally in their attribution of Freedom, between Active Travel, Car, and Other.
+In general, Active Travel is the mode most often identified as embodying Freedom, with the exception of Car travellers.
+
+The pattern with respect to Enjoyment is similar to that for Freedom, but with an even more decisive tilt towards Active Travel, with even more respondents whose primary mode of travel is Car choosing Active Travel as the mode that better represents Enjoyment.
+Notice that very few of Active Travelers selected Car as an enjoyable mode.
+Likewise, compared to Freedom, Active Travel is perceived as being more enjoyable by users of Public Transportatoin and Other modes.
+Responses with respect to Happiness are somewhere in between Freedom and Enjoyment, but Happiness is, if anything, even less frequently identified with Public Transportation.
+
+Three other affective responses show a marked difference.
+Public Transportation was seldom associated by respondents to feelings of Freedom, Enjoyment, and Happiness; on the other hand, it is the mode that is most commonly selected by respondents for evoking feelings of Poverty - even by users of Publi Transportation.
+Active Travel was the second most common response for its association with Poverty.
+Likewise, Whereas Active Travel was often associated to feelings of Freedom, Enjoyment, and Happiness, the mode most frequently associated with Luxury and Status is the Car, although active travellers seem to be somewhat more resistant to this association compared to respondents who travel by Car, Public Transportation, and Other modes.
+
+Next, we further explore these responses after stratifying by Age, Education, Income, and Commute Time.
+We test the underlying 3-way tables by means of the Cochran-Mantel-Haenszel $\chi^2$ test of independence.
+
+***
+
+Efectivamente lujo y estatus parecen similares a primera vista (Figura 1).
+En general, estos dos valores afectivos son asociados mucho mas comunmente con el automovil.
+Por otro lado, hay algunas diferencias interesantes cuando se les ve desde la perspectiva de diferentes viajeros.
+
+Por ejemplo, la tendencia a asociar estatus con el automovil tiende a incrementarse con la edad, con la posible excepcion de los usuarios de transporte publico, para quienes otras opciones (posiblemente taxi), ganan en estatus para los viajeros mayores (>54) a costa de otros modos, incluido el automovil.
+En contraste, el automovil pierde en el valor de lujo con la edad, mientras que otras opciones pasan a ser percibidas como lujo mas comunmente con la edad, incluso para los usuarios de automovil (Figure 2).
+
+se vuelven mas comunmente simbolos de estatus que cuando vemos la manera en que viajeros de diferentes edades proyectan lujo y estatus en varios modos, los usuarios de automovil mayores (>54) muestran menos disonancia en status que en lujo, mientras que los viajeros activos presentan mas disonancia en estatus que en lujo, y de hecho proyectan estatus mas comunmente en el automovil.
+
+La manera en que el lujo se asocia de manera relativamente mas frecuente con otras opciones que el estatus tambien se observa cuando vemos los diferentes niveles de educacion.
+La excepcion parece ser los usuarios de transporte activo, especialmente  aquellos con educacion superior y de post-grado, que asocian tanto estatus como lujo con el transporte activo mas que los usuarios de otros modos.
+
+***
+
+```{r figure-mosaic-plots-by-attribute-with-instrumental, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute-with-instrumental}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}
 
@@
 
-```{r figure-mosaic-plots-by-attribute-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
+```{r figure-mosaic-plots-by-attribute, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
 
@@
 
-```{r figure-mosaic-plots-by-attribute-and-age-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
+### 4.2.1 Age
+
+Words go here to discuss results by age.
+
+```{r figure-mosaic-plots-by-attribute-and-age, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS"))) + 
+# Also, use Cochran-Mantel-Haenzel tests
+# Freedom
+Modes_by_Freedom_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM")))
+
+# Enjoyment
+Modes_by_Enjoyment_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT")))
+
+# Happiness
+Modes_by_Happiness_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS")))
+
+# Luxury
+Modes_by_Luxury_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
+
+# Status
+Modes_by_Status_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
+
+labels <- c(paste('FREEDOM\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 2) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
+                                             " < 0.001")),
+            paste('ENJOYMENT\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
+                                             " < 0.001")),
+            paste('HAPPINESS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
+                                             " < 0.001")),
+            paste('LUXURY\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
+                                             " < 0.001")),
+            paste('STATUS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
+                                             " < 0.001")))
+
+ggplot(data = Modes_by_Attribute %>% 
+         filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS")) %>%
+         mutate(ATTRIBUTE = factor(ATTRIBUTE, 
+                                   levels = c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS"),
+                                   labels = labels))) + 
   geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
@@
 
-```{r figure-mosaic-plots-by-attribute-and-education-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
+### 4.2.2 Education
+
+Words go here to discuss results by education.
+
+```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("LUXURY", "STATUS"))) + 
+# Also, use Cochran-Mantel-Haenzel tests
+# Luxury
+Modes_by_Luxury_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
+
+# Status
+Modes_by_Status_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
+
+labels <- c(paste('LUXURY\np-value', ifelse(round(Modes_by_Luxury_by_Education$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Luxury_by_Education$p.value, 3)),
+                                             " < 0.001")),
+            paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Education$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Status_by_Education$p.value, 3)),
+                                             " < 0.001")))
+
+ggplot(data = Modes_by_Attribute %>% 
+         filter(ATTRIBUTE %in% c("LUXURY", "STATUS")) %>%
+         mutate(ATTRIBUTE = factor(ATTRIBUTE,
+                                   levels = c("LUXURY", "STATUS"),
+                                   labels = labels))) + 
   geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
@@
 
-```{r figure-mosaic-plots-by-attribute-and-income-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
+### 4.2.3 Income
+
+Words go here to discuss results by income.
+
+```{r figure-mosaic-plots-by-attribute-and-income, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("POVERTY", "LUXURY", "STATUS"))) + 
+# Also, use Cochran-Mantel-Haenzel tests
+# Poverty
+Modes_by_Poverty_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY")))
+
+# Luxury
+Modes_by_Luxury_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
+
+# Status
+Modes_by_Status_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
+
+labels <- c(paste('POVERTY\np-value', ifelse(round(Modes_by_Poverty_by_Income$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Poverty_by_Income$p.value, 3)),
+                                             " < 0.001")),
+            paste('LUXURY\np-value', ifelse(round(Modes_by_Luxury_by_Income$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Luxury_by_Income$p.value, 3)),
+                                             " < 0.001")),
+            paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Income$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Status_by_Income$p.value, 3)),
+                                             " < 0.001")))
+
+ggplot(data = Modes_by_Attribute %>% 
+         filter(ATTRIBUTE %in% c("POVERTY", "LUXURY", "STATUS")) %>%
+         mutate(ATTRIBUTE = factor(ATTRIBUTE, 
+                                   levels = c("POVERTY", "LUXURY", "STATUS"),
+                                   labels = labels))) + 
   geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
@@
 
-```{r figure-mosaic-plots-by-attribute-and-time-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by travel time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
+### 4.3.4 Typical commute time
+
+Words go here to discuss results by time.
+
+```{r figure-mosaic-plots-by-attribute-and-time, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by commute time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS")) %>% drop_na(TRAVEL_TIME)) + 
+# Also, use Cochran-Mantel-Haenzel tests
+# Freedom
+Modes_by_Freedom_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM")))
+
+# Happiness
+Modes_by_Happiness_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS")))
+
+# Luxury
+Modes_by_Luxury_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
+
+# Status
+Modes_by_Status_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
+
+labels <- c(paste('FREEDOM\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 2) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
+                                             " < 0.001")),
+            paste('ENJOYMENT\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
+                                             " < 0.001")),
+            paste('LUXURY\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
+                                             " < 0.001")),
+            paste('STATUS\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 3) >= 0.001,
+                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
+                                             " < 0.001")))
+
+ggplot(data = Modes_by_Attribute %>% 
+         filter(ATTRIBUTE %in% c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS")) %>% drop_na(TRAVEL_TIME) %>%
+         mutate(ATTRIBUTE = factor(ATTRIBUTE, 
+                                   levels = c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS"),
+                                   labels = labels))) + 
   geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
@@
 
-Conclusions
+***FOR DISCUSSION***
+
+@Devos2018people
+
+5. Conclusions
 ==========
 
-Words go here.
+Accordingly, the aim of this paper is to analyse some of the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
+Previous research suggests that public transport users experience a negative gap in desired and actual travel time, whereas active travellers don’t seem to mind somewhat longer trips than what strictly needed (e.g., Páez and Whalen, 2010).
+In the context of a Latin American country, historically the poor travel experience of public transit users and active travellers reflects the social inequalities of social groups that have no alternative but to move in these types of modes while living far from the work centres and main activities.
+The paper aims to reflect on the possibilities of increasing the SWB while travelling, and how this could increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
+This can help not only to reduce the use of private transport but also decrease the inequality gap between these users.
+
+The paper explores how positive affective and instrumental/utilitarian factors of SWB correspond to the use of the primary mode of transportation.
+It uses an analysis of correspondence that considers the actual primary mode versus the mode that individuals associated to both utilitarian (designed to be useful or practical rather than attractive) and affective (expressing a person's feelings) SWB factors.
+For example, it will be analysed if a person who uses public transport as the primary mode, tends to associate these modes with positive affective factors (as freedom, enjoyment or happiness) or positive utilitarian factors (as security, time-savings or efficiency).
+We hypothesize that there is a more persistent non-correspondence or mismatch within the more disadvantage groups or within the users of public transport.
+
+Acknowledgments
+==========
+
+The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `ggmosaic` [@Jeppson2019ggmosaic], `ggthemes` [@Arnold2018], `kableExtra` [@Zhu2018], `knitr` [@Xie2015; @Xie2018], `rticles` [@Allaire2018rticles], and `tidyverse` [@Wickham2017].
 

### 2019-10-21 Dissonance_Santiago_v1.tex
Worked on Analysis and Results, included Cochran-Mantel-Haenszel Chi-Squared Test for 3-way tables

@@
             pdfauthor={},
-            pdftitle={Do Drivers Dream of Walking? An Investigation of Dissonance in the Primary Mode of Travel from the Perspective of Subjective Wellbeing},
+            pdftitle={Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing},
             colorlinks=false,
@@
 
-  \title{Do Drivers Dream of Walking? An Investigation of Dissonance in the
-Primary Mode of Travel from the Perspective of Subjective Wellbeing}
+  \title{Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance
+from the Perspective of Subjective Wellbeing}
     \author[Some University]{Author 1\corref{c1}}
@@
   Transportation in most of the world has been dominated for decades by a
-  fascination with the automobile. Increasingly, however, it is recognized
-  that to achieve a variety of economic, environmental, and public health
-  policy goals it is important to attract and retain users of public
-  transport and active travel. A challenge with the way transportation
-  policy is developed is that it tends to focus on cost-benefit and
-  utilitarian considerations, which may miss other potential benefits of
-  transportation. For this reason, subjective wellbeing (SWB) has been
-  proposed as a way to enhance our understanding of the preferences and
-  choices of travellers, as well as a way to evaluate the benefits of
-  transportation beyond utilitarian considerations. The objective of this
-  paper is to analyze the modes that people commonly use, and to what
-  extent they are aligned (or not) with a variety of affective and
-  utilitarian values. In other words, we are interested in the potential
-  for dissonance with respect to the primary mode of travel, from the
-  perspective of affective and utilitarian values. The study is based on
+  fascination with the automobile. Nonetheless, there is an increasing
+  recognition that to achieve a variety of economic, environmental, and
+  public health policy goals it is important to attract and retain active
+  travelers and users of public transportation. A challenge with the way
+  transportation policy is developed, however, is that it tends to focus
+  on utilitarian considerations, which may miss other potential aspects of
+  transportation that users value. In particular, subjective wellbeing
+  (SWB) has been proposed as a way to enhance our understanding of the
+  preferences and choices of travellers, as well as a way to evaluate the
+  benefits of transportation beyond utilitarian considerations. The
+  objective of this paper is to analyze the modes that people commonly
+  use, and to what extent they are aligned (or not) with a variety of
+  affective values associated with SWB. In other words, we are interested
+  in the potential for dissonance with respect to the primary mode of
+  travel, from the perspective of affective values. The study is based on
   data collected from a sample of travellers in the city of Santiago, in
@@
   travel, and then were asked to name the mode or modes that they
-  associated to affective values (freedom, enjoyment, and happiness) and
-  to utilitarian values (safety, time waste, and efficiency). The results
-  indicate that users of public transportation experience the most
-  dissonance in terms of affective values, and active travellers the
-  least. For those travellers who experience dissonance, active travel is
-  the mode most commonly associated with affective values.
-
-  To properly assess transportation policy This poses a number of
-  challenges Broadening the commonly used transport project assessment
-  will be relevant for achieving this goal. While satisfaction with travel
-  has been mainly used in the context of daily trips and mainly under
-  cost-benefit and utilitarian considerations, subjective wellbeing (SWB)
-  over time has risen as an alternative for understanding the preferences
-  and choices of transport users. The aim of this paper is to analyse the
-  factors that can potentially affect the levels of SWB in the wide
-  spectrum of public, private and active transport modes in the context of
-  Santiago de Chile. The paper aims to reflect on the possibilities of
-  increasing the SWB with a view to enhance the attractiveness of public
-  transport and active travel. The paper investigates the affective and
-  instrumental/utilitarian factors of SWB, according to modal choice. It
-  uses an analysis of correspondence that considers the actual primary
-  mode used, versus the mode that each individual associated to both
-  utilitarian and affective SWB factors. The results show that there is
-  more persistent modal dissonance between positive emotional and
-  utilitarian associations within the more disadvantaged groups --
-  particularly among users of public transport. The study shows that apart
-  from time-savings and efficiency, security has also been
-  cross-sectionally sensitive according to the data analysed. Factors such
-  as happiness, enjoyment and freedom require far more attention in
-  transport planning as they are strongly related to the dimensions of
-  subjective and personal wellbeing. Targeting these factors will be
-  relevant for attracting new users to public transportation and active
-  travel.\\
+  associate with the affective values of freedom, enjoyment, happiness,
+  poverty, luxury and status. The results indicate that users of public
+  transportation experience the most dissonance in terms of affective
+  values, and active travellers the least. For those travellers who
+  experience dissonance, active travel is the mode most commonly
+  associated with freedom, enjoyment, and happiness, public transportation
+  is most commonly associated with poverty, and the automobil is most
+  commonly associated with luxury and status.
   \end{abstract}
@@
 \hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{1. Introduction}\label{introduction}}
 
@@
 for the private automobile. This is a model of development that was
-initially introduced in North America as a solution to urbanizations
-problems, and that was eventually copied elsewhere (Brown et al., 2009;
-Angotti, 1996) . Despite the initial promise of automotive technology,
-it is now evident that mobility centred on the private automobile has
-given rise to a litany of maladies that are in urgent need of
-correction. This includes environmental concerns (i.e., climate change;
-Chapman, 2007) as well as other social (Boschmann and Kwan, 2008),
-health (Khreis et al., 2016), and equity issues (Bocarejo and Oviedo,
-2012). As the real impacts of our societal dependence on the private
+initially introduced in North America as a solution to problems created
+by rapid urbanization, and that was eventually copied elsewhere
+(Angotti, 1996; Brown et al., 2009). Despite the initial promise of
+automotive technology, it is now evident that mobility centred on the
+private automobile has given rise to a litany of maladies that are in
+urgent need of correction. This includes environmental concerns (i.e.,
+climate change; Chapman, 2007) as well as numerous other social
+(Boschmann and Kwan, 2008; Lucas, 2019, 2012), health (Khreis et al.,
+2016; Milne, 2012), and equity issues (Bocarejo and Oviedo, 2012;
+Martens et al., 2012; Pereira et al., 2017).
+
+As the real impacts of our societal dependence on the private
 autombobile have become increasingly evident, the transportation agenda
-has in recent years aimed to shift focus to the reduction of car-use and
-towards the creation of mobility polycultures that offer a broader menu
-of transportation alternatives than just the private automobile (Miller,
-2011) . In order to successfully achieve this goal, it is essential not
-only to provide the services and facilities that support public
-transportation and active travel, but also to attract new users to these
-modes of transportation (Ettema et al.~2011). Within this context, it
-has been argued that sustainable transportation policies require all
-participants in the transportation system to challenge what Gossling and
-Cohen (2014) term ``transportation taboos'': deep-seated ideas
-concerning the contribution to emissions by individuals, the inequality
-of market-based approaches, and the social and psychological functions
-of transportation. With respect to the latter, moving beyond a purely
-utilitarian focus, it is important to understand how users perceive
-affective and instrumental elements on their transportation experience,
-since this can help to incorporate adequate improvements in alternative
-transportation, including transit and active modes, to make them more
-attractive to users (Anable and Gatersleben, 2005; Domarchi et al.,
-2008; Gatersleben and Uzzell, 2007; Steg 2005 ).
+has aimed to shift focus to the reduction of car use and towards the
+creation of mobility polycultures that offer a broader menu of
+transportation alternatives than primarily (or even just) the private
+automobile (Miller, 2011). In order to successfully achieve this goal,
+it is essential not only to provide the services and facilities that
+support public transportation and active travel, but also to attract new
+users to these modes of transportation (Ettema et al., 2011). Within
+this context, it has been argued that sustainable transportation
+policies require all participants in the transportation system to
+challenge what Gossling and Cohen (2014) termed \emph{transportation
+taboos}: deep-seated ideas concerning the contribution to emissions by
+individuals, the inequality of market-based approaches, and the social
+and psychological functions of transportation. With respect to the
+latter, it is important to move beyond a purely utilitarian focus if we
+are to understand how the affective value of the transportation
+experience can be leveraged to improve alternative transportation -
+particularly transit and active modes (Anable and Gatersleben, 2005;
+Domarchi et al., 2008; Gatersleben and Uzzell, 2007; Steg, 2005).
 
 A useful lens to investigate the social and psychological functions of
-transportation is by means of the concept of subjective wellbeing (SWB.
-See, inter alia, De Vos et al., 2013 and Chatterjee et al., 2019) . SWB
+transportation is by means of the concept of subjective wellbeing (SWB;
+see, inter alia, De Vos et al., 2013; and Chatterjee et al., 2019). SWB
 is defined by the OECD as ``{[}g{]}ood mental states, including all of
@@
 their lives, and the affective reactions of people to their
-experiences'' (OECD, 2013, p.~10). Accordingly, the aim of this paper is
-to analyse some of the factors that can potentially affect the levels of
-SWB in the wide spectrum of public, private and active transport modes
-in the context of Santiago de Chile. Previous research suggests that
-public transport users experience a negative gap in desired and actual
-travel time, whereas active travellers don't seem to mind somewhat
-longer trips than what strictly needed (e.g., Páez and Whalen, 2010). In
-the context of a Latin American country, historically the poor travel
-experience of public transit users and active travellers reflects the
-social inequalities of social groups that have no alternative but to
-move in these types of modes while living far from the work centres and
-main activities. The paper aims to reflect on the possibilities of
-increasing the SWB while travelling, and how this could increase the
-attractiveness of public transport and active travel in the
-socio-demographic groups studied. This can help not only to reduce the
-use of private transport but also decrease the inequality gap between
-these users.
+experiences'' (\textbf{OECD, 2013, p.~10}). As memorably put by Steg
+(2005): is the use of car a must, or is it a lust? A close alignment, or
+consonance, between affective values and the mode of transportation used
+to travel can result in greater subjective wellbeing and increase the
+probability of choosing that mode (i.e., by satisfying the \emph{lust});
+on the other hand, dissonance, that is, the lack of concordance between
+the mode used and affective values would be detrimental to subjective
+wellbeing, especially of those for whom the use of the mode is a
+\emph{must} (De Vos, 2019; Mokhtarian and Pendyala, 2018). With these
+considerations in mind, one aim of the present research is to
+investigate \emph{who} experiences dissonance with respect to their
+primary mode of travel and affective values, namely freedom, enjoyment,
+happiness, feelings of poverty, luxury, and status. Furthermore, it is
+possible, even if use of a particular mode is a \emph{must}, that
+travellers may still \emph{lust} for something else - in other words,
+the grass may in fact look greener from the window of the car. For this
+reason, we also aim to investigate which mode or modes are most commonly
+associated with affective values, with a focus on those travellers who
+experience dissonance in their primary mode.
 
-The paper explores how positive affective and instrumental/utilitarian
-factors of SWB correspond to the use of the primary mode of
-transportation. It uses an analysis of correspondence that considers the
-actual primary mode versus the mode that individuals associated to both
-utilitarian (designed to be useful or practical rather than attractive)
-and affective (expressing a person's feelings) SWB factors. For example,
-it will be analysed if a person who uses public transport as the primary
-mode, tends to associate these modes with positive affective factors (as
-freedom, enjoyment or happiness) or positive utilitarian factors (as
-security, time-savings or efficiency). We hypothesize that there is a
-more persistent non-correspondence or mismatch within the more
-disadvantage groups or within the users of public transport.
+Research is based on data collected from a sample of travellers in the
+city of Santiago in Chile. Survey respondents were asked about their
+primary mode of travel, and also about the mode or modes that they
+associate with the affective values mentioned above. The paper
+contributes to the literature in three ways, as follows:
 
-The paper contributes to the literature in three areas. First, it
-contributes to an emerging literature on the topic in the context of the
-Global South (Bejarano et al., 2017 ; Shao and Liang, 2019 ; Van et al.,
-2014 ; Zorrilla et al., 2019); to the best of our knowledge, the case of
-Chile has not yet been reported. Second, although there is literature on
-the enjoyment of commute and other emotional factors, from a hedonic and
-even eudaimonic perspectives, the analysis has yet to be applied more
-fully in terms of distributional issues -- i.e.~which groups are mostly
-disadvantaged. Finally, the analysis shows the attitudes of people
-towards their primary mode and their perception towards `ideal modes' --
-implying their preferences, even in situations when their ideal mode is
-not part of their actual choice set. The attitudes of travellers towards
-transport modes are critical factors to be considered by policy-makers
-in case they want to promote and increase the use of public transport or
-active modes (e.g., Bejarano et al., 2019). The paper explores these
-positive and negative associations within the transport options used in
-Santiago.
-
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  The research reported here contributes to an emerging literature on
+  the topic of transportation and affective values in the context of the
+  Global South (Al-Ayyash and Abou-Zeid, 2019; Bejarano et al., 2017;
+  Shao and Liang, 2019; Van et al., 2014; Zorrilla et al., 2019); to the
+  best of our knowledge, the case of Chile has not yet been reported.
+\item
+  Although there is an extensive literature on the enjoyment of commute
+  and other affective values (see for instance Paez and Whalen, 2010;
+  Redmond and Mokhtarian, 2001; Whalen et al., 2013; Ye and Titheridge,
+  2017), from a hedonic and even eudaimonic perspectives the analysis
+  has yet to be applied more fully in terms of distributional issues --
+  i.e.~which groups more commonly experience dissonance (see De Vos,
+  2018).
+\item
+  The analysis shows the attitudes of people towards their primary mode
+  and their perception towards `ideal modes' -- implying their
+  preferences, even in situations when their ideal mode is not part of
+  their actual choice set. More concretely, the results indicate that
+  users of public transportation experience the most dissonance in terms
+  of affective values, and active travellers the least. For those
+  travellers who experience dissonance, active travel is the mode most
+  commonly associated with freedom, enjoyment, and happiness, public
+  transportation is most commonly associated with poverty, and the
+  automobil is most commonly associated with luxury and status. We also
+  find that there are some substantial variations in dissonance by age,
+  education, income, and typical commute time. The attitudes of
+  travellers towards transport modes are critical factors to be
+  considered by policy-makers in case they want to promote and increase
+  the use of public transport or active modes (Bornioli et al., 2019; De
+  Vos et al., 2019; De Vos and Witlox, 2017; Garling et al., 2019;
+  Redman et al., 2013).
+\item ~
   \hypertarget{background}{%
   \section{Background}\label{background}}
+\end{enumerate}
 
-The transportation community has for the most part already agreed to the
-need of looking at mobility and transport issues from the lens of
-wellbeing, to broaden the commonly used utilitarian perspective to
-evaluate projects. Users' travel satisfaction (Bergstad, 2001) has been
-the primary way to direct this challenge towards everyday mobility,
-resulting on research about satisfaction with different transport modes.
-For example, numerous studies report that car users have a higher level
-of satisfaction compared to other transport modes (Redmond and
-Mokhtarian, 2001 ; Bergstad et al.~2011; Eriksson et al.~2013; Whalen et
-al., 2013). In a similar way, there are multiple reports that active
-travel also tends to yield high levels of satisfaction (Smith, 2017;
-St-Louis et al.~2014; Paez and Whalen, 2010; Whalen et al., 2013), In
-contrast, public transport users tend to assess their experience more
-negatively (De Vos et al.~2016; Abenoza et al.~2017; Ettema et al.~2012;
-Páez and Whalen, 2010). Multi-modal trips also influence satisfaction
-levels; for instance, when an individual chooses a particular mode of
-transportation, she will report a higher level of satisfaction with that
-chosen mode -- perhaps as a form of post hoc validation (Susilo and
-Cats, 2014).
+A consensus has emerged in the transportation community regarding the
+need to complement the traditional utilitarian perspective of
+transportation by looking at mobility and transport issues from the lens
+of their affective functions. The affective value of transportation in
+turn is important due to its potential to improve or detract from SWB.
+One of the primary ways to explore this has been the satisfaction that
+travelers feel towards their every day mobility experience (e.g.,
+Cecilia Jakobsson Bergstad et al., 2011). As a consequence, there is a
+wealth of research on satisfaction with the use of different modes of
+transportation. For example, numerous studies report that car users
+often have a higher level of satisfaction compared to other transport
+modes (C. J. Bergstad et al., 2011; Eriksson et al., 2013; Redmond and
+Mokhtarian, 2001; Whalen et al., 2013; but see Handy and Thigpen, 2019).
+In a similar way, there are multiple reports that active travel also
+tends to yield high levels of satisfaction (Gatersleben and Uzzell,
+2007; Handy and Thigpen, 2019; Paez and Whalen, 2010; Smith, 2017;
+St-Louis et al., 2014; Whalen et al., 2013), In contrast, public
+transport users tend to assess their experience more negatively (Abenoza
+et al., 2017; De Vos et al., 2016; Gatersleben and Uzzell, 2007; Handy
+and Thigpen, 2019; Paez and Whalen, 2010). Multi-modal trips also
+influence satisfaction levels; for instance, when an individual chooses
+a particular mode of transportation, she will report a higher level of
+satisfaction with that chosen mode -- perhaps as a form of \emph{post
+hoc} validation (Susilo and Cats, 2014).
 
 While the use of travel satisfaction has been mainly used in the context
-of daily trips -- typically been linked to cost-benefit and utilitarian
+of daily trips -- typically linked to cost-benefit and utilitarian
 measurements --, the evaluation of Subjective Wellbeing (SWB) over time
 has risen as an alternative measure. In the field of travel behaviour,
-Ettema et al.~(2010; p.~725) have defined SWB as the degree to which an
+Ettema et al.~(2010, p. 725) define SWB as the degree to which an
 individual positively evaluates the overall quality of their lives,
@@
 situations. The definition of other factors such as travel choice mode,
-attitudes and external elements of the built environment has been
-studied for a broader understanding of the changes produced in the SWB.
-As these factors do not necessarily apply to the general life
-satisfaction on the long term, the studies have aimed to determine both
-the direct and indirect effects on the perception of users (see, e.g.~Ye
-and Titheridge 2017). Other concepts have also emerged as the
-Satisfaction with Travel Scale (STS), a measurement devised by Ettema et
-al.~(2011) as well as different scales based on people's travel
-perceptions. De Vos et al.~(2015) for instance, explore in detail the
-underlying dimensions of the affective domain of STS in which SWB is
-based (for more on STS see also Friman et al.~2013).
+attitudes and external elements of the built environment have been
+studied for a broader understanding of the changes produced in the SWB
+(e.g., Handy and Thigpen, 2019). As these factors do not necessarily
+apply to the general life satisfaction on the long term, the studies
+have aimed to determine both the direct and indirect effects on the
+perception of users (see, e.g., Ye and Titheridge, 2017). Other concepts
+have also emerged as the Satisfaction with Travel Scale (STS), a
+measurement devised by Ettema et al.~(2011), as well as different scales
+based on people's travel perceptions. De Vos et al.~(2015), for
+instance, explore in detail the underlying dimensions of the affective
+domain of STS on which SWB is based (for more on STS see also Friman et
+al., 2013).
 
@@
 relationship between people's perceptions and satisfaction with their
-daily travel (Smith, 2017; St-Louis et al.~2014; Paez and Whalen, 2010;
-Whalen et al., 2013). Scholars have shown that accessibility has been
-the most developed factor that influences people's wellbeing (Delbosc,
-2012), and activities have a direct impact on travel satisfaction
-(Bergstad et al., 2010). Delbosc (2012; 28) for instance, has summarised
-the most significant influences on psychological wellbeing: poverty and
-employment, meaningful relationships and health. However, understanding
-the components affecting people's perceptions implies the
-differentiation between the emotional (also named as symbolic-affective)
-and the instrumental reasons (Bergstad, 2001). Steg et al.~(2011) have
-compared symbolic-affective opposed to instrumental-reasoned motives
-based on car-use, and other studies have also found associations between
-affective and symbolic aspects of car-use (see, e.g.~Gatersleben, 2007;
-Lois \& López-Sáez, 2009). Previous studies have demonstrated how
-socio-demographic factors affect the levels of SWB. The effect of income
-on SWB (Clarck and Oswald, 1996, Ferrer-i-Carbonell, 2005); education
-and unemployment (Argyle, 1999); age (Diener and Suh, 1997) and gender
-(Tesch-Römer et al., 2008) have already been studied. Recent research
-also suggests the links between commuting, SWB and emotional wellbeing
-assessment (Olson et al.~2013; Kahneman et al.~2004). However, more
-research is needed to understand how these socio-demographic variables,
-connect as well with the decisions on main transport mode choices; or
-research distinguishing between hedonic (journey experience) and
-eudaimonic (flourishing) value of trips.
+daily travel (e.g., Smith, 2017; Mokhtarian and Pendyala, 2018; St-Louis
+et al., 2014). Scholars have shown that accessibility has been the most
+developed factor that influences people's wellbeing (Delbosc, 2012), and
+activities have a direct impact on travel satisfaction (Cecilia
+Jakobsson Bergstad et al., 2011). Delbosc (2012, p. 28), for instance,
+has summarised the most significant influences on psychological
+wellbeing: poverty and employment, meaningful relationships and health.
+However, understanding the components affecting people's perceptions
+implies the differentiation between affective (also named as
+symbolic-affective) and instrumental values (C. J. Bergstad et al.,
+2011). Steg et al.~(2011) have compared symbolic-affective opposed to
+instrumental-reasoned motives based on car-use, and other studies have
+also found associations between affective and symbolic aspects of
+car-use (see, e.g., Gatersleben and Uzzell, 2007; Lois and Lopez-Saez,
+2009). Previous studies have also demonstrated how socio-demographic
+factors affect the levels of SWB. The effect of income on SWB (Clark and
+Oswald, 1996; Ferrer-i-Carbonell, 2005); education and unemployment
+(Argyle et al., 1999); age (Diener and Eunkook Suh, 1997), and gender
+(Tesch-Römer et al., 2008) have been extensively studied. Recent
+research also suggests the links between commuting, SWB and emotional
+wellbeing assessment (\textbf{Olson et al.~2013}; \textbf{Kahneman et
+al.~2004}). However, more research is needed to understand how these
+socio-demographic variables connect as well with the affective responses
+to mode of travel (St-Louis et al., 2014).
 
@@
 experiencing feelings of belonging to a civic culture and the enjoyment
-and pleasure of travel itself (Bejarano et al., 2019). This paper
-contributes to further our understanding of affective and instrumental
-factors in travel behaviour in a developing country.
+and pleasure of travel itself (Bejarano et al., 2017). This paper
+contributes to further our understanding of affective values in travel
+behaviour in a developing country.
 
 \hypertarget{data-and-methods}{%
-\section{Data and Methods}\label{data-and-methods}}
+\section{3. Data and Methods}\label{data-and-methods}}
 
-This paper implements an analysis of correspondence comparing the
-primary mode of transportation with affective and utilitarian SWB
-factors in a sample of travellers in Santiago de Chile.
+\hypertarget{context}{%
+\section{3.1 Context}\label{context}}
+
+Words to describe Santiago go here.
 
 \hypertarget{sample}{%
-\subsection{Sample}\label{sample}}
+\section{3.2 Sample}\label{sample}}
 
-The study is based on a survey conducted in Santiago during the months
-of November and December 2016, that collected information on a wide
+The study is based on a survey conducted in the city of Santiago during
+the months of November and December 2016, that is, the end of the Spring
+and beginning of Summer. The survey collected information on a wide
 range of travel and related issues. The data collection considered a
@@
 representation of both genders and a representation of the proportion of
-inhabitants per area have been chosen as relevant characteristics of the
-sample. In total, 451 persons validly completed the survey. In the first
-part of the questionnaire the participants were asked about basic
-socio-demographic data and main transport mode for commuting. In the
-second part, the questionnaire asked about the modes that people
-associate with affective and instrumental positive concepts of
-commuting, as well as the levels of overall satisfaction with the trips.
-These two sections of the survey have been considered for the analysis
-of this paper. The second part of the survey asked about the association
-between the primary transport mode and 18 positive and negative
-feelings. The question is: ``Indicate the modes that you associate to
-the following feelings''. The respondents could indicate all the modes
-they associated to the feelings on the list. Three affective and three
-instrumental/utilitarian factors, all positive, have been considered for
-this analysis: freedom, enjoyment, happiness (affective), and security,
-time savings, efficiency (instrumental/utilitarian). The questionnaire
-provides a binary indicator that describes the presence or absence of
-modal correspondence for each one the selected six factors. The analysis
-has considered socioeconomic variables (gender, age, education,
-occupation, income, disabilities), as well as other variables as driving
-licence, journey times, monthly expenditure on transport and
-satisfaction with the overall trip.
+inhabitants per area were chosen as relevant characteristics of the
+sample. In total, there were \(n=451\) valid surveys, although not every
+survey was complete and there were missing responses for some answers.
 
-{[}REPORT DESCRIPTIVE STATISTICS? Include definitions, e.g., is K-12
-equivalent to ``minimal mandatory education''? What is Tech Univ? What
-are the range of values of low, middle, high income? Journey time is in
-minutes{]}
+The survey was structured in eight sections, as follows: 1) Individual
+characteristics of respondent; 2) Health; 3) Feelings and emotions; 4)
+Reasons for travel and planning travel; 5) Social interaction; 6) Nature
+and sustainability; 7) Information and telecommunications; 8) Built
+environment; and 9) Commuting. For the present study, we draw data from
+sections 1), 3) and 9). In terms of individual characteristics of the
+respondents and their commute, participants were asked about basic
+socio-demographic information, including age, level of education,
+income, and the typical duration of their regular commute. The
+descriptive statistics of the sample appear in Figure
+\ref{fig:descriptive-statistics}. The sample tends to be younger, and
+well-educated, with an almost uniform distribution of income levels. The
+trend in typical commute time is towards longer commutes.
 
-\hypertarget{analytical-approach}{%
-\subsection{Analytical Approach}\label{analytical-approach}}
+\begin{figure}
+\centering
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/plot-descriptive-statistics-1.pdf}
+\caption{\label{fig:descriptive-statistics}Descriptive statistics of the
+sample}
+\end{figure}
 
-The analytical approach in this paper is based on correspondence.
-Previous research has developed the concept of modal dissonance for
-referring to the mismatch between the actual mode and the mode that
-enables users to experience positive affective or instrumental factors
-(De Vos et al., (2012; 2014) and Schwanen and Mokhtarian, 2004, 2005a,
-2005b). More concretely, Schwanen and Mokhtarian (2004; 89) define
-dissonance based on the incongruence between residential neighbourhood
-where the individual currently resides and her preference structure
-toward such characteristics of the residential environment. In this
-paper we consider correspondence, which happens when travellers
-associate the positive utilitarian and affective SWB factors to the mode
-they have used as their primary transport mode for commuting or
-performing their main activities. The opposite of correspondence would
-be modal dissonance.
+In addition, respondents were asked about their primary mode of travel
+for their regular commute. The modes available were Car, Taxi, Colectivo
+(a form of shared ride, intermediate in flexibility and capacity between
+taxi and bus); Motorcycle; Metro; Bus; Bicycle; Walking. As seen in the
+top panel of Figure \ref{fig:primary-mode-travel}, the three most common
+modes of travel are Metro, Bus, and Car, followed by Walking and Biycle.
+For the analysis, we aggregate these modes into the following categories
+(bottom panel of Figure \ref{fig:primary-mode-travel}): Car, Active
+(Walking + Bicycle), Public (Metro + Bus), and Other (Taxi + Colectivo +
+Motorcycle).
 
-More specifically, the concept of modal dissonance means that a user of
-mode X identifies a different mode Y when associating affective values.
-For example, a user of private transport (i.e., mode ``Car'') may select
-mode ``Bicycle'' when asked about the of the association between the
-concept of freedom to a transport mode. In this case, the person who
-uses the mode ``Car'' as their primary mode of transportation attaches
-positive emotional and instrumental factors not to that mode, but to a
-different one -- in this case to the bicycle. It could be the case that
-the modal dissonance corresponds just to one of the types of factors,
-either affective or instrumental. For example, it is possible that a
-person who uses the Metro as their main transport mode associates that
-mode to the instrumental factors (security, time savings, efficiency) --
-but relates positive emotional factors (freedom, enjoyment, happiness)
-to a different mode, say to the bicycle.
+\begin{figure}
+\centering
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-primary-mode-travel-1.pdf}
+\caption{\label{fig:primary-mode-travel}Frequency of primary mode used
+for regular commute; top panel: all modes, bottom panel: aggregated
+modes}
+\end{figure}
 
-The ways for measuring equity in transport projects and the most
-vulnerable groups affected by transport have been the aspects that have
-nurtured the focus of this study. The hypothesis is that public
-transport users will show a lower correspondence between their primary
-mode and the modes they relate with positive factors of SWB. This is
-relevant as more disadvantaged people have less options of choosing
-their preferred transport modes and they tend to associate positive
-affective and instrumental factors to modes that they are not able to
-use. These perceptions evidence equity gaps between groups -- where the
-most vulnerable groups are much more affected. The methods used are
-analysis of correspondence and multinomial regression, both around the
-associations of transport modes and affective and instrumental factors,
-derived from the SWB framework.
+Of particular interest for the present study is the following question
+in Part 3) of the survey:
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\begin{quote}
+\begin{quote}
+Q: Please indicate the mode(s) of transport that you relate to the
+following feelings and concepts
+\end{quote}
+\end{quote}
+
+The question was asked for each of the following affective values:
+Freedom; Enjoyment; Happiness; Poverty; Luxury; and Status. The
+respondents were not constrained to select only one alternative, but
+could indicate by means of a checkbox any and all modes that they felt
+aligned with each affective value. This allows us to do an analysis of
+modal dissonance, a concept introduced into the transportation
+literature by Schwanen and Mokhtarian (2004) based on earlier work by
+Feldman (1990). Residential neighborhood-type dissonance was defined by
+Schwanen and Mokhtarian (2004) as an incongruence in terms of the the
+land use patterns at the place of residence of an individual, and the
+individual's preferences. The concept of dissonance has since been
+extended in the travel behavior literature to encompass the mismatch
+between the choices individuals make, and the alternatives that would
+enable users to experience affective or instrumental values. This
+includes, for example, travel mode dissonance (De Vos, 2018).
+
+Based on the primary mode of travel and the questions about affective
+values, we derived a series of travel mode dissonance variables
+according to the following rule: \[
+D_i = 
+\begin{cases}
+0 & if \text{ primary mode} = \text{mode associated with value } i\\
+1 & \text{ otherwise}
+\end{cases}
+\] Therefore, if a respondent's primary mode of travel is Car, but
+indicated any other mode or modes in relation to Freedom, the respondent
+experienced dissonance: \[
+D_{\text{Freedom}} = 1
+\]
+
+Furthermore, we also expanded the responses to account for all modes
+identified by respondents in relation to the affective values. However,
+to avoid double counting the respondents in our frequency tabulations,
+we also calculated a sample weight that was the inverse of the number of
+modes selected in response to each affective value. For instance, if a
+respondent selected two modes in relation to affective value \(i\), the
+two modes receive a weight of \(1/2\); if a respondent selected three
+modes, then their weights are \(1/3\); and so on. In this way we do not
+treat unfairly those who selected only one mode, and the sum of all
+weighted modes is equal to the sample size.
+
+\hypertarget{analysis-and-results}{%
+\section{4. Analysis and Results}\label{analysis-and-results}}
+
+In what follows, analysis is done on two related but distinct questions.
+The first part of the analysis seeks to understand \emph{who}
+experiences dissonance, and the second part, building off that, aims to
+explore which modes of travel are more commonly identified as embodying
+affective values by those travellers who experience dissonance.
+
+Please note that this document was prepared using R Markdown and
+contains reproducible analysis. The R markdown file, along with the data
+file needed to reproduce the analysis, can be downloaded from the
+following anonymous Drive folder:
+
+https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg
 
 \hypertarget{who-experiences-dissonance}{%
-\subsection{Who experiences
+\section{4.1 Who experiences
 dissonance?}\label{who-experiences-dissonance}}
 
-The first step of the analysis seeks to understand whether there are
-statistical associations between the variables of interest. The analysis
-considers the cases where there is a lack of correspondence between the
-primary mode choice and the 6 SWB/instrumental factors previously
-described -- or in other words, where there is modal dissonance.
+To investigate the first question in our analysis, we create contingency
+tables that tabulate the frequency of dissonance with respect to each
+affective value, stratified by the attributes of Age, Education, Income,
+Primary Mode of Travel, and typical Commute Time. Table
+\ref{tab:cross-tabulation-results-without-instrumental} presents the
+frequency (in percentage) of dissonance, in other words, the percentage
+of respondents out of the total in their stratum who indicated mode or
+mode(s) for the affective value that do not correspond to their primary
+mode of travel.
 
-Table 1 shows the results of the analysis of correspondence and the
-dissonances between the primary mode of travel on the one hand, and SWB
-and instrumental factors on the other. As seen in the table, there are
-five categories that we use for the analysis. Three of these categories
-are socio-economic and demographic, namely age, level of education,
-income. The other two categories are transportation related, namely
-primary mode of travel and journey time. Correspondence is tested in
-every case by means of the \(\chi^2\) statistic. It is interesting to
-note that the only category for which all affective/instrumental factors
-are significant at better than 5\% level of confidence is mode of
-travel.
+As seen in the table, there are five characteristics of the respondents
+and their commutes that we use in the analysis. Three of these
+categories are socio-economic and demographic, namely age, level of
+education, and income. The other two are transportation related, namely
+primary mode of travel and commute time. The frequency tables were
+tested in every case by means of the \(\chi^2\) test of independence
+(\(p\)-values are reported in the table; lower \(p\)-values mean that
+the null hypothesis of independence can be rejected with greater
+confidence). It is interesting to note that the only category for which
+all affective values are significant at better than 5\% level of
+confidence is mode of travel.
 
-With respect to age, we observe that levels of dissonance tend to be
-high in general, and the results indicate that when it comes to
-affective factors, dissonance levels tend to be significantly higher for
-younger travellers, in particular Enjoyment. In terms of instrumental
-factors, dissonance also tends to significantly decline with age when
-considering Security. On the other hand, the levels of dissonance in
-terms of Time Savings and Efficiency, while high, do not show
-significant differences by age group. Overall, the findings suggest that
-dissonance tends to decline with age.
+\hypertarget{age}{%
+\subsubsection{4.1.1 Age}\label{age}}
 
-The results indicate that the category of Education is less useful to
-discriminate between different levels of dissonance. Two affective
-factors are significant at 10\% or better (Freedom and Happiness) and
-show that dissonance tends to decline at higher levels of education. One
-instrumental factor is significant at 10\% or better (Time Savings) and
-we see there that the level of dissonance tends to grow with higher
-levels of education. Another instrumental factor (Security) is
-significant at 5\% or better and shows that dissonance in this factor
-declines with higher education. The picture that emerges is of highly
-educated people who are relatively less dissatisfied with their primary
-mode of transportation when it comes to Freedom, Happiness, and
-Security, but more dissatisfied with their Time Savings than people who
-are less highly educated.
+With respect to Age, previous studies have reported that older adults
+tend to be more satisfied with their travel experience than younger
+people (Cao and Ettema, 2014; De Vos et al., 2016; Ye and Titheridge,
+2017). In the case, we find that five affective values show dissonance
+that significantly deviates from the null hypothesis of independence,
+namely Freedom, Enjoyment, Happiness, Luxury, and Status. We observe
+that levels of dissonance tend to be high in general, and in no case
+less than 60\%. For instance, almost 90\% of travellers younger than 35
+experience travel mode dissonance with respect to Freedom, and more than
+94\% experience dissonance with respect to enjoyment. In general,
+younger travellers tend to experience dissonance more frequently, with
+dissonance being less frequent for older travellers. The exception to
+this trend is Luxury, an affective value for which older travellers (age
+\textgreater{}54) experience dissonance more frequently than mid-aged
+travellers (ages 35-54).
 
-In general, dissonance tends to be higher for lower income individuals.
-Table 1 shows that the low-income segment has a significantly higher
-percentage of cases of dissonance for two affective factors. In the case
-of Freedom, for example, the lack of correspondence for low-income is
-83.9\% compared to 60\% for the high-income segment. The levels of
-dissonance are higher for Enjoyment and follow the same decreasing trend
-for higher levels of income. Dissonance is marginally lower for
-instrumental factors, and significant for Security and Time Savings.
+\hypertarget{education}{%
+\subsubsection{4.1.2 Education}\label{education}}
 
-As noted above, there are significant differences in dissonance by
-primary mode of travel, both for affective and instrumental factors. For
-affective factors, the highest levels of dissonance tend to be for users
-of public transportation, and the lowest for car users and active
-travellers. For instance, feelings of Freedom, Enjoyment, and Happiness
-are more frequently expressed by users of car and active travellers than
-users of public transportation. Indeed, people who travel by Metro or
-Bus almost never associate any of these positive affective attributes to
-these modes (dissonance is consistently greater than 90\%). In contrast,
-active travellers have some of the lowest levels of dissonance in all
-three affective factors, in particular Freedom and Happiness. This
-analysis is in line with previous research regarding car, active travel,
-and public transportation (e.g., Steg et al., 2001; Páez and Whalen,
-2010; Whalen et al., 2013), which tend to agree on the negative
-associations in the perception of affective factors when the primary
-mode is Metro or bus.
+When seen from the perspective of Education, the results do not support
+the hypothesis of significant differences in the frequency of dissonance
+by levels of education for the values of Freedom, Enjoyment, Happiness,
+and Poverty, and only two affective values show significant differences
+between education levels: Luxury and Status. In the case of Luxury,
+dissonance is more frequent among people who have only K-12 education,
+and less frequently, albeit still high, for people with
+technical/university level education and post-graduate education.
+Furthermore, highly educated people (with postgraduate degrees)
+experience dissonance with respect to Status more frequently than with
+respect to Luxury.
 
-Figure 4 shows the percentage of dissonance by primary transport mode,
-for both affective and instrumental factors. For instance, the graph at
-the top shows that the highest percentages of dissonances come from
-users of Metro and bus , compared to other modes as the car or active
-transport. This is consistent with previous studies that have separately
-demonstrated that public transport users tend to assess more negatively
-subjective factors (explored e.g.~in Stradling et al., 1999; Gatersleben
-and Uzzell, 2007). For example, although car users have higher
-dissonance values than active transport, comparatively this segment has
-much lower percentages of dissonances than public transport, idea also
-supported by research that has shown that car users tend to attribute
-importance to symbolic aspects that positively contribute to their
-perception on driving (Steg et al., 2001; Mokhtarian and Salomon, 2001).
+\hypertarget{income}{%
+\subsubsection{4.1.3 Income}\label{income}}
 
-Freedom and happiness tend to have a lower percentage of dissonances in
-the case of active transport, which means that cyclists and individuals
-who mainly walk for their commutes, tend to associate positive
-subjective values while using these modes. This is also consistent with
-other studies that have shown positive affective associations with the
-use of cycling and walking (Anable and Gatersleben, 2005; Gatersleben
-and Uzzell, 2007). The question at the survey has not specify the
-dimensions of freedom, thus has open the door for different
-interpretations as the freedom to choose certain mode or route, freedom
-while using the mode, or the freedom to access to certain places while
-travelling. Journey time: As shown in Figure 3, the analysis carried out
-by journey time also reveals coincidences with previous research in this
-area, since for shorter trips (up to 20 minutes) the analysis shows less
-dissonance between the primary mode and positive subjective associations
-mainly for affective factors. On the contrary, as journey time
-increases, higher is the dissonance. Strangely, the feelings of Security
-and Efficiency have not been statistically representative for the
-Journey Time analysis.
+The next variable we examine is income, and in this case three affective
+values are significant: Poverty, Luxury, and Status. Since Poverty is a
+negative affect, we see here that lower income people tend to associate
+this feeling to their primary mode of commuting more frequently (almost
+20\% of the time) than other income groups. For example, whereas
+approximately 16\% of mid-income people are dissatisfied with their
+primary mode of travel in this respect, less than 7\% of high income
+individuals are. Dissonance with respect to Luxury and Status also tends
+to be more common among lower income people, and declines substantially
+for mid- and high income respondents. Notice as well that the frequency
+of dissonance is higher in terms of Luxury than Status for mid- and high
+income people.
 
-In terms of instrumental factors, interestingly Figure 4 shows that bus
-users have the lowest percentage of dissonance regarding time savings
-(29\%). However, considering the other instrumental factors, bus users
-have a high percentage of dissonance for security and efficiency. In the
-case of security, this means that most bus users (71\%) have considered
-the bus as a mode that they associate to time-savings, although it is
-the mode that has more dissonant evaluations in all other SWB factors.
-This also seems difficult to explain considering the negative evaluation
-that the Transantiago system has consistently had. Some data provided by
-the Survey of Satisfaction with Transantiago Operators (DTPM, 2017) is
-about users' perception of journey time from origin to destination. In
-this question, and after 10 years of implementation of the system, users
-diagnose an average journey of 47 minutes, a value that tends to
-increase with respect to the data delivered by the same survey 5 years
-before (43.5 minutes on average). Worryingly, long trips of more than 30
-minutes have had inconsistent variability over the years, reaching an
-average of more than 37 minutes in 2016. Short trips, however, remain
-roughly equal to previous years, and do not show significant changes in
-the average of 6-7 minutes per trip . This survey has the peculiarity of
-being developed by the Metropolitan Public Transport Board (DTPM), whose
-mission is to articulate the functions of the different modes of public
-transport with a specific interest in buses Transantiago and Metro de
-Santiago.
+\hypertarget{primary-mode-of-travel}{%
+\subsubsection{4.1.4 Primary mode of
+travel}\label{primary-mode-of-travel}}
 
-Another big gap on these instrumental factors relates to the perception
-of security that is especially significant for car users. This means
-that a 75\% of car users have chosen as primary mode the same one as
-they relate to the feeling of security, which is completely opposite to
-other transport modes, specially bus users. Bus users have the highest
-dissonance (98\%), which means that practically all this group of users
-have chosen another mode for referring to the feelings of security. The
-recently referred DTPM survey does not have any particular question that
-addresses the issue of safety -- mostly related in this context as
-security.
+The variable that shows the largest differences in the frequency of
+dissonance is the primary mode of travel. It can be seen in Table
+\ref{tab:cross-tabulation-results-without-instrumental} that the
+differences are significative for all six affective values. Dissonance
+is particularly accute for users of public transportation when it comes
+to the values of Freedom, Enjoyment, and Happiness: almost 100\% of
+users of public transportation have identified other mode or modes as
+better representing those values. Dissonance on these values is the
+least for active travellers: less than 50\% of respondents associate
+Freedom to a different mode, and only around 60\% identified a different
+mode when responding to the values of Enjoyment and Happiness, compared
+to approximately 79\% and 71\% of those who travelled by Car. The
+picture changes when the values of Poverty, Luxury, and Status are
+considered. In this case, dissonance is less frequent for people who
+travel by car: less than 3\% of car users associate car with feelings of
+poverty, 41\% associate Luxury with a mode other than car, and only
+about 31\% relate Status to a different mode. Dissonance is more
+frequent in these values for active travellers, and users of public
+transportation and other modes, in no case being less than 75\%, and
+being virtually 100\% for users of public transportation, who
+consistently associate Luxury and Status with modes \emph{other} than
+public transportation.
+
+\hypertarget{typical-commute-time}{%
+\subsubsection{4.1.5 Typical commute time}\label{typical-commute-time}}
+
+Turning now to typical commute time, four affectie values show
+significant differences at better than 10\% confidence: Freedom,
+Happiness, Luxury, and Status. Perhaps not surprisingly, dissonance is
+more frequent among people whose typical commutes are longer. This is in
+line with previous findings: both St-Louis et al.~(2014) and Smith
+(2017) report that commute satisfaction tends to decline with longer
+commutes, whereas Handy and Thigpen (2019) found that commute distance
+was a negative covariate of commute satisfaction.
 
@@
 
-\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors}
+\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results-without-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors}
 \centering
@@
 \multicolumn{13}{l}{\textbf{Mode}}\\
-\hspace{1em}Auto & 58.93 &  & 78.90 &  & 70.91 &  & 97.96 &  & 41.00 &  & 30.69 & \\
+\hspace{1em}Car & 58.93 &  & 78.90 &  & 70.91 &  & 97.96 &  & 41.00 &  & 30.69 & \\
 
@@
 \addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Journey Time}}\\
+\multicolumn{13}{l}{\textbf{Commute Time}}\\
 \hspace{1em}< 20 min & 65.93 &  & 82.95 &  & 77.27 &  & 86.11 &  & 73.49 &  & 67.09 & \\
@@
 
-Figure 5 shows the points of origin of the survey for the case of public
-transport users. Metro users as primary mode are shown, bus users are
-shown in cyan. The size of the points represents the number of
-dissonances. The higher the point, the greater the number of SWB factors
-that do not coincide with the primary transport mode. The image shows
-that the intensity or size of the circles is homogeneously distributed
-in the territory, even though the blue circles (metro) tend to show
-slightly less dissonance. The visualisation of this map is more dramatic
-when it is compared to the following Figure 6.
+\textbf{FOR DISCUSSION}
 
-Figure 6 shows the points of origin for the case of private transport
-(cars) and active transport (walking and cycling). Again, the size of
-the circles represents intensity levels of dissonance. The number of
-dissonances is lower than in the case of Figure 5, which indicates that
-users of private and active transport tend to use a mode of transport
-that they relate to one of the positive factors derived from subjective
-wellbeing. In this sense, it could be said that this type of user tends
-to be more advantaged than the public transport user, in a dimension not
-only utilitarian but also emotional and attitudinal.
+Al-Ayyash and Abou-Zeid (2019) Bornioli et al. (2019) De Vos et al.
+(2019) Gatersleben and Uzzell (2007) Smith (2017) Ye and Titheridge
+(2017)
 
-\hypertarget{which-modes-do-travelers-associate-with-affective-and-instrumental-values}{%
-\subsection{Which modes do travelers associate with affective and
-instrumental
-values?}\label{which-modes-do-travelers-associate-with-affective-and-instrumental-values}}
+\hypertarget{which-modes-do-travellers-associate-with-affective-values}{%
+\subsection{4.2 Which modes do travellers associate with affective
+values?}\label{which-modes-do-travellers-associate-with-affective-values}}
 
-Here we can visualize the modes that travellers associate with different
-affective and instrumental values. The tool we use for this is a mosaic
-plot. See the mosaic plots in Figure
-\ref{fig:mosaic-plots-by-attribute}.
+The preceding analysis suggests that there is significant mode
+dissonance along various dimensions and for various affective values.
+Once we have developed a profile of the travelers who experience mode
+dissonance, we are interested in what modes they tend to associate with
+various affective values. For this analysis, we employ a visualization
+technique known as a mosaic plot that is used for exploring categorical
+data (Friendly, 1994; Hofmann, 2000). A mosaic plot is a visual
+representation of a multi-way contingency table, whereby the dimensions
+of each tile in the mosaic are proportional to the values in the
+underlying table.
+
+We begin by plotting the cross-tabulation of primary mode of travel to
+mode associated with each affective value (see Figure
+\ref{fig:mosaic-plots-by-attribute}). The height of tile \(j\) in these
+mosaics corresponds to the proportion of travellers who primarily travel
+by mode \(j\), hence we can see that the most common primary mode of
+travel in this sample is by public transportation, followed by car,
+active travel, and other (also see Figure
+\ref{fig:primary-mode-travel}). Notice that there are some small
+discrepancies in the heights across affective values: these are caused
+by a small number of non-responses. Next, the width of the tile \(k\) in
+the mosaics is proportional to the frequency with which a mode was named
+in relation to affective value \(i\). Recall that respondents could
+nominate more than one mode in response to each affective value, and
+some did. For this reason, we used sampling weights, so that the total
+number of responses corresponds to the size of the sample.
+
+In terms of Freedom, we see that Car users frequently identify this
+affect with the use of Car; however, those who do not, very often select
+Active Travel as the mode that better represents Freedom. A majority of
+active travellers, on the other hand, identify Active Travel as the mode
+associated with Freedom; few of them attach this value to Car, and even
+fewer to public transportation and other modes. Travellers whose primary
+mode of travel is public transportation seldom associate this mode with
+Freedom, and in fact more frequently relate this affective response to
+Active Travel followed by Car. Users of other modes seem to be split
+almost equally in their attribution of Freedom, between Active Travel,
+Car, and Other. In general, Active Travel is the mode most often
+identified as embodying Freedom, with the exception of Car travellers.
+
+The pattern with respect to Enjoyment is similar to that for Freedom,
+but with an even more decisive tilt towards Active Travel, with even
+more respondents whose primary mode of travel is Car choosing Active
+Travel as the mode that better represents Enjoyment. Notice that very
+few of Active Travelers selected Car as an enjoyable mode. Likewise,
+compared to Freedom, Active Travel is perceived as being more enjoyable
+by users of Public Transportatoin and Other modes. Responses with
+respect to Happiness are somewhere in between Freedom and Enjoyment, but
+Happiness is, if anything, even less frequently identified with Public
+Transportation.
+
+Three other affective responses show a marked difference. Public
+Transportation was seldom associated by respondents to feelings of
+Freedom, Enjoyment, and Happiness; on the other hand, it is the mode
+that is most commonly selected by respondents for evoking feelings of
+Poverty - even by users of Publi Transportation. Active Travel was the
+second most common response for its association with Poverty. Likewise,
+Whereas Active Travel was often associated to feelings of Freedom,
+Enjoyment, and Happiness, the mode most frequently associated with
+Luxury and Status is the Car, although active travellers seem to be
+somewhat more resistant to this association compared to respondents who
+travel by Car, Public Transportation, and Other modes.
+
+Next, we further explore these responses after stratifying by Age,
+Education, Income, and Commute Time. We test the underlying 3-way tables
+by means of the Cochran-Mantel-Haenszel \(\chi^2\) test of independence.
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+Efectivamente lujo y estatus parecen similares a primera vista (Figura
+1). En general, estos dos valores afectivos son asociados mucho mas
+comunmente con el automovil. Por otro lado, hay algunas diferencias
+interesantes cuando se les ve desde la perspectiva de diferentes
+viajeros.
+
+Por ejemplo, la tendencia a asociar estatus con el automovil tiende a
+incrementarse con la edad, con la posible excepcion de los usuarios de
+transporte publico, para quienes otras opciones (posiblemente taxi),
+ganan en estatus para los viajeros mayores (\textgreater{}54) a costa de
+otros modos, incluido el automovil. En contraste, el automovil pierde en
+el valor de lujo con la edad, mientras que otras opciones pasan a ser
+percibidas como lujo mas comunmente con la edad, incluso para los
+usuarios de automovil (Figure 2).
+
+se vuelven mas comunmente simbolos de estatus que cuando vemos la manera
+en que viajeros de diferentes edades proyectan lujo y estatus en varios
+modos, los usuarios de automovil mayores (\textgreater{}54) muestran
+menos disonancia en status que en lujo, mientras que los viajeros
+activos presentan mas disonancia en estatus que en lujo, y de hecho
+proyectan estatus mas comunmente en el automovil.
+
+La manera en que el lujo se asocia de manera relativamente mas frecuente
+con otras opciones que el estatus tambien se observa cuando vemos los
+diferentes niveles de educacion. La excepcion parece ser los usuarios de
+transporte activo, especialmente aquellos con educacion superior y de
+post-grado, que asocian tanto estatus como lujo con el transporte activo
+mas que los usuarios de otros modos.
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-without-instrumental-1.pdf}
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-1.pdf}
 \caption{\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective
@@
 
+\hypertarget{age-1}{%
+\subsubsection{4.2.1 Age}\label{age-1}}
+
+Words go here to discuss results by age.
+
 \begin{figure}
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-age-without-instrumental-1.pdf}
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-age-1.pdf}
 \caption{\label{fig:mosaic-plots-by-age}Mosaic plots for affective
@@
 of transportation, and the x-axis is the proportion of modes selected
-for each value}
+for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared
+Test)}
 \end{figure}
+
+\hypertarget{education-1}{%
+\subsubsection{4.2.2 Education}\label{education-1}}
+
+Words go here to discuss results by education.
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-education-without-instrumental-1.pdf}
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-education-1.pdf}
 \caption{\label{fig:mosaic-plots-by-education}Mosaic plots for affective
@@
 mode of transportation, and the x-axis is the proportion of modes
-selected for each value}
+selected for each value (p-values are for Cochran-Mantel-Haenszel
+Chi-Squared Test)}
 \end{figure}
+
+\hypertarget{income-1}{%
+\subsubsection{4.2.3 Income}\label{income-1}}
+
+Words go here to discuss results by income.
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-income-without-instrumental-1.pdf}
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-income-1.pdf}
 \caption{\label{fig:mosaic-plots-by-income}Mosaic plots for affective
@@
 mode of transportation, and the x-axis is the proportion of modes
-selected for each value}
+selected for each value (p-values are for Cochran-Mantel-Haenszel
+Chi-Squared Test)}
 \end{figure}
+
+\hypertarget{typical-commute-time-1}{%
+\subsubsection{4.3.4 Typical commute
+time}\label{typical-commute-time-1}}
+
+Words go here to discuss results by time.
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-time-without-instrumental-1.pdf}
+\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-time-1.pdf}
 \caption{\label{fig:mosaic-plots-by-travel-time}Mosaic plots for
-affective values by travel time; the y-axis is the proportion of
+affective values by commute time; the y-axis is the proportion of
 respondents by main mode of transportation, and the x-axis is the
-proportion of modes selected for each value}
+proportion of modes selected for each value (p-values are for
+Cochran-Mantel-Haenszel Chi-Squared Test)}
 \end{figure}
 
+\textbf{\emph{FOR DISCUSSION}}
+
+De Vos (2018)
+
 \hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\section{5. Conclusions}\label{conclusions}}
 
-Words go here.
+Accordingly, the aim of this paper is to analyse some of the factors
+that can potentially affect the levels of SWB in the wide spectrum of
+public, private and active transport modes in the context of Santiago de
+Chile. Previous research suggests that public transport users experience
+a negative gap in desired and actual travel time, whereas active
+travellers don't seem to mind somewhat longer trips than what strictly
+needed (e.g., Páez and Whalen, 2010). In the context of a Latin American
+country, historically the poor travel experience of public transit users
+and active travellers reflects the social inequalities of social groups
+that have no alternative but to move in these types of modes while
+living far from the work centres and main activities. The paper aims to
+reflect on the possibilities of increasing the SWB while travelling, and
+how this could increase the attractiveness of public transport and
+active travel in the socio-demographic groups studied. This can help not
+only to reduce the use of private transport but also decrease the
+inequality gap between these users.
+
+The paper explores how positive affective and instrumental/utilitarian
+factors of SWB correspond to the use of the primary mode of
+transportation. It uses an analysis of correspondence that considers the
+actual primary mode versus the mode that individuals associated to both
+utilitarian (designed to be useful or practical rather than attractive)
+and affective (expressing a person's feelings) SWB factors. For example,
+it will be analysed if a person who uses public transport as the primary
+mode, tends to associate these modes with positive affective factors (as
+freedom, enjoyment or happiness) or positive utilitarian factors (as
+security, time-savings or efficiency). We hypothesize that there is a
+more persistent non-correspondence or mismatch within the more
+disadvantage groups or within the users of public transport.
+
+\hypertarget{acknowledgments}{%
+\section{Acknowledgments}\label{acknowledgments}}
+
+The following \texttt{R} packages were used in the course of this
+investigation and the authors wish to acknowledge their developers:
+\texttt{ggmosaic} (Jeppson et al., 2018), \texttt{ggthemes} (Arnold,
+2018), \texttt{kableExtra} (Zhu, 2018), \texttt{knitr} (Xie, 2018,
+2015), \texttt{rticles} (Allaire et al., 2018), and \texttt{tidyverse}
+(Wickham, 2017).
 
@@
 
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Abenoza2017travel}{}%
+Abenoza, R.F., Cats, O., Susilo, Y.O., 2017. Travel satisfaction with
+public transport: Determinants, user classes, regional disparities and
+their evolution. Transportation Research Part A: Policy and Practice 95,
+64--84.
+
+\leavevmode\hypertarget{ref-Alayyash2019commute}{}%
+Al-Ayyash, Z., Abou-Zeid, M., 2019. Investigating commute satisfaction
+differences of private car users and public transport users in a
+developing country context. Transportation 46, 515--536.
+doi:\href{https://doi.org/10.1007/s11116-019-10000-2}{10.1007/s11116-019-10000-2}
+
+\leavevmode\hypertarget{ref-Allaire2018rticles}{}%
+Allaire, J., Xie, Y., R Foundation, Wickham, H., Journal of Statistical
+Software, Vaidyanathan, R., Association for Computing Machinery,
+Boettiger, C., Elsevier, Broman, K., Mueller, K., Quast, B., Pruim, R.,
+Marwick, B., Wickham, C., Keyes, O., Yu, M., Emaasit, D., Onkelinx, T.,
+Gasparini, A., Desautels, M.-A., Leutnant, D., MDPI, Ögreden, O., Hance,
+D., Nüst, D., 2018. Rticles: Article formats for r markdown.
+
+\leavevmode\hypertarget{ref-Anable2005work}{}%
+Anable, J., Gatersleben, B., 2005. All work and no play? The role of
+instrumental and affective factors in work and leisure journeys by
+different travel modes. Transportation Research Part A 39, 163--181.
+
+\leavevmode\hypertarget{ref-Angotti1996latin}{}%
+Angotti, T., 1996. Latin american urbanization and planning: Inequality
+and unsustainability in north and south. Latin American Perspectives 23,
+12--34.
+doi:\href{https://doi.org/10.1177/0094582X9602300403}{10.1177/0094582X9602300403}
+
+\leavevmode\hypertarget{ref-Argyle1999causes}{}%
+Argyle, M., Kahneman, D., Diener, E., Schwarz, N., 1999. Causes and
+correlates of happiness well-being: The foundations of hedonic
+psychology.(pp. 353-373). New York, NY US: Russell Sage Foundation.
+
+\leavevmode\hypertarget{ref-Arnold2018}{}%
+Arnold, J.B., 2018. Ggthemes: Extra themes, scales and geoms for
+'ggplot2'.
+
+\leavevmode\hypertarget{ref-Bejarano2017user}{}%
+Bejarano, M., Ceballos, L.M., Maya, J., 2017. A user-centred assessment
+of a new bicycle sharing system in medellin. Transportation Research
+Part F-Traffic Psychology and Behaviour 44, 145--158.
+doi:\href{https://doi.org/10.1016/j.trf.2016.11.004}{10.1016/j.trf.2016.11.004}
+
+\leavevmode\hypertarget{ref-Bergstad2011subjective}{}%
+Bergstad, C.J., Gamble, A., Gärling, T., Hagman, O., Polk, M., Ettema,
+D., Friman, M., Olsson, L.E., 2011. Subjective well-being related to
+satisfaction with daily travel. Transportation 38, 1--15.
+
+\leavevmode\hypertarget{ref-Bergstad2011affective}{}%
+Bergstad, C.J., Gamble, A., Hagman, O., Polk, M., Garling, T., Olsson,
+L.E., 2011. Affective-symbolic and instrumental-independence
+psychological motives mediating effects of socio-demographic variables
+on daily car use. Journal of Transport Geography 19, 33--38.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.11.006}{10.1016/j.jtrangeo.2009.11.006}
+
+\leavevmode\hypertarget{ref-Bocarejo2012transport}{}%
+Bocarejo, S.J.P., Oviedo, H.D.R., 2012. Transport accessibility and
+social inequities: A tool for identification of mobility needs and
+evaluation of transport investments. Journal of Transport Geography 24,
+142--154.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2011.12.004}{10.1016/j.jtrangeo.2011.12.004}
+
+\leavevmode\hypertarget{ref-Bornioli2019affective}{}%
+Bornioli, A., Parkhurst, G., Morgan, P.L., 2019. Affective experiences
+of built environments and the promotion of urban walking. Transportation
+Research Part a-Policy and Practice 123, 200--215.
+doi:\href{https://doi.org/10.1016/j.tra.2018.12.006}{10.1016/j.tra.2018.12.006}
+
+\leavevmode\hypertarget{ref-Boschman2008toward}{}%
+Boschmann, E.E., Kwan, M.P., 2008. Toward socially sustainable urban
+transportation: Progress and potentials. International Journal of
+Sustainable Transportation 2, 138--157.
+
+\leavevmode\hypertarget{ref-Brown2009planning}{}%
+Brown, J.R., Morris, E.A., Taylor, B.D., 2009. Planning for cars in
+cities: Planners, engineers, and freeways in the 20th century. Journal
+of the American Planning Association 75, 161--177.
+doi:\href{https://doi.org/10.1080/01944360802640016}{10.1080/01944360802640016}
+
+\leavevmode\hypertarget{ref-Cao2014satisfaction}{}%
+Cao, X.Y., Ettema, D.F., 2014. Satisfaction with travel and residential
+self-selection: How do preferences moderate the impact of the hiawatha
+light rail transit line? Journal of Transport and Land Use 7, 93--108.
+doi:\href{https://doi.org/10.5198/jtlu.v7i3.485}{10.5198/jtlu.v7i3.485}
+
+\leavevmode\hypertarget{ref-Chapman2007transport}{}%
+Chapman, L., 2007. Transport and climate change: A review. Journal of
+Transport Geography 15, 354--367.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2006.11.008}{10.1016/j.jtrangeo.2006.11.008}
+
+\leavevmode\hypertarget{ref-Chatterjee2019commuting}{}%
+Chatterjee, K., Chng, S., Clark, B., Davis, A., De Vos, J., Ettema, D.,
+Handy, S., Martin, A., Reardon, L., 2019. Commuting and wellbeing: A
+critical overview of the literature with implications for policy and
+future research. Transport Reviews 30.
+doi:\href{https://doi.org/10.1080/01441647.2019.1649317}{10.1080/01441647.2019.1649317}
+
+\leavevmode\hypertarget{ref-Clark1996satisfaction}{}%
+Clark, A.E., Oswald, A.J., 1996. Satisfaction and comparison income.
+Journal of public economics 61, 359--381.
+
+\leavevmode\hypertarget{ref-Delbosc2012role}{}%
+Delbosc, A., 2012. The role of well-being in transport policy. Transport
+Policy 23, 25--33.
+doi:\href{https://doi.org/10.1016/j.tranpol.2012.06.005}{10.1016/j.tranpol.2012.06.005}
+
+\leavevmode\hypertarget{ref-Devos2018people}{}%
+De Vos, J., 2018. Do people travel with their preferred travel mode?
+Analysing the extent of travel mode dissonance and its effect on travel
+satisfaction. Transportation Research Part a-Policy and Practice 117,
+261--274.
+doi:\href{https://doi.org/10.1016/j.tra.2018.08.034}{10.1016/j.tra.2018.08.034}
+
+\leavevmode\hypertarget{ref-Devos2019satisfaction}{}%
+De Vos, J., 2019. Satisfaction-induced travel behaviour. Transportation
+Research Part F-Traffic Psychology and Behaviour 63, 12--21.
+doi:\href{https://doi.org/10.1016/j.trf.2019.03.001}{10.1016/j.trf.2019.03.001}
+
+\leavevmode\hypertarget{ref-Devos2016travel}{}%
+De Vos, J., Mokhtarian, P.L., Schwanen, T., Van Acker, V., Witlox, F.,
+2016. Travel mode choice and travel satisfaction: Bridging the gap
+between decision utility and experienced utility. Transportation 43,
+771--796.
+
+\leavevmode\hypertarget{ref-Devos2013travel}{}%
+De Vos, J., Schwanen, T., Van Acker, V., Witlox, F., 2013. Travel and
+subjective well-being: A focus on findings, methods and future research
+needs. Transport Reviews 33, 421--442.
+doi:\href{https://doi.org/10.1080/01441647.2013.815665}{10.1080/01441647.2013.815665}
+
+\leavevmode\hypertarget{ref-Devos2015satisfying}{}%
+De Vos, J., Schwanen, T., Van Acker, V., Witlox, F., 2015. How
+satisfying is the scale for travel satisfaction? Transportation Research
+Part F-Traffic Psychology and Behaviour 29, 121--130.
+doi:\href{https://doi.org/10.1016/j.trf.2015.01.007}{10.1016/j.trf.2015.01.007}
+
+\leavevmode\hypertarget{ref-Devos2019satisfying}{}%
+De Vos, J., Schwanen, T., Van Acker, V., Witlox, F., 2019. Do satisfying
+walking and cycling trips result in more future trips with active travel
+modes? An exploratory study. International Journal of Sustainable
+Transportation 13, 180--196.
+doi:\href{https://doi.org/10.1080/15568318.2018.1456580}{10.1080/15568318.2018.1456580}
+
+\leavevmode\hypertarget{ref-Devos2017travel}{}%
+De Vos, J., Witlox, F., 2017. Travel satisfaction revisited. On the
+pivotal role of travel satisfaction in conceptualising a travel
+behaviour process. Transportation Research Part a-Policy and Practice
+106, 364--373.
+doi:\href{https://doi.org/10.1016/j.tra.2017.10.009}{10.1016/j.tra.2017.10.009}
+
+\leavevmode\hypertarget{ref-Diener1997subjective}{}%
+Diener, E., Eunkook Suh, M., 1997. Subjective well-being and age: An
+international analysis. Annual review of gerontology and geriatrics 17,
+304--324.
+
+\leavevmode\hypertarget{ref-Domarchi2008effect}{}%
+Domarchi, C., Tudela, A., Gonzalez, A., 2008. Effect of attitudes, habit
+and affective appraisal on mode choice: An application to university
+workers. Transportation 35, 585--599.
+doi:\href{https://doi.org/10.1007/s11116-008-9168-6}{10.1007/s11116-008-9168-6}
+
+\leavevmode\hypertarget{ref-Eriksson2013perceived}{}%
+Eriksson, L., Friman, M., Gärling, T., 2013. Perceived attributes of bus
+and car mediating satisfaction with the work commute. Transportation
+Research Part A: Policy and Practice 47, 87--96.
+
+\leavevmode\hypertarget{ref-Ettema2011satisfaction}{}%
+Ettema, D., Garling, T., Eriksson, L., Friman, M., Olsson, L.E., Fujii,
+S., 2011. Satisfaction with travel and subjective well-being:
+Development and test of a measurement tool. Transportation Research Part
+F-Traffic Psychology and Behaviour 14, 167--175.
+doi:\href{https://doi.org/10.1016/j.trf.2010.11.002}{10.1016/j.trf.2010.11.002}
+
+\leavevmode\hypertarget{ref-Ettema2010out}{}%
+Ettema, D., Garling, T., Olsson, L.E., Friman, M., 2010. Out-of-home
+activities, daily travel, and subjective well-being. Transportation
+Research Part a-Policy and Practice 44, 723--732.
+doi:\href{https://doi.org/10.1016/j.tra.2010.07.005}{10.1016/j.tra.2010.07.005}
+
+\leavevmode\hypertarget{ref-Feldman1990settlement}{}%
+Feldman, R.M., 1990. Settlement-identity: Psychological bonds with home
+places in a mobile society. Environment and behavior 22, 183--229.
+
+\leavevmode\hypertarget{ref-Ferrer2005income}{}%
+Ferrer-i-Carbonell, A., 2005. Income and well-being: An empirical
+analysis of the comparison income effect. Journal of public economics
+89, 997--1019.
+
+\leavevmode\hypertarget{ref-Friendly1994mosaic}{}%
+Friendly, M., 1994. Mosaic displays for multi-way contingency tables.
+Journal of the American Statistical Association 89, 190--200.
+
+\leavevmode\hypertarget{ref-Friman2013psychometric}{}%
+Friman, M., Fujii, S., Ettema, D., Gärling, T., Olsson, L.E., 2013.
+Psychometric analysis of the satisfaction with travel scale.
+Transportation Research Part A: Policy and Practice 48, 132--145.
+
+\leavevmode\hypertarget{ref-Garling2019role}{}%
+Garling, T., Bamberg, S., Friman, M., 2019. THE role of attitude in
+choice of travel, satisfaction with travel, and change to sustainable
+travel, Handbook of attitudes, vol 2: Applications, 2nd ed.
+
+\leavevmode\hypertarget{ref-Gatersleben2007affective}{}%
+Gatersleben, B., Uzzell, D., 2007. Affective appraisals of the daily
+commute - comparing perceptions of drivers, cyclists, walkers, and users
+of public transport. Environment and Behavior 39, 416--431.
+
+\leavevmode\hypertarget{ref-Gossling2014sustainable}{}%
+Gossling, S., Cohen, S., 2014. Why sustainable transport policies will
+fail: EU climate policy in the light of transport taboos. Journal of
+Transport Geography 39, 197--207.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2014.07.010}{10.1016/j.jtrangeo.2014.07.010}
+
+\leavevmode\hypertarget{ref-Handy2019commute}{}%
+Handy, S., Thigpen, C., 2019. Commute quality and its implications for
+commute satisfaction: Exploring the role of mode, location, and other
+factors. Travel Behaviour and Society 16, 241--248.
+doi:\href{https://doi.org/10.1016/j.tbs.2018.03.001}{10.1016/j.tbs.2018.03.001}
+
+\leavevmode\hypertarget{ref-Hofmann2000exploring}{}%
+Hofmann, H., 2000. Exploring categorical data: Interactive mosaic plots.
+Metrika 51, 11--26.
+
+\leavevmode\hypertarget{ref-Jeppson2019ggmosaic}{}%
+Jeppson, H., Hofmann, H., Cook, D., 2018. Ggmosaic: Mosaic plots in the
+'ggplot2' framework.
+
+\leavevmode\hypertarget{ref-Khreis2016health}{}%
+Khreis, H., Warsow, K.M., Verlinghieri, E., Guzman, A., Pellecuer, L.,
+Ferreira, A., Jones, I., Heinen, E., Rojas-Rueda, D., Mueller, N.,
+Schepers, P., Lucas, K., Nieuwenhuijsen, M., 2016. The health impacts of
+traffic-related exposures in urban areas: Understanding real effects,
+underlying driving forces and co-producing future directions. Journal of
+Transport \& Health 3, 249--267.
+doi:\href{https://doi.org/10.1016/j.jth.2016.07.002}{10.1016/j.jth.2016.07.002}
+
+\leavevmode\hypertarget{ref-Lois2009relationship}{}%
+Lois, D., Lopez-Saez, M., 2009. The relationship between instrumental,
+symbolic and affective factors as predictors of car use: A structural
+equation modeling approach. Transportation Research Part a-Policy and
+Practice 43, 790--799.
+doi:\href{https://doi.org/10.1016/j.tra.2009.07.008}{10.1016/j.tra.2009.07.008}
+
+\leavevmode\hypertarget{ref-Lucas2012transport}{}%
+Lucas, K., 2012. Transport and social exclusion: Where are we now?
+Transport Policy 20, 107--115.
+doi:\href{https://doi.org/10.1016/j.tranpol.2012.01.013}{10.1016/j.tranpol.2012.01.013}
+
+\leavevmode\hypertarget{ref-Lucas2019evolution}{}%
+Lucas, K., 2019. A new evolution for transport-related social exclusion
+research? Journal of Transport Geography 102529.
+doi:\href{https://doi.org/https://doi.org/10.1016/j.jtrangeo.2019.102529}{https://doi.org/10.1016/j.jtrangeo.2019.102529}
+
+\leavevmode\hypertarget{ref-Martens2012justice}{}%
+Martens, K., Golub, A., Robinson, G., 2012. A justice-theoretic approach
+to the distribution of transportation benefits: Implications for
+transportation planning practice in the united states. Transportation
+research part A: policy and practice 46, 684--695.
+
+\leavevmode\hypertarget{ref-Miller2011collaborative}{}%
+Miller, H.J., 2011. Collaborative mobility: Using geographic information
+science to cultivate cooperative transportation systems. Procedia -
+Social and Behavioral Sciences 21, 24--28.
+doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.sbspro.2011.07.005}{http://dx.doi.org/10.1016/j.sbspro.2011.07.005}
+
+\leavevmode\hypertarget{ref-Milne2012public}{}%
+Milne, E.M.G., 2012. A public health perspective on transport policy
+priorities. Journal of Transport Geography 21, 62--69.
+doi:\href{https://doi.org/https://doi.org/10.1016/j.jtrangeo.2012.01.013}{https://doi.org/10.1016/j.jtrangeo.2012.01.013}
+
+\leavevmode\hypertarget{ref-Mokhtarian2018travel}{}%
+Mokhtarian, P.L., Pendyala, R.M., 2018. Travel satisfaction and
+well-being, in: Friman, M., Ettema, D., Olsson, L.E. (Eds.), Quality of
+Life and Daily Travel, Applying Quality of Life Research-Best Practices.
+pp. 17--39.
+doi:\href{https://doi.org/10.1007/978-3-319-76623-2_2}{10.1007/978-3-319-76623-2\_2}
+
+\leavevmode\hypertarget{ref-Paez2010enjoyment}{}%
+Paez, A., Whalen, K., 2010. Enjoyment of commute: A comparison of
+different transportation modes. Transportation Research Part a-Policy
+and Practice 44, 537--549.
+doi:\href{https://doi.org/10.1016/j.tra.2010.04.003}{10.1016/j.tra.2010.04.003}
+
+\leavevmode\hypertarget{ref-Pereira2017distributive}{}%
+Pereira, R.H., Schwanen, T., Banister, D., 2017. Distributive justice
+and equity in transportation. Transport reviews 37, 170--191.
+
+\leavevmode\hypertarget{ref-Redman2013quality}{}%
+Redman, L., Friman, M., Gärling, T., Hartig, T., 2013. Quality
+attributes of public transport that attract car users: A research
+review. Transport policy 25, 119--127.
+
+\leavevmode\hypertarget{ref-Redmond2001positive}{}%
+Redmond, L.S., Mokhtarian, P.L., 2001. The positive utility of the
+commute: Modeling ideal commute time and relative desired commute
+amount. Transportation 28, 179--205.
+
+\leavevmode\hypertarget{ref-Schwanen2004extent}{}%
+Schwanen, T., Mokhtarian, P.L., 2004. The extent and determinants of
+dissonance between actual and preferred residential neighborhood type.
+Environment and Planning B-Planning \& Design 31, 759--784.
+
+\leavevmode\hypertarget{ref-Shao2019analysis}{}%
+Shao, P., Liang, J., 2019. An analysis of the factors influencing the
+sustainable use intention of urban shared bicycles in china.
+Sustainability 11.
+doi:\href{https://doi.org/10.3390/su11102721}{10.3390/su11102721}
+
+\leavevmode\hypertarget{ref-Smith2017commute}{}%
+Smith, O., 2017. Commute well-being differences by mode: Evidence from
+portland, oregon, usa. Journal of Transport \& Health 4, 246--254.
+doi:\href{https://doi.org/10.1016/j.jth.2016.08.005}{10.1016/j.jth.2016.08.005}
+
+\leavevmode\hypertarget{ref-Steg2005car}{}%
+Steg, L., 2005. Car use: Lust and must. Instrumental, symbolic and
+affective motives for car use. Transportation Research Part A 39,
+147--162.
+
+\leavevmode\hypertarget{ref-Stlouis2014happy}{}%
+St-Louis, E., Manaugh, K., Lierop, D. van, El-Geneidy, A., 2014. The
+happy commuter: A comparison of commuter satisfaction across modes.
+Transportation Research Part F-Traffic Psychology and Behaviour 26,
+160--170.
+doi:\href{https://doi.org/10.1016/j.trf.2014.07.004}{10.1016/j.trf.2014.07.004}
+
+\leavevmode\hypertarget{ref-Susilo2014exploring}{}%
+Susilo, Y.O., Cats, O., 2014. Exploring key determinants of travel
+satisfaction for multi-modal trips by different traveler groups.
+Transportation Research Part a-Policy and Practice 67, 366--380.
+doi:\href{https://doi.org/10.1016/j.tra.2014.08.002}{10.1016/j.tra.2014.08.002}
+
+\leavevmode\hypertarget{ref-Tesch2008gender}{}%
+Tesch-Römer, C., Motel-Klingebiel, A., Tomasik, M.J., 2008. Gender
+differences in subjective well-being: Comparing societies with respect
+to gender equality. Social Indicators Research 85, 329--349.
+
+\leavevmode\hypertarget{ref-Van2014effect}{}%
+Van, H.T., Choocharukul, K., Fujii, S., 2014. The effect of attitudes
+toward cars and public transportation on behavioral intention in
+commuting mode choice-a comparison across six asian countries.
+Transportation Research Part a-Policy and Practice 69, 36--44.
+doi:\href{https://doi.org/10.1016/j.tra.2014.08.008}{10.1016/j.tra.2014.08.008}
+
+\leavevmode\hypertarget{ref-Whalen2013mode}{}%
+Whalen, K.E., Páez, A., Carrasco, J.A., 2013. Mode choice of university
+students commuting to school and the role of active travel. Journal of
+Transport Geography 31, 132--142.
+doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.jtrangeo.2013.06.008}{http://dx.doi.org/10.1016/j.jtrangeo.2013.06.008}
+
+\leavevmode\hypertarget{ref-Wickham2017}{}%
+Wickham, H., 2017. Tidyverse: Easily install and load the 'tidyverse'.
+
+\leavevmode\hypertarget{ref-Xie2015}{}%
+Xie, Y., 2015. Dynamic documents with r and knitr, 2nd ed. Chapman;
+Hall/CRC, Boca Raton, Florida.
+
+\leavevmode\hypertarget{ref-Xie2018}{}%
+Xie, Y., 2018. Knitr: A general-purpose package for dynamic report
+generation in r.
+
+\leavevmode\hypertarget{ref-Ye2017satisfaction}{}%
+Ye, R.N., Titheridge, H., 2017. Satisfaction with the commute: The role
+of travel mode choice, built environment and attitudes. Transportation
+Research Part D-Transport and Environment 52, 535--547.
+doi:\href{https://doi.org/10.1016/j.trd.2016.06.011}{10.1016/j.trd.2016.06.011}
+
+\leavevmode\hypertarget{ref-Zhu2018}{}%
+Zhu, H., 2018. KableExtra: Construct complex table with 'kable' and pipe
+syntax.
+
+\leavevmode\hypertarget{ref-Zorrilla2019exploring}{}%
+Zorrilla, M.C., Hodgson, F., Jopson, A., 2019. Exploring the influence
+of attitudes, social comparison and image and prestige among
+non-cyclists to predict intention to cycle in mexico city.
+Transportation Research Part F-Traffic Psychology and Behaviour 60,
+327--342.
+doi:\href{https://doi.org/10.1016/j.trf.2018.10.009}{10.1016/j.trf.2018.10.009}
+
 \end{document}

### 2019-10-23 ModeDissonanceSantiago.Rcheck/00_pkg_src/ModeDissonanceSantiago/R/addnums.R
Created data package

@@ -1,0 +1,3 @@
+addnums <- function(a, b){
+  a + b
+}

### 2019-10-23 ModeDissonanceSantiago.Rcheck/ModeDissonanceSantiago-Ex.R

@@ -1,0 +1,51 @@
+pkgname <- "ModeDissonanceSantiago"
+source(file.path(R.home("share"), "R", "examples-header.R"))
+options(warn = 1)
+options(pager = "console")
+base::assign(".ExTimings", "ModeDissonanceSantiago-Ex.timings", pos = 'CheckExEnv')
+base::cat("name\tuser\tsystem\telapsed\n", file=base::get(".ExTimings", pos = 'CheckExEnv'))
+base::assign(".format_ptime",
+function(x) {
+  if(!is.na(x[4L])) x[1L] <- x[1L] + x[4L]
+  if(!is.na(x[5L])) x[2L] <- x[2L] + x[5L]
+  options(OutDec = '.')
+  format(x[1L:3L], digits = 7L)
+},
+pos = 'CheckExEnv')
+
+### * </HEADER>
+library('ModeDissonanceSantiago')
+
+base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
+base::assign(".old_wd", base::getwd(), pos = 'CheckExEnv')
+cleanEx()
+nameEx("hello")
+### * hello
+
+flush(stderr()); flush(stdout())
+
+base::assign(".ptime", proc.time(), pos = "CheckExEnv")
+### Name: hello
+### Title: Hello, World!
+### Aliases: hello
+
+### ** Examples
+
+hello()
+
+
+
+base::assign(".dptime", (proc.time() - get(".ptime", pos = "CheckExEnv")), pos = "CheckExEnv")
+base::cat("hello", base::get(".format_ptime", pos = 'CheckExEnv')(get(".dptime", pos = "CheckExEnv")), "\n", file=base::get(".ExTimings", pos = 'CheckExEnv'), append=TRUE, sep="\t")
+### * <FOOTER>
+###
+cleanEx()
+options(digits = 7L)
+base::cat("Time elapsed: ", proc.time() - base::get("ptime", pos = 'CheckExEnv'),"\n")
+grDevices::dev.off()
+###
+### Local variables: ***
+### mode: outline-minor ***
+### outline-regexp: "\\(> \\)?### [*]+" ***
+### End: ***
+quit('no')

### 2019-10-23 Dissonance_Santiago_v1.Rmd
Commit files from Paez-Laptop

--- 2019-10-19 Dissonance_Santiago_v1.Rmd
@@
 author:
-  - name: Author 1
-    email: a1@university.com
+  - name: Beasly Bee
+    email: alice@university.com
     affiliation: Some University
     footnote: Corresponding Author
-  - name: Author 2
-    email: a2@school.com
+  - name: Antsy Aardvark
+    email: aa@school.com
     affiliation: Some School
@@
 
-library(rticles)
 library(readxl)
@@
 
-```{r figure-mosaic-plots-by-attribute-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
+```{r figure-mosaic-plots-by-attribute-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}
 
@@
               divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Poverty, Luxury, Status}") +
-  ylab("Primary mode of travel") +
+  xlab("Proportion of responses by mode associated with {Freedom, Enjoyment, Happiness, Poverty, Luxury, Status}") +
+  ylab("Proportion of respondents by primary mode of travel") +
   scale_fill_viridis_d(direction = -1) +
@@
 
-```{r figure-mosaic-plots-by-attribute-and-age-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(AGE ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-and-education-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(EDUCATION ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-and-income-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("POVERTY", "LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Poverty, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(INCOME ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-and-time-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by travel time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-# Select only affective values that were significant in the tests of independence
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS")) %>% drop_na(TRAVEL_TIME)) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Happiness, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(TRAVEL_TIME ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
 Conclusions

### 2019-10-23 Dissonance_Santiago_v1.tex
Commit files from Paez-Laptop

--- 2019-10-19 Dissonance_Santiago_v1.tex
@@
 Primary Mode of Travel from the Perspective of Subjective Wellbeing}
-    \author[Some University]{Author 1\corref{c1}}
-   \ead{a1@university.com} 
+    \author[Some University]{Beasly Bee\corref{c1}}
+   \ead{alice@university.com} 
    \cortext[c1]{Corresponding Author}
-    \author[Some School]{Author 2}
-   \ead{a2@school.com}
+    \author[Some School]{Antsy Aardvark}
+   \ead{aa@school.com}
 
@@
 \includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-without-instrumental-1.pdf}
-\caption{\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective
-values; the y-axis is the proportion of respondents by main mode of
-transportation, and the x-axis is the proportion of modes selected for
-each value}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-age-without-instrumental-1.pdf}
-\caption{\label{fig:mosaic-plots-by-age}Mosaic plots for affective
-values by age; the y-axis is the proportion of respondents by main mode
-of transportation, and the x-axis is the proportion of modes selected
-for each value}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-education-without-instrumental-1.pdf}
-\caption{\label{fig:mosaic-plots-by-education}Mosaic plots for affective
-values by education; the y-axis is the proportion of respondents by main
-mode of transportation, and the x-axis is the proportion of modes
-selected for each value}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-income-without-instrumental-1.pdf}
-\caption{\label{fig:mosaic-plots-by-income}Mosaic plots for affective
-values by income; the y-axis is the proportion of respondents by main
-mode of transportation, and the x-axis is the proportion of modes
-selected for each value}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-time-without-instrumental-1.pdf}
-\caption{\label{fig:mosaic-plots-by-travel-time}Mosaic plots for
-affective values by travel time; the y-axis is the proportion of
-respondents by main mode of transportation, and the x-axis is the
-proportion of modes selected for each value}
+\caption{\label{fig:mosaic-plots-by-attribute}Mosaic plots for three
+affective and three instrumental values; values on the x-axis represent
+proportion of modes selected for each value, and values on the y-axis
+represent proportion of respondents by main mode of transportation}
 \end{figure}

### 2019-10-23 Dissonance_Santiago_v1.Rmd

--- 2019-10-21 Dissonance_Santiago_v1.Rmd
@@
       booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results-without-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
+      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
       escape = FALSE,
@@
 
-***
-
-Efectivamente lujo y estatus parecen similares a primera vista (Figura 1).
+>>> Efectivamente lujo y estatus parecen similares a primera vista (Figura 1).
 En general, estos dos valores afectivos son asociados mucho mas comunmente con el automovil.
@@
 
-Por ejemplo, la tendencia a asociar estatus con el automovil tiende a incrementarse con la edad, con la posible excepcion de los usuarios de transporte publico, para quienes otras opciones (posiblemente taxi), ganan en estatus para los viajeros mayores (>54) a costa de otros modos, incluido el automovil.
+>>> Por ejemplo, la tendencia a asociar estatus con el automovil tiende a incrementarse con la edad, con la posible excepcion de los usuarios de transporte publico, para quienes otras opciones (posiblemente taxi), ganan en estatus para los viajeros mayores (>54) a costa de otros modos, incluido el automovil.
 En contraste, el automovil pierde en el valor de lujo con la edad, mientras que otras opciones pasan a ser percibidas como lujo mas comunmente con la edad, incluso para los usuarios de automovil (Figure 2).
 
-se vuelven mas comunmente simbolos de estatus que cuando vemos la manera en que viajeros de diferentes edades proyectan lujo y estatus en varios modos, los usuarios de automovil mayores (>54) muestran menos disonancia en status que en lujo, mientras que los viajeros activos presentan mas disonancia en estatus que en lujo, y de hecho proyectan estatus mas comunmente en el automovil.
-
-La manera en que el lujo se asocia de manera relativamente mas frecuente con otras opciones que el estatus tambien se observa cuando vemos los diferentes niveles de educacion.
+>>> se vuelven mas comunmente simbolos de estatus que cuando vemos la manera en que viajeros de diferentes edades proyectan lujo y estatus en varios modos, los usuarios de automovil mayores (>54) muestran menos disonancia en status que en lujo, mientras que los viajeros activos presentan mas disonancia en estatus que en lujo, y de hecho proyectan estatus mas comunmente en el automovil.
+
+>>> La manera en que el lujo se asocia de manera relativamente mas frecuente con otras opciones que el estatus tambien se observa cuando vemos los diferentes niveles de educacion.
 La excepcion parece ser los usuarios de transporte activo, especialmente  aquellos con educacion superior y de post-grado, que asocian tanto estatus como lujo con el transporte activo mas que los usuarios de otros modos.
-
-***
 

### 2019-10-23 Dissonance_Santiago_v1.tex

--- 2019-10-21 Dissonance_Santiago_v1.tex
@@
 this trend is Luxury, an affective value for which older travellers (age
-\textgreater{}54) experience dissonance more frequently than mid-aged
+\textgreater54) experience dissonance more frequently than mid-aged
 travellers (ages 35-54).
@@
 
-\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results-without-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors}
+\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors}
 \centering
@@
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
+\begin{quote}
+\begin{quote}
+\begin{quote}
 Efectivamente lujo y estatus parecen similares a primera vista (Figura
@@
 viajeros.
-
+\end{quote}
+\end{quote}
+\end{quote}
+
+\begin{quote}
+\begin{quote}
+\begin{quote}
 Por ejemplo, la tendencia a asociar estatus con el automovil tiende a
@@
 transporte publico, para quienes otras opciones (posiblemente taxi),
-ganan en estatus para los viajeros mayores (\textgreater{}54) a costa de
+ganan en estatus para los viajeros mayores (\textgreater54) a costa de
 otros modos, incluido el automovil. En contraste, el automovil pierde en
@@
 usuarios de automovil (Figure 2).
-
+\end{quote}
+\end{quote}
+\end{quote}
+
+\begin{quote}
+\begin{quote}
+\begin{quote}
 se vuelven mas comunmente simbolos de estatus que cuando vemos la manera
 en que viajeros de diferentes edades proyectan lujo y estatus en varios
-modos, los usuarios de automovil mayores (\textgreater{}54) muestran
-menos disonancia en status que en lujo, mientras que los viajeros
-activos presentan mas disonancia en estatus que en lujo, y de hecho
-proyectan estatus mas comunmente en el automovil.
-
+modos, los usuarios de automovil mayores (\textgreater54) muestran menos
+disonancia en status que en lujo, mientras que los viajeros activos
+presentan mas disonancia en estatus que en lujo, y de hecho proyectan
+estatus mas comunmente en el automovil.
+\end{quote}
+\end{quote}
+\end{quote}
+
+\begin{quote}
+\begin{quote}
+\begin{quote}
 La manera en que el lujo se asocia de manera relativamente mas frecuente
@@
 mas que los usuarios de otros modos.
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+\end{quote}
+\end{quote}
+\end{quote}
 

### 2019-11-01 Dissonance_Santiago_Title_Page_v1.Rmd
Added discussion based on the files sent by Beatriz, and prepared files for submission

--- 2019-10-23 Dissonance_Santiago_v1.Rmd
@@
 ---
-title: Do Drivers Dream of Walking? An Investigation of Dissonance in the Primary Mode of Travel from the Perspective of Subjective Wellbeing
+title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing
 author:
-  - name: Beasly Bee
-    email: alice@university.com
-    affiliation: Some University
+  - name: Beatriz Mella Lira
+    email: beatriz.lira.14@ucl.ac.uk
+    affiliation: University College London
     footnote: Corresponding Author
-  - name: Antsy Aardvark
-    email: aa@school.com
-    affiliation: Some School
+  - name: Antonio Paez
+    email: paezha@mcmaster.ca
+    affiliation: McMaster University
 address:
-  - code: Some University
-    address: Department, Street, City, State, Zip
-  - code: Some School
-    address: Department, Street, City, State, Zip
+  - code: University College London
+    address: Bartlett School of Planning, Sixth Floor, Central House, 14 Upper Woburn Place, London, WC1H0NN UK
+  - code: McMaster University
+    address: School of Geography and Earth Sciences, 1280 Main St W, Hamilton, Ontario, L8S 1S4 Canada
 abstract: |
-  Transportation in most of the world has been dominated for decades by a fascination with the automobile.
-Increasingly, however, it is recognized that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain users of public transport and active travel.
-A challenge with the way transportation policy is developed is that it tends to focus on cost-benefit and utilitarian considerations, which may miss other potential benefits of transportation.
-For this reason, subjective wellbeing (SWB) has been proposed as a way to enhance our understanding of the preferences and choices of travellers, as well as a way to evaluate the benefits of transportation beyond utilitarian considerations.
-The objective of this paper is to analyze the modes that people commonly use, and to what extent they are aligned (or not) with a variety of affective and utilitarian values.
-In other words, we are interested in the potential for dissonance with respect to the primary mode of travel, from the perspective of affective and utilitarian values.
+  Subjective wellbeing is a topic that has attracted considerable attention in recent years due to the way it correlates with health.
+From a transportation perspective, there is a burgeoning literature on the way travel can impact subjective wellbeing, and how this, in turn, can influence behavior.
+After decades of fascination with the automobile, subjective wellbeing is increasingly recognized as an alternative approach to assess transportation, and to gain valuable insights to attract and retain active travelers and users of public transportation.
+The objective of this paper is to analyze a number of affective values associated with subjective wellbeing and the modes of transportation that people commonly use.
+In particular, we are interested in the potential for dissonance with respect to the primary mode of travel.
 The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
-Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associated to affective values (freedom, enjoyment, and happiness) and to utilitarian values (safety, time waste, and efficiency).
+Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associate with the affective values of freedom, enjoyment, happiness, poverty, luxury and status.
 The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with affective values.
-
-  To properly assess transportation policy This poses a number of challenges Broadening the commonly used transport project assessment will be relevant for achieving this goal.
-While satisfaction with travel has been mainly used in the context of daily trips and mainly under cost-benefit and utilitarian considerations, subjective wellbeing (SWB) over time has risen as an alternative for understanding the preferences and choices of transport users.
-The aim of this paper is to analyse the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
-The paper aims to reflect on the possibilities of increasing the SWB with a view to enhance the attractiveness of public transport and active travel.
-The paper investigates the affective and instrumental/utilitarian factors of SWB, according to modal choice.
-It uses an analysis of correspondence that considers the actual primary mode used, versus the mode that each individual associated to both utilitarian and affective SWB factors.
-The results show that there is more persistent modal dissonance between positive emotional and utilitarian associations within the more disadvantaged groups – particularly among users of public transport.
-The study shows that apart from time-savings and efficiency, security has also been cross-sectionally sensitive according to the data analysed.
-Factors such as happiness, enjoyment and freedom require far more attention in transport planning as they are strongly related to the dimensions of subjective and personal wellbeing.
-Targeting these factors will be relevant for attracting new users to public transportation and active travel.
+For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
 
@@
 ---
-
-<!-- This paper is an R markdown document that includes self-contained, reproducible analysis. To reproduce the paper the following files are needed:
-
-1. Dissonance_Santiago_v1.Rmd (this R markdown document)
-
-2.
-`Dissonance_Santiago.RData`.
-For reference: this data file was created using R notebook `00.
-Analysis of Dissonance Detailed.Rmd`.
-The initial analysis was done in the same R notebook.
-Neither of these two notebooks are needed for this document.
-
-3.
-For compiling into a pdf in the style of an Elsevier document: elsarticle.cls, elsevier-harvard.csl, elsevier-harvard-without-titles.csl, elsevier-vancouver.csl, elsevier-without-titles.cls, elsevier-with-titles.csl, elsevier-with-titles-alphabetical.csl, mybibfile.bib
--->
-
-```{r load-packages, include=FALSE}
-
-# Load packages used in this document
-
-library(readxl)
-library(tidyverse)
-library(rgdal)
-library(sf)
-library(ggmosaic)
-library(ggthemes)
-library(kableExtra)
-```
-
-```{r load-data, include=FALSE}
-
-# To run this notebook, the file `Dissonance_Santiago.RData` is needed. This file contains the following object:
-# 
-# master: a dataframe with information collected from 451 respondents. The variables in the dataframe are:
-# 
-# - NUMERO: Respondent ID
-# - USED: Main mode of transportation used by the respondent
-# - FREEDOM: Mode(s) that the respondent associates with feelings of freedom
-# - ENJOYMENT: Mode(s) that the respondent associates with feelings of enjoyment
-# - HAPPINESS: Mode(s) that the respondent associates with feelings of happiness
-# - POVERTY: Mode(s) that the respondent associates with feelings of poverty
-# - LUXURY: Mode(s) that the respondent associates with feelings of luxury
-# - STATUS: Mode(s) that the respondent associates with feelings of status
-# - SAFETY: Mode(s) that the respondent associates with feelings of safety
-# - TIME: Mode(s) that the respondent associates with feelings of WASTED TIME
-# - EFFICIENCY: Mode(s) that the respondent associates with feelings of efficiency
-# - AGE: Age of the respondent
-# - EDUCATION: Level of education of the respondent
-# - INCOME: Level of income of respondent
-# - TRAVEL_TIME: Trip duration of regular commuting trip 
-# - WEIGHT_*: A weight for the responses by ATTRIBUTE.
-Some respondents selected more than one mode that they associated with feelings of {FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, and EFFICIENCY}.
-To avoid giving greater weight to respondents who indicated several modes of transportation, a weight was calculated that is the inverse of the number of modes indicated.
-These weights can be used to weight the frequencies prior to any analysis.
-# 
-# The modes of transportation (USED, FREEDOM, ENJOYMENT, HAPPINESS, SAFETY, TIME, EFFICIENCY) are coded as: 
-# "A": Auto
-# "B": Taxi
-# "C": Colectivo
-# "D": Moto
-# "E": Metro
-# "F": Bus
-# "G": Bicycle
-# "H": Walk
-#
-# AGE is coded as:
-#
-# "A": Less18
-# "B": 18to24
-# "C": 25to34
-# "D": 35to54
-# "E": 55to64
-# "F": 65more
-# 
-# EDUCATION is coded as:
-# 
-# "A": ELEMENTARY
-# "B": SECUNDARY
-# "C": PROFESS_TECH
-# "D": COLLEGE
-# "E": POSTGRAD
-#
-# INCOME is coded as (in pesos?):
-# 
-# "A": Less423
-# "B": 423to639
-# "C": 639to977
-# "D": 977to1550
-# "E": 1550to2380
-# "F": 2380more
-# 
-# TRAVEL_TIME is coded as:
-#
-# "A": 0-20 min
-# "B": 20-40 min
-# "C": 40-60 min
-# "D": 1h and more
-
-# Read the RData file:
-
-load("Dissonance_Santiago.RData")
-```
-
-```{r data-preparation, include=FALSE}
-
-# The master dataframe is processed for analysis. We plan to conduct two distinct types of analysis:
-#
-# 1.
-Analysis of dissonace using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.).
-In this case, dissonance is defined as follows:
-#
-# >> If the mode used is identical to the mode that the respondent associates with ATTRIBUTE (i.e.
-FREEDOM et al.), we consider that there is no dissonance; otherwise, we consider that there is dissonance.
-For example, if the respondent's main mode of transportation is Auto, and the respondent associates Auto with feelings of FREEDOM, then there is no dissonance.
-On the other hand, if the respondent's main mode of transportation is Auto, but associates Walking with feelings of FREEDOM, there is dissonance.
-# 
-# Given this, we will calculate how frequently there is dissonance at different levels of AGE, EDUCATION, INCOME, MODE, TRAVEL_TIME. Tests of independence can be implemented.
-#
-# 2.
-Analysis of dissonance using the mode USED and the mode respondents associated with ATTRIBUTE, then stratified by characteristics of respondents (i.e., AGE et al.) in this case, we see how frequently each mode was associated with ATTRIBUTE, given the main mode of transportation of the respondents.
-#
-# Here the dataframes are prepared to support these two types of analysis
-
-#################################################################################
-# Prepare a dataframe for the analysis of dissonance by attribute (Analysis 1.) #
-#################################################################################
-
-# First, select the variables needed from the master table, and code dissonance as 1 (no dissonance) or two (dissonance):
-
-Overall_dissonance <- master %>%
-  transmute(USED, 
-            FREEDOM_DISSONANCE = ifelse(USED == FREEDOM, 1, 2),
-            ENJOYMENT_DISSONANCE = ifelse(USED == ENJOYMENT, 1, 2),
-            HAPPINESS_DISSONANCE = ifelse(USED == HAPPINESS, 1, 2),
-            POVERTY_DISSONANCE = ifelse(USED == POVERTY, 1, 2),
-            LUXURY_DISSONANCE = ifelse(USED == LUXURY, 1, 2),
-            STATUS_DISSONANCE = ifelse(USED == STATUS, 1, 2),
-            SAFETY_DISSONANCE = ifelse(USED == SAFETY, 1, 2),
-            TIME_DISSONANCE = ifelse(USED == TIME, 1, 2),
-            EFFICIENCY_DISSONANCE = ifelse(USED == EFFICIENCY, 1, 2),
-            AGE,
-            EDUCATION,
-            INCOME,
-            TRAVEL_TIME)
-
-# Recode variables and convert to factors:
-
-Overall_dissonance <- Overall_dissonance %>%
-  mutate(USED = case_when(USED == "A" ~ "Auto",
-                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
-                                  USED == "E" | USED == "F" ~ "Public",
-                                  USED == "G" | USED == "H" ~ "Active"),
-         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
-                         AGE == "D" ~ "35 - 54",
-                         AGE == "E" | AGE == "F" ~ "> 54"),
-         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
-                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
-                               EDUCATION == "E" ~ "Graduate"),
-         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
-                            INCOME == "C" | INCOME == "D" ~ "Middle",
-                            INCOME == "E" | INCOME == "F" ~ "High"),
-         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
-                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
-                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
-                                 TRAVEL_TIME == "D" ~ "> 60 min")) %>%
-  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
-         FREEDOM_DISSONANCE = factor(FREEDOM_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         ENJOYMENT_DISSONANCE = factor(ENJOYMENT_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         HAPPINESS_DISSONANCE = factor(HAPPINESS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         POVERTY_DISSONANCE = factor(POVERTY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         LUXURY_DISSONANCE = factor(LUXURY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         STATUS_DISSONANCE = factor(STATUS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         SAFETY_DISSONANCE = factor(SAFETY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         TIME_DISSONANCE = factor(TIME_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         EFFICIENCY_DISSONANCE = factor(EFFICIENCY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
-         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
-         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
-         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))
-
-#############################################################################
-# Prepare a dataframe for the analysis of dissonance by modes (Analysis 2.) #
-#############################################################################
-
-# First, split the responses regarding the modes associated with each attribute, so that we can record each mode selected individually:
-
-Modes_by_Attribute <- master %>% 
-    mutate(FREEDOM = strsplit(as.character(FREEDOM), ""),
-           ENJOYMENT = strsplit(as.character(ENJOYMENT), ""),
-           HAPPINESS = strsplit(as.character(HAPPINESS), ""),
-           POVERTY = strsplit(as.character(POVERTY), ""),
-           LUXURY = strsplit(as.character(LUXURY), ""),
-           STATUS = strsplit(as.character(STATUS), ""),
-           SAFETY = strsplit(as.character(SAFETY), ""),
-           TIME = strsplit(as.character(TIME), ""),
-           EFFICIENCY = strsplit(as.character(EFFICIENCY), ""))
-
-# Here, we convert each of the responses into an individual row and stack the resulting dataframes, after adding the name of the attribute for identification:
-
-Modes_by_Attribute <- rbind(data.frame(Modes_by_Attribute %>% 
-                                         select(-c(ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = FREEDOM, WEIGHT = WEIGHT_FREEDOM) %>%
-                                         unnest(IDEAL),
-                                       ATTRIBUTE = "FREEDOM"),
-                            data.frame(Modes_by_Attribute %>%
-                                         select(-c(FREEDOM, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = ENJOYMENT, WEIGHT = WEIGHT_ENJOYMENT) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "ENJOYMENT"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM,
-                                                   WEIGHT_ENJOYMENT,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = HAPPINESS, WEIGHT = WEIGHT_HAPPINESS) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "HAPPINESS"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = POVERTY, WEIGHT = WEIGHT_POVERTY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "POVERTY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   #LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   #WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = LUXURY, WEIGHT = WEIGHT_LUXURY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "LUXURY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   #STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   #WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = STATUS, WEIGHT = WEIGHT_STATUS) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "STATUS"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = SAFETY, WEIGHT = WEIGHT_SAFETY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "SAFETY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = TIME, WEIGHT = WEIGHT_TIME) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "TIME"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME)) %>%
-                                         rename(IDEAL = EFFICIENCY, WEIGHT = WEIGHT_EFFICIENCY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "EFFICIENCY"))
-
-# There are some missing values. Drop all NAs:
-
-Modes_by_Attribute <- drop_na(Modes_by_Attribute)
-
-# We now recode the variables:
-
-Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = case_when(USED == "A" ~ "Auto",
-                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
-                                  USED == "E" | USED == "F" ~ "Public",
-                                  USED == "G" | USED == "H" ~ "Active"),
-         IDEAL = case_when(IDEAL == "A" ~ "Auto",
-                                  IDEAL == "B" | IDEAL == "C" | IDEAL == "D" ~ "Other",
-                                  IDEAL == "E" | IDEAL == "F" ~ "Public",
-                                  IDEAL == "G" | IDEAL == "H" ~ "Active"),
-         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
-                         AGE == "D" ~ "35 - 54",
-                         AGE == "E" | AGE == "F" ~ "> 54"),
-         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
-                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
-                               EDUCATION == "E" ~ "Graduate"),
-         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
-                            INCOME == "C" | INCOME == "D" ~ "Middle",
-                            INCOME == "E" | INCOME == "F" ~ "High"),
-         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
-                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
-                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
-                                 TRAVEL_TIME == "D" ~ "> 60 min"))
-
-# After recoding the , there will be some duplicate entries, because a person may have attributed, say, feelings of freedom to walking and cycling, so in the table this will appear as two instances of "Active".
-This is ok, because each is weighted appropriately.
-
-# Convert to factors:
-
-Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = factor(USED, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
-         IDEAL = factor(IDEAL, levels = c("Auto", "Active", "Public", "Other"), labels = c("Auto", "Active", "Public", "Other")),
-         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
-         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
-         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
-         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))
-```
-
-```{r cross-tabs-function, include=FALSE}
-
-## Define functions for crosstabs; these functions enhance the base crosstabs functions and make it easier to report cross tabulations in different ways.
-
-crosstab <- function (..., dec.places = NULL,
-                           type = NULL,
-                           style = "wide",
-                           row.vars = NULL,
-                           col.vars = NULL,
-                           percentages = TRUE, 
-                           addmargins = TRUE,
-                           subtotals=TRUE)
-
-###################################################################################
-#                                                                                 #
-# Function created by Dr Paul Williamson, Dept. of Geography and Planning,        #
-# School of Environmental Sciences, University of Liverpool, UK.                  #
-#                                                                                 #
-# Adapted from the function ctab() in the catspec packge.                         #
-#                                                                                 #
-# Version: 12th July 2013                                                         #
-#                                                                                 #
-# Output best viewed using the companion function print.crosstab()                #
-#                                                                                 #
-###################################################################################
-
-  #Declare function used to convert frequency counts into relevant type of proportion or percentage
-  {mk.pcnt.tbl <- function(tbl, type) {
-        a <- length(row.vars)
-        b <- length(col.vars)
-        mrgn <- switch(type, column.pct = c(row.vars[-a], col.vars), 
-                            row.pct = c(row.vars, col.vars[-b]),
-                            joint.pct = c(row.vars[-a], col.vars[-b]),
-                            total.pct = NULL)
-        tbl <- prop.table(tbl, mrgn)
-        if (percentages) {
-            tbl <- tbl * 100
-        }
-        tbl
-    }
-
-    #Find no. of vars (all; row; col) for use in subsequent code
-    n.row.vars <- length(row.vars)
-    n.col.vars <- length(col.vars)
-    n.vars <- n.row.vars + n.col.vars
-
-    #Check to make sure all user-supplied arguments have valid values
-    stopifnot(as.integer(dec.places) == dec.places, dec.places > -1)
-    #type: see next section of code
-    stopifnot(is.character(style))    
-    stopifnot(is.logical(percentages))
-    stopifnot(is.logical(addmargins))
-    stopifnot(is.logical(subtotals))
-    stopifnot(n.vars>=1)
-
-    #Convert supplied table type(s) into full text string (e.g. "f" becomes "frequency")
-    #If invalid type supplied, failed match gives user automatic error message
-    types <- NULL
-    choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
-    for (tp in type) types <- c(types, match.arg(tp, choices))
-    type <- types
-
-    #If no type supplied, default to 'frequency + total' for univariate tables and to
-    #'frequency' for multi-dimenstional tables
-
-    #For univariate table....
-    if (n.vars == 1) {
-      if (is.null(type)) {
-        # default = freq count + total.pct  
-        type <- c("frequency", "total.pct")
-        #row.vars <- 1
-      } else {
-        #and any requests for row / col / joint.pct must be changed into requests for 'total.pct'
-        type <- ifelse(type == "frequency", "frequency", "total.pct")
-      }
-    #For multivariate tables...
-    } else if (is.null(type)) {
-      # default = frequency count  
-      type <- "frequency"
-    }
-
-    #Check for integrity of requested analysis and adjust values of function arguments as required
-
-    if ((addmargins==FALSE) & (subtotals==FALSE)) {
-      warning("WARNING: Request to suppress subtotals (subtotals=FALSE) ignored because no margins requested (addmargins=FALSE)")
-      subtotals <- TRUE
-    }
-
-    if ((n.vars>1) & (length(type)>1) & (addmargins==TRUE)) {
-      warning("WARNING: Only row totals added when more than one table type requested")
-      #Code lower down selecting type of margin implements this...
-    }
-
-    if ((length(type)>1) & (subtotals==FALSE)) { 
-      warning("WARNING: Can only request supply one table type if requesting suppression of subtotals; suppression of subtotals not executed")
-      subtotals <- TRUE
-    }
-
-    if ((length(type)==1) & (subtotals==FALSE)) {
-      choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
-      tp <- match.arg(type, choices)
-      if (tp %in% c("row.pct","column.pct","joint.pct")) {
-          warning("WARNING: subtotals can only be suppressed for tables of type 'frequency' or 'total.pct'")
-          subtotals<- TRUE
-         }
-    }
-
-    if ((n.vars > 2) & (n.col.vars>1) & (subtotals==FALSE)) 
-      warning("WARNING: suppression of subtotals assumes only 1 col var; table flattened accordingly")
-
-    if ( (subtotals==FALSE) & (n.vars>2) )  {
-    #If subtotals not required AND total table vars > 2
-    #Reassign all but last col.var as row vars
-    #[because, for simplicity, crosstabs assumes removal of subtotals uses tables with only ONE col var]
-    #N.B. Subtotals only present in tables with > 2 cross-classified vars...
-      if (length(col.vars)>1) {
-        row.vars <- c(row.vars,col.vars[-length(col.vars)])
-        col.vars <- col.vars[length(col.vars)]
-        n.row.vars <- length(row.vars)
-        n.col.vars <- 1
-      }
-    }
-
-    #If dec.places not set by user, set to 2 unlesss only one table of type frequency requested,
-    #in which case set to 0.  [Leaves user with possibility of having frequency tables with > 0 dp]
-    if (is.null(dec.places)) {
-      if ((length(type)==1) & (type[1]=="frequency")) {
-        dec.places <- 0
-      } else {
-        dec.places <-2
-      }
-    }
-
-    #Take the original input data, whatever form originally supplied in,
-    #convert into table format using requested row and col vars, and save as 'tbl'
-
-    args <- list(...)
-
-    if (length(args) > 1) {
-        if (!all(sapply(args, is.factor))) 
-            stop("If more than one argument is passed then all must be factors")
-        tbl <- table(...)
-    }
-    else {
-        if (is.factor(...)) {
-            tbl <- table(...)
-        }
-        else if (is.table(...)) {
-            tbl <- eval(...)
-        }
-        else if (is.data.frame(...)) {
-            #tbl <- table(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-              tbl <- table(...)
-            }
-            else {
-              var.names <- c(row.vars,col.vars)
-              A <- (...)
-              tbl <- table(A[var.names])
-              if(length(var.names==1)) names(dimnames(tbl)) <- var.names
-              #[table() only autocompletes dimnames for multivariate crosstabs of dataframes]
-            }
-        }
-        else if (class(...) == "ftable") {
-            tbl <- eval(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-                row.vars <- names(attr(tbl, "row.vars"))
-                col.vars <- names(attr(tbl, "col.vars"))
-            }
-            tbl <- as.table(tbl)
-        }
-        else if (class(...) == "ctab") {
-            tbl <- eval(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-                row.vars <- tbl$row.vars
-                col.vars <- tbl$col.vars
-            }
-            for (opt in c("dec.places", "type", "style", "percentages", 
-                "addmargins", "subtotals")) if (is.null(get(opt))) 
-                assign(opt, eval(parse(text = paste("tbl$", opt, 
-                  sep = ""))))
-            tbl <- tbl$table
-        }
-        else {
-            stop("first argument must be either factors or a table object")
-        }
-    }
-
-    #Convert supplied table style into full text string (e.g. "l" becomes "long")
-    style <- match.arg(style, c("long", "wide"))
-
-    #Extract row and col names to be used in creating 'tbl' from supplied input data
-    nms <- names(dimnames(tbl))
-    z <- length(nms)
-    if (!is.null(row.vars) && !is.numeric(row.vars)) {
-        row.vars <- order(match(nms, row.vars), na.last = NA)
-    }
-    if (!is.null(col.vars) && !is.numeric(col.vars)) {
-        col.vars <- order(match(nms, col.vars), na.last = NA)
-    }
-    if (!is.null(row.vars) && is.null(col.vars)) {
-        col.vars <- (1:z)[-row.vars]
-    }
-    if (!is.null(col.vars) && is.null(row.vars)) {
-        row.vars <- (1:z)[-col.vars]
-    }
-    if (is.null(row.vars) && is.null(col.vars)) {
-        col.vars <- z
-        row.vars <- (1:z)[-col.vars]
-    }
-
-    #Take the original input data, converted into table format using supplied row and col vars (tbl)
-    #and create a second version (crosstab) which stores results as percentages if a percentage table type is requested.
-    if (type[1] == "frequency") 
-      crosstab <- tbl
-    else 
-      crosstab <- mk.pcnt.tbl(tbl, type[1])
-
-    #If multiple table types requested, create and add these to 
-    if (length(type) > 1) {
-      tbldat <- as.data.frame.table(crosstab)
-      z <- length(names(tbldat)) + 1
-      tbldat[z] <- 1
-      pcntlab <- type
-      pcntlab[match("frequency", type)] <- "Count"
-      pcntlab[match("row.pct", type)] <- "Row %"
-      pcntlab[match("column.pct", type)] <- "Column %"
-      pcntlab[match("joint.pct", type)] <- "Joint %"
-      pcntlab[match("total.pct", type)] <- "Total %"
-      for (i in 2:length(type)) {
-          if (type[i] == "frequency") 
-              crosstab <- tbl
-          else crosstab <- mk.pcnt.tbl(tbl, type[i])
-          crosstab <- as.data.frame.table(crosstab)
-          crosstab[z] <- i
-          tbldat <- rbind(tbldat, crosstab)
-      }
-      tbldat[[z]] <- as.factor(tbldat[[z]])
-      levels(tbldat[[z]]) <- pcntlab
-      crosstab <- xtabs(Freq ~ ., data = tbldat)
-      names(dimnames(crosstab))[z - 1] <- ""
-    }
-
-    #Add margins if required, adding only those margins appropriate to user request
-    if (addmargins==TRUE) {
-
-      vars <- c(row.vars,col.vars)
-
-      if (length(type)==1) {
-      if (type=="row.pct") 
-        { crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
-          tbl <- addmargins(tbl,margin=c(vars[n.vars]))
-        }
-      else 
-        { if (type=="column.pct") 
-            { crosstab <- addmargins(crosstab,margin=c(vars[n.row.vars]))
-              tbl <- addmargins(tbl,margin=c(vars[n.row.vars]))
-            }
-          else 
-            { if (type=="joint.pct") 
-              { crosstab <- addmargins(crosstab,margin=c(vars[(n.row.vars)],vars[n.vars])) 
-                tbl <- addmargins(tbl,margin=c(vars[(n.row.vars)],vars[n.vars])) 
-              }
-              else #must be total.pct OR frequency
-                { crosstab <- addmargins(crosstab)
-                  tbl <- addmargins(tbl)
-                }
-            }
-  	     } 
-      }
-
-      #If more than one table type requested, only adding row totals makes any sense...
-      if (length(type)>1) {
-        crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
-        tbl <- addmargins(tbl,margin=c(vars[n.vars]))
-      }
-
-    }
-
-    #If subtotals not required, and total vars > 2, create dataframe version of table, with relevent
-    #subtotal rows / cols dropped [Subtotals only present in tables with > 2 cross-classified vars]
-    t1 <- NULL
-    if ( (subtotals==FALSE) & (n.vars>2) )  {
-
-    #Create version of crosstab in ftable format
-    t1 <- crosstab 
-    t1 <- ftable(t1,row.vars=row.vars,col.vars=col.vars)
-
-    #Convert to a dataframe
-    t1 <- as.data.frame(format(t1),stringsAsFactors=FALSE)
-
-    #Remove backslashes from category names AND colnames
-    t1 <- apply(t1[,],2, function(x) gsub("\"","",x))
-    #Remove preceding and trailing spaces from category names to enable accurate capture of 'sum' rows/cols
-    #[Use of grep might extrac category labels with 'sum' as part of a longer one or two word string...]
-    t1 <- apply(t1,2,function(x) gsub("[[:space:]]*$","",gsub("^[[:space:]]*","",x)))
-
-    #Reshape dataframe to that variable and category labels display as required
-    #(a) Move col category names down one row; and move col variable name one column to right
-    t1[2,(n.row.vars+1):ncol(t1)] <- t1[1,(n.row.vars+1):ncol(t1)]
-    t1[1,] <- ""
-    t1[1,(n.row.vars+2)] <- t1[2,(n.row.vars+1)]    
-    #(b) Drop the now redundant column separating the row.var labels from the table data + col.var labels
-    t1 <- t1[,-(n.row.vars+1)]
-
-    #In 'lab', assign category labels for each variable to all rows (to allow identification of sub-totals) 
-    lab <- t1[,1:n.row.vars]
-    for (c in 1:n.row.vars) {
-      for (r in 2:nrow(lab)) {
-        if (lab[r,c]=="") lab[r,c] <- lab[r-1,c]  
-      }
-    }
-
-    lab <- (apply(lab[,1:n.row.vars],2,function(x) x=="Sum"))
-    lab <- apply(lab,1,sum)
-    #Filter out rows of dataframe containing subtotals
-
-    t1 <- t1[((lab==0) | (lab==n.row.vars)),]
-
-    #Move the 'Sum' label associated with last row to the first column; in the process
-    #setting the final row labels associated with other row variables to ""
-    t1[nrow(t1),1] <- "Sum"
-    t1[nrow(t1),(2:n.row.vars)] <- ""
-
-    #set row and column names to NULL
-    rownames(t1) <- NULL
-    colnames(t1) <- NULL
-
-    }
-
-    #Create output object 'result' [class: crosstab]
-    result <- NULL
-    #(a) record of argument values used to produce tabular output
-    result$row.vars <- row.vars
-    result$col.vars <- col.vars
-    result$dec.places <- dec.places
-    result$type <- type
-    result$style <- style
-    result$percentages <- percentages
-    result$addmargins <- addmargins
-    result$subtotals <- subtotals
-
-    #(b) tabular output [3 variants]
-    result$table <- tbl  #Stores original cross-tab frequency counts without margins [class: table]
-    result$crosstab <- crosstab #Stores cross-tab in table format using requested style(frequency/pct) and table margins (on/off)
-                                #[class: table]  
-    result$crosstab.nosub <- t1  #crosstab with subtotals suppressed [class: dataframe; or NULL if no subtotals suppressed]  
-    class(result) <- "crosstab"
-
-    #Return 'result' as output of function
-    result
-}
-```
-
-Introduction
-==========================
-
-Transportation planning for decades has focused on providing mobility for the private automobile.
-This is a model of development that was initially introduced in North America as a solution to urbanizations problems, and that was eventually copied elsewhere (Brown et al., 2009; Angotti, 1996) .
-Despite the initial promise of automotive technology, it is now evident that mobility centred on the private automobile has given rise to a litany of maladies that are in urgent need of correction.
-This includes environmental concerns (i.e., climate change; Chapman, 2007) as well as other social (Boschmann and Kwan, 2008), health (Khreis et al., 2016), and equity issues (Bocarejo and Oviedo, 2012).
-As the real impacts of our societal dependence on the private autombobile have become increasingly evident, the transportation agenda has in recent years aimed to shift focus to the reduction of car-use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives than just the private automobile (Miller, 2011) .
-In order to successfully achieve this goal, it is essential not only to provide the services and facilities that support public transportation and active travel, but also to attract new users to these modes of transportation (Ettema et al.
-2011).
-Within this context, it has been argued that sustainable transportation policies require all participants in the transportation system to challenge what Gossling and Cohen (2014) term “transportation taboos”: deep-seated ideas concerning the contribution to emissions by individuals, the inequality of market-based approaches, and the social and psychological functions of transportation.
-With respect to the latter, moving beyond a purely utilitarian focus, it is important to understand how users perceive affective and instrumental elements on their transportation experience, since this can help to incorporate adequate improvements in alternative transportation, including transit and active modes, to make them more attractive to users (Anable and Gatersleben, 2005; Domarchi et al., 2008; Gatersleben and Uzzell, 2007; Steg 2005 ).
-
-A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing (SWB.
-See, inter alia, De Vos et al., 2013 and Chatterjee et al., 2019) .
-SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” (OECD, 2013, p.
-10).
-Accordingly, the aim of this paper is to analyse some of the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
-Previous research suggests that public transport users experience a negative gap in desired and actual travel time, whereas active travellers don’t seem to mind somewhat longer trips than what strictly needed (e.g., Páez and Whalen, 2010).
-In the context of a Latin American country, historically the poor travel experience of public transit users and active travellers reflects the social inequalities of social groups that have no alternative but to move in these types of modes while living far from the work centres and main activities.
-The paper aims to reflect on the possibilities of increasing the SWB while travelling, and how this could increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
-This can help not only to reduce the use of private transport but also decrease the inequality gap between these users.
-
-The paper explores how positive affective and instrumental/utilitarian factors of SWB correspond to the use of the primary mode of transportation.
-It uses an analysis of correspondence that considers the actual primary mode versus the mode that individuals associated to both utilitarian (designed to be useful or practical rather than attractive) and affective (expressing a person's feelings) SWB factors.
-For example, it will be analysed if a person who uses public transport as the primary mode, tends to associate these modes with positive affective factors (as freedom, enjoyment or happiness) or positive utilitarian factors (as security, time-savings or efficiency).
-We hypothesize that there is a more persistent non-correspondence or mismatch within the more disadvantage groups or within the users of public transport.
-
-The paper contributes to the literature in three areas.
-First, it contributes to an emerging literature on the topic in the context of the Global South (Bejarano et al., 2017 ; Shao and Liang, 2019 ; Van et al., 2014 ; Zorrilla et al., 2019);  to the best of our knowledge, the case of Chile has not yet been reported.
-Second, although there is literature on the enjoyment of commute and other emotional factors, from a hedonic and even eudaimonic perspectives, the analysis has yet to be applied more fully in terms of distributional issues – i.e.
-which groups are mostly disadvantaged.
-Finally, the analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’ – implying their preferences, even in situations when their ideal mode is not part of their actual choice set.
-The attitudes of travellers towards transport modes are critical factors to be considered by policy-makers in case they want to promote and increase the use of public transport or active modes (e.g., Bejarano et al., 2019).
-The paper explores these positive and negative associations within the transport options used in Santiago.
-
-Background
-============
-
-The transportation community has for the most part already agreed to the need of looking at mobility and transport issues from the lens of wellbeing, to broaden the commonly used utilitarian perspective to evaluate projects.
-Users’ travel satisfaction (Bergstad, 2001) has been the primary way to direct this challenge towards everyday mobility, resulting on research about satisfaction with different transport modes.
-For example, numerous studies report that car users have a higher level of satisfaction compared to other transport modes (Redmond and Mokhtarian, 2001 ; Bergstad et al.
-2011; Eriksson et al.
-2013; Whalen et al., 2013).
-In a similar way, there are multiple reports that active travel also tends to yield high levels of satisfaction (Smith, 2017; St-Louis et al.
-2014; Paez and Whalen, 2010; Whalen et al., 2013), In contrast, public transport users tend to assess their experience more negatively (De Vos et al.
-2016; Abenoza et al.
-2017; Ettema et al.
-2012; Páez and Whalen, 2010).
-Multi-modal trips also influence satisfaction levels; for instance, when an individual chooses a particular mode of transportation, she will report a higher level of satisfaction with that chosen mode – perhaps as a form of post hoc validation (Susilo and Cats, 2014).
-
-While the use of travel satisfaction has been mainly used in the context of daily trips – typically been linked to cost-benefit and utilitarian measurements –, the evaluation of Subjective Wellbeing (SWB) over time has risen as an alternative measure.
-In the field of travel behaviour, Ettema et al.
-(2010; p.
-725) have defined SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporality – which implies assuming a tendency to be more stable over time.
-This concept has prompted a growing literature that complements and applies SWB in a broader range of satisfaction scales and situations.
-The definition of other factors such as travel choice mode, attitudes and external elements of the built environment has been studied for a broader understanding of the changes produced in the SWB.
-As these factors do not necessarily apply to the general life satisfaction on the long term, the studies have aimed to determine both the direct and indirect effects on the perception of users (see, e.g.
-Ye and Titheridge 2017).
-Other concepts have also emerged as the Satisfaction with Travel Scale (STS), a measurement devised by Ettema et al.
-(2011) as well as different scales based on people’s travel perceptions.
-De Vos et al.
-(2015) for instance, explore in detail the underlying dimensions of the affective domain of STS in which SWB is based (for more on STS see also Friman et al.
-2013).
-
-Recent literature on SWB and its link with transport have demonstrated a relationship between people’s perceptions and satisfaction with their daily travel (Smith, 2017; St-Louis et al.
-2014; Paez and Whalen, 2010; Whalen et al., 2013).
-Scholars have shown that accessibility has been the most developed factor that influences people’s wellbeing (Delbosc, 2012), and activities have a direct impact on travel satisfaction (Bergstad et al., 2010).
-Delbosc (2012; 28) for instance, has summarised the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.
-However, understanding the components affecting people’s perceptions implies the differentiation between the emotional (also named as symbolic-affective) and the instrumental reasons (Bergstad, 2001).
-Steg et al.
-(2011) have compared symbolic-affective opposed to instrumental-reasoned motives based on car-use, and other studies have also found associations between affective and symbolic aspects of car-use (see, e.g.
-Gatersleben, 2007; Lois & López-Sáez, 2009).
-Previous studies have demonstrated how socio-demographic factors affect the levels of SWB.
-The effect of income on SWB (Clarck and Oswald, 1996, Ferrer-i-Carbonell, 2005); education and unemployment (Argyle, 1999); age (Diener and Suh, 1997) and gender (Tesch-Römer et al., 2008) have already been studied.
-Recent research also suggests the links between commuting, SWB and emotional wellbeing assessment (Olson et al.
-2013; Kahneman et al.
-2004).
-However, more research is needed to understand how these socio-demographic variables, connect as well with the decisions on main transport mode choices; or research distinguishing between hedonic (journey experience) and eudaimonic (flourishing) value of trips.
-
-The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel (Zorrilla et al., 2019).
-In this way, there is an emerging literature that investigates affective factors in travel behaviour in a number of developing countries.
-A cross-country study in Asia revealed that the affective factors of public transportation and car use are important, and in particular the social orderliness of transit was suggested as a way to make this mode more attractive to users (Van et al., 2014).
-In terms of active travel, a study in China found that attitudes that embrace new styles and technologies despite their cost are associated with the intention to continue using shared bicycles (Shao and Liang, 2019).
-The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows how users felt proud using a bicycle shared system, in addition to experiencing feelings of belonging to a civic culture and the enjoyment and pleasure of travel itself (Bejarano et al., 2019).
-This paper contributes to further our understanding of affective and instrumental factors in travel behaviour in a developing country.
-
-Data and Methods
-===================
-
-This paper implements an analysis of correspondence comparing the primary mode of transportation with affective and utilitarian SWB factors in a sample of travellers in Santiago de Chile.
-
-## Sample
-
-The study is based on a survey conducted in Santiago during the months of November and December 2016, that collected information on a wide range of travel and related issues.
-The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
-An equal representation of both genders and a representation of the proportion of inhabitants per area have been chosen as relevant characteristics of the sample.
-In total, 451 persons validly completed the survey.
-In the first part of the questionnaire the participants were asked about basic socio-demographic data and main transport mode for commuting.
-In the second part, the questionnaire asked about the modes that people associate with affective and instrumental positive concepts of commuting, as well as the levels of overall satisfaction with the trips.
-These two sections of the survey have been considered for the analysis of this paper.
-The second part of the survey asked about the association between the primary transport mode and 18 positive and negative feelings.
-The question is: “Indicate the modes that you associate to the following feelings”.
-The respondents could indicate all the modes they associated to the feelings on the list.
-Three affective and three instrumental/utilitarian factors, all positive, have been considered for this analysis: freedom, enjoyment, happiness (affective), and security, time savings, efficiency (instrumental/utilitarian).
-The questionnaire provides a binary indicator that describes the presence or absence of modal correspondence for each one the selected six factors.
-The analysis has considered socioeconomic variables (gender, age, education, occupation, income, disabilities), as well as other variables as driving licence, journey times, monthly expenditure on transport and satisfaction with the overall trip.
-
-[REPORT DESCRIPTIVE STATISTICS?
-Include definitions, e.g., is K-12 equivalent to “minimal mandatory education”?
-What is Tech Univ?
-What are the range of values of low, middle, high income?
-Journey time is in minutes]
-
-## Analytical Approach
-
-The analytical approach in this paper is based on correspondence.
-Previous research has developed the concept of modal dissonance for referring to the mismatch between the actual mode and the mode that enables users to experience positive affective or instrumental factors (De Vos et al., (2012; 2014) and Schwanen and Mokhtarian, 2004, 2005a, 2005b).
-More concretely, Schwanen and Mokhtarian (2004; 89) define dissonance based on the incongruence between residential neighbourhood where the individual currently resides and her preference structure toward such characteristics of the residential environment.
-In this paper we consider correspondence, which happens when travellers associate the positive utilitarian and affective SWB factors to the mode they have used as their primary transport mode for commuting or performing their main activities.
-The opposite of correspondence would be modal dissonance.
-
-More specifically, the concept of modal dissonance means that a user of mode X identifies a different mode Y when associating affective values.
-For example, a user of private transport (i.e., mode “Car”)  may select mode “Bicycle” when asked about the of the association between the concept of freedom to a transport mode.
-In this case, the person who uses the mode “Car” as their primary mode of transportation attaches positive emotional and instrumental factors not to that mode, but to a different one – in this case to the bicycle.
-It could be the case that the modal dissonance corresponds just to one of the types of factors, either affective or instrumental.
-For example, it is possible that a person who uses the Metro as their main transport mode associates that mode to the instrumental factors (security, time savings, efficiency) – but relates positive emotional factors (freedom, enjoyment, happiness) to a different mode, say to the bicycle.
-
-The ways for measuring equity in transport projects and the most vulnerable groups affected by transport have been the aspects that have nurtured the focus of this study.
-The hypothesis is that public transport users will show a lower correspondence between their primary mode and the modes they relate with positive factors of SWB.
-This is relevant as more disadvantaged people have less options of choosing their preferred transport modes and they tend to associate positive affective and instrumental factors to modes that they are not able to use.
-These perceptions evidence equity gaps between groups – where the most vulnerable groups are much more affected.
-The methods used are analysis of correspondence and multinomial regression, both around the associations of transport modes and affective and instrumental factors, derived from the SWB framework.
-
-Results
-==========
-
-```{r cross-with-instrumental, include=FALSE, eval=FALSE}
-
-# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)
-
-## Age
-
-age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
-age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-age_by_safety <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "SAFETY_DISSONANCE", type = "r")
-age_by_time <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "TIME_DISSONANCE", type = "r")
-age_by_efficiency <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Education
-
-education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
-education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-education_by_safety <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "SAFETY_DISSONANCE", type = "r")
-education_by_time <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "TIME_DISSONANCE", type = "r")
-education_by_efficiency <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Income
-
-income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-income_by_safety <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "SAFETY_DISSONANCE", type = "r")
-income_by_time <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "TIME_DISSONANCE", type = "r")
-income_by_efficiency <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Mode
-
-mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
-mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-mode_by_safety <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "SAFETY_DISSONANCE", type = "r")
-mode_by_time <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "TIME_DISSONANCE", type = "r")
-mode_by_efficiency <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Travel Time
-
-time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-time_by_safety <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "SAFETY_DISSONANCE", type = "r")
-time_by_time <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "TIME_DISSONANCE", type = "r")
-time_by_efficiency <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-```
-
-```{r cross-without-instrumental, include=FALSE}
-
-# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)
-
-## Age
-
-age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
-age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-age_by_poverty <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "POVERTY_DISSONANCE", type = "r")
-age_by_luxury <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "LUXURY_DISSONANCE", type = "r")
-age_by_status <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Education
-
-education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
-education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-education_by_poverty <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "POVERTY_DISSONANCE", type = "r")
-education_by_luxury <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "LUXURY_DISSONANCE", type = "r")
-education_by_status <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Income
-
-income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-income_by_poverty <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "POVERTY_DISSONANCE", type = "r")
-income_by_luxury <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "LUXURY_DISSONANCE", type = "r")
-income_by_status <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Mode
-
-mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
-mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-mode_by_poverty <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "POVERTY_DISSONANCE", type = "r")
-mode_by_luxury <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "LUXURY_DISSONANCE", type = "r")
-mode_by_status <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Travel Time
-
-time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-time_by_poverty <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "POVERTY_DISSONANCE", type = "r")
-time_by_luxury <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "LUXURY_DISSONANCE", type = "r")
-time_by_status <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "STATUS_DISSONANCE", type = "r")
-
-```
-
-```{r collect-cross-tabulation-results-with-instrumental, include=FALSE, eval=FALSE}
-
-# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES
-
-## Age
-
-age_results <- cbind(age_by_freedom$crosstab, 
-                     age_by_enjoyment$crosstab, 
-                     age_by_happiness$crosstab,
-                     age_by_safety$crosstab,
-                     age_by_time$crosstab,
-                     age_by_efficiency$crosstab)
-
-# Drop the row totals
-age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-age_results <- age_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-age_results <- age_results %>%
-  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(age_by_happiness$table)$p.value,
-         chi2.safety = summary(age_by_safety$table)$p.value,
-         chi2.time = summary(age_by_time$table)$p.value,
-         chi2.efficiency = summary(age_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Education
-
-education_results <- cbind(education_by_freedom$crosstab, 
-                     education_by_enjoyment$crosstab, 
-                     education_by_happiness$crosstab,
-                     education_by_safety$crosstab,
-                     education_by_time$crosstab,
-                     education_by_efficiency$crosstab)
-
-# Drop the row totals
-education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-education_results <- education_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-education_results <- education_results %>%
-  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(education_by_happiness$table)$p.value,
-         chi2.safety = summary(education_by_safety$table)$p.value,
-         chi2.time = summary(education_by_time$table)$p.value,
-         chi2.efficiency = summary(education_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Income
-
-income_results <- cbind(income_by_freedom$crosstab, 
-                     income_by_enjoyment$crosstab, 
-                     income_by_happiness$crosstab,
-                     income_by_safety$crosstab,
-                     income_by_time$crosstab,
-                     income_by_efficiency$crosstab)
-
-# Drop the row totals
-income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-income_results <- income_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-income_results <- income_results %>%
-  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(income_by_happiness$table)$p.value,
-         chi2.safety = summary(income_by_safety$table)$p.value,
-         chi2.time = summary(income_by_time$table)$p.value,
-         chi2.efficiency = summary(income_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Mode USED
-
-mode_results <- cbind(mode_by_freedom$crosstab, 
-                     mode_by_enjoyment$crosstab, 
-                     mode_by_happiness$crosstab,
-                     mode_by_safety$crosstab,
-                     mode_by_time$crosstab,
-                     mode_by_efficiency$crosstab)
-
-# Drop the row totals
-mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-mode_results <- mode_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-mode_results <- mode_results %>%
-  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(mode_by_happiness$table)$p.value,
-         chi2.safety = summary(mode_by_safety$table)$p.value,
-         chi2.time = summary(mode_by_time$table)$p.value,
-         chi2.efficiency = summary(mode_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Time
-
-time_results <- cbind(time_by_freedom$crosstab, 
-                     time_by_enjoyment$crosstab, 
-                     time_by_happiness$crosstab,
-                     time_by_safety$crosstab,
-                     time_by_time$crosstab,
-                     time_by_efficiency$crosstab)
-
-# Drop the row totals
-time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-time_results <- time_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-time_results <- time_results %>%
-  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(time_by_happiness$table)$p.value,
-         chi2.safety = summary(time_by_safety$table)$p.value,
-         chi2.time = summary(time_by_time$table)$p.value,
-         chi2.efficiency = summary(time_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-```
-
-```{r collect-cross-tabulation-results-without-instrumental, include=FALSE}
-
-# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES
-
-## Age
-
-age_results <- cbind(age_by_freedom$crosstab, 
-                     age_by_enjoyment$crosstab, 
-                     age_by_happiness$crosstab,
-                     age_by_poverty$crosstab,
-                     age_by_luxury$crosstab,
-                     age_by_status$crosstab)
-
-# Drop the row totals
-age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-age_results <- age_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-age_results <- age_results %>%
-  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(age_by_happiness$table)$p.value,
-         chi2.poverty = summary(age_by_poverty$table)$p.value,
-         chi2.luxury = summary(age_by_luxury$table)$p.value,
-         chi2.status = summary(age_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Education
-
-education_results <- cbind(education_by_freedom$crosstab, 
-                     education_by_enjoyment$crosstab, 
-                     education_by_happiness$crosstab,
-                     education_by_poverty$crosstab,
-                     education_by_luxury$crosstab,
-                     education_by_status$crosstab)
-
-# Drop the row totals
-education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-education_results <- education_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-education_results <- education_results %>%
-  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(education_by_happiness$table)$p.value,
-         chi2.poverty = summary(education_by_poverty$table)$p.value,
-         chi2.luxury = summary(education_by_luxury$table)$p.value,
-         chi2.status = summary(education_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Income
-
-income_results <- cbind(income_by_freedom$crosstab, 
-                     income_by_enjoyment$crosstab, 
-                     income_by_happiness$crosstab,
-                     income_by_poverty$crosstab,
-                     income_by_luxury$crosstab,
-                     income_by_status$crosstab)
-
-# Drop the row totals
-income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-income_results <- income_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-income_results <- income_results %>%
-  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(income_by_happiness$table)$p.value,
-         chi2.poverty = summary(income_by_poverty$table)$p.value,
-         chi2.luxury = summary(income_by_luxury$table)$p.value,
-         chi2.status = summary(income_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Mode USED
-
-mode_results <- cbind(mode_by_freedom$crosstab, 
-                     mode_by_enjoyment$crosstab, 
-                     mode_by_happiness$crosstab,
-                     mode_by_poverty$crosstab,
-                     mode_by_luxury$crosstab,
-                     mode_by_status$crosstab)
-
-# Drop the row totals
-mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-mode_results <- mode_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-mode_results <- mode_results %>%
-  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(mode_by_happiness$table)$p.value,
-         chi2.poverty = summary(mode_by_poverty$table)$p.value,
-         chi2.luxury = summary(mode_by_luxury$table)$p.value,
-         chi2.status = summary(mode_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Time
-
-time_results <- cbind(time_by_freedom$crosstab, 
-                     time_by_enjoyment$crosstab, 
-                     time_by_happiness$crosstab,
-                     time_by_poverty$crosstab,
-                     time_by_luxury$crosstab,
-                     time_by_status$crosstab)
-
-# Drop the row totals
-time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-time_results <- time_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-time_results <- time_results %>%
-  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(time_by_happiness$table)$p.value,
-         chi2.poverty = summary(time_by_poverty$table)$p.value,
-         chi2.luxury = summary(time_by_luxury$table)$p.value,
-         chi2.status = summary(time_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-```
-
-```{r crosstab-all-results-with-instrumental, include=FALSE, eval=FALSE}
-
-# Here we bind all the results into a single dataframe for printing
-
-xtab_results <- rbind(age_results,
-                      education_results,
-                      income_results,
-                      mode_results,
-                      time_results) %>%
-  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
-         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
-         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
-         chi2.safety = ifelse(chi2.safety >= 0.001, paste0(round(chi2.safety, 4)), "$<0.001$"),
-         chi2.time = ifelse(chi2.time >= 0.001, paste0(round(chi2.time, 4)), "$<0.001$"),
-         chi2.efficiency = ifelse(chi2.efficiency >= 0.001, paste0(round(chi2.efficiency, 4)), "$<0.001$"))
-
-xtab_results[10:13, 3] <- "$< 0.001$"
-```
-
-```{r crosstab-all-results-without-instrumental, echo=FALSE}
-
-# Here we bind all the results into a single dataframe for printing
-
-xtab_results <- rbind(age_results,
-                      education_results,
-                      income_results,
-                      mode_results,
-                      time_results) %>%
-  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
-         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
-         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
-         chi2.poverty = ifelse(chi2.poverty >= 0.001, paste0(round(chi2.poverty, 4)), "$<0.001$"),
-         chi2.luxury = ifelse(chi2.luxury >= 0.001, paste0(round(chi2.luxury, 4)), "$<0.001$"),
-         chi2.status = ifelse(chi2.status >= 0.001, paste0(round(chi2.status, 4)), "$<0.001$"))
-
-xtab_results[10:13, 3] <- "$< 0.001$"
-```
-
-## Who experiences dissonance?
-
-The first step of the analysis seeks to understand whether there are statistical associations between the variables of interest.
-The analysis considers the cases where there is a lack of correspondence between the primary mode choice and the 6 SWB/instrumental factors previously described  – or in other words, where there is modal dissonance.
-
-Table 1 shows the results of the analysis of correspondence and the dissonances between the primary mode of travel on the one hand, and SWB and instrumental factors on the other.
-As seen in the table, there are five categories that we use for the analysis.
-Three of these categories are socio-economic and demographic, namely age, level of education, income.
-The other two categories are transportation related, namely primary mode of travel and journey time.
-Correspondence is tested in every case by means of the $\chi^2$ statistic.
-It is interesting to note that the only category for which all affective/instrumental factors are significant at better than 5% level of confidence is mode of travel.
-
-With respect to age, we observe that levels of dissonance tend to be high in general, and the results indicate that when it comes to affective factors, dissonance levels tend to be significantly higher for younger travellers, in particular Enjoyment.
-In terms of instrumental factors, dissonance also tends to significantly decline with age when considering Security.
-On the other hand, the levels of dissonance in terms of Time Savings and Efficiency, while high, do not show significant differences by age group.
-Overall, the findings suggest that dissonance tends to decline with age.
-
-The results indicate that the category of Education is less useful to discriminate between different levels of dissonance.
-Two affective factors are significant at 10% or better (Freedom and Happiness) and show that dissonance tends to decline at higher levels of education.
-One instrumental factor is significant at 10% or better (Time Savings) and we see there that the level of dissonance tends to grow with higher levels of education.
-Another instrumental factor (Security) is significant at 5% or better and shows that dissonance in this factor declines with higher education.
-The picture that emerges is of highly educated people who are relatively less dissatisfied with their primary mode of transportation when it comes to Freedom, Happiness, and Security, but more dissatisfied with their Time Savings than people who are less highly educated.
-
-In general, dissonance tends to be higher for lower income individuals.
-Table 1 shows that the low-income segment has a significantly higher percentage of cases of dissonance for two affective factors.
-In the case of Freedom, for example, the lack of correspondence for low-income is 83.9% compared to 60% for the high-income segment.
-The levels of dissonance are higher for Enjoyment and follow the same decreasing trend for higher levels of income.
-Dissonance is marginally lower for instrumental factors, and significant for Security and Time Savings.
-
-As noted above, there are significant differences in dissonance by primary mode of travel, both for affective and instrumental factors.
-For affective factors, the highest levels of dissonance tend to be for users of public transportation, and the lowest for car users and active travellers.
-For instance, feelings of Freedom, Enjoyment, and Happiness are more frequently expressed by users of car and active travellers than users of public transportation.
-Indeed, people who travel by Metro or Bus almost never associate any of these positive affective attributes to these modes (dissonance is consistently greater than 90%).
-In contrast, active travellers have some of the lowest levels of dissonance in all three affective factors, in particular Freedom and Happiness.
-This analysis is in line with previous research regarding car, active travel, and public transportation (e.g., Steg et al., 2001; Páez and Whalen, 2010; Whalen et al., 2013), which tend to agree on the negative associations in the perception of affective factors when the primary mode is Metro or bus.
-
-Figure 4 shows the percentage of dissonance by primary transport mode, for both affective and instrumental factors.
-For instance, the graph at the top shows that the highest percentages of dissonances come from users of Metro and bus , compared to other modes as the car or active transport.
-This is consistent with previous studies that have separately demonstrated that public transport users tend to assess more negatively subjective factors (explored e.g.
-in Stradling et al., 1999; Gatersleben and Uzzell, 2007).
-For example, although car users have higher dissonance values than active transport, comparatively this segment has much lower percentages of dissonances than public transport, idea also supported by research that has shown that car users tend to attribute importance to symbolic aspects that positively contribute to their perception on driving (Steg et al., 2001; Mokhtarian and Salomon, 2001).
-
-Freedom and happiness tend to have a lower percentage of dissonances in the case of active transport, which means that cyclists and individuals who mainly walk for their commutes, tend to associate positive subjective values while using these modes.
-This is also consistent with other studies that have shown positive affective associations with the use of cycling and walking (Anable and Gatersleben, 2005; Gatersleben and Uzzell, 2007).
-The question at the survey has not specify the dimensions of freedom, thus has open the door for different interpretations as the freedom to choose certain mode or route, freedom while using the mode, or the freedom to access to certain places while travelling.
-Journey time: As shown in Figure 3, the analysis carried out by journey time also reveals coincidences with previous research in this area, since for shorter trips (up to 20 minutes) the analysis shows less dissonance between the primary mode and positive subjective associations mainly for affective factors.
-On the contrary, as journey time increases, higher is the dissonance.
-Strangely, the feelings of Security and Efficiency have not been statistically representative for the Journey Time analysis.
-
-In terms of instrumental factors, interestingly Figure 4 shows that bus users have the lowest percentage of dissonance regarding time savings (29%).
-However, considering the other instrumental factors, bus users have a high percentage of dissonance for security and efficiency.
-In the case of security, this means that most bus users (71%) have considered the bus as a mode that they associate to time-savings, although it is the mode that has more dissonant evaluations in all other SWB factors.
-This also seems difficult to explain considering the negative evaluation that the Transantiago system has consistently had.
-Some data provided by the Survey of Satisfaction with Transantiago Operators (DTPM, 2017) is about users' perception of journey time from origin to destination.
-In this question, and after 10 years of implementation of the system, users diagnose an average journey of 47 minutes, a value that tends to increase with respect to the data delivered by the same survey 5 years before (43.5 minutes on average).
-Worryingly, long trips of more than 30 minutes have had inconsistent variability over the years, reaching an average of more than 37 minutes in 2016.
-Short trips, however, remain roughly equal to previous years, and do not show significant changes in the average of 6-7 minutes per trip .
-This survey has the peculiarity  of being developed by the Metropolitan Public Transport Board (DTPM), whose mission is to articulate the functions of the different modes of public transport with a specific interest in buses Transantiago and Metro de Santiago.
-
-Another big gap on these instrumental factors relates to the perception of security that is especially significant for car users.
-This means that a 75% of car users have chosen as primary mode the same one as they relate to the feeling of security, which is completely opposite to other transport modes, specially bus users.
-Bus users have the highest dissonance (98%), which means that practically all this group of users have chosen another mode for referring to the feelings of security.
-The recently referred DTPM survey does not have any particular question that addresses the issue of safety – mostly related in this context as security.
-
-```{r table-cross-tabulation-results-with-instrumental, echo = FALSE, eval=FALSE}
-kable(xtab_results,
-      "latex",
-      digits = 2,
-      booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
-      escape = FALSE,
-      align = c("l", rep("c", 12)),
-      col.names = c("Variable", 
-                    "Freedom", "$\\chi^2$ p-val", 
-                    "Enjoyment", "$\\chi^2$ p-val",
-                    "Happiness", "$\\chi^2$ p-val",
-                    "Safety", "$\\chi^2$ p-val",
-                    "Time", "$\\chi^2$ p-val",
-                    "Efficiency", "$\\chi^2$ p-val")) %>%
-  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
-  pack_rows("Age", 1, 3) %>%
-  pack_rows("Education", 4, 6) %>%
-  pack_rows("Income", 7, 9) %>%
-  pack_rows("Mode", 10, 13) %>%
-  pack_rows("Journey Time", 14, 17)  %>%
-  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
-  landscape()
-```
-
-```{r table-cross-tabulation-results-without-instrumental, echo = FALSE}
-kable(xtab_results,
-      "latex",
-      digits = 2,
-      booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
-      escape = FALSE,
-      align = c("l", rep("c", 12)),
-      col.names = c("Variable", 
-                    "Freedom", "$\\chi^2$ p-val", 
-                    "Enjoyment", "$\\chi^2$ p-val",
-                    "Happiness", "$\\chi^2$ p-val",
-                    "Poverty", "$\\chi^2$ p-val",
-                    "Luxury", "$\\chi^2$ p-val",
-                    "Status", "$\\chi^2$ p-val")) %>%
-  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
-  pack_rows("Age", 1, 3) %>%
-  pack_rows("Education", 4, 6) %>%
-  pack_rows("Income", 7, 9) %>%
-  pack_rows("Mode", 10, 13) %>%
-  pack_rows("Journey Time", 14, 17)  %>%
-  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
-  landscape()
-```
-
-Figure 5 shows the points of origin of the survey for the case of public transport users.
-Metro users as primary mode are shown, bus users are shown in cyan.
-The size of the points represents the number of dissonances.
-The higher the point, the greater the number of SWB factors that do not coincide with the primary transport mode.
-The image shows that the intensity or size of the circles is homogeneously distributed in the territory, even though the blue circles (metro) tend to show slightly less dissonance.
-The visualisation of this map is more dramatic when it is compared to the following Figure 6.
-
-Figure 6 shows the points of origin for the case of private transport (cars) and active transport (walking and cycling).
-Again, the size of the circles represents intensity levels of dissonance.
-The number of dissonances is lower than in the case of Figure 5, which indicates that users of private and active transport tend to use a mode of transport that they relate to one of the positive factors derived from subjective wellbeing.
-In this sense, it could be said that this type of user tends to be more advantaged than the public transport user, in a dimension not only utilitarian but also emotional and attitudinal.
-
-## Which modes do travelers associate with affective and instrumental values?
-
-Here we can visualize the modes that travellers associate with different affective and instrumental values.
-The tool we use for this is a mosaic plot.
-See the mosaic plots in Figure \ref{fig:mosaic-plots-by-attribute}.
-
-```{r figure-mosaic-plots-by-attribute-with-instrumental, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}
-
-ggplot(data = Modes_by_Attribute) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode selected for the value of {Freedom, Enjoyment, Happiness, Safety, Time, Efficiency}") +
-  ylab("Main mode of transportation") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_wrap(~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute-without-instrumental, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Proportion of responses by mode associated with {Freedom, Enjoyment, Happiness, Poverty, Luxury, Status}") +
-  ylab("Proportion of respondents by primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_wrap(~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-Conclusions
-==========
-
-Words go here.
-
-References {#references .unnumbered}
-==========

### 2019-11-01 Dissonance_Santiago_Title_Page_v1.tex
Added discussion based on the files sent by Beatriz, and prepared files for submission

--- 2019-10-23 Dissonance_Santiago_v1.tex
@@
 \bibliographystyle{elsarticle-harv}
-\usepackage{graphicx}
-% We will generate all images so they have a width \maxwidth. This means
-% that they will get their normal width if they fit onto the page, but
-% are scaled down if they would overflow the margins.
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
-\else\Gin@nat@width\fi}
-\makeatother
-\let\Oldincludegraphics\includegraphics
-\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
 \ifxetex
@@
 % Pandoc header
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 
@@
 
-  \title{Do Drivers Dream of Walking? An Investigation of Dissonance in the
-Primary Mode of Travel from the Perspective of Subjective Wellbeing}
-    \author[Some University]{Beasly Bee\corref{c1}}
-   \ead{alice@university.com} 
+  \title{Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance
+from the Perspective of Subjective Wellbeing}
+    \author[University College London]{Beatriz Mella Lira\corref{c1}}
+   \ead{beatriz.lira.14@ucl.ac.uk} 
    \cortext[c1]{Corresponding Author}
-    \author[Some School]{Antsy Aardvark}
-   \ead{aa@school.com}
+    \author[McMaster University]{Antonio Paez}
+   \ead{paezha@mcmaster.ca}
 
-      \address[Some University]{Department, Street, City, State, Zip}
-    \address[Some School]{Department, Street, City, State, Zip}
+      \address[University College London]{Bartlett School of Planning, Sixth Floor, Central House, 14 Upper Woburn
+Place, London, WC1H0NN UK}
+    \address[McMaster University]{School of Geography and Earth Sciences, 1280 Main St W, Hamilton,
+Ontario, L8S 1S4 Canada}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Transportation planning for decades has focused on providing mobility
-for the private automobile. This is a model of development that was
-initially introduced in North America as a solution to urbanizations
-problems, and that was eventually copied elsewhere (Brown et al., 2009;
-Angotti, 1996) . Despite the initial promise of automotive technology,
-it is now evident that mobility centred on the private automobile has
-given rise to a litany of maladies that are in urgent need of
-correction. This includes environmental concerns (i.e., climate change;
-Chapman, 2007) as well as other social (Boschmann and Kwan, 2008),
-health (Khreis et al., 2016), and equity issues (Bocarejo and Oviedo,
-2012). As the real impacts of our societal dependence on the private
-autombobile have become increasingly evident, the transportation agenda
-has in recent years aimed to shift focus to the reduction of car-use and
-towards the creation of mobility polycultures that offer a broader menu
-of transportation alternatives than just the private automobile (Miller,
-2011) . In order to successfully achieve this goal, it is essential not
-only to provide the services and facilities that support public
-transportation and active travel, but also to attract new users to these
-modes of transportation (Ettema et al.~2011). Within this context, it
-has been argued that sustainable transportation policies require all
-participants in the transportation system to challenge what Gossling and
-Cohen (2014) term ``transportation taboos'': deep-seated ideas
-concerning the contribution to emissions by individuals, the inequality
-of market-based approaches, and the social and psychological functions
-of transportation. With respect to the latter, moving beyond a purely
-utilitarian focus, it is important to understand how users perceive
-affective and instrumental elements on their transportation experience,
-since this can help to incorporate adequate improvements in alternative
-transportation, including transit and active modes, to make them more
-attractive to users (Anable and Gatersleben, 2005; Domarchi et al.,
-2008; Gatersleben and Uzzell, 2007; Steg 2005 ).
-
-A useful lens to investigate the social and psychological functions of
-transportation is by means of the concept of subjective wellbeing (SWB.
-See, inter alia, De Vos et al., 2013 and Chatterjee et al., 2019) . SWB
-is defined by the OECD as ``{[}g{]}ood mental states, including all of
-the various evaluations, positive and negative, that people make of
-their lives, and the affective reactions of people to their
-experiences'' (OECD, 2013, p.~10). Accordingly, the aim of this paper is
-to analyse some of the factors that can potentially affect the levels of
-SWB in the wide spectrum of public, private and active transport modes
-in the context of Santiago de Chile. Previous research suggests that
-public transport users experience a negative gap in desired and actual
-travel time, whereas active travellers don't seem to mind somewhat
-longer trips than what strictly needed (e.g., Páez and Whalen, 2010). In
-the context of a Latin American country, historically the poor travel
-experience of public transit users and active travellers reflects the
-social inequalities of social groups that have no alternative but to
-move in these types of modes while living far from the work centres and
-main activities. The paper aims to reflect on the possibilities of
-increasing the SWB while travelling, and how this could increase the
-attractiveness of public transport and active travel in the
-socio-demographic groups studied. This can help not only to reduce the
-use of private transport but also decrease the inequality gap between
-these users.
-
-The paper explores how positive affective and instrumental/utilitarian
-factors of SWB correspond to the use of the primary mode of
-transportation. It uses an analysis of correspondence that considers the
-actual primary mode versus the mode that individuals associated to both
-utilitarian (designed to be useful or practical rather than attractive)
-and affective (expressing a person's feelings) SWB factors. For example,
-it will be analysed if a person who uses public transport as the primary
-mode, tends to associate these modes with positive affective factors (as
-freedom, enjoyment or happiness) or positive utilitarian factors (as
-security, time-savings or efficiency). We hypothesize that there is a
-more persistent non-correspondence or mismatch within the more
-disadvantage groups or within the users of public transport.
-
-The paper contributes to the literature in three areas. First, it
-contributes to an emerging literature on the topic in the context of the
-Global South (Bejarano et al., 2017 ; Shao and Liang, 2019 ; Van et al.,
-2014 ; Zorrilla et al., 2019); to the best of our knowledge, the case of
-Chile has not yet been reported. Second, although there is literature on
-the enjoyment of commute and other emotional factors, from a hedonic and
-even eudaimonic perspectives, the analysis has yet to be applied more
-fully in terms of distributional issues -- i.e.~which groups are mostly
-disadvantaged. Finally, the analysis shows the attitudes of people
-towards their primary mode and their perception towards `ideal modes' --
-implying their preferences, even in situations when their ideal mode is
-not part of their actual choice set. The attitudes of travellers towards
-transport modes are critical factors to be considered by policy-makers
-in case they want to promote and increase the use of public transport or
-active modes (e.g., Bejarano et al., 2019). The paper explores these
-positive and negative associations within the transport options used in
-Santiago.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
-
-The transportation community has for the most part already agreed to the
-need of looking at mobility and transport issues from the lens of
-wellbeing, to broaden the commonly used utilitarian perspective to
-evaluate projects. Users' travel satisfaction (Bergstad, 2001) has been
-the primary way to direct this challenge towards everyday mobility,
-resulting on research about satisfaction with different transport modes.
-For example, numerous studies report that car users have a higher level
-of satisfaction compared to other transport modes (Redmond and
-Mokhtarian, 2001 ; Bergstad et al.~2011; Eriksson et al.~2013; Whalen et
-al., 2013). In a similar way, there are multiple reports that active
-travel also tends to yield high levels of satisfaction (Smith, 2017;
-St-Louis et al.~2014; Paez and Whalen, 2010; Whalen et al., 2013), In
-contrast, public transport users tend to assess their experience more
-negatively (De Vos et al.~2016; Abenoza et al.~2017; Ettema et al.~2012;
-Páez and Whalen, 2010). Multi-modal trips also influence satisfaction
-levels; for instance, when an individual chooses a particular mode of
-transportation, she will report a higher level of satisfaction with that
-chosen mode -- perhaps as a form of post hoc validation (Susilo and
-Cats, 2014).
-
-While the use of travel satisfaction has been mainly used in the context
-of daily trips -- typically been linked to cost-benefit and utilitarian
-measurements --, the evaluation of Subjective Wellbeing (SWB) over time
-has risen as an alternative measure. In the field of travel behaviour,
-Ettema et al.~(2010; p.~725) have defined SWB as the degree to which an
-individual positively evaluates the overall quality of their lives,
-where the general life satisfaction encompasses a more extended
-temporality -- which implies assuming a tendency to be more stable over
-time. This concept has prompted a growing literature that complements
-and applies SWB in a broader range of satisfaction scales and
-situations. The definition of other factors such as travel choice mode,
-attitudes and external elements of the built environment has been
-studied for a broader understanding of the changes produced in the SWB.
-As these factors do not necessarily apply to the general life
-satisfaction on the long term, the studies have aimed to determine both
-the direct and indirect effects on the perception of users (see, e.g.~Ye
-and Titheridge 2017). Other concepts have also emerged as the
-Satisfaction with Travel Scale (STS), a measurement devised by Ettema et
-al.~(2011) as well as different scales based on people's travel
-perceptions. De Vos et al.~(2015) for instance, explore in detail the
-underlying dimensions of the affective domain of STS in which SWB is
-based (for more on STS see also Friman et al.~2013).
-
-Recent literature on SWB and its link with transport have demonstrated a
-relationship between people's perceptions and satisfaction with their
-daily travel (Smith, 2017; St-Louis et al.~2014; Paez and Whalen, 2010;
-Whalen et al., 2013). Scholars have shown that accessibility has been
-the most developed factor that influences people's wellbeing (Delbosc,
-2012), and activities have a direct impact on travel satisfaction
-(Bergstad et al., 2010). Delbosc (2012; 28) for instance, has summarised
-the most significant influences on psychological wellbeing: poverty and
-employment, meaningful relationships and health. However, understanding
-the components affecting people's perceptions implies the
-differentiation between the emotional (also named as symbolic-affective)
-and the instrumental reasons (Bergstad, 2001). Steg et al.~(2011) have
-compared symbolic-affective opposed to instrumental-reasoned motives
-based on car-use, and other studies have also found associations between
-affective and symbolic aspects of car-use (see, e.g.~Gatersleben, 2007;
-Lois \& López-Sáez, 2009). Previous studies have demonstrated how
-socio-demographic factors affect the levels of SWB. The effect of income
-on SWB (Clarck and Oswald, 1996, Ferrer-i-Carbonell, 2005); education
-and unemployment (Argyle, 1999); age (Diener and Suh, 1997) and gender
-(Tesch-Römer et al., 2008) have already been studied. Recent research
-also suggests the links between commuting, SWB and emotional wellbeing
-assessment (Olson et al.~2013; Kahneman et al.~2004). However, more
-research is needed to understand how these socio-demographic variables,
-connect as well with the decisions on main transport mode choices; or
-research distinguishing between hedonic (journey experience) and
-eudaimonic (flourishing) value of trips.
-
-The research needs already recognized in the developed world are also
-markedly acute in the context of the Global South, where historical
-inequality has tended to create a symbolic attachment to the automobile,
-in addition to negative connotations for public transport and active
-travel (Zorrilla et al., 2019). In this way, there is an emerging
-literature that investigates affective factors in travel behaviour in a
-number of developing countries. A cross-country study in Asia revealed
-that the affective factors of public transportation and car use are
-important, and in particular the social orderliness of transit was
-suggested as a way to make this mode more attractive to users (Van et
-al., 2014). In terms of active travel, a study in China found that
-attitudes that embrace new styles and technologies despite their cost
-are associated with the intention to continue using shared bicycles
-(Shao and Liang, 2019). The importance of affective factors for policy
-and planning is further highlighted by research in Colombia that shows
-how users felt proud using a bicycle shared system, in addition to
-experiencing feelings of belonging to a civic culture and the enjoyment
-and pleasure of travel itself (Bejarano et al., 2019). This paper
-contributes to further our understanding of affective and instrumental
-factors in travel behaviour in a developing country.
-
-\hypertarget{data-and-methods}{%
-\section{Data and Methods}\label{data-and-methods}}
-
-This paper implements an analysis of correspondence comparing the
-primary mode of transportation with affective and utilitarian SWB
-factors in a sample of travellers in Santiago de Chile.
-
-\hypertarget{sample}{%
-\subsection{Sample}\label{sample}}
-
-The study is based on a survey conducted in Santiago during the months
-of November and December 2016, that collected information on a wide
-range of travel and related issues. The data collection considered a
-quota-sampling method for gathering the information, considering the
-socio-demographic information from Pre-Census of 2012. An equal
-representation of both genders and a representation of the proportion of
-inhabitants per area have been chosen as relevant characteristics of the
-sample. In total, 451 persons validly completed the survey. In the first
-part of the questionnaire the participants were asked about basic
-socio-demographic data and main transport mode for commuting. In the
-second part, the questionnaire asked about the modes that people
-associate with affective and instrumental positive concepts of
-commuting, as well as the levels of overall satisfaction with the trips.
-These two sections of the survey have been considered for the analysis
-of this paper. The second part of the survey asked about the association
-between the primary transport mode and 18 positive and negative
-feelings. The question is: ``Indicate the modes that you associate to
-the following feelings''. The respondents could indicate all the modes
-they associated to the feelings on the list. Three affective and three
-instrumental/utilitarian factors, all positive, have been considered for
-this analysis: freedom, enjoyment, happiness (affective), and security,
-time savings, efficiency (instrumental/utilitarian). The questionnaire
-provides a binary indicator that describes the presence or absence of
-modal correspondence for each one the selected six factors. The analysis
-has considered socioeconomic variables (gender, age, education,
-occupation, income, disabilities), as well as other variables as driving
-licence, journey times, monthly expenditure on transport and
-satisfaction with the overall trip.
-
-{[}REPORT DESCRIPTIVE STATISTICS? Include definitions, e.g., is K-12
-equivalent to ``minimal mandatory education''? What is Tech Univ? What
-are the range of values of low, middle, high income? Journey time is in
-minutes{]}
-
-\hypertarget{analytical-approach}{%
-\subsection{Analytical Approach}\label{analytical-approach}}
-
-The analytical approach in this paper is based on correspondence.
-Previous research has developed the concept of modal dissonance for
-referring to the mismatch between the actual mode and the mode that
-enables users to experience positive affective or instrumental factors
-(De Vos et al., (2012; 2014) and Schwanen and Mokhtarian, 2004, 2005a,
-2005b). More concretely, Schwanen and Mokhtarian (2004; 89) define
-dissonance based on the incongruence between residential neighbourhood
-where the individual currently resides and her preference structure
-toward such characteristics of the residential environment. In this
-paper we consider correspondence, which happens when travellers
-associate the positive utilitarian and affective SWB factors to the mode
-they have used as their primary transport mode for commuting or
-performing their main activities. The opposite of correspondence would
-be modal dissonance.
-
-More specifically, the concept of modal dissonance means that a user of
-mode X identifies a different mode Y when associating affective values.
-For example, a user of private transport (i.e., mode ``Car'') may select
-mode ``Bicycle'' when asked about the of the association between the
-concept of freedom to a transport mode. In this case, the person who
-uses the mode ``Car'' as their primary mode of transportation attaches
-positive emotional and instrumental factors not to that mode, but to a
-different one -- in this case to the bicycle. It could be the case that
-the modal dissonance corresponds just to one of the types of factors,
-either affective or instrumental. For example, it is possible that a
-person who uses the Metro as their main transport mode associates that
-mode to the instrumental factors (security, time savings, efficiency) --
-but relates positive emotional factors (freedom, enjoyment, happiness)
-to a different mode, say to the bicycle.
-
-The ways for measuring equity in transport projects and the most
-vulnerable groups affected by transport have been the aspects that have
-nurtured the focus of this study. The hypothesis is that public
-transport users will show a lower correspondence between their primary
-mode and the modes they relate with positive factors of SWB. This is
-relevant as more disadvantaged people have less options of choosing
-their preferred transport modes and they tend to associate positive
-affective and instrumental factors to modes that they are not able to
-use. These perceptions evidence equity gaps between groups -- where the
-most vulnerable groups are much more affected. The methods used are
-analysis of correspondence and multinomial regression, both around the
-associations of transport modes and affective and instrumental factors,
-derived from the SWB framework.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{who-experiences-dissonance}{%
-\subsection{Who experiences
-dissonance?}\label{who-experiences-dissonance}}
-
-The first step of the analysis seeks to understand whether there are
-statistical associations between the variables of interest. The analysis
-considers the cases where there is a lack of correspondence between the
-primary mode choice and the 6 SWB/instrumental factors previously
-described -- or in other words, where there is modal dissonance.
-
-Table 1 shows the results of the analysis of correspondence and the
-dissonances between the primary mode of travel on the one hand, and SWB
-and instrumental factors on the other. As seen in the table, there are
-five categories that we use for the analysis. Three of these categories
-are socio-economic and demographic, namely age, level of education,
-income. The other two categories are transportation related, namely
-primary mode of travel and journey time. Correspondence is tested in
-every case by means of the \(\chi^2\) statistic. It is interesting to
-note that the only category for which all affective/instrumental factors
-are significant at better than 5\% level of confidence is mode of
-travel.
-
-With respect to age, we observe that levels of dissonance tend to be
-high in general, and the results indicate that when it comes to
-affective factors, dissonance levels tend to be significantly higher for
-younger travellers, in particular Enjoyment. In terms of instrumental
-factors, dissonance also tends to significantly decline with age when
-considering Security. On the other hand, the levels of dissonance in
-terms of Time Savings and Efficiency, while high, do not show
-significant differences by age group. Overall, the findings suggest that
-dissonance tends to decline with age.
-
-The results indicate that the category of Education is less useful to
-discriminate between different levels of dissonance. Two affective
-factors are significant at 10\% or better (Freedom and Happiness) and
-show that dissonance tends to decline at higher levels of education. One
-instrumental factor is significant at 10\% or better (Time Savings) and
-we see there that the level of dissonance tends to grow with higher
-levels of education. Another instrumental factor (Security) is
-significant at 5\% or better and shows that dissonance in this factor
-declines with higher education. The picture that emerges is of highly
-educated people who are relatively less dissatisfied with their primary
-mode of transportation when it comes to Freedom, Happiness, and
-Security, but more dissatisfied with their Time Savings than people who
-are less highly educated.
-
-In general, dissonance tends to be higher for lower income individuals.
-Table 1 shows that the low-income segment has a significantly higher
-percentage of cases of dissonance for two affective factors. In the case
-of Freedom, for example, the lack of correspondence for low-income is
-83.9\% compared to 60\% for the high-income segment. The levels of
-dissonance are higher for Enjoyment and follow the same decreasing trend
-for higher levels of income. Dissonance is marginally lower for
-instrumental factors, and significant for Security and Time Savings.
-
-As noted above, there are significant differences in dissonance by
-primary mode of travel, both for affective and instrumental factors. For
-affective factors, the highest levels of dissonance tend to be for users
-of public transportation, and the lowest for car users and active
-travellers. For instance, feelings of Freedom, Enjoyment, and Happiness
-are more frequently expressed by users of car and active travellers than
-users of public transportation. Indeed, people who travel by Metro or
-Bus almost never associate any of these positive affective attributes to
-these modes (dissonance is consistently greater than 90\%). In contrast,
-active travellers have some of the lowest levels of dissonance in all
-three affective factors, in particular Freedom and Happiness. This
-analysis is in line with previous research regarding car, active travel,
-and public transportation (e.g., Steg et al., 2001; Páez and Whalen,
-2010; Whalen et al., 2013), which tend to agree on the negative
-associations in the perception of affective factors when the primary
-mode is Metro or bus.
-
-Figure 4 shows the percentage of dissonance by primary transport mode,
-for both affective and instrumental factors. For instance, the graph at
-the top shows that the highest percentages of dissonances come from
-users of Metro and bus , compared to other modes as the car or active
-transport. This is consistent with previous studies that have separately
-demonstrated that public transport users tend to assess more negatively
-subjective factors (explored e.g.~in Stradling et al., 1999; Gatersleben
-and Uzzell, 2007). For example, although car users have higher
-dissonance values than active transport, comparatively this segment has
-much lower percentages of dissonances than public transport, idea also
-supported by research that has shown that car users tend to attribute
-importance to symbolic aspects that positively contribute to their
-perception on driving (Steg et al., 2001; Mokhtarian and Salomon, 2001).
-
-Freedom and happiness tend to have a lower percentage of dissonances in
-the case of active transport, which means that cyclists and individuals
-who mainly walk for their commutes, tend to associate positive
-subjective values while using these modes. This is also consistent with
-other studies that have shown positive affective associations with the
-use of cycling and walking (Anable and Gatersleben, 2005; Gatersleben
-and Uzzell, 2007). The question at the survey has not specify the
-dimensions of freedom, thus has open the door for different
-interpretations as the freedom to choose certain mode or route, freedom
-while using the mode, or the freedom to access to certain places while
-travelling. Journey time: As shown in Figure 3, the analysis carried out
-by journey time also reveals coincidences with previous research in this
-area, since for shorter trips (up to 20 minutes) the analysis shows less
-dissonance between the primary mode and positive subjective associations
-mainly for affective factors. On the contrary, as journey time
-increases, higher is the dissonance. Strangely, the feelings of Security
-and Efficiency have not been statistically representative for the
-Journey Time analysis.
-
-In terms of instrumental factors, interestingly Figure 4 shows that bus
-users have the lowest percentage of dissonance regarding time savings
-(29\%). However, considering the other instrumental factors, bus users
-have a high percentage of dissonance for security and efficiency. In the
-case of security, this means that most bus users (71\%) have considered
-the bus as a mode that they associate to time-savings, although it is
-the mode that has more dissonant evaluations in all other SWB factors.
-This also seems difficult to explain considering the negative evaluation
-that the Transantiago system has consistently had. Some data provided by
-the Survey of Satisfaction with Transantiago Operators (DTPM, 2017) is
-about users' perception of journey time from origin to destination. In
-this question, and after 10 years of implementation of the system, users
-diagnose an average journey of 47 minutes, a value that tends to
-increase with respect to the data delivered by the same survey 5 years
-before (43.5 minutes on average). Worryingly, long trips of more than 30
-minutes have had inconsistent variability over the years, reaching an
-average of more than 37 minutes in 2016. Short trips, however, remain
-roughly equal to previous years, and do not show significant changes in
-the average of 6-7 minutes per trip . This survey has the peculiarity of
-being developed by the Metropolitan Public Transport Board (DTPM), whose
-mission is to articulate the functions of the different modes of public
-transport with a specific interest in buses Transantiago and Metro de
-Santiago.
-
-Another big gap on these instrumental factors relates to the perception
-of security that is especially significant for car users. This means
-that a 75\% of car users have chosen as primary mode the same one as
-they relate to the feeling of security, which is completely opposite to
-other transport modes, specially bus users. Bus users have the highest
-dissonance (98\%), which means that practically all this group of users
-have chosen another mode for referring to the feelings of security. The
-recently referred DTPM survey does not have any particular question that
-addresses the issue of safety -- mostly related in this context as
-security.
-
-\begin{landscape}\begin{table}
-
-\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors}
-\centering
-\begin{tabular}[t]{lcccccccccccc}
-\toprule
-Variable & Freedom & $\chi^2$ p-val & Enjoyment & $\chi^2$ p-val & Happiness & $\chi^2$ p-val & Poverty & $\chi^2$ p-val & Luxury & $\chi^2$ p-val & Status & $\chi^2$ p-val\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Age}}\\
-\hspace{1em}< 35 & 89.88 &  & 94.33 &  & 93.52 &  & 87.63 &  & 89.43 &  & 87.17 & \\
-
-\hspace{1em}35 - 54 & 74.22 &  & 81.45 &  & 82.26 &  & 87.38 &  & 70.18 &  & 68.70 & \\
-
-> 54 & 74.00 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 72.92 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 68.75 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 76.19 & \multirow{-3}{*}{\centering\arraybackslash 0.4095} & 78.57 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 66.67 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Education}}\\
-\hspace{1em}K-12 & 85.98 &  & 92.16 &  & 89.22 &  & 79.27 &  & 95.10 &  & 92.39 & \\
-
-\hspace{1em}Tech/Univ & 83.00 &  & 86.94 &  & 86.94 &  & 88.51 &  & 78.99 &  & 75.00 & \\
-
-Graduate & 78.57 & \multirow{-3}{*}{\centering\arraybackslash 0.9063} & 85.19 & \multirow{-3}{*}{\centering\arraybackslash 0.7005} & 84.62 & \multirow{-3}{*}{\centering\arraybackslash 0.9694} & 86.36 & \multirow{-3}{*}{\centering\arraybackslash 0.3608} & 76.00 & \multirow{-3}{*}{\centering\arraybackslash 0.0058} & 79.17 & \multirow{-3}{*}{\centering\arraybackslash 0.013}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Income}}\\
-\hspace{1em}Low & 86.51 &  & 82.11 &  & 88.62 &  & 80.19 &  & 88.71 &  & 88.70 & \\
-
-\hspace{1em}Middle & 84.52 &  & 89.80 &  & 88.00 &  & 83.76 &  & 85.82 &  & 80.00 & \\
-
-High & 79.19 & \multirow{-3}{*}{\centering\arraybackslash 0.5755} & 90.97 & \multirow{-3}{*}{\centering\arraybackslash 0.2264} & 85.82 & \multirow{-3}{*}{\centering\arraybackslash 0.9698} & 93.69 & \multirow{-3}{*}{\centering\arraybackslash 0.0642} & 73.68 & \multirow{-3}{*}{\centering\arraybackslash 0.0204} & 70.31 & \multirow{-3}{*}{\centering\arraybackslash 0.0137}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Mode}}\\
-\hspace{1em}Auto & 58.93 &  & 78.90 &  & 70.91 &  & 97.96 &  & 41.00 &  & 30.69 & \\
-
-\hspace{1em}Active & 46.34 &  & 60.98 &  & 57.89 &  & 75.76 &  & 89.47 &  & 81.82 & \\
-
-\hspace{1em}Public & 99.23 &  & 96.76 &  & 98.80 &  & 81.35 &  & 100.00 &  & 99.57 & \\
-
-Other & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $< 0.001$} & 86.96 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 93.33 & \multirow{-4}{*}{\centering\arraybackslash 0.0045} & 72.73 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 90.00 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Journey Time}}\\
-\hspace{1em}< 20 min & 65.93 &  & 82.95 &  & 77.27 &  & 86.11 &  & 73.49 &  & 67.09 & \\
-
-\hspace{1em}20 - 40 min & 85.86 &  & 87.50 &  & 89.58 &  & 90.41 &  & 83.87 &  & 81.18 & \\
-
-\hspace{1em}40 - 60 min & 83.04 &  & 89.91 &  & 89.62 &  & 86.08 &  & 82.35 &  & 77.78 & \\
-
-> 60 min & 95.93 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 92.17 & \multirow{-4}{*}{\centering\arraybackslash 0.6115} & 93.28 & \multirow{-4}{*}{\centering\arraybackslash 0.0394} & 83.02 & \multirow{-4}{*}{\centering\arraybackslash 0.9225} & 91.15 & \multirow{-4}{*}{\centering\arraybackslash 0.0925} & 90.09 & \multirow{-4}{*}{\centering\arraybackslash 0.0158}\\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{landscape}
-
-Figure 5 shows the points of origin of the survey for the case of public
-transport users. Metro users as primary mode are shown, bus users are
-shown in cyan. The size of the points represents the number of
-dissonances. The higher the point, the greater the number of SWB factors
-that do not coincide with the primary transport mode. The image shows
-that the intensity or size of the circles is homogeneously distributed
-in the territory, even though the blue circles (metro) tend to show
-slightly less dissonance. The visualisation of this map is more dramatic
-when it is compared to the following Figure 6.
-
-Figure 6 shows the points of origin for the case of private transport
-(cars) and active transport (walking and cycling). Again, the size of
-the circles represents intensity levels of dissonance. The number of
-dissonances is lower than in the case of Figure 5, which indicates that
-users of private and active transport tend to use a mode of transport
-that they relate to one of the positive factors derived from subjective
-wellbeing. In this sense, it could be said that this type of user tends
-to be more advantaged than the public transport user, in a dimension not
-only utilitarian but also emotional and attitudinal.
-
-\hypertarget{which-modes-do-travelers-associate-with-affective-and-instrumental-values}{%
-\subsection{Which modes do travelers associate with affective and
-instrumental
-values?}\label{which-modes-do-travelers-associate-with-affective-and-instrumental-values}}
-
-Here we can visualize the modes that travellers associate with different
-affective and instrumental values. The tool we use for this is a mosaic
-plot. See the mosaic plots in Figure
-\ref{fig:mosaic-plots-by-attribute}.
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-without-instrumental-1.pdf}
-\caption{\label{fig:mosaic-plots-by-attribute}Mosaic plots for three
-affective and three instrumental values; values on the x-axis represent
-proportion of modes selected for each value, and values on the y-axis
-represent proportion of respondents by main mode of transportation}
-\end{figure}
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-Words go here.
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
 \end{document}

### 2019-11-01 Dissonance_Santiago_v1.Rmd
Added discussion based on the files sent by Beatriz, and prepared files for submission

@@
 abstract: |
-  Transportation in most of the world has been dominated for decades by a fascination with the automobile.
-Nonetheless, there is an increasing recognition that to achieve a variety of economic, environmental, and public health policy goals it is important to attract and retain active travelers and users of public transportation.
-A challenge with the way transportation policy is developed, however, is that it tends to focus on utilitarian considerations, which may miss other potential aspects of transportation that users value.
-In particular, subjective wellbeing (SWB) has been proposed as a way to enhance our understanding of the preferences and choices of travellers, as well as a way to evaluate the benefits of transportation beyond utilitarian considerations.
-The objective of this paper is to analyze the modes that people commonly use, and to what extent they are aligned (or not) with a variety of affective values associated with SWB.
-In other words, we are interested in the potential for dissonance with respect to the primary mode of travel, from the perspective of affective values.
+  Subjective wellbeing is a topic that has attracted considerable attention in recent years due to the way it correlates with health.
+From a transportation perspective, there is a burgeoning literature on the way travel can impact subjective wellbeing, and how this, in turn, can influence behavior.
+After decades of fascination with the automobile, subjective wellbeing is increasingly recognized as an alternative approach to assess transportation, and to gain valuable insights to attract and retain active travelers and users of public transportation.
+The objective of this paper is to analyze a number of affective values associated with subjective wellbeing and the modes of transportation that people commonly use.
+In particular, we are interested in the potential for dissonance with respect to the primary mode of travel.
 The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
@@
 1. Introduction
-==========================
+===================
 
@@
 A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing [SWB; see, inter alia, @Devos2013travel; and @Chatterjee2019commuting].
-SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” (**OECD, 2013, p.
-10**).
+SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” [@oecd2013oecd, p.
+10].
 As memorably put by Steg [-@Steg2005car]: is the use of car a must, or is it a lust?
@@
 
+The structure of the paper is as follows.
+After these introductory remarks, we follow up with a background section that reviews the literature.
+Next, we discuss the case study and data used in the research.
+Then, the analysis and results are presented, before concluding with some discussion and directions for future research.
+
 2. Background
-============
+===================
 
@@
 
-3. Data and Methods
+3. Case Study and Data
 ===================
 
-# 3.1 Context
-
-Words to describe Santiago go here.
-
-# 3.2 Sample
+## 3.1 Context
+
+The case study to contextualize the discussion is Santiago de Chile, the capital of one of the countries with the highest levels of inequality in terms of socio-economic distribution in the world.
+These inequities have manifested in a disproportionate expense in transport by the different socioe-conomic sectors, a disproportion in travel times and distances travelled.
+On the other hand, car ownership and use of public transport in the capital are directly conditioned by strong spatial segregation – the higher the income, the higher is the use of the automobile; conversely, and the lower the income, the higher is the predisposition to use public transport.
+Although transport is a reflection of deep inequities in various dimensions, it has triggered an exceptional discomfort and disagreement with the daily travel experience and quality of life.
+
+## 3.2 Sample
 
@@
 
-# 4.1 Who experiences dissonance?
+## 4.1 Who experiences dissonance?
 
@@
       booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
+      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB factors",
       escape = FALSE,
@@
 
-**FOR DISCUSSION**
-
-@Alayyash2019commute
-@Bornioli2019affective
-@Devos2019satisfying
-@Gatersleben2007affective
-@Smith2017commute
-@Ye2017satisfaction
-
 ## 4.2 Which modes do travellers associate with affective values?
@@
 The preceding analysis suggests that there is significant mode dissonance along various dimensions and for various affective values.
-Once we have developed a profile of the travelers who experience mode dissonance, we are interested in what modes they tend to associate with various affective values.
-For this analysis, we employ a visualization technique known as a mosaic plot that is used for exploring categorical data [@Friendly1994mosaic; @Hofmann2000exploring].
-A mosaic plot is a visual representation of a multi-way contingency table, whereby the dimensions of each tile in the mosaic are proportional to the values in the underlying table.
-
-We begin by plotting the cross-tabulation of primary mode of travel to mode associated with each affective value (see Figure \ref{fig:mosaic-plots-by-attribute}).
+This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better in terms of how travellers respond to different affects.
+Less is known about the values that travellers associate with modes _other_ than the one they use.
+For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travellers with respect to the modes they tend to associate with various affective values.
+For this analysis we employ a visualization technique known as a mosaic plot.
+Mosaic plots are used in the exploration of multivariate categorical data [@Friendly1994mosaic; @Hofmann2000exploring], and they provide visual representations of multi-way contingency tables.
+The elements of the mosaic plot are called _tiles_, and the dimensions of each tile are proportional to values of variables in the underlying table.
+
+We begin our analysis by plotting primary mode of travel and the modes associated with each affective value (see Figure \ref{fig:mosaic-plots-by-attribute}).
 The height of tile $j$ in these mosaics corresponds to the proportion of travellers who primarily travel by mode $j$, hence we can see that the most common primary mode of travel in this sample is by public transportation, followed by car, active travel, and other (also see Figure \ref{fig:primary-mode-travel}).
@@
 In terms of Freedom, we see that Car users frequently identify this affect with the use of Car; however, those who do not, very often select Active Travel as the mode that better represents Freedom.
-A majority of active travellers, on the other hand, identify Active Travel as the mode associated with Freedom; few of them attach this value to Car, and even fewer to public transportation and other modes.
+A majority of active travellers, on the other hand, identify Active Travel as the mode that evokes feelings of Freedom; few of them attach this value to Car, and even fewer to public transportation and other modes.
 Travellers whose primary mode of travel is public transportation seldom associate this mode with Freedom, and in fact more frequently relate this affective response to Active Travel followed by Car.
@@
 Three other affective responses show a marked difference.
-Public Transportation was seldom associated by respondents to feelings of Freedom, Enjoyment, and Happiness; on the other hand, it is the mode that is most commonly selected by respondents for evoking feelings of Poverty - even by users of Publi Transportation.
+Public Transportation was seldom associated by respondents to feelings of Freedom, Enjoyment, and Happiness; on the other hand, it is the mode that is most commonly selected by respondents for evoking feelings of Poverty - even by users of Public Transportation.
 Active Travel was the second most common response for its association with Poverty.
@@
 We test the underlying 3-way tables by means of the Cochran-Mantel-Haenszel $\chi^2$ test of independence.
-
->>> Efectivamente lujo y estatus parecen similares a primera vista (Figura 1).
-En general, estos dos valores afectivos son asociados mucho mas comunmente con el automovil.
-Por otro lado, hay algunas diferencias interesantes cuando se les ve desde la perspectiva de diferentes viajeros.
-
->>> Por ejemplo, la tendencia a asociar estatus con el automovil tiende a incrementarse con la edad, con la posible excepcion de los usuarios de transporte publico, para quienes otras opciones (posiblemente taxi), ganan en estatus para los viajeros mayores (>54) a costa de otros modos, incluido el automovil.
-En contraste, el automovil pierde en el valor de lujo con la edad, mientras que otras opciones pasan a ser percibidas como lujo mas comunmente con la edad, incluso para los usuarios de automovil (Figure 2).
-
->>> se vuelven mas comunmente simbolos de estatus que cuando vemos la manera en que viajeros de diferentes edades proyectan lujo y estatus en varios modos, los usuarios de automovil mayores (>54) muestran menos disonancia en status que en lujo, mientras que los viajeros activos presentan mas disonancia en estatus que en lujo, y de hecho proyectan estatus mas comunmente en el automovil.
-
->>> La manera en que el lujo se asocia de manera relativamente mas frecuente con otras opciones que el estatus tambien se observa cuando vemos los diferentes niveles de educacion.
-La excepcion parece ser los usuarios de transporte activo, especialmente  aquellos con educacion superior y de post-grado, que asocian tanto estatus como lujo con el transporte activo mas que los usuarios de otros modos.
 
@@
 
-Words go here to discuss results by age.
+There are some interesting differences when viewed from the perspective of travellers of different ages (see Figure \ref{fig:mosaic-plots-by-age}).
+For example, as seen above, active travel is commonly associated with freedom, happiness, and enjoyment, even by car users, but especially by users of public transportation and other modes.
+However, when we break this down by age, we notice that this tendency weakens as people age, and older travellers increasingly associate these affective values to the car.
+Furthermore, the tendency to associate status with the car tends to increase with age, with the possible exception of public transport users, for whom other options (possibly taxi), gain status for older travellers (> 54) at the expense of other modes, including the car.
+In contrast, the car loses in the value of luxury with age, while other options become more commonly associated with feelings of luxury for older respondents, even for car users (Figure 2).
+Older car users (> 54) show less dissonance in status than in luxury, while active travellers present more dissonance in status than in luxury - and in fact, they more commonly project status in the car.
 
@@
 
-Words go here to discuss results by education.
-
-```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+Only two affective values were significant in the preceding analysis when seen from the perspective of education, namely luxury and status.
+As seen in Figure \ref{fig:mosaic-plots-by-education}, the perceptions of luxury and status are fairly consistent when differentiated by education.
+Most respondents tend to associate luxury and status to the use of car, albeit this association is stronger for status than for luxury.
+The second mode most often mentioned in relation to luxury is "other" likely due to the flexibility and convenience (but cost) of using taxis.
+The exception in this case is the traveller with graduate education who uses active modes.
+This type of respondent, while still more likely to associate luxury and status with the car, more commonly links active travel to these affects than travellers with lower levels of education.
+Most public transport users tend to associate luxury and status to the car, however, they associate active modes with status more than the same group with respect to luxury.
+
+```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, fig.width= 6, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
-Words go here to discuss results by income.
-
-```{r figure-mosaic-plots-by-attribute-and-income, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+Three affective values were significant in the analysis by income; perhaps not surprisingly, all three have an economic dimension.
+Figure \ref{fig:mosaic-plots-by-income} reflects some important social inequalities associated with the way users feel about transportation in Santiago.
+When the affective perception of poverty is analyzed, the image shows that generally public transport is the mode most commonly associated with poverty.
+There are some interesting differences, however, to be observed by income level.
+Whereas middle income users of public transportation associate this mode to poverty most frequently, this is not the case of high income users of public transportation, who tend to link active travel to poverty with greater frequency.
+Similarly, active travel is more often associated with poverty by low income travellers than middle or high income travellers.
+A possible explanation for this is that walking or cycling are related to the idea of a lack of financial means to access other modes of transport.
+For high income car users, on the other hand, public transportation may have connotations of poverty due to its massive use, whereas active travel may be seen more as a lifestyle alternative.
+
+With respect to luxury and status, we see again that these two values coincide more strongly in their association with the car.
+Moreover, we also notice that these perceptions become increasingly frequent at higher levels of income.
+Unlike users of other modes, the high-income public transport user group tends to concentrate a broader association of luxury and status factors with active transport, reinforcing the notion that at higher levels of income, people may see active modes as a lifestyle alternative.
+High income active travellers, although still more likely to associate luxury and status to the car, are more likely than users of other modes to associate these affects to active travel, perhaps due to an awareness of the benefits of walking and using the bicycle.
+Furthermore, high-income users of cars are more likely to experience consonance with respect to status and luxury, in what might be a form of self-congratulatory confirmation of success.
+
+```{r figure-mosaic-plots-by-attribute-and-income, echo=FALSE, cache = TRUE, fig.width= 7, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
-Words go here to discuss results by time.
+The last dimension that we examine is typical commute time.
+Four affective values were significant along this dimension in Table \ref{tab:cross-tabulation-results}.
+Figure \ref{fig:mosaic-plots-by-travel-time} shows the way travellers associate different affective values to modes of transportation by length of typical commute.
+The first couple of factors, freedom and enjoyment, are associated with eudaimonic and hedonic factors of wellbeing, as discussed earlier in the paper.
+On the other hand, the luxury and status are defined mainly by a socio-economic component.
+As seen in the figure, freedom and enjoyment are most frequently mentioned in relation to active travel, followed by car.
+However, active travel is more frequently associated with freedom and enjoyment by people who typically undertake relatively short trips (<20 min) or travellers whose typical trips are longer (>60 min).
+In this respect, active travel may be seen as an ideal mode for trips, and as an enviable mode by people whose trips are longer.
+
+In the case of luxury and status factors, both follow a similar pattern, despite variations in travel times.
+Despite the travel time exceeding 60 minutes, car users consider that their transport mode is mostly associated with luxury and status.
+The users of active transport in the sample tend to travel less than 20 minutes, and this is the same segment that considers that the status and luxury factors correspond mainly to the car and then to active transport.
+Looking at the four factors set out in Figure \ref{fig:mosaic-plots-by-travel-time}, it could be understood that the modes that are associated with intrinsically positive characteristics such as freedom and enjoyment tend to use public transport.
+On the contrary, factors such as luxury and status tend to have a negative connotation, where the association with the car and other modes of transport (such as the individual taxi and the collective taxi) tends to dominate.
 
@@
 
-***FOR DISCUSSION***
-
-@Devos2018people
-
 5. Conclusions
@@
 
-Accordingly, the aim of this paper is to analyse some of the factors that can potentially affect the levels of SWB in the wide spectrum of public, private and active transport modes in the context of Santiago de Chile.
-Previous research suggests that public transport users experience a negative gap in desired and actual travel time, whereas active travellers don’t seem to mind somewhat longer trips than what strictly needed (e.g., Páez and Whalen, 2010).
-In the context of a Latin American country, historically the poor travel experience of public transit users and active travellers reflects the social inequalities of social groups that have no alternative but to move in these types of modes while living far from the work centres and main activities.
-The paper aims to reflect on the possibilities of increasing the SWB while travelling, and how this could increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
-This can help not only to reduce the use of private transport but also decrease the inequality gap between these users.
-
-The paper explores how positive affective and instrumental/utilitarian factors of SWB correspond to the use of the primary mode of transportation.
-It uses an analysis of correspondence that considers the actual primary mode versus the mode that individuals associated to both utilitarian (designed to be useful or practical rather than attractive) and affective (expressing a person's feelings) SWB factors.
-For example, it will be analysed if a person who uses public transport as the primary mode, tends to associate these modes with positive affective factors (as freedom, enjoyment or happiness) or positive utilitarian factors (as security, time-savings or efficiency).
-We hypothesize that there is a more persistent non-correspondence or mismatch within the more disadvantage groups or within the users of public transport.
+Subjective wellbeing is a topic that has attracted considerable attention in recent years due to its relationship with health.
+In the field of transportation, there is a large and growing body of literature that documents the way transportation can impact subjective wellbeing.
+Likewise, there is strong evidence that subjective wellbeing can influence travel behavior.
+As the world tries to move from a culture dominated by a century-long love affair with the automobile, there is a pressing need to understand how travellers perceive different modes of transportation from the lens of subjective wellbeing.
+Insights in this regard could prove valuable to develop and implement plans and policies to attract and retain users to healthier, more environmentally friendly transportation options, in particular active travel and public transportation.
+For this reason, understanding mode dissonance, the extent to which the context of travellers differs from their aspirations, is a worthwhile topic for research.
+
+The premise of the research presented in this paper is that subjective wellbeing is a composite construct of various affective values.
+In this paper we investigated mode dissonance from the perspective of six affective values associated with subjective wellbeing, namely freedom, enjoyment, happiness, poverty, luxury, and status.
+The research presented here was based on a sample of travellers in Santiago, the capital of Chile.
+Participants in this research were asked about their typical mode of travel, and then about the mode or modes that they associate with each of the six affective values.
+Analysis using hypothesis testing (tests of independence) and vizualization techniques (mosaic plots) uncovered interesting patterns.
+Some of our findings are well aligned with previous research; for example, active travellers experience less dissonance than car users, and users of public transportation experience the most dissonance of all.
+However, by considering affective values separately instead of aggregating them into a single indicator of subjective wellbeing, we manage to preserve some granularity with respect to various responses.
+This turns out to be important, because hedonic/eudaimonic values are more frequently related to active travel (freedom, enjoyment, happiness), whereas poverty is more frequently related to public transportation and active travel.
+Luxury and status, on the other hand, are more frequently associated to luxury and status.
+
+Further delving into the question of which modes are associated with these affective values, we find that there are important differences in terms of the typical mode of travel.
+Active travellers experience dissonance with relatively little frequently with respect to freedom, enjoyment, and happiness, but when they do, they tend to attach positive values to the car.
+Car users experience dissonance with respect to these affects more frequently than active travellers, and when they do, they strongly relate possitive hedonic/eudaimonic values to active travel.
+In other words, it is possible that drivers dream of walking when it comes to feelings especially of enjoyment and happiness.
+The other side of the coin is also interesting.
+When it comes to affective values with a stronger socio-economic flavor, such as poverty, luxury, and status, car users tend to experience dissonance less frequently than users of other modes.
+Active travellers, altough more resistant to the lure of the car compared to users of public transportation, also tend to attach values of luxury and status to the car when they experience dissonance.
+
+An examination of these effects by age, level of education, level of income, and typical trip duration reveals that some of the responses become more pronounced.
+For instance, older people are less likely than younger people to associate active travel with positive hedonic/eudaimonic affects, and are more likely to attach these values to the car.
+People with higher incomes are more atuned to the luxury and status values of cars, whereas lower income people are more likely to relate active travel to luxury and status.
+
+Our results not only help to flesh out some ways in which mode dissonance could play out from the perspective of different affects, but also does so in the context of a Latin American country, a region where historically there are deep-seated tabooes with respect to different modes of transportation: the poor travel by public transportation and/or are forced active travellers; where the rich enjoy the luxury of private vehicles and/or are active travellers by choice.
+In this way, the paper helps us to reflect on the ways the public experiences transportation-related subjective wellbeing, and how this in turn could be used to increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
+
+With respect to opportunities for future research, a possible avenue for extending the findings reported in this paper relates to the use of the modes other than the typical mode of transportation.
+In a recent paper that investigaed commute satisfaction for car users, Al-Ayyash and Abou-Zeid [-@Alayyash2019commute] considered three models: for current trip satisfaction, remembered satisfaction while using public transport, and current satisfaction using public transport.
+The findings suggest that low service quality in public transportation can result in a generalised negative perception, and that this perception is more difficult to smooth if commuters do not regularly use public transport.
+Another avenue for future research could be to consider the mix of modes typically used.
+While in this paper the analysis focused on the primary mode of transportation, many travellers experience more than one mode of transportation in their daily activities.
+For this reason, considering the multimodal component of travel would be interesting; for example, future research could consider people who eventually arrive by bicycle to the metro station or people that, after using a colectivo for part of a trip, end their journey by bus.
 

### 2019-11-01 Dissonance_Santiago_v1.tex
Added discussion based on the files sent by Beatriz, and prepared files for submission

@@
   \begin{abstract}
-  Transportation in most of the world has been dominated for decades by a
-  fascination with the automobile. Nonetheless, there is an increasing
-  recognition that to achieve a variety of economic, environmental, and
-  public health policy goals it is important to attract and retain active
-  travelers and users of public transportation. A challenge with the way
-  transportation policy is developed, however, is that it tends to focus
-  on utilitarian considerations, which may miss other potential aspects of
-  transportation that users value. In particular, subjective wellbeing
-  (SWB) has been proposed as a way to enhance our understanding of the
-  preferences and choices of travellers, as well as a way to evaluate the
-  benefits of transportation beyond utilitarian considerations. The
-  objective of this paper is to analyze the modes that people commonly
-  use, and to what extent they are aligned (or not) with a variety of
-  affective values associated with SWB. In other words, we are interested
-  in the potential for dissonance with respect to the primary mode of
-  travel, from the perspective of affective values. The study is based on
-  data collected from a sample of travellers in the city of Santiago, in
-  Chile. Participants in the study were asked about their usual mode of
-  travel, and then were asked to name the mode or modes that they
-  associate with the affective values of freedom, enjoyment, happiness,
-  poverty, luxury and status. The results indicate that users of public
-  transportation experience the most dissonance in terms of affective
-  values, and active travellers the least. For those travellers who
-  experience dissonance, active travel is the mode most commonly
+  Subjective wellbeing is a topic that has attracted considerable
+  attention in recent years due to the way it correlates with health. From
+  a transportation perspective, there is a burgeoning literature on the
+  way travel can impact subjective wellbeing, and how this, in turn, can
+  influence behavior. After decades of fascination with the automobile,
+  subjective wellbeing is increasingly recognized as an alternative
+  approach to assess transportation, and to gain valuable insights to
+  attract and retain active travelers and users of public transportation.
+  The objective of this paper is to analyze a number of affective values
+  associated with subjective wellbeing and the modes of transportation
+  that people commonly use. In particular, we are interested in the
+  potential for dissonance with respect to the primary mode of travel. The
+  study is based on data collected from a sample of travellers in the city
+  of Santiago, in Chile. Participants in the study were asked about their
+  usual mode of travel, and then were asked to name the mode or modes that
+  they associate with the affective values of freedom, enjoyment,
+  happiness, poverty, luxury and status. The results indicate that users
+  of public transportation experience the most dissonance in terms of
+  affective values, and active travellers the least. For those travellers
+  who experience dissonance, active travel is the mode most commonly
   associated with freedom, enjoyment, and happiness, public transportation
@@
 their lives, and the affective reactions of people to their
-experiences'' (\textbf{OECD, 2013, p.~10}). As memorably put by Steg
-(2005): is the use of car a must, or is it a lust? A close alignment, or
+experiences'' (OECD, 2013, p. 10). As memorably put by Steg (2005): is
+the use of car a must, or is it a lust? A close alignment, or
 consonance, between affective values and the mode of transportation used
@@
   Redman et al., 2013).
-\item ~
+\end{enumerate}
+
+The structure of the paper is as follows. After these introductory
+remarks, we follow up with a background section that reviews the
+literature. Next, we discuss the case study and data used in the
+research. Then, the analysis and results are presented, before
+concluding with some discussion and directions for future research.
+
 \hypertarget{background}{%
-  \section{Background}\label{background}}
-\end{enumerate}
+\section{2. Background}\label{background}}
 
@@
 
-\hypertarget{data-and-methods}{%
-\section{3. Data and Methods}\label{data-and-methods}}
+\hypertarget{case-study-and-data}{%
+\section{3. Case Study and Data}\label{case-study-and-data}}
 
 \hypertarget{context}{%
-\section{3.1 Context}\label{context}}
-
-Words to describe Santiago go here.
+\subsection{3.1 Context}\label{context}}
+
+The case study to contextualize the discussion is Santiago de Chile, the
+capital of one of the countries with the highest levels of inequality in
+terms of socio-economic distribution in the world. These inequities have
+manifested in a disproportionate expense in transport by the different
+socioe-conomic sectors, a disproportion in travel times and distances
+travelled. On the other hand, car ownership and use of public transport
+in the capital are directly conditioned by strong spatial segregation --
+the higher the income, the higher is the use of the automobile;
+conversely, and the lower the income, the higher is the predisposition
+to use public transport. Although transport is a reflection of deep
+inequities in various dimensions, it has triggered an exceptional
+discomfort and disagreement with the daily travel experience and quality
+of life.
 
 \hypertarget{sample}{%
-\section{3.2 Sample}\label{sample}}
+\subsection{3.2 Sample}\label{sample}}
 
@@
 \hypertarget{who-experiences-dissonance}{%
-\section{4.1 Who experiences
+\subsection{4.1 Who experiences
 dissonance?}\label{who-experiences-dissonance}}
@@
 
-\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors}
+\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB factors}
 \centering
@@
 
-\textbf{FOR DISCUSSION}
-
-Al-Ayyash and Abou-Zeid (2019) Bornioli et al. (2019) De Vos et al.
-(2019) Gatersleben and Uzzell (2007) Smith (2017) Ye and Titheridge
-(2017)
-
 \hypertarget{which-modes-do-travellers-associate-with-affective-values}{%
@@
 dissonance along various dimensions and for various affective values.
-Once we have developed a profile of the travelers who experience mode
-dissonance, we are interested in what modes they tend to associate with
-various affective values. For this analysis, we employ a visualization
-technique known as a mosaic plot that is used for exploring categorical
-data (Friendly, 1994; Hofmann, 2000). A mosaic plot is a visual
-representation of a multi-way contingency table, whereby the dimensions
-of each tile in the mosaic are proportional to the values in the
-underlying table.
-
-We begin by plotting the cross-tabulation of primary mode of travel to
-mode associated with each affective value (see Figure
+This is for the most part in line with previous research, although by
+examining different affective values individually instead of a summary
+measure of wellbeing, we are able to differentiate better in terms of
+how travellers respond to different affects. Less is known about the
+values that travellers associate with modes \emph{other} than the one
+they use. For this reason, after developing a profile of the travelers
+who experience mode dissonance in the preceding section, we are now
+interested in the responses of travellers with respect to the modes they
+tend to associate with various affective values. For this analysis we
+employ a visualization technique known as a mosaic plot. Mosaic plots
+are used in the exploration of multivariate categorical data (Friendly,
+1994; Hofmann, 2000), and they provide visual representations of
+multi-way contingency tables. The elements of the mosaic plot are called
+\emph{tiles}, and the dimensions of each tile are proportional to values
+of variables in the underlying table.
+
+We begin our analysis by plotting primary mode of travel and the modes
+associated with each affective value (see Figure
 \ref{fig:mosaic-plots-by-attribute}). The height of tile \(j\) in these
@@
 active travellers, on the other hand, identify Active Travel as the mode
-associated with Freedom; few of them attach this value to Car, and even
-fewer to public transportation and other modes. Travellers whose primary
-mode of travel is public transportation seldom associate this mode with
-Freedom, and in fact more frequently relate this affective response to
-Active Travel followed by Car. Users of other modes seem to be split
-almost equally in their attribution of Freedom, between Active Travel,
-Car, and Other. In general, Active Travel is the mode most often
-identified as embodying Freedom, with the exception of Car travellers.
+that evokes feelings of Freedom; few of them attach this value to Car,
+and even fewer to public transportation and other modes. Travellers
+whose primary mode of travel is public transportation seldom associate
+this mode with Freedom, and in fact more frequently relate this
+affective response to Active Travel followed by Car. Users of other
+modes seem to be split almost equally in their attribution of Freedom,
+between Active Travel, Car, and Other. In general, Active Travel is the
+mode most often identified as embodying Freedom, with the exception of
+Car travellers.
 
@@
 that is most commonly selected by respondents for evoking feelings of
-Poverty - even by users of Publi Transportation. Active Travel was the
+Poverty - even by users of Public Transportation. Active Travel was the
 second most common response for its association with Poverty. Likewise,
@@
 by means of the Cochran-Mantel-Haenszel \(\chi^2\) test of independence.
-
-\begin{quote}
-\begin{quote}
-\begin{quote}
-Efectivamente lujo y estatus parecen similares a primera vista (Figura
-1). En general, estos dos valores afectivos son asociados mucho mas
-comunmente con el automovil. Por otro lado, hay algunas diferencias
-interesantes cuando se les ve desde la perspectiva de diferentes
-viajeros.
-\end{quote}
-\end{quote}
-\end{quote}
-
-\begin{quote}
-\begin{quote}
-\begin{quote}
-Por ejemplo, la tendencia a asociar estatus con el automovil tiende a
-incrementarse con la edad, con la posible excepcion de los usuarios de
-transporte publico, para quienes otras opciones (posiblemente taxi),
-ganan en estatus para los viajeros mayores (\textgreater54) a costa de
-otros modos, incluido el automovil. En contraste, el automovil pierde en
-el valor de lujo con la edad, mientras que otras opciones pasan a ser
-percibidas como lujo mas comunmente con la edad, incluso para los
-usuarios de automovil (Figure 2).
-\end{quote}
-\end{quote}
-\end{quote}
-
-\begin{quote}
-\begin{quote}
-\begin{quote}
-se vuelven mas comunmente simbolos de estatus que cuando vemos la manera
-en que viajeros de diferentes edades proyectan lujo y estatus en varios
-modos, los usuarios de automovil mayores (\textgreater54) muestran menos
-disonancia en status que en lujo, mientras que los viajeros activos
-presentan mas disonancia en estatus que en lujo, y de hecho proyectan
-estatus mas comunmente en el automovil.
-\end{quote}
-\end{quote}
-\end{quote}
-
-\begin{quote}
-\begin{quote}
-\begin{quote}
-La manera en que el lujo se asocia de manera relativamente mas frecuente
-con otras opciones que el estatus tambien se observa cuando vemos los
-diferentes niveles de educacion. La excepcion parece ser los usuarios de
-transporte activo, especialmente aquellos con educacion superior y de
-post-grado, que asocian tanto estatus como lujo con el transporte activo
-mas que los usuarios de otros modos.
-\end{quote}
-\end{quote}
-\end{quote}
 
@@
 
-Words go here to discuss results by age.
+There are some interesting differences when viewed from the perspective
+of travellers of different ages (see Figure
+\ref{fig:mosaic-plots-by-age}). For example, as seen above, active
+travel is commonly associated with freedom, happiness, and enjoyment,
+even by car users, but especially by users of public transportation and
+other modes. However, when we break this down by age, we notice that
+this tendency weakens as people age, and older travellers increasingly
+associate these affective values to the car. Furthermore, the tendency
+to associate status with the car tends to increase with age, with the
+possible exception of public transport users, for whom other options
+(possibly taxi), gain status for older travellers (\textgreater{} 54) at
+the expense of other modes, including the car. In contrast, the car
+loses in the value of luxury with age, while other options become more
+commonly associated with feelings of luxury for older respondents, even
+for car users (Figure 2). Older car users (\textgreater{} 54) show less
+dissonance in status than in luxury, while active travellers present
+more dissonance in status than in luxury - and in fact, they more
+commonly project status in the car.
 
@@
 
-Words go here to discuss results by education.
+Only two affective values were significant in the preceding analysis
+when seen from the perspective of education, namely luxury and status.
+As seen in Figure \ref{fig:mosaic-plots-by-education}, the perceptions
+of luxury and status are fairly consistent when differentiated by
+education. Most respondents tend to associate luxury and status to the
+use of car, albeit this association is stronger for status than for
+luxury. The second mode most often mentioned in relation to luxury is
+``other'' likely due to the flexibility and convenience (but cost) of
+using taxis. The exception in this case is the traveller with graduate
+education who uses active modes. This type of respondent, while still
+more likely to associate luxury and status with the car, more commonly
+links active travel to these affects than travellers with lower levels
+of education. Most public transport users tend to associate luxury and
+status to the car, however, they associate active modes with status more
+than the same group with respect to luxury.
 
@@
 
-Words go here to discuss results by income.
+Three affective values were significant in the analysis by income;
+perhaps not surprisingly, all three have an economic dimension. Figure
+\ref{fig:mosaic-plots-by-income} reflects some important social
+inequalities associated with the way users feel about transportation in
+Santiago. When the affective perception of poverty is analyzed, the
+image shows that generally public transport is the mode most commonly
+associated with poverty. There are some interesting differences,
+however, to be observed by income level. Whereas middle income users of
+public transportation associate this mode to poverty most frequently,
+this is not the case of high income users of public transportation, who
+tend to link active travel to poverty with greater frequency. Similarly,
+active travel is more often associated with poverty by low income
+travellers than middle or high income travellers. A possible explanation
+for this is that walking or cycling are related to the idea of a lack of
+financial means to access other modes of transport. For high income car
+users, on the other hand, public transportation may have connotations of
+poverty due to its massive use, whereas active travel may be seen more
+as a lifestyle alternative.
+
+With respect to luxury and status, we see again that these two values
+coincide more strongly in their association with the car. Moreover, we
+also notice that these perceptions become increasingly frequent at
+higher levels of income. Unlike users of other modes, the high-income
+public transport user group tends to concentrate a broader association
+of luxury and status factors with active transport, reinforcing the
+notion that at higher levels of income, people may see active modes as a
+lifestyle alternative. High income active travellers, although still
+more likely to associate luxury and status to the car, are more likely
+than users of other modes to associate these affects to active travel,
+perhaps due to an awareness of the benefits of walking and using the
+bicycle. Furthermore, high-income users of cars are more likely to
+experience consonance with respect to status and luxury, in what might
+be a form of self-congratulatory confirmation of success.
 
@@
 
-Words go here to discuss results by time.
+The last dimension that we examine is typical commute time. Four
+affective values were significant along this dimension in Table
+\ref{tab:cross-tabulation-results}. Figure
+\ref{fig:mosaic-plots-by-travel-time} shows the way travellers associate
+different affective values to modes of transportation by length of
+typical commute. The first couple of factors, freedom and enjoyment, are
+associated with eudaimonic and hedonic factors of wellbeing, as
+discussed earlier in the paper. On the other hand, the luxury and status
+are defined mainly by a socio-economic component. As seen in the figure,
+freedom and enjoyment are most frequently mentioned in relation to
+active travel, followed by car. However, active travel is more
+frequently associated with freedom and enjoyment by people who typically
+undertake relatively short trips (\textless20 min) or travellers whose
+typical trips are longer (\textgreater60 min). In this respect, active
+travel may be seen as an ideal mode for trips, and as an enviable mode
+by people whose trips are longer.
+
+In the case of luxury and status factors, both follow a similar pattern,
+despite variations in travel times. Despite the travel time exceeding 60
+minutes, car users consider that their transport mode is mostly
+associated with luxury and status. The users of active transport in the
+sample tend to travel less than 20 minutes, and this is the same segment
+that considers that the status and luxury factors correspond mainly to
+the car and then to active transport. Looking at the four factors set
+out in Figure \ref{fig:mosaic-plots-by-travel-time}, it could be
+understood that the modes that are associated with intrinsically
+positive characteristics such as freedom and enjoyment tend to use
+public transport. On the contrary, factors such as luxury and status
+tend to have a negative connotation, where the association with the car
+and other modes of transport (such as the individual taxi and the
+collective taxi) tends to dominate.
 
@@
 
-\textbf{\emph{FOR DISCUSSION}}
-
-De Vos (2018)
-
 \hypertarget{conclusions}{%
@@
 
-Accordingly, the aim of this paper is to analyse some of the factors
-that can potentially affect the levels of SWB in the wide spectrum of
-public, private and active transport modes in the context of Santiago de
-Chile. Previous research suggests that public transport users experience
-a negative gap in desired and actual travel time, whereas active
-travellers don't seem to mind somewhat longer trips than what strictly
-needed (e.g., Páez and Whalen, 2010). In the context of a Latin American
-country, historically the poor travel experience of public transit users
-and active travellers reflects the social inequalities of social groups
-that have no alternative but to move in these types of modes while
-living far from the work centres and main activities. The paper aims to
-reflect on the possibilities of increasing the SWB while travelling, and
-how this could increase the attractiveness of public transport and
-active travel in the socio-demographic groups studied. This can help not
-only to reduce the use of private transport but also decrease the
-inequality gap between these users.
-
-The paper explores how positive affective and instrumental/utilitarian
-factors of SWB correspond to the use of the primary mode of
-transportation. It uses an analysis of correspondence that considers the
-actual primary mode versus the mode that individuals associated to both
-utilitarian (designed to be useful or practical rather than attractive)
-and affective (expressing a person's feelings) SWB factors. For example,
-it will be analysed if a person who uses public transport as the primary
-mode, tends to associate these modes with positive affective factors (as
-freedom, enjoyment or happiness) or positive utilitarian factors (as
-security, time-savings or efficiency). We hypothesize that there is a
-more persistent non-correspondence or mismatch within the more
-disadvantage groups or within the users of public transport.
+Subjective wellbeing is a topic that has attracted considerable
+attention in recent years due to its relationship with health. In the
+field of transportation, there is a large and growing body of literature
+that documents the way transportation can impact subjective wellbeing.
+Likewise, there is strong evidence that subjective wellbeing can
+influence travel behavior. As the world tries to move from a culture
+dominated by a century-long love affair with the automobile, there is a
+pressing need to understand how travellers perceive different modes of
+transportation from the lens of subjective wellbeing. Insights in this
+regard could prove valuable to develop and implement plans and policies
+to attract and retain users to healthier, more environmentally friendly
+transportation options, in particular active travel and public
+transportation. For this reason, understanding mode dissonance, the
+extent to which the context of travellers differs from their
+aspirations, is a worthwhile topic for research.
+
+The premise of the research presented in this paper is that subjective
+wellbeing is a composite construct of various affective values. In this
+paper we investigated mode dissonance from the perspective of six
+affective values associated with subjective wellbeing, namely freedom,
+enjoyment, happiness, poverty, luxury, and status. The research
+presented here was based on a sample of travellers in Santiago, the
+capital of Chile. Participants in this research were asked about their
+typical mode of travel, and then about the mode or modes that they
+associate with each of the six affective values. Analysis using
+hypothesis testing (tests of independence) and vizualization techniques
+(mosaic plots) uncovered interesting patterns. Some of our findings are
+well aligned with previous research; for example, active travellers
+experience less dissonance than car users, and users of public
+transportation experience the most dissonance of all. However, by
+considering affective values separately instead of aggregating them into
+a single indicator of subjective wellbeing, we manage to preserve some
+granularity with respect to various responses. This turns out to be
+important, because hedonic/eudaimonic values are more frequently related
+to active travel (freedom, enjoyment, happiness), whereas poverty is
+more frequently related to public transportation and active travel.
+Luxury and status, on the other hand, are more frequently associated to
+luxury and status.
+
+Further delving into the question of which modes are associated with
+these affective values, we find that there are important differences in
+terms of the typical mode of travel. Active travellers experience
+dissonance with relatively little frequently with respect to freedom,
+enjoyment, and happiness, but when they do, they tend to attach positive
+values to the car. Car users experience dissonance with respect to these
+affects more frequently than active travellers, and when they do, they
+strongly relate possitive hedonic/eudaimonic values to active travel. In
+other words, it is possible that drivers dream of walking when it comes
+to feelings especially of enjoyment and happiness. The other side of the
+coin is also interesting. When it comes to affective values with a
+stronger socio-economic flavor, such as poverty, luxury, and status, car
+users tend to experience dissonance less frequently than users of other
+modes. Active travellers, altough more resistant to the lure of the car
+compared to users of public transportation, also tend to attach values
+of luxury and status to the car when they experience dissonance.
+
+An examination of these effects by age, level of education, level of
+income, and typical trip duration reveals that some of the responses
+become more pronounced. For instance, older people are less likely than
+younger people to associate active travel with positive
+hedonic/eudaimonic affects, and are more likely to attach these values
+to the car. People with higher incomes are more atuned to the luxury and
+status values of cars, whereas lower income people are more likely to
+relate active travel to luxury and status.
+
+Our results not only help to flesh out some ways in which mode
+dissonance could play out from the perspective of different affects, but
+also does so in the context of a Latin American country, a region where
+historically there are deep-seated tabooes with respect to different
+modes of transportation: the poor travel by public transportation and/or
+are forced active travellers; where the rich enjoy the luxury of private
+vehicles and/or are active travellers by choice. In this way, the paper
+helps us to reflect on the ways the public experiences
+transportation-related subjective wellbeing, and how this in turn could
+be used to increase the attractiveness of public transport and active
+travel in the socio-demographic groups studied.
+
+With respect to opportunities for future research, a possible avenue for
+extending the findings reported in this paper relates to the use of the
+modes other than the typical mode of transportation. In a recent paper
+that investigaed commute satisfaction for car users, Al-Ayyash and
+Abou-Zeid (2019) considered three models: for current trip satisfaction,
+remembered satisfaction while using public transport, and current
+satisfaction using public transport. The findings suggest that low
+service quality in public transportation can result in a generalised
+negative perception, and that this perception is more difficult to
+smooth if commuters do not regularly use public transport. Another
+avenue for future research could be to consider the mix of modes
+typically used. While in this paper the analysis focused on the primary
+mode of transportation, many travellers experience more than one mode of
+transportation in their daily activities. For this reason, considering
+the multimodal component of travel would be interesting; for example,
+future research could consider people who eventually arrive by bicycle
+to the metro station or people that, after using a colectivo for part of
+a trip, end their journey by bus.
 
@@
 
+\leavevmode\hypertarget{ref-oecd2013oecd}{}%
+OECD, 2013. OECD guidelines on measuring subjective well-being. OECD
+Publishing.
+
 \leavevmode\hypertarget{ref-Paez2010enjoyment}{}%

### 2019-11-05 Dissonance_Santiago_Title_Page_v1.Rmd
Format changes requested by editorial team of Journal of Transportation and Health on initial submission

@@
 abstract: |
+   **Introduction**  
    Subjective wellbeing is a topic that has attracted considerable attention in recent years due to the way it correlates with health.
 From a transportation perspective, there is a burgeoning literature on the way travel can impact subjective wellbeing, and how this, in turn, can influence behavior.
-After decades of fascination with the automobile, subjective wellbeing is increasingly recognized as an alternative approach to assess transportation, and to gain valuable insights to attract and retain active travelers and users of public transportation.
+   **Objective**  
    The objective of this paper is to analyze a number of affective values associated with subjective wellbeing and the modes of transportation that people commonly use.
 In particular, we are interested in the potential for dissonance with respect to the primary mode of travel.
+   **Materials and Methods**  
    The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
 Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associate with the affective values of freedom, enjoyment, happiness, poverty, luxury and status.
+Analysis is based on tests of independence and visualization via mosaic plots.
+   **Results**  
    The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
@@
 
-journal: "An Elsevier journal"
+journal: "Journal of Transportation & Health"
 date: "`r Sys.Date()`"
 bibliography: mybibfile.bib
-#linenumbers: true
-#numbersections: true
+linenumbers: true
+numbersections: true
 csl: elsevier-harvard.csl

### 2019-11-05 Dissonance_Santiago_Title_Page_v1.tex
Format changes requested by editorial team of Journal of Transportation and Health on initial submission

@@
 
-  \journal{An Elsevier journal} % Sets Journal name
+  \journal{Journal of Transportation \& Health} % Sets Journal name
 
 \usepackage{lineno} % add
+  \linenumbers % turns line numbering on
 \providecommand{\tightlist}{%
@@
 
-\setcounter{secnumdepth}{0}
+\setcounter{secnumdepth}{5}
 % Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{0}
 % Pandoc header
@@
   \begin{abstract}
-  Transportation in most of the world has been dominated for decades by a
-  fascination with the automobile. Nonetheless, there is an increasing
-  recognition that to achieve a variety of economic, environmental, and
-  public health policy goals it is important to attract and retain active
-  travelers and users of public transportation. A challenge with the way
-  transportation policy is developed, however, is that it tends to focus
-  on utilitarian considerations, which may miss other potential aspects of
-  transportation that users value. In particular, subjective wellbeing
-  (SWB) has been proposed as a way to enhance our understanding of the
-  preferences and choices of travellers, as well as a way to evaluate the
-  benefits of transportation beyond utilitarian considerations. The
-  objective of this paper is to analyze the modes that people commonly
-  use, and to what extent they are aligned (or not) with a variety of
-  affective values associated with SWB. In other words, we are interested
-  in the potential for dissonance with respect to the primary mode of
-  travel, from the perspective of affective values. The study is based on
-  data collected from a sample of travellers in the city of Santiago, in
-  Chile. Participants in the study were asked about their usual mode of
-  travel, and then were asked to name the mode or modes that they
-  associate with the affective values of freedom, enjoyment, happiness,
-  poverty, luxury and status. The results indicate that users of public
-  transportation experience the most dissonance in terms of affective
-  values, and active travellers the least. For those travellers who
-  experience dissonance, active travel is the mode most commonly
-  associated with freedom, enjoyment, and happiness, public transportation
-  is most commonly associated with poverty, and the automobil is most
-  commonly associated with luxury and status.
+  \textbf{Introduction}\\
+  Subjective wellbeing is a topic that has attracted considerable
+  attention in recent years due to the way it correlates with health. From
+  a transportation perspective, there is a burgeoning literature on the
+  way travel can impact subjective wellbeing, and how this, in turn, can
+  influence behavior.\\
+  \textbf{Objective}\\
+  The objective of this paper is to analyze a number of affective values
+  associated with subjective wellbeing and the modes of transportation
+  that people commonly use. In particular, we are interested in the
+  potential for dissonance with respect to the primary mode of travel.\\
+  \textbf{Materials and Methods}\\
+  The study is based on data collected from a sample of travellers in the
+  city of Santiago, in Chile. Participants in the study were asked about
+  their usual mode of travel, and then were asked to name the mode or
+  modes that they associate with the affective values of freedom,
+  enjoyment, happiness, poverty, luxury and status. Analysis is based on
+  tests of independence and visualization via mosaic plots.\\
+  \textbf{Results}\\
+  The results indicate that users of public transportation experience the
+  most dissonance in terms of affective values, and active travellers the
+  least. For those travellers who experience dissonance, active travel is
+  the mode most commonly associated with freedom, enjoyment, and
+  happiness, public transportation is most commonly associated with
+  poverty, and the automobil is most commonly associated with luxury and
+  status.
   \end{abstract}

### 2019-11-05 Dissonance_Santiago_v1.Rmd
Format changes requested by editorial team of Journal of Transportation and Health on initial submission

@@
 
-1. Introduction
+Introduction
 ===================
@@
 
-2. Background
+Background
 ===================
@@
 
-3. Case Study and Data
+Case Study and Data
 ===================
 
-## 3.1 Context
+## Context
 
@@
 
-## 3.2 Sample
+## Sample
 
@@
 
-4. Analysis and Results
+Analysis and Results
 ==========
@@
 
-## 4.1 Who experiences dissonance?
+## Who experiences dissonance?
 
 To investigate the first question in our analysis, we create contingency tables that tabulate the frequency of dissonance with respect to each affective value, stratified by the attributes of Age, Education, Income, Primary Mode of Travel, and typical Commute Time.
-Table \ref{tab:cross-tabulation-results-without-instrumental} presents the frequency (in percentage) of dissonance, in other words, the percentage of respondents out of the total in their stratum who indicated mode or mode(s) for the affective value that do not correspond to their primary mode of travel.
+Table \ref{tab:cross-tabulation-results} presents the frequency (in percentage) of dissonance, in other words, the percentage of respondents out of the total in their stratum who indicated mode or mode(s) for the affective value that do not correspond to their primary mode of travel.
 
@@
 
-### 4.1.1 Age
+### Age
 
@@
 
-### 4.1.2 Education
+### Education
 
@@
 
-### 4.1.3 Income
+### Income
 
@@
 
-### 4.1.4 Primary mode of travel
+### Primary mode of travel
 
 The variable that shows the largest differences in the frequency of dissonance is the primary mode of travel.
-It can be seen in Table \ref{tab:cross-tabulation-results-without-instrumental} that the differences are significative for all six affective values.
+It can be seen in Table \ref{tab:cross-tabulation-results} that the differences are significative for all six affective values.
 Dissonance is particularly accute for users of public transportation when it comes to the values of Freedom, Enjoyment, and Happiness: almost 100% of users of public transportation have identified other mode or modes as better representing those values.
@@
 
-### 4.1.5 Typical commute time
+### Typical commute time
 
@@
 
-## 4.2 Which modes do travellers associate with affective values?
+## Which modes do travellers associate with affective values?
 
@@
 
-### 4.2.1 Age
+### Age
 
@@
 
-### 4.2.2 Education
+### Education
 
@@
 
-### 4.2.3 Income
+### Income
 
@@
 
-### 4.3.4 Typical commute time
+### Typical commute time
 
@@
 
-5. Conclusions
+Conclusions
 ==========

### 2020-02-06 Dissonance_Santiago_v1/Dissonance_Santiago_v1.tex
Reorganized folder structure and created a new version to revise the paper after receiving reviewer comments from Journal of Transportation and Health.

--- 2019-11-01 Dissonance_Santiago_v1.tex
@@
   \begin{abstract}
+  \textbf{Introduction}\\
   Subjective wellbeing is a topic that has attracted considerable
@@
   way travel can impact subjective wellbeing, and how this, in turn, can
-  influence behavior. After decades of fascination with the automobile,
-  subjective wellbeing is increasingly recognized as an alternative
-  approach to assess transportation, and to gain valuable insights to
-  attract and retain active travelers and users of public transportation.
+  influence behavior.\\
+  \textbf{Objective}\\
   The objective of this paper is to analyze a number of affective values
@@
   that people commonly use. In particular, we are interested in the
-  potential for dissonance with respect to the primary mode of travel. The
-  study is based on data collected from a sample of travellers in the city
-  of Santiago, in Chile. Participants in the study were asked about their
-  usual mode of travel, and then were asked to name the mode or modes that
-  they associate with the affective values of freedom, enjoyment,
-  happiness, poverty, luxury and status. The results indicate that users
-  of public transportation experience the most dissonance in terms of
-  affective values, and active travellers the least. For those travellers
-  who experience dissonance, active travel is the mode most commonly
-  associated with freedom, enjoyment, and happiness, public transportation
-  is most commonly associated with poverty, and the automobil is most
-  commonly associated with luxury and status.
+  potential for dissonance with respect to the primary mode of travel.\\
+  \textbf{Materials and Methods}\\
+  The study is based on data collected from a sample of travellers in the
+  city of Santiago, in Chile. Participants in the study were asked about
+  their usual mode of travel, and then were asked to name the mode or
+  modes that they associate with the affective values of freedom,
+  enjoyment, happiness, poverty, luxury and status. Analysis is based on
+  tests of independence and visualization via mosaic plots.\\
+  \textbf{Results}\\
+  The results indicate that users of public transportation experience the
+  most dissonance in terms of affective values, and active travellers the
+  least. For those travellers who experience dissonance, active travel is
+  the mode most commonly associated with freedom, enjoyment, and
+  happiness, public transportation is most commonly associated with
+  poverty, and the automobil is most commonly associated with luxury and
+  status.
   \end{abstract}
@@
 \hypertarget{introduction}{%
-\section{1. Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}}
 
@@
 \hypertarget{background}{%
-\section{2. Background}\label{background}}
+\section{Background}\label{background}}
 
@@
 \hypertarget{case-study-and-data}{%
-\section{3. Case Study and Data}\label{case-study-and-data}}
+\section{Case Study and Data}\label{case-study-and-data}}
 
 \hypertarget{context}{%
-\subsection{3.1 Context}\label{context}}
+\subsection{Context}\label{context}}
 
@@
 \hypertarget{sample}{%
-\subsection{3.2 Sample}\label{sample}}
+\subsection{Sample}\label{sample}}
 
@@
 \hypertarget{analysis-and-results}{%
-\section{4. Analysis and Results}\label{analysis-and-results}}
+\section{Analysis and Results}\label{analysis-and-results}}
 
@@
 \hypertarget{who-experiences-dissonance}{%
-\subsection{4.1 Who experiences
+\subsection{Who experiences
 dissonance?}\label{who-experiences-dissonance}}
@@
 Primary Mode of Travel, and typical Commute Time. Table
-\ref{tab:cross-tabulation-results-without-instrumental} presents the
-frequency (in percentage) of dissonance, in other words, the percentage
-of respondents out of the total in their stratum who indicated mode or
-mode(s) for the affective value that do not correspond to their primary
-mode of travel.
+\ref{tab:cross-tabulation-results} presents the frequency (in
+percentage) of dissonance, in other words, the percentage of respondents
+out of the total in their stratum who indicated mode or mode(s) for the
+affective value that do not correspond to their primary mode of travel.
 
@@
 \hypertarget{age}{%
-\subsubsection{4.1.1 Age}\label{age}}
+\subsubsection{Age}\label{age}}
 
@@
 \hypertarget{education}{%
-\subsubsection{4.1.2 Education}\label{education}}
+\subsubsection{Education}\label{education}}
 
@@
 \hypertarget{income}{%
-\subsubsection{4.1.3 Income}\label{income}}
+\subsubsection{Income}\label{income}}
 
@@
 \hypertarget{primary-mode-of-travel}{%
-\subsubsection{4.1.4 Primary mode of
-travel}\label{primary-mode-of-travel}}
+\subsubsection{Primary mode of travel}\label{primary-mode-of-travel}}
 
@@
 dissonance is the primary mode of travel. It can be seen in Table
-\ref{tab:cross-tabulation-results-without-instrumental} that the
-differences are significative for all six affective values. Dissonance
-is particularly accute for users of public transportation when it comes
-to the values of Freedom, Enjoyment, and Happiness: almost 100\% of
-users of public transportation have identified other mode or modes as
-better representing those values. Dissonance on these values is the
-least for active travellers: less than 50\% of respondents associate
-Freedom to a different mode, and only around 60\% identified a different
-mode when responding to the values of Enjoyment and Happiness, compared
-to approximately 79\% and 71\% of those who travelled by Car. The
-picture changes when the values of Poverty, Luxury, and Status are
-considered. In this case, dissonance is less frequent for people who
-travel by car: less than 3\% of car users associate car with feelings of
-poverty, 41\% associate Luxury with a mode other than car, and only
-about 31\% relate Status to a different mode. Dissonance is more
-frequent in these values for active travellers, and users of public
-transportation and other modes, in no case being less than 75\%, and
-being virtually 100\% for users of public transportation, who
-consistently associate Luxury and Status with modes \emph{other} than
-public transportation.
+\ref{tab:cross-tabulation-results} that the differences are
+significative for all six affective values. Dissonance is particularly
+accute for users of public transportation when it comes to the values of
+Freedom, Enjoyment, and Happiness: almost 100\% of users of public
+transportation have identified other mode or modes as better
+representing those values. Dissonance on these values is the least for
+active travellers: less than 50\% of respondents associate Freedom to a
+different mode, and only around 60\% identified a different mode when
+responding to the values of Enjoyment and Happiness, compared to
+approximately 79\% and 71\% of those who travelled by Car. The picture
+changes when the values of Poverty, Luxury, and Status are considered.
+In this case, dissonance is less frequent for people who travel by car:
+less than 3\% of car users associate car with feelings of poverty, 41\%
+associate Luxury with a mode other than car, and only about 31\% relate
+Status to a different mode. Dissonance is more frequent in these values
+for active travellers, and users of public transportation and other
+modes, in no case being less than 75\%, and being virtually 100\% for
+users of public transportation, who consistently associate Luxury and
+Status with modes \emph{other} than public transportation.
 
 \hypertarget{typical-commute-time}{%
-\subsubsection{4.1.5 Typical commute time}\label{typical-commute-time}}
+\subsubsection{Typical commute time}\label{typical-commute-time}}
 
@@
 \hypertarget{which-modes-do-travellers-associate-with-affective-values}{%
-\subsection{4.2 Which modes do travellers associate with affective
+\subsection{Which modes do travellers associate with affective
 values?}\label{which-modes-do-travellers-associate-with-affective-values}}
@@
 \hypertarget{age-1}{%
-\subsubsection{4.2.1 Age}\label{age-1}}
+\subsubsection{Age}\label{age-1}}
 
@@
 \hypertarget{education-1}{%
-\subsubsection{4.2.2 Education}\label{education-1}}
+\subsubsection{Education}\label{education-1}}
 
@@
 \hypertarget{income-1}{%
-\subsubsection{4.2.3 Income}\label{income-1}}
+\subsubsection{Income}\label{income-1}}
 
@@
 \hypertarget{typical-commute-time-1}{%
-\subsubsection{4.3.4 Typical commute
-time}\label{typical-commute-time-1}}
+\subsubsection{Typical commute time}\label{typical-commute-time-1}}
 
@@
 \hypertarget{conclusions}{%
-\section{5. Conclusions}\label{conclusions}}
+\section{Conclusions}\label{conclusions}}
 

### 2020-02-06 Dissonance_Santiago_v2/Dissonance_Santiago_v2.Rmd
Reorganized folder structure and created a new version to revise the paper after receiving reviewer comments from Journal of Transportation and Health.

--- 2019-11-05 Dissonance_Santiago_v1.Rmd
@@
 output: rticles::elsevier_article
+
+header-includes:
+   - \usepackage[margin=1in]{geometry}
+   - \usepackage{lineno}
+   - \linenumbers
 ---
@@
 # Load packages used in this document
-
-library(rticles)
-library(readxl)
-library(tidyverse)
-library(rgdal)
-library(sf)
 library(ggmosaic)
 library(ggthemes)
+library(grid)
+library(gridExtra)
 library(kableExtra)
-library(gridExtra)
+library(readxl)
+library(rgdal)
+library(rticles)
+library(sf)
+library(tidyverse)
 ```
@@
 
-age_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = AGE)) +
+age_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = AGE, fill = AGE)) +
   geom_bar() +
@@
   xlab("Age of respondents") +
-  theme(axis.text.x = element_text(angle = 90))
-
-education_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = EDUCATION)) +
+  scale_fill_viridis_d() +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "none")
+
+education_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = EDUCATION, fill = EDUCATION)) +
   geom_bar() +
@@
   xlab("Education level of respondents") +
-  theme(axis.text.x = element_text(angle = 90))
-
-income_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = INCOME)) +
+  scale_fill_viridis_d() +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "none")
+
+income_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = INCOME, fill = INCOME)) +
   geom_bar() +
@@
   xlab("Income level of respondents") +
-  theme(axis.text.x = element_text(angle = 90))
-
-time_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = TRAVEL_TIME)) +
+  scale_fill_viridis_d() +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "none")
+
+time_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = TRAVEL_TIME, fill = TRAVEL_TIME)) +
   geom_bar() +
@@
   xlab("Duration of regular commute") +
-  theme(axis.text.x = element_text(angle = 90))
+  scale_fill_viridis_d() +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "none")
 
@@
 ```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
-mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "B", "C", "D", "E", "F", "G", "H"),
-                                     labels = c("Car", "Taxi", "Colectivo", "Motorcycle", "Metro", "Bus", "Bicycle", "Walk")))) +
+mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "G", "H", "E", "F", "B", "C", "D"),
+                                                   labels = c("Car", "Bicycle", "Walk", "Metro", "Bus", "Taxi", "Colectivo", "Motorcycle")),
+                                        fill = USED)) +
   geom_bar() +
   xlab("Primary Mode of Travel") +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-
-mode_plot2 <- ggplot(data = Overall_dissonance, aes(x = USED)) +
+  scale_fill_manual(values = c("A" = "#F8766D", 
+                               "G" = "#00BA38", "H" = "#00BA38", 
+                               "E" = "#619CFF", "F" = "#619CFF", 
+                               "B" = "#C77CFF", "C" = "#C77CFF", "D" = "#C77CFF")) +
+  theme_tufte() +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "none")
+
+mode_plot2 <- ggplot(data = Overall_dissonance, aes(x = USED, fill = USED)) +
   geom_bar() +
   xlab("Primary Mode of Travel") +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
+  scale_fill_manual(values = c("Car" = "#F8766D", "Active" = "#00BA38", "Public" = "#619CFF", "Other" = "#C77CFF")) +
+  theme_tufte() +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "none")
 
@@
 For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travellers with respect to the modes they tend to associate with various affective values.
-For this analysis we employ a visualization technique known as a mosaic plot.
+
+__**For this analysis we employ a visualization technique known as a mosaic plot.
 Mosaic plots are used in the exploration of multivariate categorical data [@Friendly1994mosaic; @Hofmann2000exploring], and they provide visual representations of multi-way contingency tables.
-The elements of the mosaic plot are called _tiles_, and the dimensions of each tile are proportional to values of variables in the underlying table.
-
-We begin our analysis by plotting primary mode of travel and the modes associated with each affective value (see Figure \ref{fig:mosaic-plots-by-attribute}).
+The elements of the mosaic plot are called _tiles_, and the dimensions of each tile are proportional to values of variables in the underlying table.**__
+
+We begin our analysis by plotting primary mode of travel and the modes associated with each affective value (see Figure \ref{fig:bar-plots-by-attribute}).
 The height of tile $j$ in these mosaics corresponds to the proportion of travellers who primarily travel by mode $j$, hence we can see that the most common primary mode of travel in this sample is by public transportation, followed by car, active travel, and other (also see Figure \ref{fig:primary-mode-travel}).
@@
 
-```{r figure-mosaic-plots-by-attribute, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
+```{r figure-mosaic-plots-by-attribute, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
 
@@
 
+```{r figure-bar-plots-by-attribute, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:bar-plots-by-attribute}Plots for affective values; in the y-axis are the number of cases by primary mode of transportation, and in the x-axis are the modes selected for each affective value"}
+
+Attribute_by_ideal <- Modes_by_Attribute %>% 
+  drop_na() %>%
+  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
+         USED != "Other", 
+         IDEAL != "Other") %>%
+  group_by(IDEAL, ATTRIBUTE, USED) %>%
+  summarize(n= sum(WEIGHT)) %>%
+  ungroup() %>%
+  # rename(MODE = IDEAL) %>%
+  mutate(CASE = "IDEAL",
+         USED = factor(USED, 
+                       levels = c("Car", "Active", "Public"),
+                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC")))
+
+Attribute_by_used <- Attribute_by_ideal %>%
+  group_by(USED, ATTRIBUTE) %>%
+  summarize(t = sum(n))
+
+Attribute_by_ideal <- Attribute_by_ideal %>%
+  left_join(Attribute_by_used, 
+            by = c("USED" = "USED", 
+                   "ATTRIBUTE" = "ATTRIBUTE")) %>% 
+  mutate(p = n/t)
+
+Attribute_by_ideal_by_mode <- ggplot(data = Attribute_by_ideal,
+       aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col() +
+  facet_grid(USED ~ ATTRIBUTE) +
+  #xlab("Modes associated with affective values") +
+  scale_y_continuous(name = "Proportion", 
+                     breaks = c(0, 0.5, 1), 
+                     limits = c(0, 1)) +
+  theme_tufte() +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        panel.border = element_rect(color = "black", fill = NA),
+        axis.title.x = element_blank(),
+        legend.title = element_blank())
+
+grid.arrange(Attribute_by_ideal_by_mode, 
+             textGrob("Primary Mode of Travel",
+                      rot = 270,
+                      gp = gpar(fontsize = 11),
+                      y = 0.6),
+             widths = c(10, 0.5),
+             ncol = 2,
+             top = "Affective Values",
+             bottom = "Modes Associated with Affective Values")
+```
+
 ### Age
 
-There are some interesting differences when viewed from the perspective of travellers of different ages (see Figure \ref{fig:mosaic-plots-by-age}).
+There are some interesting differences when viewed from the perspective of travellers of different ages (see Figure \ref{fig:bar-plots-by-age}).
 For example, as seen above, active travel is commonly associated with freedom, happiness, and enjoyment, even by car users, but especially by users of public transportation and other modes.
@@
 
-```{r figure-mosaic-plots-by-attribute-and-age, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+```{r tests-by-attribute-and-age, echo=FALSE, cache = TRUE}
 
@@
 # Freedom
-Modes_by_Freedom_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM")))
+Modes_by_Freedom_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
 
 # Enjoyment
-Modes_by_Enjoyment_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT")))
+Modes_by_Enjoyment_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
 
 # Happiness
-Modes_by_Happiness_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS")))
+Modes_by_Happiness_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
+
+# Poverty (p = 0.9702)
+Modes_by_Poverty_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
 
 # Luxury
-Modes_by_Luxury_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
+Modes_by_Luxury_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"), 
+                                                drop.unused.levels = TRUE))
 
 # Status
-Modes_by_Status_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
-
-labels <- c(paste('FREEDOM\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 2) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('ENJOYMENT\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('HAPPINESS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('LUXURY\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('STATUS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")))
+Modes_by_Status_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"),
+                                                drop.unused.levels = TRUE))
+```
+
+```{r figure-mosaic-plots-by-attribute-and-age, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
+```{r figure-bar-plots-by-attribute-and-age, echo=FALSE, cache = TRUE, fig.cap="\\label{fig:bar-plots-by-age}Plots for affective values by age; in the y-axis is the proportion in the interval [0, 1], and the x-axis is the mode selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+Attribute_by_ideal_by_age <- Modes_by_Attribute %>% 
+  drop_na() %>%
+  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
+         USED != "Other", 
+         IDEAL != "Other") %>%
+  group_by(IDEAL, ATTRIBUTE, AGE, USED) %>%
+  summarize(n= sum(WEIGHT)) %>%
+  ungroup() %>%
+  # rename(MODE = IDEAL) %>%
+  mutate(CASE = "IDEAL",
+         USED = factor(USED, 
+                       levels = c("Car", "Active", "Public", "Other"),
+                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC", "USED: OTHER")))
+
+Attribute_by_ideal <- Attribute_by_ideal_by_age %>%
+  group_by(USED, ATTRIBUTE, AGE) %>%
+  summarize(t = sum(n))
+
+Attribute_by_ideal_by_age <- Attribute_by_ideal_by_age %>%
+  left_join(Attribute_by_ideal, 
+            by = c("USED" = "USED", 
+                   "ATTRIBUTE" = "ATTRIBUTE", 
+                   "AGE" = "AGE")) %>% 
+  mutate(p = n/t)
+
+Freedom_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
+                           filter(ATTRIBUTE %in% c("FREEDOM"),
+                                  USED != "USED: OTHER", 
+                                  IDEAL != "Other"),
+                         aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ AGE, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        legend.title = element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Enjoyment_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
+                             filter(ATTRIBUTE %in% c("ENJOYMENT"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ AGE, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Happiness_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
+                             filter(ATTRIBUTE %in% c("HAPPINESS"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ AGE, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Luxury_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
+                          filter(ATTRIBUTE %in% c("LUXURY"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ AGE, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Status_by_age <- ggplot(data = Attribute_by_ideal_by_age  %>% 
+                          filter(ATTRIBUTE %in% c("STATUS"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ AGE, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+#extract legend
+#https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(Freedom_by_age)
+
+lay <- rbind(c(1, 2, 3, 4, 5, NA),
+             c(6, 7, 8, 9, 10, 11),
+             c(6, 7, 8, 9, 10, 12),
+             c(6, 7, 8, 9, 10, 13),
+             c(14, 14, 14, 14, 14, NA))
+
+grid.arrange(textGrob(paste('FREEDOM\np-value', 
+                            ifelse(round(Modes_by_Freedom_by_Age$p.value, 2) >= 0.001,
+                                   paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('ENJOYMENT\np-value', 
+                            ifelse(round(Modes_by_Enjoyment_by_Age$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Enjoyment_by_Age$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('HAPPINESS\np-value', 
+                            ifelse(round(Modes_by_Happiness_by_Age$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Happiness_by_Age$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('LUXURY\np-value', 
+                            ifelse(round(Modes_by_Luxury_by_Age$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Luxury_by_Age$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Age$p.value, 3) >= 0.001,
+                                                      paste("=", round(Modes_by_Status_by_Age$p.value, 3)),
+                                                      " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             Freedom_by_age + theme(legend.position="none", 
+                                    strip.text.x = element_text(angle = 90),
+                                    strip.text.y = element_blank(),
+                                    axis.title.y=element_blank(),
+                                    axis.text.y=element_blank(),
+                                    axis.ticks.y=element_blank()),
+             Enjoyment_by_age + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Happiness_by_age + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Luxury_by_age + theme(legend.position="none", 
+                                   strip.text.x = element_text(angle = 90),
+                                   strip.text.y = element_blank(),
+                                   axis.title.y=element_blank(),
+                                   axis.text.y=element_blank(),
+                                   axis.ticks.y=element_blank()),
+             Status_by_age + theme(legend.position="none",
+                                   strip.text.x = element_text(angle = 90),
+                                   strip.text.y = element_blank(),
+                                   axis.title.y=element_blank(),
+                                   axis.text.y=element_blank(),
+                                   axis.ticks.y=element_blank()),
+             textGrob("Car",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.2),
+             textGrob("Active",
+                      rot = 270,
+                      gp = gpar(fontsize = 9)),
+             textGrob("Public",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.7),
+             mylegend, 
+             layout_matrix = lay,
+             heights = c(1, 3, 3, 3, 1),
+             widths = c(3, 3, 3, 3, 3, 0.5),
+             left = "Proportion",
+             right = "Primary Mode of Travel",
+             top = "Affective Values by Age",
+             bottom = "Modes Associated with Affective Values")
+```
+
 ### Education
 
-Only two affective values were significant in the preceding analysis when seen from the perspective of education, namely luxury and status.
-As seen in Figure \ref{fig:mosaic-plots-by-education}, the perceptions of luxury and status are fairly consistent when differentiated by education.
+__**Only two affective values were significant in the preceding analysis when seen from the perspective of education, namely luxury and status.
+As seen in Figure \ref{fig:bar-plots-by-education}, the perceptions of luxury and status are fairly consistent when differentiated by education.
 Most respondents tend to associate luxury and status to the use of car, albeit this association is stronger for status than for luxury.
@@
 This type of respondent, while still more likely to associate luxury and status with the car, more commonly links active travel to these affects than travellers with lower levels of education.
-Most public transport users tend to associate luxury and status to the car, however, they associate active modes with status more than the same group with respect to luxury.
-
-```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, fig.width= 6, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+Most public transport users tend to associate luxury and status to the car, however, they associate active modes with status more than the same group with respect to luxury.**__
+
+```{r tests-by-attribute-and-education, echo=FALSE, cache = TRUE}
+
+# Select only values that were significant in the tests of independence
+
+# Also, use Cochran-Mantel-Haenzel tests
+# Freedom
+Modes_by_Freedom_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
+
+# Enjoyment
+Modes_by_Enjoyment_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
+
+# Happiness
+Modes_by_Happiness_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
+
+# Poverty (p = 0.827)
+Modes_by_Poverty_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
+
+# Luxury
+Modes_by_Luxury_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"), 
+                                                drop.unused.levels = TRUE))
+
+# Status
+Modes_by_Status_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"),
+                                                drop.unused.levels = TRUE))
+```
+
+```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, eval=FALSE, fig.width= 6, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
+```{r figure-bar-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, fig.cap="\\label{fig:bar-plots-by-education}Plots for affective values by level of education; in the y-axis is the proportion in the interval [0, 1], and the x-axis is the mode selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+
+Attribute_by_ideal_by_education <- Modes_by_Attribute %>% 
+  drop_na() %>%
+  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
+         USED != "Other", 
+         IDEAL != "Other") %>%
+  group_by(IDEAL, ATTRIBUTE, EDUCATION, USED) %>%
+  summarize(n= sum(WEIGHT)) %>%
+  ungroup() %>%
+  # rename(MODE = IDEAL) %>%
+  mutate(CASE = "IDEAL",
+         USED = factor(USED, 
+                       levels = c("Car", "Active", "Public", "Other"),
+                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC", "USED: OTHER")))
+
+Attribute_by_ideal <- Attribute_by_ideal_by_education %>%
+  group_by(USED, ATTRIBUTE, EDUCATION) %>%
+  summarize(t = sum(n))
+
+Attribute_by_ideal_by_education <- Attribute_by_ideal_by_education %>%
+  left_join(Attribute_by_ideal, 
+            by = c("USED" = "USED", 
+                   "ATTRIBUTE" = "ATTRIBUTE", 
+                   "EDUCATION" = "EDUCATION")) %>% 
+  mutate(p = n/t)
+
+Freedom_by_education <- ggplot(data = Attribute_by_ideal_by_education  %>% 
+                           filter(ATTRIBUTE %in% c("FREEDOM"),
+                                  USED != "USED: OTHER", 
+                                  IDEAL != "Other"),
+                         aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ EDUCATION, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        legend.title = element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Enjoyment_by_education <- ggplot(data = Attribute_by_ideal_by_education  %>% 
+                             filter(ATTRIBUTE %in% c("ENJOYMENT"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ EDUCATION, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Happiness_by_education <- ggplot(data = Attribute_by_ideal_by_education  %>% 
+                             filter(ATTRIBUTE %in% c("HAPPINESS"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ EDUCATION, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Luxury_by_education <- ggplot(data = Attribute_by_ideal_by_education  %>% 
+                          filter(ATTRIBUTE %in% c("LUXURY"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ EDUCATION, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Status_by_education <- ggplot(data = Attribute_by_ideal_by_education  %>% 
+                          filter(ATTRIBUTE %in% c("STATUS"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ EDUCATION, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+#extract legend
+#https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(Freedom_by_education)
+
+lay <- rbind(c(1, 2, 3, 4, 5, NA),
+             c(6, 7, 8, 9, 10, 11),
+             c(6, 7, 8, 9, 10, 12),
+             c(6, 7, 8, 9, 10, 13),
+             c(14, 14, 14, 14, 14, NA))
+
+grid.arrange(textGrob(paste('FREEDOM\np-value', 
+                            ifelse(round(Modes_by_Freedom_by_Education$p.value, 2) >= 0.001,
+                                   paste("=", round(Modes_by_Freedom_by_Education$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('ENJOYMENT\np-value', 
+                            ifelse(round(Modes_by_Enjoyment_by_Education$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Enjoyment_by_Education$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('HAPPINESS\np-value', 
+                            ifelse(round(Modes_by_Happiness_by_Education$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Happiness_by_Education$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('LUXURY\np-value', 
+                            ifelse(round(Modes_by_Luxury_by_Education$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Luxury_by_Education$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Education$p.value, 3) >= 0.001,
+                                                      paste("=", round(Modes_by_Status_by_Education$p.value, 3)),
+                                                      " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             Freedom_by_education + theme(legend.position="none", 
+                                    strip.text.x = element_text(angle = 90),
+                                    strip.text.y = element_blank(),
+                                    axis.title.y=element_blank(),
+                                    axis.text.y=element_blank(),
+                                    axis.ticks.y=element_blank()),
+             Enjoyment_by_education + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Happiness_by_education + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Luxury_by_education + theme(legend.position="none", 
+                                   strip.text.x = element_text(angle = 90),
+                                   strip.text.y = element_blank(),
+                                   axis.title.y=element_blank(),
+                                   axis.text.y=element_blank(),
+                                   axis.ticks.y=element_blank()),
+             Status_by_education + theme(legend.position="none",
+                                   strip.text.x = element_text(angle = 90),
+                                   strip.text.y = element_blank(),
+                                   axis.title.y=element_blank(),
+                                   axis.text.y=element_blank(),
+                                   axis.ticks.y=element_blank()),
+             textGrob("Car",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.2),
+             textGrob("Active",
+                      rot = 270,
+                      gp = gpar(fontsize = 9)),
+             textGrob("Public",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.7),
+             mylegend, 
+             layout_matrix = lay,
+             #nrow=3,
+             #widths = c(2.4, 1.9, 1.9, 1.9, 1.9), 
+             heights = c(1, 3, 3, 3, 1),
+             widths = c(3, 3, 3, 3, 3, 0.5),
+             left = "Proportion",
+             right = "Primary Mode of Travel",
+             top = "Affective Values by Education",
+             bottom = "Modes Associated with Affective Values")
+```
+
 ### Income
@@
 Three affective values were significant in the analysis by income; perhaps not surprisingly, all three have an economic dimension.
-Figure \ref{fig:mosaic-plots-by-income} reflects some important social inequalities associated with the way users feel about transportation in Santiago.
+Figure \ref{fig:bar-plots-by-income} reflects some important social inequalities associated with the way users feel about transportation in Santiago.
 When the affective perception of poverty is analyzed, the image shows that generally public transport is the mode most commonly associated with poverty.
@@
 
-```{r figure-mosaic-plots-by-attribute-and-income, echo=FALSE, cache = TRUE, fig.width= 7, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+```{r tests-by-attribute-and-income, echo=FALSE, cache = TRUE}
+
+# Select only values that were significant in the tests of independence
+
+# Also, use Cochran-Mantel-Haenzel tests
+# Freedom
+Modes_by_Freedom_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
+
+# Enjoyment
+Modes_by_Enjoyment_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
+
+# Happiness
+Modes_by_Happiness_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
+
+# Poverty (p = 0.8752)
+Modes_by_Poverty_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
+
+# Luxury
+Modes_by_Luxury_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"), 
+                                                drop.unused.levels = TRUE))
+
+# Status
+Modes_by_Status_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"),
+                                                drop.unused.levels = TRUE))
+```
+
+```{r figure-mosaic-plots-by-attribute-and-income, echo=FALSE, cache = TRUE, eval=FALSE, fig.width= 7, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
+```{r figure-bar-plots-by-attribute-and-income, echo=FALSE, cache = TRUE, fig.cap="\\label{fig:bar-plots-by-income}Plots for affective values by level of income; in the y-axis is the proportion in the interval [0, 1], and the x-axis is the mode selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+
+Attribute_by_ideal_by_income <- Modes_by_Attribute %>% 
+  drop_na() %>%
+  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
+         USED != "Other", 
+         IDEAL != "Other") %>%
+  group_by(IDEAL, ATTRIBUTE, INCOME, USED) %>%
+  summarize(n= sum(WEIGHT)) %>%
+  ungroup() %>%
+  # rename(MODE = IDEAL) %>%
+  mutate(CASE = "IDEAL",
+         USED = factor(USED, 
+                       levels = c("Car", "Active", "Public", "Other"),
+                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC", "USED: OTHER")))
+
+Attribute_by_ideal <- Attribute_by_ideal_by_income %>%
+  group_by(USED, ATTRIBUTE, INCOME) %>%
+  summarize(t = sum(n))
+
+Attribute_by_ideal_by_income <- Attribute_by_ideal_by_income %>%
+  left_join(Attribute_by_ideal, 
+            by = c("USED" = "USED", 
+                   "ATTRIBUTE" = "ATTRIBUTE", 
+                   "INCOME" = "INCOME")) %>% 
+  mutate(p = n/t)
+
+Freedom_by_income <- ggplot(data = Attribute_by_ideal_by_income  %>% 
+                           filter(ATTRIBUTE %in% c("FREEDOM"),
+                                  USED != "USED: OTHER", 
+                                  IDEAL != "Other"),
+                         aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ INCOME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        legend.title = element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Enjoyment_by_income <- ggplot(data = Attribute_by_ideal_by_income  %>% 
+                             filter(ATTRIBUTE %in% c("ENJOYMENT"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ INCOME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Happiness_by_income <- ggplot(data = Attribute_by_ideal_by_income  %>% 
+                             filter(ATTRIBUTE %in% c("HAPPINESS"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ INCOME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Luxury_by_income <- ggplot(data = Attribute_by_ideal_by_income  %>% 
+                          filter(ATTRIBUTE %in% c("LUXURY"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ INCOME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Status_by_income <- ggplot(data = Attribute_by_ideal_by_income  %>% 
+                          filter(ATTRIBUTE %in% c("STATUS"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ INCOME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+#extract legend
+#https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(Freedom_by_income)
+
+lay <- rbind(c(1, 2, 3, 4, 5, NA),
+             c(6, 7, 8, 9, 10, 11),
+             c(6, 7, 8, 9, 10, 12),
+             c(6, 7, 8, 9, 10, 13),
+             c(14, 14, 14, 14, 14, NA))
+
+grid.arrange(textGrob(paste('FREEDOM\np-value', 
+                            ifelse(round(Modes_by_Freedom_by_Income$p.value, 2) >= 0.001,
+                                   paste("=", round(Modes_by_Freedom_by_Income$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('ENJOYMENT\np-value', 
+                            ifelse(round(Modes_by_Enjoyment_by_Income$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Enjoyment_by_Income$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('HAPPINESS\np-value', 
+                            ifelse(round(Modes_by_Happiness_by_Income$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Happiness_by_Income$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('LUXURY\np-value', 
+                            ifelse(round(Modes_by_Luxury_by_Income$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Luxury_by_Income$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Income$p.value, 3) >= 0.001,
+                                                      paste("=", round(Modes_by_Status_by_Income$p.value, 3)),
+                                                      " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             Freedom_by_income + theme(legend.position="none", 
+                                    strip.text.x = element_text(angle = 90),
+                                    strip.text.y = element_blank(),
+                                    axis.title.y=element_blank(),
+                                    axis.text.y=element_blank(),
+                                    axis.ticks.y=element_blank()),
+             Enjoyment_by_income + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Happiness_by_income + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Luxury_by_income + theme(legend.position="none", 
+                                   strip.text.x = element_text(angle = 90),
+                                   strip.text.y = element_blank(),
+                                   axis.title.y=element_blank(),
+                                   axis.text.y=element_blank(),
+                                   axis.ticks.y=element_blank()),
+             Status_by_income + theme(legend.position="none",
+                                   strip.text.x = element_text(angle = 90),
+                                   strip.text.y = element_blank(),
+                                   axis.title.y=element_blank(),
+                                   axis.text.y=element_blank(),
+                                   axis.ticks.y=element_blank()),
+             textGrob("Car",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.2),
+             textGrob("Active",
+                      rot = 270,
+                      gp = gpar(fontsize = 9)),
+             textGrob("Public",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.7),
+             mylegend, 
+             layout_matrix = lay,
+             #nrow=3,
+             #widths = c(2.4, 1.9, 1.9, 1.9, 1.9), 
+             heights = c(1, 3, 3, 3, 1),
+             widths = c(3, 3, 3, 3, 3, 0.5),
+             left = "Proportion",
+             right = "Primary Mode of Travel",
+             top = "Affective Values by Income",
+             bottom = "Modes Associated with Affective Values")
+```
+
 ### Typical commute time
@@
 Four affective values were significant along this dimension in Table \ref{tab:cross-tabulation-results}.
-Figure \ref{fig:mosaic-plots-by-travel-time} shows the way travellers associate different affective values to modes of transportation by length of typical commute.
+Figure \ref{fig:bar-plots-by-travel-time} shows the way travellers associate different affective values to modes of transportation by length of typical commute.
 The first couple of factors, freedom and enjoyment, are associated with eudaimonic and hedonic factors of wellbeing, as discussed earlier in the paper.
@@
 The users of active transport in the sample tend to travel less than 20 minutes, and this is the same segment that considers that the status and luxury factors correspond mainly to the car and then to active transport.
-Looking at the four factors set out in Figure \ref{fig:mosaic-plots-by-travel-time}, it could be understood that the modes that are associated with intrinsically positive characteristics such as freedom and enjoyment tend to use public transport.
+Looking at the four factors set out in Figure \ref{fig:bar-plots-by-travel-time}, it could be understood that the modes that are associated with intrinsically positive characteristics such as freedom and enjoyment tend to use public transport.
 On the contrary, factors such as luxury and status tend to have a negative connotation, where the association with the car and other modes of transport (such as the individual taxi and the collective taxi) tends to dominate.
 
-```{r figure-mosaic-plots-by-attribute-and-time, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by commute time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+```{r tests-by-attribute-and-travel-time, echo=FALSE, cache = TRUE}
+
+# Select only values that were significant in the tests of independence
+
+# Also, use Cochran-Mantel-Haenzel tests
+# Freedom
+Modes_by_Freedom_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
+
+# Enjoyment
+Modes_by_Enjoyment_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
+
+# Happiness
+Modes_by_Happiness_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, 
+                                                   data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS",
+                                                                 USED != "Other", 
+                                                                 IDEAL != "Other"), 
+                                                   drop.unused.levels = TRUE))
+
+# Poverty (p = 0.6087)
+Modes_by_Poverty_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, 
+                                                 data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY",
+                                                               USED != "Other", 
+                                                               IDEAL != "Other"), 
+                                                 drop.unused.levels = TRUE))
+
+# Luxury (p = 0.5685)
+Modes_by_Luxury_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"), 
+                                                drop.unused.levels = TRUE))
+
+# Status
+Modes_by_Status_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, 
+                                                data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS",
+                                                              USED != "Other", 
+                                                              IDEAL != "Other"),
+                                                drop.unused.levels = TRUE))
+```
+
+```{r figure-mosaic-plots-by-attribute-and-time, echo=FALSE, cache = TRUE, eval=FALSE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by commute time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
 
@@
 
+```{r figure-bar-plots-by-attribute-and-travel-time, echo=FALSE, cache = TRUE, fig.cap="\\label{fig:bar-plots-by-travel-time}Plots for affective values by commute time; in the y-axis is the proportion in the interval [0, 1], and the x-axis is the mode selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
+
+Attribute_by_ideal_by_time <- Modes_by_Attribute %>% 
+  drop_na() %>%
+  filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"),
+         USED != "Other", 
+         IDEAL != "Other") %>%
+  group_by(IDEAL, ATTRIBUTE, TRAVEL_TIME, USED) %>%
+  summarize(n= sum(WEIGHT)) %>%
+  ungroup() %>%
+  # rename(MODE = IDEAL) %>%
+  mutate(CASE = "IDEAL",
+         USED = factor(USED, 
+                       levels = c("Car", "Active", "Public", "Other"),
+                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC", "USED: OTHER")))
+
+Attribute_by_ideal <- Attribute_by_ideal_by_time %>%
+  group_by(USED, ATTRIBUTE, TRAVEL_TIME) %>%
+  summarize(t = sum(n))
+
+Attribute_by_ideal_by_time <- Attribute_by_ideal_by_time %>%
+  left_join(Attribute_by_ideal, 
+            by = c("USED" = "USED", 
+                   "ATTRIBUTE" = "ATTRIBUTE", 
+                   "TRAVEL_TIME" = "TRAVEL_TIME")) %>% 
+  mutate(p = n/t)
+
+Freedom_by_time <- ggplot(data = Attribute_by_ideal_by_time  %>% 
+                           filter(ATTRIBUTE %in% c("FREEDOM"),
+                                  USED != "USED: OTHER", 
+                                  IDEAL != "Other"),
+                         aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ TRAVEL_TIME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        legend.title = element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Enjoyment_by_time <- ggplot(data = Attribute_by_ideal_by_time  %>% 
+                             filter(ATTRIBUTE %in% c("ENJOYMENT"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ TRAVEL_TIME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Happiness_by_time <- ggplot(data = Attribute_by_ideal_by_time  %>% 
+                             filter(ATTRIBUTE %in% c("HAPPINESS"),
+                                    USED != "USED: OTHER", 
+                                    IDEAL != "Other"),
+                           aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ TRAVEL_TIME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Luxury_by_time <- ggplot(data = Attribute_by_ideal_by_time  %>% 
+                          filter(ATTRIBUTE %in% c("LUXURY"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ TRAVEL_TIME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+Status_by_time <- ggplot(data = Attribute_by_ideal_by_time  %>% 
+                          filter(ATTRIBUTE %in% c("STATUS"),
+                                 USED != "USED: OTHER", 
+                                 IDEAL != "Other"),
+                        aes(x = IDEAL, y = p, fill = IDEAL)) + 
+  geom_col(position = "dodge") +
+  facet_grid(USED ~ TRAVEL_TIME, shrink = TRUE) +
+  xlab("Modes associated with affective values") +
+  ylab("Number of cases") +
+  theme_tufte() +
+  theme(panel.border = element_rect(color = "black", fill = NA)) +
+  theme(axis.text.x = element_text(angle = 90),
+        legend.position = "bottom",
+        axis.title.x=element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        plot.margin = margin(0, 0, 0, 0, "cm"))
+
+#extract legend
+#https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(Freedom_by_time)
+
+lay <- rbind(c(1, 2, 3, 4, NA),
+             c(6, 7, 8, 9, 11),
+             c(6, 7, 8, 9, 12),
+             c(6, 7, 8, 9, 13),
+             c(14, 14, 14, 14, NA))
+
+grid.arrange(textGrob(paste('FREEDOM\np-value', 
+                            ifelse(round(Modes_by_Freedom_by_Time$p.value, 2) >= 0.001,
+                                   paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('ENJOYMENT\np-value', 
+                            ifelse(round(Modes_by_Enjoyment_by_Time$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Enjoyment_by_Time$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('HAPPINESS\np-value', 
+                            ifelse(round(Modes_by_Happiness_by_Time$p.value, 3) >= 0.001,
+                                   paste("=", round(Modes_by_Happiness_by_Time$p.value, 3)),
+                                   " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             textGrob(paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Time$p.value, 3) >= 0.001,
+                                                      paste("=", round(Modes_by_Status_by_Time$p.value, 3)),
+                                                      " < 0.001")),
+                      gp = gpar(fontsize = 9)),
+             Freedom_by_time + theme(legend.position="none", 
+                                    strip.text.x = element_text(angle = 90),
+                                    strip.text.y = element_blank(),
+                                    axis.title.y=element_blank(),
+                                    axis.text.y=element_blank(),
+                                    axis.ticks.y=element_blank()),
+             Enjoyment_by_time + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Happiness_by_time + theme(legend.position="none", 
+                                      strip.text.x = element_text(angle = 90),
+                                      strip.text.y = element_blank(),
+                                      axis.title.y=element_blank(),
+                                      axis.text.y=element_blank(),
+                                      axis.ticks.y=element_blank()),
+             Status_by_time + theme(legend.position="none",
+                                   strip.text.x = element_text(angle = 90),
+                                   strip.text.y = element_blank(),
+                                   axis.title.y=element_blank(),
+                                   axis.text.y=element_blank(),
+                                   axis.ticks.y=element_blank()),
+             textGrob("Car",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.2),
+             textGrob("Active",
+                      rot = 270,
+                      gp = gpar(fontsize = 9)),
+             textGrob("Public",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.7),
+             mylegend, 
+             layout_matrix = lay,
+             #nrow=3,
+             #widths = c(2.4, 1.9, 1.9, 1.9, 1.9), 
+             heights = c(1, 3, 3, 3, 1),
+             widths = c(3, 3, 3, 3, 0.5),
+             left = "Proportion",
+             right = "Primary Mode of Travel",
+             top = "Affective Values by Commute Time",
+             bottom = "Modes Associated with Affective Values")
+```
+
 Conclusions

### 2020-02-06 Dissonance_Santiago_v2/Dissonance_Santiago_v2.tex
Reorganized folder structure and created a new version to revise the paper after receiving reviewer comments from Journal of Transportation and Health.

--- 2020-02-06 Dissonance_Santiago_v1/Dissonance_Santiago_v1.tex
@@
 \usepackage[hyphens]{url}
-
-  \journal{Journal of Transportation \& Health} % Sets Journal name
 
@@
 % Pandoc toggle for numbering sections (defaults to be off)
+
 % Pandoc header
+\usepackage[margin=1in]{geometry}
+\usepackage{lineno}
+\linenumbers
 \usepackage{booktabs}
@@
 from the Perspective of Subjective Wellbeing}
-    \author[Some University]{Author 1\corref{c1}}
+    \author[Some University]{Author 1\corref{Corresponding Author}}
    \ead{a1@university.com} 
-   \cortext[c1]{Corresponding Author}
     \author[Some School]{Author 2}
    \ead{a2@school.com} 
-
       \address[Some University]{Department, Street, City, State, Zip}
@@
   status.
+
+  journal: ``Journal of Transportation \& Health''
   \end{abstract}
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/plot-descriptive-statistics-1.pdf}
+\includegraphics{Dissonance_Santiago_v2_files/figure-latex/plot-descriptive-statistics-1.pdf}
 \caption{\label{fig:descriptive-statistics}Descriptive statistics of the
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-primary-mode-travel-1.pdf}
+\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-primary-mode-travel-1.pdf}
 \caption{\label{fig:primary-mode-travel}Frequency of primary mode used
@@
 interested in the responses of travellers with respect to the modes they
-tend to associate with various affective values. For this analysis we
-employ a visualization technique known as a mosaic plot. Mosaic plots
-are used in the exploration of multivariate categorical data (Friendly,
-1994; Hofmann, 2000), and they provide visual representations of
-multi-way contingency tables. The elements of the mosaic plot are called
-\emph{tiles}, and the dimensions of each tile are proportional to values
-of variables in the underlying table.
+tend to associate with various affective values.
+
+\textbf{\textbf{For this analysis we employ a visualization technique
+known as a mosaic plot. Mosaic plots are used in the exploration of
+multivariate categorical data (Friendly, 1994; Hofmann, 2000), and they
+provide visual representations of multi-way contingency tables. The
+elements of the mosaic plot are called \emph{tiles}, and the dimensions
+of each tile are proportional to values of variables in the underlying
+table.}}
 
@@
 associated with each affective value (see Figure
-\ref{fig:mosaic-plots-by-attribute}). The height of tile \(j\) in these
+\ref{fig:bar-plots-by-attribute}). The height of tile \(j\) in these
 mosaics corresponds to the proportion of travellers who primarily travel
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-1.pdf}
-\caption{\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective
-values; the y-axis is the proportion of respondents by main mode of
-transportation, and the x-axis is the proportion of modes selected for
-each value}
+\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-1.pdf}
+\caption{\label{fig:bar-plots-by-attribute}Plots for affective values;
+in the y-axis are the number of cases by primary mode of transportation,
+and in the x-axis are the modes selected for each affective value}
 \end{figure}
@@
 There are some interesting differences when viewed from the perspective
-of travellers of different ages (see Figure
-\ref{fig:mosaic-plots-by-age}). For example, as seen above, active
-travel is commonly associated with freedom, happiness, and enjoyment,
-even by car users, but especially by users of public transportation and
-other modes. However, when we break this down by age, we notice that
-this tendency weakens as people age, and older travellers increasingly
-associate these affective values to the car. Furthermore, the tendency
-to associate status with the car tends to increase with age, with the
-possible exception of public transport users, for whom other options
-(possibly taxi), gain status for older travellers (\textgreater{} 54) at
-the expense of other modes, including the car. In contrast, the car
-loses in the value of luxury with age, while other options become more
-commonly associated with feelings of luxury for older respondents, even
-for car users (Figure 2). Older car users (\textgreater{} 54) show less
-dissonance in status than in luxury, while active travellers present
-more dissonance in status than in luxury - and in fact, they more
-commonly project status in the car.
+of travellers of different ages (see Figure \ref{fig:bar-plots-by-age}).
+For example, as seen above, active travel is commonly associated with
+freedom, happiness, and enjoyment, even by car users, but especially by
+users of public transportation and other modes. However, when we break
+this down by age, we notice that this tendency weakens as people age,
+and older travellers increasingly associate these affective values to
+the car. Furthermore, the tendency to associate status with the car
+tends to increase with age, with the possible exception of public
+transport users, for whom other options (possibly taxi), gain status for
+older travellers (\textgreater{} 54) at the expense of other modes,
+including the car. In contrast, the car loses in the value of luxury
+with age, while other options become more commonly associated with
+feelings of luxury for older respondents, even for car users (Figure 2).
+Older car users (\textgreater{} 54) show less dissonance in status than
+in luxury, while active travellers present more dissonance in status
+than in luxury - and in fact, they more commonly project status in the
+car.
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-age-1.pdf}
-\caption{\label{fig:mosaic-plots-by-age}Mosaic plots for affective
-values by age; the y-axis is the proportion of respondents by main mode
-of transportation, and the x-axis is the proportion of modes selected
-for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared
-Test)}
+\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-age-1.pdf}
+\caption{\label{fig:bar-plots-by-age}Plots for affective values by age;
+in the y-axis is the proportion in the interval {[}0, 1{]}, and the
+x-axis is the mode selected for each value (p-values are for
+Cochran-Mantel-Haenszel Chi-Squared Test)}
 \end{figure}
@@
 
-Only two affective values were significant in the preceding analysis
-when seen from the perspective of education, namely luxury and status.
-As seen in Figure \ref{fig:mosaic-plots-by-education}, the perceptions
-of luxury and status are fairly consistent when differentiated by
-education. Most respondents tend to associate luxury and status to the
-use of car, albeit this association is stronger for status than for
-luxury. The second mode most often mentioned in relation to luxury is
-``other'' likely due to the flexibility and convenience (but cost) of
-using taxis. The exception in this case is the traveller with graduate
-education who uses active modes. This type of respondent, while still
-more likely to associate luxury and status with the car, more commonly
-links active travel to these affects than travellers with lower levels
-of education. Most public transport users tend to associate luxury and
-status to the car, however, they associate active modes with status more
-than the same group with respect to luxury.
+\textbf{\textbf{Only two affective values were significant in the
+preceding analysis when seen from the perspective of education, namely
+luxury and status. As seen in Figure \ref{fig:bar-plots-by-education},
+the perceptions of luxury and status are fairly consistent when
+differentiated by education. Most respondents tend to associate luxury
+and status to the use of car, albeit this association is stronger for
+status than for luxury. The second mode most often mentioned in relation
+to luxury is ``other'' likely due to the flexibility and convenience
+(but cost) of using taxis. The exception in this case is the traveller
+with graduate education who uses active modes. This type of respondent,
+while still more likely to associate luxury and status with the car,
+more commonly links active travel to these affects than travellers with
+lower levels of education. Most public transport users tend to associate
+luxury and status to the car, however, they associate active modes with
+status more than the same group with respect to luxury.}}
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-education-1.pdf}
-\caption{\label{fig:mosaic-plots-by-education}Mosaic plots for affective
-values by education; the y-axis is the proportion of respondents by main
-mode of transportation, and the x-axis is the proportion of modes
-selected for each value (p-values are for Cochran-Mantel-Haenszel
-Chi-Squared Test)}
+\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-education-1.pdf}
+\caption{\label{fig:bar-plots-by-education}Plots for affective values by
+level of education; in the y-axis is the proportion in the interval
+{[}0, 1{]}, and the x-axis is the mode selected for each value (p-values
+are for Cochran-Mantel-Haenszel Chi-Squared Test)}
 \end{figure}
@@
 perhaps not surprisingly, all three have an economic dimension. Figure
-\ref{fig:mosaic-plots-by-income} reflects some important social
+\ref{fig:bar-plots-by-income} reflects some important social
 inequalities associated with the way users feel about transportation in
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-income-1.pdf}
-\caption{\label{fig:mosaic-plots-by-income}Mosaic plots for affective
-values by income; the y-axis is the proportion of respondents by main
-mode of transportation, and the x-axis is the proportion of modes
-selected for each value (p-values are for Cochran-Mantel-Haenszel
-Chi-Squared Test)}
+\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-income-1.pdf}
+\caption{\label{fig:bar-plots-by-income}Plots for affective values by
+level of income; in the y-axis is the proportion in the interval {[}0,
+1{]}, and the x-axis is the mode selected for each value (p-values are
+for Cochran-Mantel-Haenszel Chi-Squared Test)}
 \end{figure}
@@
 \ref{tab:cross-tabulation-results}. Figure
-\ref{fig:mosaic-plots-by-travel-time} shows the way travellers associate
+\ref{fig:bar-plots-by-travel-time} shows the way travellers associate
 different affective values to modes of transportation by length of
@@
 the car and then to active transport. Looking at the four factors set
-out in Figure \ref{fig:mosaic-plots-by-travel-time}, it could be
-understood that the modes that are associated with intrinsically
-positive characteristics such as freedom and enjoyment tend to use
-public transport. On the contrary, factors such as luxury and status
-tend to have a negative connotation, where the association with the car
-and other modes of transport (such as the individual taxi and the
-collective taxi) tends to dominate.
+out in Figure \ref{fig:bar-plots-by-travel-time}, it could be understood
+that the modes that are associated with intrinsically positive
+characteristics such as freedom and enjoyment tend to use public
+transport. On the contrary, factors such as luxury and status tend to
+have a negative connotation, where the association with the car and
+other modes of transport (such as the individual taxi and the collective
+taxi) tends to dominate.
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-time-1.pdf}
-\caption{\label{fig:mosaic-plots-by-travel-time}Mosaic plots for
-affective values by commute time; the y-axis is the proportion of
-respondents by main mode of transportation, and the x-axis is the
-proportion of modes selected for each value (p-values are for
-Cochran-Mantel-Haenszel Chi-Squared Test)}
+\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-travel-time-1.pdf}
+\caption{\label{fig:bar-plots-by-travel-time}Plots for affective values
+by commute time; in the y-axis is the proportion in the interval {[}0,
+1{]}, and the x-axis is the mode selected for each value (p-values are
+for Cochran-Mantel-Haenszel Chi-Squared Test)}
 \end{figure}

### 2020-03-05 Dissonance_Santiago_v2/Dissonance_Santiago_v2_Word.Rmd
Created Word file for Beatriz

--- 2020-02-06 Dissonance_Santiago_v2/Dissonance_Santiago_v2.Rmd
@@
 ---
-title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing
-author:
-  - name: Author 1
-    email: a1@university.com
-    affiliation: Some University
-    footnote: Corresponding Author
-  - name: Author 2
-    email: a2@school.com
-    affiliation: Some School
-address:
-  - code: Some University
-    address: Department, Street, City, State, Zip
-  - code: Some School
-    address: Department, Street, City, State, Zip
-abstract: |
-   **Introduction**  
-   Subjective wellbeing is a topic that has attracted considerable attention in recent years due to the way it correlates with health.
-From a transportation perspective, there is a burgeoning literature on the way travel can impact subjective wellbeing, and how this, in turn, can influence behavior.
-   **Objective**  
-   The objective of this paper is to analyze a number of affective values associated with subjective wellbeing and the modes of transportation that people commonly use.
-In particular, we are interested in the potential for dissonance with respect to the primary mode of travel.
-   **Materials and Methods**  
-   The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
-Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associate with the affective values of freedom, enjoyment, happiness, poverty, luxury and status.
-Analysis is based on tests of independence and visualization via mosaic plots.
-   **Results**  
-   The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
-
-   journal: "Journal of Transportation & Health"
-date: "`r Sys.Date()`"
-bibliography: mybibfile.bib
-linenumbers: true
-numbersections: true
-csl: elsevier-harvard.csl
-output: rticles::elsevier_article
-
-header-includes:
-   - \usepackage[margin=1in]{geometry}
-   - \usepackage{lineno}
-   - \linenumbers
+title: "Dissonance-Santiago-v2-Word"
+author: "Antonio Paez"
+date: "3/4/2020"
+output: word_document
 ---
-
-<!-- This paper is an R markdown document that includes self-contained, reproducible analysis. To reproduce the paper the following files are needed:
-
-1. Dissonance_Santiago_v1.Rmd (this R markdown document)
-
-2.
-`Dissonance_Santiago.RData`.
-For reference: this data file was created using R notebook `00.
-Analysis of Dissonance Detailed.Rmd`.
-The initial analysis was done in the same R notebook.
-Neither of these two notebooks are needed for this document.
-
-3.
-For compiling into a pdf in the style of an Elsevier document: elsarticle.cls, elsevier-harvard.csl, elsevier-harvard-without-titles.csl, elsevier-vancouver.csl, elsevier-without-titles.cls, elsevier-with-titles.csl, elsevier-with-titles-alphabetical.csl, mybibfile.bib
--->
 

### 2020-08-14 Dissonance_Santiago_v2/Response-to-Reviewers-v2.Rmd
v2 BLM and AP revisions

---
title: "Response to Reviewers"
output: pdf_document
---

We would like to thank the editor and three anonymous reviewers for their thoughtful comments and suggestions to revise the paper. We believe that the paper has been substantially improved by their input. In this letter we respond to the feedback received, and describe the actions taken to revise the paper.

\newpage

# Reviewer 1

Policy and aims: The main and most important thing to work on is answering the ‘so what?’ question. Your findings are interesting but how does it change the way we see the world and think about transport? Although, I understand that exploring policy aims in detail is not the focus of your study, because implications for policy and interventions are an important aim of the journal, try and sell the importance of your findings and analysis for practical policies and practice with as much persuasiveness as you can. Are there specific areas of policy that your analysis inform. What policies or practice could be employed in which the differences between age groups, income or commute length, for example, would be necessary to take into account.

>\textcolor{blue}{Added: In various contexts, not only in Santiago, the perception of users is considered mainly from the scope of the trip satisfaction. Understanding dissonances allow public policy to recognise that public transport users are clearly at a disadvantage compared to other transport modes. On the other hand, the results recognise that within public transport users, there are also socioeconomic disadvantages – compared to other groups. This is relevant information for the generation of public policies that promote the use of sustainable modes and public transport, considering aspects of their personal well-being that transcend the areas of travel satisfaction. The factors defined in this study can, and should, be considered in the evaluation of measures that promote the use of sustainable transport in the long term.}

Justifying the use of SWB for transport: I'm not clear about how users can be attracted (line (L)26) to public transport and active travel. would overcoming psychological taboos be enough? So general point, need to argue well for the importance of SWB around travel, in comparison to considerations of travel time, and cost - I know this is hard to do!

>\textcolor{blue}{The consideration of factors related to the subjective personal well-being will enable targeting public policy strategies focused on nudging public and active transport users}

Contribution of the paper to the literature: I don't think you need to number the ways the paper contributes to literature the way you have - you can just say 'Firstly,...'etc. I would actually leave most of the material under these 1,2,3 points untill later in the paper. I would include the bits of it that justify the study in the introduction but would leave the findings till later. (i.e. 'The analysis shows that the people...etc')

>\textcolor{blue}{moved comments about literature towards the section of concluding remarks; leaving some results in the introductory section}

About the structure of the paper: Make the paragraph L90-94 more interesting.

>\textcolor{blue}{Done.}

Context: The paragraph from 179 to 189  could be better grounded in evidence – do you have any relevant references about the transport situation in Santiago de Chile? – local council or local authority documents on transport, economic, planning situations etc.

>\textcolor{blue}{Recent social demands have highlighted the relevance and impacts of the neoliberal economic model in the development of the city – which correlates with the construction of the society and therefore shapes the development of transport infrastructure (see for recent protests and social crisis: Davies, 2019; Guardiola-Rivera, 2019; Sehnbruch, 2019). Even though everyday mobility in Santiago has also been contextualized in relation to other Latin American cities (Avellaneda and Lazo, 2011; Rodriguez Vignoli, 2008), there is much more to be explored in other regions in the Chilean context. Measuring instruments and new methodologies have allowed a more accurate and precise understanding of the social issues arising as consequence of transport infrastructure and housing provision (Cox and Hurtubia, 2016), and the minimum provision of basic services (Tiznado-Aitken et al., 2016). However, the focus on accessibility as a measure of inequities remains predominant (Tiznado-Aitken et al., 2018; Figueroa Martínez, et al., 2018; Niehaus et al., 2016; Rojas et al., 2016).}

Figure 1: Place figure 1 so that it is introduced in the text before the figure itself is presented. The figure could be formatted more attractively.

>\textcolor{blue}{Done.}

Survey description: L 200 The sections of the survey that were not used for the present study do not need to be listed.

>\textcolor{blue}{The study considers data from 3 out of 8 sections of a longer survey – data being more relevant for the study. The topics around these sections are Individual characteristics of respondents, feelings and emotions related to their commute, and aspects describing their regular commute trips.}

Results description: In general be more precise in the case study section – for example L210 – what percentage took commutes more than 60minutes.

>\textcolor{blue}{The sample tends to be younger (56% is younger than 34 years old), and well-educated (68% of respondents having technical or professional education), with an almost uniform distribution of income levels. The trend in typical commute time is towards longer commutes – e.g. 55% of the trips are longer than 40 minutes, and from those 56% corresponds to trips over the 60 minutes long.}

St Louis et al 2014: L157 Explain why ‘more research is needed’

>\textcolor{blue}{Because most literature focuses in trip satisfaction – the study goes beyond the understanding of determinants of trip satisfaction.}

Aggrupation of transport modes: P218 – why is motorcycle different to car? – they are both private motorised vehicles – explain the categories that you have split the modes into.

>\textcolor{blue}{Car (26% of total modes – which corresponds to 91% of the total of private motorised modes), Active (9% - Walking + Bicycle), Public (60% - Metro + Bus), and Other motorised modes (6% - Taxi + Colectivo + Motorcycle).}

Affective values: p.223 Why were these affective values chosen?  - needs to be explained. I would not normally think of ‘Poverty’ as a value, but rather as an economic condition, so explain the nature of these affective values.

>\textcolor{blue}{Words.}

Figure 2 – again make more attractive.

>\textcolor{blue}{Words.}

Who experiences dissonance: L257 Why is it important to know who experiences dissonance?

>\textcolor{blue}{Understanding who experiences dissonance is relevant in this study. We believe most disadvantageous groups will experience more dissonance with respect to their primary travel mode and affective values, namely freedom, enjoyment, happiness, feelings of poverty, luxury, and status.}

Figure 3: It may be me being a bit stupid but I found the Mosaic figures hard to understand – could you explain even more clearly? I can’t see tile J or K on figure 3. However, the ensuing discussion around which groups attribute which attributes to which mode is clear and well explained, and I grasped the general concept of what you were analysing, is just the figures I am unclear on.

>\textcolor{blue}{Words.}

\newpage

# Reviewer 2

Chile and wellbeing: This paper is about subjective well-being, mode of transport, and dissonance. In the introduction, three areas are identified where this study is expected to contribute. One contribution is that the study includes data from Chile, which is a country that has not been highlighted in previous transport research. This could be further discussed. Are there any thoughts/expectations of similar or different results from studies from other parts of the world? The authors partly address this by pointing to large income gaps, a different approach to transport but also a different culture. Perhaps this can be clarified.

>\textcolor{blue}{As noted in our response to Reviewer 1, recent social demands have highlighted the relevance and impacts of the neoliberal economic model in the development of the city – which correlates with the construction of the society and therefore shapes the development of transport infrastructure (see for recent protests and social crisis: Davies, 2019; Guardiola-Rivera, 2019; Sehnbruch, 2019). Even though everyday mobility in Santiago has also been contextualized in relation to other Latin American cities (Avellaneda and Lazo, 2011; Rodriguez Vignoli, 2008), there is much more to be explored in other regions in the Chilean context. Measuring instruments and new methodologies have allowed a more accurate and precise understanding of the social issues arising as consequence of transport infrastructure and housing provision (Cox and Hurtubia, 2016), and the minimum provision of basic services (Tiznado-Aitken et al., 2016). However, the focus on accessibility as a measure of inequities remains predominant (Tiznado-Aitken et al., 2018; Figueroa Martínez, et al., 2018; Niehaus et al., 2016; Rojas et al., 2016).}

Paragraph 3 is fuzzy and can be clarified. Remove redundant information and stick to the specific contribution. Then, compare points 1, 2 and 3 with the objectives presented later in the paper (e.g., line 247). It is important that the purpose is reproduced correctly throughout the paper.

>\textcolor{blue}{}

Relation of studies in the literature: The introduction provides a background to why subjective well-being is a relevant area to study. The authors highlight relevant references and show current knowledge within the field. However, different concepts are used and it is not always clear what is meant and how the different studies relate to each other. It is unclear whether previous studies focused on satisfaction, affective values, perceptions in general, or attitudes.

>\textcolor{blue}{}

Aims: This confusion also related to the aim of this specific paper, will it focus on affect or affective values (which may be something else?).

>\textcolor{blue}{}

Attitudes and satisfaction: Also in the introduction attitudes was mentioned as an important variable to study. It is also unclear why studies that focused on "life satisfaction" is discussed since this is not the focus of this study

>\textcolor{blue}{Because satisfaction has been the conventional way of addressing unconventional factors. Paragraph 3 clearly states the aim of the study focused on affective values – and also explain how this goes beyond satisfaction.}

Dissonance: I also think dissonance, which is an important concept in this study, is not discussed in the background.

>\textcolor{blue}{This has been discussed in section 3.2. paragraph 4.}

Taken together, the introduction needs clarification when it comes to previous studies, the aim of this specific study and the contribution to existing knowledge.

>\textcolor{blue}{See response to Reviewer 1.}

Although the authors highlight tools from transport research to capture well-being in travel, such as STS, it is not this instrument chosen for data collection. It is unclear why Freedom; Enjoyment; Happiness; Poverty; Luxury; and Status are selected concepts. Motivate the choice more clearly and how they relate to previous research.

>\textcolor{blue}{See response to Reviewer 1 about election of affective values.}

Developing and developed countries: In a concluding section, you choose to discuss the need for this type of research in developing countries. This could advantageously be a separate section where more clearly discusses and justifies any differences between developing and developed countries.

>\textcolor{blue}{This has been also commented in the Background section: “The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel”. A separated paragraph in the conclusion addresses this discussion, in the Chilean and LA context.}

Method: The data collection procedure is not described.

>\textcolor{blue}{The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012. The survey was carried out face-to-face in centres of activity with dense provision of offices, services and educational centres.}

Separate results and analysis: I recommend separating results reporting and discussion/analysis to clarify what has been found.

>\textcolor{blue}{The results section has been divided in the two questions/aims of the study. The conclusion section discusses the findings.}

Figures 3, 4 and 7: The mosaic plot is however not helpful. Please consider other ways of presenting the data.

>\textcolor{blue}{Differs from Reviewer 3. The value of the mosaic figures is… we’ll keep them.}

Table 1: The tables are hard to interpret. I recommend to replace figure 1 with a table. Please be clear with the labels (for instance K-12 it unknown to me). If possible, add mean value and standard deviation to the table. This table should be in section 3.2.

>\textcolor{blue}{Words.}

The discussion is good although I miss a part on how this knowledge can help develop the alternatives and make them more attractive.

>\textcolor{blue}{See response to Reviewer 1.}

\newpage

# Reviewer 3

This paper is interesting as it details mode dissonance in terms of five affective values. The analysis method using visualization (through mosaic plots) is unique and suitable to the kind of data collected. Overall, the paper is structured very well.

>\textcolor{blue}{Words.}

SWB and health: The author(s) could at least add a paragraph about how SWB affects health, except for just mentioning that SWB has been found to be correlated with health.

>\textcolor{blue}{Words.}

Election of affective values: Second, the author(s) could make it clear how these affective values such as freedom, enjoyment, luxury and other are related to SWB. The connection is not quite clear in the first two sections.

>\textcolor{blue}{See our response to Reviewer 1 about election of affective values.}

Pg 6, L196-198: How were different areas divided?

>\textcolor{blue}{The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012. The survey was carried out face-to-face in centres of activity with dense provision of offices, services and educational centres.}

Pg 217-218: Taxi, colectivo and motorcycle are grouped as same. I find that the affective evaluations of motorcycle users could be different than those made by users of the other two modes. It would be better if the author(s) could explain it or mention it in some part of their limitations.

>\textcolor{blue}{Addressed in Reviewer 1. Only 0,9% of the sample used motorcycle as primary transport mode.}

Figure 4: NA is shown in the legend but not in the figure. The x-axis labels are overlapped. I understand this might be due to low values.

>\textcolor{blue}{Words.}

Figure 7: Same as Figure 4. Is there any alternative way to make it better?

>\textcolor{blue}{Words.}

### 2020-08-14 Dissonance_Santiago_v2/Dissonance_Santiago_v2.Rmd
v2 BLM and AP revisions

@@
 ---
-title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing
+title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Affective Values
 author:
@@
 abstract: |
-   **Introduction**  
-   Subjective wellbeing is a topic that has attracted considerable attention in recent years due to the way it correlates with health.
-From a transportation perspective, there is a burgeoning literature on the way travel can impact subjective wellbeing, and how this, in turn, can influence behavior.
-   **Objective**  
-   The objective of this paper is to analyze a number of affective values associated with subjective wellbeing and the modes of transportation that people commonly use.
-In particular, we are interested in the potential for dissonance with respect to the primary mode of travel.
-   **Materials and Methods**  
-   The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
-Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associate with the affective values of freedom, enjoyment, happiness, poverty, luxury and status.
-Analysis is based on tests of independence and visualization via mosaic plots.
-   **Results**  
-   The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
-
-   journal: "Journal of Transportation & Health"
+   *Introduction*  
+   Subjective wellbeing is a topic that has attracted considerable attention in the transportation literature in recent years.
+As a result, there is a burgeoning literature that investigates the impacts of travel on subjective wellbeing, and how wellbeing, in turn, can influence behavior.
+An important aspect of subjective wellbeing are the affective reactions of people to their experiences.
+   *Objective*  
+   The objective of this paper is to analyze the affective reactions of travelers with respect to various modes of transportation.
+In particular, we are interested in the potential for dissonance between primary mode of travel and the mode(s) of travel identified as evoking various affective reactions.
+   *Materials and Methods*  
+   The study is based on data collected from a sample of travelers in the city of Santiago, in Chile.
+Participants in the study were asked about their usual mode of travel, and then were asked to name their ideal mode(s) of transportation from the perspective of various affective reactions.
+The reactions we investigate are associated with the values of freedom, enjoyment, happiness, poverty, luxury, and status.
+Analysis is based on tests of independence and visualization techniques.
+   *Results*  
+   The results indicate that users of public transportation experience the most dissonance in terms of affective reactions, and active travelers the least.
+For those travelers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, whereas public transportation is most commonly associated with poverty.
+The automobile, in contrast, is the mode most commonly associated with luxury and status.
+
+journal: "Journal of Transport & Health"
 date: "`r Sys.Date()`"
@@
 This is a model of development that was initially introduced in North America as a solution to problems created by rapid urbanization, and that was eventually copied elsewhere [@Brown2009planning;@Angotti1996latin].
-Despite the initial promise of automotive technology, it is now evident that mobility centred on the private automobile has given rise to a litany of maladies that are in urgent need of correction.
+Despite the initial promise of automotive technology, it is now evident that mobility centered on the private automobile has given rise to a litany of maladies that are in urgent need of correction.
 This includes environmental concerns [i.e., climate change; @Chapman2007transport] as well as numerous other social [@Boschman2008toward; @Lucas2012transport; @Lucas2019evolution], health [@Khreis2016health; @Milne2012public], and equity issues [@Bocarejo2012transport; @Martens2012justice; @Pereira2017distributive].
 
-As the real impacts of our societal dependence on the private autombobile have become increasingly evident, the transportation agenda has aimed to shift focus to the reduction of car use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives than primarily (or even just) the private automobile [@Miller2011collaborative].
+As the impacts of our societal dependence on the private automobile have become increasingly evident, the transportation agenda has aimed to shift focus to the reduction of car use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives other than primarily (or even just) the private automobile [@Miller2011collaborative; @Lavery2013driving].
 In order to successfully achieve this goal, it is essential not only to provide the services and facilities that support public transportation and active travel, but also to attract new users to these modes of transportation [@Ettema2011satisfaction].
 Within this context, it has been argued that sustainable transportation policies require all participants in the transportation system to challenge what Gossling and Cohen [-@Gossling2014sustainable] termed _transportation taboos_: deep-seated ideas concerning the contribution to emissions by individuals, the inequality of market-based approaches, and the social and psychological functions of transportation.
-With respect to the latter, it is important to move beyond a purely utilitarian focus if we are to understand how the affective value of the transportation experience can be leveraged to improve alternative transportation - particularly transit and active modes [@Anable2005work; @Domarchi2008effect; @Gatersleben2007affective; @Steg2005car].
-
-A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing [SWB; see, inter alia, @Devos2013travel; and @Chatterjee2019commuting].
-SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” [@oecd2013oecd, p.
+With respect to the latter, subjective wellbeing (SWB) is increasingly recognized as a policy goal in and of itself [@Diener2015national; @Dolan2012measuring], and also as an intermediate objective to achieve ulterior goals.
+Accordingly, there is a growing consensus in the field of transportation about the need to move beyond a purely utilitarian focus to understand the affective and wellbeing values of the transportation experience [e.g., @Anable2005work; @Devos2013travel; @Domarchi2008effect; @Gatersleben2007affective; @Steg2005car].
+Consideration of factors related to subjective wellbeing, for example, are useful for policy-makers to enhance the experience of travel, to increase satisfaction with travel, and to meet the preferences of travelers [@Chatterjee2019commuting].
+
+A definition of subjective wellbeing is as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” [@oecd2013oecd, p.
 10].
-As memorably put by Steg [-@Steg2005car]: is the use of car a must, or is it a lust?
-A close alignment, or consonance, between affective values and the mode of transportation used to travel can result in greater subjective wellbeing and increase the probability of choosing that mode  (i.e., by satisfying the _lust_); on the other hand, dissonance, that is, the lack of concordance between the mode used and affective values would be detrimental to subjective wellbeing, especially of those for whom the use of the mode is a _must_ [@Devos2019satisfaction; @Mokhtarian2018travel].
-With these considerations in mind, one aim of the present research is to investigate _who_ experiences dissonance with respect to their primary mode of travel and affective values, namely freedom, enjoyment, happiness, feelings of poverty, luxury, and status.
-Furthermore, it is possible, even if use of a particular mode is a _must_, that travellers may still _lust_ for something else - in other words, the grass may in fact look greener from the window of the car.
-For this reason, we also aim to investigate which mode or modes are most commonly associated with affective values, with a focus on those travellers who experience dissonance in their primary mode.
-
-Research is based on data collected from a sample of travellers in the city of Santiago in Chile.
-Survey respondents were asked about their primary mode of travel, and also about the mode or modes that they associate with the affective values mentioned above.
-The paper contributes to the literature in three ways, as follows:
-
-1.
-The research reported here contributes to an emerging literature on the topic of transportation and affective values in the context of the Global South [@Alayyash2019commute; @Bejarano2017user; @Shao2019analysis; @Van2014effect; @Zorrilla2019exploring]; to the best of our knowledge, the case of Chile has not yet been reported.
-
-2.
-Although there is an extensive literature on the enjoyment of commute and other affective values [see for instance @Paez2010enjoyment; @Redmond2001positive; @Whalen2013mode; @Ye2017satisfaction], from a hedonic and even eudaimonic perspectives the analysis has yet to be applied more fully in terms of distributional issues – i.e.
-which groups more commonly experience dissonance [see @Devos2018people].
-
-3.
-The analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’ – implying their preferences, even in situations when their ideal mode is not part of their actual choice set.
-More concretely, the results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
-We also find that there are some substantial variations in dissonance by age, education, income, and typical commute time.
-The attitudes of travellers towards transport modes are critical factors to be considered by policy-makers in case they want to promote and increase the use of public transport or active modes [@Bornioli2019affective; @Devos2017travel; @Devos2019satisfying; @Garling2019role; @Redman2013quality].
-
-The structure of the paper is as follows.
-After these introductory remarks, we follow up with a background section that reviews the literature.
-Next, we discuss the case study and data used in the research.
-Then, the analysis and results are presented, before concluding with some discussion and directions for future research.
+As memorably put by Steg [-@Steg2005car]: is the use of a car a must, or is it a lust?
+A close alignment, or consonance, between affective reactions and the mode of transportation used to travel can result in greater subjective wellbeing and increase the probability of choosing that mode (i.e., by satisfying the _lust_); on the other hand, dissonance, namely the lack of concordance between the mode used and the affective reaction to that mode, would be detrimental to subjective wellbeing, especially to those for whom the use of the mode is a _must_ [@Devos2019satisfaction; @Mokhtarian2018travel].
+With these considerations in mind, the present research aims to investigate _who_ experiences affective dissonance with respect to their primary mode of travel.
+We focus our investigation on reactions from the perspective of feelings of freedom, enjoyment, happiness, poverty, luxury, and status - concepts termed _affective values_ hereafter.
+Furthermore, it is possible, even if use of a particular mode is a _must_, that travelers may still _lust_ for something else - in other words, the grass may look greener from the window of a car.
+For this reason, we also aim to investigate which mode or modes are most commonly identified as ideal from the perspective of the aforementioned affective values.
+
+Our research is based on data collected from a sample of travelers in the city of Santiago in Chile.
+The analysis sheds light on the affective reactions of people towards their primary mode of travel, and their perceptions towards 'ideal modes'.
+This reveals important differences in situations when the ideal mode of a traveler is not the mode they actually use - or in other words, the affective dissonance between actual and ideal modes of travel.
+More concretely, the results indicate that users of public transportation experience the most dissonance, followed by automobile users, and finally active travelers, who tend to experience the least affective dissonance.
+For those travelers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, whereas public transportation is most commonly associated with poverty, and the automobile is most commonly associated with luxury and status.
+We also find that there are significant variations in dissonance by age, education, income, and typical commute time.
+The reactions of travelers towards various transport modes are critical factors that policy-makers need to consider to promote and increase the use of public transport and active modes [@Bornioli2019affective; @Devos2017travel; @Devos2019satisfying; @Garling2019role; @Redman2013quality].
+
+After these introductory remarks, the paper follows up with a review of the literature on the topics of subjective wellbeing and affective values.
+Next, we discuss the case study, as well as the methodology and data used for this research.
+The analysis and results of the study are presented afterwards, before concluding with some discussion and directions for future research and policy.
+
+Please note that this document  was prepared using R Markdown and is an example of reproducible research [@Brunsdon2020opening].
+The R Markdown file, along with the data file needed to reproduce the analysis, are available for download\footnote{\url{https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg}}.
 
@@
 
-A consensus has emerged in the transportation community regarding the need to complement the traditional utilitarian perspective of transportation by looking at mobility and transport issues from the lens of their affective functions.
-The affective value of transportation in turn is important due to its potential to improve or detract from SWB.
-One of the primary ways to explore this has been the satisfaction that travelers feel towards their every day mobility experience [e.g., @Bergstad2011subjective].
+A consensus has emerged in recent years regarding the need to complement the traditional utilitarian perspective of transportation by investigating mobility and transport from the lens of their affective functions.
+The affective value of transportation is important due to its potential to improve or detract from SWB.
+
+One of the primary ways to explore issues of subjective wellbeing in transportation has been the satisfaction that travelers feel towards their everyday mobility experience [e.g., @Bergstad2011subjective].
 As a consequence, there is a wealth of research on satisfaction with the use of different modes of transportation.
-For example, numerous studies report that car users often have a higher level of satisfaction compared to other transport modes [@Bergstad2011affective; @Eriksson2013perceived; @Redmond2001positive; @Whalen2013mode; but see @Handy2019commute].
-In a similar way, there are multiple reports that active travel also tends to yield high levels of satisfaction [@Gatersleben2007affective; @Smith2017commute; @Stlouis2014happy; @Paez2010enjoyment; @Whalen2013mode; @Handy2019commute], In contrast, public transport users tend to assess their experience more negatively [@Abenoza2017travel; @Devos2016travel; @Gatersleben2007affective; @Handy2019commute; @Paez2010enjoyment].
-Multi-modal trips also influence satisfaction levels; for instance, when an individual chooses a particular mode of transportation, she will report a higher level of satisfaction with that chosen mode – perhaps as a form of _post hoc_ validation [@Susilo2014exploring].
-
-While the use of travel satisfaction has been mainly used in the context of daily trips – typically linked to cost-benefit and utilitarian measurements –, the evaluation of Subjective Wellbeing (SWB) over time has risen as an alternative measure.
-In the field of travel behaviour, Ettema et al.
+For example, numerous studies report that car users often have a higher level of satisfaction compared to other transport modes [@Bergstad2011affective; @Eriksson2013perceived; @Redmond2001positive], although others report highest commute satisfaction for bicycle and train commuters [e.g., @Whalen2013mode; @Handy2019commute].
+In a similar way, there are multiple reports that active travel also tends to yield higher levels of satisfaction [@Gatersleben2007affective; @Smith2017commute; @Stlouis2014happy; @Paez2010enjoyment; @Whalen2013mode; @Handy2019commute], In contrast, public transport users often assess their experience more negatively [@Abenoza2017travel; @Devos2016travel; @Gatersleben2007affective; @Handy2019commute; @Paez2010enjoyment].
+Multi-modal trips also influence satisfaction levels; for instance, individuals tend to report higher levels of satisfaction with the mode they use – perhaps as a form of _post hoc_ validation of their choices or circumstance [@Susilo2014exploring].
+
+While travel satisfaction has often been used in the context of daily trips – typically linked to cost-benefit and utilitarian measurements –, the evaluation of subjective wellbeing (SWB) over time has risen as an alternative measure.
+Ettema et al.
 [-@Ettema2010out, p.
-725] define SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporality – which implies assuming a tendency to be more stable over time.
+725] define SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporal period – which implies greater temporal stability.
 This concept has prompted a growing literature that complements and applies SWB in a broader range of satisfaction scales and situations.
-The definition of other factors such as travel choice mode, attitudes and external elements of the built environment have been studied for a broader understanding of the changes produced in the SWB [e.g., @Handy2019commute].
-As these factors do not necessarily apply to the general life satisfaction on the long term, the studies have aimed to determine both the direct and indirect effects on the perception of users [see, e.g., @Ye2017satisfaction].
-Other concepts have also emerged as the Satisfaction with Travel Scale (STS), a measurement devised by Ettema et al.
-[-@Ettema2011satisfaction], as well as different scales based on people’s travel perceptions.
+The definition of other factors such as travel choice mode, attitudes, and external elements of the built environment have been studied for a broader understanding of the changes produced in the SWB [e.g., @Handy2019commute].
+As these factors do not necessarily apply to longer-term general life satisfaction, other studies have aimed to determine both the direct and indirect effects on the perception of users [see, e.g., @Ye2017satisfaction].
+Other concepts have also emerged, including the Satisfaction with Travel Scale [@Ettema2011satisfaction], as well as different scales based on people’s perceptions of travel.
 De Vos et al.
-[-@Devos2015satisfying], for instance, explore in detail the underlying dimensions of the affective domain of STS on which SWB is based [for more on STS see also @Friman2013psychometric].
-
-Recent literature on SWB and its link with transport have demonstrated a relationship between people’s perceptions and satisfaction with their daily travel [e.g., @Smith2017commute; @Stlouis2014happy; @Mokhtarian2018travel].
-Scholars have shown that accessibility has been the most developed factor that influences people’s wellbeing [@Delbosc2012role], and activities have a direct impact on travel satisfaction [@Bergstad2011subjective].
+[-@Devos2015satisfying], for instance, explore in detail the underlying dimensions of the affective domain of STS on which SWB is based [for more on STS also see @Friman2013psychometric].
+
+The literature on SWB has demonstrated a relationship between people’s perceptions and satisfaction with their daily travel [e.g., @Smith2017commute; @Stlouis2014happy; @Mokhtarian2018travel].
+Scholars have shown that accessibility is among the most studied factors that influences subjective wellbeing [@Delbosc2012role], and activities have a direct impact on travel satisfaction [@Bergstad2011subjective].
 Delbosc [-@Delbosc2012role, p.
-28], for instance, has summarised the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.
-However, understanding the components affecting people’s perceptions implies the differentiation between affective (also named as symbolic-affective) and instrumental values [@Bergstad2011affective].
+28], for instance, has summarized the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.
+However, understanding the components that affect these perceptions implies the differentiation between affective (also named as symbolic-affective) and instrumental values [@Bergstad2011affective].
 Steg et al.
-(2011) have compared symbolic-affective opposed to instrumental-reasoned motives based on car-use, and other studies have also found associations between affective and symbolic aspects of car-use [see, e.g., @Gatersleben2007affective; @Lois2009relationship].
-Previous studies have also demonstrated how socio-demographic factors affect the levels of SWB.
-The effect of income on SWB [@Clark1996satisfaction; @Ferrer2005income]; education and unemployment [@Argyle1999causes]; age [@Diener1997subjective], and gender [@Tesch2008gender] have been extensively studied.
-Recent research also suggests the links between commuting, SWB and emotional wellbeing assessment (**Olson et al.
-2013**; **Kahneman et al.
-2004**).
-However, more research is needed to understand how these socio-demographic variables connect as well with the affective responses to mode of travel [@Stlouis2014happy].
-
-The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel [@Zorrilla2019exploring].
-In this way, there is an emerging literature that investigates affective factors in travel behaviour in a number of developing countries.
+(2011) have compared symbolic-affective and instrumental-reasoned motives for car-use, and similar findings are reported in other studies [e.g., @Gatersleben2007affective; @Lois2009relationship].
+Previous research also demonstrates how socio-demographic factors affect the levels of SWB, includin income [@Clark1996satisfaction; @Ferrer2005income], education and unemployment [@Argyle1999causes], age [@Diener1997subjective], and gender [@Tesch2008gender].
+However, further research beyond the determinants of trip satisfaction is needed to understand how these socio-demographic variables connect with the affective reactions to various modes of travel [@Stlouis2014happy].
+
+The research needs outlined above are well-recognized in the developed world, but there is still a dearth of research in the context of the Global South.
+Historical inequality in many developing countries has led to strong symbolic attachments to the automobile, in addition to negative connotations for public transport and active travel [@Zorrilla2019exploring].
+To address this gap in knowledge a body of literature has emerged to investigate the affective aspects of travel behavior in a number of developing countries.
 A cross-country study in Asia revealed that the affective factors of public transportation and car use are important, and in particular the social orderliness of transit was suggested as a way to make this mode more attractive to users [@Van2014effect].
 In terms of active travel, a study in China found that attitudes that embrace new styles and technologies despite their cost are associated with the intention to continue using shared bicycles [@Shao2019analysis].
-The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows how users felt proud using a bicycle shared system, in addition to experiencing feelings of belonging to a civic culture and the enjoyment and pleasure of travel itself [@Bejarano2017user].
-This paper contributes to further our understanding of affective values in travel behaviour in a developing country.
+The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows the pride users feel when using a bicycle shared system.
+This affective reaction is above and beyond other positive feelings, such as a sense of belongingness to a civic culture, and the enjoyment and pleasure of active travel itself [@Bejarano2017user].
 
@@
 
-The case study to contextualize the discussion is Santiago de Chile, the capital of one of the countries with the highest levels of inequality in terms of socio-economic distribution in the world.
-These inequities have manifested in a disproportionate expense in transport by the different socioe-conomic sectors, a disproportion in travel times and distances travelled.
-On the other hand, car ownership and use of public transport in the capital are directly conditioned by strong spatial segregation – the higher the income, the higher is the use of the automobile; conversely, and the lower the income, the higher is the predisposition to use public transport.
-Although transport is a reflection of deep inequities in various dimensions, it has triggered an exceptional discomfort and disagreement with the daily travel experience and quality of life.
-
-## Sample
-
-The study is based on a survey conducted in the city of Santiago during the months of November and December 2016, that is, the end of the Spring and beginning of Summer.
-The survey collected information on a wide range of travel and related issues.
-The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
+The case study for the present research is Santiago.
+Santiago is the capital of Chile, a country with one of the highest levels of socio-economic inequality in the world.
+A tangible manifestation of the inequalities experienced by many in Chile is the large disparity in the relative cost of transportation, travel time, and distance traveled by different socio-economic segments of the population.
+To further complicate matters, strong spatial segregation also conditions car ownership and the use of public transportation – the higher the income, the higher the use of the automobile; conversely, the lower the income, the higher the reliance on public transportation.
+Although the transportation experience is but one of many dimensions of inequality, the experiences in this sector have triggered exceptional discomfort and dissatisfaction among the public.
+Recent social unrest, triggered by a seemingly minor hike in the fare of public transportation, has brought many of these concerns to the forefront of the public conscience in dramatic fashion [e.g., @Davis2019; @GuardiolaRivera2019; @Sehnbruch2019].
+
+Previous research has helped to contextualize everyday mobility in Santiago relative to other Latin American cities [e.g., @Avellaneda2011; @RodriguesVignoli2008], but much remains to be explored.
+Measuring instruments and new methods have led to more accurate and precise understandings of the social issues that arise as consequence of transport infrastructure and housing provision [@Cox2016], and the minimum provision of basic services [@TiznadoAitken2016].
+However, the focus on accessibility as a measure of inequalities remains predominant [@TiznadoAitken2016; @Figueroa2018; @Niehaus2016; @Rojas2016].
+
+## Data
+
+The study is based on a survey conducted in the city of Santiago during the months of November and December of 2016, at the end of the Spring and beginning of Summer seasons.
+The survey collected information on a wide range of transportation and related issues, and the data collection protocol considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
+The survey was carried out face-to-face in centers of activity with dense provision of offices, services, and educational centers.
 An equal representation of both genders and a representation of the proportion of inhabitants per area were chosen as relevant characteristics of the sample.
-In total, there were $n=451$ valid surveys, although not every survey was complete and there were missing responses for some answers.
-
-The survey was structured in eight sections, as follows: 1) Individual characteristics of respondent; 2) Health; 3) Feelings and emotions; 4) Reasons for travel and planning travel; 5) Social interaction; 6) Nature and sustainability; 7) Information and telecommunications; 8) Built environment; and 9) Commuting.
-For the present study, we draw data from sections 1), 3) and 9).
-In terms of individual characteristics of the respondents and their commute, participants were asked about basic socio-demographic information, including age, level of education, income, and the typical duration of their regular commute.
+In total, there were $n=451$ valid reponses, although not every response was complete and some questions have missing values.
+
+The study considers data from 3 out of 8 sections of a longer survey.
+The relevant sections of the survey concern the individual characteristics of respondents, their feelings and affective responses related to their commute, and aspects describing their regular commute trips.
+In terms of individual characteristics and their commute, participants were asked socio-demographic information, including age (coded in three classes: younger than 35, older than 35 but younger than 55, and 55 and olde); level of education (three classes: Kindergarden to grade 12, or K-12, technical diploma or university graduate, and graduate degree), income (three classes, by tertile), and the typical duration of the respondent's regular commute (four classes, by duration in minutes).
 The descriptive statistics of the sample appear in Figure \ref{fig:descriptive-statistics}.
-The sample tends to be younger, and well-educated, with an almost uniform distribution of income levels.
-The trend in typical commute time is towards longer commutes.
+The sample trends to younger (56% is younger than 34 years old) and well-educated respondents (68% of respondents having technical or professional education), with an almost uniform distribution of income levels.
+The trend in typical commute time is towards longer commutes – e.g.
+55% of the trips are longer than 40 minutes, and from those 56% corresponds to trips over the 60 minutes long.
 
@@
 In addition, respondents were asked about their primary mode of travel for their regular commute.
-The modes available were Car, Taxi, Colectivo (a form of shared ride, intermediate in flexibility and capacity between taxi and bus); Motorcycle; Metro; Bus; Bicycle; Walking.
-As seen in the top panel of Figure \ref{fig:primary-mode-travel}, the three most common modes of travel are Metro, Bus, and Car, followed by Walking and Biycle.
-For the analysis, we aggregate these modes into the following categories (bottom panel of Figure \ref{fig:primary-mode-travel}): Car, Active (Walking + Bicycle), Public (Metro + Bus), and Other (Taxi + Colectivo + Motorcycle).
+The modes available were Car; Taxi; _Colectivo_ (a form of shared ride, intermediate in flexibility and capacity between taxi and bus); Motorcycle; Metro; Bus; Bicycle; and Walking.
+As seen in the top panel of Figure \ref{fig:primary-mode-travel}, the three most common modes of travel are Metro, Bus, and Car, followed by Walking and Bicycle.
+For the analysis, we aggregate these modes into the following categories (bottom panel of Figure \ref{fig:primary-mode-travel}): (26% of total modes – which corresponds to 91% of the total of private motorized modes), Active (9% - Walking + Bicycle), Public (60% - Metro + Bus), and Other motorized modes (6% - Taxi + Colectivo + Motorcycle).
 
@@
 
-Of particular interest for the present study is the following question in Part 3) of the survey:
+Of particular interest for the present study is the following question in Part 3 of the survey:
 
@@
 The question was asked for each of the following affective values: Freedom; Enjoyment; Happiness; Poverty; Luxury; and Status.
-The respondents were not constrained to select only one alternative, but could indicate by means of a checkbox any and all modes that they felt aligned with each affective value.
-This allows us to do an analysis of modal dissonance, a concept introduced into the transportation literature by Schwanen and Mokhtarian [-@Schwanen2004extent] based on earlier work by Feldman [-@Feldman1990settlement].
-Residential neighborhood-type dissonance was defined by Schwanen and Mokhtarian [-@Schwanen2004extent] as an incongruence in terms of the the land use patterns at the place of residence of an individual, and the individual's preferences.
-The concept of dissonance has since been extended in the travel behavior literature to encompass the mismatch between the choices individuals make, and the alternatives that would enable users to experience affective or instrumental values.
+The respondents were not constrained to select only one alternative, but could indicate by means of checkboxes any and all modes that they felt aligned with each affective value.
+This allows us to analyze the mode dissonance.
+Dissonance is a concept introduced into the transportation literature by Schwanen and Mokhtarian [-@Schwanen2004extent] based on earlier work by Feldman [-@Feldman1990settlement].
+Originally used to investigate residential dissonance [@Schwanen2004extent], the concept has since been extended in the travel behavior literature to encompass the mismatch between the choices individuals make, and the alternatives that would enable users to improve their experience.
 This includes, for example, travel mode dissonance [@Devos2018people].
@@
 $$
-D_i = 
+D_{ij} = 
 \begin{cases}
-0 & if \text{ primary mode} = \text{mode associated with value } i\\
+0 & if \text{ primary mode of traveler }i == \text{mode associated with value } j\\
 1 & \text{ otherwise}
@@
 $$
-Therefore, if a respondent's primary mode of travel is Car, but indicated any other mode or modes in relation to Freedom, the respondent experienced dissonance:
+Therefore, if respondent $i$ travels primarily by Car, but indicated any other mode(s) in relation to Freedom, the respondent experienced dissonance:
 $$
-D_{\text{Freedom}} = 1
+D_{i,\text{Freedom}} = 1
 $$
 
-Furthermore, we also expanded the responses to account for all modes identified by respondents in relation to the affective values.
-However, to avoid double counting the respondents in our frequency tabulations, we also calculated a sample weight that was the inverse of the number of modes selected in response to each affective value.
-For instance, if a respondent selected two modes in relation to affective value $i$, the two modes receive a weight of $1/2$; if a respondent selected three modes, then their weights are $1/3$; and so on.
-In this way we do not treat unfairly those who selected only one mode, and the sum of all weighted modes is equal to the sample size.
-
-Analysis and Results
+In these calculations we account for all modes identified by respondents in relation to the affective values.
+Therefore, to avoid double counting the respondents in our frequency tabulations, we also calculated a sample weight as the inverse of the number of modes selected in response to each affective value.
+For instance, for respondents who selected two modes in relation to affective value $j$, each of these two modes receive a weight of $w_{ij}=1/2$; if a respondent selected three modes, then their weights are $w_{ij}=1/3$; and so on.
+In this way we do not treat unfairly those respondents who selected only one mode, and the sum of all weighted responses is equal to the size of the sample $n$.
+
+Results
 ==========
 
-In what follows, analysis is done on two related but distinct questions.
-The first part of the analysis seeks to understand _who_ experiences dissonance, and the second part, building off that, aims to explore which modes of travel are more commonly identified as embodying affective values by those travellers who experience dissonance.
-
-Please note that this document was prepared using R Markdown and contains reproducible analysis.
-The R markdown file, along with the data file needed to reproduce the analysis, can be downloaded from the following anonymous Drive folder:
-
-https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg
+In what follows, the results refer to two related but distinct questions.
+The first part of the analysis seeks to understand _who_ experiences dissonance, whereas the second part, building off that, aims to explore _which modes_ are more commonly identified as embodying affective values by those travelers who experience dissonance.
 
@@
 
-To investigate the first question in our analysis, we create contingency tables that tabulate the frequency of dissonance with respect to each affective value, stratified by the attributes of Age, Education, Income, Primary Mode of Travel, and typical Commute Time.
-Table \ref{tab:cross-tabulation-results} presents the frequency (in percentage) of dissonance, in other words, the percentage of respondents out of the total in their stratum who indicated mode or mode(s) for the affective value that do not correspond to their primary mode of travel.
-
-As seen in the table, there are five characteristics of the respondents and their commutes that we use in the analysis.
-Three of these categories are socio-economic and demographic, namely age, level of education, and income.
+We begin by profiling the travelers who experience dissonance.
+The null hypothesis is that there are no systematic differences in terms of who tends to experience affective dissonance with respect to their primary mode of travel.
+To investigate this hypothesis we create contingency tables to tabulate the frequency of dissonance with respect to each affective value, stratified by the individual attributes of respondents.
+Table \ref{tab:cross-tabulation-results} presents the frequency (in percentage) of dissonance.
+This is the percentage of respondents out of the total in their stratum who selected, for each affective value, a mode or mode(s) of transportation that do not correspond to their primary mode of travel.
+
+As seen in the table, there are five individual attributes that we analyze.
+Three of these are socio-economic and demographic, namely age, level of education, and income.
 The other two are transportation related, namely primary mode of travel and commute time.
-The frequency tables were tested in every case by means of the $\chi^2$ test of independence ($p$-values are reported in the table; lower $p$-values mean that the null hypothesis of independence can be rejected with greater confidence).
+The frequency tables are tested in every case using $\chi^2$ tests of independence ($p$-values are reported in the table; lower $p$-values mean that the null hypothesis of independence can be rejected with greater confidence).
 It is interesting to note that the only category for which all affective values are significant at better than 5% level of confidence is mode of travel.
@@
 
-With respect to Age, previous studies have reported that older adults tend to be more satisfied with their travel experience than younger people [@Cao2014satisfaction; @Devos2016travel; @Ye2017satisfaction].
-In the case, we find that five affective values show dissonance that significantly deviates from the null hypothesis of independence, namely Freedom, Enjoyment, Happiness, Luxury, and Status.
+With respect to age, previous studies have reported that older adults tend to be more satisfied with their travel experience than younger people [@Cao2014satisfaction; @Devos2016travel; @Ye2017satisfaction].
+In the case, we find that there there are significant differences in dissonance by age with respect to five affective values, namely Freedom, Enjoyment, Happiness, Luxury, and Status.
 We observe that levels of dissonance tend to be high in general, and in no case less than 60%.
-For instance, almost 90% of travellers younger than 35 experience travel mode dissonance with respect to Freedom, and more than 94% experience dissonance with respect to enjoyment.
-In general, younger travellers tend to experience dissonance more frequently, with dissonance being less frequent for older travellers.
-The exception to this trend is Luxury, an affective value for which older travellers (age >54) experience dissonance more frequently than mid-aged travellers (ages 35-54).
+For instance, almost 90% of travelers younger than 35 experience travel mode dissonance with respect to Freedom, and more than 94% experience dissonance with respect to Enjoyment.
+In general, younger travelers tend to experience dissonance more frequently, with dissonance being less frequent for older travelers.
+The exception to this trend is Luxury, an affective value for which older travelers (age >54) experience dissonance more frequently than mid-aged travelers (ages 35-54).
 
@@
 
-When seen from the perspective of Education, the results do not support the hypothesis of  significant differences in the frequency of dissonance by levels of education for the values of Freedom, Enjoyment, Happiness, and Poverty, and only two affective values show significant differences between education levels: Luxury and Status.
+The results do not allow us to reject the hypothesis of equal levels of dissonance by levels of education for the values of Freedom, Enjoyment, Happiness, and Poverty.
+In contrast we can reject the null hypothesis in the case of two affective values, namely Luxury and Status.
 In the case of Luxury, dissonance is more frequent among people who have only K-12 education, and less frequently, albeit still high, for people with technical/university level education and post-graduate education.
@@
 
-The next variable we examine is income, and in this case three affective values are significant: Poverty, Luxury, and Status.
-Since Poverty is a negative affect, we see here that lower income people tend to associate this feeling to their primary mode of commuting more frequently (almost 20% of the time) than other income groups.
-For example, whereas approximately 16% of mid-income people are dissatisfied with their primary mode of travel in this respect, less than 7% of high income individuals are.
-Dissonance with respect to Luxury and Status also tends to be more common among lower income people, and declines substantially for mid- and high income respondents.
+The next individual attribute that we examine is income, and in this case we detect significant differences in dissonance for three affective values: Poverty, Luxury, and Status.
+Since Poverty is a negative affect, we see here that lower income individuals tend to associate this feeling to their primary mode of commuting with higher frequency (almost 20% of the time) than other income groups.
+Whereas approximately 16% of mid-income people are dissatisfied with their primary mode of travel when it comes to evoking feelings of Poverty, less than 7% of high income individuals are.
+Dissonance with respect to Luxury and Status also tends to be more common among lower income individuals, and declines substantially for mid- and high income respondents.
 Notice as well that the frequency of dissonance is higher in terms of Luxury than Status for mid- and high income people.
@@
 The variable that shows the largest differences in the frequency of dissonance is the primary mode of travel.
-It can be seen in Table \ref{tab:cross-tabulation-results} that the differences are significative for all six affective values.
-Dissonance is particularly accute for users of public transportation when it comes to the values of Freedom, Enjoyment, and Happiness: almost 100% of users of public transportation have identified other mode or modes as better representing those values.
-Dissonance on these values is the least for active travellers: less than 50% of respondents associate Freedom to a different mode, and only around 60% identified a different mode when responding to the values of Enjoyment and Happiness, compared to approximately 79% and 71% of those who travelled by Car.
+It can be seen in Table \ref{tab:cross-tabulation-results} that the differences are significant for all six affective values.
+Compared to users of other modes of transportation, dissonance is particularly acute for users of public transportation when it comes to the values of Freedom, Enjoyment, and Happiness: almost 100% of users of public transportation have identified other mode or modes as better representing those affective values.
+Dissonance on these values is the least for active travelers: less than 50% of respondents who are active travelers associate Freedom to a different mode, and only around 60% identified a different mode when responding to the values of Enjoyment and Happiness, compared to approximately 79% and 71% of those whose primary mode is car.
 The picture changes when the values of Poverty, Luxury, and Status are considered.
-In this case, dissonance is less frequent for people who travel by car: less than 3% of car users associate car with feelings of poverty, 41% associate Luxury with a mode other than car, and only about 31% relate Status to a different mode.
-Dissonance is more frequent in these values for active travellers, and users of public transportation and other modes, in no case being less than 75%, and being virtually 100% for users of public transportation, who consistently associate Luxury and Status with modes _other_ than public transportation.
+In this case, dissonance is less frequent for people who travel by car: less than 3% of car users associate the car with feelings of Poverty, only 41% associate Luxury with a mode other than car, and only about 31% relate Status to a different mode.
+Dissonance is more frequent in these values for active travelers, and users of public transportation and other modes, in no case being lower than 75%.
+This figure is virtually as high as 100% for users of public transportation, a group of travelers who consistently associate Luxury and Status with modes _other_ than public transportation.
 
@@
 
-Turning now to typical commute time, four affectie values show significant differences at better than 10% confidence: Freedom, Happiness, Luxury, and Status.
+Turning now to typical commute time, four affective values show significant differences at better than 10% confidence: Freedom, Happiness, Luxury, and Status.
 Perhaps not surprisingly, dissonance is more frequent among people whose typical commutes are longer.
@@
       booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB factors",
+      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various affective values",
       escape = FALSE,
@@
 
-## Which modes do travellers associate with affective values?
-
-The preceding analysis suggests that there is significant mode dissonance along various dimensions and for various affective values.
-This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better in terms of how travellers respond to different affects.
-Less is known about the values that travellers associate with modes _other_ than the one they use.
-For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travellers with respect to the modes they tend to associate with various affective values.
-
-__**For this analysis we employ a visualization technique known as a mosaic plot.
-Mosaic plots are used in the exploration of multivariate categorical data [@Friendly1994mosaic; @Hofmann2000exploring], and they provide visual representations of multi-way contingency tables.
-The elements of the mosaic plot are called _tiles_, and the dimensions of each tile are proportional to values of variables in the underlying table.**__
-
-We begin our analysis by plotting primary mode of travel and the modes associated with each affective value (see Figure \ref{fig:bar-plots-by-attribute}).
-The height of tile $j$ in these mosaics corresponds to the proportion of travellers who primarily travel by mode $j$, hence we can see that the most common primary mode of travel in this sample is by public transportation, followed by car, active travel, and other (also see Figure \ref{fig:primary-mode-travel}).
-Notice that there are some small discrepancies in the heights across affective values: these are caused by a small number of non-responses.
-Next, the width of the tile $k$ in the mosaics is proportional to the frequency with which a mode was named in relation to affective value $i$.
-Recall that respondents could nominate more than one mode in response to each affective value, and some did.
-For this reason, we used sampling weights, so that the total number of responses corresponds to the size of the sample.
-
-In terms of Freedom, we see that Car users frequently identify this affect with the use of Car; however, those who do not, very often select Active Travel as the mode that better represents Freedom.
-A majority of active travellers, on the other hand, identify Active Travel as the mode that evokes feelings of Freedom; few of them attach this value to Car, and even fewer to public transportation and other modes.
-Travellers whose primary mode of travel is public transportation seldom associate this mode with Freedom, and in fact more frequently relate this affective response to Active Travel followed by Car.
-Users of other modes seem to be split almost equally in their attribution of Freedom, between Active Travel, Car, and Other.
-In general, Active Travel is the mode most often identified as embodying Freedom, with the exception of Car travellers.
-
-The pattern with respect to Enjoyment is similar to that for Freedom, but with an even more decisive tilt towards Active Travel, with even more respondents whose primary mode of travel is Car choosing Active Travel as the mode that better represents Enjoyment.
-Notice that very few of Active Travelers selected Car as an enjoyable mode.
-Likewise, compared to Freedom, Active Travel is perceived as being more enjoyable by users of Public Transportatoin and Other modes.
-Responses with respect to Happiness are somewhere in between Freedom and Enjoyment, but Happiness is, if anything, even less frequently identified with Public Transportation.
-
-Three other affective responses show a marked difference.
-Public Transportation was seldom associated by respondents to feelings of Freedom, Enjoyment, and Happiness; on the other hand, it is the mode that is most commonly selected by respondents for evoking feelings of Poverty - even by users of Public Transportation.
-Active Travel was the second most common response for its association with Poverty.
-Likewise, Whereas Active Travel was often associated to feelings of Freedom, Enjoyment, and Happiness, the mode most frequently associated with Luxury and Status is the Car, although active travellers seem to be somewhat more resistant to this association compared to respondents who travel by Car, Public Transportation, and Other modes.
-
-Next, we further explore these responses after stratifying by Age, Education, Income, and Commute Time.
-We test the underlying 3-way tables by means of the Cochran-Mantel-Haenszel $\chi^2$ test of independence.
+## Which modes do travelers associate with affective values?
+
+The preceding analysis indicates that there is significant mode dissonance along various dimensions and for various affective values.
+This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better the affective reactions of travelers.
+Less is known about the values that travelers associate with modes _other_ than the one they use.
+For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travelers with respect to the modes they ideally tend to associate with various affective values.
+For this analysis we employ a visualization technique known as _faceting_.
+Bar charts are used to plot the proportions of respondents who associate each mode of transportation with an affective value.
+Faceting allows us to explore these proportions in a multivariate way by slicing the data according to additional attributes.
+The result is a visual representation of a multi-way contingency table.
+Please note that due to the small numbers of travellers who use modes categorized as "Other" we henceforth exclude them from the analysis.
+
+We begin our investigation of the modes more frequently associated with different affective values by plotting the primary mode of travel and the modes associated with the values (see Figure \ref{fig:bar-plots-by-attribute}).
+We can think of the figure as a matrix of plots, with each dimension of the matrix a _facet_.
+In this figure, the columns of the matrix of plots correspond to different affective values, and the rows to different modes of primary mode of transportation, i.e., the mode actually used.
+The height of the bars in these plots is the proportion of respondents who selected mode $j = \text{Car, Active, Public}$ as embodying the corresponding affective value.
+
+We know from the preceding analysis (Table \ref{tab:cross-tabulation-results}) that users of public transportation tend to experience dissonance with significantly higher frequency than car users and active travelers.
+But which mode(s) would align better to their expectations with regards to the affective values under study?
+If we inspect the bottom row of plots, we see that public transport users most of the time associate Freedom, Enjoyment, and Happiness with active travel.
+Users of public transportation are more or less equally split in terms of associating Poverty with active travel and public transportation, whereas they overwhelmingly associate Luxury and Status with the private car.
+
+Active travelers rarely experience dissonance with respect to Freedom, Enjoyment, and Happiness.
+And although the experience of dissonance is more frequent with respect to Luxury and Status, there is still a sizeable plurality of active travellers who associate these two affective values with active travel, _not_ the car (contrast these to the responses of public transit users.)
+
+Interestingly, dissonance among car users with respect to Freedom, Enjoyment, and Happiness is relatively high.
+While car is still the most frequently chosen mode associated with Freedom among car users, the proportion of car users who identify Freedom with active travel is almost as high.
+And when it comes to Enjoyment and Happiness, car users experience significant dissonance and in fact a majority tend to indicate active travel as representing these two affective values.
+In contrast, car users display little dissonance with respect to feelings of Luxury and Status.
+
+It is interesting to note that feelings of "Poverty" are associated with public transportation and active travel in almost exactly the same proportions, irrespective of the primary mode of travel.
+
+Next, we further explore these responses after stratifying by age, education, income, and typical commute time.
+We test the underlying 3-way tables by means of the Cochran-Mantel-Haenszel $\chi^2$ test of independence, (the $p$-values of the tests are reported in the figures.) The next set of figures adds a facet to the columns, so that each affective value is now further divided into columns that correspond to the levels of an individual attribute (i.e., age, education, income, and typical commute time.)
 
@@
 
-There are some interesting differences when viewed from the perspective of travellers of different ages (see Figure \ref{fig:bar-plots-by-age}).
-For example, as seen above, active travel is commonly associated with freedom, happiness, and enjoyment, even by car users, but especially by users of public transportation and other modes.
-However, when we break this down by age, we notice that this tendency weakens as people age, and older travellers increasingly associate these affective values to the car.
-Furthermore, the tendency to associate status with the car tends to increase with age, with the possible exception of public transport users, for whom other options (possibly taxi), gain status for older travellers (> 54) at the expense of other modes, including the car.
-In contrast, the car loses in the value of luxury with age, while other options become more commonly associated with feelings of luxury for older respondents, even for car users (Figure 2).
-Older car users (> 54) show less dissonance in status than in luxury, while active travellers present more dissonance in status than in luxury - and in fact, they more commonly project status in the car.
+We find some interesting differences when exploring dissonance from the perspective of age of the travelers (see Figure \ref{fig:bar-plots-by-age}).
+For example, as seen in the preceding section, active travel is commonly associated with Freedom, Happiness, and Enjoyment, even by car users, but especially by users of public transportation.
+However, when we break this down by age, we notice that this tendency weakens as people age, and older travelers increasingly assign these affective values to the car.
+Furthermore, the tendency to associate Status with the car tends to increase with age.
+In contrast, the car loses in the value of Luxury with age among car and public transport users, but gains among active travelers after dropping among mid-aged respondents.
+Older travelers almost universally associate Status with the car.
 
@@
 
-__**Only two affective values were significant in the preceding analysis when seen from the perspective of education, namely luxury and status.
-As seen in Figure \ref{fig:bar-plots-by-education}, the perceptions of luxury and status are fairly consistent when differentiated by education.
-Most respondents tend to associate luxury and status to the use of car, albeit this association is stronger for status than for luxury.
-The second mode most often mentioned in relation to luxury is "other" likely due to the flexibility and convenience (but cost) of using taxis.
-The exception in this case is the traveller with graduate education who uses active modes.
-This type of respondent, while still more likely to associate luxury and status with the car, more commonly links active travel to these affects than travellers with lower levels of education.
-Most public transport users tend to associate luxury and status to the car, however, they associate active modes with status more than the same group with respect to luxury.**__
+Significant differences in dissonance by education are detected for five affective values.
+As seen in Figure \ref{fig:bar-plots-by-education}, the association between active travel and Freedom is weaker among car travelers who are less educated (i.e., education K-12).
+Feelings of enjoyment are more frequently associated with active travel, and more so for less educated (K-12) and highly educated (graduate) car users and active travelers.
+This is somewhat different among users of public transportation, a majority of whom still assign feelings of Freedom to active travel, but with a higher proportion of travelers who associate this affective value to the car, especially among highly educated individuals.
+Less educated travelers who use the car are less likely to associate the value of Happiness to active travel, and this changes among people with higher levels of academic achievement, for whom active travel more frequently evokes feelings of Happiness.
+As before, most respondents identify the car with the values of Luxury and Status, and in general, people with lower education declare positive associations with the car more frequently.
+The exception is Status among active travelers: the more highly educated the traveler, the lower the probability of dissonance with respect to this affective value.
 
@@
 
-Three affective values were significant in the analysis by income; perhaps not surprisingly, all three have an economic dimension.
-Figure \ref{fig:bar-plots-by-income} reflects some important social inequalities associated with the way users feel about transportation in Santiago.
-When the affective perception of poverty is analyzed, the image shows that generally public transport is the mode most commonly associated with poverty.
-There are some interesting differences, however, to be observed by income level.
-Whereas middle income users of public transportation associate this mode to poverty most frequently, this is not the case of high income users of public transportation, who tend to link active travel to poverty with greater frequency.
-Similarly, active travel is more often associated with poverty by low income travellers than middle or high income travellers.
-A possible explanation for this is that walking or cycling are related to the idea of a lack of financial means to access other modes of transport.
-For high income car users, on the other hand, public transportation may have connotations of poverty due to its massive use, whereas active travel may be seen more as a lifestyle alternative.
-
-With respect to luxury and status, we see again that these two values coincide more strongly in their association with the car.
-Moreover, we also notice that these perceptions become increasingly frequent at higher levels of income.
-Unlike users of other modes, the high-income public transport user group tends to concentrate a broader association of luxury and status factors with active transport, reinforcing the notion that at higher levels of income, people may see active modes as a lifestyle alternative.
-High income active travellers, although still more likely to associate luxury and status to the car, are more likely than users of other modes to associate these affects to active travel, perhaps due to an awareness of the benefits of walking and using the bicycle.
+Like with education, there are significant differences in dissonance by income for five affective values.
+As seen in Figure \ref{fig:bar-plots-by-income}, car users with lower incomes tend to associate Freedom and Enjoyment with active travel, but more with respect to Enjoyment.
+In contrast, Enjoyment is more frequently associated with active travel among more affluent car users.
+Active travelers seldom experience dissonance with respect to Freedom, Enjoyment, and Happiness, irrespective of income level.
+However, although public transport users still tend to link active travel with feelings of Freedom, Enjoyment, and Happiness, they remain more likely to attribute these values to the car.
+
+With respect to luxury and status, we see again that these two values generally are attributed to the car, but with some interesting differences by income and primary mode of travel.
+Indeed, higher income active travelers, although still more likely to associate Luxury and Status with the car, are more likely than users of other modes to associate these affects to active travel, perhaps due to an awareness of the benefits of walking and using the bicycle.
 Furthermore, high-income users of cars are more likely to experience consonance with respect to status and luxury, in what might be a form of self-congratulatory confirmation of success.
@@
 
-The last dimension that we examine is typical commute time.
-Four affective values were significant along this dimension in Table \ref{tab:cross-tabulation-results}.
-Figure \ref{fig:bar-plots-by-travel-time} shows the way travellers associate different affective values to modes of transportation by length of typical commute.
-The first couple of factors, freedom and enjoyment, are associated with eudaimonic and hedonic factors of wellbeing, as discussed earlier in the paper.
-On the other hand, the luxury and status are defined mainly by a socio-economic component.
-As seen in the figure, freedom and enjoyment are most frequently mentioned in relation to active travel, followed by car.
-However, active travel is more frequently associated with freedom and enjoyment by people who typically undertake relatively short trips (<20 min) or travellers whose typical trips are longer (>60 min).
-In this respect, active travel may be seen as an ideal mode for trips, and as an enviable mode by people whose trips are longer.
-
-In the case of luxury and status factors, both follow a similar pattern, despite variations in travel times.
-Despite the travel time exceeding 60 minutes, car users consider that their transport mode is mostly associated with luxury and status.
-The users of active transport in the sample tend to travel less than 20 minutes, and this is the same segment that considers that the status and luxury factors correspond mainly to the car and then to active transport.
-Looking at the four factors set out in Figure \ref{fig:bar-plots-by-travel-time}, it could be understood that the modes that are associated with intrinsically positive characteristics such as freedom and enjoyment tend to use public transport.
-On the contrary, factors such as luxury and status tend to have a negative connotation, where the association with the car and other modes of transport (such as the individual taxi and the collective taxi) tends to dominate.
+The last dimension of dissonance that we examine is typical commute time.
+Four affective values are significant along this dimension, namely Freedom, Enjoyment, Happiness, and Status.
+Figure \ref{fig:bar-plots-by-travel-time} shows the way travelers associate different affective values to modes of transportation by length of typical commute.
+
+Among car users, Freedom is associated with the car in the case of every commute but the longest (>60 min), in which case active travel is more frequently identified as the mode that evokes feelings of Freedom.
+The associations of active travel with Enjoyment  and Happiness are consistently high among car users, although car becomes more frequently associated with this value for longer commutes.
+As we have seen before, active travelers seldom experience dissonance with respect to Freedom, Enjoyment, and Happiness, and if anything the strength of this association increases with longer commutes.
+Public transportation users again are split in their preference towards active travel and car as the modes more likely to evoke feelings of Freedom, Enjoyment, and Happiness, and there are only relatively minor differences in these preferences by length of commute.
+The last affective value that displays significant differences in dissonance by length of typical commute is Status.
+The car tends to dominate as the mode more frequently associated with this value among car and public transportation users.
+Active travelers, on the other hand, associate status more strongly with short or very long commutes: only when commutes are shorter than 20 minutes or longer than 60 minutes do active travelers associate feelings of Status with the car.
 
@@
 
-Conclusions
+Summary and Concluding Remarks
 ==========
 
-Subjective wellbeing is a topic that has attracted considerable attention in recent years due to its relationship with health.
-In the field of transportation, there is a large and growing body of literature that documents the way transportation can impact subjective wellbeing.
-Likewise, there is strong evidence that subjective wellbeing can influence travel behavior.
-As the world tries to move from a culture dominated by a century-long love affair with the automobile, there is a pressing need to understand how travellers perceive different modes of transportation from the lens of subjective wellbeing.
-Insights in this regard could prove valuable to develop and implement plans and policies to attract and retain users to healthier, more environmentally friendly transportation options, in particular active travel and public transportation.
-For this reason, understanding mode dissonance, the extent to which the context of travellers differs from their aspirations, is a worthwhile topic for research.
-
-The premise of the research presented in this paper is that subjective wellbeing is a composite construct of various affective values.
-In this paper we investigated mode dissonance from the perspective of six affective values associated with subjective wellbeing, namely freedom, enjoyment, happiness, poverty, luxury, and status.
-The research presented here was based on a sample of travellers in Santiago, the capital of Chile.
+The topic of subjective wellbeing has attracted considerable attention in recent years due to its relationship with health.
+As the world tries to move from a culture dominated by a century-long love affair with the automobile, there is a pressing need to understand how travelers perceive different modes of transportation from the lens of subjective wellbeing.
+Insights in this regard could prove valuable to develop and implement plans and policies to attract and retain users to healthier, more environmentally friendly transportation options [@Chatterjee2019commuting].
+For this reason, understanding mode dissonance, the extent to which the experience of travelers differs from their aspirations, is a worthwhile topic for research.
+
+This paper contributes to the literature in three ways.
+
+First, the research contributes to an emerging literature on the topic of transportation and subjective wellbeing in the context of the Global South [@Alayyash2019commute; @Bejarano2017user; @Shao2019analysis; @Van2014effect; @Zorrilla2019exploring]; to the best of our knowledge, the case of Chile has not yet been reported.
+Second, although there is an extensive literature on the enjoyment of commute and other affective values [see for instance @Paez2010enjoyment; @Redmond2001positive; @Whalen2013mode; @Ye2017satisfaction], from a hedonic and even eudaimonic perspectives the analysis has yet to be applied more fully in terms of distributional issues – i.e.
+which groups more commonly experience dissonance [see @Devos2018people].
+Third, the analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’, complementing the studies based on affective factors on transit or active modes [@Bornioli2019affective; @Devos2017travel], satisfaction [@Devos2019satisfying], or quality [@Redman2013quality].
+
+The premise of this study is that a key component of subjective wellbeing is the affective reaction to experience [see the definition of wellbeing offered by the OECD; -@@oecd2013oecd].
+In this paper we investigated mode dissonance from the perspective of six affective values.
+The research presented here was based on a sample of travelers in Santiago, the capital of Chile.
 Participants in this research were asked about their typical mode of travel, and then about the mode or modes that they associate with each of the six affective values.
-Analysis using hypothesis testing (tests of independence) and vizualization techniques (mosaic plots) uncovered interesting patterns.
-Some of our findings are well aligned with previous research; for example, active travellers experience less dissonance than car users, and users of public transportation experience the most dissonance of all.
-However, by considering affective values separately instead of aggregating them into a single indicator of subjective wellbeing, we manage to preserve some granularity with respect to various responses.
-This turns out to be important, because hedonic/eudaimonic values are more frequently related to active travel (freedom, enjoyment, happiness), whereas poverty is more frequently related to public transportation and active travel.
-Luxury and status, on the other hand, are more frequently associated to luxury and status.
+Analysis using hypothesis testing (tests of independence) and visualization techniques (bar charts with faceting) uncovered interesting patterns.
+Some of our findings are well aligned with previous research; for example, active travelers experience less dissonance than car users, and users of public transportation experience the most dissonance of all.
+However, by considering affective values separately instead of aggregating them into a single indicator of subjective wellbeing, we manage to preserve greater granularity with respect to various responses than most studies.
+This is important because hedonic/eudaimonic values are more frequently related to active travel (Freedom, Enjoyment, Happiness), whereas Poverty is more frequently related to public transportation and active travel.
+Luxury and Status, on the other hand, are more frequently associated to car.
 
 Further delving into the question of which modes are associated with these affective values, we find that there are important differences in terms of the typical mode of travel.
-Active travellers experience dissonance with relatively little frequently with respect to freedom, enjoyment, and happiness, but when they do, they tend to attach positive values to the car.
-Car users experience dissonance with respect to these affects more frequently than active travellers, and when they do, they strongly relate possitive hedonic/eudaimonic values to active travel.
-In other words, it is possible that drivers dream of walking when it comes to feelings especially of enjoyment and happiness.
+Active travelers experience dissonance with relatively little frequently with respect to Freedom, Enjoyment, and Happiness, but when they do, they tend to attach positive values to the car.
+Car users experience dissonance with respect to these affects more frequently than active travelers, and when they do, they strongly relate positive hedonic/eudaimonic values to active travel.
+In other words, it is possible that drivers dream of walking when it comes to feelings of Enjoyment and Happiness, and to a lesser extent Freedom.
 The other side of the coin is also interesting.
-When it comes to affective values with a stronger socio-economic flavor, such as poverty, luxury, and status, car users tend to experience dissonance less frequently than users of other modes.
-Active travellers, altough more resistant to the lure of the car compared to users of public transportation, also tend to attach values of luxury and status to the car when they experience dissonance.
-
-An examination of these effects by age, level of education, level of income, and typical trip duration reveals that some of the responses become more pronounced.
+When it comes to affective values with a stronger socio-economic flavor, such as Poverty, Luxury, and Status, car users tend to experience dissonance less frequently than users of other modes.
+Active travelers, although more resistant to the lure of the car compared to users of public transportation, also tend to attach values of Luxury and Status to the car when they experience dissonance.
+
+An examination of these effects by age, level of education, level of income, and typical trip duration reveals some ways in which these trends become more pronounced.
 For instance, older people are less likely than younger people to associate active travel with positive hedonic/eudaimonic affects, and are more likely to attach these values to the car.
@@
 
-Our results not only help to flesh out some ways in which mode dissonance could play out from the perspective of different affects, but also does so in the context of a Latin American country, a region where historically there are deep-seated tabooes with respect to different modes of transportation: the poor travel by public transportation and/or are forced active travellers; where the rich enjoy the luxury of private vehicles and/or are active travellers by choice.
-In this way, the paper helps us to reflect on the ways the public experiences transportation-related subjective wellbeing, and how this in turn could be used to increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
-
-With respect to opportunities for future research, a possible avenue for extending the findings reported in this paper relates to the use of the modes other than the typical mode of transportation.
-In a recent paper that investigaed commute satisfaction for car users, Al-Ayyash and Abou-Zeid [-@Alayyash2019commute] considered three models: for current trip satisfaction, remembered satisfaction while using public transport, and current satisfaction using public transport.
-The findings suggest that low service quality in public transportation can result in a generalised negative perception, and that this perception is more difficult to smooth if commuters do not regularly use public transport.
+These results not only help to flesh out some ways in which mode dissonance could play out from the perspective of different affects, but does so in the context of a Latin American country, a region where deep-seated taboos with respect to different modes of transportation exist: the poor travel by public transportation and/or are forced active travelers; a country where the rich enjoy the luxury of private vehicles and/or are active travelers by choice.
+In this way, the paper helps us to reflect on the affective reaction of members of the public with respect to their transportation experience.
+A better understanding of these responses can in turn be used to judiciously enhance the experience of commuting, to increase the satisfaction of commuters, and to meet their preferences.
+
+In  this respect, it is important to note that the perception of users has been considered mainly from the lens of trip satisfaction, but the more granular approach taken in this study offers some advantages.
+For example, understanding dissonances reveals that public transport users are clearly at a disadvantage (i.e., they experience dissonance more frequently) compared to other travelers.
+Furthermore, the results reveal that within public transport users, there are also important socio-economic differences.
+In contrast, users of cars do not necessarily associate hedonic/eudaimonic values to this mode, which suggests that not only these feelings could be levaraged to attract them to active modes, but could also as a result lead to gains in wellbeing.
+
+With respect to opportunities for future research, a possible extension of the present research would be to investigate the use of the modes other than the typical mode of transportation.
+In a recent paper that investigated commute satisfaction for car users, Al-Ayyash and Abou-Zeid [-@Alayyash2019commute] considered three models: for current trip satisfaction, remembered satisfaction while using public transport, and current satisfaction using public transport.
+The findings suggest that low service quality in public transportation can result in a generalized negative perception, and that this perception is more difficult to smooth if commuters do not regularly use public transport.
 Another avenue for future research could be to consider the mix of modes typically used.
-While in this paper the analysis focused on the primary mode of transportation, many travellers experience more than one mode of transportation in their daily activities.
-For this reason, considering the multimodal component of travel would be interesting; for example, future research could consider people who eventually arrive by bicycle to the metro station or people that, after using a colectivo for part of a trip, end their journey by bus.
+While in this paper the analysis focused on the primary mode of transportation, many travelers experience more than one mode of transportation in their daily activities.
+For this reason, considering the multimodal component of travel would be interesting; for example, future research could consider people who eventually arrive by bicycle to the metro station or people that, after using a _colectivo_ for part of a trip, end their journey by bus.
 
@@
 
+We wish to express our gratitude to Prof.
+Jonas De Vos and three anonymous reviewers for their feedback on an earlier version of this paper.
+Their suggestions helped to improve the quality of the research and the clarity of the presentation.
 The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `ggmosaic` [@Jeppson2019ggmosaic], `ggthemes` [@Arnold2018], `kableExtra` [@Zhu2018], `knitr` [@Xie2015; @Xie2018], `rticles` [@Allaire2018rticles], and `tidyverse` [@Wickham2017].

### 2020-08-14 Dissonance_Santiago_v2/Dissonance_Santiago_v2.tex
v2 BLM and AP revisions

@@
 \usepackage[hyphens]{url}
+
+  \journal{Journal of Transport \& Health} % Sets Journal name
 
@@
             pdfauthor={},
-            pdftitle={Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing},
+            pdftitle={Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Affective Values},
             colorlinks=false,
@@
   \title{Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance
-from the Perspective of Subjective Wellbeing}
+from the Perspective of Affective Values}
     \author[Some University]{Author 1\corref{Corresponding Author}}
@@
   \begin{abstract}
-  \textbf{Introduction}\\
+  \emph{Introduction}\\
   Subjective wellbeing is a topic that has attracted considerable
-  attention in recent years due to the way it correlates with health. From
-  a transportation perspective, there is a burgeoning literature on the
-  way travel can impact subjective wellbeing, and how this, in turn, can
-  influence behavior.\\
-  \textbf{Objective}\\
-  The objective of this paper is to analyze a number of affective values
-  associated with subjective wellbeing and the modes of transportation
-  that people commonly use. In particular, we are interested in the
-  potential for dissonance with respect to the primary mode of travel.\\
-  \textbf{Materials and Methods}\\
-  The study is based on data collected from a sample of travellers in the
+  attention in the transportation literature in recent years. As a result,
+  there is a burgeoning literature that investigates the impacts of travel
+  on subjective wellbeing, and how wellbeing, in turn, can influence
+  behavior. An important aspect of subjective wellbeing are the affective
+  reactions of people to their experiences.\\
+  \emph{Objective}\\
+  The objective of this paper is to analyze the affective reactions of
+  travelers with respect to various modes of transportation. In
+  particular, we are interested in the potential for dissonance between
+  primary mode of travel and the mode(s) of travel identified as evoking
+  various affective reactions.\\
+  \emph{Materials and Methods}\\
+  The study is based on data collected from a sample of travelers in the
   city of Santiago, in Chile. Participants in the study were asked about
-  their usual mode of travel, and then were asked to name the mode or
-  modes that they associate with the affective values of freedom,
-  enjoyment, happiness, poverty, luxury and status. Analysis is based on
-  tests of independence and visualization via mosaic plots.\\
-  \textbf{Results}\\
+  their usual mode of travel, and then were asked to name their ideal
+  mode(s) of transportation from the perspective of various affective
+  reactions. The reactions we investigate are associated with the values
+  of freedom, enjoyment, happiness, poverty, luxury, and status. Analysis
+  is based on tests of independence and visualization techniques.\\
+  \emph{Results}\\
   The results indicate that users of public transportation experience the
-  most dissonance in terms of affective values, and active travellers the
-  least. For those travellers who experience dissonance, active travel is
-  the mode most commonly associated with freedom, enjoyment, and
-  happiness, public transportation is most commonly associated with
-  poverty, and the automobil is most commonly associated with luxury and
-  status.
-
-  journal: ``Journal of Transportation \& Health''
+  most dissonance in terms of affective reactions, and active travelers
+  the least. For those travelers who experience dissonance, active travel
+  is the mode most commonly associated with freedom, enjoyment, and
+  happiness, whereas public transportation is most commonly associated
+  with poverty. The automobile, in contrast, is the mode most commonly
+  associated with luxury and status.
   \end{abstract}
@@
 (Angotti, 1996; Brown et al., 2009). Despite the initial promise of
-automotive technology, it is now evident that mobility centred on the
+automotive technology, it is now evident that mobility centered on the
 private automobile has given rise to a litany of maladies that are in
@@
 
-As the real impacts of our societal dependence on the private
-autombobile have become increasingly evident, the transportation agenda
-has aimed to shift focus to the reduction of car use and towards the
-creation of mobility polycultures that offer a broader menu of
-transportation alternatives than primarily (or even just) the private
-automobile (Miller, 2011). In order to successfully achieve this goal,
-it is essential not only to provide the services and facilities that
-support public transportation and active travel, but also to attract new
-users to these modes of transportation (Ettema et al., 2011). Within
-this context, it has been argued that sustainable transportation
-policies require all participants in the transportation system to
-challenge what Gossling and Cohen (2014) termed \emph{transportation
-taboos}: deep-seated ideas concerning the contribution to emissions by
-individuals, the inequality of market-based approaches, and the social
-and psychological functions of transportation. With respect to the
-latter, it is important to move beyond a purely utilitarian focus if we
-are to understand how the affective value of the transportation
-experience can be leveraged to improve alternative transportation -
-particularly transit and active modes (Anable and Gatersleben, 2005;
-Domarchi et al., 2008; Gatersleben and Uzzell, 2007; Steg, 2005).
-
-A useful lens to investigate the social and psychological functions of
-transportation is by means of the concept of subjective wellbeing (SWB;
-see, inter alia, De Vos et al., 2013; and Chatterjee et al., 2019). SWB
-is defined by the OECD as ``{[}g{]}ood mental states, including all of
-the various evaluations, positive and negative, that people make of
-their lives, and the affective reactions of people to their
-experiences'' (OECD, 2013, p. 10). As memorably put by Steg (2005): is
-the use of car a must, or is it a lust? A close alignment, or
-consonance, between affective values and the mode of transportation used
-to travel can result in greater subjective wellbeing and increase the
-probability of choosing that mode (i.e., by satisfying the \emph{lust});
-on the other hand, dissonance, that is, the lack of concordance between
-the mode used and affective values would be detrimental to subjective
-wellbeing, especially of those for whom the use of the mode is a
-\emph{must} (De Vos, 2019; Mokhtarian and Pendyala, 2018). With these
-considerations in mind, one aim of the present research is to
-investigate \emph{who} experiences dissonance with respect to their
-primary mode of travel and affective values, namely freedom, enjoyment,
-happiness, feelings of poverty, luxury, and status. Furthermore, it is
-possible, even if use of a particular mode is a \emph{must}, that
-travellers may still \emph{lust} for something else - in other words,
-the grass may in fact look greener from the window of the car. For this
-reason, we also aim to investigate which mode or modes are most commonly
-associated with affective values, with a focus on those travellers who
-experience dissonance in their primary mode.
-
-Research is based on data collected from a sample of travellers in the
-city of Santiago in Chile. Survey respondents were asked about their
-primary mode of travel, and also about the mode or modes that they
-associate with the affective values mentioned above. The paper
-contributes to the literature in three ways, as follows:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  The research reported here contributes to an emerging literature on
-  the topic of transportation and affective values in the context of the
-  Global South (Al-Ayyash and Abou-Zeid, 2019; Bejarano et al., 2017;
-  Shao and Liang, 2019; Van et al., 2014; Zorrilla et al., 2019); to the
-  best of our knowledge, the case of Chile has not yet been reported.
-\item
-  Although there is an extensive literature on the enjoyment of commute
-  and other affective values (see for instance Paez and Whalen, 2010;
-  Redmond and Mokhtarian, 2001; Whalen et al., 2013; Ye and Titheridge,
-  2017), from a hedonic and even eudaimonic perspectives the analysis
-  has yet to be applied more fully in terms of distributional issues --
-  i.e.~which groups more commonly experience dissonance (see De Vos,
-  2018).
-\item
-  The analysis shows the attitudes of people towards their primary mode
-  and their perception towards `ideal modes' -- implying their
-  preferences, even in situations when their ideal mode is not part of
-  their actual choice set. More concretely, the results indicate that
-  users of public transportation experience the most dissonance in terms
-  of affective values, and active travellers the least. For those
-  travellers who experience dissonance, active travel is the mode most
-  commonly associated with freedom, enjoyment, and happiness, public
+As the impacts of our societal dependence on the private automobile have
+become increasingly evident, the transportation agenda has aimed to
+shift focus to the reduction of car use and towards the creation of
+mobility polycultures that offer a broader menu of transportation
+alternatives other than primarily (or even just) the private automobile
+(Lavery et al., 2013; Miller, 2011). In order to successfully achieve
+this goal, it is essential not only to provide the services and
+facilities that support public transportation and active travel, but
+also to attract new users to these modes of transportation (Ettema et
+al., 2011). Within this context, it has been argued that sustainable
+transportation policies require all participants in the transportation
+system to challenge what Gossling and Cohen (2014) termed
+\emph{transportation taboos}: deep-seated ideas concerning the
+contribution to emissions by individuals, the inequality of market-based
+approaches, and the social and psychological functions of
+transportation. With respect to the latter, subjective wellbeing (SWB)
+is increasingly recognized as a policy goal in and of itself (Diener et
+al., 2015; Dolan and Metcalfe, 2012), and also as an intermediate
+objective to achieve ulterior goals. Accordingly, there is a growing
+consensus in the field of transportation about the need to move beyond a
+purely utilitarian focus to understand the affective and wellbeing
+values of the transportation experience (e.g., Anable and Gatersleben,
+2005; De Vos et al., 2013; Domarchi et al., 2008; Gatersleben and
+Uzzell, 2007; Steg, 2005). Consideration of factors related to
+subjective wellbeing, for example, are useful for policy-makers to
+enhance the experience of travel, to increase satisfaction with travel,
+and to meet the preferences of travelers (Chatterjee et al., 2019).
+
+A definition of subjective wellbeing is as ``{[}g{]}ood mental states,
+including all of the various evaluations, positive and negative, that
+people make of their lives, and the affective reactions of people to
+their experiences'' (OECD, 2013, p. 10). As memorably put by Steg
+(2005): is the use of a car a must, or is it a lust? A close alignment,
+or consonance, between affective reactions and the mode of
+transportation used to travel can result in greater subjective wellbeing
+and increase the probability of choosing that mode (i.e., by satisfying
+the \emph{lust}); on the other hand, dissonance, namely the lack of
+concordance between the mode used and the affective reaction to that
+mode, would be detrimental to subjective wellbeing, especially to those
+for whom the use of the mode is a \emph{must} (De Vos, 2019; Mokhtarian
+and Pendyala, 2018). With these considerations in mind, the present
+research aims to investigate \emph{who} experiences affective dissonance
+with respect to their primary mode of travel. We focus our investigation
+on reactions from the perspective of feelings of freedom, enjoyment,
+happiness, poverty, luxury, and status - concepts termed \emph{affective
+values} hereafter. Furthermore, it is possible, even if use of a
+particular mode is a \emph{must}, that travelers may still \emph{lust}
+for something else - in other words, the grass may look greener from the
+window of a car. For this reason, we also aim to investigate which mode
+or modes are most commonly identified as ideal from the perspective of
+the aforementioned affective values.
+
+Our research is based on data collected from a sample of travelers in
+the city of Santiago in Chile. The analysis sheds light on the affective
+reactions of people towards their primary mode of travel, and their
+perceptions towards `ideal modes'. This reveals important differences in
+situations when the ideal mode of a traveler is not the mode they
+actually use - or in other words, the affective dissonance between
+actual and ideal modes of travel. More concretely, the results indicate
+that users of public transportation experience the most dissonance,
+followed by automobile users, and finally active travelers, who tend to
+experience the least affective dissonance. For those travelers who
+experience dissonance, active travel is the mode most commonly
+associated with freedom, enjoyment, and happiness, whereas public
 transportation is most commonly associated with poverty, and the
-  automobil is most commonly associated with luxury and status. We also
-  find that there are some substantial variations in dissonance by age,
-  education, income, and typical commute time. The attitudes of
-  travellers towards transport modes are critical factors to be
-  considered by policy-makers in case they want to promote and increase
-  the use of public transport or active modes (Bornioli et al., 2019; De
-  Vos et al., 2019; De Vos and Witlox, 2017; Garling et al., 2019;
-  Redman et al., 2013).
-\end{enumerate}
-
-The structure of the paper is as follows. After these introductory
-remarks, we follow up with a background section that reviews the
-literature. Next, we discuss the case study and data used in the
-research. Then, the analysis and results are presented, before
-concluding with some discussion and directions for future research.
+automobile is most commonly associated with luxury and status. We also
+find that there are significant variations in dissonance by age,
+education, income, and typical commute time. The reactions of travelers
+towards various transport modes are critical factors that policy-makers
+need to consider to promote and increase the use of public transport and
+active modes (Bornioli et al., 2019; De Vos et al., 2019; De Vos and
+Witlox, 2017; Garling et al., 2019; Redman et al., 2013).
+
+After these introductory remarks, the paper follows up with a review of
+the literature on the topics of subjective wellbeing and affective
+values. Next, we discuss the case study, as well as the methodology and
+data used for this research. The analysis and results of the study are
+presented afterwards, before concluding with some discussion and
+directions for future research and policy.
+
+Please note that this document was prepared using R Markdown and is an
+example of reproducible research (Brunsdon and Comber, 2020). The R
+Markdown file, along with the data file needed to reproduce the
+analysis, are available for
+download\footnote{\url{https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg}}.
 
@@
 
-A consensus has emerged in the transportation community regarding the
-need to complement the traditional utilitarian perspective of
-transportation by looking at mobility and transport issues from the lens
-of their affective functions. The affective value of transportation in
-turn is important due to its potential to improve or detract from SWB.
-One of the primary ways to explore this has been the satisfaction that
-travelers feel towards their every day mobility experience (e.g.,
-Cecilia Jakobsson Bergstad et al., 2011). As a consequence, there is a
-wealth of research on satisfaction with the use of different modes of
-transportation. For example, numerous studies report that car users
-often have a higher level of satisfaction compared to other transport
-modes (C. J. Bergstad et al., 2011; Eriksson et al., 2013; Redmond and
-Mokhtarian, 2001; Whalen et al., 2013; but see Handy and Thigpen, 2019).
-In a similar way, there are multiple reports that active travel also
-tends to yield high levels of satisfaction (Gatersleben and Uzzell,
-2007; Handy and Thigpen, 2019; Paez and Whalen, 2010; Smith, 2017;
-St-Louis et al., 2014; Whalen et al., 2013), In contrast, public
-transport users tend to assess their experience more negatively (Abenoza
-et al., 2017; De Vos et al., 2016; Gatersleben and Uzzell, 2007; Handy
-and Thigpen, 2019; Paez and Whalen, 2010). Multi-modal trips also
-influence satisfaction levels; for instance, when an individual chooses
-a particular mode of transportation, she will report a higher level of
-satisfaction with that chosen mode -- perhaps as a form of \emph{post
-hoc} validation (Susilo and Cats, 2014).
-
-While the use of travel satisfaction has been mainly used in the context
-of daily trips -- typically linked to cost-benefit and utilitarian
-measurements --, the evaluation of Subjective Wellbeing (SWB) over time
-has risen as an alternative measure. In the field of travel behaviour,
-Ettema et al.~(2010, p. 725) define SWB as the degree to which an
-individual positively evaluates the overall quality of their lives,
-where the general life satisfaction encompasses a more extended
-temporality -- which implies assuming a tendency to be more stable over
-time. This concept has prompted a growing literature that complements
-and applies SWB in a broader range of satisfaction scales and
-situations. The definition of other factors such as travel choice mode,
-attitudes and external elements of the built environment have been
-studied for a broader understanding of the changes produced in the SWB
-(e.g., Handy and Thigpen, 2019). As these factors do not necessarily
-apply to the general life satisfaction on the long term, the studies
-have aimed to determine both the direct and indirect effects on the
-perception of users (see, e.g., Ye and Titheridge, 2017). Other concepts
-have also emerged as the Satisfaction with Travel Scale (STS), a
-measurement devised by Ettema et al.~(2011), as well as different scales
-based on people's travel perceptions. De Vos et al.~(2015), for
-instance, explore in detail the underlying dimensions of the affective
-domain of STS on which SWB is based (for more on STS see also Friman et
-al., 2013).
-
-Recent literature on SWB and its link with transport have demonstrated a
-relationship between people's perceptions and satisfaction with their
-daily travel (e.g., Smith, 2017; Mokhtarian and Pendyala, 2018; St-Louis
-et al., 2014). Scholars have shown that accessibility has been the most
-developed factor that influences people's wellbeing (Delbosc, 2012), and
-activities have a direct impact on travel satisfaction (Cecilia
-Jakobsson Bergstad et al., 2011). Delbosc (2012, p. 28), for instance,
-has summarised the most significant influences on psychological
-wellbeing: poverty and employment, meaningful relationships and health.
-However, understanding the components affecting people's perceptions
-implies the differentiation between affective (also named as
-symbolic-affective) and instrumental values (C. J. Bergstad et al.,
-2011). Steg et al.~(2011) have compared symbolic-affective opposed to
-instrumental-reasoned motives based on car-use, and other studies have
-also found associations between affective and symbolic aspects of
-car-use (see, e.g., Gatersleben and Uzzell, 2007; Lois and Lopez-Saez,
-2009). Previous studies have also demonstrated how socio-demographic
-factors affect the levels of SWB. The effect of income on SWB (Clark and
-Oswald, 1996; Ferrer-i-Carbonell, 2005); education and unemployment
-(Argyle et al., 1999); age (Diener and Eunkook Suh, 1997), and gender
-(Tesch-Römer et al., 2008) have been extensively studied. Recent
-research also suggests the links between commuting, SWB and emotional
-wellbeing assessment (\textbf{Olson et al.~2013}; \textbf{Kahneman et
-al.~2004}). However, more research is needed to understand how these
-socio-demographic variables connect as well with the affective responses
-to mode of travel (St-Louis et al., 2014).
-
-The research needs already recognized in the developed world are also
-markedly acute in the context of the Global South, where historical
-inequality has tended to create a symbolic attachment to the automobile,
-in addition to negative connotations for public transport and active
-travel (Zorrilla et al., 2019). In this way, there is an emerging
-literature that investigates affective factors in travel behaviour in a
+A consensus has emerged in recent years regarding the need to complement
+the traditional utilitarian perspective of transportation by
+investigating mobility and transport from the lens of their affective
+functions. The affective value of transportation is important due to its
+potential to improve or detract from SWB.
+
+One of the primary ways to explore issues of subjective wellbeing in
+transportation has been the satisfaction that travelers feel towards
+their everyday mobility experience (e.g., Cecilia Jakobsson Bergstad et
+al., 2011). As a consequence, there is a wealth of research on
+satisfaction with the use of different modes of transportation. For
+example, numerous studies report that car users often have a higher
+level of satisfaction compared to other transport modes (C. J. Bergstad
+et al., 2011; Eriksson et al., 2013; Redmond and Mokhtarian, 2001),
+although others report highest commute satisfaction for bicycle and
+train commuters (e.g., Whalen et al., 2013; Handy and Thigpen, 2019). In
+a similar way, there are multiple reports that active travel also tends
+to yield higher levels of satisfaction (Gatersleben and Uzzell, 2007;
+Handy and Thigpen, 2019; Paez and Whalen, 2010; Smith, 2017; St-Louis et
+al., 2014; Whalen et al., 2013), In contrast, public transport users
+often assess their experience more negatively (Abenoza et al., 2017; De
+Vos et al., 2016; Gatersleben and Uzzell, 2007; Handy and Thigpen, 2019;
+Paez and Whalen, 2010). Multi-modal trips also influence satisfaction
+levels; for instance, individuals tend to report higher levels of
+satisfaction with the mode they use -- perhaps as a form of \emph{post
+hoc} validation of their choices or circumstance (Susilo and Cats,
+2014).
+
+While travel satisfaction has often been used in the context of daily
+trips -- typically linked to cost-benefit and utilitarian measurements
+--, the evaluation of subjective wellbeing (SWB) over time has risen as
+an alternative measure. Ettema et al.~(2010, p. 725) define SWB as the
+degree to which an individual positively evaluates the overall quality
+of their lives, where the general life satisfaction encompasses a more
+extended temporal period -- which implies greater temporal stability.
+This concept has prompted a growing literature that complements and
+applies SWB in a broader range of satisfaction scales and situations.
+The definition of other factors such as travel choice mode, attitudes,
+and external elements of the built environment have been studied for a
+broader understanding of the changes produced in the SWB (e.g., Handy
+and Thigpen, 2019). As these factors do not necessarily apply to
+longer-term general life satisfaction, other studies have aimed to
+determine both the direct and indirect effects on the perception of
+users (see, e.g., Ye and Titheridge, 2017). Other concepts have also
+emerged, including the Satisfaction with Travel Scale (Ettema et al.,
+2011), as well as different scales based on people's perceptions of
+travel. De Vos et al.~(2015), for instance, explore in detail the
+underlying dimensions of the affective domain of STS on which SWB is
+based (for more on STS also see Friman et al., 2013).
+
+The literature on SWB has demonstrated a relationship between people's
+perceptions and satisfaction with their daily travel (e.g., Smith, 2017;
+Mokhtarian and Pendyala, 2018; St-Louis et al., 2014). Scholars have
+shown that accessibility is among the most studied factors that
+influences subjective wellbeing (Delbosc, 2012), and activities have a
+direct impact on travel satisfaction (Cecilia Jakobsson Bergstad et al.,
+2011). Delbosc (2012, p. 28), for instance, has summarized the most
+significant influences on psychological wellbeing: poverty and
+employment, meaningful relationships and health. However, understanding
+the components that affect these perceptions implies the differentiation
+between affective (also named as symbolic-affective) and instrumental
+values (C. J. Bergstad et al., 2011). Steg et al.~(2011) have compared
+symbolic-affective and instrumental-reasoned motives for car-use, and
+similar findings are reported in other studies (e.g., Gatersleben and
+Uzzell, 2007; Lois and Lopez-Saez, 2009). Previous research also
+demonstrates how socio-demographic factors affect the levels of SWB,
+includin income (Clark and Oswald, 1996; Ferrer-i-Carbonell, 2005),
+education and unemployment (Argyle et al., 1999), age (Diener and
+Eunkook Suh, 1997), and gender (Tesch-Römer et al., 2008). However,
+further research beyond the determinants of trip satisfaction is needed
+to understand how these socio-demographic variables connect with the
+affective reactions to various modes of travel (St-Louis et al., 2014).
+
+The research needs outlined above are well-recognized in the developed
+world, but there is still a dearth of research in the context of the
+Global South. Historical inequality in many developing countries has led
+to strong symbolic attachments to the automobile, in addition to
+negative connotations for public transport and active travel (Zorrilla
+et al., 2019). To address this gap in knowledge a body of literature has
+emerged to investigate the affective aspects of travel behavior in a
 number of developing countries. A cross-country study in Asia revealed
@@
 and planning is further highlighted by research in Colombia that shows
-how users felt proud using a bicycle shared system, in addition to
-experiencing feelings of belonging to a civic culture and the enjoyment
-and pleasure of travel itself (Bejarano et al., 2017). This paper
-contributes to further our understanding of affective values in travel
-behaviour in a developing country.
+the pride users feel when using a bicycle shared system. This affective
+reaction is above and beyond other positive feelings, such as a sense of
+belongingness to a civic culture, and the enjoyment and pleasure of
+active travel itself (Bejarano et al., 2017).
 
@@
 
-The case study to contextualize the discussion is Santiago de Chile, the
-capital of one of the countries with the highest levels of inequality in
-terms of socio-economic distribution in the world. These inequities have
-manifested in a disproportionate expense in transport by the different
-socioe-conomic sectors, a disproportion in travel times and distances
-travelled. On the other hand, car ownership and use of public transport
-in the capital are directly conditioned by strong spatial segregation --
-the higher the income, the higher is the use of the automobile;
-conversely, and the lower the income, the higher is the predisposition
-to use public transport. Although transport is a reflection of deep
-inequities in various dimensions, it has triggered an exceptional
-discomfort and disagreement with the daily travel experience and quality
-of life.
-
-\hypertarget{sample}{%
-\subsection{Sample}\label{sample}}
+The case study for the present research is Santiago. Santiago is the
+capital of Chile, a country with one of the highest levels of
+socio-economic inequality in the world. A tangible manifestation of the
+inequalities experienced by many in Chile is the large disparity in the
+relative cost of transportation, travel time, and distance traveled by
+different socio-economic segments of the population. To further
+complicate matters, strong spatial segregation also conditions car
+ownership and the use of public transportation -- the higher the income,
+the higher the use of the automobile; conversely, the lower the income,
+the higher the reliance on public transportation. Although the
+transportation experience is but one of many dimensions of inequality,
+the experiences in this sector have triggered exceptional discomfort and
+dissatisfaction among the public. Recent social unrest, triggered by a
+seemingly minor hike in the fare of public transportation, has brought
+many of these concerns to the forefront of the public conscience in
+dramatic fashion (e.g., Davies, 2019; {\textbf{???}}; {\textbf{???}}).
+
+Previous research has helped to contextualize everyday mobility in
+Santiago relative to other Latin American cities (e.g., Avellaneda and
+Lazo, 2011; Rodríguez Vignoli, 2008), but much remains to be explored.
+Measuring instruments and new methods have led to more accurate and
+precise understandings of the social issues that arise as consequence of
+transport infrastructure and housing provision (Cox and Hurtubia, 2016),
+and the minimum provision of basic services (Tiznado-Aitken et al.,
+2016). However, the focus on accessibility as a measure of inequalities
+remains predominant ({\textbf{???}}; Martínez et al., 2018; Niehaus et
+al., 2016; Rojas et al., 2016).
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
 
 The study is based on a survey conducted in the city of Santiago during
-the months of November and December 2016, that is, the end of the Spring
-and beginning of Summer. The survey collected information on a wide
-range of travel and related issues. The data collection considered a
-quota-sampling method for gathering the information, considering the
-socio-demographic information from Pre-Census of 2012. An equal
-representation of both genders and a representation of the proportion of
-inhabitants per area were chosen as relevant characteristics of the
-sample. In total, there were \(n=451\) valid surveys, although not every
-survey was complete and there were missing responses for some answers.
-
-The survey was structured in eight sections, as follows: 1) Individual
-characteristics of respondent; 2) Health; 3) Feelings and emotions; 4)
-Reasons for travel and planning travel; 5) Social interaction; 6) Nature
-and sustainability; 7) Information and telecommunications; 8) Built
-environment; and 9) Commuting. For the present study, we draw data from
-sections 1), 3) and 9). In terms of individual characteristics of the
-respondents and their commute, participants were asked about basic
-socio-demographic information, including age, level of education,
-income, and the typical duration of their regular commute. The
-descriptive statistics of the sample appear in Figure
-\ref{fig:descriptive-statistics}. The sample tends to be younger, and
-well-educated, with an almost uniform distribution of income levels. The
-trend in typical commute time is towards longer commutes.
+the months of November and December of 2016, at the end of the Spring
+and beginning of Summer seasons. The survey collected information on a
+wide range of transportation and related issues, and the data collection
+protocol considered a quota-sampling method for gathering the
+information, considering the socio-demographic information from
+Pre-Census of 2012. The survey was carried out face-to-face in centers
+of activity with dense provision of offices, services, and educational
+centers. An equal representation of both genders and a representation of
+the proportion of inhabitants per area were chosen as relevant
+characteristics of the sample. In total, there were \(n=451\) valid
+reponses, although not every response was complete and some questions
+have missing values.
+
+The study considers data from 3 out of 8 sections of a longer survey.
+The relevant sections of the survey concern the individual
+characteristics of respondents, their feelings and affective responses
+related to their commute, and aspects describing their regular commute
+trips. In terms of individual characteristics and their commute,
+participants were asked socio-demographic information, including age
+(coded in three classes: younger than 35, older than 35 but younger than
+55, and 55 and olde); level of education (three classes: Kindergarden to
+grade 12, or K-12, technical diploma or university graduate, and
+graduate degree), income (three classes, by tertile), and the typical
+duration of the respondent's regular commute (four classes, by duration
+in minutes). The descriptive statistics of the sample appear in Figure
+\ref{fig:descriptive-statistics}. The sample trends to younger (56\% is
+younger than 34 years old) and well-educated respondents (68\% of
+respondents having technical or professional education), with an almost
+uniform distribution of income levels. The trend in typical commute time
+is towards longer commutes -- e.g.~55\% of the trips are longer than 40
+minutes, and from those 56\% corresponds to trips over the 60 minutes
+long.
 
@@
 In addition, respondents were asked about their primary mode of travel
-for their regular commute. The modes available were Car, Taxi, Colectivo
-(a form of shared ride, intermediate in flexibility and capacity between
-taxi and bus); Motorcycle; Metro; Bus; Bicycle; Walking. As seen in the
-top panel of Figure \ref{fig:primary-mode-travel}, the three most common
-modes of travel are Metro, Bus, and Car, followed by Walking and Biycle.
-For the analysis, we aggregate these modes into the following categories
-(bottom panel of Figure \ref{fig:primary-mode-travel}): Car, Active
-(Walking + Bicycle), Public (Metro + Bus), and Other (Taxi + Colectivo +
-Motorcycle).
+for their regular commute. The modes available were Car; Taxi;
+\emph{Colectivo} (a form of shared ride, intermediate in flexibility and
+capacity between taxi and bus); Motorcycle; Metro; Bus; Bicycle; and
+Walking. As seen in the top panel of Figure
+\ref{fig:primary-mode-travel}, the three most common modes of travel are
+Metro, Bus, and Car, followed by Walking and Bicycle. For the analysis,
+we aggregate these modes into the following categories (bottom panel of
+Figure \ref{fig:primary-mode-travel}): (26\% of total modes -- which
+corresponds to 91\% of the total of private motorized modes), Active
+(9\% - Walking + Bicycle), Public (60\% - Metro + Bus), and Other
+motorized modes (6\% - Taxi + Colectivo + Motorcycle).
 
@@
 Of particular interest for the present study is the following question
-in Part 3) of the survey:
+in Part 3 of the survey:
 
@@
 respondents were not constrained to select only one alternative, but
-could indicate by means of a checkbox any and all modes that they felt
-aligned with each affective value. This allows us to do an analysis of
-modal dissonance, a concept introduced into the transportation
+could indicate by means of checkboxes any and all modes that they felt
+aligned with each affective value. This allows us to analyze the mode
+dissonance. Dissonance is a concept introduced into the transportation
 literature by Schwanen and Mokhtarian (2004) based on earlier work by
-Feldman (1990). Residential neighborhood-type dissonance was defined by
-Schwanen and Mokhtarian (2004) as an incongruence in terms of the the
-land use patterns at the place of residence of an individual, and the
-individual's preferences. The concept of dissonance has since been
-extended in the travel behavior literature to encompass the mismatch
-between the choices individuals make, and the alternatives that would
-enable users to experience affective or instrumental values. This
-includes, for example, travel mode dissonance (De Vos, 2018).
+Feldman (1990). Originally used to investigate residential dissonance
+(Schwanen and Mokhtarian, 2004), the concept has since been extended in
+the travel behavior literature to encompass the mismatch between the
+choices individuals make, and the alternatives that would enable users
+to improve their experience. This includes, for example, travel mode
+dissonance (De Vos, 2018).
 
@@
 according to the following rule: \[
-D_i = 
+D_{ij} = 
 \begin{cases}
-0 & if \text{ primary mode} = \text{mode associated with value } i\\
+0 & if \text{ primary mode of traveler }i == \text{mode associated with value } j\\
 1 & \text{ otherwise}
 \end{cases}
-\] Therefore, if a respondent's primary mode of travel is Car, but
-indicated any other mode or modes in relation to Freedom, the respondent
+\] Therefore, if respondent \(i\) travels primarily by Car, but
+indicated any other mode(s) in relation to Freedom, the respondent
 experienced dissonance: \[
-D_{\text{Freedom}} = 1
+D_{i,\text{Freedom}} = 1
 \]
 
-Furthermore, we also expanded the responses to account for all modes
-identified by respondents in relation to the affective values. However,
-to avoid double counting the respondents in our frequency tabulations,
-we also calculated a sample weight that was the inverse of the number of
-modes selected in response to each affective value. For instance, if a
-respondent selected two modes in relation to affective value \(i\), the
-two modes receive a weight of \(1/2\); if a respondent selected three
-modes, then their weights are \(1/3\); and so on. In this way we do not
-treat unfairly those who selected only one mode, and the sum of all
-weighted modes is equal to the sample size.
-
-\hypertarget{analysis-and-results}{%
-\section{Analysis and Results}\label{analysis-and-results}}
-
-In what follows, analysis is done on two related but distinct questions.
-The first part of the analysis seeks to understand \emph{who}
-experiences dissonance, and the second part, building off that, aims to
-explore which modes of travel are more commonly identified as embodying
-affective values by those travellers who experience dissonance.
-
-Please note that this document was prepared using R Markdown and
-contains reproducible analysis. The R markdown file, along with the data
-file needed to reproduce the analysis, can be downloaded from the
-following anonymous Drive folder:
-
-https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg
+In these calculations we account for all modes identified by respondents
+in relation to the affective values. Therefore, to avoid double counting
+the respondents in our frequency tabulations, we also calculated a
+sample weight as the inverse of the number of modes selected in response
+to each affective value. For instance, for respondents who selected two
+modes in relation to affective value \(j\), each of these two modes
+receive a weight of \(w_{ij}=1/2\); if a respondent selected three
+modes, then their weights are \(w_{ij}=1/3\); and so on. In this way we
+do not treat unfairly those respondents who selected only one mode, and
+the sum of all weighted responses is equal to the size of the sample
+\(n\).
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+In what follows, the results refer to two related but distinct
+questions. The first part of the analysis seeks to understand \emph{who}
+experiences dissonance, whereas the second part, building off that, aims
+to explore \emph{which modes} are more commonly identified as embodying
+affective values by those travelers who experience dissonance.
 
@@
 
-To investigate the first question in our analysis, we create contingency
-tables that tabulate the frequency of dissonance with respect to each
-affective value, stratified by the attributes of Age, Education, Income,
-Primary Mode of Travel, and typical Commute Time. Table
-\ref{tab:cross-tabulation-results} presents the frequency (in
-percentage) of dissonance, in other words, the percentage of respondents
-out of the total in their stratum who indicated mode or mode(s) for the
-affective value that do not correspond to their primary mode of travel.
-
-As seen in the table, there are five characteristics of the respondents
-and their commutes that we use in the analysis. Three of these
-categories are socio-economic and demographic, namely age, level of
-education, and income. The other two are transportation related, namely
-primary mode of travel and commute time. The frequency tables were
-tested in every case by means of the \(\chi^2\) test of independence
+We begin by profiling the travelers who experience dissonance. The null
+hypothesis is that there are no systematic differences in terms of who
+tends to experience affective dissonance with respect to their primary
+mode of travel. To investigate this hypothesis we create contingency
+tables to tabulate the frequency of dissonance with respect to each
+affective value, stratified by the individual attributes of respondents.
+Table \ref{tab:cross-tabulation-results} presents the frequency (in
+percentage) of dissonance. This is the percentage of respondents out of
+the total in their stratum who selected, for each affective value, a
+mode or mode(s) of transportation that do not correspond to their
+primary mode of travel.
+
+As seen in the table, there are five individual attributes that we
+analyze. Three of these are socio-economic and demographic, namely age,
+level of education, and income. The other two are transportation
+related, namely primary mode of travel and commute time. The frequency
+tables are tested in every case using \(\chi^2\) tests of independence
 (\(p\)-values are reported in the table; lower \(p\)-values mean that
@@
 
-With respect to Age, previous studies have reported that older adults
+With respect to age, previous studies have reported that older adults
 tend to be more satisfied with their travel experience than younger
 people (Cao and Ettema, 2014; De Vos et al., 2016; Ye and Titheridge,
-2017). In the case, we find that five affective values show dissonance
-that significantly deviates from the null hypothesis of independence,
-namely Freedom, Enjoyment, Happiness, Luxury, and Status. We observe
-that levels of dissonance tend to be high in general, and in no case
-less than 60\%. For instance, almost 90\% of travellers younger than 35
+2017). In the case, we find that there there are significant differences
+in dissonance by age with respect to five affective values, namely
+Freedom, Enjoyment, Happiness, Luxury, and Status. We observe that
+levels of dissonance tend to be high in general, and in no case less
+than 60\%. For instance, almost 90\% of travelers younger than 35
 experience travel mode dissonance with respect to Freedom, and more than
-94\% experience dissonance with respect to enjoyment. In general,
-younger travellers tend to experience dissonance more frequently, with
-dissonance being less frequent for older travellers. The exception to
-this trend is Luxury, an affective value for which older travellers (age
+94\% experience dissonance with respect to Enjoyment. In general,
+younger travelers tend to experience dissonance more frequently, with
+dissonance being less frequent for older travelers. The exception to
+this trend is Luxury, an affective value for which older travelers (age
 \textgreater54) experience dissonance more frequently than mid-aged
-travellers (ages 35-54).
+travelers (ages 35-54).
 
@@
 
-When seen from the perspective of Education, the results do not support
-the hypothesis of significant differences in the frequency of dissonance
-by levels of education for the values of Freedom, Enjoyment, Happiness,
-and Poverty, and only two affective values show significant differences
-between education levels: Luxury and Status. In the case of Luxury,
-dissonance is more frequent among people who have only K-12 education,
-and less frequently, albeit still high, for people with
+The results do not allow us to reject the hypothesis of equal levels of
+dissonance by levels of education for the values of Freedom, Enjoyment,
+Happiness, and Poverty. In contrast we can reject the null hypothesis in
+the case of two affective values, namely Luxury and Status. In the case
+of Luxury, dissonance is more frequent among people who have only K-12
+education, and less frequently, albeit still high, for people with
 technical/university level education and post-graduate education.
@@
 
-The next variable we examine is income, and in this case three affective
-values are significant: Poverty, Luxury, and Status. Since Poverty is a
-negative affect, we see here that lower income people tend to associate
-this feeling to their primary mode of commuting more frequently (almost
-20\% of the time) than other income groups. For example, whereas
-approximately 16\% of mid-income people are dissatisfied with their
-primary mode of travel in this respect, less than 7\% of high income
-individuals are. Dissonance with respect to Luxury and Status also tends
-to be more common among lower income people, and declines substantially
-for mid- and high income respondents. Notice as well that the frequency
-of dissonance is higher in terms of Luxury than Status for mid- and high
-income people.
+The next individual attribute that we examine is income, and in this
+case we detect significant differences in dissonance for three affective
+values: Poverty, Luxury, and Status. Since Poverty is a negative affect,
+we see here that lower income individuals tend to associate this feeling
+to their primary mode of commuting with higher frequency (almost 20\% of
+the time) than other income groups. Whereas approximately 16\% of
+mid-income people are dissatisfied with their primary mode of travel
+when it comes to evoking feelings of Poverty, less than 7\% of high
+income individuals are. Dissonance with respect to Luxury and Status
+also tends to be more common among lower income individuals, and
+declines substantially for mid- and high income respondents. Notice as
+well that the frequency of dissonance is higher in terms of Luxury than
+Status for mid- and high income people.
 
@@
 dissonance is the primary mode of travel. It can be seen in Table
-\ref{tab:cross-tabulation-results} that the differences are
-significative for all six affective values. Dissonance is particularly
-accute for users of public transportation when it comes to the values of
-Freedom, Enjoyment, and Happiness: almost 100\% of users of public
-transportation have identified other mode or modes as better
-representing those values. Dissonance on these values is the least for
-active travellers: less than 50\% of respondents associate Freedom to a
-different mode, and only around 60\% identified a different mode when
-responding to the values of Enjoyment and Happiness, compared to
-approximately 79\% and 71\% of those who travelled by Car. The picture
-changes when the values of Poverty, Luxury, and Status are considered.
-In this case, dissonance is less frequent for people who travel by car:
-less than 3\% of car users associate car with feelings of poverty, 41\%
-associate Luxury with a mode other than car, and only about 31\% relate
-Status to a different mode. Dissonance is more frequent in these values
-for active travellers, and users of public transportation and other
-modes, in no case being less than 75\%, and being virtually 100\% for
-users of public transportation, who consistently associate Luxury and
-Status with modes \emph{other} than public transportation.
+\ref{tab:cross-tabulation-results} that the differences are significant
+for all six affective values. Compared to users of other modes of
+transportation, dissonance is particularly acute for users of public
+transportation when it comes to the values of Freedom, Enjoyment, and
+Happiness: almost 100\% of users of public transportation have
+identified other mode or modes as better representing those affective
+values. Dissonance on these values is the least for active travelers:
+less than 50\% of respondents who are active travelers associate Freedom
+to a different mode, and only around 60\% identified a different mode
+when responding to the values of Enjoyment and Happiness, compared to
+approximately 79\% and 71\% of those whose primary mode is car. The
+picture changes when the values of Poverty, Luxury, and Status are
+considered. In this case, dissonance is less frequent for people who
+travel by car: less than 3\% of car users associate the car with
+feelings of Poverty, only 41\% associate Luxury with a mode other than
+car, and only about 31\% relate Status to a different mode. Dissonance
+is more frequent in these values for active travelers, and users of
+public transportation and other modes, in no case being lower than 75\%.
+This figure is virtually as high as 100\% for users of public
+transportation, a group of travelers who consistently associate Luxury
+and Status with modes \emph{other} than public transportation.
 
@@
 
-Turning now to typical commute time, four affectie values show
+Turning now to typical commute time, four affective values show
 significant differences at better than 10\% confidence: Freedom,
@@
 
-\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB factors}
+\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various affective values}
 \centering
@@
 
-\hypertarget{which-modes-do-travellers-associate-with-affective-values}{%
-\subsection{Which modes do travellers associate with affective
-values?}\label{which-modes-do-travellers-associate-with-affective-values}}
-
-The preceding analysis suggests that there is significant mode
+\hypertarget{which-modes-do-travelers-associate-with-affective-values}{%
+\subsection{Which modes do travelers associate with affective
+values?}\label{which-modes-do-travelers-associate-with-affective-values}}
+
+The preceding analysis indicates that there is significant mode
 dissonance along various dimensions and for various affective values.
@@
 examining different affective values individually instead of a summary
-measure of wellbeing, we are able to differentiate better in terms of
-how travellers respond to different affects. Less is known about the
-values that travellers associate with modes \emph{other} than the one
-they use. For this reason, after developing a profile of the travelers
-who experience mode dissonance in the preceding section, we are now
-interested in the responses of travellers with respect to the modes they
-tend to associate with various affective values.
-
-\textbf{\textbf{For this analysis we employ a visualization technique
-known as a mosaic plot. Mosaic plots are used in the exploration of
-multivariate categorical data (Friendly, 1994; Hofmann, 2000), and they
-provide visual representations of multi-way contingency tables. The
-elements of the mosaic plot are called \emph{tiles}, and the dimensions
-of each tile are proportional to values of variables in the underlying
-table.}}
-
-We begin our analysis by plotting primary mode of travel and the modes
-associated with each affective value (see Figure
-\ref{fig:bar-plots-by-attribute}). The height of tile \(j\) in these
-mosaics corresponds to the proportion of travellers who primarily travel
-by mode \(j\), hence we can see that the most common primary mode of
-travel in this sample is by public transportation, followed by car,
-active travel, and other (also see Figure
-\ref{fig:primary-mode-travel}). Notice that there are some small
-discrepancies in the heights across affective values: these are caused
-by a small number of non-responses. Next, the width of the tile \(k\) in
-the mosaics is proportional to the frequency with which a mode was named
-in relation to affective value \(i\). Recall that respondents could
-nominate more than one mode in response to each affective value, and
-some did. For this reason, we used sampling weights, so that the total
-number of responses corresponds to the size of the sample.
-
-In terms of Freedom, we see that Car users frequently identify this
-affect with the use of Car; however, those who do not, very often select
-Active Travel as the mode that better represents Freedom. A majority of
-active travellers, on the other hand, identify Active Travel as the mode
-that evokes feelings of Freedom; few of them attach this value to Car,
-and even fewer to public transportation and other modes. Travellers
-whose primary mode of travel is public transportation seldom associate
-this mode with Freedom, and in fact more frequently relate this
-affective response to Active Travel followed by Car. Users of other
-modes seem to be split almost equally in their attribution of Freedom,
-between Active Travel, Car, and Other. In general, Active Travel is the
-mode most often identified as embodying Freedom, with the exception of
-Car travellers.
-
-The pattern with respect to Enjoyment is similar to that for Freedom,
-but with an even more decisive tilt towards Active Travel, with even
-more respondents whose primary mode of travel is Car choosing Active
-Travel as the mode that better represents Enjoyment. Notice that very
-few of Active Travelers selected Car as an enjoyable mode. Likewise,
-compared to Freedom, Active Travel is perceived as being more enjoyable
-by users of Public Transportatoin and Other modes. Responses with
-respect to Happiness are somewhere in between Freedom and Enjoyment, but
-Happiness is, if anything, even less frequently identified with Public
-Transportation.
-
-Three other affective responses show a marked difference. Public
-Transportation was seldom associated by respondents to feelings of
-Freedom, Enjoyment, and Happiness; on the other hand, it is the mode
-that is most commonly selected by respondents for evoking feelings of
-Poverty - even by users of Public Transportation. Active Travel was the
-second most common response for its association with Poverty. Likewise,
-Whereas Active Travel was often associated to feelings of Freedom,
-Enjoyment, and Happiness, the mode most frequently associated with
-Luxury and Status is the Car, although active travellers seem to be
-somewhat more resistant to this association compared to respondents who
-travel by Car, Public Transportation, and Other modes.
-
-Next, we further explore these responses after stratifying by Age,
-Education, Income, and Commute Time. We test the underlying 3-way tables
-by means of the Cochran-Mantel-Haenszel \(\chi^2\) test of independence.
+measure of wellbeing, we are able to differentiate better the affective
+reactions of travelers. Less is known about the values that travelers
+associate with modes \emph{other} than the one they use. For this
+reason, after developing a profile of the travelers who experience mode
+dissonance in the preceding section, we are now interested in the
+responses of travelers with respect to the modes they ideally tend to
+associate with various affective values. For this analysis we employ a
+visualization technique known as \emph{faceting}. Bar charts are used to
+plot the proportions of respondents who associate each mode of
+transportation with an affective value. Faceting allows us to explore
+these proportions in a multivariate way by slicing the data according to
+additional attributes. The result is a visual representation of a
+multi-way contingency table. Please note that due to the small numbers
+of travellers who use modes categorized as ``Other'' we henceforth
+exclude them from the analysis.
+
+We begin our investigation of the modes more frequently associated with
+different affective values by plotting the primary mode of travel and
+the modes associated with the values (see Figure
+\ref{fig:bar-plots-by-attribute}). We can think of the figure as a
+matrix of plots, with each dimension of the matrix a \emph{facet}. In
+this figure, the columns of the matrix of plots correspond to different
+affective values, and the rows to different modes of primary mode of
+transportation, i.e., the mode actually used. The height of the bars in
+these plots is the proportion of respondents who selected mode
+\(j = \text{Car, Active, Public}\) as embodying the corresponding
+affective value.
+
+We know from the preceding analysis (Table
+\ref{tab:cross-tabulation-results}) that users of public transportation
+tend to experience dissonance with significantly higher frequency than
+car users and active travelers. But which mode(s) would align better to
+their expectations with regards to the affective values under study? If
+we inspect the bottom row of plots, we see that public transport users
+most of the time associate Freedom, Enjoyment, and Happiness with active
+travel. Users of public transportation are more or less equally split in
+terms of associating Poverty with active travel and public
+transportation, whereas they overwhelmingly associate Luxury and Status
+with the private car.
+
+Active travelers rarely experience dissonance with respect to Freedom,
+Enjoyment, and Happiness. And although the experience of dissonance is
+more frequent with respect to Luxury and Status, there is still a
+sizeable plurality of active travellers who associate these two
+affective values with active travel, \emph{not} the car (contrast these
+to the responses of public transit users.)
+
+Interestingly, dissonance among car users with respect to Freedom,
+Enjoyment, and Happiness is relatively high. While car is still the most
+frequently chosen mode associated with Freedom among car users, the
+proportion of car users who identify Freedom with active travel is
+almost as high. And when it comes to Enjoyment and Happiness, car users
+experience significant dissonance and in fact a majority tend to
+indicate active travel as representing these two affective values. In
+contrast, car users display little dissonance with respect to feelings
+of Luxury and Status.
+
+It is interesting to note that feelings of ``Poverty'' are associated
+with public transportation and active travel in almost exactly the same
+proportions, irrespective of the primary mode of travel.
+
+Next, we further explore these responses after stratifying by age,
+education, income, and typical commute time. We test the underlying
+3-way tables by means of the Cochran-Mantel-Haenszel \(\chi^2\) test of
+independence, (the \(p\)-values of the tests are reported in the
+figures.) The next set of figures adds a facet to the columns, so that
+each affective value is now further divided into columns that correspond
+to the levels of an individual attribute (i.e., age, education, income,
+and typical commute time.)
 
@@
 
-There are some interesting differences when viewed from the perspective
-of travellers of different ages (see Figure \ref{fig:bar-plots-by-age}).
-For example, as seen above, active travel is commonly associated with
-freedom, happiness, and enjoyment, even by car users, but especially by
-users of public transportation and other modes. However, when we break
-this down by age, we notice that this tendency weakens as people age,
-and older travellers increasingly associate these affective values to
-the car. Furthermore, the tendency to associate status with the car
-tends to increase with age, with the possible exception of public
-transport users, for whom other options (possibly taxi), gain status for
-older travellers (\textgreater{} 54) at the expense of other modes,
-including the car. In contrast, the car loses in the value of luxury
-with age, while other options become more commonly associated with
-feelings of luxury for older respondents, even for car users (Figure 2).
-Older car users (\textgreater{} 54) show less dissonance in status than
-in luxury, while active travellers present more dissonance in status
-than in luxury - and in fact, they more commonly project status in the
-car.
+We find some interesting differences when exploring dissonance from the
+perspective of age of the travelers (see Figure
+\ref{fig:bar-plots-by-age}). For example, as seen in the preceding
+section, active travel is commonly associated with Freedom, Happiness,
+and Enjoyment, even by car users, but especially by users of public
+transportation. However, when we break this down by age, we notice that
+this tendency weakens as people age, and older travelers increasingly
+assign these affective values to the car. Furthermore, the tendency to
+associate Status with the car tends to increase with age. In contrast,
+the car loses in the value of Luxury with age among car and public
+transport users, but gains among active travelers after dropping among
+mid-aged respondents. Older travelers almost universally associate
+Status with the car.
 
@@
 
-\textbf{\textbf{Only two affective values were significant in the
-preceding analysis when seen from the perspective of education, namely
-luxury and status. As seen in Figure \ref{fig:bar-plots-by-education},
-the perceptions of luxury and status are fairly consistent when
-differentiated by education. Most respondents tend to associate luxury
-and status to the use of car, albeit this association is stronger for
-status than for luxury. The second mode most often mentioned in relation
-to luxury is ``other'' likely due to the flexibility and convenience
-(but cost) of using taxis. The exception in this case is the traveller
-with graduate education who uses active modes. This type of respondent,
-while still more likely to associate luxury and status with the car,
-more commonly links active travel to these affects than travellers with
-lower levels of education. Most public transport users tend to associate
-luxury and status to the car, however, they associate active modes with
-status more than the same group with respect to luxury.}}
+Significant differences in dissonance by education are detected for five
+affective values. As seen in Figure \ref{fig:bar-plots-by-education},
+the association between active travel and Freedom is weaker among car
+travelers who are less educated (i.e., education K-12). Feelings of
+enjoyment are more frequently associated with active travel, and more so
+for less educated (K-12) and highly educated (graduate) car users and
+active travelers. This is somewhat different among users of public
+transportation, a majority of whom still assign feelings of Freedom to
+active travel, but with a higher proportion of travelers who associate
+this affective value to the car, especially among highly educated
+individuals. Less educated travelers who use the car are less likely to
+associate the value of Happiness to active travel, and this changes
+among people with higher levels of academic achievement, for whom active
+travel more frequently evokes feelings of Happiness. As before, most
+respondents identify the car with the values of Luxury and Status, and
+in general, people with lower education declare positive associations
+with the car more frequently. The exception is Status among active
+travelers: the more highly educated the traveler, the lower the
+probability of dissonance with respect to this affective value.
 
@@
 
-Three affective values were significant in the analysis by income;
-perhaps not surprisingly, all three have an economic dimension. Figure
-\ref{fig:bar-plots-by-income} reflects some important social
-inequalities associated with the way users feel about transportation in
-Santiago. When the affective perception of poverty is analyzed, the
-image shows that generally public transport is the mode most commonly
-associated with poverty. There are some interesting differences,
-however, to be observed by income level. Whereas middle income users of
-public transportation associate this mode to poverty most frequently,
-this is not the case of high income users of public transportation, who
-tend to link active travel to poverty with greater frequency. Similarly,
-active travel is more often associated with poverty by low income
-travellers than middle or high income travellers. A possible explanation
-for this is that walking or cycling are related to the idea of a lack of
-financial means to access other modes of transport. For high income car
-users, on the other hand, public transportation may have connotations of
-poverty due to its massive use, whereas active travel may be seen more
-as a lifestyle alternative.
+Like with education, there are significant differences in dissonance by
+income for five affective values. As seen in Figure
+\ref{fig:bar-plots-by-income}, car users with lower incomes tend to
+associate Freedom and Enjoyment with active travel, but more with
+respect to Enjoyment. In contrast, Enjoyment is more frequently
+associated with active travel among more affluent car users. Active
+travelers seldom experience dissonance with respect to Freedom,
+Enjoyment, and Happiness, irrespective of income level. However,
+although public transport users still tend to link active travel with
+feelings of Freedom, Enjoyment, and Happiness, they remain more likely
+to attribute these values to the car.
 
 With respect to luxury and status, we see again that these two values
-coincide more strongly in their association with the car. Moreover, we
-also notice that these perceptions become increasingly frequent at
-higher levels of income. Unlike users of other modes, the high-income
-public transport user group tends to concentrate a broader association
-of luxury and status factors with active transport, reinforcing the
-notion that at higher levels of income, people may see active modes as a
-lifestyle alternative. High income active travellers, although still
-more likely to associate luxury and status to the car, are more likely
-than users of other modes to associate these affects to active travel,
-perhaps due to an awareness of the benefits of walking and using the
-bicycle. Furthermore, high-income users of cars are more likely to
-experience consonance with respect to status and luxury, in what might
-be a form of self-congratulatory confirmation of success.
+generally are attributed to the car, but with some interesting
+differences by income and primary mode of travel. Indeed, higher income
+active travelers, although still more likely to associate Luxury and
+Status with the car, are more likely than users of other modes to
+associate these affects to active travel, perhaps due to an awareness of
+the benefits of walking and using the bicycle. Furthermore, high-income
+users of cars are more likely to experience consonance with respect to
+status and luxury, in what might be a form of self-congratulatory
+confirmation of success.
 
@@
 
-The last dimension that we examine is typical commute time. Four
-affective values were significant along this dimension in Table
-\ref{tab:cross-tabulation-results}. Figure
-\ref{fig:bar-plots-by-travel-time} shows the way travellers associate
+The last dimension of dissonance that we examine is typical commute
+time. Four affective values are significant along this dimension, namely
+Freedom, Enjoyment, Happiness, and Status. Figure
+\ref{fig:bar-plots-by-travel-time} shows the way travelers associate
 different affective values to modes of transportation by length of
-typical commute. The first couple of factors, freedom and enjoyment, are
-associated with eudaimonic and hedonic factors of wellbeing, as
-discussed earlier in the paper. On the other hand, the luxury and status
-are defined mainly by a socio-economic component. As seen in the figure,
-freedom and enjoyment are most frequently mentioned in relation to
-active travel, followed by car. However, active travel is more
-frequently associated with freedom and enjoyment by people who typically
-undertake relatively short trips (\textless20 min) or travellers whose
-typical trips are longer (\textgreater60 min). In this respect, active
-travel may be seen as an ideal mode for trips, and as an enviable mode
-by people whose trips are longer.
-
-In the case of luxury and status factors, both follow a similar pattern,
-despite variations in travel times. Despite the travel time exceeding 60
-minutes, car users consider that their transport mode is mostly
-associated with luxury and status. The users of active transport in the
-sample tend to travel less than 20 minutes, and this is the same segment
-that considers that the status and luxury factors correspond mainly to
-the car and then to active transport. Looking at the four factors set
-out in Figure \ref{fig:bar-plots-by-travel-time}, it could be understood
-that the modes that are associated with intrinsically positive
-characteristics such as freedom and enjoyment tend to use public
-transport. On the contrary, factors such as luxury and status tend to
-have a negative connotation, where the association with the car and
-other modes of transport (such as the individual taxi and the collective
-taxi) tends to dominate.
+typical commute.
+
+Among car users, Freedom is associated with the car in the case of every
+commute but the longest (\textgreater60 min), in which case active
+travel is more frequently identified as the mode that evokes feelings of
+Freedom. The associations of active travel with Enjoyment and Happiness
+are consistently high among car users, although car becomes more
+frequently associated with this value for longer commutes. As we have
+seen before, active travelers seldom experience dissonance with respect
+to Freedom, Enjoyment, and Happiness, and if anything the strength of
+this association increases with longer commutes. Public transportation
+users again are split in their preference towards active travel and car
+as the modes more likely to evoke feelings of Freedom, Enjoyment, and
+Happiness, and there are only relatively minor differences in these
+preferences by length of commute. The last affective value that displays
+significant differences in dissonance by length of typical commute is
+Status. The car tends to dominate as the mode more frequently associated
+with this value among car and public transportation users. Active
+travelers, on the other hand, associate status more strongly with short
+or very long commutes: only when commutes are shorter than 20 minutes or
+longer than 60 minutes do active travelers associate feelings of Status
+with the car.
 
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-Subjective wellbeing is a topic that has attracted considerable
-attention in recent years due to its relationship with health. In the
-field of transportation, there is a large and growing body of literature
-that documents the way transportation can impact subjective wellbeing.
-Likewise, there is strong evidence that subjective wellbeing can
-influence travel behavior. As the world tries to move from a culture
-dominated by a century-long love affair with the automobile, there is a
-pressing need to understand how travellers perceive different modes of
-transportation from the lens of subjective wellbeing. Insights in this
-regard could prove valuable to develop and implement plans and policies
-to attract and retain users to healthier, more environmentally friendly
-transportation options, in particular active travel and public
-transportation. For this reason, understanding mode dissonance, the
-extent to which the context of travellers differs from their
-aspirations, is a worthwhile topic for research.
-
-The premise of the research presented in this paper is that subjective
-wellbeing is a composite construct of various affective values. In this
-paper we investigated mode dissonance from the perspective of six
-affective values associated with subjective wellbeing, namely freedom,
-enjoyment, happiness, poverty, luxury, and status. The research
-presented here was based on a sample of travellers in Santiago, the
-capital of Chile. Participants in this research were asked about their
-typical mode of travel, and then about the mode or modes that they
-associate with each of the six affective values. Analysis using
-hypothesis testing (tests of independence) and vizualization techniques
-(mosaic plots) uncovered interesting patterns. Some of our findings are
-well aligned with previous research; for example, active travellers
-experience less dissonance than car users, and users of public
-transportation experience the most dissonance of all. However, by
-considering affective values separately instead of aggregating them into
-a single indicator of subjective wellbeing, we manage to preserve some
-granularity with respect to various responses. This turns out to be
-important, because hedonic/eudaimonic values are more frequently related
-to active travel (freedom, enjoyment, happiness), whereas poverty is
-more frequently related to public transportation and active travel.
-Luxury and status, on the other hand, are more frequently associated to
-luxury and status.
+\hypertarget{summary-and-concluding-remarks}{%
+\section{Summary and Concluding
+Remarks}\label{summary-and-concluding-remarks}}
+
+The topic of subjective wellbeing has attracted considerable attention
+in recent years due to its relationship with health. As the world tries
+to move from a culture dominated by a century-long love affair with the
+automobile, there is a pressing need to understand how travelers
+perceive different modes of transportation from the lens of subjective
+wellbeing. Insights in this regard could prove valuable to develop and
+implement plans and policies to attract and retain users to healthier,
+more environmentally friendly transportation options (Chatterjee et al.,
+2019). For this reason, understanding mode dissonance, the extent to
+which the experience of travelers differs from their aspirations, is a
+worthwhile topic for research.
+
+This paper contributes to the literature in three ways.
+
+First, the research contributes to an emerging literature on the topic
+of transportation and subjective wellbeing in the context of the Global
+South (Al-Ayyash and Abou-Zeid, 2019; Bejarano et al., 2017; Shao and
+Liang, 2019; Van et al., 2014; Zorrilla et al., 2019); to the best of
+our knowledge, the case of Chile has not yet been reported. Second,
+although there is an extensive literature on the enjoyment of commute
+and other affective values (see for instance Paez and Whalen, 2010;
+Redmond and Mokhtarian, 2001; Whalen et al., 2013; Ye and Titheridge,
+2017), from a hedonic and even eudaimonic perspectives the analysis has
+yet to be applied more fully in terms of distributional issues --
+i.e.~which groups more commonly experience dissonance (see De Vos,
+2018). Third, the analysis shows the attitudes of people towards their
+primary mode and their perception towards `ideal modes', complementing
+the studies based on affective factors on transit or active modes
+(Bornioli et al., 2019; De Vos and Witlox, 2017), satisfaction (De Vos
+et al., 2019), or quality (Redman et al., 2013).
+
+The premise of this study is that a key component of subjective
+wellbeing is the affective reaction to experience (see the definition of
+wellbeing offered by the OECD; -@ OECD, 2013). In this paper we
+investigated mode dissonance from the perspective of six affective
+values. The research presented here was based on a sample of travelers
+in Santiago, the capital of Chile. Participants in this research were
+asked about their typical mode of travel, and then about the mode or
+modes that they associate with each of the six affective values.
+Analysis using hypothesis testing (tests of independence) and
+visualization techniques (bar charts with faceting) uncovered
+interesting patterns. Some of our findings are well aligned with
+previous research; for example, active travelers experience less
+dissonance than car users, and users of public transportation experience
+the most dissonance of all. However, by considering affective values
+separately instead of aggregating them into a single indicator of
+subjective wellbeing, we manage to preserve greater granularity with
+respect to various responses than most studies. This is important
+because hedonic/eudaimonic values are more frequently related to active
+travel (Freedom, Enjoyment, Happiness), whereas Poverty is more
+frequently related to public transportation and active travel. Luxury
+and Status, on the other hand, are more frequently associated to car.
 
@@
 these affective values, we find that there are important differences in
-terms of the typical mode of travel. Active travellers experience
-dissonance with relatively little frequently with respect to freedom,
-enjoyment, and happiness, but when they do, they tend to attach positive
+terms of the typical mode of travel. Active travelers experience
+dissonance with relatively little frequently with respect to Freedom,
+Enjoyment, and Happiness, but when they do, they tend to attach positive
 values to the car. Car users experience dissonance with respect to these
-affects more frequently than active travellers, and when they do, they
-strongly relate possitive hedonic/eudaimonic values to active travel. In
+affects more frequently than active travelers, and when they do, they
+strongly relate positive hedonic/eudaimonic values to active travel. In
 other words, it is possible that drivers dream of walking when it comes
-to feelings especially of enjoyment and happiness. The other side of the
-coin is also interesting. When it comes to affective values with a
-stronger socio-economic flavor, such as poverty, luxury, and status, car
-users tend to experience dissonance less frequently than users of other
-modes. Active travellers, altough more resistant to the lure of the car
-compared to users of public transportation, also tend to attach values
-of luxury and status to the car when they experience dissonance.
+to feelings of Enjoyment and Happiness, and to a lesser extent Freedom.
+The other side of the coin is also interesting. When it comes to
+affective values with a stronger socio-economic flavor, such as Poverty,
+Luxury, and Status, car users tend to experience dissonance less
+frequently than users of other modes. Active travelers, although more
+resistant to the lure of the car compared to users of public
+transportation, also tend to attach values of Luxury and Status to the
+car when they experience dissonance.
 
 An examination of these effects by age, level of education, level of
-income, and typical trip duration reveals that some of the responses
-become more pronounced. For instance, older people are less likely than
-younger people to associate active travel with positive
+income, and typical trip duration reveals some ways in which these
+trends become more pronounced. For instance, older people are less
+likely than younger people to associate active travel with positive
 hedonic/eudaimonic affects, and are more likely to attach these values
@@
 
-Our results not only help to flesh out some ways in which mode
+These results not only help to flesh out some ways in which mode
 dissonance could play out from the perspective of different affects, but
-also does so in the context of a Latin American country, a region where
-historically there are deep-seated tabooes with respect to different
-modes of transportation: the poor travel by public transportation and/or
-are forced active travellers; where the rich enjoy the luxury of private
-vehicles and/or are active travellers by choice. In this way, the paper
-helps us to reflect on the ways the public experiences
-transportation-related subjective wellbeing, and how this in turn could
-be used to increase the attractiveness of public transport and active
-travel in the socio-demographic groups studied.
-
-With respect to opportunities for future research, a possible avenue for
-extending the findings reported in this paper relates to the use of the
-modes other than the typical mode of transportation. In a recent paper
-that investigaed commute satisfaction for car users, Al-Ayyash and
-Abou-Zeid (2019) considered three models: for current trip satisfaction,
+does so in the context of a Latin American country, a region where
+deep-seated taboos with respect to different modes of transportation
+exist: the poor travel by public transportation and/or are forced active
+travelers; a country where the rich enjoy the luxury of private vehicles
+and/or are active travelers by choice. In this way, the paper helps us
+to reflect on the affective reaction of members of the public with
+respect to their transportation experience. A better understanding of
+these responses can in turn be used to judiciously enhance the
+experience of commuting, to increase the satisfaction of commuters, and
+to meet their preferences.
+
+In this respect, it is important to note that the perception of users
+has been considered mainly from the lens of trip satisfaction, but the
+more granular approach taken in this study offers some advantages. For
+example, understanding dissonances reveals that public transport users
+are clearly at a disadvantage (i.e., they experience dissonance more
+frequently) compared to other travelers. Furthermore, the results reveal
+that within public transport users, there are also important
+socio-economic differences. In contrast, users of cars do not
+necessarily associate hedonic/eudaimonic values to this mode, which
+suggests that not only these feelings could be levaraged to attract them
+to active modes, but could also as a result lead to gains in wellbeing.
+
+With respect to opportunities for future research, a possible extension
+of the present research would be to investigate the use of the modes
+other than the typical mode of transportation. In a recent paper that
+investigated commute satisfaction for car users, Al-Ayyash and Abou-Zeid
+(2019) considered three models: for current trip satisfaction,
 remembered satisfaction while using public transport, and current
 satisfaction using public transport. The findings suggest that low
-service quality in public transportation can result in a generalised
+service quality in public transportation can result in a generalized
 negative perception, and that this perception is more difficult to
@@
 typically used. While in this paper the analysis focused on the primary
-mode of transportation, many travellers experience more than one mode of
+mode of transportation, many travelers experience more than one mode of
 transportation in their daily activities. For this reason, considering
@@
 future research could consider people who eventually arrive by bicycle
-to the metro station or people that, after using a colectivo for part of
-a trip, end their journey by bus.
+to the metro station or people that, after using a \emph{colectivo} for
+part of a trip, end their journey by bus.
 
@@
 
-The following \texttt{R} packages were used in the course of this
-investigation and the authors wish to acknowledge their developers:
-\texttt{ggmosaic} (Jeppson et al., 2018), \texttt{ggthemes} (Arnold,
-2018), \texttt{kableExtra} (Zhu, 2018), \texttt{knitr} (Xie, 2018,
-2015), \texttt{rticles} (Allaire et al., 2018), and \texttt{tidyverse}
-(Wickham, 2017).
+We wish to express our gratitude to Prof.~Jonas De Vos and three
+anonymous reviewers for their feedback on an earlier version of this
+paper. Their suggestions helped to improve the quality of the research
+and the clarity of the presentation. The following \texttt{R} packages
+were used in the course of this investigation and the authors wish to
+acknowledge their developers: \texttt{ggmosaic} (Jeppson et al., 2018),
+\texttt{ggthemes} (Arnold, 2018), \texttt{kableExtra} (Zhu, 2018),
+\texttt{knitr} (Xie, 2018, 2015), \texttt{rticles} (Allaire et al.,
+2018), and \texttt{tidyverse} (Wickham, 2017).
 
@@
 
+\leavevmode\hypertarget{ref-Avellaneda2011}{}%
+Avellaneda, P., Lazo, A., 2011. APROXIMACION a la movilidad cotidiana en
+la periferia pobre de dos ciudades latinoamericanas. LOS casos de lima y
+santiago de chile. Revista transporte y territorio 47--58.
+
 \leavevmode\hypertarget{ref-Bejarano2017user}{}%
@@
 
+\leavevmode\hypertarget{ref-Brunsdon2020opening}{}%
+Brunsdon, C., Comber, A., 2020. Opening practice: Supporting
+reproducibility and critical spatial data science. Journal of
+Geographical Systems.
+doi:\href{https://doi.org/10.1007/s10109-020-00334-2}{10.1007/s10109-020-00334-2}
+
 \leavevmode\hypertarget{ref-Cao2014satisfaction}{}%
@@
 
+\leavevmode\hypertarget{ref-Cox2016}{}%
+Cox, T., Hurtubia, R., 2016. Vectores de expansión urbana y su
+interacción con los patrones socioeconómicos existentes en la ciudad de
+santiago. EURE (Santiago) 42, 185--207.
+
+\leavevmode\hypertarget{ref-Davis2019}{}%
+Davies, R., 2019. Why is inequality booming in chile? Blame the chicago
+boys. The Guardian, November.
+
 \leavevmode\hypertarget{ref-Delbosc2012role}{}%
@@
 
+\leavevmode\hypertarget{ref-Diener2015national}{}%
+Diener, E., Oishi, S., Lucas, R.E., 2015. National accounts of
+subjective well-being. American Psychologist 70, 234--242.
+doi:\href{https://doi.org/10.1037/a0038899}{10.1037/a0038899}
+
+\leavevmode\hypertarget{ref-Dolan2012measuring}{}%
+Dolan, P., Metcalfe, R., 2012. Measuring subjective wellbeing:
+Recommendations on measures for use by national governments. Journal of
+Social Policy 41, 409--427.
+doi:\href{https://doi.org/10.1017/s0047279411000833}{10.1017/s0047279411000833}
+
 \leavevmode\hypertarget{ref-Domarchi2008effect}{}%
@@
 
-\leavevmode\hypertarget{ref-Friendly1994mosaic}{}%
-Friendly, M., 1994. Mosaic displays for multi-way contingency tables.
-Journal of the American Statistical Association 89, 190--200.
-
 \leavevmode\hypertarget{ref-Friman2013psychometric}{}%
@@
 doi:\href{https://doi.org/10.1016/j.tbs.2018.03.001}{10.1016/j.tbs.2018.03.001}
-
-\leavevmode\hypertarget{ref-Hofmann2000exploring}{}%
-Hofmann, H., 2000. Exploring categorical data: Interactive mosaic plots.
-Metrika 51, 11--26.
 
@@
 
+\leavevmode\hypertarget{ref-Lavery2013driving}{}%
+Lavery, T.A., Paez, A., Kanaroglou, P.S., 2013. Driving out of choices:
+An investigation of transport modality in a university sample.
+Transportation Research Part A-Policy and Practice 57, 37--46.
+doi:\href{https://doi.org/10.1016/j.tra.2013.09.010}{10.1016/j.tra.2013.09.010}
+
 \leavevmode\hypertarget{ref-Lois2009relationship}{}%
@@
 
+\leavevmode\hypertarget{ref-Figueroa2018}{}%
+Martínez, C.F., Hodgson, F., Mullen, C., Timms, P., 2018. Creating
+inequality in accessibility: The relationships between public transport
+and social housing policy in deprived areas of santiago de chile.
+Journal of Transport Geography 67, 102--109.
+
 \leavevmode\hypertarget{ref-Miller2011collaborative}{}%
@@
 
+\leavevmode\hypertarget{ref-Niehaus2016}{}%
+Niehaus, M., Galilea, P., Hurtubia, R., 2016. Accessibility and equity:
+An approach for wider transport project assessment in chile. Research in
+Transportation Economics 59, 412--422.
+
 \leavevmode\hypertarget{ref-oecd2013oecd}{}%
@@
 amount. Transportation 28, 179--205.
+
+\leavevmode\hypertarget{ref-RodriguesVignoli2008}{}%
+Rodríguez Vignoli, J., 2008. Movilidad cotidiana, desigualdad social y
+segregación residencial en cuatro metrópolis de américa latina. EURE
+(Santiago) 34, 49--71.
+
+\leavevmode\hypertarget{ref-Rojas2016}{}%
+Rojas, C., Paez, A., Barbosa, O., Carrasco, J., 2016. Accessibility to
+urban green spaces in chilean cities using adaptive thresholds. Journal
+of Transport Geography 57, 227--240.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2016.10.012}{10.1016/j.jtrangeo.2016.10.012}
 
@@
 to gender equality. Social Indicators Research 85, 329--349.
+
+\leavevmode\hypertarget{ref-TiznadoAitken2016}{}%
+Tiznado-Aitken, I., Muñoz, J.C., Hurtubia, R., 2016. How equitable is
+access to opportunities and basic services considering the impact of the
+level of service? The case of santiago, chile, in:. International
+Transport Forum Discussion Paper.
 

### 2020-08-17 Dissonance_Santiago_v2/Response-to-Reviewers-v2.Rmd
v2 Revisions with BML

@@
 
->\textcolor{blue}{The consideration of factors related to the subjective personal well-being will enable targeting public policy strategies focused on nudging public and active transport users}
+>\textcolor{blue}{Consideration of factors related to subjective wellbeing, for example, are useful for policy-makers to enhance the experience of travel, to increase satisfaction with travel, and to meet the preferences of travelers (Chatterjee et al., 2019).}
 
@@
 
->\textcolor{blue}{Done.}
+>\textcolor{blue}{Done. L60-63}
 
@@
 
->\textcolor{blue}{Recent social demands have highlighted the relevance and impacts of the neoliberal economic model in the development of the city – which correlates with the construction of the society and therefore shapes the development of transport infrastructure (see for recent protests and social crisis: Davies, 2019; Guardiola-Rivera, 2019; Sehnbruch, 2019).
-Even though everyday mobility in Santiago has also been contextualized in relation to other Latin American cities (Avellaneda and Lazo, 2011; Rodriguez Vignoli, 2008), there is much more to be explored in other regions in the Chilean context.
-Measuring instruments and new methodologies have allowed a more accurate and precise understanding of the social issues arising as consequence of transport infrastructure and housing provision (Cox and Hurtubia, 2016), and the minimum provision of basic services (Tiznado-Aitken et al., 2016).
-However, the focus on accessibility as a measure of inequities remains predominant (Tiznado-Aitken et al., 2018; Figueroa Martínez, et al., 2018; Niehaus et al., 2016; Rojas et al., 2016).}
+>\textcolor{blue}{A tangible manifestation of the inequalities experienced by many in Chile is the large disparity in the relative cost of transportation, travel time, and distance traveled by different socio-economic segments of the population.
+To further complicate matters, strong spatial segregation also conditions car ownership and the use of public transportation – the higher the income, the higher the use of the automobile; conversely, the lower the income, the higher the reliance on public transportation.
+Although the transportation experience is but one of many dimensions of inequality, the experiences in this sector have triggered exceptional discomfort and dissatisfaction among the public.
+Recent social unrest, triggered by a seemingly minor hike in the fare of public transportation, has brought many of these concerns to the forefront of the public conscience in dramatic fashion (e.g., Davies, 2019).
+Previous research has helped to contextualize everyday mobility in Santiago relative to other Latin American cities (e.g., Avellaneda and Lazo, 2011), but much remains to be explored.
+Measuring instruments and new methods have led to more accurate and precise understandings of the social issues that arise as consequence of transport infrastructure and housing provision (Cox and Hurtubia, 2016), and the minimum provision of basic services (Tiznado-Aitken et al., 2016).
+However, the focus on accessibility as a measure of inequalities remains predominant.}
 
@@
 
->\textcolor{blue}{The study considers data from 3 out of 8 sections of a longer survey – data being more relevant for the study.
-The topics around these sections are Individual characteristics of respondents, feelings and emotions related to their commute, and aspects describing their regular commute trips.}
+>\textcolor{blue}{ The study considers data from 3 out of 8 sections of a longer survey.
+The relevant sections of the survey concern the individual characteristics of respondents, their feelings and affective responses related to their commute, and aspects describing their regular commute trips.
+In terms of individual characteristics and their commute, participants were asked socio-demographic information, including age (coded in three classes: younger than 35, older than 35 but younger than 55, and 55 and olde); level of education (three classes: Kindergarden to grade 12, or K-12, technical diploma or university graduate, and graduate degree), income  (three classes, by tertile), and the typical duration of the respondent’s regular commute (four classes, by duration in minutes).
+}
 
@@
 
->\textcolor{blue}{The sample tends to be younger (56% is younger than 34 years old), and well-educated (68% of respondents having technical or professional education), with an almost uniform distribution of income levels.
+>\textcolor{blue}{The sample trends to younger (56% is younger than 34 years old) and well-educated respondents (68% of respondents having technical or professional education), with an almost uniform distribution of income levels.
 The trend in typical commute time is towards longer commutes – e.g.
@@
 
->\textcolor{blue}{Because most literature focuses in trip satisfaction – the study goes beyond the understanding of determinants of trip satisfaction.}
+>\textcolor{blue}{Because most literature focuses in trip satisfaction.
+However, further research beyond the determinants of trip satisfaction is needed to understand how these socio-demographic variables connect with the affective reactions to various modes of travel (St-Louis et al., 2014).}
 
@@
 I would not normally think of ‘Poverty’ as a value, but rather as an economic condition, so explain the nature of these affective values.
-
->\textcolor{blue}{Words.}
+>\textcolor{blue}{Delbosc (2012, p. 28), for instance, has summarized the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.}
 
@@
 
->\textcolor{blue}{Words.}
+>\textcolor{blue}{Done.}
 
@@
 
->\textcolor{blue}{Understanding who experiences dissonance is relevant in this study.
-We believe most disadvantageous groups will experience more dissonance with respect to their primary travel mode and affective values, namely freedom, enjoyment, happiness, feelings of poverty, luxury, and status.}
+>\textcolor{blue}{We begin by profiling the travellers who experience dissonance.
+The null hypothesis is that there are no systematic differences in terms of who tends to experience affective dissonance with respect to their primary mode of travel.}
 
@@
 
->\textcolor{blue}{As noted in our response to Reviewer 1, recent social demands have highlighted the relevance and impacts of the neoliberal economic model in the development of the city – which correlates with the construction of the society and therefore shapes the development of transport infrastructure (see for recent protests and social crisis: Davies, 2019; Guardiola-Rivera, 2019; Sehnbruch, 2019).
-Even though everyday mobility in Santiago has also been contextualized in relation to other Latin American cities (Avellaneda and Lazo, 2011; Rodriguez Vignoli, 2008), there is much more to be explored in other regions in the Chilean context.
-Measuring instruments and new methodologies have allowed a more accurate and precise understanding of the social issues arising as consequence of transport infrastructure and housing provision (Cox and Hurtubia, 2016), and the minimum provision of basic services (Tiznado-Aitken et al., 2016).
-However, the focus on accessibility as a measure of inequities remains predominant (Tiznado-Aitken et al., 2018; Figueroa Martínez, et al., 2018; Niehaus et al., 2016; Rojas et al., 2016).}
+>\textcolor{blue}{As noted in our response to Reviewer 1, a tangible manifestation of the inequalities experienced by many in Chile is the large disparity in the relative cost of transportation, travel time, and distance traveled by different socio-economic segments of the population.
+To further complicate matters, strong spatial segregation also conditions car ownership and the use of public transportation – the higher the income, the higher the use of the automobile; conversely, the lower the income, the higher the reliance on public transportation.
+Although the transportation experience is but one of many dimensions of inequality, the experiences in this sector have triggered exceptional discomfort and dissatisfaction among the public.
+Recent social unrest, triggered by a seemingly minor hike in the fare of public transportation, has brought many of these concerns to the forefront of the public conscience in dramatic fashion (e.g., Davies, 2019).
+Previous research has helped to contextualize everyday mobility in Santiago relative to other Latin American cities (e.g., Avellaneda and Lazo, 2011), but much remains to be explored.
+Measuring instruments and new methods have led to more accurate and precise understandings of the social issues that arise as consequence of transport infrastructure and housing provision (Cox and Hurtubia, 2016), and the minimum provision of basic services (Tiznado-Aitken et al., 2016).
+However, the focus on accessibility as a measure of inequalities remains predominant.}
 
@@
 
->\textcolor{blue}{}
+>\textcolor{blue}{ As noted in our response to Reviewer 1, we moved comments about literature towards the section of concluding remarks; leaving some results in the introductory section.}
 
@@
 
->\textcolor{blue}{}
+>\textcolor{blue}{We differenced studies which are purely focused on satisfaction and subjective wellbeing.
+Affective values and perceptions are considered in more general approaches (Zorrilla et al, 2019).
+We mentioned attitudes for the case of Asian cities (Shao et al, 2019).}
 
@@
 
->\textcolor{blue}{}
+>\textcolor{blue}{Affective values – as we mentioned by the end of paragraph 3.}
 
@@
 
->\textcolor{blue}{This has been discussed in section 3.2. paragraph 4.}
+>\textcolor{blue}{This has been discussed in the Introduction section.}
 
@@
 
->\textcolor{blue}{This has been also commented in the Background section: “The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel”.
+>\textcolor{blue}{This has been also commented in the Background section: “The research needs outlined above are well-recognized in the developed world, but there is still a dearth
+of research in the context of the Global South.
+Historical inequality in many developing countries has led to strong symbolic attachments to the automobile, in addition to negative connotations for public transport and active travel (Zorrilla et al., 2019)”.
 A separated paragraph in the conclusion addresses this discussion, in the Chilean and LA context.}
@@
 
->\textcolor{blue}{The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
-The survey was carried out face-to-face in centres of activity with dense provision of offices, services and educational centres.}
+>\textcolor{blue}{The survey collected information on a wide range of transportation and related issues, and the data collection protocol considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
+The survey was carried out face-to-face in centres of activity with dense provision of offices, services, and educational centres.
+An equal representation of both genders and a representation of the proportion of inhabitants per area were chosen as relevant characteristics of the sample.
+In total, there were n = 451 valid responses, although not every response was complete and some questions have missing values.}
 
@@
 
->\textcolor{blue}{Words.}
+>\textcolor{blue}{We think figure 1 is good for visualizing the descriptive statistics. Labels are clear now.}
 
@@
 
->\textcolor{blue}{Words.}
-
-SWB and health: The author(s) could at least add a paragraph about how SWB affects health, except for just mentioning that SWB has been found to be correlated with health.
-
->\textcolor{blue}{Words.}
+>\textcolor{blue}{Thanks.}
 
@@
 
->\textcolor{blue}{The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
-The survey was carried out face-to-face in centres of activity with dense provision of offices, services and educational centres.}
+>\textcolor{blue}{See response to reviewer 2 about methodology.}
 
@@
 
->\textcolor{blue}{Words.}
+>\textcolor{blue}{Done.}

### 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_Title_Page_v2.Rmd
v2 Revisions with BML

--- 2019-11-05 Dissonance_Santiago_v1.Rmd
@@
 author:
-  - name: Author 1
-    email: a1@university.com
-    affiliation: Some University
+  - name: Beatriz Mella Lira
+    email: beatriz.lira.14@ucl.ac.uk
+    affiliation: PUC
     footnote: Corresponding Author
-  - name: Author 2
-    email: a2@school.com
-    affiliation: Some School
+  - name: Antonio Paez
+    email: paezha@mcmaster.ca
+    affiliation: McMaster University
 address:
-  - code: Some University
-    address: Department, Street, City, State, Zip
-  - code: Some School
-    address: Department, Street, City, State, Zip
+  - code: PUC
+    address: BRT+ Centre of Excellence, Departamento Ingeniería de Transporte y Logística, Escuela de Ingeniería, Pontificia Universidad Católica de Chile
+  - code: McMaster University
+    address: School of Earth, Environment, and Society, McMaster University, 1280 Main St W, Hamilton, Ontario, L8S 1S4 Canada
 abstract: |
-   **Introduction**  
-   Subjective wellbeing is a topic that has attracted considerable attention in recent years due to the way it correlates with health.
-From a transportation perspective, there is a burgeoning literature on the way travel can impact subjective wellbeing, and how this, in turn, can influence behavior.
-   **Objective**  
-   The objective of this paper is to analyze a number of affective values associated with subjective wellbeing and the modes of transportation that people commonly use.
-In particular, we are interested in the potential for dissonance with respect to the primary mode of travel.
-   **Materials and Methods**  
-   The study is based on data collected from a sample of travellers in the city of Santiago, in Chile.
-Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associate with the affective values of freedom, enjoyment, happiness, poverty, luxury and status.
-Analysis is based on tests of independence and visualization via mosaic plots.
-   **Results**  
-   The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
+   *Introduction*  
+   Subjective wellbeing is a topic that has attracted considerable attention in the transportation literature in recent years.
+As a result, there is a burgeoning literature that investigates the impacts of travel on subjective wellbeing, and how wellbeing, in turn, can influence behavior.
+An important aspect of subjective wellbeing are the affective reactions of people to their experiences.
+   *Objective*  
+   The objective of this paper is to analyze the affective reactions of travelers with respect to various modes of transportation.
+In particular, we are interested in the potential for dissonance between primary mode of travel and the mode(s) of travel identified as evoking various affective reactions.
+   *Materials and Methods*  
+   The study is based on data collected from a sample of travelers in the city of Santiago, in Chile.
+Participants in the study were asked about their usual mode of travel, and then were asked to name their ideal mode(s) of transportation from the perspective of various affective reactions.
+The reactions we investigate are associated with the values of freedom, enjoyment, happiness, poverty, luxury, and status.
+Analysis is based on tests of independence and visualization techniques.
+   *Results*  
+   The results indicate that users of public transportation experience the most dissonance in terms of affective reactions, and active travelers the least.
+For those travelers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, whereas public transportation is most commonly associated with poverty.
+The automobile, in contrast, is the mode most commonly associated with luxury and status.
 
@@
 ---
-
-<!-- This paper is an R markdown document that includes self-contained, reproducible analysis. To reproduce the paper the following files are needed:
-
-1. Dissonance_Santiago_v1.Rmd (this R markdown document)
-
-2.
-`Dissonance_Santiago.RData`.
-For reference: this data file was created using R notebook `00.
-Analysis of Dissonance Detailed.Rmd`.
-The initial analysis was done in the same R notebook.
-Neither of these two notebooks are needed for this document.
-
-3.
-For compiling into a pdf in the style of an Elsevier document: elsarticle.cls, elsevier-harvard.csl, elsevier-harvard-without-titles.csl, elsevier-vancouver.csl, elsevier-without-titles.cls, elsevier-with-titles.csl, elsevier-with-titles-alphabetical.csl, mybibfile.bib
--->
-
-```{r load-packages, include=FALSE}
-
-# Load packages used in this document
-
-library(rticles)
-library(readxl)
-library(tidyverse)
-library(rgdal)
-library(sf)
-library(ggmosaic)
-library(ggthemes)
-library(kableExtra)
-library(gridExtra)
-```
-
-```{r load-data, include=FALSE}
-
-# To run this notebook, the file `Dissonance_Santiago.RData` is needed. This file contains the following object:
-# 
-# master: a dataframe with information collected from 451 respondents. The variables in the dataframe are:
-# 
-# - NUMERO: Respondent ID
-# - USED: Main mode of transportation used by the respondent
-# - FREEDOM: Mode(s) that the respondent associates with feelings of freedom
-# - ENJOYMENT: Mode(s) that the respondent associates with feelings of enjoyment
-# - HAPPINESS: Mode(s) that the respondent associates with feelings of happiness
-# - POVERTY: Mode(s) that the respondent associates with feelings of poverty
-# - LUXURY: Mode(s) that the respondent associates with feelings of luxury
-# - STATUS: Mode(s) that the respondent associates with feelings of status
-# - SAFETY: Mode(s) that the respondent associates with feelings of safety
-# - TIME: Mode(s) that the respondent associates with feelings of WASTED TIME
-# - EFFICIENCY: Mode(s) that the respondent associates with feelings of efficiency
-# - AGE: Age of the respondent
-# - EDUCATION: Level of education of the respondent
-# - INCOME: Level of income of respondent
-# - TRAVEL_TIME: Trip duration of regular commuting trip 
-# - WEIGHT_*: A weight for the responses by ATTRIBUTE.
-Some respondents selected more than one mode that they associated with feelings of {FREEDOM, ENJOYMENT, HAPPINESS, POVERTY, LUXURY, STATUS, SAFETY, TIME, and EFFICIENCY}.
-To avoid giving greater weight to respondents who indicated several modes of transportation, a weight was calculated that is the inverse of the number of modes indicated.
-These weights can be used to weight the frequencies prior to any analysis.
-# 
-# The modes of transportation (USED, FREEDOM, ENJOYMENT, HAPPINESS, POVERTY, LUXURY, STATUS, SAFETY, TIME, EFFICIENCY) are coded as: 
-# "A": Car
-# "B": Taxi
-# "C": Colectivo
-# "D": Moto
-# "E": Metro
-# "F": Bus
-# "G": Bicycle
-# "H": Walk
-#
-# AGE is coded as:
-#
-# "A": Less18
-# "B": 18to24
-# "C": 25to34
-# "D": 35to54
-# "E": 55to64
-# "F": 65more
-# 
-# EDUCATION is coded as:
-# 
-# "A": ELEMENTARY
-# "B": SECUNDARY
-# "C": PROFESS_TECH
-# "D": COLLEGE
-# "E": POSTGRAD
-#
-# INCOME is coded as (in pesos?):
-# 
-# "A": Less423
-# "B": 423to639
-# "C": 639to977
-# "D": 977to1550
-# "E": 1550to2380
-# "F": 2380more
-# 
-# TRAVEL_TIME is coded as:
-#
-# "A": 0-20 min
-# "B": 20-40 min
-# "C": 40-60 min
-# "D": 1h and more
-
-# Read the RData file:
-
-load("Dissonance_Santiago.RData")
-```
-
-```{r data-preparation, include=FALSE}
-
-# The master dataframe is processed for analysis. We plan to conduct two distinct types of analysis:
-#
-# 1. Who experiences dissonace?
-#
-# Analysis of dissonace using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.).
-In this case, dissonance is defined as follows:
-#
-# >> If the mode used is identical to the mode that the respondent associates with ATTRIBUTE (i.e.
-FREEDOM et al.), we consider that there is no dissonance; otherwise, we consider that there is dissonance.
-For example, if the respondent's main mode of transportation is Car, and the respondent associates Car with feelings of FREEDOM, then there is no dissonance.
-On the other hand, if the respondent's main mode of transportation is Car, but associates Walking with feelings of FREEDOM, there is dissonance.
-# 
-# Given this, we will calculate how frequently there is dissonance at different levels of AGE, EDUCATION, INCOME, MODE, TRAVEL_TIME. Tests of independence can be implemented.
-#
-# 2. For those respondents who experience dissonance, what mode(s) are better aligned with various affective values
-#
-# Analysis of dissonance using the mode USED and the mode respondents associated with ATTRIBUTE, then stratified by characteristics of respondents (i.e., AGE et al.) in this case, we see how frequently each mode was associated with ATTRIBUTE, given the main mode of transportation of the respondents.
-#
-# Here the dataframes are prepared to support these two types of analysis
-
-#####################################################################################
-# Prepare a dataframe for Analysis 1: Who experiences dissonance by affective value #
-#####################################################################################
-
-# First, select the variables needed from the master table, and code dissonance as 1 (no dissonance) or two (dissonance):
-
-Overall_dissonance <- master %>%
-  transmute(USED, 
-            FREEDOM_DISSONANCE = ifelse(USED == FREEDOM, 1, 2),
-            ENJOYMENT_DISSONANCE = ifelse(USED == ENJOYMENT, 1, 2),
-            HAPPINESS_DISSONANCE = ifelse(USED == HAPPINESS, 1, 2),
-            POVERTY_DISSONANCE = ifelse(USED == POVERTY, 1, 2),
-            LUXURY_DISSONANCE = ifelse(USED == LUXURY, 1, 2),
-            STATUS_DISSONANCE = ifelse(USED == STATUS, 1, 2),
-            SAFETY_DISSONANCE = ifelse(USED == SAFETY, 1, 2),
-            TIME_DISSONANCE = ifelse(USED == TIME, 1, 2),
-            EFFICIENCY_DISSONANCE = ifelse(USED == EFFICIENCY, 1, 2),
-            AGE,
-            EDUCATION,
-            INCOME,
-            TRAVEL_TIME)
-
-# Recode variables and convert to factors:
-
-Overall_dissonance <- Overall_dissonance %>%
-  mutate(USED = case_when(USED == "A" ~ "Car",
-                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
-                                  USED == "E" | USED == "F" ~ "Public",
-                                  USED == "G" | USED == "H" ~ "Active"),
-         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
-                         AGE == "D" ~ "35 - 54",
-                         AGE == "E" | AGE == "F" ~ "> 54"),
-         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
-                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
-                               EDUCATION == "E" ~ "Graduate"),
-         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
-                            INCOME == "C" | INCOME == "D" ~ "Middle",
-                            INCOME == "E" | INCOME == "F" ~ "High"),
-         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
-                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
-                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
-                                 TRAVEL_TIME == "D" ~ "> 60 min")) %>%
-  mutate(USED = factor(USED, levels = c("Car", "Active", "Public", "Other"), labels = c("Car", "Active", "Public", "Other")),
-         FREEDOM_DISSONANCE = factor(FREEDOM_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         ENJOYMENT_DISSONANCE = factor(ENJOYMENT_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         HAPPINESS_DISSONANCE = factor(HAPPINESS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         POVERTY_DISSONANCE = factor(POVERTY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         LUXURY_DISSONANCE = factor(LUXURY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         STATUS_DISSONANCE = factor(STATUS_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         SAFETY_DISSONANCE = factor(SAFETY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         TIME_DISSONANCE = factor(TIME_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         EFFICIENCY_DISSONANCE = factor(EFFICIENCY_DISSONANCE, levels = c(1, 2), labels = c("No Dissonance", "Dissonance")),
-         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
-         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
-         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
-         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))
-
-###############################################################################################
-# Prepare a dataframe for Analysis 2: What mode(s) align better with various affective values #
-###############################################################################################
-
-# First, split the responses regarding the modes associated with each attribute, so that we can record each mode selected individually:
-
-Modes_by_Attribute <- master %>% 
-    mutate(FREEDOM = strsplit(as.character(FREEDOM), ""),
-           ENJOYMENT = strsplit(as.character(ENJOYMENT), ""),
-           HAPPINESS = strsplit(as.character(HAPPINESS), ""),
-           POVERTY = strsplit(as.character(POVERTY), ""),
-           LUXURY = strsplit(as.character(LUXURY), ""),
-           STATUS = strsplit(as.character(STATUS), ""),
-           SAFETY = strsplit(as.character(SAFETY), ""),
-           TIME = strsplit(as.character(TIME), ""),
-           EFFICIENCY = strsplit(as.character(EFFICIENCY), ""))
-
-# Here, we convert each of the responses into an individual row and stack the resulting dataframes, after adding the name of the attribute for identification:
-
-Modes_by_Attribute <- rbind(data.frame(Modes_by_Attribute %>% 
-                                         select(-c(ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = FREEDOM, WEIGHT = WEIGHT_FREEDOM) %>%
-                                         unnest(IDEAL),
-                                       ATTRIBUTE = "FREEDOM"),
-                            data.frame(Modes_by_Attribute %>%
-                                         select(-c(FREEDOM, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = ENJOYMENT, WEIGHT = WEIGHT_ENJOYMENT) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "ENJOYMENT"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY, 
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM,
-                                                   WEIGHT_ENJOYMENT,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY, 
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>% 
-                                         rename(IDEAL = HAPPINESS, WEIGHT = WEIGHT_HAPPINESS) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "HAPPINESS"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = POVERTY, WEIGHT = WEIGHT_POVERTY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "POVERTY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   #LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   #WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = LUXURY, WEIGHT = WEIGHT_LUXURY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "LUXURY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   #STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   #WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = STATUS, WEIGHT = WEIGHT_STATUS) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "STATUS"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   TIME, 
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_TIME, 
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = SAFETY, WEIGHT = WEIGHT_SAFETY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "SAFETY"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   EFFICIENCY,
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_EFFICIENCY)) %>%
-                                         rename(IDEAL = TIME, WEIGHT = WEIGHT_TIME) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "TIME"),
-                            data.frame(Modes_by_Attribute %>% 
-                                         select(-c(FREEDOM, 
-                                                   ENJOYMENT, 
-                                                   HAPPINESS,
-                                                   POVERTY,
-                                                   LUXURY,
-                                                   STATUS,
-                                                   SAFETY,
-                                                   TIME, 
-                                                   WEIGHT_FREEDOM, 
-                                                   WEIGHT_ENJOYMENT, 
-                                                   WEIGHT_HAPPINESS,
-                                                   WEIGHT_POVERTY,
-                                                   WEIGHT_LUXURY,
-                                                   WEIGHT_STATUS,
-                                                   WEIGHT_SAFETY,
-                                                   WEIGHT_TIME)) %>%
-                                         rename(IDEAL = EFFICIENCY, WEIGHT = WEIGHT_EFFICIENCY) %>%
-                                         unnest(IDEAL), 
-                                       ATTRIBUTE = "EFFICIENCY"))
-
-# There are some missing values. Drop all NAs:
-
-Modes_by_Attribute <- drop_na(Modes_by_Attribute)
-
-# We now recode the variables:
-
-Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = case_when(USED == "A" ~ "Car",
-                                  USED == "B" | USED == "C" | USED == "D" ~ "Other",
-                                  USED == "E" | USED == "F" ~ "Public",
-                                  USED == "G" | USED == "H" ~ "Active"),
-         IDEAL = case_when(IDEAL == "A" ~ "Car",
-                                  IDEAL == "B" | IDEAL == "C" | IDEAL == "D" ~ "Other",
-                                  IDEAL == "E" | IDEAL == "F" ~ "Public",
-                                  IDEAL == "G" | IDEAL == "H" ~ "Active"),
-         AGE = case_when(AGE == "A" | AGE == "B" | AGE == "C" ~ "< 35",
-                         AGE == "D" ~ "35 - 54",
-                         AGE == "E" | AGE == "F" ~ "> 54"),
-         EDUCATION = case_when(EDUCATION == "A" | EDUCATION == "B" ~ "K-12",
-                               EDUCATION == "C" | EDUCATION == "D" ~ "Tech/Univ",
-                               EDUCATION == "E" ~ "Graduate"),
-         INCOME = case_when(INCOME == "A" | INCOME == "B" ~ "Low",
-                            INCOME == "C" | INCOME == "D" ~ "Middle",
-                            INCOME == "E" | INCOME == "F" ~ "High"),
-         TRAVEL_TIME = case_when(TRAVEL_TIME == "A" ~ "< 20 min",
-                                 TRAVEL_TIME == "B" ~ "20 - 40 min",
-                                 TRAVEL_TIME == "C" ~ "40 - 60 min",
-                                 TRAVEL_TIME == "D" ~ "> 60 min"))
-
-# After recoding the , there will be some duplicate entries, because a person may have attributed, say, feelings of freedom to walking and cycling, so in the table this will appear as two instances of "Active".
-This is ok, because each is weighted appropriately.
-
-# Convert to factors:
-
-Modes_by_Attribute <- Modes_by_Attribute %>%
-  mutate(USED = factor(USED, levels = c("Car", "Active", "Public", "Other"), labels = c("Car", "Active", "Public", "Other")),
-         IDEAL = factor(IDEAL, levels = c("Car", "Active", "Public", "Other"), labels = c("Car", "Active", "Public", "Other")),
-         AGE = factor(AGE, levels = c("< 35", "35 - 54", "> 54"), labels = c("< 35", "35 - 54", "> 54")),
-         EDUCATION = factor(EDUCATION, levels = c("K-12", "Tech/Univ", "Graduate"), labels = c("K-12", "Tech/Univ", "Graduate")),
-         INCOME = factor(INCOME, levels = c("Low", "Middle", "High"), labels = c("Low", "Middle", "High")),
-         TRAVEL_TIME = factor(TRAVEL_TIME, levels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min"), labels = c("< 20 min", "20 - 40 min", "40 - 60 min", "> 60 min")))
-```
-
-```{r cross-tabs-function, include=FALSE}
-
-## Define functions for crosstabs; these functions enhance the base crosstabs functions and make it easier to report cross tabulations in different ways.
-
-crosstab <- function (..., dec.places = NULL,
-                           type = NULL,
-                           style = "wide",
-                           row.vars = NULL,
-                           col.vars = NULL,
-                           percentages = TRUE, 
-                           addmargins = TRUE,
-                           subtotals=TRUE)
-
-###################################################################################
-#                                                                                 #
-# Function created by Dr Paul Williamson, Dept. of Geography and Planning,        #
-# School of Environmental Sciences, University of Liverpool, UK.                  #
-#                                                                                 #
-# Adapted from the function ctab() in the catspec packge.                         #
-#                                                                                 #
-# Version: 12th July 2013                                                         #
-#                                                                                 #
-# Output best viewed using the companion function print.crosstab()                #
-#                                                                                 #
-###################################################################################
-
-  #Declare function used to convert frequency counts into relevant type of proportion or percentage
-  {mk.pcnt.tbl <- function(tbl, type) {
-        a <- length(row.vars)
-        b <- length(col.vars)
-        mrgn <- switch(type, column.pct = c(row.vars[-a], col.vars), 
-                            row.pct = c(row.vars, col.vars[-b]),
-                            joint.pct = c(row.vars[-a], col.vars[-b]),
-                            total.pct = NULL)
-        tbl <- prop.table(tbl, mrgn)
-        if (percentages) {
-            tbl <- tbl * 100
-        }
-        tbl
-    }
-
-    #Find no. of vars (all; row; col) for use in subsequent code
-    n.row.vars <- length(row.vars)
-    n.col.vars <- length(col.vars)
-    n.vars <- n.row.vars + n.col.vars
-
-    #Check to make sure all user-supplied arguments have valid values
-    stopifnot(as.integer(dec.places) == dec.places, dec.places > -1)
-    #type: see next section of code
-    stopifnot(is.character(style))    
-    stopifnot(is.logical(percentages))
-    stopifnot(is.logical(addmargins))
-    stopifnot(is.logical(subtotals))
-    stopifnot(n.vars>=1)
-
-    #Convert supplied table type(s) into full text string (e.g. "f" becomes "frequency")
-    #If invalid type supplied, failed match gives user automatic error message
-    types <- NULL
-    choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
-    for (tp in type) types <- c(types, match.arg(tp, choices))
-    type <- types
-
-    #If no type supplied, default to 'frequency + total' for univariate tables and to
-    #'frequency' for multi-dimenstional tables
-
-    #For univariate table....
-    if (n.vars == 1) {
-      if (is.null(type)) {
-        # default = freq count + total.pct  
-        type <- c("frequency", "total.pct")
-        #row.vars <- 1
-      } else {
-        #and any requests for row / col / joint.pct must be changed into requests for 'total.pct'
-        type <- ifelse(type == "frequency", "frequency", "total.pct")
-      }
-    #For multivariate tables...
-    } else if (is.null(type)) {
-      # default = frequency count  
-      type <- "frequency"
-    }
-
-    #Check for integrity of requested analysis and adjust values of function arguments as required
-
-    if ((addmargins==FALSE) & (subtotals==FALSE)) {
-      warning("WARNING: Request to suppress subtotals (subtotals=FALSE) ignored because no margins requested (addmargins=FALSE)")
-      subtotals <- TRUE
-    }
-
-    if ((n.vars>1) & (length(type)>1) & (addmargins==TRUE)) {
-      warning("WARNING: Only row totals added when more than one table type requested")
-      #Code lower down selecting type of margin implements this...
-    }
-
-    if ((length(type)>1) & (subtotals==FALSE)) { 
-      warning("WARNING: Can only request supply one table type if requesting suppression of subtotals; suppression of subtotals not executed")
-      subtotals <- TRUE
-    }
-
-    if ((length(type)==1) & (subtotals==FALSE)) {
-      choices <- c("frequency", "row.pct", "column.pct", "joint.pct", "total.pct")
-      tp <- match.arg(type, choices)
-      if (tp %in% c("row.pct","column.pct","joint.pct")) {
-          warning("WARNING: subtotals can only be suppressed for tables of type 'frequency' or 'total.pct'")
-          subtotals<- TRUE
-         }
-    }
-
-    if ((n.vars > 2) & (n.col.vars>1) & (subtotals==FALSE)) 
-      warning("WARNING: suppression of subtotals assumes only 1 col var; table flattened accordingly")
-
-    if ( (subtotals==FALSE) & (n.vars>2) )  {
-    #If subtotals not required AND total table vars > 2
-    #Reassign all but last col.var as row vars
-    #[because, for simplicity, crosstabs assumes removal of subtotals uses tables with only ONE col var]
-    #N.B. Subtotals only present in tables with > 2 cross-classified vars...
-      if (length(col.vars)>1) {
-        row.vars <- c(row.vars,col.vars[-length(col.vars)])
-        col.vars <- col.vars[length(col.vars)]
-        n.row.vars <- length(row.vars)
-        n.col.vars <- 1
-      }
-    }
-
-    #If dec.places not set by user, set to 2 unlesss only one table of type frequency requested,
-    #in which case set to 0.  [Leaves user with possibility of having frequency tables with > 0 dp]
-    if (is.null(dec.places)) {
-      if ((length(type)==1) & (type[1]=="frequency")) {
-        dec.places <- 0
-      } else {
-        dec.places <-2
-      }
-    }
-
-    #Take the original input data, whatever form originally supplied in,
-    #convert into table format using requested row and col vars, and save as 'tbl'
-
-    args <- list(...)
-
-    if (length(args) > 1) {
-        if (!all(sapply(args, is.factor))) 
-            stop("If more than one argument is passed then all must be factors")
-        tbl <- table(...)
-    }
-    else {
-        if (is.factor(...)) {
-            tbl <- table(...)
-        }
-        else if (is.table(...)) {
-            tbl <- eval(...)
-        }
-        else if (is.data.frame(...)) {
-            #tbl <- table(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-              tbl <- table(...)
-            }
-            else {
-              var.names <- c(row.vars,col.vars)
-              A <- (...)
-              tbl <- table(A[var.names])
-              if(length(var.names==1)) names(dimnames(tbl)) <- var.names
-              #[table() only autocompletes dimnames for multivariate crosstabs of dataframes]
-            }
-        }
-        else if (class(...) == "ftable") {
-            tbl <- eval(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-                row.vars <- names(attr(tbl, "row.vars"))
-                col.vars <- names(attr(tbl, "col.vars"))
-            }
-            tbl <- as.table(tbl)
-        }
-        else if (class(...) == "ctab") {
-            tbl <- eval(...)
-            if (is.null(row.vars) && is.null(col.vars)) {
-                row.vars <- tbl$row.vars
-                col.vars <- tbl$col.vars
-            }
-            for (opt in c("dec.places", "type", "style", "percentages", 
-                "addmargins", "subtotals")) if (is.null(get(opt))) 
-                assign(opt, eval(parse(text = paste("tbl$", opt, 
-                  sep = ""))))
-            tbl <- tbl$table
-        }
-        else {
-            stop("first argument must be either factors or a table object")
-        }
-    }
-
-    #Convert supplied table style into full text string (e.g. "l" becomes "long")
-    style <- match.arg(style, c("long", "wide"))
-
-    #Extract row and col names to be used in creating 'tbl' from supplied input data
-    nms <- names(dimnames(tbl))
-    z <- length(nms)
-    if (!is.null(row.vars) && !is.numeric(row.vars)) {
-        row.vars <- order(match(nms, row.vars), na.last = NA)
-    }
-    if (!is.null(col.vars) && !is.numeric(col.vars)) {
-        col.vars <- order(match(nms, col.vars), na.last = NA)
-    }
-    if (!is.null(row.vars) && is.null(col.vars)) {
-        col.vars <- (1:z)[-row.vars]
-    }
-    if (!is.null(col.vars) && is.null(row.vars)) {
-        row.vars <- (1:z)[-col.vars]
-    }
-    if (is.null(row.vars) && is.null(col.vars)) {
-        col.vars <- z
-        row.vars <- (1:z)[-col.vars]
-    }
-
-    #Take the original input data, converted into table format using supplied row and col vars (tbl)
-    #and create a second version (crosstab) which stores results as percentages if a percentage table type is requested.
-    if (type[1] == "frequency") 
-      crosstab <- tbl
-    else 
-      crosstab <- mk.pcnt.tbl(tbl, type[1])
-
-    #If multiple table types requested, create and add these to 
-    if (length(type) > 1) {
-      tbldat <- as.data.frame.table(crosstab)
-      z <- length(names(tbldat)) + 1
-      tbldat[z] <- 1
-      pcntlab <- type
-      pcntlab[match("frequency", type)] <- "Count"
-      pcntlab[match("row.pct", type)] <- "Row %"
-      pcntlab[match("column.pct", type)] <- "Column %"
-      pcntlab[match("joint.pct", type)] <- "Joint %"
-      pcntlab[match("total.pct", type)] <- "Total %"
-      for (i in 2:length(type)) {
-          if (type[i] == "frequency") 
-              crosstab <- tbl
-          else crosstab <- mk.pcnt.tbl(tbl, type[i])
-          crosstab <- as.data.frame.table(crosstab)
-          crosstab[z] <- i
-          tbldat <- rbind(tbldat, crosstab)
-      }
-      tbldat[[z]] <- as.factor(tbldat[[z]])
-      levels(tbldat[[z]]) <- pcntlab
-      crosstab <- xtabs(Freq ~ ., data = tbldat)
-      names(dimnames(crosstab))[z - 1] <- ""
-    }
-
-    #Add margins if required, adding only those margins appropriate to user request
-    if (addmargins==TRUE) {
-
-      vars <- c(row.vars,col.vars)
-
-      if (length(type)==1) {
-      if (type=="row.pct") 
-        { crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
-          tbl <- addmargins(tbl,margin=c(vars[n.vars]))
-        }
-      else 
-        { if (type=="column.pct") 
-            { crosstab <- addmargins(crosstab,margin=c(vars[n.row.vars]))
-              tbl <- addmargins(tbl,margin=c(vars[n.row.vars]))
-            }
-          else 
-            { if (type=="joint.pct") 
-              { crosstab <- addmargins(crosstab,margin=c(vars[(n.row.vars)],vars[n.vars])) 
-                tbl <- addmargins(tbl,margin=c(vars[(n.row.vars)],vars[n.vars])) 
-              }
-              else #must be total.pct OR frequency
-                { crosstab <- addmargins(crosstab)
-                  tbl <- addmargins(tbl)
-                }
-            }
-  	     } 
-      }
-
-      #If more than one table type requested, only adding row totals makes any sense...
-      if (length(type)>1) {
-        crosstab <- addmargins(crosstab,margin=c(vars[n.vars]))
-        tbl <- addmargins(tbl,margin=c(vars[n.vars]))
-      }
-
-    }
-
-    #If subtotals not required, and total vars > 2, create dataframe version of table, with relevent
-    #subtotal rows / cols dropped [Subtotals only present in tables with > 2 cross-classified vars]
-    t1 <- NULL
-    if ( (subtotals==FALSE) & (n.vars>2) )  {
-
-    #Create version of crosstab in ftable format
-    t1 <- crosstab 
-    t1 <- ftable(t1,row.vars=row.vars,col.vars=col.vars)
-
-    #Convert to a dataframe
-    t1 <- as.data.frame(format(t1),stringsAsFactors=FALSE)
-
-    #Remove backslashes from category names AND colnames
-    t1 <- apply(t1[,],2, function(x) gsub("\"","",x))
-    #Remove preceding and trailing spaces from category names to enable accurate capture of 'sum' rows/cols
-    #[Use of grep might extrac category labels with 'sum' as part of a longer one or two word string...]
-    t1 <- apply(t1,2,function(x) gsub("[[:space:]]*$","",gsub("^[[:space:]]*","",x)))
-
-    #Reshape dataframe to that variable and category labels display as required
-    #(a) Move col category names down one row; and move col variable name one column to right
-    t1[2,(n.row.vars+1):ncol(t1)] <- t1[1,(n.row.vars+1):ncol(t1)]
-    t1[1,] <- ""
-    t1[1,(n.row.vars+2)] <- t1[2,(n.row.vars+1)]    
-    #(b) Drop the now redundant column separating the row.var labels from the table data + col.var labels
-    t1 <- t1[,-(n.row.vars+1)]
-
-    #In 'lab', assign category labels for each variable to all rows (to allow identification of sub-totals) 
-    lab <- t1[,1:n.row.vars]
-    for (c in 1:n.row.vars) {
-      for (r in 2:nrow(lab)) {
-        if (lab[r,c]=="") lab[r,c] <- lab[r-1,c]  
-      }
-    }
-
-    lab <- (apply(lab[,1:n.row.vars],2,function(x) x=="Sum"))
-    lab <- apply(lab,1,sum)
-    #Filter out rows of dataframe containing subtotals
-
-    t1 <- t1[((lab==0) | (lab==n.row.vars)),]
-
-    #Move the 'Sum' label associated with last row to the first column; in the process
-    #setting the final row labels associated with other row variables to ""
-    t1[nrow(t1),1] <- "Sum"
-    t1[nrow(t1),(2:n.row.vars)] <- ""
-
-    #set row and column names to NULL
-    rownames(t1) <- NULL
-    colnames(t1) <- NULL
-
-    }
-
-    #Create output object 'result' [class: crosstab]
-    result <- NULL
-    #(a) record of argument values used to produce tabular output
-    result$row.vars <- row.vars
-    result$col.vars <- col.vars
-    result$dec.places <- dec.places
-    result$type <- type
-    result$style <- style
-    result$percentages <- percentages
-    result$addmargins <- addmargins
-    result$subtotals <- subtotals
-
-    #(b) tabular output [3 variants]
-    result$table <- tbl  #Stores original cross-tab frequency counts without margins [class: table]
-    result$crosstab <- crosstab #Stores cross-tab in table format using requested style(frequency/pct) and table margins (on/off)
-                                #[class: table]  
-    result$crosstab.nosub <- t1  #crosstab with subtotals suppressed [class: dataframe; or NULL if no subtotals suppressed]  
-    class(result) <- "crosstab"
-
-    #Return 'result' as output of function
-    result
-}
-```
-
-Introduction
-===================
-
-Transportation planning for decades has focused on providing mobility for the private automobile.
-This is a model of development that was initially introduced in North America as a solution to problems created by rapid urbanization, and that was eventually copied elsewhere [@Brown2009planning;@Angotti1996latin].
-Despite the initial promise of automotive technology, it is now evident that mobility centred on the private automobile has given rise to a litany of maladies that are in urgent need of correction.
-This includes environmental concerns [i.e., climate change; @Chapman2007transport] as well as numerous other social [@Boschman2008toward; @Lucas2012transport; @Lucas2019evolution], health [@Khreis2016health; @Milne2012public], and equity issues [@Bocarejo2012transport; @Martens2012justice; @Pereira2017distributive].
-
-As the real impacts of our societal dependence on the private autombobile have become increasingly evident, the transportation agenda has aimed to shift focus to the reduction of car use and towards the creation of mobility polycultures that offer a broader menu of transportation alternatives than primarily (or even just) the private automobile [@Miller2011collaborative].
-In order to successfully achieve this goal, it is essential not only to provide the services and facilities that support public transportation and active travel, but also to attract new users to these modes of transportation [@Ettema2011satisfaction].
-Within this context, it has been argued that sustainable transportation policies require all participants in the transportation system to challenge what Gossling and Cohen [-@Gossling2014sustainable] termed _transportation taboos_: deep-seated ideas concerning the contribution to emissions by individuals, the inequality of market-based approaches, and the social and psychological functions of transportation.
-With respect to the latter, it is important to move beyond a purely utilitarian focus if we are to understand how the affective value of the transportation experience can be leveraged to improve alternative transportation - particularly transit and active modes [@Anable2005work; @Domarchi2008effect; @Gatersleben2007affective; @Steg2005car].
-
-A useful lens to investigate the social and psychological functions of transportation is by means of the concept of subjective wellbeing [SWB; see, inter alia, @Devos2013travel; and @Chatterjee2019commuting].
-SWB is defined by the OECD as “[g]ood mental states, including all of the various evaluations, positive and negative, that people make of their lives, and the affective reactions of people to their experiences” [@oecd2013oecd, p.
-10].
-As memorably put by Steg [-@Steg2005car]: is the use of car a must, or is it a lust?
-A close alignment, or consonance, between affective values and the mode of transportation used to travel can result in greater subjective wellbeing and increase the probability of choosing that mode  (i.e., by satisfying the _lust_); on the other hand, dissonance, that is, the lack of concordance between the mode used and affective values would be detrimental to subjective wellbeing, especially of those for whom the use of the mode is a _must_ [@Devos2019satisfaction; @Mokhtarian2018travel].
-With these considerations in mind, one aim of the present research is to investigate _who_ experiences dissonance with respect to their primary mode of travel and affective values, namely freedom, enjoyment, happiness, feelings of poverty, luxury, and status.
-Furthermore, it is possible, even if use of a particular mode is a _must_, that travellers may still _lust_ for something else - in other words, the grass may in fact look greener from the window of the car.
-For this reason, we also aim to investigate which mode or modes are most commonly associated with affective values, with a focus on those travellers who experience dissonance in their primary mode.
-
-Research is based on data collected from a sample of travellers in the city of Santiago in Chile.
-Survey respondents were asked about their primary mode of travel, and also about the mode or modes that they associate with the affective values mentioned above.
-The paper contributes to the literature in three ways, as follows:
-
-1.
-The research reported here contributes to an emerging literature on the topic of transportation and affective values in the context of the Global South [@Alayyash2019commute; @Bejarano2017user; @Shao2019analysis; @Van2014effect; @Zorrilla2019exploring]; to the best of our knowledge, the case of Chile has not yet been reported.
-
-2.
-Although there is an extensive literature on the enjoyment of commute and other affective values [see for instance @Paez2010enjoyment; @Redmond2001positive; @Whalen2013mode; @Ye2017satisfaction], from a hedonic and even eudaimonic perspectives the analysis has yet to be applied more fully in terms of distributional issues – i.e.
-which groups more commonly experience dissonance [see @Devos2018people].
-
-3.
-The analysis shows the attitudes of people towards their primary mode and their perception towards ‘ideal modes’ – implying their preferences, even in situations when their ideal mode is not part of their actual choice set.
-More concretely, the results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least.
-For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.
-We also find that there are some substantial variations in dissonance by age, education, income, and typical commute time.
-The attitudes of travellers towards transport modes are critical factors to be considered by policy-makers in case they want to promote and increase the use of public transport or active modes [@Bornioli2019affective; @Devos2017travel; @Devos2019satisfying; @Garling2019role; @Redman2013quality].
-
-The structure of the paper is as follows.
-After these introductory remarks, we follow up with a background section that reviews the literature.
-Next, we discuss the case study and data used in the research.
-Then, the analysis and results are presented, before concluding with some discussion and directions for future research.
-
-Background
-===================
-
-A consensus has emerged in the transportation community regarding the need to complement the traditional utilitarian perspective of transportation by looking at mobility and transport issues from the lens of their affective functions.
-The affective value of transportation in turn is important due to its potential to improve or detract from SWB.
-One of the primary ways to explore this has been the satisfaction that travelers feel towards their every day mobility experience [e.g., @Bergstad2011subjective].
-As a consequence, there is a wealth of research on satisfaction with the use of different modes of transportation.
-For example, numerous studies report that car users often have a higher level of satisfaction compared to other transport modes [@Bergstad2011affective; @Eriksson2013perceived; @Redmond2001positive; @Whalen2013mode; but see @Handy2019commute].
-In a similar way, there are multiple reports that active travel also tends to yield high levels of satisfaction [@Gatersleben2007affective; @Smith2017commute; @Stlouis2014happy; @Paez2010enjoyment; @Whalen2013mode; @Handy2019commute], In contrast, public transport users tend to assess their experience more negatively [@Abenoza2017travel; @Devos2016travel; @Gatersleben2007affective; @Handy2019commute; @Paez2010enjoyment].
-Multi-modal trips also influence satisfaction levels; for instance, when an individual chooses a particular mode of transportation, she will report a higher level of satisfaction with that chosen mode – perhaps as a form of _post hoc_ validation [@Susilo2014exploring].
-
-While the use of travel satisfaction has been mainly used in the context of daily trips – typically linked to cost-benefit and utilitarian measurements –, the evaluation of Subjective Wellbeing (SWB) over time has risen as an alternative measure.
-In the field of travel behaviour, Ettema et al.
-[-@Ettema2010out, p.
-725] define SWB as the degree to which an individual positively evaluates the overall quality of their lives, where the general life satisfaction encompasses a more extended temporality – which implies assuming a tendency to be more stable over time.
-This concept has prompted a growing literature that complements and applies SWB in a broader range of satisfaction scales and situations.
-The definition of other factors such as travel choice mode, attitudes and external elements of the built environment have been studied for a broader understanding of the changes produced in the SWB [e.g., @Handy2019commute].
-As these factors do not necessarily apply to the general life satisfaction on the long term, the studies have aimed to determine both the direct and indirect effects on the perception of users [see, e.g., @Ye2017satisfaction].
-Other concepts have also emerged as the Satisfaction with Travel Scale (STS), a measurement devised by Ettema et al.
-[-@Ettema2011satisfaction], as well as different scales based on people’s travel perceptions.
-De Vos et al.
-[-@Devos2015satisfying], for instance, explore in detail the underlying dimensions of the affective domain of STS on which SWB is based [for more on STS see also @Friman2013psychometric].
-
-Recent literature on SWB and its link with transport have demonstrated a relationship between people’s perceptions and satisfaction with their daily travel [e.g., @Smith2017commute; @Stlouis2014happy; @Mokhtarian2018travel].
-Scholars have shown that accessibility has been the most developed factor that influences people’s wellbeing [@Delbosc2012role], and activities have a direct impact on travel satisfaction [@Bergstad2011subjective].
-Delbosc [-@Delbosc2012role, p.
-28], for instance, has summarised the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health.
-However, understanding the components affecting people’s perceptions implies the differentiation between affective (also named as symbolic-affective) and instrumental values [@Bergstad2011affective].
-Steg et al.
-(2011) have compared symbolic-affective opposed to instrumental-reasoned motives based on car-use, and other studies have also found associations between affective and symbolic aspects of car-use [see, e.g., @Gatersleben2007affective; @Lois2009relationship].
-Previous studies have also demonstrated how socio-demographic factors affect the levels of SWB.
-The effect of income on SWB [@Clark1996satisfaction; @Ferrer2005income]; education and unemployment [@Argyle1999causes]; age [@Diener1997subjective], and gender [@Tesch2008gender] have been extensively studied.
-Recent research also suggests the links between commuting, SWB and emotional wellbeing assessment (**Olson et al.
-2013**; **Kahneman et al.
-2004**).
-However, more research is needed to understand how these socio-demographic variables connect as well with the affective responses to mode of travel [@Stlouis2014happy].
-
-The research needs already recognized in the developed world are also markedly acute in the context of the Global South, where historical inequality has tended to create a symbolic attachment to the automobile, in addition to negative connotations for public transport and active travel [@Zorrilla2019exploring].
-In this way, there is an emerging literature that investigates affective factors in travel behaviour in a number of developing countries.
-A cross-country study in Asia revealed that the affective factors of public transportation and car use are important, and in particular the social orderliness of transit was suggested as a way to make this mode more attractive to users [@Van2014effect].
-In terms of active travel, a study in China found that attitudes that embrace new styles and technologies despite their cost are associated with the intention to continue using shared bicycles [@Shao2019analysis].
-The importance of affective factors for policy and planning is further highlighted by research in Colombia that shows how users felt proud using a bicycle shared system, in addition to experiencing feelings of belonging to a civic culture and the enjoyment and pleasure of travel itself [@Bejarano2017user].
-This paper contributes to further our understanding of affective values in travel behaviour in a developing country.
-
-Case Study and Data
-===================
-
-## Context
-
-The case study to contextualize the discussion is Santiago de Chile, the capital of one of the countries with the highest levels of inequality in terms of socio-economic distribution in the world.
-These inequities have manifested in a disproportionate expense in transport by the different socioe-conomic sectors, a disproportion in travel times and distances travelled.
-On the other hand, car ownership and use of public transport in the capital are directly conditioned by strong spatial segregation – the higher the income, the higher is the use of the automobile; conversely, and the lower the income, the higher is the predisposition to use public transport.
-Although transport is a reflection of deep inequities in various dimensions, it has triggered an exceptional discomfort and disagreement with the daily travel experience and quality of life.
-
-## Sample
-
-The study is based on a survey conducted in the city of Santiago during the months of November and December 2016, that is, the end of the Spring and beginning of Summer.
-The survey collected information on a wide range of travel and related issues.
-The data collection considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012.
-An equal representation of both genders and a representation of the proportion of inhabitants per area were chosen as relevant characteristics of the sample.
-In total, there were $n=451$ valid surveys, although not every survey was complete and there were missing responses for some answers.
-
-The survey was structured in eight sections, as follows: 1) Individual characteristics of respondent; 2) Health; 3) Feelings and emotions; 4) Reasons for travel and planning travel; 5) Social interaction; 6) Nature and sustainability; 7) Information and telecommunications; 8) Built environment; and 9) Commuting.
-For the present study, we draw data from sections 1), 3) and 9).
-In terms of individual characteristics of the respondents and their commute, participants were asked about basic socio-demographic information, including age, level of education, income, and the typical duration of their regular commute.
-The descriptive statistics of the sample appear in Figure \ref{fig:descriptive-statistics}.
-The sample tends to be younger, and well-educated, with an almost uniform distribution of income levels.
-The trend in typical commute time is towards longer commutes.
-
-```{r plot-descriptive-statistics, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:descriptive-statistics}Descriptive statistics of the sample"}
-
-# Bar plots with descriptive statistics for the sample
-
-age_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = AGE)) +
-  geom_bar() +
-  theme_tufte() +
-  xlab("Age of respondents") +
-  theme(axis.text.x = element_text(angle = 90))
-
-education_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = EDUCATION)) +
-  geom_bar() +
-  theme_tufte() +
-  xlab("Education level of respondents") +
-  theme(axis.text.x = element_text(angle = 90))
-
-income_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = INCOME)) +
-  geom_bar() +
-  theme_tufte() +
-  xlab("Income level of respondents") +
-  theme(axis.text.x = element_text(angle = 90))
-
-time_plot <- ggplot(data = drop_na(Overall_dissonance), aes(x = TRAVEL_TIME)) +
-  geom_bar() +
-  theme_tufte() +
-  xlab("Duration of regular commute") +
-  theme(axis.text.x = element_text(angle = 90))
-
-grid.arrange(age_plot, education_plot, income_plot, time_plot)
-```
-
-In addition, respondents were asked about their primary mode of travel for their regular commute.
-The modes available were Car, Taxi, Colectivo (a form of shared ride, intermediate in flexibility and capacity between taxi and bus); Motorcycle; Metro; Bus; Bicycle; Walking.
-As seen in the top panel of Figure \ref{fig:primary-mode-travel}, the three most common modes of travel are Metro, Bus, and Car, followed by Walking and Biycle.
-For the analysis, we aggregate these modes into the following categories (bottom panel of Figure \ref{fig:primary-mode-travel}): Car, Active (Walking + Bicycle), Public (Metro + Bus), and Other (Taxi + Colectivo + Motorcycle).
-
-```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
-mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "B", "C", "D", "E", "F", "G", "H"),
-                                     labels = c("Car", "Taxi", "Colectivo", "Motorcycle", "Metro", "Bus", "Bicycle", "Walk")))) +
-  geom_bar() +
-  xlab("Primary Mode of Travel") +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-
-mode_plot2 <- ggplot(data = Overall_dissonance, aes(x = USED)) +
-  geom_bar() +
-  xlab("Primary Mode of Travel") +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-
-grid.arrange(mode_plot1, mode_plot2, nrow = 2)
-```
-
-Of particular interest for the present study is the following question in Part 3) of the survey:
-
->> Q: Please indicate the mode(s) of transport that you relate to the following feelings and concepts
-
-The question was asked for each of the following affective values: Freedom; Enjoyment; Happiness; Poverty; Luxury; and Status.
-The respondents were not constrained to select only one alternative, but could indicate by means of a checkbox any and all modes that they felt aligned with each affective value.
-This allows us to do an analysis of modal dissonance, a concept introduced into the transportation literature by Schwanen and Mokhtarian [-@Schwanen2004extent] based on earlier work by Feldman [-@Feldman1990settlement].
-Residential neighborhood-type dissonance was defined by Schwanen and Mokhtarian [-@Schwanen2004extent] as an incongruence in terms of the the land use patterns at the place of residence of an individual, and the individual's preferences.
-The concept of dissonance has since been extended in the travel behavior literature to encompass the mismatch between the choices individuals make, and the alternatives that would enable users to experience affective or instrumental values.
-This includes, for example, travel mode dissonance [@Devos2018people].
-
-Based on the primary mode of travel and the questions about affective values, we derived a series of travel mode dissonance variables according to the following rule:
-$$
-D_i = 
-\begin{cases}
-0 & if \text{ primary mode} = \text{mode associated with value } i\\
-1 & \text{ otherwise}
-\end{cases}
-$$
-Therefore, if a respondent's primary mode of travel is Car, but indicated any other mode or modes in relation to Freedom, the respondent experienced dissonance:
-$$
-D_{\text{Freedom}} = 1
-$$
-
-Furthermore, we also expanded the responses to account for all modes identified by respondents in relation to the affective values.
-However, to avoid double counting the respondents in our frequency tabulations, we also calculated a sample weight that was the inverse of the number of modes selected in response to each affective value.
-For instance, if a respondent selected two modes in relation to affective value $i$, the two modes receive a weight of $1/2$; if a respondent selected three modes, then their weights are $1/3$; and so on.
-In this way we do not treat unfairly those who selected only one mode, and the sum of all weighted modes is equal to the sample size.
-
-Analysis and Results
-==========
-
-In what follows, analysis is done on two related but distinct questions.
-The first part of the analysis seeks to understand _who_ experiences dissonance, and the second part, building off that, aims to explore which modes of travel are more commonly identified as embodying affective values by those travellers who experience dissonance.
-
-Please note that this document was prepared using R Markdown and contains reproducible analysis.
-The R markdown file, along with the data file needed to reproduce the analysis, can be downloaded from the following anonymous Drive folder:
-
-https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg
-
-```{r cross-with-instrumental, include=FALSE, eval=FALSE}
-
-# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)
-
-## Age
-
-age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
-age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-age_by_safety <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "SAFETY_DISSONANCE", type = "r")
-age_by_time <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "TIME_DISSONANCE", type = "r")
-age_by_efficiency <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Education
-
-education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
-education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-education_by_safety <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "SAFETY_DISSONANCE", type = "r")
-education_by_time <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "TIME_DISSONANCE", type = "r")
-education_by_efficiency <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Income
-
-income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-income_by_safety <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "SAFETY_DISSONANCE", type = "r")
-income_by_time <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "TIME_DISSONANCE", type = "r")
-income_by_efficiency <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Mode
-
-mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
-mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-mode_by_safety <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "SAFETY_DISSONANCE", type = "r")
-mode_by_time <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "TIME_DISSONANCE", type = "r")
-mode_by_efficiency <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-## Travel Time
-
-time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-time_by_safety <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "SAFETY_DISSONANCE", type = "r")
-time_by_time <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "TIME_DISSONANCE", type = "r")
-time_by_efficiency <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "EFFICIENCY_DISSONANCE", type = "r")
-
-```
-
-```{r cross-without-instrumental, include=FALSE}
-
-# Create cross tabulations by each respondent characteristic (i.e., AGE, EDUCATION, INCOME, mode USED, and TRAVEL_TIME)
-
-## Age
-
-age_by_freedom <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "FREEDOM_DISSONANCE", type = "r")
-age_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-age_by_happiness <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-age_by_poverty <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "POVERTY_DISSONANCE", type = "r")
-age_by_luxury <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "LUXURY_DISSONANCE", type = "r")
-age_by_status <- crosstab(Overall_dissonance, row.vars = "AGE", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Education
-
-education_by_freedom <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "FREEDOM_DISSONANCE", type = "r")
-education_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-education_by_happiness <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-education_by_poverty <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "POVERTY_DISSONANCE", type = "r")
-education_by_luxury <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "LUXURY_DISSONANCE", type = "r")
-education_by_status <- crosstab(Overall_dissonance, row.vars = "EDUCATION", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Income
-
-income_by_freedom <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-income_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-income_by_happiness <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-income_by_poverty <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "POVERTY_DISSONANCE", type = "r")
-income_by_luxury <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "LUXURY_DISSONANCE", type = "r")
-income_by_status <- crosstab(Overall_dissonance, row.vars = "INCOME", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Mode
-
-mode_by_freedom <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "FREEDOM_DISSONANCE", type = "r")
-mode_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-mode_by_happiness <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-mode_by_poverty <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "POVERTY_DISSONANCE", type = "r")
-mode_by_luxury <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "LUXURY_DISSONANCE", type = "r")
-mode_by_status <- crosstab(Overall_dissonance, row.vars = "USED", col.vars = "STATUS_DISSONANCE", type = "r")
-
-## Travel Time
-
-time_by_freedom <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "FREEDOM_DISSONANCE", type = "r")
-time_by_enjoyment <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "ENJOYMENT_DISSONANCE", type = "r")
-time_by_happiness <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "HAPPINESS_DISSONANCE", type = "r")
-time_by_poverty <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "POVERTY_DISSONANCE", type = "r")
-time_by_luxury <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "LUXURY_DISSONANCE", type = "r")
-time_by_status <- crosstab(Overall_dissonance, row.vars = "TRAVEL_TIME", col.vars = "STATUS_DISSONANCE", type = "r")
-
-```
-
-```{r collect-cross-tabulation-results-with-instrumental, include=FALSE, eval=FALSE}
-
-# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES
-
-## Age
-
-age_results <- cbind(age_by_freedom$crosstab, 
-                     age_by_enjoyment$crosstab, 
-                     age_by_happiness$crosstab,
-                     age_by_safety$crosstab,
-                     age_by_time$crosstab,
-                     age_by_efficiency$crosstab)
-
-# Drop the row totals
-age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-age_results <- age_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-age_results <- age_results %>%
-  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(age_by_happiness$table)$p.value,
-         chi2.safety = summary(age_by_safety$table)$p.value,
-         chi2.time = summary(age_by_time$table)$p.value,
-         chi2.efficiency = summary(age_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Education
-
-education_results <- cbind(education_by_freedom$crosstab, 
-                     education_by_enjoyment$crosstab, 
-                     education_by_happiness$crosstab,
-                     education_by_safety$crosstab,
-                     education_by_time$crosstab,
-                     education_by_efficiency$crosstab)
-
-# Drop the row totals
-education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-education_results <- education_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-education_results <- education_results %>%
-  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(education_by_happiness$table)$p.value,
-         chi2.safety = summary(education_by_safety$table)$p.value,
-         chi2.time = summary(education_by_time$table)$p.value,
-         chi2.efficiency = summary(education_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Income
-
-income_results <- cbind(income_by_freedom$crosstab, 
-                     income_by_enjoyment$crosstab, 
-                     income_by_happiness$crosstab,
-                     income_by_safety$crosstab,
-                     income_by_time$crosstab,
-                     income_by_efficiency$crosstab)
-
-# Drop the row totals
-income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-income_results <- income_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-income_results <- income_results %>%
-  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(income_by_happiness$table)$p.value,
-         chi2.safety = summary(income_by_safety$table)$p.value,
-         chi2.time = summary(income_by_time$table)$p.value,
-         chi2.efficiency = summary(income_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Mode USED
-
-mode_results <- cbind(mode_by_freedom$crosstab, 
-                     mode_by_enjoyment$crosstab, 
-                     mode_by_happiness$crosstab,
-                     mode_by_safety$crosstab,
-                     mode_by_time$crosstab,
-                     mode_by_efficiency$crosstab)
-
-# Drop the row totals
-mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-mode_results <- mode_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-mode_results <- mode_results %>%
-  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(mode_by_happiness$table)$p.value,
-         chi2.safety = summary(mode_by_safety$table)$p.value,
-         chi2.time = summary(mode_by_time$table)$p.value,
-         chi2.efficiency = summary(mode_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-
-## Time
-
-time_results <- cbind(time_by_freedom$crosstab, 
-                     time_by_enjoyment$crosstab, 
-                     time_by_happiness$crosstab,
-                     time_by_safety$crosstab,
-                     time_by_time$crosstab,
-                     time_by_efficiency$crosstab)
-
-# Drop the row totals
-time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Safety", "Time", "Efficiency")
-
-# Convert to dataframe and make the rownames a variable
-time_results <- time_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-time_results <- time_results %>%
-  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(time_by_happiness$table)$p.value,
-         chi2.safety = summary(time_by_safety$table)$p.value,
-         chi2.time = summary(time_by_time$table)$p.value,
-         chi2.efficiency = summary(time_by_efficiency$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Safety,
-         chi2.safety,
-         Time,
-         chi2.time,
-         Efficiency,
-         chi2.efficiency)
-```
-
-```{r collect-cross-tabulation-results-without-instrumental, include=FALSE}
-
-# Collect the cross tabulations for each of the respondent's characteristics and the ATTRIBUTES
-
-## Age
-
-age_results <- cbind(age_by_freedom$crosstab, 
-                     age_by_enjoyment$crosstab, 
-                     age_by_happiness$crosstab,
-                     age_by_poverty$crosstab,
-                     age_by_luxury$crosstab,
-                     age_by_status$crosstab)
-
-# Drop the row totals
-age_results <- age_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(age_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-age_results <- age_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-age_results <- age_results %>%
-  mutate(chi2.freedom = summary(age_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(age_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(age_by_happiness$table)$p.value,
-         chi2.poverty = summary(age_by_poverty$table)$p.value,
-         chi2.luxury = summary(age_by_luxury$table)$p.value,
-         chi2.status = summary(age_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Education
-
-education_results <- cbind(education_by_freedom$crosstab, 
-                     education_by_enjoyment$crosstab, 
-                     education_by_happiness$crosstab,
-                     education_by_poverty$crosstab,
-                     education_by_luxury$crosstab,
-                     education_by_status$crosstab)
-
-# Drop the row totals
-education_results <- education_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(education_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-education_results <- education_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-education_results <- education_results %>%
-  mutate(chi2.freedom = summary(education_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(education_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(education_by_happiness$table)$p.value,
-         chi2.poverty = summary(education_by_poverty$table)$p.value,
-         chi2.luxury = summary(education_by_luxury$table)$p.value,
-         chi2.status = summary(education_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Income
-
-income_results <- cbind(income_by_freedom$crosstab, 
-                     income_by_enjoyment$crosstab, 
-                     income_by_happiness$crosstab,
-                     income_by_poverty$crosstab,
-                     income_by_luxury$crosstab,
-                     income_by_status$crosstab)
-
-# Drop the row totals
-income_results <- income_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(income_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-income_results <- income_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-income_results <- income_results %>%
-  mutate(chi2.freedom = summary(income_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(income_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(income_by_happiness$table)$p.value,
-         chi2.poverty = summary(income_by_poverty$table)$p.value,
-         chi2.luxury = summary(income_by_luxury$table)$p.value,
-         chi2.status = summary(income_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Mode USED
-
-mode_results <- cbind(mode_by_freedom$crosstab, 
-                     mode_by_enjoyment$crosstab, 
-                     mode_by_happiness$crosstab,
-                     mode_by_poverty$crosstab,
-                     mode_by_luxury$crosstab,
-                     mode_by_status$crosstab)
-
-# Drop the row totals
-mode_results <- mode_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(mode_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-mode_results <- mode_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-mode_results <- mode_results %>%
-  mutate(chi2.freedom = summary(mode_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(mode_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(mode_by_happiness$table)$p.value,
-         chi2.poverty = summary(mode_by_poverty$table)$p.value,
-         chi2.luxury = summary(mode_by_luxury$table)$p.value,
-         chi2.status = summary(mode_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-
-## Time
-
-time_results <- cbind(time_by_freedom$crosstab, 
-                     time_by_enjoyment$crosstab, 
-                     time_by_happiness$crosstab,
-                     time_by_poverty$crosstab,
-                     time_by_luxury$crosstab,
-                     time_by_status$crosstab)
-
-# Drop the row totals
-time_results <- time_results[,c(2, 5, 8, 11, 14, 17)]
-
-# Change column names
-colnames(time_results) <- c("Freedom", "Enjoyment", "Happiness", "Poverty", "Luxury", "Status")
-
-# Convert to dataframe and make the rownames a variable
-time_results <- time_results %>%
-  as.data.frame() %>%
-  rownames_to_column()
-
-# Add significance of chi2 tests
-time_results <- time_results %>%
-  mutate(chi2.freedom = summary(time_by_freedom$table)$p.value,
-         chi2.enjoyment = summary(time_by_enjoyment$table)$p.value,
-         chi2.happiness = summary(time_by_happiness$table)$p.value,
-         chi2.poverty = summary(time_by_poverty$table)$p.value,
-         chi2.luxury = summary(time_by_luxury$table)$p.value,
-         chi2.status = summary(time_by_status$table)$p.value) %>%
-  dplyr::select(rowname, 
-         Freedom, 
-         chi2.freedom,
-         Enjoyment,
-         chi2.enjoyment,
-         Happiness,
-         chi2.happiness,
-         Poverty,
-         chi2.poverty,
-         Luxury,
-         chi2.luxury,
-         Status,
-         chi2.status)
-```
-
-```{r crosstab-all-results-with-instrumental, include=FALSE, eval=FALSE}
-
-# Here we bind all the results into a single dataframe for printing
-
-xtab_results <- rbind(age_results,
-                      education_results,
-                      income_results,
-                      mode_results,
-                      time_results) %>%
-  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
-         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
-         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
-         chi2.safety = ifelse(chi2.safety >= 0.001, paste0(round(chi2.safety, 4)), "$<0.001$"),
-         chi2.time = ifelse(chi2.time >= 0.001, paste0(round(chi2.time, 4)), "$<0.001$"),
-         chi2.efficiency = ifelse(chi2.efficiency >= 0.001, paste0(round(chi2.efficiency, 4)), "$<0.001$"))
-
-xtab_results[10:13, 3] <- "$< 0.001$" # Edit the format of these cells to avoid six cells collapsing together in table
-```
-
-```{r crosstab-all-results-without-instrumental, echo=FALSE}
-
-# Here we bind all the results into a single dataframe for printing
-
-xtab_results <- rbind(age_results,
-                      education_results,
-                      income_results,
-                      mode_results,
-                      time_results) %>%
-  mutate(chi2.freedom = ifelse(chi2.freedom >= 0.001, paste0(round(chi2.freedom, 4)), "$<0.001$"),
-         chi2.enjoyment = ifelse(chi2.enjoyment >= 0.001, paste0(round(chi2.enjoyment, 4)), "$<0.001$"),
-         chi2.happiness = ifelse(chi2.happiness >= 0.001, paste0(round(chi2.happiness, 4)), "$<0.001$"),
-         chi2.poverty = ifelse(chi2.poverty >= 0.001, paste0(round(chi2.poverty, 4)), "$<0.001$"),
-         chi2.luxury = ifelse(chi2.luxury >= 0.001, paste0(round(chi2.luxury, 4)), "$<0.001$"),
-         chi2.status = ifelse(chi2.status >= 0.001, paste0(round(chi2.status, 4)), "$<0.001$"))
-
-xtab_results[10:13, 3] <- "$< 0.001$" # Edit the format of these cells to avoid six cells collapsing together in table
-```
-
-## Who experiences dissonance?
-
-To investigate the first question in our analysis, we create contingency tables that tabulate the frequency of dissonance with respect to each affective value, stratified by the attributes of Age, Education, Income, Primary Mode of Travel, and typical Commute Time.
-Table \ref{tab:cross-tabulation-results} presents the frequency (in percentage) of dissonance, in other words, the percentage of respondents out of the total in their stratum who indicated mode or mode(s) for the affective value that do not correspond to their primary mode of travel.
-
-As seen in the table, there are five characteristics of the respondents and their commutes that we use in the analysis.
-Three of these categories are socio-economic and demographic, namely age, level of education, and income.
-The other two are transportation related, namely primary mode of travel and commute time.
-The frequency tables were tested in every case by means of the $\chi^2$ test of independence ($p$-values are reported in the table; lower $p$-values mean that the null hypothesis of independence can be rejected with greater confidence).
-It is interesting to note that the only category for which all affective values are significant at better than 5% level of confidence is mode of travel.
-
-### Age
-
-With respect to Age, previous studies have reported that older adults tend to be more satisfied with their travel experience than younger people [@Cao2014satisfaction; @Devos2016travel; @Ye2017satisfaction].
-In the case, we find that five affective values show dissonance that significantly deviates from the null hypothesis of independence, namely Freedom, Enjoyment, Happiness, Luxury, and Status.
-We observe that levels of dissonance tend to be high in general, and in no case less than 60%.
-For instance, almost 90% of travellers younger than 35 experience travel mode dissonance with respect to Freedom, and more than 94% experience dissonance with respect to enjoyment.
-In general, younger travellers tend to experience dissonance more frequently, with dissonance being less frequent for older travellers.
-The exception to this trend is Luxury, an affective value for which older travellers (age >54) experience dissonance more frequently than mid-aged travellers (ages 35-54).
-
-### Education
-
-When seen from the perspective of Education, the results do not support the hypothesis of  significant differences in the frequency of dissonance by levels of education for the values of Freedom, Enjoyment, Happiness, and Poverty, and only two affective values show significant differences between education levels: Luxury and Status.
-In the case of Luxury, dissonance is more frequent among people who have only K-12 education, and less frequently, albeit still high, for people with technical/university level education and post-graduate education.
-Furthermore, highly educated people (with postgraduate degrees) experience dissonance with respect to Status more frequently than with respect to Luxury.
-
-### Income
-
-The next variable we examine is income, and in this case three affective values are significant: Poverty, Luxury, and Status.
-Since Poverty is a negative affect, we see here that lower income people tend to associate this feeling to their primary mode of commuting more frequently (almost 20% of the time) than other income groups.
-For example, whereas approximately 16% of mid-income people are dissatisfied with their primary mode of travel in this respect, less than 7% of high income individuals are.
-Dissonance with respect to Luxury and Status also tends to be more common among lower income people, and declines substantially for mid- and high income respondents.
-Notice as well that the frequency of dissonance is higher in terms of Luxury than Status for mid- and high income people.
-
-### Primary mode of travel
-
-The variable that shows the largest differences in the frequency of dissonance is the primary mode of travel.
-It can be seen in Table \ref{tab:cross-tabulation-results} that the differences are significative for all six affective values.
-Dissonance is particularly accute for users of public transportation when it comes to the values of Freedom, Enjoyment, and Happiness: almost 100% of users of public transportation have identified other mode or modes as better representing those values.
-Dissonance on these values is the least for active travellers: less than 50% of respondents associate Freedom to a different mode, and only around 60% identified a different mode when responding to the values of Enjoyment and Happiness, compared to approximately 79% and 71% of those who travelled by Car.
-The picture changes when the values of Poverty, Luxury, and Status are considered.
-In this case, dissonance is less frequent for people who travel by car: less than 3% of car users associate car with feelings of poverty, 41% associate Luxury with a mode other than car, and only about 31% relate Status to a different mode.
-Dissonance is more frequent in these values for active travellers, and users of public transportation and other modes, in no case being less than 75%, and being virtually 100% for users of public transportation, who consistently associate Luxury and Status with modes _other_ than public transportation.
-
-### Typical commute time
-
-Turning now to typical commute time, four affectie values show significant differences at better than 10% confidence: Freedom, Happiness, Luxury, and Status.
-Perhaps not surprisingly, dissonance is more frequent among people whose typical commutes are longer.
-This is in line with previous findings: both St-Louis et al.
-[-@Stlouis2014happy] and Smith [-@Smith2017commute] report that commute satisfaction tends to decline with longer commutes, whereas Handy and Thigpen [-@Handy2019commute] found that commute distance was a negative covariate of commute satisfaction.
-
-```{r table-cross-tabulation-results-with-instrumental, echo = FALSE, eval=FALSE}
-kable(xtab_results,
-      "latex",
-      digits = 2,
-      booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results-with-instrumental}Percentage of respondents who report mode dissonance with respect to various SWB and instrumental factors",
-      escape = FALSE,
-      align = c("l", rep("c", 12)),
-      col.names = c("Variable", 
-                    "Freedom", "$\\chi^2$ p-val", 
-                    "Enjoyment", "$\\chi^2$ p-val",
-                    "Happiness", "$\\chi^2$ p-val",
-                    "Safety", "$\\chi^2$ p-val",
-                    "Time", "$\\chi^2$ p-val",
-                    "Efficiency", "$\\chi^2$ p-val")) %>%
-  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
-  pack_rows("Age", 1, 3) %>%
-  pack_rows("Education", 4, 6) %>%
-  pack_rows("Income", 7, 9) %>%
-  pack_rows("Mode", 10, 13) %>%
-  pack_rows("Commute Time", 14, 17)  %>%
-  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
-  landscape()
-```
-
-```{r table-cross-tabulation-results-without-instrumental, echo = FALSE}
-kable(xtab_results,
-      "latex",
-      digits = 2,
-      booktabs = TRUE,
-      caption = "\\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB factors",
-      escape = FALSE,
-      align = c("l", rep("c", 12)),
-      col.names = c("Variable", 
-                    "Freedom", "$\\chi^2$ p-val", 
-                    "Enjoyment", "$\\chi^2$ p-val",
-                    "Happiness", "$\\chi^2$ p-val",
-                    "Poverty", "$\\chi^2$ p-val",
-                    "Luxury", "$\\chi^2$ p-val",
-                    "Status", "$\\chi^2$ p-val")) %>%
-  collapse_rows(columns = c(3, 5, 7, 9, 11, 13), latex_hline = "major", valign = "middle") %>%
-  pack_rows("Age", 1, 3) %>%
-  pack_rows("Education", 4, 6) %>%
-  pack_rows("Income", 7, 9) %>%
-  pack_rows("Mode", 10, 13) %>%
-  pack_rows("Commute Time", 14, 17)  %>%
-  kable_styling(bootstrap_options = c("striped", "scaled_down")) %>%
-  landscape()
-```
-
-## Which modes do travellers associate with affective values?
-
-The preceding analysis suggests that there is significant mode dissonance along various dimensions and for various affective values.
-This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better in terms of how travellers respond to different affects.
-Less is known about the values that travellers associate with modes _other_ than the one they use.
-For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travellers with respect to the modes they tend to associate with various affective values.
-For this analysis we employ a visualization technique known as a mosaic plot.
-Mosaic plots are used in the exploration of multivariate categorical data [@Friendly1994mosaic; @Hofmann2000exploring], and they provide visual representations of multi-way contingency tables.
-The elements of the mosaic plot are called _tiles_, and the dimensions of each tile are proportional to values of variables in the underlying table.
-
-We begin our analysis by plotting primary mode of travel and the modes associated with each affective value (see Figure \ref{fig:mosaic-plots-by-attribute}).
-The height of tile $j$ in these mosaics corresponds to the proportion of travellers who primarily travel by mode $j$, hence we can see that the most common primary mode of travel in this sample is by public transportation, followed by car, active travel, and other (also see Figure \ref{fig:primary-mode-travel}).
-Notice that there are some small discrepancies in the heights across affective values: these are caused by a small number of non-responses.
-Next, the width of the tile $k$ in the mosaics is proportional to the frequency with which a mode was named in relation to affective value $i$.
-Recall that respondents could nominate more than one mode in response to each affective value, and some did.
-For this reason, we used sampling weights, so that the total number of responses corresponds to the size of the sample.
-
-In terms of Freedom, we see that Car users frequently identify this affect with the use of Car; however, those who do not, very often select Active Travel as the mode that better represents Freedom.
-A majority of active travellers, on the other hand, identify Active Travel as the mode that evokes feelings of Freedom; few of them attach this value to Car, and even fewer to public transportation and other modes.
-Travellers whose primary mode of travel is public transportation seldom associate this mode with Freedom, and in fact more frequently relate this affective response to Active Travel followed by Car.
-Users of other modes seem to be split almost equally in their attribution of Freedom, between Active Travel, Car, and Other.
-In general, Active Travel is the mode most often identified as embodying Freedom, with the exception of Car travellers.
-
-The pattern with respect to Enjoyment is similar to that for Freedom, but with an even more decisive tilt towards Active Travel, with even more respondents whose primary mode of travel is Car choosing Active Travel as the mode that better represents Enjoyment.
-Notice that very few of Active Travelers selected Car as an enjoyable mode.
-Likewise, compared to Freedom, Active Travel is perceived as being more enjoyable by users of Public Transportatoin and Other modes.
-Responses with respect to Happiness are somewhere in between Freedom and Enjoyment, but Happiness is, if anything, even less frequently identified with Public Transportation.
-
-Three other affective responses show a marked difference.
-Public Transportation was seldom associated by respondents to feelings of Freedom, Enjoyment, and Happiness; on the other hand, it is the mode that is most commonly selected by respondents for evoking feelings of Poverty - even by users of Public Transportation.
-Active Travel was the second most common response for its association with Poverty.
-Likewise, Whereas Active Travel was often associated to feelings of Freedom, Enjoyment, and Happiness, the mode most frequently associated with Luxury and Status is the Car, although active travellers seem to be somewhat more resistant to this association compared to respondents who travel by Car, Public Transportation, and Other modes.
-
-Next, we further explore these responses after stratifying by Age, Education, Income, and Commute Time.
-We test the underlying 3-way tables by means of the Cochran-Mantel-Haenszel $\chi^2$ test of independence.
-
-```{r figure-mosaic-plots-by-attribute-with-instrumental, echo=FALSE, cache = TRUE, eval=FALSE, fig.cap="\\label{fig:mosaic-plots-by-attribute-with-instrumental}Mosaic plots for three affective and three instrumental values; values on the x-axis represent proportion of modes selected for each value, and values on the y-axis represent proportion of respondents by main mode of transportation"}
-
-ggplot(data = Modes_by_Attribute) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode selected for the value of {Freedom, Enjoyment, Happiness, Safety, Time, Efficiency}") +
-  ylab("Main mode of transportation") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_wrap(~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-```{r figure-mosaic-plots-by-attribute, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective values; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value"}
-
-ggplot(data = Modes_by_Attribute %>% filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS"))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Poverty, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_wrap(~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-### Age
-
-There are some interesting differences when viewed from the perspective of travellers of different ages (see Figure \ref{fig:mosaic-plots-by-age}).
-For example, as seen above, active travel is commonly associated with freedom, happiness, and enjoyment, even by car users, but especially by users of public transportation and other modes.
-However, when we break this down by age, we notice that this tendency weakens as people age, and older travellers increasingly associate these affective values to the car.
-Furthermore, the tendency to associate status with the car tends to increase with age, with the possible exception of public transport users, for whom other options (possibly taxi), gain status for older travellers (> 54) at the expense of other modes, including the car.
-In contrast, the car loses in the value of luxury with age, while other options become more commonly associated with feelings of luxury for older respondents, even for car users (Figure 2).
-Older car users (> 54) show less dissonance in status than in luxury, while active travellers present more dissonance in status than in luxury - and in fact, they more commonly project status in the car.
-
-```{r figure-mosaic-plots-by-attribute-and-age, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-age}Mosaic plots for affective values by age; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
-
-# Select only values that were significant in the tests of independence
-
-# Also, use Cochran-Mantel-Haenzel tests
-# Freedom
-Modes_by_Freedom_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM")))
-
-# Enjoyment
-Modes_by_Enjoyment_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "ENJOYMENT")))
-
-# Happiness
-Modes_by_Happiness_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS")))
-
-# Luxury
-Modes_by_Luxury_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
-
-# Status
-Modes_by_Status_by_Age <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + AGE, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
-
-labels <- c(paste('FREEDOM\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 2) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('ENJOYMENT\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('HAPPINESS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('LUXURY\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")),
-            paste('STATUS\np-value', ifelse(round(Modes_by_Freedom_by_Age$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Age$p.value, 3)),
-                                             " < 0.001")))
-
-ggplot(data = Modes_by_Attribute %>% 
-         filter(ATTRIBUTE %in% c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS")) %>%
-         mutate(ATTRIBUTE = factor(ATTRIBUTE, 
-                                   levels = c("FREEDOM", "ENJOYMENT", "HAPPINESS", "LUXURY", "STATUS"),
-                                   labels = labels))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Enjoyment, Happiness, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(AGE ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-### Education
-
-Only two affective values were significant in the preceding analysis when seen from the perspective of education, namely luxury and status.
-As seen in Figure \ref{fig:mosaic-plots-by-education}, the perceptions of luxury and status are fairly consistent when differentiated by education.
-Most respondents tend to associate luxury and status to the use of car, albeit this association is stronger for status than for luxury.
-The second mode most often mentioned in relation to luxury is "other" likely due to the flexibility and convenience (but cost) of using taxis.
-The exception in this case is the traveller with graduate education who uses active modes.
-This type of respondent, while still more likely to associate luxury and status with the car, more commonly links active travel to these affects than travellers with lower levels of education.
-Most public transport users tend to associate luxury and status to the car, however, they associate active modes with status more than the same group with respect to luxury.
-
-```{r figure-mosaic-plots-by-attribute-and-education, echo=FALSE, cache = TRUE, fig.width= 6, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-education}Mosaic plots for affective values by education; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
-
-# Select only values that were significant in the tests of independence
-
-# Also, use Cochran-Mantel-Haenzel tests
-# Luxury
-Modes_by_Luxury_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
-
-# Status
-Modes_by_Status_by_Education <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + EDUCATION, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
-
-labels <- c(paste('LUXURY\np-value', ifelse(round(Modes_by_Luxury_by_Education$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Luxury_by_Education$p.value, 3)),
-                                             " < 0.001")),
-            paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Education$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Status_by_Education$p.value, 3)),
-                                             " < 0.001")))
-
-ggplot(data = Modes_by_Attribute %>% 
-         filter(ATTRIBUTE %in% c("LUXURY", "STATUS")) %>%
-         mutate(ATTRIBUTE = factor(ATTRIBUTE,
-                                   levels = c("LUXURY", "STATUS"),
-                                   labels = labels))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(EDUCATION ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-### Income
-
-Three affective values were significant in the analysis by income; perhaps not surprisingly, all three have an economic dimension.
-Figure \ref{fig:mosaic-plots-by-income} reflects some important social inequalities associated with the way users feel about transportation in Santiago.
-When the affective perception of poverty is analyzed, the image shows that generally public transport is the mode most commonly associated with poverty.
-There are some interesting differences, however, to be observed by income level.
-Whereas middle income users of public transportation associate this mode to poverty most frequently, this is not the case of high income users of public transportation, who tend to link active travel to poverty with greater frequency.
-Similarly, active travel is more often associated with poverty by low income travellers than middle or high income travellers.
-A possible explanation for this is that walking or cycling are related to the idea of a lack of financial means to access other modes of transport.
-For high income car users, on the other hand, public transportation may have connotations of poverty due to its massive use, whereas active travel may be seen more as a lifestyle alternative.
-
-With respect to luxury and status, we see again that these two values coincide more strongly in their association with the car.
-Moreover, we also notice that these perceptions become increasingly frequent at higher levels of income.
-Unlike users of other modes, the high-income public transport user group tends to concentrate a broader association of luxury and status factors with active transport, reinforcing the notion that at higher levels of income, people may see active modes as a lifestyle alternative.
-High income active travellers, although still more likely to associate luxury and status to the car, are more likely than users of other modes to associate these affects to active travel, perhaps due to an awareness of the benefits of walking and using the bicycle.
-Furthermore, high-income users of cars are more likely to experience consonance with respect to status and luxury, in what might be a form of self-congratulatory confirmation of success.
-
-```{r figure-mosaic-plots-by-attribute-and-income, echo=FALSE, cache = TRUE, fig.width= 7, fig.height=5, fig.cap="\\label{fig:mosaic-plots-by-income}Mosaic plots for affective values by income; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
-
-# Select only values that were significant in the tests of independence
-
-# Also, use Cochran-Mantel-Haenzel tests
-# Poverty
-Modes_by_Poverty_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, data = filter(Modes_by_Attribute, ATTRIBUTE == "POVERTY")))
-
-# Luxury
-Modes_by_Luxury_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
-
-# Status
-Modes_by_Status_by_Income <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + INCOME, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
-
-labels <- c(paste('POVERTY\np-value', ifelse(round(Modes_by_Poverty_by_Income$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Poverty_by_Income$p.value, 3)),
-                                             " < 0.001")),
-            paste('LUXURY\np-value', ifelse(round(Modes_by_Luxury_by_Income$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Luxury_by_Income$p.value, 3)),
-                                             " < 0.001")),
-            paste('STATUS\np-value', ifelse(round(Modes_by_Status_by_Income$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Status_by_Income$p.value, 3)),
-                                             " < 0.001")))
-
-ggplot(data = Modes_by_Attribute %>% 
-         filter(ATTRIBUTE %in% c("POVERTY", "LUXURY", "STATUS")) %>%
-         mutate(ATTRIBUTE = factor(ATTRIBUTE, 
-                                   levels = c("POVERTY", "LUXURY", "STATUS"),
-                                   labels = labels))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Poverty, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(INCOME ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-### Typical commute time
-
-The last dimension that we examine is typical commute time.
-Four affective values were significant along this dimension in Table \ref{tab:cross-tabulation-results}.
-Figure \ref{fig:mosaic-plots-by-travel-time} shows the way travellers associate different affective values to modes of transportation by length of typical commute.
-The first couple of factors, freedom and enjoyment, are associated with eudaimonic and hedonic factors of wellbeing, as discussed earlier in the paper.
-On the other hand, the luxury and status are defined mainly by a socio-economic component.
-As seen in the figure, freedom and enjoyment are most frequently mentioned in relation to active travel, followed by car.
-However, active travel is more frequently associated with freedom and enjoyment by people who typically undertake relatively short trips (<20 min) or travellers whose typical trips are longer (>60 min).
-In this respect, active travel may be seen as an ideal mode for trips, and as an enviable mode by people whose trips are longer.
-
-In the case of luxury and status factors, both follow a similar pattern, despite variations in travel times.
-Despite the travel time exceeding 60 minutes, car users consider that their transport mode is mostly associated with luxury and status.
-The users of active transport in the sample tend to travel less than 20 minutes, and this is the same segment that considers that the status and luxury factors correspond mainly to the car and then to active transport.
-Looking at the four factors set out in Figure \ref{fig:mosaic-plots-by-travel-time}, it could be understood that the modes that are associated with intrinsically positive characteristics such as freedom and enjoyment tend to use public transport.
-On the contrary, factors such as luxury and status tend to have a negative connotation, where the association with the car and other modes of transport (such as the individual taxi and the collective taxi) tends to dominate.
-
-```{r figure-mosaic-plots-by-attribute-and-time, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:mosaic-plots-by-travel-time}Mosaic plots for affective values by commute time; the y-axis is the proportion of respondents by main mode of transportation, and the x-axis is the proportion of modes selected for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared Test)"}
-
-# Select only affective values that were significant in the tests of independence
-
-# Also, use Cochran-Mantel-Haenzel tests
-# Freedom
-Modes_by_Freedom_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "FREEDOM")))
-
-# Happiness
-Modes_by_Happiness_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "HAPPINESS")))
-
-# Luxury
-Modes_by_Luxury_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "LUXURY")))
-
-# Status
-Modes_by_Status_by_Time <- mantelhaen.test(xtabs(WEIGHT ~ USED + IDEAL + TRAVEL_TIME, data = filter(Modes_by_Attribute, ATTRIBUTE == "STATUS")))
-
-labels <- c(paste('FREEDOM\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 2) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
-                                             " < 0.001")),
-            paste('ENJOYMENT\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
-                                             " < 0.001")),
-            paste('LUXURY\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
-                                             " < 0.001")),
-            paste('STATUS\np-value', ifelse(round(Modes_by_Freedom_by_Time$p.value, 3) >= 0.001,
-                                             paste("=", round(Modes_by_Freedom_by_Time$p.value, 3)),
-                                             " < 0.001")))
-
-ggplot(data = Modes_by_Attribute %>% 
-         filter(ATTRIBUTE %in% c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS")) %>% drop_na(TRAVEL_TIME) %>%
-         mutate(ATTRIBUTE = factor(ATTRIBUTE, 
-                                   levels = c("FREEDOM", "HAPPINESS", "LUXURY", "STATUS"),
-                                   labels = labels))) + 
-  geom_mosaic(aes(product(IDEAL, USED), fill = IDEAL, weight = WEIGHT),
-              divider = mosaic("vertical")) + 
-  xlab("Mode associated with {Freedom, Happiness, Luxury, Status}") +
-  ylab("Primary mode of travel") +
-  scale_fill_viridis_d(direction = -1) +
-  facet_grid(TRAVEL_TIME ~ ATTRIBUTE) +
-  theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-Conclusions
-==========
-
-Subjective wellbeing is a topic that has attracted considerable attention in recent years due to its relationship with health.
-In the field of transportation, there is a large and growing body of literature that documents the way transportation can impact subjective wellbeing.
-Likewise, there is strong evidence that subjective wellbeing can influence travel behavior.
-As the world tries to move from a culture dominated by a century-long love affair with the automobile, there is a pressing need to understand how travellers perceive different modes of transportation from the lens of subjective wellbeing.
-Insights in this regard could prove valuable to develop and implement plans and policies to attract and retain users to healthier, more environmentally friendly transportation options, in particular active travel and public transportation.
-For this reason, understanding mode dissonance, the extent to which the context of travellers differs from their aspirations, is a worthwhile topic for research.
-
-The premise of the research presented in this paper is that subjective wellbeing is a composite construct of various affective values.
-In this paper we investigated mode dissonance from the perspective of six affective values associated with subjective wellbeing, namely freedom, enjoyment, happiness, poverty, luxury, and status.
-The research presented here was based on a sample of travellers in Santiago, the capital of Chile.
-Participants in this research were asked about their typical mode of travel, and then about the mode or modes that they associate with each of the six affective values.
-Analysis using hypothesis testing (tests of independence) and vizualization techniques (mosaic plots) uncovered interesting patterns.
-Some of our findings are well aligned with previous research; for example, active travellers experience less dissonance than car users, and users of public transportation experience the most dissonance of all.
-However, by considering affective values separately instead of aggregating them into a single indicator of subjective wellbeing, we manage to preserve some granularity with respect to various responses.
-This turns out to be important, because hedonic/eudaimonic values are more frequently related to active travel (freedom, enjoyment, happiness), whereas poverty is more frequently related to public transportation and active travel.
-Luxury and status, on the other hand, are more frequently associated to luxury and status.
-
-Further delving into the question of which modes are associated with these affective values, we find that there are important differences in terms of the typical mode of travel.
-Active travellers experience dissonance with relatively little frequently with respect to freedom, enjoyment, and happiness, but when they do, they tend to attach positive values to the car.
-Car users experience dissonance with respect to these affects more frequently than active travellers, and when they do, they strongly relate possitive hedonic/eudaimonic values to active travel.
-In other words, it is possible that drivers dream of walking when it comes to feelings especially of enjoyment and happiness.
-The other side of the coin is also interesting.
-When it comes to affective values with a stronger socio-economic flavor, such as poverty, luxury, and status, car users tend to experience dissonance less frequently than users of other modes.
-Active travellers, altough more resistant to the lure of the car compared to users of public transportation, also tend to attach values of luxury and status to the car when they experience dissonance.
-
-An examination of these effects by age, level of education, level of income, and typical trip duration reveals that some of the responses become more pronounced.
-For instance, older people are less likely than younger people to associate active travel with positive hedonic/eudaimonic affects, and are more likely to attach these values to the car.
-People with higher incomes are more atuned to the luxury and status values of cars, whereas lower income people are more likely to relate active travel to luxury and status.
-
-Our results not only help to flesh out some ways in which mode dissonance could play out from the perspective of different affects, but also does so in the context of a Latin American country, a region where historically there are deep-seated tabooes with respect to different modes of transportation: the poor travel by public transportation and/or are forced active travellers; where the rich enjoy the luxury of private vehicles and/or are active travellers by choice.
-In this way, the paper helps us to reflect on the ways the public experiences transportation-related subjective wellbeing, and how this in turn could be used to increase the attractiveness of public transport and active travel in the socio-demographic groups studied.
-
-With respect to opportunities for future research, a possible avenue for extending the findings reported in this paper relates to the use of the modes other than the typical mode of transportation.
-In a recent paper that investigaed commute satisfaction for car users, Al-Ayyash and Abou-Zeid [-@Alayyash2019commute] considered three models: for current trip satisfaction, remembered satisfaction while using public transport, and current satisfaction using public transport.
-The findings suggest that low service quality in public transportation can result in a generalised negative perception, and that this perception is more difficult to smooth if commuters do not regularly use public transport.
-Another avenue for future research could be to consider the mix of modes typically used.
-While in this paper the analysis focused on the primary mode of transportation, many travellers experience more than one mode of transportation in their daily activities.
-For this reason, considering the multimodal component of travel would be interesting; for example, future research could consider people who eventually arrive by bicycle to the metro station or people that, after using a colectivo for part of a trip, end their journey by bus.
-
-Acknowledgments
-==========
-
-The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `ggmosaic` [@Jeppson2019ggmosaic], `ggthemes` [@Arnold2018], `kableExtra` [@Zhu2018], `knitr` [@Xie2015; @Xie2018], `rticles` [@Allaire2018rticles], and `tidyverse` [@Wickham2017].
-
-References {#references .unnumbered}
-==========

### 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_Title_Page_v2.tex
v2 Revisions with BML

--- 2020-02-06 Dissonance_Santiago_v1/Dissonance_Santiago_v1.tex
@@
 % Pandoc toggle for numbering sections (defaults to be off)
+
 % Pandoc header
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 
@@
 from the Perspective of Subjective Wellbeing}
-    \author[Some University]{Author 1\corref{c1}}
-   \ead{a1@university.com} 
-   \cortext[c1]{Corresponding Author}
-    \author[Some School]{Author 2}
-   \ead{a2@school.com}
-
-      \address[Some University]{Department, Street, City, State, Zip}
-    \address[Some School]{Department, Street, City, State, Zip}
+    \author[PUC]{Beatriz Mella Lira\corref{Corresponding Author}}
+   \ead{beatriz.lira.14@ucl.ac.uk} 
+    \author[McMaster University]{Antonio Paez}
+   \ead{paezha@mcmaster.ca} 
+      \address[PUC]{BRT+ Centre of Excellence, Departamento Ingeniería de Transporte y
+Logística, Escuela de Ingeniería, Pontificia Universidad Católica de
+Chile}
+    \address[McMaster University]{School of Earth, Environment, and Society, McMaster University, 1280
+Main St W, Hamilton, Ontario, L8S 1S4 Canada}
 
   \begin{abstract}
-  \textbf{Introduction}\\
+  \emph{Introduction}\\
   Subjective wellbeing is a topic that has attracted considerable
-  attention in recent years due to the way it correlates with health. From
-  a transportation perspective, there is a burgeoning literature on the
-  way travel can impact subjective wellbeing, and how this, in turn, can
-  influence behavior.\\
-  \textbf{Objective}\\
-  The objective of this paper is to analyze a number of affective values
-  associated with subjective wellbeing and the modes of transportation
-  that people commonly use. In particular, we are interested in the
-  potential for dissonance with respect to the primary mode of travel.\\
-  \textbf{Materials and Methods}\\
-  The study is based on data collected from a sample of travellers in the
+  attention in the transportation literature in recent years. As a result,
+  there is a burgeoning literature that investigates the impacts of travel
+  on subjective wellbeing, and how wellbeing, in turn, can influence
+  behavior. An important aspect of subjective wellbeing are the affective
+  reactions of people to their experiences.\\
+  \emph{Objective}\\
+  The objective of this paper is to analyze the affective reactions of
+  travelers with respect to various modes of transportation. In
+  particular, we are interested in the potential for dissonance between
+  primary mode of travel and the mode(s) of travel identified as evoking
+  various affective reactions.\\
+  \emph{Materials and Methods}\\
+  The study is based on data collected from a sample of travelers in the
   city of Santiago, in Chile. Participants in the study were asked about
-  their usual mode of travel, and then were asked to name the mode or
-  modes that they associate with the affective values of freedom,
-  enjoyment, happiness, poverty, luxury and status. Analysis is based on
-  tests of independence and visualization via mosaic plots.\\
-  \textbf{Results}\\
+  their usual mode of travel, and then were asked to name their ideal
+  mode(s) of transportation from the perspective of various affective
+  reactions. The reactions we investigate are associated with the values
+  of freedom, enjoyment, happiness, poverty, luxury, and status. Analysis
+  is based on tests of independence and visualization techniques.\\
+  \emph{Results}\\
   The results indicate that users of public transportation experience the
-  most dissonance in terms of affective values, and active travellers the
-  least. For those travellers who experience dissonance, active travel is
-  the mode most commonly associated with freedom, enjoyment, and
-  happiness, public transportation is most commonly associated with
-  poverty, and the automobil is most commonly associated with luxury and
-  status.
+  most dissonance in terms of affective reactions, and active travelers
+  the least. For those travelers who experience dissonance, active travel
+  is the mode most commonly associated with freedom, enjoyment, and
+  happiness, whereas public transportation is most commonly associated
+  with poverty. The automobile, in contrast, is the mode most commonly
+  associated with luxury and status.
   \end{abstract}
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Transportation planning for decades has focused on providing mobility
-for the private automobile. This is a model of development that was
-initially introduced in North America as a solution to problems created
-by rapid urbanization, and that was eventually copied elsewhere
-(Angotti, 1996; Brown et al., 2009). Despite the initial promise of
-automotive technology, it is now evident that mobility centred on the
-private automobile has given rise to a litany of maladies that are in
-urgent need of correction. This includes environmental concerns (i.e.,
-climate change; Chapman, 2007) as well as numerous other social
-(Boschmann and Kwan, 2008; Lucas, 2019, 2012), health (Khreis et al.,
-2016; Milne, 2012), and equity issues (Bocarejo and Oviedo, 2012;
-Martens et al., 2012; Pereira et al., 2017).
-
-As the real impacts of our societal dependence on the private
-autombobile have become increasingly evident, the transportation agenda
-has aimed to shift focus to the reduction of car use and towards the
-creation of mobility polycultures that offer a broader menu of
-transportation alternatives than primarily (or even just) the private
-automobile (Miller, 2011). In order to successfully achieve this goal,
-it is essential not only to provide the services and facilities that
-support public transportation and active travel, but also to attract new
-users to these modes of transportation (Ettema et al., 2011). Within
-this context, it has been argued that sustainable transportation
-policies require all participants in the transportation system to
-challenge what Gossling and Cohen (2014) termed \emph{transportation
-taboos}: deep-seated ideas concerning the contribution to emissions by
-individuals, the inequality of market-based approaches, and the social
-and psychological functions of transportation. With respect to the
-latter, it is important to move beyond a purely utilitarian focus if we
-are to understand how the affective value of the transportation
-experience can be leveraged to improve alternative transportation -
-particularly transit and active modes (Anable and Gatersleben, 2005;
-Domarchi et al., 2008; Gatersleben and Uzzell, 2007; Steg, 2005).
-
-A useful lens to investigate the social and psychological functions of
-transportation is by means of the concept of subjective wellbeing (SWB;
-see, inter alia, De Vos et al., 2013; and Chatterjee et al., 2019). SWB
-is defined by the OECD as ``{[}g{]}ood mental states, including all of
-the various evaluations, positive and negative, that people make of
-their lives, and the affective reactions of people to their
-experiences'' (OECD, 2013, p. 10). As memorably put by Steg (2005): is
-the use of car a must, or is it a lust? A close alignment, or
-consonance, between affective values and the mode of transportation used
-to travel can result in greater subjective wellbeing and increase the
-probability of choosing that mode (i.e., by satisfying the \emph{lust});
-on the other hand, dissonance, that is, the lack of concordance between
-the mode used and affective values would be detrimental to subjective
-wellbeing, especially of those for whom the use of the mode is a
-\emph{must} (De Vos, 2019; Mokhtarian and Pendyala, 2018). With these
-considerations in mind, one aim of the present research is to
-investigate \emph{who} experiences dissonance with respect to their
-primary mode of travel and affective values, namely freedom, enjoyment,
-happiness, feelings of poverty, luxury, and status. Furthermore, it is
-possible, even if use of a particular mode is a \emph{must}, that
-travellers may still \emph{lust} for something else - in other words,
-the grass may in fact look greener from the window of the car. For this
-reason, we also aim to investigate which mode or modes are most commonly
-associated with affective values, with a focus on those travellers who
-experience dissonance in their primary mode.
-
-Research is based on data collected from a sample of travellers in the
-city of Santiago in Chile. Survey respondents were asked about their
-primary mode of travel, and also about the mode or modes that they
-associate with the affective values mentioned above. The paper
-contributes to the literature in three ways, as follows:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  The research reported here contributes to an emerging literature on
-  the topic of transportation and affective values in the context of the
-  Global South (Al-Ayyash and Abou-Zeid, 2019; Bejarano et al., 2017;
-  Shao and Liang, 2019; Van et al., 2014; Zorrilla et al., 2019); to the
-  best of our knowledge, the case of Chile has not yet been reported.
-\item
-  Although there is an extensive literature on the enjoyment of commute
-  and other affective values (see for instance Paez and Whalen, 2010;
-  Redmond and Mokhtarian, 2001; Whalen et al., 2013; Ye and Titheridge,
-  2017), from a hedonic and even eudaimonic perspectives the analysis
-  has yet to be applied more fully in terms of distributional issues --
-  i.e.~which groups more commonly experience dissonance (see De Vos,
-  2018).
-\item
-  The analysis shows the attitudes of people towards their primary mode
-  and their perception towards `ideal modes' -- implying their
-  preferences, even in situations when their ideal mode is not part of
-  their actual choice set. More concretely, the results indicate that
-  users of public transportation experience the most dissonance in terms
-  of affective values, and active travellers the least. For those
-  travellers who experience dissonance, active travel is the mode most
-  commonly associated with freedom, enjoyment, and happiness, public
-  transportation is most commonly associated with poverty, and the
-  automobil is most commonly associated with luxury and status. We also
-  find that there are some substantial variations in dissonance by age,
-  education, income, and typical commute time. The attitudes of
-  travellers towards transport modes are critical factors to be
-  considered by policy-makers in case they want to promote and increase
-  the use of public transport or active modes (Bornioli et al., 2019; De
-  Vos et al., 2019; De Vos and Witlox, 2017; Garling et al., 2019;
-  Redman et al., 2013).
-\end{enumerate}
-
-The structure of the paper is as follows. After these introductory
-remarks, we follow up with a background section that reviews the
-literature. Next, we discuss the case study and data used in the
-research. Then, the analysis and results are presented, before
-concluding with some discussion and directions for future research.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
-
-A consensus has emerged in the transportation community regarding the
-need to complement the traditional utilitarian perspective of
-transportation by looking at mobility and transport issues from the lens
-of their affective functions. The affective value of transportation in
-turn is important due to its potential to improve or detract from SWB.
-One of the primary ways to explore this has been the satisfaction that
-travelers feel towards their every day mobility experience (e.g.,
-Cecilia Jakobsson Bergstad et al., 2011). As a consequence, there is a
-wealth of research on satisfaction with the use of different modes of
-transportation. For example, numerous studies report that car users
-often have a higher level of satisfaction compared to other transport
-modes (C. J. Bergstad et al., 2011; Eriksson et al., 2013; Redmond and
-Mokhtarian, 2001; Whalen et al., 2013; but see Handy and Thigpen, 2019).
-In a similar way, there are multiple reports that active travel also
-tends to yield high levels of satisfaction (Gatersleben and Uzzell,
-2007; Handy and Thigpen, 2019; Paez and Whalen, 2010; Smith, 2017;
-St-Louis et al., 2014; Whalen et al., 2013), In contrast, public
-transport users tend to assess their experience more negatively (Abenoza
-et al., 2017; De Vos et al., 2016; Gatersleben and Uzzell, 2007; Handy
-and Thigpen, 2019; Paez and Whalen, 2010). Multi-modal trips also
-influence satisfaction levels; for instance, when an individual chooses
-a particular mode of transportation, she will report a higher level of
-satisfaction with that chosen mode -- perhaps as a form of \emph{post
-hoc} validation (Susilo and Cats, 2014).
-
-While the use of travel satisfaction has been mainly used in the context
-of daily trips -- typically linked to cost-benefit and utilitarian
-measurements --, the evaluation of Subjective Wellbeing (SWB) over time
-has risen as an alternative measure. In the field of travel behaviour,
-Ettema et al.~(2010, p. 725) define SWB as the degree to which an
-individual positively evaluates the overall quality of their lives,
-where the general life satisfaction encompasses a more extended
-temporality -- which implies assuming a tendency to be more stable over
-time. This concept has prompted a growing literature that complements
-and applies SWB in a broader range of satisfaction scales and
-situations. The definition of other factors such as travel choice mode,
-attitudes and external elements of the built environment have been
-studied for a broader understanding of the changes produced in the SWB
-(e.g., Handy and Thigpen, 2019). As these factors do not necessarily
-apply to the general life satisfaction on the long term, the studies
-have aimed to determine both the direct and indirect effects on the
-perception of users (see, e.g., Ye and Titheridge, 2017). Other concepts
-have also emerged as the Satisfaction with Travel Scale (STS), a
-measurement devised by Ettema et al.~(2011), as well as different scales
-based on people's travel perceptions. De Vos et al.~(2015), for
-instance, explore in detail the underlying dimensions of the affective
-domain of STS on which SWB is based (for more on STS see also Friman et
-al., 2013).
-
-Recent literature on SWB and its link with transport have demonstrated a
-relationship between people's perceptions and satisfaction with their
-daily travel (e.g., Smith, 2017; Mokhtarian and Pendyala, 2018; St-Louis
-et al., 2014). Scholars have shown that accessibility has been the most
-developed factor that influences people's wellbeing (Delbosc, 2012), and
-activities have a direct impact on travel satisfaction (Cecilia
-Jakobsson Bergstad et al., 2011). Delbosc (2012, p. 28), for instance,
-has summarised the most significant influences on psychological
-wellbeing: poverty and employment, meaningful relationships and health.
-However, understanding the components affecting people's perceptions
-implies the differentiation between affective (also named as
-symbolic-affective) and instrumental values (C. J. Bergstad et al.,
-2011). Steg et al.~(2011) have compared symbolic-affective opposed to
-instrumental-reasoned motives based on car-use, and other studies have
-also found associations between affective and symbolic aspects of
-car-use (see, e.g., Gatersleben and Uzzell, 2007; Lois and Lopez-Saez,
-2009). Previous studies have also demonstrated how socio-demographic
-factors affect the levels of SWB. The effect of income on SWB (Clark and
-Oswald, 1996; Ferrer-i-Carbonell, 2005); education and unemployment
-(Argyle et al., 1999); age (Diener and Eunkook Suh, 1997), and gender
-(Tesch-Römer et al., 2008) have been extensively studied. Recent
-research also suggests the links between commuting, SWB and emotional
-wellbeing assessment (\textbf{Olson et al.~2013}; \textbf{Kahneman et
-al.~2004}). However, more research is needed to understand how these
-socio-demographic variables connect as well with the affective responses
-to mode of travel (St-Louis et al., 2014).
-
-The research needs already recognized in the developed world are also
-markedly acute in the context of the Global South, where historical
-inequality has tended to create a symbolic attachment to the automobile,
-in addition to negative connotations for public transport and active
-travel (Zorrilla et al., 2019). In this way, there is an emerging
-literature that investigates affective factors in travel behaviour in a
-number of developing countries. A cross-country study in Asia revealed
-that the affective factors of public transportation and car use are
-important, and in particular the social orderliness of transit was
-suggested as a way to make this mode more attractive to users (Van et
-al., 2014). In terms of active travel, a study in China found that
-attitudes that embrace new styles and technologies despite their cost
-are associated with the intention to continue using shared bicycles
-(Shao and Liang, 2019). The importance of affective factors for policy
-and planning is further highlighted by research in Colombia that shows
-how users felt proud using a bicycle shared system, in addition to
-experiencing feelings of belonging to a civic culture and the enjoyment
-and pleasure of travel itself (Bejarano et al., 2017). This paper
-contributes to further our understanding of affective values in travel
-behaviour in a developing country.
-
-\hypertarget{case-study-and-data}{%
-\section{Case Study and Data}\label{case-study-and-data}}
-
-\hypertarget{context}{%
-\subsection{Context}\label{context}}
-
-The case study to contextualize the discussion is Santiago de Chile, the
-capital of one of the countries with the highest levels of inequality in
-terms of socio-economic distribution in the world. These inequities have
-manifested in a disproportionate expense in transport by the different
-socioe-conomic sectors, a disproportion in travel times and distances
-travelled. On the other hand, car ownership and use of public transport
-in the capital are directly conditioned by strong spatial segregation --
-the higher the income, the higher is the use of the automobile;
-conversely, and the lower the income, the higher is the predisposition
-to use public transport. Although transport is a reflection of deep
-inequities in various dimensions, it has triggered an exceptional
-discomfort and disagreement with the daily travel experience and quality
-of life.
-
-\hypertarget{sample}{%
-\subsection{Sample}\label{sample}}
-
-The study is based on a survey conducted in the city of Santiago during
-the months of November and December 2016, that is, the end of the Spring
-and beginning of Summer. The survey collected information on a wide
-range of travel and related issues. The data collection considered a
-quota-sampling method for gathering the information, considering the
-socio-demographic information from Pre-Census of 2012. An equal
-representation of both genders and a representation of the proportion of
-inhabitants per area were chosen as relevant characteristics of the
-sample. In total, there were \(n=451\) valid surveys, although not every
-survey was complete and there were missing responses for some answers.
-
-The survey was structured in eight sections, as follows: 1) Individual
-characteristics of respondent; 2) Health; 3) Feelings and emotions; 4)
-Reasons for travel and planning travel; 5) Social interaction; 6) Nature
-and sustainability; 7) Information and telecommunications; 8) Built
-environment; and 9) Commuting. For the present study, we draw data from
-sections 1), 3) and 9). In terms of individual characteristics of the
-respondents and their commute, participants were asked about basic
-socio-demographic information, including age, level of education,
-income, and the typical duration of their regular commute. The
-descriptive statistics of the sample appear in Figure
-\ref{fig:descriptive-statistics}. The sample tends to be younger, and
-well-educated, with an almost uniform distribution of income levels. The
-trend in typical commute time is towards longer commutes.
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/plot-descriptive-statistics-1.pdf}
-\caption{\label{fig:descriptive-statistics}Descriptive statistics of the
-sample}
-\end{figure}
-
-In addition, respondents were asked about their primary mode of travel
-for their regular commute. The modes available were Car, Taxi, Colectivo
-(a form of shared ride, intermediate in flexibility and capacity between
-taxi and bus); Motorcycle; Metro; Bus; Bicycle; Walking. As seen in the
-top panel of Figure \ref{fig:primary-mode-travel}, the three most common
-modes of travel are Metro, Bus, and Car, followed by Walking and Biycle.
-For the analysis, we aggregate these modes into the following categories
-(bottom panel of Figure \ref{fig:primary-mode-travel}): Car, Active
-(Walking + Bicycle), Public (Metro + Bus), and Other (Taxi + Colectivo +
-Motorcycle).
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-primary-mode-travel-1.pdf}
-\caption{\label{fig:primary-mode-travel}Frequency of primary mode used
-for regular commute; top panel: all modes, bottom panel: aggregated
-modes}
-\end{figure}
-
-Of particular interest for the present study is the following question
-in Part 3) of the survey:
-
-\begin{quote}
-\begin{quote}
-Q: Please indicate the mode(s) of transport that you relate to the
-following feelings and concepts
-\end{quote}
-\end{quote}
-
-The question was asked for each of the following affective values:
-Freedom; Enjoyment; Happiness; Poverty; Luxury; and Status. The
-respondents were not constrained to select only one alternative, but
-could indicate by means of a checkbox any and all modes that they felt
-aligned with each affective value. This allows us to do an analysis of
-modal dissonance, a concept introduced into the transportation
-literature by Schwanen and Mokhtarian (2004) based on earlier work by
-Feldman (1990). Residential neighborhood-type dissonance was defined by
-Schwanen and Mokhtarian (2004) as an incongruence in terms of the the
-land use patterns at the place of residence of an individual, and the
-individual's preferences. The concept of dissonance has since been
-extended in the travel behavior literature to encompass the mismatch
-between the choices individuals make, and the alternatives that would
-enable users to experience affective or instrumental values. This
-includes, for example, travel mode dissonance (De Vos, 2018).
-
-Based on the primary mode of travel and the questions about affective
-values, we derived a series of travel mode dissonance variables
-according to the following rule: \[
-D_i = 
-\begin{cases}
-0 & if \text{ primary mode} = \text{mode associated with value } i\\
-1 & \text{ otherwise}
-\end{cases}
-\] Therefore, if a respondent's primary mode of travel is Car, but
-indicated any other mode or modes in relation to Freedom, the respondent
-experienced dissonance: \[
-D_{\text{Freedom}} = 1
-\]
-
-Furthermore, we also expanded the responses to account for all modes
-identified by respondents in relation to the affective values. However,
-to avoid double counting the respondents in our frequency tabulations,
-we also calculated a sample weight that was the inverse of the number of
-modes selected in response to each affective value. For instance, if a
-respondent selected two modes in relation to affective value \(i\), the
-two modes receive a weight of \(1/2\); if a respondent selected three
-modes, then their weights are \(1/3\); and so on. In this way we do not
-treat unfairly those who selected only one mode, and the sum of all
-weighted modes is equal to the sample size.
-
-\hypertarget{analysis-and-results}{%
-\section{Analysis and Results}\label{analysis-and-results}}
-
-In what follows, analysis is done on two related but distinct questions.
-The first part of the analysis seeks to understand \emph{who}
-experiences dissonance, and the second part, building off that, aims to
-explore which modes of travel are more commonly identified as embodying
-affective values by those travellers who experience dissonance.
-
-Please note that this document was prepared using R Markdown and
-contains reproducible analysis. The R markdown file, along with the data
-file needed to reproduce the analysis, can be downloaded from the
-following anonymous Drive folder:
-
-https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg
-
-\hypertarget{who-experiences-dissonance}{%
-\subsection{Who experiences
-dissonance?}\label{who-experiences-dissonance}}
-
-To investigate the first question in our analysis, we create contingency
-tables that tabulate the frequency of dissonance with respect to each
-affective value, stratified by the attributes of Age, Education, Income,
-Primary Mode of Travel, and typical Commute Time. Table
-\ref{tab:cross-tabulation-results} presents the frequency (in
-percentage) of dissonance, in other words, the percentage of respondents
-out of the total in their stratum who indicated mode or mode(s) for the
-affective value that do not correspond to their primary mode of travel.
-
-As seen in the table, there are five characteristics of the respondents
-and their commutes that we use in the analysis. Three of these
-categories are socio-economic and demographic, namely age, level of
-education, and income. The other two are transportation related, namely
-primary mode of travel and commute time. The frequency tables were
-tested in every case by means of the \(\chi^2\) test of independence
-(\(p\)-values are reported in the table; lower \(p\)-values mean that
-the null hypothesis of independence can be rejected with greater
-confidence). It is interesting to note that the only category for which
-all affective values are significant at better than 5\% level of
-confidence is mode of travel.
-
-\hypertarget{age}{%
-\subsubsection{Age}\label{age}}
-
-With respect to Age, previous studies have reported that older adults
-tend to be more satisfied with their travel experience than younger
-people (Cao and Ettema, 2014; De Vos et al., 2016; Ye and Titheridge,
-2017). In the case, we find that five affective values show dissonance
-that significantly deviates from the null hypothesis of independence,
-namely Freedom, Enjoyment, Happiness, Luxury, and Status. We observe
-that levels of dissonance tend to be high in general, and in no case
-less than 60\%. For instance, almost 90\% of travellers younger than 35
-experience travel mode dissonance with respect to Freedom, and more than
-94\% experience dissonance with respect to enjoyment. In general,
-younger travellers tend to experience dissonance more frequently, with
-dissonance being less frequent for older travellers. The exception to
-this trend is Luxury, an affective value for which older travellers (age
-\textgreater54) experience dissonance more frequently than mid-aged
-travellers (ages 35-54).
-
-\hypertarget{education}{%
-\subsubsection{Education}\label{education}}
-
-When seen from the perspective of Education, the results do not support
-the hypothesis of significant differences in the frequency of dissonance
-by levels of education for the values of Freedom, Enjoyment, Happiness,
-and Poverty, and only two affective values show significant differences
-between education levels: Luxury and Status. In the case of Luxury,
-dissonance is more frequent among people who have only K-12 education,
-and less frequently, albeit still high, for people with
-technical/university level education and post-graduate education.
-Furthermore, highly educated people (with postgraduate degrees)
-experience dissonance with respect to Status more frequently than with
-respect to Luxury.
-
-\hypertarget{income}{%
-\subsubsection{Income}\label{income}}
-
-The next variable we examine is income, and in this case three affective
-values are significant: Poverty, Luxury, and Status. Since Poverty is a
-negative affect, we see here that lower income people tend to associate
-this feeling to their primary mode of commuting more frequently (almost
-20\% of the time) than other income groups. For example, whereas
-approximately 16\% of mid-income people are dissatisfied with their
-primary mode of travel in this respect, less than 7\% of high income
-individuals are. Dissonance with respect to Luxury and Status also tends
-to be more common among lower income people, and declines substantially
-for mid- and high income respondents. Notice as well that the frequency
-of dissonance is higher in terms of Luxury than Status for mid- and high
-income people.
-
-\hypertarget{primary-mode-of-travel}{%
-\subsubsection{Primary mode of travel}\label{primary-mode-of-travel}}
-
-The variable that shows the largest differences in the frequency of
-dissonance is the primary mode of travel. It can be seen in Table
-\ref{tab:cross-tabulation-results} that the differences are
-significative for all six affective values. Dissonance is particularly
-accute for users of public transportation when it comes to the values of
-Freedom, Enjoyment, and Happiness: almost 100\% of users of public
-transportation have identified other mode or modes as better
-representing those values. Dissonance on these values is the least for
-active travellers: less than 50\% of respondents associate Freedom to a
-different mode, and only around 60\% identified a different mode when
-responding to the values of Enjoyment and Happiness, compared to
-approximately 79\% and 71\% of those who travelled by Car. The picture
-changes when the values of Poverty, Luxury, and Status are considered.
-In this case, dissonance is less frequent for people who travel by car:
-less than 3\% of car users associate car with feelings of poverty, 41\%
-associate Luxury with a mode other than car, and only about 31\% relate
-Status to a different mode. Dissonance is more frequent in these values
-for active travellers, and users of public transportation and other
-modes, in no case being less than 75\%, and being virtually 100\% for
-users of public transportation, who consistently associate Luxury and
-Status with modes \emph{other} than public transportation.
-
-\hypertarget{typical-commute-time}{%
-\subsubsection{Typical commute time}\label{typical-commute-time}}
-
-Turning now to typical commute time, four affectie values show
-significant differences at better than 10\% confidence: Freedom,
-Happiness, Luxury, and Status. Perhaps not surprisingly, dissonance is
-more frequent among people whose typical commutes are longer. This is in
-line with previous findings: both St-Louis et al.~(2014) and Smith
-(2017) report that commute satisfaction tends to decline with longer
-commutes, whereas Handy and Thigpen (2019) found that commute distance
-was a negative covariate of commute satisfaction.
-
-\begin{landscape}\begin{table}
-
-\caption{\label{tab:table-cross-tabulation-results-without-instrumental}\label{tab:cross-tabulation-results}Percentage of respondents who report mode dissonance with respect to various SWB factors}
-\centering
-\begin{tabular}[t]{lcccccccccccc}
-\toprule
-Variable & Freedom & $\chi^2$ p-val & Enjoyment & $\chi^2$ p-val & Happiness & $\chi^2$ p-val & Poverty & $\chi^2$ p-val & Luxury & $\chi^2$ p-val & Status & $\chi^2$ p-val\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Age}}\\
-\hspace{1em}< 35 & 89.88 &  & 94.33 &  & 93.52 &  & 87.63 &  & 89.43 &  & 87.17 & \\
-
-\hspace{1em}35 - 54 & 74.22 &  & 81.45 &  & 82.26 &  & 87.38 &  & 70.18 &  & 68.70 & \\
-
-> 54 & 74.00 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 72.92 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 68.75 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 76.19 & \multirow{-3}{*}{\centering\arraybackslash 0.4095} & 78.57 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 66.67 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Education}}\\
-\hspace{1em}K-12 & 85.98 &  & 92.16 &  & 89.22 &  & 79.27 &  & 95.10 &  & 92.39 & \\
-
-\hspace{1em}Tech/Univ & 83.00 &  & 86.94 &  & 86.94 &  & 88.51 &  & 78.99 &  & 75.00 & \\
-
-Graduate & 78.57 & \multirow{-3}{*}{\centering\arraybackslash 0.9063} & 85.19 & \multirow{-3}{*}{\centering\arraybackslash 0.7005} & 84.62 & \multirow{-3}{*}{\centering\arraybackslash 0.9694} & 86.36 & \multirow{-3}{*}{\centering\arraybackslash 0.3608} & 76.00 & \multirow{-3}{*}{\centering\arraybackslash 0.0058} & 79.17 & \multirow{-3}{*}{\centering\arraybackslash 0.013}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Income}}\\
-\hspace{1em}Low & 86.51 &  & 82.11 &  & 88.62 &  & 80.19 &  & 88.71 &  & 88.70 & \\
-
-\hspace{1em}Middle & 84.52 &  & 89.80 &  & 88.00 &  & 83.76 &  & 85.82 &  & 80.00 & \\
-
-High & 79.19 & \multirow{-3}{*}{\centering\arraybackslash 0.5755} & 90.97 & \multirow{-3}{*}{\centering\arraybackslash 0.2264} & 85.82 & \multirow{-3}{*}{\centering\arraybackslash 0.9698} & 93.69 & \multirow{-3}{*}{\centering\arraybackslash 0.0642} & 73.68 & \multirow{-3}{*}{\centering\arraybackslash 0.0204} & 70.31 & \multirow{-3}{*}{\centering\arraybackslash 0.0137}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Mode}}\\
-\hspace{1em}Car & 58.93 &  & 78.90 &  & 70.91 &  & 97.96 &  & 41.00 &  & 30.69 & \\
-
-\hspace{1em}Active & 46.34 &  & 60.98 &  & 57.89 &  & 75.76 &  & 89.47 &  & 81.82 & \\
-
-\hspace{1em}Public & 99.23 &  & 96.76 &  & 98.80 &  & 81.35 &  & 100.00 &  & 99.57 & \\
-
-Other & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $< 0.001$} & 86.96 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 93.33 & \multirow{-4}{*}{\centering\arraybackslash 0.0045} & 72.73 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 90.00 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$}\\
-\cmidrule{1-13}
-\addlinespace[0.3em]
-\multicolumn{13}{l}{\textbf{Commute Time}}\\
-\hspace{1em}< 20 min & 65.93 &  & 82.95 &  & 77.27 &  & 86.11 &  & 73.49 &  & 67.09 & \\
-
-\hspace{1em}20 - 40 min & 85.86 &  & 87.50 &  & 89.58 &  & 90.41 &  & 83.87 &  & 81.18 & \\
-
-\hspace{1em}40 - 60 min & 83.04 &  & 89.91 &  & 89.62 &  & 86.08 &  & 82.35 &  & 77.78 & \\
-
-> 60 min & 95.93 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 92.17 & \multirow{-4}{*}{\centering\arraybackslash 0.6115} & 93.28 & \multirow{-4}{*}{\centering\arraybackslash 0.0394} & 83.02 & \multirow{-4}{*}{\centering\arraybackslash 0.9225} & 91.15 & \multirow{-4}{*}{\centering\arraybackslash 0.0925} & 90.09 & \multirow{-4}{*}{\centering\arraybackslash 0.0158}\\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{landscape}
-
-\hypertarget{which-modes-do-travellers-associate-with-affective-values}{%
-\subsection{Which modes do travellers associate with affective
-values?}\label{which-modes-do-travellers-associate-with-affective-values}}
-
-The preceding analysis suggests that there is significant mode
-dissonance along various dimensions and for various affective values.
-This is for the most part in line with previous research, although by
-examining different affective values individually instead of a summary
-measure of wellbeing, we are able to differentiate better in terms of
-how travellers respond to different affects. Less is known about the
-values that travellers associate with modes \emph{other} than the one
-they use. For this reason, after developing a profile of the travelers
-who experience mode dissonance in the preceding section, we are now
-interested in the responses of travellers with respect to the modes they
-tend to associate with various affective values. For this analysis we
-employ a visualization technique known as a mosaic plot. Mosaic plots
-are used in the exploration of multivariate categorical data (Friendly,
-1994; Hofmann, 2000), and they provide visual representations of
-multi-way contingency tables. The elements of the mosaic plot are called
-\emph{tiles}, and the dimensions of each tile are proportional to values
-of variables in the underlying table.
-
-We begin our analysis by plotting primary mode of travel and the modes
-associated with each affective value (see Figure
-\ref{fig:mosaic-plots-by-attribute}). The height of tile \(j\) in these
-mosaics corresponds to the proportion of travellers who primarily travel
-by mode \(j\), hence we can see that the most common primary mode of
-travel in this sample is by public transportation, followed by car,
-active travel, and other (also see Figure
-\ref{fig:primary-mode-travel}). Notice that there are some small
-discrepancies in the heights across affective values: these are caused
-by a small number of non-responses. Next, the width of the tile \(k\) in
-the mosaics is proportional to the frequency with which a mode was named
-in relation to affective value \(i\). Recall that respondents could
-nominate more than one mode in response to each affective value, and
-some did. For this reason, we used sampling weights, so that the total
-number of responses corresponds to the size of the sample.
-
-In terms of Freedom, we see that Car users frequently identify this
-affect with the use of Car; however, those who do not, very often select
-Active Travel as the mode that better represents Freedom. A majority of
-active travellers, on the other hand, identify Active Travel as the mode
-that evokes feelings of Freedom; few of them attach this value to Car,
-and even fewer to public transportation and other modes. Travellers
-whose primary mode of travel is public transportation seldom associate
-this mode with Freedom, and in fact more frequently relate this
-affective response to Active Travel followed by Car. Users of other
-modes seem to be split almost equally in their attribution of Freedom,
-between Active Travel, Car, and Other. In general, Active Travel is the
-mode most often identified as embodying Freedom, with the exception of
-Car travellers.
-
-The pattern with respect to Enjoyment is similar to that for Freedom,
-but with an even more decisive tilt towards Active Travel, with even
-more respondents whose primary mode of travel is Car choosing Active
-Travel as the mode that better represents Enjoyment. Notice that very
-few of Active Travelers selected Car as an enjoyable mode. Likewise,
-compared to Freedom, Active Travel is perceived as being more enjoyable
-by users of Public Transportatoin and Other modes. Responses with
-respect to Happiness are somewhere in between Freedom and Enjoyment, but
-Happiness is, if anything, even less frequently identified with Public
-Transportation.
-
-Three other affective responses show a marked difference. Public
-Transportation was seldom associated by respondents to feelings of
-Freedom, Enjoyment, and Happiness; on the other hand, it is the mode
-that is most commonly selected by respondents for evoking feelings of
-Poverty - even by users of Public Transportation. Active Travel was the
-second most common response for its association with Poverty. Likewise,
-Whereas Active Travel was often associated to feelings of Freedom,
-Enjoyment, and Happiness, the mode most frequently associated with
-Luxury and Status is the Car, although active travellers seem to be
-somewhat more resistant to this association compared to respondents who
-travel by Car, Public Transportation, and Other modes.
-
-Next, we further explore these responses after stratifying by Age,
-Education, Income, and Commute Time. We test the underlying 3-way tables
-by means of the Cochran-Mantel-Haenszel \(\chi^2\) test of independence.
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-1.pdf}
-\caption{\label{fig:mosaic-plots-by-attribute}Mosaic plots for affective
-values; the y-axis is the proportion of respondents by main mode of
-transportation, and the x-axis is the proportion of modes selected for
-each value}
-\end{figure}
-
-\hypertarget{age-1}{%
-\subsubsection{Age}\label{age-1}}
-
-There are some interesting differences when viewed from the perspective
-of travellers of different ages (see Figure
-\ref{fig:mosaic-plots-by-age}). For example, as seen above, active
-travel is commonly associated with freedom, happiness, and enjoyment,
-even by car users, but especially by users of public transportation and
-other modes. However, when we break this down by age, we notice that
-this tendency weakens as people age, and older travellers increasingly
-associate these affective values to the car. Furthermore, the tendency
-to associate status with the car tends to increase with age, with the
-possible exception of public transport users, for whom other options
-(possibly taxi), gain status for older travellers (\textgreater{} 54) at
-the expense of other modes, including the car. In contrast, the car
-loses in the value of luxury with age, while other options become more
-commonly associated with feelings of luxury for older respondents, even
-for car users (Figure 2). Older car users (\textgreater{} 54) show less
-dissonance in status than in luxury, while active travellers present
-more dissonance in status than in luxury - and in fact, they more
-commonly project status in the car.
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-age-1.pdf}
-\caption{\label{fig:mosaic-plots-by-age}Mosaic plots for affective
-values by age; the y-axis is the proportion of respondents by main mode
-of transportation, and the x-axis is the proportion of modes selected
-for each value (p-values are for Cochran-Mantel-Haenszel Chi-Squared
-Test)}
-\end{figure}
-
-\hypertarget{education-1}{%
-\subsubsection{Education}\label{education-1}}
-
-Only two affective values were significant in the preceding analysis
-when seen from the perspective of education, namely luxury and status.
-As seen in Figure \ref{fig:mosaic-plots-by-education}, the perceptions
-of luxury and status are fairly consistent when differentiated by
-education. Most respondents tend to associate luxury and status to the
-use of car, albeit this association is stronger for status than for
-luxury. The second mode most often mentioned in relation to luxury is
-``other'' likely due to the flexibility and convenience (but cost) of
-using taxis. The exception in this case is the traveller with graduate
-education who uses active modes. This type of respondent, while still
-more likely to associate luxury and status with the car, more commonly
-links active travel to these affects than travellers with lower levels
-of education. Most public transport users tend to associate luxury and
-status to the car, however, they associate active modes with status more
-than the same group with respect to luxury.
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-education-1.pdf}
-\caption{\label{fig:mosaic-plots-by-education}Mosaic plots for affective
-values by education; the y-axis is the proportion of respondents by main
-mode of transportation, and the x-axis is the proportion of modes
-selected for each value (p-values are for Cochran-Mantel-Haenszel
-Chi-Squared Test)}
-\end{figure}
-
-\hypertarget{income-1}{%
-\subsubsection{Income}\label{income-1}}
-
-Three affective values were significant in the analysis by income;
-perhaps not surprisingly, all three have an economic dimension. Figure
-\ref{fig:mosaic-plots-by-income} reflects some important social
-inequalities associated with the way users feel about transportation in
-Santiago. When the affective perception of poverty is analyzed, the
-image shows that generally public transport is the mode most commonly
-associated with poverty. There are some interesting differences,
-however, to be observed by income level. Whereas middle income users of
-public transportation associate this mode to poverty most frequently,
-this is not the case of high income users of public transportation, who
-tend to link active travel to poverty with greater frequency. Similarly,
-active travel is more often associated with poverty by low income
-travellers than middle or high income travellers. A possible explanation
-for this is that walking or cycling are related to the idea of a lack of
-financial means to access other modes of transport. For high income car
-users, on the other hand, public transportation may have connotations of
-poverty due to its massive use, whereas active travel may be seen more
-as a lifestyle alternative.
-
-With respect to luxury and status, we see again that these two values
-coincide more strongly in their association with the car. Moreover, we
-also notice that these perceptions become increasingly frequent at
-higher levels of income. Unlike users of other modes, the high-income
-public transport user group tends to concentrate a broader association
-of luxury and status factors with active transport, reinforcing the
-notion that at higher levels of income, people may see active modes as a
-lifestyle alternative. High income active travellers, although still
-more likely to associate luxury and status to the car, are more likely
-than users of other modes to associate these affects to active travel,
-perhaps due to an awareness of the benefits of walking and using the
-bicycle. Furthermore, high-income users of cars are more likely to
-experience consonance with respect to status and luxury, in what might
-be a form of self-congratulatory confirmation of success.
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-income-1.pdf}
-\caption{\label{fig:mosaic-plots-by-income}Mosaic plots for affective
-values by income; the y-axis is the proportion of respondents by main
-mode of transportation, and the x-axis is the proportion of modes
-selected for each value (p-values are for Cochran-Mantel-Haenszel
-Chi-Squared Test)}
-\end{figure}
-
-\hypertarget{typical-commute-time-1}{%
-\subsubsection{Typical commute time}\label{typical-commute-time-1}}
-
-The last dimension that we examine is typical commute time. Four
-affective values were significant along this dimension in Table
-\ref{tab:cross-tabulation-results}. Figure
-\ref{fig:mosaic-plots-by-travel-time} shows the way travellers associate
-different affective values to modes of transportation by length of
-typical commute. The first couple of factors, freedom and enjoyment, are
-associated with eudaimonic and hedonic factors of wellbeing, as
-discussed earlier in the paper. On the other hand, the luxury and status
-are defined mainly by a socio-economic component. As seen in the figure,
-freedom and enjoyment are most frequently mentioned in relation to
-active travel, followed by car. However, active travel is more
-frequently associated with freedom and enjoyment by people who typically
-undertake relatively short trips (\textless20 min) or travellers whose
-typical trips are longer (\textgreater60 min). In this respect, active
-travel may be seen as an ideal mode for trips, and as an enviable mode
-by people whose trips are longer.
-
-In the case of luxury and status factors, both follow a similar pattern,
-despite variations in travel times. Despite the travel time exceeding 60
-minutes, car users consider that their transport mode is mostly
-associated with luxury and status. The users of active transport in the
-sample tend to travel less than 20 minutes, and this is the same segment
-that considers that the status and luxury factors correspond mainly to
-the car and then to active transport. Looking at the four factors set
-out in Figure \ref{fig:mosaic-plots-by-travel-time}, it could be
-understood that the modes that are associated with intrinsically
-positive characteristics such as freedom and enjoyment tend to use
-public transport. On the contrary, factors such as luxury and status
-tend to have a negative connotation, where the association with the car
-and other modes of transport (such as the individual taxi and the
-collective taxi) tends to dominate.
-
-\begin{figure}
-\centering
-\includegraphics{Dissonance_Santiago_v1_files/figure-latex/figure-mosaic-plots-by-attribute-and-time-1.pdf}
-\caption{\label{fig:mosaic-plots-by-travel-time}Mosaic plots for
-affective values by commute time; the y-axis is the proportion of
-respondents by main mode of transportation, and the x-axis is the
-proportion of modes selected for each value (p-values are for
-Cochran-Mantel-Haenszel Chi-Squared Test)}
-\end{figure}
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-Subjective wellbeing is a topic that has attracted considerable
-attention in recent years due to its relationship with health. In the
-field of transportation, there is a large and growing body of literature
-that documents the way transportation can impact subjective wellbeing.
-Likewise, there is strong evidence that subjective wellbeing can
-influence travel behavior. As the world tries to move from a culture
-dominated by a century-long love affair with the automobile, there is a
-pressing need to understand how travellers perceive different modes of
-transportation from the lens of subjective wellbeing. Insights in this
-regard could prove valuable to develop and implement plans and policies
-to attract and retain users to healthier, more environmentally friendly
-transportation options, in particular active travel and public
-transportation. For this reason, understanding mode dissonance, the
-extent to which the context of travellers differs from their
-aspirations, is a worthwhile topic for research.
-
-The premise of the research presented in this paper is that subjective
-wellbeing is a composite construct of various affective values. In this
-paper we investigated mode dissonance from the perspective of six
-affective values associated with subjective wellbeing, namely freedom,
-enjoyment, happiness, poverty, luxury, and status. The research
-presented here was based on a sample of travellers in Santiago, the
-capital of Chile. Participants in this research were asked about their
-typical mode of travel, and then about the mode or modes that they
-associate with each of the six affective values. Analysis using
-hypothesis testing (tests of independence) and vizualization techniques
-(mosaic plots) uncovered interesting patterns. Some of our findings are
-well aligned with previous research; for example, active travellers
-experience less dissonance than car users, and users of public
-transportation experience the most dissonance of all. However, by
-considering affective values separately instead of aggregating them into
-a single indicator of subjective wellbeing, we manage to preserve some
-granularity with respect to various responses. This turns out to be
-important, because hedonic/eudaimonic values are more frequently related
-to active travel (freedom, enjoyment, happiness), whereas poverty is
-more frequently related to public transportation and active travel.
-Luxury and status, on the other hand, are more frequently associated to
-luxury and status.
-
-Further delving into the question of which modes are associated with
-these affective values, we find that there are important differences in
-terms of the typical mode of travel. Active travellers experience
-dissonance with relatively little frequently with respect to freedom,
-enjoyment, and happiness, but when they do, they tend to attach positive
-values to the car. Car users experience dissonance with respect to these
-affects more frequently than active travellers, and when they do, they
-strongly relate possitive hedonic/eudaimonic values to active travel. In
-other words, it is possible that drivers dream of walking when it comes
-to feelings especially of enjoyment and happiness. The other side of the
-coin is also interesting. When it comes to affective values with a
-stronger socio-economic flavor, such as poverty, luxury, and status, car
-users tend to experience dissonance less frequently than users of other
-modes. Active travellers, altough more resistant to the lure of the car
-compared to users of public transportation, also tend to attach values
-of luxury and status to the car when they experience dissonance.
-
-An examination of these effects by age, level of education, level of
-income, and typical trip duration reveals that some of the responses
-become more pronounced. For instance, older people are less likely than
-younger people to associate active travel with positive
-hedonic/eudaimonic affects, and are more likely to attach these values
-to the car. People with higher incomes are more atuned to the luxury and
-status values of cars, whereas lower income people are more likely to
-relate active travel to luxury and status.
-
-Our results not only help to flesh out some ways in which mode
-dissonance could play out from the perspective of different affects, but
-also does so in the context of a Latin American country, a region where
-historically there are deep-seated tabooes with respect to different
-modes of transportation: the poor travel by public transportation and/or
-are forced active travellers; where the rich enjoy the luxury of private
-vehicles and/or are active travellers by choice. In this way, the paper
-helps us to reflect on the ways the public experiences
-transportation-related subjective wellbeing, and how this in turn could
-be used to increase the attractiveness of public transport and active
-travel in the socio-demographic groups studied.
-
-With respect to opportunities for future research, a possible avenue for
-extending the findings reported in this paper relates to the use of the
-modes other than the typical mode of transportation. In a recent paper
-that investigaed commute satisfaction for car users, Al-Ayyash and
-Abou-Zeid (2019) considered three models: for current trip satisfaction,
-remembered satisfaction while using public transport, and current
-satisfaction using public transport. The findings suggest that low
-service quality in public transportation can result in a generalised
-negative perception, and that this perception is more difficult to
-smooth if commuters do not regularly use public transport. Another
-avenue for future research could be to consider the mix of modes
-typically used. While in this paper the analysis focused on the primary
-mode of transportation, many travellers experience more than one mode of
-transportation in their daily activities. For this reason, considering
-the multimodal component of travel would be interesting; for example,
-future research could consider people who eventually arrive by bicycle
-to the metro station or people that, after using a colectivo for part of
-a trip, end their journey by bus.
-
-\hypertarget{acknowledgments}{%
-\section{Acknowledgments}\label{acknowledgments}}
-
-The following \texttt{R} packages were used in the course of this
-investigation and the authors wish to acknowledge their developers:
-\texttt{ggmosaic} (Jeppson et al., 2018), \texttt{ggthemes} (Arnold,
-2018), \texttt{kableExtra} (Zhu, 2018), \texttt{knitr} (Xie, 2018,
-2015), \texttt{rticles} (Allaire et al., 2018), and \texttt{tidyverse}
-(Wickham, 2017).
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Abenoza2017travel}{}%
-Abenoza, R.F., Cats, O., Susilo, Y.O., 2017. Travel satisfaction with
-public transport: Determinants, user classes, regional disparities and
-their evolution. Transportation Research Part A: Policy and Practice 95,
-64--84.
-
-\leavevmode\hypertarget{ref-Alayyash2019commute}{}%
-Al-Ayyash, Z., Abou-Zeid, M., 2019. Investigating commute satisfaction
-differences of private car users and public transport users in a
-developing country context. Transportation 46, 515--536.
-doi:\href{https://doi.org/10.1007/s11116-019-10000-2}{10.1007/s11116-019-10000-2}
-
-\leavevmode\hypertarget{ref-Allaire2018rticles}{}%
-Allaire, J., Xie, Y., R Foundation, Wickham, H., Journal of Statistical
-Software, Vaidyanathan, R., Association for Computing Machinery,
-Boettiger, C., Elsevier, Broman, K., Mueller, K., Quast, B., Pruim, R.,
-Marwick, B., Wickham, C., Keyes, O., Yu, M., Emaasit, D., Onkelinx, T.,
-Gasparini, A., Desautels, M.-A., Leutnant, D., MDPI, Ögreden, O., Hance,
-D., Nüst, D., 2018. Rticles: Article formats for r markdown.
-
-\leavevmode\hypertarget{ref-Anable2005work}{}%
-Anable, J., Gatersleben, B., 2005. All work and no play? The role of
-instrumental and affective factors in work and leisure journeys by
-different travel modes. Transportation Research Part A 39, 163--181.
-
-\leavevmode\hypertarget{ref-Angotti1996latin}{}%
-Angotti, T., 1996. Latin american urbanization and planning: Inequality
-and unsustainability in north and south. Latin American Perspectives 23,
-12--34.
-doi:\href{https://doi.org/10.1177/0094582X9602300403}{10.1177/0094582X9602300403}
-
-\leavevmode\hypertarget{ref-Argyle1999causes}{}%
-Argyle, M., Kahneman, D., Diener, E., Schwarz, N., 1999. Causes and
-correlates of happiness well-being: The foundations of hedonic
-psychology.(pp. 353-373). New York, NY US: Russell Sage Foundation.
-
-\leavevmode\hypertarget{ref-Arnold2018}{}%
-Arnold, J.B., 2018. Ggthemes: Extra themes, scales and geoms for
-'ggplot2'.
-
-\leavevmode\hypertarget{ref-Bejarano2017user}{}%
-Bejarano, M., Ceballos, L.M., Maya, J., 2017. A user-centred assessment
-of a new bicycle sharing system in medellin. Transportation Research
-Part F-Traffic Psychology and Behaviour 44, 145--158.
-doi:\href{https://doi.org/10.1016/j.trf.2016.11.004}{10.1016/j.trf.2016.11.004}
-
-\leavevmode\hypertarget{ref-Bergstad2011subjective}{}%
-Bergstad, C.J., Gamble, A., Gärling, T., Hagman, O., Polk, M., Ettema,
-D., Friman, M., Olsson, L.E., 2011. Subjective well-being related to
-satisfaction with daily travel. Transportation 38, 1--15.
-
-\leavevmode\hypertarget{ref-Bergstad2011affective}{}%
-Bergstad, C.J., Gamble, A., Hagman, O., Polk, M., Garling, T., Olsson,
-L.E., 2011. Affective-symbolic and instrumental-independence
-psychological motives mediating effects of socio-demographic variables
-on daily car use. Journal of Transport Geography 19, 33--38.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.11.006}{10.1016/j.jtrangeo.2009.11.006}
-
-\leavevmode\hypertarget{ref-Bocarejo2012transport}{}%
-Bocarejo, S.J.P., Oviedo, H.D.R., 2012. Transport accessibility and
-social inequities: A tool for identification of mobility needs and
-evaluation of transport investments. Journal of Transport Geography 24,
-142--154.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2011.12.004}{10.1016/j.jtrangeo.2011.12.004}
-
-\leavevmode\hypertarget{ref-Bornioli2019affective}{}%
-Bornioli, A., Parkhurst, G., Morgan, P.L., 2019. Affective experiences
-of built environments and the promotion of urban walking. Transportation
-Research Part a-Policy and Practice 123, 200--215.
-doi:\href{https://doi.org/10.1016/j.tra.2018.12.006}{10.1016/j.tra.2018.12.006}
-
-\leavevmode\hypertarget{ref-Boschman2008toward}{}%
-Boschmann, E.E., Kwan, M.P., 2008. Toward socially sustainable urban
-transportation: Progress and potentials. International Journal of
-Sustainable Transportation 2, 138--157.
-
-\leavevmode\hypertarget{ref-Brown2009planning}{}%
-Brown, J.R., Morris, E.A., Taylor, B.D., 2009. Planning for cars in
-cities: Planners, engineers, and freeways in the 20th century. Journal
-of the American Planning Association 75, 161--177.
-doi:\href{https://doi.org/10.1080/01944360802640016}{10.1080/01944360802640016}
-
-\leavevmode\hypertarget{ref-Cao2014satisfaction}{}%
-Cao, X.Y., Ettema, D.F., 2014. Satisfaction with travel and residential
-self-selection: How do preferences moderate the impact of the hiawatha
-light rail transit line? Journal of Transport and Land Use 7, 93--108.
-doi:\href{https://doi.org/10.5198/jtlu.v7i3.485}{10.5198/jtlu.v7i3.485}
-
-\leavevmode\hypertarget{ref-Chapman2007transport}{}%
-Chapman, L., 2007. Transport and climate change: A review. Journal of
-Transport Geography 15, 354--367.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2006.11.008}{10.1016/j.jtrangeo.2006.11.008}
-
-\leavevmode\hypertarget{ref-Chatterjee2019commuting}{}%
-Chatterjee, K., Chng, S., Clark, B., Davis, A., De Vos, J., Ettema, D.,
-Handy, S., Martin, A., Reardon, L., 2019. Commuting and wellbeing: A
-critical overview of the literature with implications for policy and
-future research. Transport Reviews 30.
-doi:\href{https://doi.org/10.1080/01441647.2019.1649317}{10.1080/01441647.2019.1649317}
-
-\leavevmode\hypertarget{ref-Clark1996satisfaction}{}%
-Clark, A.E., Oswald, A.J., 1996. Satisfaction and comparison income.
-Journal of public economics 61, 359--381.
-
-\leavevmode\hypertarget{ref-Delbosc2012role}{}%
-Delbosc, A., 2012. The role of well-being in transport policy. Transport
-Policy 23, 25--33.
-doi:\href{https://doi.org/10.1016/j.tranpol.2012.06.005}{10.1016/j.tranpol.2012.06.005}
-
-\leavevmode\hypertarget{ref-Devos2018people}{}%
-De Vos, J., 2018. Do people travel with their preferred travel mode?
-Analysing the extent of travel mode dissonance and its effect on travel
-satisfaction. Transportation Research Part a-Policy and Practice 117,
-261--274.
-doi:\href{https://doi.org/10.1016/j.tra.2018.08.034}{10.1016/j.tra.2018.08.034}
-
-\leavevmode\hypertarget{ref-Devos2019satisfaction}{}%
-De Vos, J., 2019. Satisfaction-induced travel behaviour. Transportation
-Research Part F-Traffic Psychology and Behaviour 63, 12--21.
-doi:\href{https://doi.org/10.1016/j.trf.2019.03.001}{10.1016/j.trf.2019.03.001}
-
-\leavevmode\hypertarget{ref-Devos2016travel}{}%
-De Vos, J., Mokhtarian, P.L., Schwanen, T., Van Acker, V., Witlox, F.,
-2016. Travel mode choice and travel satisfaction: Bridging the gap
-between decision utility and experienced utility. Transportation 43,
-771--796.
-
-\leavevmode\hypertarget{ref-Devos2013travel}{}%
-De Vos, J., Schwanen, T., Van Acker, V., Witlox, F., 2013. Travel and
-subjective well-being: A focus on findings, methods and future research
-needs. Transport Reviews 33, 421--442.
-doi:\href{https://doi.org/10.1080/01441647.2013.815665}{10.1080/01441647.2013.815665}
-
-\leavevmode\hypertarget{ref-Devos2015satisfying}{}%
-De Vos, J., Schwanen, T., Van Acker, V., Witlox, F., 2015. How
-satisfying is the scale for travel satisfaction? Transportation Research
-Part F-Traffic Psychology and Behaviour 29, 121--130.
-doi:\href{https://doi.org/10.1016/j.trf.2015.01.007}{10.1016/j.trf.2015.01.007}
-
-\leavevmode\hypertarget{ref-Devos2019satisfying}{}%
-De Vos, J., Schwanen, T., Van Acker, V., Witlox, F., 2019. Do satisfying
-walking and cycling trips result in more future trips with active travel
-modes? An exploratory study. International Journal of Sustainable
-Transportation 13, 180--196.
-doi:\href{https://doi.org/10.1080/15568318.2018.1456580}{10.1080/15568318.2018.1456580}
-
-\leavevmode\hypertarget{ref-Devos2017travel}{}%
-De Vos, J., Witlox, F., 2017. Travel satisfaction revisited. On the
-pivotal role of travel satisfaction in conceptualising a travel
-behaviour process. Transportation Research Part a-Policy and Practice
-106, 364--373.
-doi:\href{https://doi.org/10.1016/j.tra.2017.10.009}{10.1016/j.tra.2017.10.009}
-
-\leavevmode\hypertarget{ref-Diener1997subjective}{}%
-Diener, E., Eunkook Suh, M., 1997. Subjective well-being and age: An
-international analysis. Annual review of gerontology and geriatrics 17,
-304--324.
-
-\leavevmode\hypertarget{ref-Domarchi2008effect}{}%
-Domarchi, C., Tudela, A., Gonzalez, A., 2008. Effect of attitudes, habit
-and affective appraisal on mode choice: An application to university
-workers. Transportation 35, 585--599.
-doi:\href{https://doi.org/10.1007/s11116-008-9168-6}{10.1007/s11116-008-9168-6}
-
-\leavevmode\hypertarget{ref-Eriksson2013perceived}{}%
-Eriksson, L., Friman, M., Gärling, T., 2013. Perceived attributes of bus
-and car mediating satisfaction with the work commute. Transportation
-Research Part A: Policy and Practice 47, 87--96.
-
-\leavevmode\hypertarget{ref-Ettema2011satisfaction}{}%
-Ettema, D., Garling, T., Eriksson, L., Friman, M., Olsson, L.E., Fujii,
-S., 2011. Satisfaction with travel and subjective well-being:
-Development and test of a measurement tool. Transportation Research Part
-F-Traffic Psychology and Behaviour 14, 167--175.
-doi:\href{https://doi.org/10.1016/j.trf.2010.11.002}{10.1016/j.trf.2010.11.002}
-
-\leavevmode\hypertarget{ref-Ettema2010out}{}%
-Ettema, D., Garling, T., Olsson, L.E., Friman, M., 2010. Out-of-home
-activities, daily travel, and subjective well-being. Transportation
-Research Part a-Policy and Practice 44, 723--732.
-doi:\href{https://doi.org/10.1016/j.tra.2010.07.005}{10.1016/j.tra.2010.07.005}
-
-\leavevmode\hypertarget{ref-Feldman1990settlement}{}%
-Feldman, R.M., 1990. Settlement-identity: Psychological bonds with home
-places in a mobile society. Environment and behavior 22, 183--229.
-
-\leavevmode\hypertarget{ref-Ferrer2005income}{}%
-Ferrer-i-Carbonell, A., 2005. Income and well-being: An empirical
-analysis of the comparison income effect. Journal of public economics
-89, 997--1019.
-
-\leavevmode\hypertarget{ref-Friendly1994mosaic}{}%
-Friendly, M., 1994. Mosaic displays for multi-way contingency tables.
-Journal of the American Statistical Association 89, 190--200.
-
-\leavevmode\hypertarget{ref-Friman2013psychometric}{}%
-Friman, M., Fujii, S., Ettema, D., Gärling, T., Olsson, L.E., 2013.
-Psychometric analysis of the satisfaction with travel scale.
-Transportation Research Part A: Policy and Practice 48, 132--145.
-
-\leavevmode\hypertarget{ref-Garling2019role}{}%
-Garling, T., Bamberg, S., Friman, M., 2019. THE role of attitude in
-choice of travel, satisfaction with travel, and change to sustainable
-travel, Handbook of attitudes, vol 2: Applications, 2nd ed.
-
-\leavevmode\hypertarget{ref-Gatersleben2007affective}{}%
-Gatersleben, B., Uzzell, D., 2007. Affective appraisals of the daily
-commute - comparing perceptions of drivers, cyclists, walkers, and users
-of public transport. Environment and Behavior 39, 416--431.
-
-\leavevmode\hypertarget{ref-Gossling2014sustainable}{}%
-Gossling, S., Cohen, S., 2014. Why sustainable transport policies will
-fail: EU climate policy in the light of transport taboos. Journal of
-Transport Geography 39, 197--207.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2014.07.010}{10.1016/j.jtrangeo.2014.07.010}
-
-\leavevmode\hypertarget{ref-Handy2019commute}{}%
-Handy, S., Thigpen, C., 2019. Commute quality and its implications for
-commute satisfaction: Exploring the role of mode, location, and other
-factors. Travel Behaviour and Society 16, 241--248.
-doi:\href{https://doi.org/10.1016/j.tbs.2018.03.001}{10.1016/j.tbs.2018.03.001}
-
-\leavevmode\hypertarget{ref-Hofmann2000exploring}{}%
-Hofmann, H., 2000. Exploring categorical data: Interactive mosaic plots.
-Metrika 51, 11--26.
-
-\leavevmode\hypertarget{ref-Jeppson2019ggmosaic}{}%
-Jeppson, H., Hofmann, H., Cook, D., 2018. Ggmosaic: Mosaic plots in the
-'ggplot2' framework.
-
-\leavevmode\hypertarget{ref-Khreis2016health}{}%
-Khreis, H., Warsow, K.M., Verlinghieri, E., Guzman, A., Pellecuer, L.,
-Ferreira, A., Jones, I., Heinen, E., Rojas-Rueda, D., Mueller, N.,
-Schepers, P., Lucas, K., Nieuwenhuijsen, M., 2016. The health impacts of
-traffic-related exposures in urban areas: Understanding real effects,
-underlying driving forces and co-producing future directions. Journal of
-Transport \& Health 3, 249--267.
-doi:\href{https://doi.org/10.1016/j.jth.2016.07.002}{10.1016/j.jth.2016.07.002}
-
-\leavevmode\hypertarget{ref-Lois2009relationship}{}%
-Lois, D., Lopez-Saez, M., 2009. The relationship between instrumental,
-symbolic and affective factors as predictors of car use: A structural
-equation modeling approach. Transportation Research Part a-Policy and
-Practice 43, 790--799.
-doi:\href{https://doi.org/10.1016/j.tra.2009.07.008}{10.1016/j.tra.2009.07.008}
-
-\leavevmode\hypertarget{ref-Lucas2012transport}{}%
-Lucas, K., 2012. Transport and social exclusion: Where are we now?
-Transport Policy 20, 107--115.
-doi:\href{https://doi.org/10.1016/j.tranpol.2012.01.013}{10.1016/j.tranpol.2012.01.013}
-
-\leavevmode\hypertarget{ref-Lucas2019evolution}{}%
-Lucas, K., 2019. A new evolution for transport-related social exclusion
-research? Journal of Transport Geography 102529.
-doi:\href{https://doi.org/https://doi.org/10.1016/j.jtrangeo.2019.102529}{https://doi.org/10.1016/j.jtrangeo.2019.102529}
-
-\leavevmode\hypertarget{ref-Martens2012justice}{}%
-Martens, K., Golub, A., Robinson, G., 2012. A justice-theoretic approach
-to the distribution of transportation benefits: Implications for
-transportation planning practice in the united states. Transportation
-research part A: policy and practice 46, 684--695.
-
-\leavevmode\hypertarget{ref-Miller2011collaborative}{}%
-Miller, H.J., 2011. Collaborative mobility: Using geographic information
-science to cultivate cooperative transportation systems. Procedia -
-Social and Behavioral Sciences 21, 24--28.
-doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.sbspro.2011.07.005}{http://dx.doi.org/10.1016/j.sbspro.2011.07.005}
-
-\leavevmode\hypertarget{ref-Milne2012public}{}%
-Milne, E.M.G., 2012. A public health perspective on transport policy
-priorities. Journal of Transport Geography 21, 62--69.
-doi:\href{https://doi.org/https://doi.org/10.1016/j.jtrangeo.2012.01.013}{https://doi.org/10.1016/j.jtrangeo.2012.01.013}
-
-\leavevmode\hypertarget{ref-Mokhtarian2018travel}{}%
-Mokhtarian, P.L., Pendyala, R.M., 2018. Travel satisfaction and
-well-being, in: Friman, M., Ettema, D., Olsson, L.E. (Eds.), Quality of
-Life and Daily Travel, Applying Quality of Life Research-Best Practices.
-pp. 17--39.
-doi:\href{https://doi.org/10.1007/978-3-319-76623-2_2}{10.1007/978-3-319-76623-2\_2}
-
-\leavevmode\hypertarget{ref-oecd2013oecd}{}%
-OECD, 2013. OECD guidelines on measuring subjective well-being. OECD
-Publishing.
-
-\leavevmode\hypertarget{ref-Paez2010enjoyment}{}%
-Paez, A., Whalen, K., 2010. Enjoyment of commute: A comparison of
-different transportation modes. Transportation Research Part a-Policy
-and Practice 44, 537--549.
-doi:\href{https://doi.org/10.1016/j.tra.2010.04.003}{10.1016/j.tra.2010.04.003}
-
-\leavevmode\hypertarget{ref-Pereira2017distributive}{}%
-Pereira, R.H., Schwanen, T., Banister, D., 2017. Distributive justice
-and equity in transportation. Transport reviews 37, 170--191.
-
-\leavevmode\hypertarget{ref-Redman2013quality}{}%
-Redman, L., Friman, M., Gärling, T., Hartig, T., 2013. Quality
-attributes of public transport that attract car users: A research
-review. Transport policy 25, 119--127.
-
-\leavevmode\hypertarget{ref-Redmond2001positive}{}%
-Redmond, L.S., Mokhtarian, P.L., 2001. The positive utility of the
-commute: Modeling ideal commute time and relative desired commute
-amount. Transportation 28, 179--205.
-
-\leavevmode\hypertarget{ref-Schwanen2004extent}{}%
-Schwanen, T., Mokhtarian, P.L., 2004. The extent and determinants of
-dissonance between actual and preferred residential neighborhood type.
-Environment and Planning B-Planning \& Design 31, 759--784.
-
-\leavevmode\hypertarget{ref-Shao2019analysis}{}%
-Shao, P., Liang, J., 2019. An analysis of the factors influencing the
-sustainable use intention of urban shared bicycles in china.
-Sustainability 11.
-doi:\href{https://doi.org/10.3390/su11102721}{10.3390/su11102721}
-
-\leavevmode\hypertarget{ref-Smith2017commute}{}%
-Smith, O., 2017. Commute well-being differences by mode: Evidence from
-portland, oregon, usa. Journal of Transport \& Health 4, 246--254.
-doi:\href{https://doi.org/10.1016/j.jth.2016.08.005}{10.1016/j.jth.2016.08.005}
-
-\leavevmode\hypertarget{ref-Steg2005car}{}%
-Steg, L., 2005. Car use: Lust and must. Instrumental, symbolic and
-affective motives for car use. Transportation Research Part A 39,
-147--162.
-
-\leavevmode\hypertarget{ref-Stlouis2014happy}{}%
-St-Louis, E., Manaugh, K., Lierop, D. van, El-Geneidy, A., 2014. The
-happy commuter: A comparison of commuter satisfaction across modes.
-Transportation Research Part F-Traffic Psychology and Behaviour 26,
-160--170.
-doi:\href{https://doi.org/10.1016/j.trf.2014.07.004}{10.1016/j.trf.2014.07.004}
-
-\leavevmode\hypertarget{ref-Susilo2014exploring}{}%
-Susilo, Y.O., Cats, O., 2014. Exploring key determinants of travel
-satisfaction for multi-modal trips by different traveler groups.
-Transportation Research Part a-Policy and Practice 67, 366--380.
-doi:\href{https://doi.org/10.1016/j.tra.2014.08.002}{10.1016/j.tra.2014.08.002}
-
-\leavevmode\hypertarget{ref-Tesch2008gender}{}%
-Tesch-Römer, C., Motel-Klingebiel, A., Tomasik, M.J., 2008. Gender
-differences in subjective well-being: Comparing societies with respect
-to gender equality. Social Indicators Research 85, 329--349.
-
-\leavevmode\hypertarget{ref-Van2014effect}{}%
-Van, H.T., Choocharukul, K., Fujii, S., 2014. The effect of attitudes
-toward cars and public transportation on behavioral intention in
-commuting mode choice-a comparison across six asian countries.
-Transportation Research Part a-Policy and Practice 69, 36--44.
-doi:\href{https://doi.org/10.1016/j.tra.2014.08.008}{10.1016/j.tra.2014.08.008}
-
-\leavevmode\hypertarget{ref-Whalen2013mode}{}%
-Whalen, K.E., Páez, A., Carrasco, J.A., 2013. Mode choice of university
-students commuting to school and the role of active travel. Journal of
-Transport Geography 31, 132--142.
-doi:\href{https://doi.org/http://dx.doi.org/10.1016/j.jtrangeo.2013.06.008}{http://dx.doi.org/10.1016/j.jtrangeo.2013.06.008}
-
-\leavevmode\hypertarget{ref-Wickham2017}{}%
-Wickham, H., 2017. Tidyverse: Easily install and load the 'tidyverse'.
-
-\leavevmode\hypertarget{ref-Xie2015}{}%
-Xie, Y., 2015. Dynamic documents with r and knitr, 2nd ed. Chapman;
-Hall/CRC, Boca Raton, Florida.
-
-\leavevmode\hypertarget{ref-Xie2018}{}%
-Xie, Y., 2018. Knitr: A general-purpose package for dynamic report
-generation in r.
-
-\leavevmode\hypertarget{ref-Ye2017satisfaction}{}%
-Ye, R.N., Titheridge, H., 2017. Satisfaction with the commute: The role
-of travel mode choice, built environment and attitudes. Transportation
-Research Part D-Transport and Environment 52, 535--547.
-doi:\href{https://doi.org/10.1016/j.trd.2016.06.011}{10.1016/j.trd.2016.06.011}
-
-\leavevmode\hypertarget{ref-Zhu2018}{}%
-Zhu, H., 2018. KableExtra: Construct complex table with 'kable' and pipe
-syntax.
-
-\leavevmode\hypertarget{ref-Zorrilla2019exploring}{}%
-Zorrilla, M.C., Hodgson, F., Jopson, A., 2019. Exploring the influence
-of attitudes, social comparison and image and prestige among
-non-cyclists to predict intention to cycle in mexico city.
-Transportation Research Part F-Traffic Psychology and Behaviour 60,
-327--342.
-doi:\href{https://doi.org/10.1016/j.trf.2018.10.009}{10.1016/j.trf.2018.10.009}
-
 \end{document}

### 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_v2.Rmd
v2 Revisions with BML

@@
 (2011) have compared symbolic-affective and instrumental-reasoned motives for car-use, and similar findings are reported in other studies [e.g., @Gatersleben2007affective; @Lois2009relationship].
-Previous research also demonstrates how socio-demographic factors affect the levels of SWB, includin income [@Clark1996satisfaction; @Ferrer2005income], education and unemployment [@Argyle1999causes], age [@Diener1997subjective], and gender [@Tesch2008gender].
+Previous research also demonstrates how socio-demographic factors affect the levels of SWB, including income [@Clark1996satisfaction; @Ferrer2005income], education and unemployment [@Argyle1999causes], age [@Diener1997subjective], and gender [@Tesch2008gender].
 However, further research beyond the determinants of trip satisfaction is needed to understand how these socio-demographic variables connect with the affective reactions to various modes of travel [@Stlouis2014happy].
@@
 Although the transportation experience is but one of many dimensions of inequality, the experiences in this sector have triggered exceptional discomfort and dissatisfaction among the public.
-Recent social unrest, triggered by a seemingly minor hike in the fare of public transportation, has brought many of these concerns to the forefront of the public conscience in dramatic fashion [e.g., @Davis2019; @GuardiolaRivera2019; @Sehnbruch2019].
+Recent social unrest, triggered by a seemingly minor hike in the fare of public transportation, brought many of these concerns to the forefront of the public conscience in dramatic fashion [e.g., @Davis2019].
 
@@
 An equal representation of both genders and a representation of the proportion of inhabitants per area were chosen as relevant characteristics of the sample.
-In total, there were $n=451$ valid reponses, although not every response was complete and some questions have missing values.
+In total, there were $n=451$ valid responses, although not every response was complete and some questions have missing values.
 
@@
 The relevant sections of the survey concern the individual characteristics of respondents, their feelings and affective responses related to their commute, and aspects describing their regular commute trips.
-In terms of individual characteristics and their commute, participants were asked socio-demographic information, including age (coded in three classes: younger than 35, older than 35 but younger than 55, and 55 and olde); level of education (three classes: Kindergarden to grade 12, or K-12, technical diploma or university graduate, and graduate degree), income (three classes, by tertile), and the typical duration of the respondent's regular commute (four classes, by duration in minutes).
+In terms of individual characteristics and their commute, participants were asked socio-demographic information, including age (coded in three classes: younger than 35, older than 35 but younger than 55, and 55 and older); level of education (three classes: Kindergarten to grade 12, or K-12, technical diploma or university graduate, and graduate degree), income (three classes, by tertile), and the typical duration of the respondent's regular commute (four classes, by duration in minutes).
 The descriptive statistics of the sample appear in Figure \ref{fig:descriptive-statistics}.
@@
 The next individual attribute that we examine is income, and in this case we detect significant differences in dissonance for three affective values: Poverty, Luxury, and Status.
-Since Poverty is a negative affect, we see here that lower income individuals tend to associate this feeling to their primary mode of commuting with higher frequency (almost 20% of the time) than other income groups.
+Poverty is a negative affect, and can be associated with the lack of a car [@Reutter2009who].
+In our case, we see that lower income individuals tend to associate this feeling to their primary mode of commuting with higher frequency (almost 20% of the time) than other income groups.
 Whereas approximately 16% of mid-income people are dissatisfied with their primary mode of travel when it comes to evoking feelings of Poverty, less than 7% of high income individuals are.
@@
 The result is a visual representation of a multi-way contingency table.
-Please note that due to the small numbers of travellers who use modes categorized as "Other" we henceforth exclude them from the analysis.
+Please note that due to the small numbers of travelers who use modes categorized as "Other" we henceforth exclude them from the analysis.
 
@@
 Active travelers rarely experience dissonance with respect to Freedom, Enjoyment, and Happiness.
-And although the experience of dissonance is more frequent with respect to Luxury and Status, there is still a sizeable plurality of active travellers who associate these two affective values with active travel, _not_ the car (contrast these to the responses of public transit users.)
+And although the experience of dissonance is more frequent with respect to Luxury and Status, there is still a sizable plurality of active travelers who associate these two affective values with active travel, _not_ the car (contrast these to the responses of public transit users.)
 
@@
 
-With respect to luxury and status, we see again that these two values generally are attributed to the car, but with some interesting differences by income and primary mode of travel.
+Interestingly, despite lower income individuals experiencing dissonance more frequently with respect to feelings of Poverty, we do not find that those feelings are specific to a transportation mode.
+In contrast, we see again that Luxury and Status generally are almost always attributed to the car, but with some interesting differences by income and primary mode of travel.
 Indeed, higher income active travelers, although still more likely to associate Luxury and Status with the car, are more likely than users of other modes to associate these affects to active travel, perhaps due to an awareness of the benefits of walking and using the bicycle.
@@
 Furthermore, the results reveal that within public transport users, there are also important socio-economic differences.
-In contrast, users of cars do not necessarily associate hedonic/eudaimonic values to this mode, which suggests that not only these feelings could be levaraged to attract them to active modes, but could also as a result lead to gains in wellbeing.
+In contrast, users of cars do not necessarily associate hedonic/eudaimonic values to this mode, which suggests that not only these feelings could be leveraged to attract them to active modes, but could also as a result lead to gains in wellbeing.
 

### 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_v2.tex
v2 Revisions with BML

@@
 demonstrates how socio-demographic factors affect the levels of SWB,
-includin income (Clark and Oswald, 1996; Ferrer-i-Carbonell, 2005),
+including income (Clark and Oswald, 1996; Ferrer-i-Carbonell, 2005),
 education and unemployment (Argyle et al., 1999), age (Diener and
@@
 dissatisfaction among the public. Recent social unrest, triggered by a
-seemingly minor hike in the fare of public transportation, has brought
-many of these concerns to the forefront of the public conscience in
-dramatic fashion (e.g., Davies, 2019; {\textbf{???}}; {\textbf{???}}).
+seemingly minor hike in the fare of public transportation, brought many
+of these concerns to the forefront of the public conscience in dramatic
+fashion (e.g., Davies, 2019).
 
@@
 2016). However, the focus on accessibility as a measure of inequalities
-remains predominant ({\textbf{???}}; Martínez et al., 2018; Niehaus et
-al., 2016; Rojas et al., 2016).
+remains predominant (Martínez et al., 2018; Niehaus et al., 2016; Rojas
+et al., 2016; Tiznado-Aitken et al., 2016).
 
@@
 characteristics of the sample. In total, there were \(n=451\) valid
-reponses, although not every response was complete and some questions
+responses, although not every response was complete and some questions
 have missing values.
@@
 (coded in three classes: younger than 35, older than 35 but younger than
-55, and 55 and olde); level of education (three classes: Kindergarden to
-grade 12, or K-12, technical diploma or university graduate, and
+55, and 55 and older); level of education (three classes: Kindergarten
+to grade 12, or K-12, technical diploma or university graduate, and
 graduate degree), income (three classes, by tertile), and the typical
@@
 case we detect significant differences in dissonance for three affective
-values: Poverty, Luxury, and Status. Since Poverty is a negative affect,
-we see here that lower income individuals tend to associate this feeling
-to their primary mode of commuting with higher frequency (almost 20\% of
-the time) than other income groups. Whereas approximately 16\% of
-mid-income people are dissatisfied with their primary mode of travel
+values: Poverty, Luxury, and Status. Poverty is a negative affect, and
+can be associated with the lack of a car (Reutter et al., 2009). In our
+case, we see that lower income individuals tend to associate this
+feeling to their primary mode of commuting with higher frequency (almost
+20\% of the time) than other income groups. Whereas approximately 16\%
+of mid-income people are dissatisfied with their primary mode of travel
 when it comes to evoking feelings of Poverty, less than 7\% of high
@@
 multi-way contingency table. Please note that due to the small numbers
-of travellers who use modes categorized as ``Other'' we henceforth
+of travelers who use modes categorized as ``Other'' we henceforth
 exclude them from the analysis.
@@
 more frequent with respect to Luxury and Status, there is still a
-sizeable plurality of active travellers who associate these two
-affective values with active travel, \emph{not} the car (contrast these
-to the responses of public transit users.)
+sizable plurality of active travelers who associate these two affective
+values with active travel, \emph{not} the car (contrast these to the
+responses of public transit users.)
 
@@
 
-With respect to luxury and status, we see again that these two values
-generally are attributed to the car, but with some interesting
-differences by income and primary mode of travel. Indeed, higher income
-active travelers, although still more likely to associate Luxury and
-Status with the car, are more likely than users of other modes to
-associate these affects to active travel, perhaps due to an awareness of
-the benefits of walking and using the bicycle. Furthermore, high-income
-users of cars are more likely to experience consonance with respect to
-status and luxury, in what might be a form of self-congratulatory
-confirmation of success.
+Interestingly, despite lower income individuals experiencing dissonance
+more frequently with respect to feelings of Poverty, we do not find that
+those feelings are specific to a transportation mode. In contrast, we
+see again that Luxury and Status generally are almost always attributed
+to the car, but with some interesting differences by income and primary
+mode of travel. Indeed, higher income active travelers, although still
+more likely to associate Luxury and Status with the car, are more likely
+than users of other modes to associate these affects to active travel,
+perhaps due to an awareness of the benefits of walking and using the
+bicycle. Furthermore, high-income users of cars are more likely to
+experience consonance with respect to status and luxury, in what might
+be a form of self-congratulatory confirmation of success.
 
@@
 necessarily associate hedonic/eudaimonic values to this mode, which
-suggests that not only these feelings could be levaraged to attract them
+suggests that not only these feelings could be leveraged to attract them
 to active modes, but could also as a result lead to gains in wellbeing.
@@
 
+\leavevmode\hypertarget{ref-Reutter2009who}{}%
+Reutter, L.I., Stewart, M.J., Veenstra, G., Love, R., Raphael, D.,
+Makwarimba, E., 2009. ``Who do they think we are, anyway?'': Perceptions
+of and responses to poverty stigma. Qualitative Health Research 19,
+297--311.
+doi:\href{https://doi.org/10.1177/1049732308330246}{10.1177/1049732308330246}
+
 \leavevmode\hypertarget{ref-RodriguesVignoli2008}{}%

### 2021-01-14 Dissonance_Santiago_v3/Response-to-Reviewers-v3.Rmd
v3 Revisions after comments from anonymous reviewers, Journal of Transport and Health

---
title: "Response to Reviewers"
output: pdf_document
---

We would like to thank the editor and three anonymous reviewers for their thoughtful comments and suggestions for revisions. We believe that the paper has been substantially improved by their input and we hope that they will find this version to fully address all their comments. In this letter we respond to the feedback received, and describe the actions taken to revise the paper.

\newpage

# Reviewer 1

You have helpfully structured your responses to the initial review, so your actions relating to this review can be seen. I am not entirely satisfied with some of your responses. For instance whilst Figures 1 and 2 may have been improved, they still look fairly 'amateur'. Also I am not fully satisfied that the explanation of how affective values were chosen has been substantially and explicitly acted upon. However, on my first review I considered this a good paper needing iterative improvements. I feel such improvements have been made. It is a well written paper, and better than it was, with a strong and clear narrative, an interesting topic, and detailed and extensive findings. I therefore recommend it be published.

>\textcolor{blue}{Thank you very much for your suggestions to improve the paper and for endorsing it for publication.}

\newpage

# Reviewer 2

The manuscript has been improved. It is now easier to follow the arguments and the different choices that the authors make in method, design, and analysis. I have a few minor comments.

>\textcolor{blue}{Thank you again for your suggestions to improve the paper and for endorsing it for publication.}

K-12 is still not explained (Figure 1). I do not know what it stands for.

>\textcolor{blue}{This is now explained in section 3.2, where we note that there are three levels of education, one of which is Kindergarten to grade 12, or K-12.}

Paragraph 3 is fuzzy and can be clarified. Remove redundant information and stick to the specific contribution. Then, compare points 1, 2 and 3 with the objectives presented later in the paper (e.g., line 247). It is important that the purpose is reproduced correctly throughout the paper.

>\textcolor{blue}{As noted in our response to Reviewer 1, we moved comments about literature towards the section of concluding remarks; leaving some results in the introductory section.}

Line 102 and 142. It is not common to write out the full name in references. "Cecilia" used in the reference Cecilia Jakobsson Bergstad et al., 2011 is her first name. "Cecilia" should be removed.

>\textcolor{blue}{True. We have modified that now.}

Line 105 and 147. Replace C. J. Bergstad et al., 2011 with Jakobsson Bergstad et al., 2011

>\textcolor{blue}{Done.}

Line 106/107. Remove " but see…"

>\textcolor{blue}{Done.}

Line 156/157. Replace bold text with normal text

>\textcolor{blue}{Done.}

Line 156. Replace Olson with Olsson

>\textcolor{blue}{Done.}

Line 273. significant at better than" remove "at"

>\textcolor{blue}{Done.}

Line 277. "In the case…" replace with "In this case"

>\textcolor{blue}{Done.}

Line 331. "…differences at better than 10%" remove "at"

>\textcolor{blue}{Done.}

Line 381. Misspelling of "Transportatoin"

>\textcolor{blue}{Done.}

Line 390. "Whereas" replace "W" with a lower-case "w" (don’t find that correct)

>\textcolor{blue}{Done.}

Reading difficulties in figure 3, 4 and 7. Check travel mode.

>\textcolor{blue}{We recreated this figures to remove some cluttering, hopefully increasing their readability.}

Please use upper-cases (e.g. line 391) or lower-cases (e.g., 409) for affective values throughout the manuscript.

>\textcolor{blue}{We have revised the manuscript to use upper case consistently.}

Line 514/515. Please check the sentence: "Luxury and status, on the other hand, are more frequently associated to luxury and status."

>\textcolor{blue}{Corrected.}

\newpage

# Reviewer 3

The authors have addressed my concerns and the paper looks strong. Hence, I recommend it for publication.

>\textcolor{blue}{Thank you again for your useful feedback and for endorsing the paper for publication.}

### 2021-01-14 Dissonance_Santiago_v3/Dissonance_Santiago_Title_Page_v3.Rmd
v3 Revisions after comments from anonymous reviewers, Journal of Transport and Health

--- 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_Title_Page_v2.Rmd
@@
 Participants in the study were asked about their usual mode of travel, and then were asked to name their ideal mode(s) of transportation from the perspective of various affective reactions.
-The reactions we investigate are associated with the values of freedom, enjoyment, happiness, poverty, luxury, and status.
+The reactions we investigate are associated with the values of Freedom, Enjoyment, Happiness, Poverty, Luxury, and Status.
 Analysis is based on tests of independence and visualization techniques.
@@
    The results indicate that users of public transportation experience the most dissonance in terms of affective reactions, and active travelers the least.
-For those travelers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, whereas public transportation is most commonly associated with poverty.
-The automobile, in contrast, is the mode most commonly associated with luxury and status.
+For those travelers who experience dissonance, active travel is the mode most commonly associated with Freedom, Enjoyment, and Happiness, while public transportation is most commonly associated with Poverty.
+The automobile, in contrast, is the mode most commonly associated with Luxury and Status.
 

### 2021-01-14 Dissonance_Santiago_v3/Dissonance_Santiago_Title_Page_v3.tex
v3 Revisions after comments from anonymous reviewers, Journal of Transport and Health

--- 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_Title_Page_v2.tex
@@
 
+% Pandoc citation processing
+
 % Pandoc header
@@
   reactions. The reactions we investigate are associated with the values
-  of freedom, enjoyment, happiness, poverty, luxury, and status. Analysis
+  of Freedom, Enjoyment, Happiness, Poverty, Luxury, and Status. Analysis
   is based on tests of independence and visualization techniques.\\
@@
   the least. For those travelers who experience dissonance, active travel
-  is the mode most commonly associated with freedom, enjoyment, and
-  happiness, whereas public transportation is most commonly associated
-  with poverty. The automobile, in contrast, is the mode most commonly
-  associated with luxury and status.
+  is the mode most commonly associated with Freedom, Enjoyment, and
+  Happiness, while public transportation is most commonly associated with
+  Poverty. The automobile, in contrast, is the mode most commonly
+  associated with Luxury and Status.
   \end{abstract}

### 2021-01-14 Dissonance_Santiago_v3/Dissonance_Santiago_v3.Rmd
v3 Revisions after comments from anonymous reviewers, Journal of Transport and Health

--- 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_v2.Rmd
@@
 #
-# Analysis of dissonace using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.).
+# Analysis of dissonance using the characteristics of respondents (i.e., AGE, EDUCATION, INCOME, (Mode) USED, and TRAVEL_TIME) by ATTRIBUTE (i.e., FREEDOM et al.).
 In this case, dissonance is defined as follows:
@@
 #                                                                                 #
-# Adapted from the function ctab() in the catspec packge.                         #
+# Adapted from the function ctab() in the catspec package.                         #
 #                                                                                 #
@@
 #If no type supplied, default to 'frequency + total' for univariate tables and to
-#'frequency' for multi-dimenstional tables
+#'frequency' for multi-dimensional tables
 
@@
 
-#If dec.places not set by user, set to 2 unlesss only one table of type frequency requested,
+#If dec.places not set by user, set to 2 unless only one table of type frequency requested,
 #in which case set to 0.  [Leaves user with possibility of having frequency tables with > 0 dp]
@@
 
-#If subtotals not required, and total vars > 2, create dataframe version of table, with relevent
+#If subtotals not required, and total vars > 2, create dataframe version of table, with relevant
 #subtotal rows / cols dropped [Subtotals only present in tables with > 2 cross-classified vars]
@@
   #Remove preceding and trailing spaces from category names to enable accurate capture of 'sum' rows/cols
-  #[Use of grep might extrac category labels with 'sum' as part of a longer one or two word string...]
+  #[Use of grep might extract category labels with 'sum' as part of a longer one or two word string...]
   t1 <- apply(t1,2,function(x) gsub("[[:space:]]*$","",gsub("^[[:space:]]*","",x)))
@@
 With these considerations in mind, the present research aims to investigate _who_ experiences affective dissonance with respect to their primary mode of travel.
-We focus our investigation on reactions from the perspective of feelings of freedom, enjoyment, happiness, poverty, luxury, and status - concepts termed _affective values_ hereafter.
+We focus our investigation on reactions from the perspective of feelings of Freedom, Enjoyment, Happiness, Poverty, Luxury, and Status - concepts termed _affective values_ hereafter.
 Furthermore, it is possible, even if use of a particular mode is a _must_, that travelers may still _lust_ for something else - in other words, the grass may look greener from the window of a car.
@@
 More concretely, the results indicate that users of public transportation experience the most dissonance, followed by automobile users, and finally active travelers, who tend to experience the least affective dissonance.
-For those travelers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, whereas public transportation is most commonly associated with poverty, and the automobile is most commonly associated with luxury and status.
+For those travelers who experience dissonance, active travel is the mode most commonly associated with Freedom, Enjoyment, and Happiness, whereas public transportation is most commonly associated with Poverty, and the automobile is most commonly associated with Luxury and Status.
 We also find that there are significant variations in dissonance by age, education, income, and typical commute time.
@@
 The frequency tables are tested in every case using $\chi^2$ tests of independence ($p$-values are reported in the table; lower $p$-values mean that the null hypothesis of independence can be rejected with greater confidence).
-It is interesting to note that the only category for which all affective values are significant at better than 5% level of confidence is mode of travel.
+It is interesting to note that the only category for which all affective values are significant ($p\leq0.05$) is mode of travel.
 
@@
 
-Turning now to typical commute time, four affective values show significant differences at better than 10% confidence: Freedom, Happiness, Luxury, and Status.
+Turning now to typical commute time, four affective values show significant differences with $p\leq0.10$: Freedom, Happiness, Luxury, and Status.
 Perhaps not surprisingly, dissonance is more frequent among people whose typical commutes are longer.
 This is in line with previous findings: both St-Louis et al.
-[-@Stlouis2014happy] and Smith [-@Smith2017commute] report that commute satisfaction tends to decline with longer commutes, whereas Handy and Thigpen [-@Handy2019commute] found that commute distance was a negative covariate of commute satisfaction.
+[-@Stlouis2014happy] and Smith [-@Smith2017commute] report that commute satisfaction tends to decline with longer commutes, and Handy and Thigpen [-@Handy2019commute] found that commute distance was a negative covariate of commute satisfaction.
 
@@
   group_by(IDEAL, ATTRIBUTE, USED) %>%
-  summarize(n= sum(WEIGHT)) %>%
+  summarize(n= sum(WEIGHT),
+            .groups = "drop") %>%
   ungroup() %>%
   # rename(MODE = IDEAL) %>%
-  mutate(CASE = "IDEAL",
+  mutate(ATTRIBUTE = factor(ATTRIBUTE,
+                            level = c("FREEDOM", "ENJOYMENT", "HAPPINESS", "POVERTY", "LUXURY", "STATUS")),
+         CASE = "IDEAL",
          USED = factor(USED, 
                        levels = c("Car", "Active", "Public"),
-                       labels = c("USED: CAR", "USED: ACTIVE", "USED: PUBLIC")))
+                       labels = c("Used: Car", "Used: Active", "Used: Public")))
 
@@
   group_by(USED, ATTRIBUTE) %>%
-  summarize(t = sum(n))
+  summarize(t = sum(n),
+            .groups = "drop")
 
@@
   theme_tufte() +
-  theme(axis.text.x = element_text(angle = 90),
+  theme(axis.text.x = element_blank(),
         legend.position = "bottom",
@@
         axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
         legend.title = element_blank())
@@
   group_by(IDEAL, ATTRIBUTE, AGE, USED) %>%
-  summarize(n= sum(WEIGHT)) %>%
+  summarize(n= sum(WEIGHT),
+            .groups = "drop") %>%
   ungroup() %>%
@@
   group_by(USED, ATTRIBUTE, AGE) %>%
-  summarize(t = sum(n))
+  summarize(t = sum(n),
+            .groups = "drop")
 
@@
                                     strip.text.y = element_blank(),
-                                    axis.title.y=element_blank(),
-                                    axis.text.y=element_blank(),
-                                    axis.ticks.y=element_blank()),
+                                    axis.title.y = element_blank(),
+                                    axis.text.y = element_blank(),
+                                    axis.ticks.y = element_blank(),
+                                    axis.text.x = element_blank(),
+                                    axis.ticks.x = element_blank()),
              Enjoyment_by_age + theme(legend.position="none", 
@@
                                       strip.text.y = element_blank(),
-                                      axis.title.y=element_blank(),
-                                      axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.title.y = element_blank(),
+                                      axis.text.y = element_blank(),
+                                      axis.ticks.y = element_blank(),
+                                    axis.text.x = element_blank(),
+                                    axis.ticks.x =element_blank()),
              Happiness_by_age + theme(legend.position="none", 
@@
                                       strip.text.y = element_blank(),
-                                      axis.title.y=element_blank(),
-                                      axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.title.y = element_blank(),
+                                      axis.text.y = element_blank(),
+                                      axis.ticks.y = element_blank(),
+                                    axis.text.x = element_blank(),
+                                    axis.ticks.x = element_blank()),
              Luxury_by_age + theme(legend.position="none", 
@@
                                    strip.text.y = element_blank(),
-                                   axis.title.y=element_blank(),
-                                   axis.text.y=element_blank(),
-                                   axis.ticks.y=element_blank()),
+                                   axis.title.y = element_blank(),
+                                   axis.text.y = element_blank(),
+                                   axis.ticks.y = element_blank(),
+                                    axis.text.x = element_blank(),
+                                    axis.ticks.x = element_blank()),
              Status_by_age + theme(legend.position="none",
@@
                                    strip.text.y = element_blank(),
-                                   axis.title.y=element_blank(),
-                                   axis.text.y=element_blank(),
-                                   axis.ticks.y=element_blank()),
-             textGrob("Car",
+                                   axis.title.y = element_blank(),
+                                   axis.text.y = element_blank(),
+                                   axis.ticks.y = element_blank(),
+                                    axis.text.x = element_blank(),
+                                    axis.ticks.x = element_blank()),
+             textGrob("Used: Car",
                       rot = 270,
                       gp = gpar(fontsize = 9),
-                      y = 0.2),
-             textGrob("Active",
-                      rot = 270,
-                      gp = gpar(fontsize = 9)),
-             textGrob("Public",
+                      y = 0.1),
+             textGrob("Used: Active",
                       rot = 270,
                       gp = gpar(fontsize = 9),
-                      y = 0.7),
+                      y = 0.3),
+             textGrob("Used: Public",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.4),
              mylegend, 
@@
   group_by(IDEAL, ATTRIBUTE, EDUCATION, USED) %>%
-  summarize(n= sum(WEIGHT)) %>%
+  summarize(n= sum(WEIGHT),
+            .groups = "drop") %>%
   ungroup() %>%
@@
   group_by(USED, ATTRIBUTE, EDUCATION) %>%
-  summarize(t = sum(n))
+  summarize(t = sum(n),
+            .groups = "drop")
 
@@
                                     strip.text.y = element_blank(),
-                                    axis.title.y=element_blank(),
-                                    axis.text.y=element_blank(),
-                                    axis.ticks.y=element_blank()),
+                                    axis.title.y = element_blank(),
+                                    axis.text.y = element_blank(),
+                                    axis.ticks.y = element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Enjoyment_by_education + theme(legend.position="none", 
@@
                                       strip.text.y = element_blank(),
-                                      axis.title.y=element_blank(),
-                                      axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.title.y = element_blank(),
+                                      axis.text.y = element_blank(),
+                                      axis.ticks.y = element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Happiness_by_education + theme(legend.position="none", 
@@
                                       strip.text.y = element_blank(),
-                                      axis.title.y=element_blank(),
-                                      axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.title.y = element_blank(),
+                                      axis.text.y = element_blank(),
+                                      axis.ticks.y = element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Luxury_by_education + theme(legend.position="none", 
@@
                                    strip.text.y = element_blank(),
-                                   axis.title.y=element_blank(),
-                                   axis.text.y=element_blank(),
-                                   axis.ticks.y=element_blank()),
+                                   axis.title.y = element_blank(),
+                                   axis.text.y = element_blank(),
+                                   axis.ticks.y = element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Status_by_education + theme(legend.position="none",
@@
                                    strip.text.y = element_blank(),
-                                   axis.title.y=element_blank(),
-                                   axis.text.y=element_blank(),
-                                   axis.ticks.y=element_blank()),
-             textGrob("Car",
+                                   axis.title.y = element_blank(),
+                                   axis.text.y = element_blank(),
+                                   axis.ticks.y = element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
+             textGrob("Used: Car",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.0),
+             textGrob("Used: Active",
                       rot = 270,
@@
                       y = 0.2),
-             textGrob("Active",
-                      rot = 270,
-                      gp = gpar(fontsize = 9)),
-             textGrob("Public",
+             textGrob("Used: Public",
                       rot = 270,
                       gp = gpar(fontsize = 9),
-                      y = 0.7),
+                      y = 0.4),
              mylegend, 
@@
   group_by(IDEAL, ATTRIBUTE, INCOME, USED) %>%
-  summarize(n= sum(WEIGHT)) %>%
+  summarize(n= sum(WEIGHT),
+            .groups = "drop") %>%
   ungroup() %>%
@@
   group_by(USED, ATTRIBUTE, INCOME) %>%
-  summarize(t = sum(n))
+  summarize(t = sum(n),
+            .groups = "drop")
 
@@
                                     axis.text.y=element_blank(),
-                                    axis.ticks.y=element_blank()),
+                                    axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Enjoyment_by_income + theme(legend.position="none", 
@@
                                       axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Happiness_by_income + theme(legend.position="none", 
@@
                                       axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Luxury_by_income + theme(legend.position="none", 
@@
                                    axis.text.y=element_blank(),
-                                   axis.ticks.y=element_blank()),
+                                   axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Status_by_income + theme(legend.position="none",
@@
                                    axis.text.y=element_blank(),
-                                   axis.ticks.y=element_blank()),
-             textGrob("Car",
+                                   axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
+             textGrob("Used: Car",
                       rot = 270,
                       gp = gpar(fontsize = 9),
-                      y = 0.2),
-             textGrob("Active",
-                      rot = 270,
-                      gp = gpar(fontsize = 9)),
-             textGrob("Public",
+                      y = 0.1),
+             textGrob("Used: Active",
                       rot = 270,
                       gp = gpar(fontsize = 9),
-                      y = 0.7),
+                      y = 0.3),
+             textGrob("Used: Public",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.4),
              mylegend, 
@@
 
-Among car users, Freedom is associated with the car in the case of every commute but the longest (>60 min), in which case active travel is more frequently identified as the mode that evokes feelings of Freedom.
+Among car users, Freedom is associated with the car in all but the longest commutes (>60 min), in which case active travel is more frequently identified as the mode that evokes feelings of Freedom.
 The associations of active travel with Enjoyment  and Happiness are consistently high among car users, although car becomes more frequently associated with this value for longer commutes.
@@
   group_by(IDEAL, ATTRIBUTE, TRAVEL_TIME, USED) %>%
-  summarize(n= sum(WEIGHT)) %>%
+  summarize(n= sum(WEIGHT),
+            .groups = "drop") %>%
   ungroup() %>%
@@
   group_by(USED, ATTRIBUTE, TRAVEL_TIME) %>%
-  summarize(t = sum(n))
+  summarize(t = sum(n),
+            .groups = "drop")
 
@@
                                     axis.text.y=element_blank(),
-                                    axis.ticks.y=element_blank()),
+                                    axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Enjoyment_by_time + theme(legend.position="none", 
@@
                                       axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Happiness_by_time + theme(legend.position="none", 
@@
                                       axis.text.y=element_blank(),
-                                      axis.ticks.y=element_blank()),
+                                      axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
              Status_by_time + theme(legend.position="none",
@@
                                    axis.text.y=element_blank(),
-                                   axis.ticks.y=element_blank()),
-             textGrob("Car",
+                                   axis.ticks.y=element_blank(),
+                                   axis.text.x = element_blank(),
+                                   axis.ticks.x = element_blank()),
+             textGrob("Used: Car",
+                      rot = 270,
+                      gp = gpar(fontsize = 9),
+                      y = 0.0),
+             textGrob("Used: Active",
                       rot = 270,
@@
 However, by considering affective values separately instead of aggregating them into a single indicator of subjective wellbeing, we manage to preserve greater granularity with respect to various responses than most studies.
-This is important because hedonic/eudaimonic values are more frequently related to active travel (Freedom, Enjoyment, Happiness), whereas Poverty is more frequently related to public transportation and active travel.
+This is important because hedonic/eudaimonic values are more frequently related to active travel (Freedom, Enjoyment, Happiness), while Poverty is more frequently related to public transportation and active travel.
 Luxury and Status, on the other hand, are more frequently associated to car.

### 2021-01-14 Dissonance_Santiago_v3/Dissonance_Santiago_v3.tex
v3 Revisions after comments from anonymous reviewers, Journal of Transport and Health

--- 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_v2.tex
@@
 \usepackage{graphicx}
-% We will generate all images so they have a width \maxwidth. This means
-% that they will get their normal width if they fit onto the page, but
-% are scaled down if they would overflow the margins.
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
-\else\Gin@nat@width\fi}
-\makeatother
-\let\Oldincludegraphics\includegraphics
-\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
 \ifxetex
@@
 % Pandoc toggle for numbering sections (defaults to be off)
+
+% Pandoc citation processing
 
@@
 with respect to their primary mode of travel. We focus our investigation
-on reactions from the perspective of feelings of freedom, enjoyment,
-happiness, poverty, luxury, and status - concepts termed \emph{affective
+on reactions from the perspective of feelings of Freedom, Enjoyment,
+Happiness, Poverty, Luxury, and Status - concepts termed \emph{affective
 values} hereafter. Furthermore, it is possible, even if use of a
@@
 experience dissonance, active travel is the mode most commonly
-associated with freedom, enjoyment, and happiness, whereas public
-transportation is most commonly associated with poverty, and the
-automobile is most commonly associated with luxury and status. We also
+associated with Freedom, Enjoyment, and Happiness, whereas public
+transportation is most commonly associated with Poverty, and the
+automobile is most commonly associated with Luxury and Status. We also
 find that there are significant variations in dissonance by age,
@@
 transportation has been the satisfaction that travelers feel towards
-their everyday mobility experience (e.g., Cecilia Jakobsson Bergstad et
-al., 2011). As a consequence, there is a wealth of research on
-satisfaction with the use of different modes of transportation. For
+their everyday mobility experience (e.g., Jakobsson Bergstad, Gamble, T.
+Gärling, et al., 2011). As a consequence, there is a wealth of research
+on satisfaction with the use of different modes of transportation. For
 example, numerous studies report that car users often have a higher
-level of satisfaction compared to other transport modes (C. J. Bergstad
-et al., 2011; Eriksson et al., 2013; Redmond and Mokhtarian, 2001),
-although others report highest commute satisfaction for bicycle and
-train commuters (e.g., Whalen et al., 2013; Handy and Thigpen, 2019). In
-a similar way, there are multiple reports that active travel also tends
-to yield higher levels of satisfaction (Gatersleben and Uzzell, 2007;
-Handy and Thigpen, 2019; Paez and Whalen, 2010; Smith, 2017; St-Louis et
-al., 2014; Whalen et al., 2013), In contrast, public transport users
-often assess their experience more negatively (Abenoza et al., 2017; De
-Vos et al., 2016; Gatersleben and Uzzell, 2007; Handy and Thigpen, 2019;
-Paez and Whalen, 2010). Multi-modal trips also influence satisfaction
-levels; for instance, individuals tend to report higher levels of
-satisfaction with the mode they use -- perhaps as a form of \emph{post
-hoc} validation of their choices or circumstance (Susilo and Cats,
-2014).
+level of satisfaction compared to other transport modes (Eriksson et
+al., 2013; Jakobsson Bergstad, Gamble, Hagman, et al., 2011; Redmond and
+Mokhtarian, 2001), although others report highest commute satisfaction
+for bicycle and train commuters (e.g., Whalen et al., 2013; Handy and
+Thigpen, 2019). In a similar way, there are multiple reports that active
+travel also tends to yield higher levels of satisfaction (Gatersleben
+and Uzzell, 2007; Handy and Thigpen, 2019; Paez and Whalen, 2010; Smith,
+2017; St-Louis et al., 2014; Whalen et al., 2013), In contrast, public
+transport users often assess their experience more negatively (Abenoza
+et al., 2017; De Vos et al., 2016; Gatersleben and Uzzell, 2007; Handy
+and Thigpen, 2019; Paez and Whalen, 2010). Multi-modal trips also
+influence satisfaction levels; for instance, individuals tend to report
+higher levels of satisfaction with the mode they use -- perhaps as a
+form of \emph{post hoc} validation of their choices or circumstance
+(Susilo and Cats, 2014).
 
@@
 influences subjective wellbeing (Delbosc, 2012), and activities have a
-direct impact on travel satisfaction (Cecilia Jakobsson Bergstad et al.,
-2011). Delbosc (2012, p. 28), for instance, has summarized the most
-significant influences on psychological wellbeing: poverty and
-employment, meaningful relationships and health. However, understanding
-the components that affect these perceptions implies the differentiation
-between affective (also named as symbolic-affective) and instrumental
-values (C. J. Bergstad et al., 2011). Steg et al.~(2011) have compared
-symbolic-affective and instrumental-reasoned motives for car-use, and
-similar findings are reported in other studies (e.g., Gatersleben and
-Uzzell, 2007; Lois and Lopez-Saez, 2009). Previous research also
-demonstrates how socio-demographic factors affect the levels of SWB,
-including income (Clark and Oswald, 1996; Ferrer-i-Carbonell, 2005),
-education and unemployment (Argyle et al., 1999), age (Diener and
-Eunkook Suh, 1997), and gender (Tesch-Römer et al., 2008). However,
-further research beyond the determinants of trip satisfaction is needed
-to understand how these socio-demographic variables connect with the
-affective reactions to various modes of travel (St-Louis et al., 2014).
+direct impact on travel satisfaction (Jakobsson Bergstad, Gamble, T.
+Gärling, et al., 2011). Delbosc (2012, p. 28), for instance, has
+summarized the most significant influences on psychological wellbeing:
+poverty and employment, meaningful relationships and health. However,
+understanding the components that affect these perceptions implies the
+differentiation between affective (also named as symbolic-affective) and
+instrumental values (Jakobsson Bergstad, Gamble, Hagman, et al., 2011).
+Steg et al.~(2011) have compared symbolic-affective and
+instrumental-reasoned motives for car-use, and similar findings are
+reported in other studies (e.g., Gatersleben and Uzzell, 2007; Lois and
+Lopez-Saez, 2009). Previous research also demonstrates how
+socio-demographic factors affect the levels of SWB, including income
+(Clark and Oswald, 1996; Ferrer-i-Carbonell, 2005), education and
+unemployment (Argyle et al., 1999), age (Diener and Eunkook Suh, 1997),
+and gender (Tesch-Römer et al., 2008). However, further research beyond
+the determinants of trip satisfaction is needed to understand how these
+socio-demographic variables connect with the affective reactions to
+various modes of travel (St-Louis et al., 2014).
 
@@
 \centering
-\includegraphics{Dissonance_Santiago_v2_files/figure-latex/plot-descriptive-statistics-1.pdf}
+\includegraphics{Dissonance_Santiago_v3_files/figure-latex/plot-descriptive-statistics-1.pdf}
 \caption{\label{fig:descriptive-statistics}Descriptive statistics of the
@@
 \centering
-\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-primary-mode-travel-1.pdf}
+\includegraphics{Dissonance_Santiago_v3_files/figure-latex/figure-primary-mode-travel-1.pdf}
 \caption{\label{fig:primary-mode-travel}Frequency of primary mode used
@@
 confidence). It is interesting to note that the only category for which
-all affective values are significant at better than 5\% level of
-confidence is mode of travel.
+all affective values are significant (\(p\leq0.05\)) is mode of travel.
 
@@
 Turning now to typical commute time, four affective values show
-significant differences at better than 10\% confidence: Freedom,
-Happiness, Luxury, and Status. Perhaps not surprisingly, dissonance is
-more frequent among people whose typical commutes are longer. This is in
-line with previous findings: both St-Louis et al.~(2014) and Smith
-(2017) report that commute satisfaction tends to decline with longer
-commutes, whereas Handy and Thigpen (2019) found that commute distance
-was a negative covariate of commute satisfaction.
+significant differences with \(p\leq0.10\): Freedom, Happiness, Luxury,
+and Status. Perhaps not surprisingly, dissonance is more frequent among
+people whose typical commutes are longer. This is in line with previous
+findings: both St-Louis et al.~(2014) and Smith (2017) report that
+commute satisfaction tends to decline with longer commutes, and Handy
+and Thigpen (2019) found that commute distance was a negative covariate
+of commute satisfaction.
 
@@
 
-> 54 & 74.00 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 72.92 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 68.75 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 76.19 & \multirow{-3}{*}{\centering\arraybackslash 0.4095} & 78.57 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 66.67 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$}\\
+\hspace{1em}> 54 & 74.00 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 72.92 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 68.75 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 76.19 & \multirow{-3}{*}{\centering\arraybackslash 0.4095} & 78.57 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$} & 66.67 & \multirow{-3}{*}{\centering\arraybackslash $<0.001$}\\
 \cmidrule{1-13}
@@
 
-Graduate & 78.57 & \multirow{-3}{*}{\centering\arraybackslash 0.9063} & 85.19 & \multirow{-3}{*}{\centering\arraybackslash 0.7005} & 84.62 & \multirow{-3}{*}{\centering\arraybackslash 0.9694} & 86.36 & \multirow{-3}{*}{\centering\arraybackslash 0.3608} & 76.00 & \multirow{-3}{*}{\centering\arraybackslash 0.0058} & 79.17 & \multirow{-3}{*}{\centering\arraybackslash 0.013}\\
+\hspace{1em}Graduate & 78.57 & \multirow{-3}{*}{\centering\arraybackslash 0.9063} & 85.19 & \multirow{-3}{*}{\centering\arraybackslash 0.7005} & 84.62 & \multirow{-3}{*}{\centering\arraybackslash 0.9694} & 86.36 & \multirow{-3}{*}{\centering\arraybackslash 0.3608} & 76.00 & \multirow{-3}{*}{\centering\arraybackslash 0.0058} & 79.17 & \multirow{-3}{*}{\centering\arraybackslash 0.013}\\
 \cmidrule{1-13}
@@
 
-High & 79.19 & \multirow{-3}{*}{\centering\arraybackslash 0.5755} & 90.97 & \multirow{-3}{*}{\centering\arraybackslash 0.2264} & 85.82 & \multirow{-3}{*}{\centering\arraybackslash 0.9698} & 93.69 & \multirow{-3}{*}{\centering\arraybackslash 0.0642} & 73.68 & \multirow{-3}{*}{\centering\arraybackslash 0.0204} & 70.31 & \multirow{-3}{*}{\centering\arraybackslash 0.0137}\\
+\hspace{1em}High & 79.19 & \multirow{-3}{*}{\centering\arraybackslash 0.5755} & 90.97 & \multirow{-3}{*}{\centering\arraybackslash 0.2264} & 85.82 & \multirow{-3}{*}{\centering\arraybackslash 0.9698} & 93.69 & \multirow{-3}{*}{\centering\arraybackslash 0.0642} & 73.68 & \multirow{-3}{*}{\centering\arraybackslash 0.0204} & 70.31 & \multirow{-3}{*}{\centering\arraybackslash 0.0137}\\
 \cmidrule{1-13}
@@
 
-Other & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $< 0.001$} & 86.96 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 93.33 & \multirow{-4}{*}{\centering\arraybackslash 0.0045} & 72.73 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 90.00 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$}\\
+\hspace{1em}Other & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $< 0.001$} & 86.96 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 91.30 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 93.33 & \multirow{-4}{*}{\centering\arraybackslash 0.0045} & 72.73 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 90.00 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$}\\
 \cmidrule{1-13}
@@
 
-> 60 min & 95.93 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 92.17 & \multirow{-4}{*}{\centering\arraybackslash 0.6115} & 93.28 & \multirow{-4}{*}{\centering\arraybackslash 0.0394} & 83.02 & \multirow{-4}{*}{\centering\arraybackslash 0.9225} & 91.15 & \multirow{-4}{*}{\centering\arraybackslash 0.0925} & 90.09 & \multirow{-4}{*}{\centering\arraybackslash 0.0158}\\
+\hspace{1em}> 60 min & 95.93 & \multirow{-4}{*}{\centering\arraybackslash $<0.001$} & 92.17 & \multirow{-4}{*}{\centering\arraybackslash 0.6115} & 93.28 & \multirow{-4}{*}{\centering\arraybackslash 0.0394} & 83.02 & \multirow{-4}{*}{\centering\arraybackslash 0.9225} & 91.15 & \multirow{-4}{*}{\centering\arraybackslash 0.0925} & 90.09 & \multirow{-4}{*}{\centering\arraybackslash 0.0158}\\
 \bottomrule
@@
 \centering
-\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-1.pdf}
+\includegraphics{Dissonance_Santiago_v3_files/figure-latex/figure-bar-plots-by-attribute-1.pdf}
 \caption{\label{fig:bar-plots-by-attribute}Plots for affective values;
@@
 \centering
-\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-age-1.pdf}
+\includegraphics{Dissonance_Santiago_v3_files/figure-latex/figure-bar-plots-by-attribute-and-age-1.pdf}
 \caption{\label{fig:bar-plots-by-age}Plots for affective values by age;
@@
 \centering
-\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-education-1.pdf}
+\includegraphics{Dissonance_Santiago_v3_files/figure-latex/figure-bar-plots-by-attribute-and-education-1.pdf}
 \caption{\label{fig:bar-plots-by-education}Plots for affective values by
@@
 \centering
-\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-income-1.pdf}
+\includegraphics{Dissonance_Santiago_v3_files/figure-latex/figure-bar-plots-by-attribute-and-income-1.pdf}
 \caption{\label{fig:bar-plots-by-income}Plots for affective values by
@@
 
-Among car users, Freedom is associated with the car in the case of every
-commute but the longest (\textgreater60 min), in which case active
-travel is more frequently identified as the mode that evokes feelings of
-Freedom. The associations of active travel with Enjoyment and Happiness
-are consistently high among car users, although car becomes more
-frequently associated with this value for longer commutes. As we have
-seen before, active travelers seldom experience dissonance with respect
-to Freedom, Enjoyment, and Happiness, and if anything the strength of
-this association increases with longer commutes. Public transportation
-users again are split in their preference towards active travel and car
-as the modes more likely to evoke feelings of Freedom, Enjoyment, and
+Among car users, Freedom is associated with the car in all but the
+longest commutes (\textgreater60 min), in which case active travel is
+more frequently identified as the mode that evokes feelings of Freedom.
+The associations of active travel with Enjoyment and Happiness are
+consistently high among car users, although car becomes more frequently
+associated with this value for longer commutes. As we have seen before,
+active travelers seldom experience dissonance with respect to Freedom,
+Enjoyment, and Happiness, and if anything the strength of this
+association increases with longer commutes. Public transportation users
+again are split in their preference towards active travel and car as the
+modes more likely to evoke feelings of Freedom, Enjoyment, and
 Happiness, and there are only relatively minor differences in these
@@
 \centering
-\includegraphics{Dissonance_Santiago_v2_files/figure-latex/figure-bar-plots-by-attribute-and-travel-time-1.pdf}
+\includegraphics{Dissonance_Santiago_v3_files/figure-latex/figure-bar-plots-by-attribute-and-travel-time-1.pdf}
 \caption{\label{fig:bar-plots-by-travel-time}Plots for affective values
@@
 because hedonic/eudaimonic values are more frequently related to active
-travel (Freedom, Enjoyment, Happiness), whereas Poverty is more
-frequently related to public transportation and active travel. Luxury
-and Status, on the other hand, are more frequently associated to car.
+travel (Freedom, Enjoyment, Happiness), while Poverty is more frequently
+related to public transportation and active travel. Luxury and Status,
+on the other hand, are more frequently associated to car.
 
@@
 
-\leavevmode\hypertarget{ref-Bergstad2011subjective}{}%
-Bergstad, C.J., Gamble, A., Gärling, T., Hagman, O., Polk, M., Ettema,
-D., Friman, M., Olsson, L.E., 2011. Subjective well-being related to
-satisfaction with daily travel. Transportation 38, 1--15.
-
-\leavevmode\hypertarget{ref-Bergstad2011affective}{}%
-Bergstad, C.J., Gamble, A., Hagman, O., Polk, M., Garling, T., Olsson,
-L.E., 2011. Affective-symbolic and instrumental-independence
-psychological motives mediating effects of socio-demographic variables
-on daily car use. Journal of Transport Geography 19, 33--38.
-doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.11.006}{10.1016/j.jtrangeo.2009.11.006}
-
 \leavevmode\hypertarget{ref-Bocarejo2012transport}{}%
@@
 doi:\href{https://doi.org/10.1016/j.tbs.2018.03.001}{10.1016/j.tbs.2018.03.001}
+
+\leavevmode\hypertarget{ref-Bergstad2011subjective}{}%
+Jakobsson Bergstad, C., Gamble, A., Gärling, T., Hagman, O., Polk, M.,
+Ettema, D., Friman, M., Olsson, L.E., 2011. Subjective well-being
+related to satisfaction with daily travel. Transportation 38, 1--15.
+
+\leavevmode\hypertarget{ref-Bergstad2011affective}{}%
+Jakobsson Bergstad, C., Gamble, A., Hagman, O., Polk, M., Garling, T.,
+Olsson, L.E., 2011. Affective-symbolic and instrumental-independence
+psychological motives mediating effects of socio-demographic variables
+on daily car use. Journal of Transport Geography 19, 33--38.
+doi:\href{https://doi.org/10.1016/j.jtrangeo.2009.11.006}{10.1016/j.jtrangeo.2009.11.006}
 

### 2021-02-20 Dissonance_Santiago_v3/Dissonance_Santiago_v3.Rmd
Created README.Rmd and updated data package prior to release

@@
 library(tidyverse)
+```
+
+```{r install-data-package, include=FALSE}
+# Run only once if needed
+devtools::install_github("paezha/Mode-Dissonance-and-Subjective-Wellbeing", subdir = "ModeDissonanceSantiago")
+```
+
+```{r}
+library(ModeDissonanceSantiago)
 ```
@@
 
-load("Dissonance_Santiago.RData")
+#load("Dissonance_Santiago.RData")
 ```
@@
 Please note that this document  was prepared using R Markdown and is an example of reproducible research [@Brunsdon2020opening].
-The R Markdown file, along with the data file needed to reproduce the analysis, are available for download\footnote{\url{https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg}}.
+The R Markdown file, along with the data file needed to reproduce the analysis, are available for download\footnote{\url{https://github.com/paezha/Mode-Dissonance-and-Subjective-Wellbeing}}.
 

### 2021-02-20 README.Rmd
Created README.Rmd and updated data package prior to release

--- 2021-02-20 Dissonance_Santiago_v3/Dissonance_Santiago_v3.Rmd
@@
 ---
-title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Affective Values
-author:
-  - name: Author 1
-    email: a1@university.com
-    affiliation: Some University
-    footnote: Corresponding Author
-  - name: Author 2
-    email: a2@school.com
-    affiliation: Some School
-address:
-  - code: Some University
-    address: Department, Street, City, State, Zip
-  - code: Some School
-    address: Department, Street, City, State, Zip
-abstract: |
-   *Introduction*  
+output: github_document
+bibliography: Dissonance_Santiago_v3/mybibfile.bib
+always_allow_html: true
+---
+
+<!-- README.md is generated from README.Rmd. Please edit that file -->
+
+```{r, include = FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>"
+)
+```
+
+# Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Affective Values
+
+<!-- badges: start -->
+<!-- badges: end -->
+
+Beatriz Mella Lira (Pontificia Universidad Católica de Chile)
+Antonio Paez (McMaster University)
+
+Journal of Transport and Health (2021), https://doi.org/xx.xxx
+
+## Abstract
+
+### Introduction
+
 Subjective wellbeing is a topic that has attracted considerable attention in the transportation literature in recent years.
@@
 An important aspect of subjective wellbeing are the affective reactions of people to their experiences.
-   *Objective*  
+
+### Objective
+
 The objective of this paper is to analyze the affective reactions of travelers with respect to various modes of transportation.
 In particular, we are interested in the potential for dissonance between primary mode of travel and the mode(s) of travel identified as evoking various affective reactions.
-   *Materials and Methods*  
+
+### Materials and Methods
+
 The study is based on data collected from a sample of travelers in the city of Santiago, in Chile.
@@
 Analysis is based on tests of independence and visualization techniques.
-   *Results*  
+
+### Results
+
 The results indicate that users of public transportation experience the most dissonance in terms of affective reactions, and active travelers the least.
@@
 
-journal: "Journal of Transport & Health"
-date: "`r Sys.Date()`"
-bibliography: mybibfile.bib
-linenumbers: true
-numbersections: true
-csl: elsevier-harvard.csl
-output: rticles::elsevier_article
-
-header-includes:
-   - \usepackage[margin=1in]{geometry}
-   - \usepackage{lineno}
-   - \linenumbers
----
-
-<!-- This paper is an R markdown document that includes self-contained, reproducible analysis. To reproduce the paper the following files are needed:
-
-1. Dissonance_Santiago_v1.Rmd (this R markdown document)
-
-2.
-`Dissonance_Santiago.RData`.
-For reference: this data file was created using R notebook `00.
-Analysis of Dissonance Detailed.Rmd`.
-The initial analysis was done in the same R notebook.
-Neither of these two notebooks are needed for this document.
-
-3.
-For compiling into a pdf in the style of an Elsevier document: elsarticle.cls, elsevier-harvard.csl, elsevier-harvard-without-titles.csl, elsevier-vancouver.csl, elsevier-without-titles.cls, elsevier-with-titles.csl, elsevier-with-titles-alphabetical.csl, mybibfile.bib
--->
+## Keywords
+
+- Mode of travel  
+- Subjective wellbeing  
+- Dissonance  
+- Affective values  
+- Santiago de Chile  
+- Survey  
+- Data analysis
 
@@
 
-#load("Dissonance_Santiago.RData")
+#load("Dissonance_Santiago_v3/Dissonance_Santiago.RData")
 ```
@@
 
-Overall_dissonance <- master %>%
+Overall_dissonance <- Dissonance_Santiago %>%
   transmute(USED, 
@@
 
-Modes_by_Attribute <- master %>% 
+Modes_by_Attribute <- Dissonance_Santiago %>% 
   mutate(FREEDOM = strsplit(as.character(FREEDOM), ""),
@@
 Please note that this document  was prepared using R Markdown and is an example of reproducible research [@Brunsdon2020opening].
-The R Markdown file, along with the data file needed to reproduce the analysis, are available for download\footnote{\url{https://github.com/paezha/Mode-Dissonance-and-Subjective-Wellbeing}}.
+The R Markdown file, along with the data file needed to reproduce the analysis, are available for download [here](https://github.com/paezha/Mode-Dissonance-and-Subjective-Wellbeing).
 
@@
 As seen in the top panel of Figure \ref{fig:primary-mode-travel}, the three most common modes of travel are Metro, Bus, and Car, followed by Walking and Bicycle.
-For the analysis, we aggregate these modes into the following categories (bottom panel of Figure \ref{fig:primary-mode-travel}): (26% of total modes – which corresponds to 91% of the total of private motorized modes), Active (9% - Walking + Bicycle), Public (60% - Metro + Bus), and Other motorized modes (6% - Taxi + Colectivo + Motorcycle).
+For the analysis, we aggregate these modes into the following categories (bottom panel of Figure \ref{fig:primary-mode-travel}): (26% of total modes – which corresponds to 91% of the total of private motorized modes), Active (9% \- Walking + Bicycle), Public (60% \- Metro + Bus), and Other motorized modes (6% \- Taxi + Colectivo + Motorcycle).
 
@@
 
-The premise of this study is that a key component of subjective wellbeing is the affective reaction to experience [see the definition of wellbeing offered by the OECD; -@@oecd2013oecd].
+The premise of this study is that a key component of subjective wellbeing is the affective reaction to experience [see the definition of wellbeing offered by the OECD; -@oecd2013oecd].
 In this paper we investigated mode dissonance from the perspective of six affective values.

### 2021-02-20 ModeDissonanceSantiago.Rcheck/00_pkg_src/ModeDissonanceSantiago/R/addnums.R

@@ -1,3 +1,0 @@
-addnums <- function(a, b){
-  a + b
-}

### 2021-02-20 ModeDissonanceSantiago.Rcheck/ModeDissonanceSantiago-Ex.R

@@ -1,51 +1,0 @@
-pkgname <- "ModeDissonanceSantiago"
-source(file.path(R.home("share"), "R", "examples-header.R"))
-options(warn = 1)
-options(pager = "console")
-base::assign(".ExTimings", "ModeDissonanceSantiago-Ex.timings", pos = 'CheckExEnv')
-base::cat("name\tuser\tsystem\telapsed\n", file=base::get(".ExTimings", pos = 'CheckExEnv'))
-base::assign(".format_ptime",
-function(x) {
-  if(!is.na(x[4L])) x[1L] <- x[1L] + x[4L]
-  if(!is.na(x[5L])) x[2L] <- x[2L] + x[5L]
-  options(OutDec = '.')
-  format(x[1L:3L], digits = 7L)
-},
-pos = 'CheckExEnv')
-
-### * </HEADER>
-library('ModeDissonanceSantiago')
-
-base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
-base::assign(".old_wd", base::getwd(), pos = 'CheckExEnv')
-cleanEx()
-nameEx("hello")
-### * hello
-
-flush(stderr()); flush(stdout())
-
-base::assign(".ptime", proc.time(), pos = "CheckExEnv")
-### Name: hello
-### Title: Hello, World!
-### Aliases: hello
-
-### ** Examples
-
-hello()
-
-
-
-base::assign(".dptime", (proc.time() - get(".ptime", pos = "CheckExEnv")), pos = "CheckExEnv")
-base::cat("hello", base::get(".format_ptime", pos = 'CheckExEnv')(get(".dptime", pos = "CheckExEnv")), "\n", file=base::get(".ExTimings", pos = 'CheckExEnv'), append=TRUE, sep="\t")
-### * <FOOTER>
-###
-cleanEx()
-options(digits = 7L)
-base::cat("Time elapsed: ", proc.time() - base::get("ptime", pos = 'CheckExEnv'),"\n")
-grDevices::dev.off()
-###
-### Local variables: ***
-### mode: outline-minor ***
-### outline-regexp: "\\(> \\)?### [*]+" ***
-### End: ***
-quit('no')

### 2021-02-20 ModeDissonanceSantiago.Rcheck/ModeDissonanceSantiago/doc/ModeDissonanceSantiago-vignette.R

@@ -1,0 +1,40 @@
+## ---- include = FALSE---------------------------------------------------------
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>"
+)
+
+## ----setup--------------------------------------------------------------------
+library(ModeDissonanceSantiago)
+
+## ----packages-----------------------------------------------------------------
+library(dplyr)
+library(ggplot2)
+
+## ----help-dataset-------------------------------------------------------------
+?Dissonance_Santiago
+
+## ----summary-dataframe--------------------------------------------------------
+summary(Dissonance_Santiago)
+
+## ----convert-used-to-factor---------------------------------------------------
+library(dplyr)
+Dissonance_Santiago <- Dissonance_Santiago %>%
+  mutate(USED = factor(USED, 
+                       levels = c("A", "B", "C", "D", "E", "F", "G", "H"),
+                       labels = c("Car",
+                                  "Taxi",
+                                  "Colectivo",
+                                  "Moto",
+                                  "Metro",
+                                  "Bus",
+                                  "Bicycle",
+                                  "Walk")))
+
+## ----summary-used-------------------------------------------------------------
+summary(Dissonance_Santiago$USED)
+
+## ----bar-plot-used------------------------------------------------------------
+ggplot(data = Dissonance_Santiago, aes(x = USED)) +
+  geom_bar()
+

### 2021-02-20 Dissonance_Santiago_v3/Dissonance_Santiago_v3.Rmd
Knitted REAMDE.Rmd and v3 of paper after checking data package

@@
 # Run only once if needed
-devtools::install_github("paezha/Mode-Dissonance-and-Subjective-Wellbeing", subdir = "ModeDissonanceSantiago")
+#devtools::install_github("paezha/Mode-Dissonance-and-Subjective-Wellbeing", subdir = "ModeDissonanceSantiago")
 ```
 
-```{r}
+```{r load-data-package, include=FALSE}
 library(ModeDissonanceSantiago)
@@
 ```{r figure-primary-mode-travel, fig.width= 4, fig.height=6, echo=FALSE, cache = TRUE,  fig.cap="\\label{fig:primary-mode-travel}Frequency of primary mode used for regular commute; top panel: all modes, bottom panel: aggregated modes"}
-mode_plot1 <- ggplot(data = master, aes(x = factor(USED, levels = c("A", "G", "H", "E", "F", "B", "C", "D"),
+mode_plot1 <- ggplot(data = Dissonance_Santiago, aes(x = factor(USED, levels = c("A", "G", "H", "E", "F", "B", "C", "D"),
                                                    labels = c("Car", "Bicycle", "Walk", "Metro", "Bus", "Taxi", "Colectivo", "Motorcycle")),

### 2021-02-20 Dissonance_Santiago_v3/Dissonance_Santiago_v3.tex
Knitted REAMDE.Rmd and v3 of paper after checking data package

@@
 analysis, are available for
-download\footnote{\url{https://drive.google.com/open?id=189ZvfVvRis5xZA9IlviKCLW2bwbPJAgg}}.
+download\footnote{\url{https://github.com/paezha/Mode-Dissonance-and-Subjective-Wellbeing}}.
 

### 2021-02-20 README.Rmd
Knitted REAMDE.Rmd and v3 of paper after checking data package

@@
 kable(xtab_results,
-      "latex",
+      "html",
       digits = 2,
